### 2019-12-12 protocol/protocol.tex
prepare records

\documentclass[10pt, a4paper]{article}
\usepackage[utf8]{inputenc}

% Format
\setlength{\parindent}{0.5in}
\usepackage{layout}

% Font
\usepackage{MinionPro}
\input glyphtounicode
\pdfgentounicode=1
\usepackage{microtype}
\usepackage[super]{nth}

% Links
\usepackage[colorlinks=true, linkcolor=black, urlcolor=black, citecolor=black]{hyperref}

% Language
\usepackage[british]{babel}

% References
\usepackage[bibnewpage, unnumberedbib]{apacite}

% Figures
\usepackage{graphicx}
\usepackage[small, labelfont=it, labelsep=period]{caption}

% Tables
\usepackage{booktabs}
\usepackage{ltablex}

% Frontmatter
\title{Protocol:\\\textit{Meta-analysis of the\\`ironic' effects of intergroup contact}}
\date{March 22, 2019}

\begin{document}
\maketitle

\begin{abstract}
\noindent This is the preregistered protocol for our meta-analysis of the relationship between intergroup contact and support for social change among members of disadvantaged groups. This protocol follows the PRISMA-P guidelines \cite{moher_prismap_2015, shamseer_prismap_2015} for preparing a systematic review protocol.
\end{abstract}

\section{Introduction}

\subsection{Rationale}
\label{sec:rationale}

In this meta-analysis, we are considering more than a decade of empirical research \cite{dixon_intergroup_2007} on the potential `ironic' \cite{saguy_irony_2009}, `sedative' \cite{cakal_investigation_2011}, or `demobilising' \cite{dovidio_reducing_2017} effects of intergroup contact.

Prior research  mostly studied intergroup contact as a means to reduce prejudice and social conflict (for a meta-analysis, see \citeNP{pettigrew_meta_2006}). Most research on intergroup contact had studied members of advantaged or `majority' groups (for a meta-analysis, see \citeNP{tropp_meta_2005}). Reducing prejudice among advantaged-group members had been advocated as a way to reduce discrimination and to foster positive social change. Following initial theorising by \citeA{wright_strategic_2001}, \citeA{dixon_beyond_2005}, and \citeA{reicher_rethinking_2007}, researchers begun studying whether, in historically unequal societies, intergroup contact could instead \emph{hinder} social change by reducing support for social change among members of disadvantaged or `minority' groups. Since \citeauthor{dixon_intergroup_2007}'s \citeyear{dixon_intergroup_2007} first empirical test of this hypothesis, a growing number of studies have examined the relationships between intergroup contact and social change among disadvantaged-group members.

To date, this literature has been the subject of narrative reviews \cite<for example,>{mckeown_contact_2017}, but not of a systematic review or quantitative synthesis. Filling this gap, this protocol outlines a systematic review and meta-analysis of the so-called `ironic' effects of intergroup contact. This endeavour allows us to quantify the strength of the relevant relationships and to identify potential shortcomings of the available evidence.

\subsection{Objectives}
\label{sec:objectives}

In this meta-analysis, we examine the relevant literature to answer the following research questions:

\begin{enumerate}
\item [Q0] \emph{Does intergroup contact help or hinder social change?} For this review, we define social change as a reduction in social inequality that improves the situation of disadvantaged groups in a society. Though this question motivates our review, the meta-analysis will not conclusively answer whether, on balance, intergroup contact helps or hinders social change. By answering Q1--Q3, however, our review will test the most prominent hypotheses explaining how intergroup contact \emph{could} hinder social change.
\item [Q1] \emph{Does contact with advantaged-group members reduce collective action among dis\-ad\-vant\-aged-group members?} Our review uses \citeauthor{wright_collective_2010}'s \citeyear{wright_collective_2010} definition of collective action as any action taken to improve the ingroup's position in society. As such, collective action (by disadvantaged-group members) challenges the status quo and, if successful, improves the situation of the disadvantaged ingroup. To the extent that it prevents collective action, intergroup contact hinders social change.
\item [Q2] \emph{Does contact with advantaged-group members reduce dis\-ad\-vant\-aged-group members' support for policies that would benefit their ingroup?} Redistributive policies (for example, affirmative action) and similar initiatives can be important means to reduce social inequality. Members of disadvantaged groups, who stand to benefit from their implementation, are important advocates for these policies. To the extent that it reduces support for such policies, intergroup contact hinders social change.
\item [Q3] \emph{Does contact with advantaged-group members reduce perceptions of injustice among disadvantaged-group members?} Some researchers \cite<e.g.,>{saguy_irony_2009} suggest that intergroup contact could lull dis\-ad\-vant\-aged-group members into a false sense of equality. Being aware of the injustice faced by the ingroup, however, is an important prerequisite to instigating social change \cite{zomeren_toward_2008}. In addition, accurately perceiving the social reality is likely important to coping in a society marked by inequality. To the extent that it reduces perceptions of injustice, intergroup contact hinders social change.
\end{enumerate}

\noindent For Q1--Q3, we explore the following questions:

\begin{enumerate}
\item [QA]	\emph{What is the direction of the relationship between intergroup contact and the outcome variable?}
\item [QB]	\emph{How strong is the relationship between intergroup contact and the outcome variable?}
\item [QC]	\emph{How much does the relationship vary across study designs, measures, and settings?}
\end{enumerate}

\noindent Beyond the meta-analysis, we use the information collected on each study to review the quality of the available evidence and to identify gaps and limitations in the literature. Below, we describe the methods used to find, describe, and synthesise relevant studies.

\section{Methods}

\subsection{Eligibility criteria}
\label{sec:eligibility-criteria}

In this meta-analysis, we are considering studies that \textit{i.} included \textbf{participants} of a relatively disadvantaged group, see \emph{Types of participants}, that \textit{ii.} manipulated or measured \textbf{intergroup contact} with a relatively advantaged group, see \emph{Types of predictor variables}, and that \textit{iii.} measured \textbf{one or more} of: \textbf{collective action} (intentions), \textbf{support for policies} that benefit or harm the participants' ingroup, and/or perceptions or expectations of \textbf{injustice}, see \emph{Types of outcome variables}. Below, we discuss these criteria in detail.

\subsubsection{Types of studies}
We include quantitative studies of all designs, as long as they fulfil the criteria laid out above. We consider study design features as possible moderators of study effect size.

\subsubsection{Types of participants}
We include samples of participants whose ingroup is disadvantaged (in terms of status, power, and/or resources) relative to the outgroup they have (or report to have) contact with.

\subsubsection{Types of predictor variables}
\label{sec:predictor-variables}

We include studies if they measure or manipulate the quantity of, quality of, and opportunity for contact with members of outgroups that are relatively advantaged (in terms of status, power, and/or resources) compared to the participants' ingroup (see \emph{Types of participants}). We consider both positive and negative contact, where both are measured. We consider opportunity for contact, as it is a potential precursor to face-to-face contact, but not imagined or indirect contact.

\subsubsection{Types of outcome variables}
\label{sec:outcome-variables}

We include studies that measure \textbf{at least one} of the following outcome variables:

\begin{description}
\item[Collection action.] We consider measures of observed, reported, or intended engagement in any action aimed at improving the position of the participants' ingroup in society, including participating in protests, signing petitions, and other forms of violent or non-violent collective action. 
\item[Policy support.] We consider studies that measure support for policies and initiatives designed to improve the position the participants' ingroup in society.
\item[Perceived injustice.] We consider studies that measure perceptions that one is discriminated against because of one's group membership, that one's group faces discrimination in society, that one's group is relatively deprived compared to other groups, or that the deprivation and/or discrimination faced by one's group is unjust/illegitimate. We also consider expectations of fair treatment as the reverse of perceived injustice. We include studies that measure \textit{personal} and/or \textit{group} discrimination or a mixture of both.
\end{description}

\subsubsection{Other criteria}

We do not use any other criteria for eligibility for the meta-analysis.

\subsection{Information sources}
\label{sec:information-sources}

To find relevant studies, we retrieve records from electronic databases, including \emph{Scopus}, an abstract and citation database of peer-reviewed literature, the \emph{Scopus} secondary documents database\footnote{``A secondary document is a document that has been extracted from a Scopus document reference list but is not available directly in the Scopus database since it is not indexed by Scopus.''}, and \emph{PsycINFO}, an abstract database of psychological literature. We also search the \emph{ProQuest Dissertations and Theses} database for relevant grey literature. To find unpublished studies, we have sent a call for unpublished research to the mailing lists of the \emph{European Association of Social Psychology} and the \emph{Society for Personality and Social Psychology} (June/July, 2017). We send another call for unpublished research closer to publication in which we also include the mailing lists of the \emph{International Society of Political Psychology}, the \emph{Society for the Psychological Study of Social Issues}, and the \emph{Society of Australasian Social Psychologists}. To achieve more complete coverage, we retrieve records that cite, or are cited by, the included studies. We also identify experts in the field and send a list of included studies to them, asking for any studies we have missed. We consider all relevant studies published before \textbf{April 1, 2019}, as well as all unpublished studies. We update our database searches \textbf{every four months} until we submit our manuscript for publication.

\subsection{Search strategy}
\label{sec:search-strategy}

We developed a search strategy for locating studies that include the relevant predictor and outcome measures. We search titles, abstract, and keywords for relevant terms in four electronic databases. We search for relevant records in the \emph{Scopus} database using the following search terms:
\small
\begin{enumerate}
\item TITLE-ABS-KEY(*group AND (contact OR friendship) AND (``collective action'' OR protest OR ``collective behavio*r'' OR ``political behavio*r'' OR ``social change'' OR ``social justice''))
\item TITLE-ABS-KEY(*group AND (contact OR friendship) AND (policy OR policies OR ``affirmative action'' OR (politi* W/15 attitude*) OR (politi* W/15 preferenc*)) AND (redistribut* OR reparati* OR inequalit* OR equalit* OR injustice* OR justice* OR disadvantage* OR advantage* OR minorit* OR majorit*))
\item TITLE-ABS-KEY((contact OR friendship) AND (``perceived discrimination'' OR ``perceived *advantage'' OR ``relative deprivation'' OR ``group discrimination'' OR ``personal discrimination'' OR ``group deprivation'' OR ``perception* of discrimination'' OR ``perception* of group discrimination'' OR ``perception* of personal discrimination'' OR ``rac* discrimination''))
\end{enumerate}
\normalsize
We use the same terms to retrieve relevant records from the \emph{Scopus} secondary documents database. We retrieve relevant records from \emph{PsycINFO} using similar search terms:
\small
\begin{enumerate}
\item (``*group'' AND (contact OR friendship) AND (``collective action'' OR protest OR ``collective behavio*r'' OR ``political behavio*r'' OR ``social change'' OR ``social justice'')).ti,ab,id.
\item (``*group'' AND (contact OR friendship) AND (policy OR policies OR ``affirmative action'' OR (politi* AND attitude*) OR (politi* AND preferenc*)) AND (redistribut* OR reparati* OR inequalit* OR equalit* OR injustice* OR justice* OR disadvantage* OR advantage* OR minorit* OR majorit*)).ti,ab,id.
\item ((contact OR friendship) AND (``perceived discrimination'' OR ``perceived *advantage'' OR ``relative deprivation'' OR ``group discrimination'' OR ``personal discrimination'' OR ``group deprivation'' OR ``perception* of discrimination'' OR ``perception* of group discrimination'' OR ``perception* of personal discrimination'' OR ``rac* discrimination'')).ti,ab,id.
\end{enumerate}
\normalsize
We search for grey literature in the \emph{ProQuest Dissertations and Theses} database using the following search terms:
\small
\begin{enumerate}
\item NOFT(group AND (contact OR friendship) AND (``collective action'' OR protest OR ``collective behavio*r'' OR ``political behavio*r'' OR ``social change'' OR ``social justice''))
\item NOFT(group AND (contact OR friendship) AND (policy OR policies OR ``affirmative action'' OR (politi* N/15 attitude*) OR (politi* N/15 preferenc*)) AND (redistribut* OR reparati* OR inequalit* OR equalit* OR injustice* OR justice* OR disadvantage* OR advantage* OR minorit* OR majorit*))
\item NOFT((contact OR friendship) AND (``perceived discrimination'' OR ``perceived disadvantage'' OR ``perceived advantage'' OR ``relative deprivation'' OR ``group discrimination'' OR ``personal discrimination'' OR ``group deprivation'' OR ``perception* of discrimination'' OR ``perception* of group discrimination'' OR ``perception* of personal discrimination'' OR ``rac* discrimination''))
\end{enumerate}
\normalsize
We export records from each database, compile meta-data (incl. authors, title, abstract, keywords, doi, link to full-text document), and remove duplicate records. If we find search terms to be inadequate, we will amend them and report these amendments. We use \emph{Google Scholar} to find relevant records that cite any of the included studies.

\subsection{Study selection}
\label{sec:study-selection}

We select relevant studies in three steps. First, we screen records based on their title, abstract, and keywords. We divide records between two coders who each screen half of the records. We randomly select 100 records to be screened by both coders to calculate inter-rater agreement (Cohen's $\kappa$). For each record, coders decide whether the record meets the eligibility criteria (\emph{yes}, \emph{maybe}, \emph{no}), or whether it is a relevant review article. We exclude all records for which coders answered ``no'', but keep all records for which coders answered ``yes'' or ``maybe''. Second, two coders each review each of the full-text manuscripts and code whether any sample in the manuscript fulfils the eligibility criteria (see Section~\ref{sec:eligibility-criteria}). We calculate and report inter-rater agreement (Cohen's $\kappa$) for each eligibility criterion. Third, we resolve any disagreements between the two coders (by consensus) and exclude ineligible studies. At this stage, we also search for relevant records that cite, or are cited by, any of the included studies or relevant reviews. Figure~\ref{fig:f1} illustrates the study selection process. We use \emph{Qualtrics} and/or \emph{formr} \cite{arslan_formr_2018} surveys to screen and code studies.

\begin{figure}
\centering
\includegraphics[scale = 1]{coding-diagram}
\caption{Diagram illustrating how two coders search for records, select studies, and collect data for this meta-analysis.}
\label{fig:f1}
\end{figure}

\subsection{Data collection}
\label{sec:data-collection}

We collect the relevant data in two steps. First, we code moderating variables to be used in (exploratory) meta-regression analyses (see Section~\ref{sec:exploratory-analyses}). We decide which moderators to code based on a first review of the included studies. At the very least, we code publication status (\emph{published}, \emph{unpublished}, \emph{unpublished dissertation}), study setting (\emph{ingroup}, \emph{outgroup}, \emph{location}), study design (\emph{cross-sectional}, \emph{longitudinal}, \emph{quasi-experimental}, \emph{experimental}), and study sample (\emph{student}, \emph{community}, \emph{representative}). Two coders each review each of the included full-text manuscripts. We calculate and report inter-rater agreement (Cohen's $\kappa$) for each moderating variable.

% Add additional moderators!

Second, we extract correlation coefficients ($r$) as the relevant measure of effect size, and extract sample sizes ($n$) to calculate standard errors for each sample's correlation coefficients (see Section~\ref{sec:data-synthesis}). Where provided, we copy correlation coefficients from the relevant correlation matrices. Where other effect-size measure are provided, we convert the reported effect sizes to correlation coefficients using common conversion formulas \cite{borenstein_introduction_2009}. Where no effect sizes are provided, we attempt to contact the authors to obtain the relevant correlation matrices or other effect-size measures. If that fails, we impute correlation coefficients from beta coefficients \cite{peterson_beta_2005} if possible.\footnote{$r = \beta + 0.05\lambda$ where $\lambda = 1$ when $\beta \geq 0$ and $\lambda = 0$ when $\beta < 0$ .} If we fail to obtain, calculate, or impute $r$ or $n$ for a sample, we report our failure to do so and exclude the sample from the meta-analysis. At this stage, we also look for samples that might have been reported more than once in the included literature. We consider author names, effect sizes, sample sizes, and other sample characteristics as indicators for duplicate studies. We might contact authors to resolve concerns about the identity of published studies.

We collect effect sizes for all predictor and outcome variables defined in Section~\ref{sec:eligibility-criteria}, as well as all inter-scale correlations. Where more than one measure is reported, we extract effect sizes for all relevant measures.  In addition, we extract effect sizes for five other measures that might be relevant for exploratory or future analyses: negative contact, ingroup contact, group identification, group-based anger, and outgroup attitudes.

\subsection{Outcome selection}
\label{sec:outcome-selection}

As discussed, we collect data for all relevant predictor and outcome variables defined in Section~\ref{sec:eligibility-criteria}. When a study reports more than one measure of \emph{intergroup contact} (Section~\ref{sec:predictor-variables}), we prioritise the predictor variable in our confirmatory analyses (Section~\ref{sec:confirmatory-analyses}) that measure the most intense or intimate form of contact. We rate contact intensity according to the following ranking: friendship $>$ quality of contact (positive contact) $>$ quantity of contact $>$ opportunity for contact. % that is the focus of the manuscript's primary analysis. If it is unclear what the manuscript's primary analysis is---or if the manuscript's primary analyses considers more than one measure---we combine and average effect sizes across predictor variables. 
If it is unclear which of two predictor variables measures a more intense form of contact, we combine and average effect sizes across these variables. We do not consider negative contact or ingroup contact in our confirmatory analyses.

When a study reports more than one measure of one or more of the outcome variables defined in Section~\ref{sec:outcome-variables}, we proceed as follows: If a manuscript's primary analysis focuses on one of several \emph{collective action} measure, we prioritise that measure; otherwise, we combine and average effects sizes across outcome variables. If a study reports more than one measure of \emph{policy support}, we combine and average effect sizes for all policies designed to improve the position of the participants' ingroup in society. If a study reports more than one measure of \emph{perceived injustice}, we prioritise the measure closest to perceptions of injustice against the participants' ingroup (rather than against the participants themselves); if it is ambiguous which measure that is, we combine and average effect sizes across outcome variables.

Some study designs result in more than one effect size for the same (combination of) measures. If a \emph{longitudinal} study reports results from more than two waves, we prioritise effect sizes spanning the inter-survey interval closest to one year. If a longitudinal study reports results from more than two waves and spans multiple years, we combine and average effects sizes from each one-year inter-survey interval. In our confirmatory analyses, we focus on the partial correlation between the relevant predictor variable (at time 1) and outcome variable (at time 2) controlling for initial levels of the outcome variable (cross-lagged correlation). If an \emph{experimental} or \emph{quasi-experimental} study reports comparisons between more than two conditions, we prioritise the effect size that compares two conditions that most closely resemble generic contact and no-contact conditions. If it is ambiguous which conditions those are, we combine and average effect sizes comparing experimental conditions to the control condition. We record all decisions about variable selection and data simplification in the published protocol.

\subsection{Data synthesis (meta-analysis)}
\label{sec:data-synthesis}

As discussed, we extract correlation coefficients ($r$) as the relevant measure of effect size. Correlation coefficients, however, are bounded between $-1$ and $1$ and are not suitable for linear regression techniques. Therefore, we convert $r$ to Fisher's $z$, which is unbounded and approximately normally distributed.
\begin{align}
z & = \frac{1}{2} \ln\left(\frac{1 + r}{1 - r}\right) \label{eq:1} \\
\sigma & = \frac{1}{\sqrt{n - 3}} \label{eq:2} \\
r &= \frac{\exp(2z) - 1}{\exp(2z) + 1} = \tanh(z) \label{eq:3}
\end{align}
For each sample, we use equation~\ref{eq:1} to convert $r$ to $z$, and use equation~\ref{eq:2} to calculate the corresponding standard error $\sigma$ from the sample size $n$. We use equation~\ref{eq:3} to convert the effect-size estimates from our meta-analysis back to correlation coefficients.

We estimate Bayesian random-effects meta-analysis models in RStan \cite{rstan_package} using $z$-transformed correlation coefficients as outcome variables:
\begin{align}
z_{ij} &\sim \text{Normal}(\theta_{ij}, \sigma_{ij}) \tag{Likelihood} \\
\theta_{ij} &= 
  \begin{cases} 
    \mu + \textbf{X}\beta_K + \beta_j\tau_J & \text{if } I_j = 1 \\
    \mu + \textbf{X}\beta_K + \beta_j\tau_J + \beta_i\tau_I & \text{if } I_j > 1 
  \end{cases} \tag{Regression}
\end{align}
where $z_{ij}$ is the observed effect size in sample $i$ of study $j$, $\sigma_{ij}$ is the corresponding standard error, and $\theta_{ij}$ is the estimated effect size for sample $i$ of study $j$. We estimate $z_{ij}$ as a function of the estimated mean effect size $\mu$ and, if included, of a matrix $\textbf{X}$ of $K$ observed moderators multiplied by a corresponding vector of $K$ coefficients $\beta_K$. We estimate two varying intercepts, $\beta_i$ and $\beta_j$, with the corresponding standard deviations, $\tau_i$ and $\tau_j$. For studies that contain only one sample ($I_j = 1$), we only estimate $\beta_j$, the study-wise deviation from the mean effect size $\mu$. For studies that contain more than one sample ($I_j > 1$), we also estimate $\beta_i$, the sample-wise deviation from the study-specific effect size. We use the non-centred parameterisation for the varying effects \cite{betancourt_hamilton_2015}. The resulting model is a two-level random-effects meta-analysis.

Models assigned weakly informative prior distributions \cite{gelman_prior_2017} to all estimated parameters:
\begin{align*} 
\mu &\sim \text{Normal}(0, 0.31605) \\
\beta_i &\sim \text{Normal}(0, 1) \\
\beta_j &\sim \text{Normal}(0, 1) \\
\beta_k &\sim \text{Normal}(0, 1) \\
\tau_I &\sim \text{Half-Cauchy}(0, 0.3) \\
\tau_J &\sim \text{Half-Cauchy}(0, 0.3)
\end{align*}
Figure~\ref{fig:f2} shows the prior distributions for $\mu$, the mean effect size, and $\tau$, the standard deviation of the varying intercepts. The prior distribution for $\mu$ is centred around $0$ and concentrates $50\%$ of the most plausible values between $r = -0.21$ and $r = 0.21$. We focus on $|r| = 0.21$ because it corresponds to the mean effect size observed in both \citeauthor{pettigrew_meta_2006}'s \citeyear{pettigrew_meta_2006} meta-analysis of the contact literature and \citeauthor{richard_meta_2003}'s \citeyear{richard_meta_2003} meta-analysis of effect sizes across a century of social-psychological research. The prior distribution for $\tau$ allocates $30\%$ of plausible values below $\tau = 0.15$. We focus on $\tau = 0.15$ because it corresponds to the standard deviations observed in both \citeauthor{pettigrew_meta_2006}'s \citeyear{pettigrew_meta_2006}\footnote{We estimated $\tau$ in a one-level random-effects meta-analysis using data from \citeA{pettigrew_meta_2006}.} and \citeauthor{richard_meta_2003}'s \citeyear{richard_meta_2003} meta-analyses. We chose this prior distribution following recommendations by \citeA{williams_bayesian_2018}.

\begin{figure}
\centering
\includegraphics[width = \textwidth]{prior-choice}
\caption{Prior distributions for $\mu$ and $\tau$. (A) Prior distribution for $\mu$ converted from Fisher's $z$ to $r$. The $\text{Normal}(0, 0.31605)$ distribution is centred around $0$ and concentrates $50\%$ of the most plausible values between $r = -0.21$ and $r = 0.21$. (B) Prior distribution for $\tau$. The $\text{Half-Cauchy}(0, 0.3)$ distribution is strictly positive and concentrates $50\%$ of the most plausible values below $\tau = 0.30$.}
\label{fig:f2}
\end{figure}

\subsubsection{Confirmatory analyses}
\label{sec:confirmatory-analyses}

\begin{figure}
\centering
\includegraphics[scale = 1]{path-diagram}
\caption{Path diagram illustrating all correlations that are estimated in our confirmatory analyses.}
\label{fig:f3}
\end{figure}

We conduct confirmatory analyses to answer research questions Q1--Q3 (Section~\ref{sec:objectives}). Specifically, we run six two-level random-effect meta-analysis models (without moderators) to estimate the correlations between intergroup contact and perceived discrimination ($r_1$), policy support ($r_2$), and collective action ($r_3$), as well as the correlations between all three outcome variables ($r_{12}$, $r_{13}$, $r_{23}$), as illustrated in Figure~\ref{fig:f3}. Each model includes only studies/samples that contain the relevant combination of variables. Each model considers predictor and outcome variables as defined in Section~\ref{sec:outcome-selection}.

\subsubsection{Sensitivity analyses}
\label{sec:sensitivity-analyses}

To assess the robustness of our conclusions, we conduct two kinds of sensitivity analysis. First, we assess to what extent our findings are sensitive to choosing different prior distributions. We repeat the main analyses ($r_{1}$, $r_{2}$, $r_{3}$) with narrower, $\mu \sim \text{Normal}(0, 0.1)$, and wider, $\mu \sim \text{Normal}(0, 1)$, prior distributions. Second, we assess to what extent our findings are sensitive to including or excluding influential studies. We rerun the main analyses $J$ times---leaving out one of $J$ studies each time---and record how much $\mu$, the estimated mean effect size, varies across left-out studies. We calculate the mean absolute error (\textit{MAE}) and compare the study-wise absolute errors ($|\mu_K - \mu_{-k}|$) to identify the most influential studies.
% Third, we assess to what extent our findings are sensitive to studies with large sample sizes. We repeat the main analyses using $\sigma = \frac{1}{\log(n - 3)}$ instead of $\sigma = \frac{1}{\sqrt{n - 3}}$, the correct formula for the standard error. This function decreases much less steeply as $n$ increases, thus reducing the weight of studies with large sample sizes. 
We might report these analyses in an appendix to the published manuscript.

\subsubsection{Exploratory analyses}
\label{sec:exploratory-analyses}

We conduct exploratory analyses to estimate how much the strength of the relevant relationships varies across study designs, study settings, predictor variables, outcome variables, and other (potential) moderating variables. We explore these relationships in a series of two-level random-effect meta-analysis models with moderators. We enter moderating variables with $K$ categories as $K - 1$ mean-centred dummy variables. We run additional meta-analysis models (without moderators) to estimate the partial correlations between the outcome variables and positive/negative contact and ingroup/outgroup contact---if we find enough studies that measure these predictor variables. We consider these analyses exploratory because they are guided by the available data.

\subsection{Meta-biases}
\label{sec:meta-biases}

Publication bias, outcome reporting bias, and (other) questionable research practices in the relevant literature can lead meta-analyses to overestimate effect sizes. Developing methods to detect and correct for such biases is an active area of research, with no available method outperforming all others \cite{carter_correcting_2017}. We assume that the literature underlying our meta-analysis is subject to these meta-biases. We accept that, in lieu of wide-spread adoption of preregistration, detecting and correcting for these biases is difficult or impossible. Nonetheless, we attempt to quantify meta-biases in the relevant literature as follows: First, we test for publication bias by comparing the mean effect sizes of published and unpublished studies. Second, we explore publication bias and other meta biases using statistical methods to detect and correct these biases. We select these methods based on the current state of the literature. We discuss meta-biases as a potential limitation in the published manuscript.

\section{PRISMA-P (2015) checklist}

\figureversion{lining, tabular}
\small
\label{tab:t1}
\begin{tabularx}{\linewidth}{lrX} 
\caption{We explain how this protocol addresses each of the \emph{preferred reporting items for systematic review and meta-analysis protocols} (PRISMA-P; \protect\citeNP{moher_prismap_2015}), and respond to items that we have not yet addressed. \protect\citeA{shamseer_prismap_2015} explain and elaborate all recommended items.} \\
\toprule
Section/Topic~~~~~~~~~~~~~~~~~~~~~ & \# & Response \\ 
\midrule 
\addlinespace 
\endhead
\textit{Administrative information} & & \\ \addlinespace
Title: & & \\
~~~~Identification & 1a & The title identifies the report as the protocol for a meta-analysis.\\
~~~~Update & 1b & This meta-analysis is not an update or extension of any existing systematic review or meta-analysis. \\ \addlinespace
Registration & 2 & This protocol was preregistered with the Open Science Framework on the date stated on the title page. \\ \addlinespace 
Authors: & & \\
~~~~Contact & 3a & To facilitate blind peer review, we do not provide author names or contact information in this preregistered protocol. Below, we refer to the first and second author of the manuscript as A1 and A2.\\
~~~~Contributions & 3b & A1 is the guarantor. A1 and A2 jointly wrote this protocol. A1 contributed the statistical methods to be used in the meta-analysis. A1 and A2 serve, respectively, as Coder~1 and Coder~2 (Figure~\ref{fig:f1}). All authors approved this protocol.
\\ \addlinespace
Amendments & 4 & If we need to amend this protocol, we describe and justify all deviations from this preregistered protocol in the published protocol. \\ \addlinespace
Support: & & \\
~~~~Sources & 5a & No funding has been received for this meta-analysis. We will disclose any future funding received for this meta-analysis. \\
~~~~Sponsor & 5b & N/A \\
~~~~Role of sponsor or funder & 5c & N/A \\ \addlinespace \midrule \addlinespace
\textit{Introduction} & & \\ \addlinespace 
Rationale & 6 & Section~\ref{sec:rationale} summarises the rationale for the meta-analysis. \\ \addlinespace
Objectives & 7 & Section~\ref{sec:objectives} outlines the research questions that the meta-analysis addresses. \\ \addlinespace \midrule \addlinespace
\textit{Methods} & & \\ \addlinespace 
Eligibility criteria & 8 & Section~\ref{sec:eligibility-criteria} spells out all criteria for eligibility for the meta-analysis. \\ \addlinespace 
Information sources & 9 & Section~\ref{sec:information-sources} describes all intended information sources, as well as the planned dates of coverage. \\ \addlinespace 
Search strategy & 10 & Section~\ref{sec:search-strategy} describes our search strategy for four electronic databases, while the planned dates of coverage are described in Section~\ref{sec:information-sources}. \\ \addlinespace
Study records: & & \\
~~~~Data management & 11a & We do not use a dedicated systematic review data management software. We export records from electronic databases as .csv (or similar) files; we import .csv (or similar) files into \emph{R} to compile meta-data and to remove duplicate records \cite{revtools_package}. We use \emph{Qualtrics} and/or \emph{formr} \cite{arslan_formr_2018} surveys to screen and code studies (see Section~\ref{sec:study-selection}). \\
~~~~Selection process & 11b & Section~\ref{sec:study-selection} and Figure~\ref{fig:f1} describe how we select studies for inclusion in the meta-analysis. \\
~~~~Data collection process & 11c & Section~\ref{sec:data-collection} and Figure~\ref{fig:f1} describe how we collect data for each included study/sample. \\ \addlinespace
Data items & 12 & Section~\ref{sec:data-collection} lists all data that is collected; Section~\ref{sec:outcome-selection} explains all pre-planned data simplifications.\\ \addlinespace
Outcomes and prioritization & 13 & Section~\ref{sec:data-collection} describes for which predictor and outcome variables we extract effect sizes; Section~\ref{sec:outcome-selection} explains which predictor and outcome variables are prioritised in our confirmatory analyses.\\ \addlinespace
Risk of bias in individual studies & 14 & We explore study design as a potential source of bias (Section~\ref{sec:exploratory-analyses}). We include all eligible studies in our confirmatory analyses, independent of their risk of bias.\\\addlinespace
Data synthesis & 15a & We will conduct random-effects meta-analyses as described in Section~\ref{sec:data-synthesis}. \\
~~~~ & 15b & Section~\ref{sec:data-synthesis} describes our method for combining data from studies as well as the planned summary methods ($\mu$, $\tau_J$, $\tau_I$). Section~\ref{sec:confirmatory-analyses} proposes confirmatory analyses for answering research questions Q1--Q3.\\
~~~~ & 15c & Sections \ref{sec:sensitivity-analyses} and \ref{sec:exploratory-analyses} propose additional sensitivity and exploratory analyses. \\
~~~~ & 15d & Quantitative synthesis is appropriate for answering research questions Q1--Q3. We will discuss strengths and limitations of the available evidence in a narrative review. \\ \addlinespace
Meta-bias(es) & 16 & Section~\ref{sec:meta-biases} describes our approach to exploring meta-biases in the relevant literature. \\ \addlinespace
Confidence in cumulative evidence & 17 & We do not use a formal approach for assessing the quality of the available evidence, but discuss strengths and limitations of the available evidence in a narrative review.\\
\addlinespace \bottomrule
\end{tabularx}

\bibliographystyle{apacite}
\bibliography{references}

\end{document}

### 2019-12-12 protocol/prior_choice.R

@@ -1,0 +1,89 @@
+rm(list = ls())
+
+# Load packages -----------------------------------------------------------
+  library(tidyverse)
+
+
+# Choose ------------------------------------------------------------------
+  
+  # Prior for mu (chosen for 50% to fall between -0.21 <= r <= 0.21)
+  f <- function(sigma) abs(tanh(qnorm(p = 0.75, mean = 0, sd = sigma)) - 0.21) 
+  sigma <- optimise(f, lower = 0, upper = 1, tol = 1e-10)$minimum
+  mu_prior <- function(x, sd = sigma) dnorm(x = atanh(x), mean = 0, sd = sd)
+  curve(mu_prior, from = -1, to = 1)
+  
+  # Prior for tau (chosen after Williams, Rast, & Bürkner, 2018)
+  tau_prior <- Vectorize(function(x)  {
+    if_else(x >= 0, dcauchy(x, location = 0.00, scale = 0.30)/0.5, 0)
+  })
+  curve(tau_prior, from = 0, to = 2)
+  integrate(tau_prior, 0, 0.15)
+  integrate(tau_prior, 0, 0.30)
+  
+
+# Visualise ---------------------------------------------------------------
+  
+  # Prior for mu
+  mu_plot <- ggplot(NULL, aes(x = -1:1)) +
+    geom_vline(xintercept = c(-0.21, 0.21), linetype = "dashed", colour = "grey20", size = 0.364) +
+    stat_function(
+      fun = mu_prior,
+      geom = "area",
+      n = 1e4, 
+      fill = "grey20",
+      alpha = 0.2,
+      xlim = c(-0.21, 0.21)
+    ) +
+    stat_function(
+      fun = mu_prior, 
+      n = 1e4, 
+      aes(colour = "N(0, 0.31605)"),
+      size = 0.5
+    ) +
+    scale_x_continuous(breaks = c(seq(-1, 1, 0.5), -0.21, 0.21)) +
+    scale_colour_manual(values = c("#D81B60")) +
+    coord_fixed(4/3, ylim = c(0, 1.5), expand = FALSE) +
+    theme_bw(base_size = 8) +
+    theme(
+      legend.position = c(0.95, 0.05),
+      legend.justification = c(1, 0),
+      legend.background = element_rect(colour = "grey20"),
+      panel.grid.minor = element_blank()
+    ) +
+    labs(
+      tag = "A",
+      x = expression(tanh(mu)),
[…]

### 2020-08-21 manuscript/manuscript.Rmd
major update

---
title: "Meta-analysis of the `ironic' effects of intergroup contact"
author:
  - Nils K. Reimer
  - Nikhil K. Sengupta
output:
  pdf_document:
    latex_engine: pdflatex
    keep_tex: true
    # template: custom-template.tex
---

```{r setup, include = FALSE}

  # Load packages
  library(tidyverse); library(tidybayes); library(numform)

  # Functions
  r_to_z <- function(r) 0.5 * log( (1 + r) / (1 - r) )
  z_to_r <- function(z) ( exp(2 * z) - 1 ) / ( exp(2 * z) + 1 )

  # knitr options
  knitr::opts_chunk$set(echo = FALSE)

```

# Results

## Search results

## Preregistered analyses

```{r, include = FALSE}

  # Make posterior predictions
  results <- read_rds("../results/results_preregistered_analyses.rds") %>% 
    mutate(
      r_pred_l80 = z_to_r(qnorm(0.10, mu, tau_jj)),
      r_pred_u80 = z_to_r(qnorm(0.90, mu, tau_jj)),
    )

  # Summarise results
  results <- results %>% 
    pivot_longer(
      c(r_mean, tau_ii, tau_jj, r_pred_l80, r_pred_u80),
      names_to = "parameter",
      values_to = "estimate",
      values_drop_na = TRUE
    ) %>% 
    group_by(x_var, y_var, parameter) %>% 
    summarize(
      I = f_comma(unique(I)),
      J = f_comma(unique(J)),
      N = f_comma(unique(N)),
      median = median(estimate),
      .lower = quantile(estimate, 0.025),
      .upper = quantile(estimate, 0.975),
      p_below = mean(estimate < 0),
      p_above = mean(estimate > 0)
    ) %>% 
    ungroup() %>% 
    mutate(
      across(
        c(median, .lower, .upper), 
        ~f_num(., digits = 2)
      ),
      across(
        c(p_below, p_above), 
        ~case_when(
          . < .001 ~ "$<0.1\\%$",
          . > .999 ~ "$>99.9\\%$",
          TRUE ~ paste0("$", f_num(. * 100, digits = 1), "\\%$")
        )
      ),
      text = case_when(
        parameter == "r_mean" ~ paste0("$r = ", median, ", [", .lower, ", ", .upper, "]$"),
        parameter == "tau_ii" ~ paste0("$\\tau_I = ", median, ", [", .lower, ", ", .upper, "]$"),
        parameter == "tau_jj" ~ paste0("$\\tau_J = ", median, ", [", .lower, ", ", .upper, "]$"),
        TRUE ~ paste0("$", median, ", [", .lower, ", ", .upper, "]$")
      )
    ) %>% 
    select(-median, -.lower, -.upper)

```

```{r, include = FALSE}

  # Summarize predictions for statistical power
  n_req <- read_rds("../results/n_req.rds") %>%
    group_by(y_var) %>%
    summarize(
      across(
        c(n, r),
        list(
          "med" = ~median(.),
          "l95" = ~quantile(., 0.025),
          "u95" = ~quantile(., 0.975)
        )
      )
    ) %>%
    mutate(
      across(starts_with("n"), ~f_comma(ceiling(.))),
      across(starts_with("r"), ~f_num(., digits = 3)),
      n_text = paste0(n_med, ", [", n_l95, ", ", n_u95, "]"),
      r_text = paste0("$|r| > ", r_med, ", [", r_l95, ", ", r_u95, "]$")
    )

```

As preregistered, we ran three random-effects meta-analysis models, one for each outcome variable. Figure 3 shows posterior distributions from these analyses.

```{r, fig_width = "100%", fig.align = "center", fig.cap = "Results of preregistered analyses. (\\textbf{A}) Posterior distributions for the estimated mean correlation coefficient, highlighting the proportion of posterior samples for which $r_\\text{mean} < 0$. (\\textbf{B}) Posterior predictive distributions  for the estimated study-wise correlation coefficients."}
knitr::include_graphics("../figures/figure-3.pdf") 
```

```{r, include = FALSE}
pi_results <- results %>% filter(x_var == "ic", y_var == "pi")
```

*Perceived injustice.* Across `r unique(pi_results$N)` participants from `r unique(pi_results$I)` samples in `r unique(pi_results$J)` studies, we found strong evidence for a weak association (`r pi_results$text[pi_results$parameter == "r_mean"]`) between intergroup contact and perceived injustice, with `r pi_results$p_below[pi_results$parameter == "r_mean"]` of posterior samples for the mean correlation coefficient falling below zero. We found evidence that correlation coefficients varied across studies (`r pi_results$text[pi_results$parameter == "tau_jj"]`) and across samples within studies  (`r pi_results$text[pi_results$parameter == "tau_ii"]`). Based on these analyses, we predicted that 80\% of studies would result in correlation coefficients between `r pi_results$text[pi_results$parameter == "r_pred_l80"]` and `r pi_results$text[pi_results$parameter == "r_pred_u80"]` and that researchers would need sample sizes of at least `r n_req$n_text[n_req$y_var == "pi"]` participants to find significant associations ($\alpha = .05$, two-sided) in 80\% of their studies.^[Sample sizes are based on posterior predictions from the three models, which implied that, for 80\% of studies, the absolute correlation coefficient would be `r n_req$r_text[n_req$y_var == "pi"]` for perceived injustice, `r n_req$r_text[n_req$y_var == "ca"]` for collective action, and `r n_req$r_text[n_req$y_var == "ps"]` for policy support.]

```{r, include = FALSE}
ca_results <- results %>% filter(x_var == "ic", y_var == "ca")
```

*Collective action.* Across `r unique(ca_results$N)` participants from `r unique(ca_results$I)` samples in `r unique(ca_results$J)` studies, we found some evidence for a weak association (`r ca_results$text[ca_results$parameter == "r_mean"]`) between intergroup contact and collective action, with `r ca_results$p_below[ca_results$parameter == "r_mean"]` of posterior samples for the mean correlation coefficient falling below zero. We found evidence that correlation coefficients varied across studies (`r ca_results$text[ca_results$parameter == "tau_jj"]`) and across samples within studies  (`r ca_results$text[ca_results$parameter == "tau_ii"]`). Based on these analyses, we predicted that 80\% of studies would result in correlation coefficients between `r ca_results$text[pi_results$parameter == "r_pred_l80"]` and `r ca_results$text[pi_results$parameter == "r_pred_u80"]` and that researchers would need sample sizes of at least `r n_req$n_text[n_req$y_var == "ca"]` participants to find significant associations ($\alpha = .05$, two-sided) in 80\% of their studies.

```{r, include = FALSE}
ps_results <- results %>% filter(x_var == "ic", y_var == "ps")
```

*Policy support.* Across `r unique(ps_results$N)` participants from `r unique(ps_results$I)` samples in `r unique(ps_results$J)` studies, we found some evidence for a weak association (`r ps_results$text[ps_results$parameter == "r_mean"]`) between intergroup contact and policy support, with `r ps_results$p_below[ps_results$parameter == "r_mean"]` of posterior samples for the mean correlation coefficient falling below zero. We found evidence that correlation coefficients varied across studies (`r ps_results$text[ps_results$parameter == "tau_jj"]`) and, to a lesser extent, across samples within studies  (`r ps_results$text[ps_results$parameter == "tau_ii"]`). Based on these analyses, we predicted that 80\% of studies would result in correlation coefficients between `r ps_results$text[pi_results$parameter == "r_pred_l80"]` and `r ps_results$text[pi_results$parameter == "r_pred_u80"]` and that researchers would need sample sizes of at least `r n_req$n_text[n_req$y_var == "ps"]` participants to find significant associations ($\alpha = .05$, two-sided) in 80\% of their studies.

```{r, include = FALSE}
pi_ca_results <- results %>% filter(x_var == "pi", y_var == "ca", parameter == "r_mean")
pi_ps_results <- results %>% filter(x_var == "pi", y_var == "ps", parameter == "r_mean")
ca_ps_results <- results %>% filter(x_var == "ca", y_var == "ps", parameter == "r_mean")
```

As preregistered, we ran another three random-effects meta-analysis models to estimate the relationships between the three outcome variables. As we were not interested in the direction of these relationships, we used cross-sectional correlation coefficients as effect sizes for longitudinal studies. Across `r pi_ca_results$N` participants from `r pi_ca_results$I` samples in `r pi_ca_results$J` studies, we found evidence for a moderate association (`r pi_ca_results$text`) between perceived injustice and collective action. Across `r pi_ps_results$N` participants from `r pi_ps_results$I` samples in `r pi_ps_results$J` studies, we found evidence for a moderate association (`r pi_ps_results$text`) between perceived injustice and policy support. Across `r ca_ps_results$N` participants from `r ca_ps_results$I` samples in `r ca_ps_results$J` studies, we found evidence for a moderate association (`r ca_ps_results$text`) between collective action and policy support.

### Robustness checks

```{r, include = FALSE}

  # Summarize prior choice results
  d_priors <- read_rds("../results/results_robustness_checks_priors.rds") %>% 
    group_by(y_var, prior) %>% 
    median_qi(d_r_mean) %>% 
    mutate(
      across(c(d_r_mean, .lower, .upper), ~f_num(., digits = 2)),
      text = paste0("$\\Delta r = ", d_r_mean, ", [", .lower, ", ", .upper, "]$")
    )

```

```{r, include = FALSE}

  # Calculate Mean Absolute Deviation (MAD)
  mad_loo <- read_rds("../results/results_robustness_checks_loo.rds") %>% 
    group_by(.draw, y_var) %>% 
    summarize(mad_loo = mean(ae_loo)) %>% 
    group_by(y_var) %>% 
    median_qi(mad_loo) %>% 
    mutate(
      across(c(mad_loo, .lower, .upper), ~f_num(., digits = 2)),
      text = paste0("$\\textit{MAD} = ", mad_loo, ", [", .lower, ", ", .upper, "]$")
    )

  # Leave out most influential studies
  d_loo <- read_rds("../results/results_robustness_checks_loo.rds") %>% 
    group_by(y_var, id) %>%
    median_qi(e_loo) %>% 
    top_n(n = 1, wt = abs(e_loo)) %>% 
    mutate(
      across(c(e_loo, .lower, .upper), ~f_num(., digits = 2)),
      text = paste0("$\\Delta r = ", e_loo, ", [", .lower, ", ", .upper, "]$")
    )

```

First, we assessed to what extent our findings were sensitive to choosing narrower, $\mu \sim \text{Normal}(0, 0.1)$, or wider, $\mu \sim \text{Normal}(0, 1)$, prior distributions. Choosing narrower or wider prior distribution did not affect mean effect size estimates for perceived injustice (`r d_priors$text[d_priors$y_var == "pi" & d_priors$prior == "N(0, 0.1)"]` and `r d_priors$text[d_priors$y_var == "pi" & d_priors$prior == "N(0, 1.0)"]`), collective action (`r d_priors$text[d_priors$y_var == "ca" & d_priors$prior == "N(0, 0.1)"]` and `r d_priors$text[d_priors$y_var == "ca" & d_priors$prior == "N(0, 1.0)"]`), and policy support (`r d_priors$text[d_priors$y_var == "ps" & d_priors$prior == "N(0, 0.1)"]` and `r d_priors$text[d_priors$y_var == "ps" & d_priors$prior == "N(0, 1.0)"]`). Second, we assessed to what extent our findings were sensitive to including or excluding influential studies by repeating the preregistered analyses $J$ times while leaving out one of $J$ studies each time and by calculating the mean absolute difference (*MAD*) for the estimated mean effect size across left-out studies. For perceived injustice (`r mad_loo$text[mad_loo$y_var == "pi"]`), collective action (`r mad_loo$text[mad_loo$y_var == "ca"]`), and policy support (`r mad_loo$text[mad_loo$y_var == "ps"]`), the *MAD* was small. Leaving out the most influential study, for example, did not change estimates of the mean effect size for the three outcomes (`r d_loo$text[d_loo$y_var == "pi"]`; `r d_loo$text[d_loo$y_var == "ca"]`; `r d_loo$text[d_loo$y_var == "ps"]`). Together, these analyses showed that our findings were robust to choosing different prior distributions and to excluding influential studies.

### 2020-08-21 manuscript/manuscript.tex
major update

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Meta-analysis of the `ironic' effects of intergroup contact},
  pdfauthor={Nils K. Reimer; Nikhil K. Sengupta},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage[margin=1in]{geometry}
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering

\title{Meta-analysis of the `ironic' effects of intergroup contact}
\author{Nils K. Reimer \and Nikhil K. Sengupta}
\date{}

\begin{document}
\maketitle

\hypertarget{results}{%
\section{Results}\label{results}}

\hypertarget{search-results}{%
\subsection{Search results}\label{search-results}}

\hypertarget{preregistered-analyses}{%
\subsection{Preregistered analyses}\label{preregistered-analyses}}

As preregistered, we ran three random-effects meta-analysis models, one
for each outcome variable. Figure 3 shows posterior distributions from
these analyses.

\begin{figure}

{\centering \includegraphics{../figures/figure-3}

}

\caption{Results of preregistered analyses. (\textbf{A}) Posterior distributions for the estimated mean correlation coefficient, highlighting the proportion of posterior samples for which $r_\text{mean} < 0$. (\textbf{B}) Posterior predictive distributions  for the estimated study-wise correlation coefficients.}\label{fig:unnamed-chunk-3}
\end{figure}

\emph{Perceived injustice.} Across 200,229 participants from 117 samples
in 81 studies, we found strong evidence for a weak association
(\(r = -.07, [-.11, -.04]\)) between intergroup contact and perceived
injustice, with \(>99.9\%\) of posterior samples for the mean
correlation coefficient falling below zero. We found evidence that
correlation coefficients varied across studies
(\(\tau_J = .14, [.12, .17]\)) and across samples within studies
(\(\tau_I = .09, [.06, .13]\)). Based on these analyses, we predicted
that 80\% of studies would result in correlation coefficients between
\(-.25, [-.30, -.21]\) and \(.11, [.06, .16]\) and that researchers
would need sample sizes of at least 2,226, {[}1,521, 3,248{]}
participants to find significant associations (\(\alpha = .05\),
two-sided) in 80\% of their studies.\footnote{Sample sizes are based on
  posterior predictions from the three models, which implied that, for
  80\% of studies, the absolute correlation coefficient would be
  \(|r| > .042, [.034, .050]\) for perceived injustice,
  \(|r| > .046, [.033, .067]\) for collective action, and
  \(|r| > .036, [.022, .064]\) for policy support.}

\emph{Collective action.} Across 118,584 participants from 36 samples in
23 studies, we found some evidence for a weak association
(\(r = -.06, [-.14, .01]\)) between intergroup contact and collective
action, with \(95.0\%\) of posterior samples for the mean correlation
coefficient falling below zero. We found evidence that correlation
coefficients varied across studies (\(\tau_J = .17, [.12, .24]\)) and
across samples within studies (\(\tau_I = .09, [.06, .15]\)). Based on
these analyses, we predicted that 80\% of studies would result in
correlation coefficients between \(-.27, [-.38, -.18]\) and
\(.15, [.06, .27]\) and that researchers would need sample sizes of at
least 1,801, {[}848, 3,458{]} participants to find significant
associations (\(\alpha = .05\), two-sided) in 80\% of their studies.

\emph{Policy support.} Across 13,703 participants from 19 samples in 14
studies, we found some evidence for a weak association
(\(r = -.07, [-.14, -.00]\)) between intergroup contact and policy
support, with \(98.1\%\) of posterior samples for the mean correlation
coefficient falling below zero. We found evidence that correlation
coefficients varied across studies (\(\tau_J = .10, [.06, .18]\)) and,
to a lesser extent, across samples within studies
(\(\tau_I = .03, [.00, .12]\)). Based on these analyses, we predicted
that 80\% of studies would result in correlation coefficients between
\(-.20, [-.32, -.13]\) and \(.06, [-.02, .18]\) and that researchers
would need sample sizes of at least 2,992, {[}949, 8,077{]} participants
to find significant associations (\(\alpha = .05\), two-sided) in 80\%
of their studies.

As preregistered, we ran another three random-effects meta-analysis
models to estimate the relationships between the three outcome
variables. As we were not interested in the direction of these
relationships, we used cross-sectional correlation coefficients as
effect sizes for longitudinal studies. Across 111,252 participants from
24 samples in 13 studies, we found evidence for a moderate association
(\(r = .29, [.21, .37]\)) between perceived injustice and collective
action. Across 6,244 participants from 12 samples in 9 studies, we found
evidence for a moderate association (\(r = .23, [.08, .35]\)) between
perceived injustice and policy support. Across 8,558 participants from 6
samples in 3 studies, we found evidence for a moderate association
(\(r = .30, [.13, .42]\)) between collective action and policy support.

\hypertarget{robustness-checks}{%
\subsubsection{Robustness checks}\label{robustness-checks}}

First, we assessed to what extent our findings were sensitive to
choosing narrower, \(\mu \sim \text{Normal}(0, 0.1)\), or wider,
\(\mu \sim \text{Normal}(0, 1)\), prior distributions. Choosing narrower
or wider prior distribution did not affect mean effect size estimates
for perceived injustice (\(\Delta r = -.00, [-.05, .05]\) and
\(\Delta r = -.00, [-.05, .05]\)), collective action
(\(\Delta r = -.01, [-.11, .09]\) and \(\Delta r = -.00, [-.10, .11]\)),
and policy support (\(\Delta r = -.01, [-.10, .08]\) and
\(\Delta r = .00, [-.09, .10]\)). Second, we assessed to what extent our
findings were sensitive to including or excluding influential studies by
repeating the preregistered analyses \(J\) times while leaving out one
of \(J\) studies each time and by calculating the mean absolute
difference (\emph{MAD}) for the estimated mean effect size across
left-out studies. For perceived injustice
(\(\textit{MAD} = .02, [.01, .04]\)), collective action
(\(\textit{MAD} = .04, [.02, .09]\)), and policy support
(\(\textit{MAD} = .03, [.02, .08]\)), the \emph{MAD} was small. Leaving
out the most influential study, for example, did not change estimates of
the mean effect size for the three outcomes
(\(\Delta r = -.01, [-.05, .04]\); \(\Delta r = .02, [-.09, .12]\);
\(\Delta r = -.02, [-.11, .07]\)). Together, these analyses showed that
our findings were robust to choosing different prior distributions and
to excluding influential studies.

\end{document}

### 2020-08-21 manuscript/summary.Rmd
major update

---
title: "Meta-analysis of the `ironic' effects of intergroup contact"
author: 
  - Nils Karl Reimer, University of Oxford
  - Nikhil Kumar Sengupta, University of Kent
date: "12/08/2020"
output:
  pdf_document:
    keep_tex: true
---

```{r setup, include = FALSE}

  knitr::opts_chunk$set(echo = FALSE)

  # Load packages
  library(tidyverse); library(numform)

```

# Results

## Preregistered analyses

```{r, include = FALSE}

  # Summarise results
  results <- read_rds("../results/results_preregistered_analyses.rds") %>% 
    pivot_longer(
      c(r_mean, tau_ii, tau_jj),
      names_to = "parameter",
      values_to = "estimate",
      values_drop_na = TRUE
    ) %>% 
    group_by(x_var, y_var, parameter) %>% 
    summarize(
      I = f_comma(unique(I)),
      J = f_comma(unique(J)),
      N = f_comma(unique(N)),
      median = median(estimate),
      .lower = quantile(estimate, 0.025),
      .upper = quantile(estimate, 0.975),
      p_below = mean(estimate < 0),
      p_above = mean(estimate > 0)
    ) %>% 
    ungroup() %>% 
    mutate(
      across(
        c(median, .lower, .upper), 
        ~f_num(., digits = 2)
      ),
      across(
        c(p_below, p_above), 
        ~case_when(
          . < .001 ~ "$<0.1\\%$",
          . > .999 ~ "$>99.9\\%$",
          TRUE ~ paste0("$", f_num(. * 100, digits = 1), "\\%$")
        )
      ),
      text = case_when(
        parameter == "r_mean" ~ paste0("$r = ", median, ", [", .lower, ",", .upper, "]$"),
        parameter == "tau_ii" ~ paste0("$\\tau_I = ", median, ", [", .lower, ",", .upper, "]$"),
        parameter == "tau_jj" ~ paste0("$\\tau_J = ", median, ", [", .lower, ",", .upper, "]$")
      )
    ) %>% 
    select(-median, -.lower, -.upper)

```

```{r, include = FALSE}
pi_results <- results %>% filter(x_var == "ic", y_var == "pi")
ca_results <- results %>% filter(x_var == "ic", y_var == "ca")
ps_results <- results %>% filter(x_var == "ic", y_var == "ps")
````

As preregistered, we ran three random-effects meta-analysis models, one for the relationship between intergroup contact and each outcome variable. Across `r unique(pi_results$N)` participants from `r unique(pi_results$I)` samples in `r unique(pi_results$J)` studies, we found strong evidence for a weak association (`r pi_results$text[pi_results$parameter == "r_mean"]`) between intergroup contact and perceived injustice, with `r pi_results$p_below[pi_results$parameter == "r_mean"]` of posterior samples for the mean correlation coefficient falling below zero. We found evidence that correlation coefficients varied across studies (`r pi_results$text[pi_results$parameter == "tau_jj"]`) and across samples within studies  (`r pi_results$text[pi_results$parameter == "tau_ii"]`). Across `r unique(ca_results$N)` participants from `r unique(ca_results$I)` samples in `r unique(ca_results$J)` studies, we found some evidence for a weak association (`r ca_results$text[ca_results$parameter == "r_mean"]`) between intergroup contact and collective action, with `r ca_results$p_below[ca_results$parameter == "r_mean"]` of posterior samples for the mean correlation coefficient falling below zero. We found evidence that correlation coefficients varied across studies (`r ca_results$text[ca_results$parameter == "tau_jj"]`) and across samples within studies  (`r ca_results$text[ca_results$parameter == "tau_ii"]`). Across `r unique(ps_results$N)` participants from `r unique(ps_results$I)` samples in `r unique(ps_results$J)` studies, we found some evidence for a weak association (`r ps_results$text[ps_results$parameter == "r_mean"]`) between intergroup contact and policy support, with `r ps_results$p_below[ps_results$parameter == "r_mean"]` of posterior samples for the mean correlation coefficient falling below zero. We found evidence that correlation coefficients varied across studies (`r ps_results$text[ps_results$parameter == "tau_jj"]`) and, to a lesser extent, across samples within studies  (`r ps_results$text[ps_results$parameter == "tau_ii"]`).

```{r, include = FALSE}
pi_ca_results <- results %>% filter(x_var == "pi", y_var == "ca", parameter == "r_mean")
pi_ps_results <- results %>% filter(x_var == "pi", y_var == "ps", parameter == "r_mean")
ca_ps_results <- results %>% filter(x_var == "ca", y_var == "ps", parameter == "r_mean")
````

As preregistered, we ran another three random-effects meta-analysis models to estimate the relationships between the three outcome variables. As we were not interested in the direction of these relationships, we used cross-sectional correlation coefficients as effect sizes for longitudinal studies. Across `r pi_ca_results$N` participants from `r pi_ca_results$I` samples in `r pi_ca_results$J` studies, we found evidence for a moderate association (`r pi_ca_results$text`) between perceived injustice and collective action. Across `r pi_ps_results$N` participants from `r pi_ps_results$I` samples in `r pi_ps_results$J` studies, we found evidence for a moderate association (`r pi_ps_results$text`) between perceived injustice and policy support. Across `r ca_ps_results$N` participants from `r ca_ps_results$I` samples in `r ca_ps_results$J` studies, we found evidence for a moderate association (`r ca_ps_results$text`) between collective action and policy support.

### 2020-08-21 manuscript/summary.tex
major update

--- 2020-08-21 manuscript/manuscript.tex
@@
   pdftitle={Meta-analysis of the `ironic' effects of intergroup contact},
-  pdfauthor={Nils K. Reimer; Nikhil K. Sengupta},
+  pdfauthor={Nils Karl Reimer, University of Oxford; Nikhil Kumar Sengupta, University of Kent},
   hidelinks,
@@
 \title{Meta-analysis of the `ironic' effects of intergroup contact}
-\author{Nils K. Reimer \and Nikhil K. Sengupta}
-\date{}
+\author{Nils Karl Reimer, University of Oxford \and Nikhil Kumar Sengupta, University of Kent}
+\date{12/08/2020}
 
@@
 
-\hypertarget{search-results}{%
-\subsection{Search results}\label{search-results}}
-
 \hypertarget{preregistered-analyses}{%
@@
 As preregistered, we ran three random-effects meta-analysis models, one
-for each outcome variable. Figure 3 shows posterior distributions from
-these analyses.
-
-\begin{figure}
-
-{\centering \includegraphics{../figures/figure-3}
-
-}
-
-\caption{Results of preregistered analyses.
-(\textbf{A}) Posterior distributions for the estimated mean correlation coefficient, highlighting the proportion of posterior samples for which $r_\text{mean} < 0$.
-(\textbf{B}) Posterior predictive distributions  for the estimated study-wise correlation coefficients.}\label{fig:unnamed-chunk-3}
-\end{figure}
-
-\emph{Perceived injustice.} Across 200,229 participants from 117 samples
-in 81 studies, we found strong evidence for a weak association
-(\(r = -.07, [-.11, -.04]\)) between intergroup contact and perceived
-injustice, with \(>99.9\%\) of posterior samples for the mean
-correlation coefficient falling below zero. We found evidence that
-correlation coefficients varied across studies
-(\(\tau_J = .14, [.12, .17]\)) and across samples within studies
-(\(\tau_I = .09, [.06, .13]\)). Based on these analyses, we predicted
-that 80\% of studies would result in correlation coefficients between
-\(-.25, [-.30, -.21]\) and \(.11, [.06, .16]\) and that researchers
-would need sample sizes of at least 2,226, {[}1,521, 3,248{]}
-participants to find significant associations (\(\alpha = .05\),
-two-sided) in 80\% of their studies.\footnote{Sample sizes are based on
-  posterior predictions from the three models, which implied that, for
-  80\% of studies, the absolute correlation coefficient would be
-  \(|r| > .042, [.034, .050]\) for perceived injustice,
-  \(|r| > .046, [.033, .067]\) for collective action, and
-  \(|r| > .036, [.022, .064]\) for policy support.}
-
-\emph{Collective action.} Across 118,584 participants from 36 samples in
-23 studies, we found some evidence for a weak association
-(\(r = -.06, [-.14, .01]\)) between intergroup contact and collective
+for the relationship between intergroup contact and each outcome
+variable. Across 200,229 participants from 117 samples in 81 studies, we
+found strong evidence for a weak association (\(r = -.07, [-.11,-.04]\))
+between intergroup contact and perceived injustice, with \(>99.9\%\) of
+posterior samples for the mean correlation coefficient falling below
+zero. We found evidence that correlation coefficients varied across
+studies (\(\tau_J = .14, [.12,.17]\)) and across samples within studies
+(\(\tau_I = .09, [.06,.13]\)). Across 118,584 participants from 36
+samples in 23 studies, we found some evidence for a weak association
+(\(r = -.06, [-.14,.01]\)) between intergroup contact and collective
 action, with \(95.0\%\) of posterior samples for the mean correlation
 coefficient falling below zero. We found evidence that correlation
-coefficients varied across studies (\(\tau_J = .17, [.12, .24]\)) and
-across samples within studies (\(\tau_I = .09, [.06, .15]\)). Based on
-these analyses, we predicted that 80\% of studies would result in
-correlation coefficients between \(-.27, [-.38, -.18]\) and
-\(.15, [.06, .27]\) and that researchers would need sample sizes of at
-least 1,801, {[}848, 3,458{]} participants to find significant
-associations (\(\alpha = .05\), two-sided) in 80\% of their studies.
-
-\emph{Policy support.} Across 13,703 participants from 19 samples in 14
-studies, we found some evidence for a weak association
-(\(r = -.07, [-.14, -.00]\)) between intergroup contact and policy
-support, with \(98.1\%\) of posterior samples for the mean correlation
-coefficient falling below zero. We found evidence that correlation
-coefficients varied across studies (\(\tau_J = .10, [.06, .18]\)) and,
-to a lesser extent, across samples within studies
-(\(\tau_I = .03, [.00, .12]\)). Based on these analyses, we predicted
-that 80\% of studies would result in correlation coefficients between
-\(-.20, [-.32, -.13]\) and \(.06, [-.02, .18]\) and that researchers
-would need sample sizes of at least 2,992, {[}949, 8,077{]} participants
-to find significant associations (\(\alpha = .05\), two-sided) in 80\%
-of their studies.
+coefficients varied across studies (\(\tau_J = .17, [.12,.24]\)) and
+across samples within studies (\(\tau_I = .09, [.06,.15]\)). Across
+13,703 participants from 19 samples in 14 studies, we found some
+evidence for a weak association (\(r = -.07, [-.14,-.00]\)) between
+intergroup contact and policy support, with \(98.1\%\) of posterior
+samples for the mean correlation coefficient falling below zero. We
+found evidence that correlation coefficients varied across studies
+(\(\tau_J = .10, [.06,.18]\)) and, to a lesser extent, across samples
+within studies (\(\tau_I = .03, [.00,.12]\)).
 
@@
 24 samples in 13 studies, we found evidence for a moderate association
-(\(r = .29, [.21, .37]\)) between perceived injustice and collective
+(\(r = .29, [.21,.37]\)) between perceived injustice and collective
 action. Across 6,244 participants from 12 samples in 9 studies, we found
-evidence for a moderate association (\(r = .23, [.08, .35]\)) between
+evidence for a moderate association (\(r = .23, [.08,.35]\)) between
 perceived injustice and policy support. Across 8,558 participants from 6
 samples in 3 studies, we found evidence for a moderate association
-(\(r = .30, [.13, .42]\)) between collective action and policy support.
-
-\hypertarget{robustness-checks}{%
-\subsubsection{Robustness checks}\label{robustness-checks}}
-
-First, we assessed to what extent our findings were sensitive to
-choosing narrower, \(\mu \sim \text{Normal}(0, 0.1)\), or wider,
-\(\mu \sim \text{Normal}(0, 1)\), prior distributions. Choosing narrower
-or wider prior distribution did not affect mean effect size estimates
-for perceived injustice (\(\Delta r = -.00, [-.05, .05]\) and
-\(\Delta r = -.00, [-.05, .05]\)), collective action
-(\(\Delta r = -.01, [-.11, .09]\) and \(\Delta r = -.00, [-.10, .11]\)),
-and policy support (\(\Delta r = -.01, [-.10, .08]\) and
-\(\Delta r = .00, [-.09, .10]\)). Second, we assessed to what extent our
-findings were sensitive to including or excluding influential studies by
-repeating the preregistered analyses \(J\) times while leaving out one
-of \(J\) studies each time and by calculating the mean absolute
-difference (\emph{MAD}) for the estimated mean effect size across
-left-out studies. For perceived injustice
-(\(\textit{MAD} = .02, [.01, .04]\)), collective action
-(\(\textit{MAD} = .04, [.02, .09]\)), and policy support
-(\(\textit{MAD} = .03, [.02, .08]\)), the \emph{MAD} was small. Leaving
-out the most influential study, for example, did not change estimates of
-the mean effect size for the three outcomes
-(\(\Delta r = -.01, [-.05, .04]\); \(\Delta r = .02, [-.09, .12]\);
-\(\Delta r = -.02, [-.11, .07]\)). Together, these analyses showed that
-our findings were robust to choosing different prior distributions and
-to excluding influential studies.
+(\(r = .30, [.13,.42]\)) between collective action and policy support.
 

### 2020-08-21 figures/figure-3.R

@@ -1,0 +1,228 @@
+rm(list = ls())
+
+# Notes -------------------------------------------------------------------
+
+
+# Library -----------------------------------------------------------------
+
+  # Load packages
+  library(tidyverse); library(ggtext); library(patchwork); library(numform)
+
+  # Link functions
+  r_to_z <- function(r) 0.5 * log( (1 + r) / (1 - r) )
+  z_to_r <- function(z) ( exp(2 * z) - 1 ) / ( exp(2 * z) + 1 )
+  
+
+# Prepare -----------------------------------------------------------------
+  
+  # Import results from preregistered analyses
+  results <- read_rds("results/results_preregistered_analyses.rds")
+
+  # Name predictor and outcome variables
+  results <- results %>% 
+    mutate(
+      x_name = recode_factor(
+        x_var,
+        "ic" = "Intergroup contact",
+        "pi" = "Perceived injustice",
+        "ca" = "Collective action",
+        "ps" = "Policy support"
+      ),
+      y_name = recode_factor(
+        y_var,
+        "pi" = "Perceived injustice",
+        "ca" = "Collective action",
+        "ps" = "Policy support"
+      )
+    )
+  
+
+# Figure 3a ---------------------------------------------------------------
+
+  # Prepare
+  d_3a <- results %>% 
+    filter(x_var == "ic") %>% 
+    mutate(
+      text = paste0("*I* = ", I, ", *J* = ", J, ", *N* = ", f_comma(N))
+    )
+  
+  # Visualize
+  f_3a <- ggplot(d_3a, aes(x = r_mean)) +
+    geom_density(
+      aes(fill = y_name),
+      colour = NA,
+      adjust = 2,
+      n = 1e4,
+      alpha = 1.0
+    ) +
+    annotate(
+      geom = "polygon",
+      x = c(0, Inf, Inf,   0),
+      y = c(0,   0, Inf, Inf),
+      fill = "white",
+      alpha = 0.6
+    ) +
+    geom_richtext(
+      data = d_3a %>% 
+        group_by(y_name) %>% 
+        summarise(p = mean(r_mean < 0), r_mean = mean(r_mean)) %>% 
+        mutate(p = if_else(p > 0.99, "\\>99%", paste0(round(p, 2)*100, "%"))),
+      aes(label = p),
+      y = 0,
+      vjust = 0,
+      size = 10*0.8/.pt,
[…]

### 2020-08-21 records/results/extract_other_effect_sizes.R

@@ -35,6 +35,15 @@ es <- tribble(
   1411L,      1L,     "r", -0.0682, "gd", "cq", "author",    NA,
   1411L,      1L,     "r", -0.1392, "gd", "pc", "author",    NA,
   1411L,      1L,     "r",  1.0000, "gd", "gd", "author",    NA,
+  1412L,      1L,     "r",  1.0000, "cq", "cq", "author",    NA,
+  1412L,      1L,     "r", -0.0318, "cq", "pd", "author",    NA,
+  1412L,      1L,     "r", -0.2817, "cq", "oa", "author",    NA,
+  1412L,      1L,     "r", -0.0318, "pd", "cq", "author",    NA,
+  1412L,      1L,     "r",  1.0000, "pd", "pd", "author",    NA,
+  1412L,      1L,     "r",  0.0419, "pd", "oa", "author",    NA,
+  1412L,      1L,     "r", -0.2817, "oa", "cq", "author",    NA,
+  1412L,      1L,     "r",  0.0419, "oa", "pd", "author",    NA,
+  1412L,      1L,     "r",  1.0000, "oa", "oa", "author",    NA,
   1525L,      1L,     "r",  -0.162, "cf", "pd",   "data",    NA,
   1525L,      1L,     "r",  -0.075, "cf", "gi",   "data", "ethnic identity - centrality",
   1525L,      1L,     "r",   0.018, "cf", "gi",   "data", "ethnic identity - regard",
@@ -64,8 +73,10 @@ es <- tribble(
 # Extract effect sizes (d) for group differences
 es <- tribble(
     ~id, ~sample, ~metric,     ~es,   ~x,   ~y,  ~source, ~note, ~n1, ~n2, ~m1, ~s1, ~m2, ~s2,
-   244L,      1L,     "d",      NA, "ic", "pi",   "text",    NA, 59L, 70L, 7.48, 1.07, 7.01, 1.11, # This is a cross-sectional study, but the predictor was dichotomized.
-   244L,      1L,     "d",      NA, "ic", "pi",   "text",    NA, 59L, 70L,   NA, NA, NA, NA, # This is a cross-sectional study, but the predictor was dichotomized.
+   244L,      1L,     "d",      NA, "ic", "pi",   "text", "wrongfulness of race-based exclusion",          59L, 70L, 7.48, 1.07, 7.01, 1.11, # This is a cross-sectional study, but the predictor was dichotomized.
[…]

### 2020-08-21 run_scripts.R

@@ -1,0 +1,40 @@
+rm(list = ls())
+
+# Notes -------------------------------------------------------------------
+  
+  #########################################################################
+  # This script runs all R scripts in the order in which they need to be  #
+  # run to reproduce the analyses reported in the manuscript.             #
+  #########################################################################
+
+# Prepare -----------------------------------------------------------------
+
+  # Screen records for eligibility
+  source("scripts/screen_records.R")
+
+  # Code records for eligibility
+  source("scripts/code_records.R")
+
+  # Extract information about studies and measures
+  source("scripts/extract_study_information.R")
+
+  # Extract effect sizes
+  source("scripts/extract_effect_sizes.R")
+
+  # Code moderators
+  source("scripts/code_moderators.R")
+
+  # Code moderators related to predictor/outcome measures
+  source("scripts/code_measures.R")
+
+  # Combine and prepare data for analyses
+  source("scripts/prepare_data_for_analyses.R")
+
+
+# Estimate ----------------------------------------------------------------
+
+  # Run preregistered analyses
+  source("scripts/run_preregistered_analyses.R")
+
+  # Run preregistered robustness checks
+  source("scripts/run_preregistered_robustness_checks.R")

### 2020-08-21 scripts/code_measures.R

@@ -1,0 +1,99 @@
+rm(list = ls())
+
+# Notes -------------------------------------------------------------------
+
+
+# Library -----------------------------------------------------------------
+
+  # Load packages
+  library(tidyverse); library(irr)
+
+
+# Import ------------------------------------------------------------------
+  
+  # Import results from survey
+  dr <- read_csv(
+    "records/results/coding-measures.csv",
+    col_types = "ciiccccccc"
+  )
+
+  # Import .rds files (data)
+  mi <- read_rds("data/mi.rds")
+  
+
+# Exclude -----------------------------------------------------------------
+
+  # Remove excluded/failed studies
+  dr <- dr %>% semi_join(mi, by = c("id", "sample"))
+  
+
+# Code measures -----------------------------------------------------------
+
+  # Transform to long format
+  dl <- dr %>% 
+    pivot_longer(
+      c(ic_direct, pi_specific, pi_personal),
+      names_to = "item",
+      values_to = "response"
+    ) %>% 
+    pivot_wider(
+      names_from = coder, 
+      values_from = response
+    ) %>%
+    filter(!is.na(`Coder 1`) | !is.na(`Coder 2`)) %>% 
+    arrange(var, id, sample, variable, name, text, item)
+    
+  # Caclulate interrater agreement for predictor variable (directly/indirectly)
+  dl %>% 
+    filter(var == "ic", item == "ic_direct") %>% 
+    with(., kappa2(ratings = cbind(`Coder 1`, `Coder 2`)))
+  
+  # Caclulate interrater agreement for outcome variable (specific/general/both)
+  dl %>% 
+    filter(var == "pi", item == "pi_specific") %>% 
+    with(., kappa2(ratings = cbind(`Coder 1`, `Coder 2`)))
+  
+  # Caclulate interrater agreement for outcome variable (personal/group/both)
+  dl %>% 
+    filter(var == "pi", item == "pi_personal") %>% 
+    with(., kappa2(ratings = cbind(`Coder 1`, `Coder 2`)))
+  
+  # Form consensus
+  consensus <- c(
+    "Directly", "Indirectly", "Indirectly", "Indirectly", "Indirectly",
+    "Indirectly", "Directly", "Directly", "Directly", "Both", 
+    "Personal", "Specific", "Personal", "Specific",  "Personal",
+    "Specific", "Specific", "Group", "General", "General",
[…]

### 2020-08-21 scripts/code_moderators.R

@@ -1,0 +1,497 @@
+rm(list = ls())
+
+# Notes -------------------------------------------------------------------
+
+
+# Library -----------------------------------------------------------------
+
+  # Load packages
+  library(tidyverse); library(countrycode); library(irr)
+
+
+# Import ------------------------------------------------------------------
+  
+  # Import results from survey (published)
+  moderators <- read_csv(
+    "records/results/coding-moderators.csv", 
+    col_types = "ciiccccccccc"
+  )
+  
+  # Import results from survey (unpublished)
+  unpublished <- read_csv(
+    "records/results/unpublished-studies.csv", 
+    col_types = "icciicc"
+  )
+  
+  # Import results from survey (citing)
+  citing <- read_csv(
+    "records/results/citing-studies.csv", 
+    col_types = "iiicc"
+  )
+  
+  # Import status
+  status <- read_csv(
+    "records/results/recording-status.csv",
+    col_types = "Dicc"
+  )
+  
+  # Import list of countries
+  countries <- map_data("world") %>% 
+    distinct(region) %>% 
+    arrange(region) %>% 
+    pull(region)
+
+  
+# Exclude -----------------------------------------------------------------
+  
+  # Remove excluded/failed studies (literature search)
+  moderators <- semi_join(
+    moderators,
+    status %>% filter(status != "excluded", status != "failed"),
+    by = "id"
+  )
+  
+  # Remove excluded/failed studies (citing studies)
+  citing <- semi_join(
+    citing,
+    status %>% filter(status != "excluded", status != "failed"),
+    by = "id"
+  )
+  
+  # Remove excluded/failed studies (unpublished studies)
+  unpublished <- semi_join(
+    unpublished,
+    status %>% filter(status != "excluded", status != "failed"),
+    by = "id"
+  )
+
+# Code moderators (published) ---------------------------------------------
+  
+  # Rename variables (published)
+  moderators <- moderators %>% 
+    rename(
+      country = q4,
+      ingroup = q5,
+      outgroup = q6,
+      age = q7,
+      study_sample = q8,
+      study_sample_text = q8_4_text,
+      study_design = q9,
+      study_design_text = q9_6_text,
+      study_intention = q10
+    )
+  
+  # Caclulate interrater agreement for country
+  moderators %>%
+    select(id, sample, coder, country) %>% 
[…]

### 2020-08-21 scripts/code_records.R

@@ -19,15 +19,22 @@ rm(list = ls())
   
   # Remove missing/unpublished records
   records <- records %>% filter(!(id %in% c(
-     505,  715,  719, 1057, 1070, 1156, 1180, 1242, 1336, 
-    1344, 1359, 1541, 1675, 1734, 1875, 2013, 2087, 2194
+     505,  715,  719, 1057, 1070, 1156, 1180, 1242, 1336, 1344, 1359, 
+     1541, 1675, 1734, 1875, 2013, 2087, 2194
   )))
-
+  
   # Import results from surveys
   results <- read_csv(
     "records/results/coding-eligibility.csv", 
     col_types = "iciiiiiic"
   )
+  
+  # Remove duplicates and non-existing records (second search)
+  results <- results %>%
+    filter(
+      !(id %in% c(3021, 3039, 3061, 3069, 3075, 3102, 3128, 3178)), # duplicates
+      !(id %in% c(3078, 3210)) # non-existing records
+    )
 
 # Calculate ---------------------------------------------------------------
   
@@ -91,28 +98,32 @@ rm(list = ls())
   
   # Resolve disagreements
   consensus <- tribble(
-     ~id, ~include,
-      45,       1L, 
-     104,       0L, 
-     363,       0L, 
-     422,       0L, 
-     684,       1L, 
-     910,       1L, 
-     920,       0L, 
-    1170,       0L, 
-    1217,       1L, 
-    1221,       1L, 
-    1376,       1L, 
-    1658,       1L, 
-    1750,       1L, 
-    1812,       0L, 
-    1850,       1L, 
-    1891,       1L, 
-    2001,       1L, 
-    2023,       1L, 
-    2291,       0L, 
-    2295,       1L, 
-    2371,       1L 
+      ~id, ~include,
+     104L,       0L, 
+      45L,       1L, 
+     363L,       0L, 
+     422L,       0L, 
+     684L,       1L, 
+     910L,       1L, 
+     920L,       0L, 
+    1170L,       0L, 
+    1217L,       1L, 
+    1221L,       1L, 
+    1376L,       1L, 
+    1658L,       1L, 
+    1750L,       1L, 
+    1812L,       0L, 
+    1850L,       1L, 
+    1891L,       1L, 
+    2001L,       1L, 
+    2023L,       1L, 
+    2291L,       0L, 
+    2295L,       1L, 
+    2371L,       1L,
+    3005L,       1L,
+    3047L,       1L,
+    3060L,       1L,
+    3137L,       0L
   )
 
 

### 2020-08-21 scripts/extract_effect_sizes.R

@@ -1,7 +1,7 @@
 rm(list = ls())
 
 # Notes -------------------------------------------------------------------
-  # Remove duplicates across (un-)published research
+
 
 # Library -----------------------------------------------------------------
 
@@ -32,21 +32,24 @@ rm(list = ls())
     col_types = "icciicc"
   )
   
+  # Import results from survey (citing)
+  citing <- read_csv(
+    "records/results/citing-studies.csv", 
+    col_types = "iiicc"
+  )
+  
   # Import status
   status <- read_csv(
     "records/results/recording-status.csv",
-    col_types = "Diccc"
+    col_types = "Dicc"
   )
+  
+  # Import results from extracting information about studies/measures
+  si <- read_rds("data/si.rds")
+  mi <- read_rds("data/mi.rds")
 
 
 # Exclude -----------------------------------------------------------------
-  
-  # Remove excluded/failed studies
-  results <- semi_join(
-    results,
-    status %>% filter(status != "excluded", status != "failed"),
-    by = "id"
-  )
   
   # Remove excluded/failed records
   records <- semi_join(
@@ -54,11 +57,32 @@ rm(list = ls())
     status %>% filter(status != "excluded", status != "failed"),
     by = "id"
   ) 
-
+  
+  # Remove excluded/failed studies (literature search)
+  results <- semi_join(
+    results,
+    status %>% filter(status != "excluded", status != "failed"),
+    by = "id"
+  )
+  
+  # Remove excluded/failed studies (citing studies)
+  citing <- semi_join(
+    citing,
+    status %>% filter(status != "excluded", status != "failed"),
+    by = "id"
+  )
+  
+  # Remove excluded/failed studies (unpublished studies)
+  unpublished <- semi_join(
+    unpublished,
+    status %>% filter(status != "excluded", status != "failed"),
+    by = "id"
+  )
+  
 
 # Prepare -----------------------------------------------------------------
 
-  # Add unpublished study
+  # Add unpublished studies
   results <- unpublished %>% 
     mutate(
       item = case_when(
@@ -69,64 +93,31 @@ rm(list = ls())
     filter(item %in% (distinct(results, item) %>% pull(item))) %>% 
[…]

### 2020-08-21 scripts/extract_study_information.R

@@ -1,0 +1,228 @@
+rm(list = ls())
+
+# Notes -------------------------------------------------------------------
+
+
+# Library -----------------------------------------------------------------
+
+  # Load packages
+  library(tidyverse)
+  
+  # Load functions
+  source("scripts/functions.R")
+
+
+# Import ------------------------------------------------------------------
+
+  # Import records
+  records <- read_csv(
+    "records/records-cleaned.csv",
+    col_types = "icicccccccccccc"
+  )
+  
+  # Import results from survey
+  results <- read_csv(
+    "records/results/extracting-effect-sizes.csv", 
+    col_types = "iciicc"
+  )
+  
+  # Import results from survey (unpublished)
+  unpublished <- read_csv(
+    "records/results/unpublished-studies.csv", 
+    col_types = "icciicc"
+  )
+  
+  # Import results from survey (citing)
+  citing <- read_csv(
+    "records/results/citing-studies.csv", 
+    col_types = "iiicc"
+  )
+  
+  # Import status
+  status <- read_csv(
+    "records/results/recording-status.csv",
+    col_types = "Dicc"
+  )
+  
+  
+# Exclude -----------------------------------------------------------------
+  
+  # Remove excluded/failed records
+  records <- semi_join(
+    records,
+    status %>% filter(status != "excluded", status != "failed"),
+    by = "id"
+  ) 
+  
+  # Remove excluded/failed studies (literature search)
+  results <- semi_join(
+    results,
+    status %>% filter(status != "excluded", status != "failed"),
+    by = "id"
+  )
+  
+  # Remove excluded/failed studies (citing studies)
+  citing <- semi_join(
+    citing,
+    status %>% filter(status != "excluded", status != "failed"),
+    by = "id"
+  )
+  
+  # Remove excluded/failed studies (unpublished studies)
+  unpublished <- semi_join(
+    unpublished,
+    status %>% filter(status != "excluded", status != "failed"),
+    by = "id"
+  )
+
+
+# Prepare -----------------------------------------------------------------
+
+  # Add unpublished studies
+  results <- unpublished %>% 
+    mutate(
+      item = case_when(
+        item == "ingroup" ~ "name",
+        TRUE ~ item
+      )
+    ) %>% 
[…]

### 2020-08-21 scripts/functions.R

@@ -100,3 +100,12 @@ compute_d <- function(n1, m1, s1, n2, m2, s2) {
 partial_r <- function(r_ab, r_ac, r_bc) {
   (r_ab - r_ac * r_bc) / sqrt((1 - r_ac^2) * (1 - r_bc^2))
 }
+
+# Import bibliography
+read_bib <- function(file) {
+  bib <- readLines(file, encoding = "UTF-8")
+  bib <- str_replace_all(bib, "[^[:graph:]]", " ")
+  bib <- bib2df:::bib2df_gather(bib)
+  bib <- bib2df:::bib2df_tidy(bib, separate_names = FALSE)
+  return(bib)
+}

### 2020-08-21 scripts/prepare_data_for_analyses.R

@@ -1,9 +1,14 @@
 rm(list = ls())
 
 # Notes -------------------------------------------------------------------
-  # In longitudinal studies with more than two waves, I should decide on 
-  # which intervals to include (e.g., t1 -> t3).
+  
+  #########################################################################
+  # 414 (1) and 2257 are likely duplicates—but have different measures.   # 
+  #########################################################################
 
+  #########################################################################
+  # Something is wrong with 2381's entry which contains ps double.        #
+  #########################################################################
 
 # Library -----------------------------------------------------------------
 
@@ -20,6 +25,8 @@ rm(list = ls())
   si <- read_rds("data/si.rds")
   mi <- read_rds("data/mi.rds")
   es <- read_rds("data/es.rds")
+  mo <- read_rds("data/mo.rds")
+  mo_mi <- read_rds("data/mo_mi.rds")
 
 
 # Calculate effect sizes --------------------------------------------------
@@ -43,12 +50,6 @@ rm(list = ls())
       si %>% select(id, sample, n),
       by = c("id", "sample")
     ) %>% 
-    mutate(
-      n = case_when(
-        !is.na(n1) & !is.na(n2) ~ n1 + n2,
-        TRUE ~ n
-      )
-    ) %>% 
     select(id:es, n, r, everything())
 
 
@@ -62,7 +63,7 @@ rm(list = ls())
         mutate(r_bc = r) %>% 
         select(id, sample, y, y_name, t1, t2, r_bc),
       by = c("id", "sample", "y", "y_name", "t1", "t2")
-    ) %>%
+    ) %>% 
     left_join(
       dl %>% 
         filter(metric == "r", x != y, x_name != y_name, t1 == t2) %>% 
@@ -78,15 +79,6 @@ rm(list = ls())
   
   # Exclude cross-lagged effects across two waves (e.g., t1 -> t3)
   dl <- dl %>% filter((is.na(t1) & is.na(t2)) | (t2 - t1) == 1L)
-  
-
-# Select/Arrange variables -------------------------------------------------------
-
-  # Select variables
-  dl <- dl %>% 
-    select(
-      id, sample, n, r, x, y, x_name, y_name, t1, t2, r_ab, r_bc, r_ac
-    )
   
 
 # Rank variables ----------------------------------------------------------
[…]

### 2020-08-21 scripts/run_preregistered_analyses.R

@@ -1,17 +1,11 @@
 rm(list = ls())
 
 # Notes -------------------------------------------------------------------
-  # Consider changing notation from i,j to j,k to accommodate multiple
-  # effect sizes per sample.
 
-  # 1494 should prioritise "major discrimination"
-
-  # Add seeds for preregistered analyses
-
-  # I should make 2381 and 1695 samples of the same study.
-
-  # I should add the sample size required to find the range of effects.
-
+  #########################################################################
+  # Adjust the number of cores to suit your computing environment (e.g.,  #
+  # run parallel::detectCores() to find the number of available cores).   #
+  #########################################################################
 
 # Library -----------------------------------------------------------------
 
@@ -19,16 +13,20 @@ rm(list = ls())
   library(tidyverse); library(rstan); library(tidybayes)
 
   # Stan options
-  options(mc.cores = 8L)
-  # Sys.setenv(LOCAL_CPPFLAGS = '-march=native')
+  n_cores  <- 8
+  n_iter   <- 8000
+  n_warmup <- 1000
+  seeds    <- c(6967674, 5768664, 7517370, 6852246, 9115239, 5279371)
+  options(mc.cores = n_cores)
+  rstan_options(auto_write = TRUE)
   
-  # Functions
+  # Link functions
   r_to_z <- function(r) 0.5 * log( (1 + r) / (1 - r) )
   z_to_r <- function(z) ( exp(2 * z) - 1 ) / ( exp(2 * z) + 1 )
 
   
 # Prepare -----------------------------------------------------------------
-
+  
   # Load (preregistered) model
   model <- stan_model("models/2l-meta-analysis.stan")
   
@@ -36,26 +34,26 @@ rm(list = ls())
   dl <- read_rds("data/dl.rds")
   
   # Select outcomes
-  dl <- dl %>% 
+  es <- dl %>% 
     filter(x_var == "ic", y_var %in% c("pi", "ca", "ps")) %>% 
     group_by(id, sample, y_var) %>% 
     top_n(1, -x_rank) %>%
[…]

### 2020-08-21 scripts/run_preregistered_robustness_checks.R

@@ -1,0 +1,444 @@
+rm(list = ls())
+
+# Notes -------------------------------------------------------------------
+
+  #########################################################################
+  # Adjust the number of cores to suit your computing environment (e.g.,  #
+  # run parallel::detectCores() to find the number of available cores).   #
+  #########################################################################
+
+# Library -----------------------------------------------------------------
+
+  # Load packages
+  library(tidyverse); library(rstan); library(tidybayes)
+
+  # Stan options
+  n_cores  <- 8
+  n_iter   <- 8000
+  n_warmup <- 1000
+  seeds    <- c(6967674, 5768664, 7517370)
+  options(mc.cores = n_cores)
+  rstan_options(auto_write = TRUE)
+  Sys.setenv(LOCAL_CPPFLAGS = '-march=corei7 -mtune=corei7')
+  
+  # Link functions
+  r_to_z <- function(r) 0.5 * log( (1 + r) / (1 - r) )
+  z_to_r <- function(z) ( exp(2 * z) - 1 ) / ( exp(2 * z) + 1 )
+
+  
+# Prepare -----------------------------------------------------------------
+  
+  # Load (preregistered) model
+  model <- stan_model("models/2l-meta-analysis.stan")
+  
+  # Import data
+  dl <- read_rds("data/dl.rds")
+  
+  # Select outcomes
+  es <- dl %>% 
+    filter(x_var == "ic", y_var %in% c("pi", "ca", "ps")) %>% 
+    group_by(id, sample, y_var) %>% 
+    top_n(1, -x_rank) %>%
+    top_n(1, -y_rank) %>% 
+    ungroup()
+  
+  # Average effect sizes for multiple (equivalent) outcomes
+  es <- es %>% 
+    group_by(id, sample, x, y, x_var, y_var) %>% 
+    summarise(
+      n = unique(n), 
+      r = mean(r, na.rm = TRUE)
+    ) %>% 
+    ungroup() %>% 
+    select(id, sample, n, r, everything())
+  
+  # Import results from preregistered analyses
+  post <- read_rds("results/results_preregistered_analyses.rds")
+
+
+# Estimate (perceived injustice) ------------------------------------------
+  
[…]

### 2020-08-21 scripts/screen_records.R

@@ -52,6 +52,13 @@ rm(list = ls())
     select(-answer) %>% 
     pivot_wider(names_from = coder, values_from = decision) %>% 
     with(., kappa2(ratings = cbind(`Coder 1`, `Coder 2`)))
+  
+  # Caclulate interrater agreement for Second Search
+  ratings %>% 
+    filter(run == "Second Search") %>%
+    select(-answer) %>% 
+    pivot_wider(names_from = coder, values_from = decision) %>% 
+    with(., kappa2(ratings = cbind(`Coder 1`, `Coder 2`)))
 
 
 # Exclude -----------------------------------------------------------------

### 2020-08-27 manuscript/manuscript.Rmd
run meta-biases and confirmatory moderator analyses

@@
 (\\textbf{A}) Posterior distributions for the estimated mean correlation coefficient, highlighting the proportion of posterior samples for which $r_\\text{mean} < 0$.
-(\\textbf{B}) Posterior predictive distributions  for the estimated study-wise correlation coefficients."}
+(\\textbf{B}) Posterior predictive distributions for the estimated study-wise correlation coefficients, based on point estimates of the $\\mu$ and $\\tau_J$ parameters, with point estimates for the estimated correlation coefficients for all studies."}
 knitr::include_graphics("../figures/figure-3.pdf") 

### 2020-08-27 manuscript/manuscript.tex
run meta-biases and confirmatory moderator analyses

@@
 (\textbf{A}) Posterior distributions for the estimated mean correlation coefficient, highlighting the proportion of posterior samples for which $r_\text{mean} < 0$.
-(\textbf{B}) Posterior predictive distributions  for the estimated study-wise correlation coefficients.}\label{fig:unnamed-chunk-3}
+(\textbf{B}) Posterior predictive distributions for the estimated study-wise correlation coefficients, based on point estimates of the $\mu$ and $\tau_J$ parameters, with point estimates for the estimated correlation coefficients for all studies.}\label{fig:unnamed-chunk-3}
 \end{figure}

### 2020-08-27 figures/figure-2.R

@@ -1,0 +1,139 @@
+rm(list = ls())
+
+# Notes -------------------------------------------------------------------
+
+
+# Library -----------------------------------------------------------------
+
+  # Load packages
+  library(tidyverse); library(numform)
+
+
+# Prepare -----------------------------------------------------------------
+
+  # Import data
+  dl <- read_rds("data/dl.rds")
+  
+  # Select variables
+  dm <- dl %>% distinct(id, sample, n, country)
+  
+  # Separate samples with multiple countries (if possible)
+  dm <- dm %>% 
+    filter(
+      !(id == 829L & sample == 1L),
+      !(id == 956L & sample == 2L),
+      !(id == 3054L & sample == 1L)
+    ) %>% 
+    bind_rows(
+      tribble(
+          ~id, ~sample,   ~n, ~country,
+         829L,      1L,  55L, "Finland",
+         829L,      1L,  61L, "France",
+         829L,      1L,  89L, "Germany",
+         829L,      1L, 100L, "Norway",
+         829L,      1L, 273L, "Sweden",
+         829L,      1L, 158L, "Netherlands",
+         956L,      2L, 310L, "Germany",
+         956L,      2L, 123L, "UK",
+        3054L,      1L, 118L, "Chile",
+        3054L,      1L, 127L, "Chile",
+        3054L,      1L, 110L, "Germany",
+        3054L,      1L, 112L, "Kosovo",
+        3054L,      1L,  89L, "Poland",
+        3054L,      1L,  95L, "Serbia",
+        3054L,      1L,  27L, "Spain",
+        3054L,      1L,  89L, "Switzerland",
+        3054L,      1L, 127L, "UK",
+        3054L,      1L, 106L, "USA"
+      )
+    ) %>% 
+    arrange(id, sample)
+  
+  # Remove samples with multiple countries (if not)
+  dm <- dm %>% filter(
+    !(id == 3054L & sample == 11L), 
+    !(id == 303L & sample == 1L)
+  )
+  
+  # Prepare map data 
+  areas <- dm %>%
+    filter(!(country %in% c("Hong Kong", "Singapore"))) %>% 
+    group_by(country) %>% 
+    summarize(I = n(), J = n_distinct(id), N = sum(n)) %>%
+    left_join(
+      map_data("world"),
+      .,
+      by = c("region" = "country")
+    )
+    
+  # Prepare map data
+  cities <- dm %>%
+    filter(country %in% c("Hong Kong", "Singapore")) %>% 
[…]

### 2020-08-27 figures/figure-3.R

@@ -17,6 +17,9 @@ rm(list = ls())
   
   # Import results from preregistered analyses
   results <- read_rds("results/results_preregistered_analyses.rds")
+  
+  # Import study-wise estimates from preregistered analyses
+  r_pred_jj <- read_rds("results/r_pred_jj.rds")
 
   # Name predictor and outcome variables
   results <- results %>% 
@@ -27,6 +30,21 @@ rm(list = ls())
         "pi" = "Perceived injustice",
         "ca" = "Collective action",
         "ps" = "Policy support"
+      ),
+      y_name = recode_factor(
+        y_var,
+        "pi" = "Perceived injustice",
+        "ca" = "Collective action",
+        "ps" = "Policy support"
+      )
+    )
+  
+  # Name predictor and outcome variables
+  r_pred_jj <- r_pred_jj %>% 
+    mutate(
+      x_name = recode_factor(
+        x_var,
+        "ic" = "Intergroup contact",
       ),
       y_name = recode_factor(
         y_var,
@@ -177,6 +195,13 @@ rm(list = ls())
       label.colour = NA
     ) + 
     geom_vline(xintercept = 0, linetype = "dashed", size = 0.5) +
+    geom_point(
+      data = r_pred_jj %>%
+        group_by(x_name, y_name, jj) %>%
+        summarize(r = median(r_pred)),
+      y = 0,
+      shape = "|", size = 3
+    ) +
     scale_x_continuous(breaks = seq(-1, 1, 0.2)) +
     scale_fill_manual(
       values = c(

### 2020-08-27 figures/figure-meta-biases.R

@@ -1,0 +1,101 @@
+rm(list = ls())
+
+# Notes -------------------------------------------------------------------
+
+
+# Library -----------------------------------------------------------------
+
+  # Load packages
+  library(tidyverse); library(ggtext); library(numform)
+
+
+# Prepare -----------------------------------------------------------------
+
+  # Import results from meta-bias analyses
+  results <- read_rds("results/results_meta_biases.rds")
+  
+
+# Visualize ---------------------------------------------------------------
+
+  # Make figure
+  results %>% 
+    mutate(
+      estimate = if_else(method == "RMA", "unadjusted", "adjusted")
+    ) %>% 
+  ggplot(., aes(x = est, y = fct_rev(method))) +
+    geom_rect(
+      data = results %>% filter(method == "RMA"),
+      aes(xmin = l95, xmax = u95),
+      ymin = -Inf, ymax = Inf,
+      fill = "grey92"
+    ) +
+    geom_hline(
+      aes(yintercept = fct_rev(method)),
+      colour = "grey92"
+    ) +
+    geom_pointrange(
+      aes(xmin = l95, xmax = u95, fill = estimate),
+      shape = "circle filled",
+      fatten = 2,
+      size = 0.5
+    ) +
+    geom_vline(
+      xintercept = 0, 
+      linetype = "dashed",
+      size = 0.5
+    ) +
+    geom_richtext(
+      aes(label = paste0(f_num(est, 2), ", [", f_num(l95, 2), ", ", f_num(u95, 2), "]")),
+      x = 0.215,
+      size = 8/.pt,
+      hjust = 1, vjust = 0,
+      label.padding = unit(c(0, 0, 0, 0), "lines"),
+      label.margin = unit(c(0.2, 0.2, 0.2, 0.2), "lines"),
+      label.r = unit(0, "lines"),
+      label.colour = NA
+    ) +
+    scale_fill_manual(
+      values = c(
+        "adjusted" = "white",
+        "unadjusted" = "black"
+      )
+    ) +
+    coord_cartesian(
+      xlim = c(-0.215, 0.215),
+      ylim = c(0.5, 4.5),
+      expand = FALSE
+    ) +
+    facet_grid(. ~ y_name) +
+    theme_classic(base_size = 10) +
+    theme(
+      legend.position = "none",
+      strip.background = element_blank(),
+      axis.line = element_blank(),
+      axis.text.y = element_markdown(colour = "black"),
[…]

### 2020-08-27 scripts/code_measures.R

@@ -61,7 +61,7 @@ rm(list = ls())
   # Form consensus
   consensus <- c(
     "Directly", "Indirectly", "Indirectly", "Indirectly", "Indirectly",
-    "Indirectly", "Directly", "Directly", "Directly", "Both", 
+    "Indirectly", "Indirectly", "Directly", "Directly", "Directly", "Both", 
     "Personal", "Specific", "Personal", "Specific",  "Personal",
     "Specific", "Specific", "Group", "General", "General",
     "Specific", "Group", "General", "General", "Group",

### 2020-08-27 scripts/run_confirmatory_moderator_analyses.R

@@ -1,0 +1,684 @@
+rm(list = ls())
+
+# Notes -------------------------------------------------------------------
+
+  #########################################################################
+  # Adjust the number of cores to suit your computing environment (e.g.,  #
+  # run parallel::detectCores() to find the number of available cores).   #
+  #########################################################################
+
+# Library -----------------------------------------------------------------
+
+  # Load packages
+  library(tidyverse); library(rstan); library(tidybayes)
+
+  # Stan options
+  n_cores  <- 8
+  n_iter   <- 8000
+  n_warmup <- 1000
+  options(mc.cores = n_cores)
+  rstan_options(auto_write = TRUE)
+  
+  # Link functions
+  r_to_z <- function(r) 0.5 * log( (1 + r) / (1 - r) )
+  z_to_r <- function(z) ( exp(2 * z) - 1 ) / ( exp(2 * z) + 1 )
+
+  
+# Prepare -----------------------------------------------------------------
+  
+  # Import data
+  dl <- read_rds("data/dl.rds")
+  
+  # Select outcomes
+  es <- dl %>% 
+    filter(x_var == "ic", y_var %in% c("pi", "ca", "ps")) %>% 
+    group_by(id, sample, y_var) %>% 
+    top_n(1, -x_rank) %>%
+    top_n(1, -y_rank) %>% 
+    ungroup()
+  
+  # Average effect sizes for multiple (equivalent) outcomes
+  es <- es %>% 
+    group_by(id, sample, x, y, x_var, y_var) %>% 
+    summarise(
+      n = unique(n), 
+      r = mean(r, na.rm = TRUE)
+    ) %>% 
+    ungroup() %>% 
+    select(id, sample, n, r, everything())
+  
+  # Create indices
+  es <- es %>% 
+    group_by(y_var) %>% 
+    mutate(
+      ii = 1:n(),
+      jj = as.integer(factor(id))
+    ) %>% 
+    group_by(y_var, jj) %>% 
+    mutate(
+      n_sample = n(),
+      ii = if_else(n_sample == 1L, 0L, ii)
+    ) %>% 
+    ungroup() %>%
+    mutate(ii = as.integer(factor(ii)) - 1) %>% 
+    select(-n_sample)
+  
+  # Compile data as lists
+  data <- tibble(
+      y_var = c("pi", "ca", "ps"),
+      es = list(
+        es %>% filter(y_var == "pi"),
+        es %>% filter(y_var == "ca"),
[…]

### 2020-08-27 scripts/run_meta_bias_analyses.R

@@ -1,0 +1,161 @@
+rm(list = ls())
+
+# Notes -------------------------------------------------------------------
+
+
+# Library -----------------------------------------------------------------
+
+  # Load packages
+  library(tidyverse); library(metafor); library(weightr); library(puniform);
+  library(ggtext); library(numform)
+
+  # Link functions
+  r_to_z <- function(r) 0.5 * log( (1 + r) / (1 - r) )
+  z_to_r <- function(z) ( exp(2 * z) - 1 ) / ( exp(2 * z) + 1 )
+
+  
+# Prepare -----------------------------------------------------------------
+
+  # Import data
+  dl <- read_rds("data/dl.rds")
+
+  # Select outcomes
+  es <- dl %>% 
+    filter(x_var == "ic", y_var %in% c("pi", "ca", "ps")) %>% 
+    group_by(id, sample, y_var) %>% 
+    top_n(1, -x_rank) %>%
+    top_n(1, -y_rank) %>% 
+    ungroup()
+  
+  # Average effect sizes for multiple (equivalent) outcomes
+  es <- es %>% 
+    group_by(id, sample, x, y, x_var, y_var, publication_status) %>% 
+    summarise(
+      n = unique(n), 
+      r = mean(r, na.rm = TRUE)
+    ) %>% 
+    ungroup() %>% 
+    select(id, sample, n, r, everything())
+  
+  # Transform effect sizes for analyses
+  es <- es %>% 
+    group_by(y_var) %>% 
+    mutate(
+      ii = 1:n(),
+      yi = r_to_z(r),
+      vi = 1 / (n - 3)
+    ) %>% 
+    ungroup()
+  
+  # Compile for analyses
+  es <- tibble(
+      y_var = c("pi", "ca", "ps"),
+      es = list(
+        es %>% filter(y_var == "pi"),
+        es %>% filter(y_var == "ca"),
+        es %>% filter(y_var == "ps")
+      )
+    ) %>% 
+      mutate(
+      es = map(es, ~transmute(., ii, jj = as.integer(factor(id)), yi, vi))
+    )
+  
+
+# Estimate ----------------------------------------------------------------
+  
+  # Run analyses
+  results <- es %>% 
+    mutate(
+      rma = map(es, ~rma.mv(
+        yi = yi, 
+        V = vi, 
+        random = list(~ 1 | ii, ~ 1 | jj), 
[…]

### 2020-08-27 scripts/run_preregistered_analyses.R

@@ -362,6 +362,32 @@ rm(list = ls())
     by = c("x_var", "y_var")
   )
 
+  # Extract study-wise estimates
+  pred_jj <- bind_rows(
+      pi_fit %>% 
+        spread_draws(mu, tau_jj, b_jj[jj]) %>% 
+        mutate(x_var = "ic", y_var = "pi"),
+      ca_fit %>% 
+        spread_draws(mu, tau_jj, b_jj[jj]) %>% 
+        mutate(x_var = "ic", y_var = "ca"),
+      ps_fit %>% 
+        spread_draws(mu, tau_jj, b_jj[jj]) %>% 
+        mutate(x_var = "ic", y_var = "ps")
+    ) %>% 
+    mutate(
+      r_pred = z_to_r(mu + b_jj*tau_jj)
+    ) %>% 
+    select(-mu, -tau_jj, -b_jj) %>% 
+    ungroup() %>% 
+    left_join(
+      es %>% 
+        group_by(y_var) %>% 
+        mutate(jj = as.integer(factor(id))) %>% 
+        ungroup() %>% 
+        distinct(id, jj, x_var, y_var),
+      by = c("x_var", "y_var", "jj")
+    )
+  
 
 # Estimate statistical power ----------------------------------------------
 
@@ -390,6 +416,9 @@ rm(list = ls())
 
   # Export results (as .rds)
   write_rds(post, "results/results_preregistered_analyses.rds")
+  
+  # Export study-wise estimates (as .rds)
+  write_rds(pred_jj, "results/r_pred_jj.rds")
   
   # Export power predictions (as .rds)
   write_rds(n_req, "results/n_req.rds")

### 2021-03-02 manuscript/manuscript.tex
update references

@@
 
-\emph{Perceived injustice.} Across 200,229 participants from 117 samples
-in 81 studies, we found strong evidence for a weak association
+\emph{Perceived injustice.} Across 201,411 participants from 122 samples
+in 83 studies, we found strong evidence for a weak association
 (\(r = -.07, [-.11, -.04]\)) between intergroup contact and perceived
@@
 (\(\tau_J = .14, [.12, .17]\)) and across samples within studies
-(\(\tau_I = .09, [.06, .13]\)). Based on these analyses, we predicted
+(\(\tau_I = .08, [.05, .12]\)). Based on these analyses, we predicted
 that 80\% of studies would result in correlation coefficients between
-\(-.25, [-.30, -.21]\) and \(.11, [.06, .16]\) and that researchers
-would need sample sizes of at least 2,226, {[}1,521, 3,248{]}
+\(-.25, [-.30, -.21]\) and \(.10, [.06, .15]\) and that researchers
+would need sample sizes of at least 2,295, {[}1,562, 3,293{]}
 participants to find significant associations (\(\alpha = .05\),
@@
   80\% of studies, the absolute correlation coefficient would be
-  \(|r| > .042, [.034, .050]\) for perceived injustice,
+  \(|r| > .041, [.034, .050]\) for perceived injustice,
   \(|r| > .046, [.033, .067]\) for collective action, and
@@
 or wider prior distribution did not affect mean effect size estimates
-for perceived injustice (\(\Delta r = -.00, [-.05, .05]\) and
-\(\Delta r = -.00, [-.05, .05]\)), collective action
+for perceived injustice (\(\Delta r = -.00, [-.05, .04]\) and
+\(\Delta r = .00, [-.05, .05]\)), collective action
 (\(\Delta r = -.01, [-.11, .09]\) and \(\Delta r = -.00, [-.10, .11]\)),
@@
 the mean effect size for the three outcomes
-(\(\Delta r = -.01, [-.05, .04]\); \(\Delta r = .02, [-.09, .12]\);
+(\(\Delta r = .00, [-.04, .05]\); \(\Delta r = .02, [-.09, .12]\);
 \(\Delta r = -.02, [-.11, .07]\)). Together, these analyses showed that

### 2021-03-02 figures/figure-1.R

@@ -1,0 +1,246 @@
+rm(list = ls())
+
+# Notes -------------------------------------------------------------------
+
+
+# Library -----------------------------------------------------------------
+
+  # Load packages
+  library(tidyverse); library(glue); library(ggtext); library(numform)
+
+
+# Prepare -----------------------------------------------------------------
+
+  # Import data
+  dl <- read_rds("data/dl.rds")
+  
+  # Compile records
+  records <- bind_rows(
+    read_csv("records/records-cleaned.csv") %>% 
+      distinct(id) %>% 
+      mutate(stage = 1L), 
+    read_csv("records/records-screened.csv") %>% 
+      distinct(id) %>% 
+      mutate(stage = 2L),
+    read_csv("records/records-coded.csv") %>% 
+      distinct(id) %>% 
+      mutate(stage = 3L)
+  ) %>% 
+    anti_join(
+      bind_rows(
+        read_csv("records/results/unpublished-studies.csv") %>% distinct(id),
+        read_csv("records/results/citing-studies.csv") %>% distinct(id)
+      ),
+      by = "id"
+    ) %>% 
+    bind_rows(
+      dl %>% 
+        distinct(id, publication_status) %>% 
+        mutate(stage = 4L),
+      dl %>% 
+        distinct(id, publication_status) %>% 
+        mutate(stage = 5L)
+    ) %>% 
+    mutate(
+      source = case_when(
+        is.na(publication_status) ~ "database",
+        id %in% unique(read_csv("records/results/citing-studies.csv")$id) ~ "citing",
+        publication_status == "unpublished" ~ "unpublished",
+        TRUE ~ "database"
+      )
+    ) %>% 
+    bind_rows(
+      read_csv("records/results/unpublished-studies.csv") %>% 
+        distinct(id) %>% 
+        anti_join(
+          dl %>% filter(publication_status == "published") %>% distinct(id),
+          by = "id"
+        ) %>% 
+        mutate(stage = 3L, source = "unpublished"),
+      read_csv("records/results/citing-studies.csv") %>% 
+        distinct(id) %>% 
+        mutate(stage = 3L, source = "citing")
+    ) %>% 
+    count(stage, source) %>% 
+    pivot_wider(
[…]

### 2021-03-02 figures/figure-2.R

@@ -6,7 +6,12 @@ rm(list = ls())
 # Library -----------------------------------------------------------------
 
   # Load packages
-  library(tidyverse); library(numform)
+  library(tidyverse); library(numform); library(patchwork)
+
+# Visualize ---------------------------------------------------------------
+
+  # Figure 2a
+  source("figures/figure-2a.R")
 
 
 # Prepare -----------------------------------------------------------------
@@ -15,125 +20,266 @@ rm(list = ls())
   dl <- read_rds("data/dl.rds")
   
   # Select variables
-  dm <- dl %>% distinct(id, sample, n, country)
-  
-  # Separate samples with multiple countries (if possible)
-  dm <- dm %>% 
-    filter(
-      !(id == 829L & sample == 1L),
-      !(id == 956L & sample == 2L),
-      !(id == 3054L & sample == 1L)
+  dl <- dl %>% 
+    select(
+      id,
+      sample,
+      n,
+      country:publication_status 
     ) %>% 
-    bind_rows(
-      tribble(
-          ~id, ~sample,   ~n, ~country,
-         829L,      1L,  55L, "Finland",
-         829L,      1L,  61L, "France",
-         829L,      1L,  89L, "Germany",
-         829L,      1L, 100L, "Norway",
-         829L,      1L, 273L, "Sweden",
-         829L,      1L, 158L, "Netherlands",
-         956L,      2L, 310L, "Germany",
-         956L,      2L, 123L, "UK",
-        3054L,      1L, 118L, "Chile",
-        3054L,      1L, 127L, "Chile",
-        3054L,      1L, 110L, "Germany",
-        3054L,      1L, 112L, "Kosovo",
-        3054L,      1L,  89L, "Poland",
-        3054L,      1L,  95L, "Serbia",
-        3054L,      1L,  27L, "Spain",
-        3054L,      1L,  89L, "Switzerland",
-        3054L,      1L, 127L, "UK",
-        3054L,      1L, 106L, "USA"
+    distinct()
+
+# Visualize ---------------------------------------------------------------
+
+  # Figure 2b
+  f_2b <- dl %>% 
+    mutate(
+      continent = case_when(
+        str_detect(continent, ",") ~ "Mixed",
+        TRUE ~ continent
       )
     ) %>% 
-    arrange(id, sample)
-  
-  # Remove samples with multiple countries (if not)
-  dm <- dm %>% filter(
[…]

### 2021-03-02 figures/figure-2a.R

@@ -1,0 +1,227 @@
+# Notes -------------------------------------------------------------------
+
+  #########################################################################
+  # Thanks to Claus Wilke for implementing the "Interrupted Goode         #
+  # homolosine" projection in R.                                          #
+  #########################################################################
+
+# Library -----------------------------------------------------------------
+  
+  # Load packages
+  library(tidyverse); library(sf); library(rworldmap); library(numform)
+
+
+# Prepare map -------------------------------------------------------------
+
+  # Load map
+  world_sf <- st_as_sf(getMap(resolution = "low"))
+  
+  # Prepare map projection
+  crs_goode <- "+proj=igh"
+  goode_outline <- list(cbind(
+    longs <- c(
+      rep(180, 181), 
+      rep(c(80.01, 79.99), each = 91), 
+      rep(c(-19.99, -20.01), each = 91), 
+      rep(c(-99.99, -100.01), each = 91),
+      rep(-180, 181), 
+      rep(c(-40.01, -39.99), each = 91),
+      180 
+    ), 
+    lats <- c(
+      90:-90,
+      -90:0, 0:-90, 
+      -90:0, 0:-90, 
+      -90:0, 0:-90, 
+      -90:90, 
+      90:0, 0:90, 
+      90
+    )
+  )) %>%
+    st_polygon() %>%
+    st_sfc(
+      crs = "+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs"
+    )
+  goode_outline <- st_transform(goode_outline, crs = crs_goode)
+  xlim <- st_bbox(goode_outline)[c("xmin", "xmax")]*1.1
+  ylim <- st_bbox(goode_outline)[c("ymin", "ymax")]*1.1
+  goode_encl_rect <- 
+    list(
+      cbind(
+        c(xlim[1], xlim[2], xlim[2], xlim[1], xlim[1]), 
+        c(ylim[1], ylim[1], ylim[2], ylim[2], ylim[1])
+      )
+    ) %>%
+    st_polygon() %>%
+    st_sfc(crs = crs_goode)
+  goode_without <- st_difference(goode_encl_rect, goode_outline)
+  
+  
+# Prepare data ------------------------------------------------------------
+
+  # Import data
+  dl <- read_rds("data/dl.rds")
+  
+  # Select variables
+  dm <- dl %>% distinct(id, sample, n, country)
+  
[…]

### 2021-03-02 figures/figure-4.R

@@ -1,0 +1,156 @@
+rm(list = ls())
+
+# Notes -------------------------------------------------------------------
+
+
+# Library -----------------------------------------------------------------
+
+  # Load packages
+  library(tidyverse); library(tidybayes); library(ggtext); library(numform)
+
+  # Link functions
+  r_to_z <- function(r) 0.5 * log( (1 + r) / (1 - r) )
+  z_to_r <- function(z) ( exp(2 * z) - 1 ) / ( exp(2 * z) + 1 )
+  
+
+# Prepare -----------------------------------------------------------------
+  
+  # Import results from moderator analyses
+  results <- read_rds("results/results_confirmatory_moderator_analyses.rds")
+  
+  # Transform to long format
+  results <- results %>% 
+    select(y_var, moderator, r_kk) %>% 
+    filter(moderator != "cultural_distance_to_usa") %>% 
+    unnest(r_kk)
+  
+  # Name moderator and outcome variables
+  results <- results %>% 
+    mutate(
+      y_name = recode_factor(
+        y_var,
+        "pi" = "Perceived injustice",
+        "ca" = "Collective action",
+        "ps" = "Policy support"
+      ),
+      moderator = recode_factor(
+        moderator,
+        "study_setting" = "Study setting",
+        "study_design" = "Study design",
+        "study_sample" = "Study\nsample",
+        "study_intention" = "Study\nintention",
+        "publication_status" = "Publication\nstatus",
+        "ic_direct" = "Intergroup\ncontact",
+        "pi_specific" = "Perceived\ninjustice",
+        "pi_personal" = "Perceived\ninjustice "
+      ),
+      category = Hmisc::capitalize(category),
+      category = recode(
+        category,
+        "Quasi-experimental (no random assignment)" = "Quasi-experimental",
+        "Experimental (random assignment)" = "Experimental",
+      ),
+      category = factor(category, levels = c(
+        "Observational, cross-sectional", 
+        "Observational, longitudinal",
+        "Quasi-experimental",
+        "Experimental",
+        "Short-term migration",
+        "Long-term migration",
+        "Slavery",
+        "Colonization",
+        "Religion",
+        "Caste",
+        "Sexuality",
+        "Other",
+        "Convenience sample",
+        "Probability/representative sample",
[…]

### 2021-03-02 figures/figure-5.R

@@ -1,0 +1,117 @@
+rm(list = ls())
+
+# Notes -------------------------------------------------------------------
+
+
+# Library -----------------------------------------------------------------
+
+  # Load packages
+  library(tidyverse); library(tidybayes); library(ggrepel)
+
+  # Link functions
+  r_to_z <- function(r) 0.5 * log( (1 + r) / (1 - r) )
+  z_to_r <- function(z) ( exp(2 * z) - 1 ) / ( exp(2 * z) + 1 )
+  
+
+# Prepare -----------------------------------------------------------------
+  
+  # Import results from preregistered analyses
+  results <- read_rds("results/results_cultural_distance.rds")
+  
+  # Name predictor and outcome variables
+  results <- results %>% 
+    mutate(
+      y_name = recode_factor(
+        y_var,
+        "pi" = "Perceived injustice",
+        "ca" = "Collective action",
+        "ps" = "Policy support"
+      )
+    )
+  
+  # Extract estimates
+  r_fixed <- results %>% 
+    select(-jj, -b_jj, -tau_jj, -country, -cultural_distance) %>% 
+    distinct() %>% 
+    crossing(cultural_distance = seq(0.0, 0.2, 0.001)) %>% 
+    group_by(y_name, cultural_distance) %>% 
+    mutate(
+      r = z_to_r(mu + b_x*cultural_distance)
+    ) %>% 
+    median_qi(r)
+  
+  # Extract country-wise estimates
+  r_country <- results %>% 
+    group_by(y_name, country, cultural_distance) %>% 
+    mutate(
+      r = z_to_r(mu + b_x*cultural_distance + b_jj*tau_jj)
+    ) %>% 
+    median_qi(r)
+  
+
+# Figure 5 ----------------------------------------------------------------
+
+  # Visualize
+  ggplot(r_fixed, aes(x = cultural_distance, y = r)) +
+    geom_ribbon(
+      aes(ymin = .lower, ymax = .upper, fill = y_name),
+      alpha = 0.4
+    ) +
+    geom_pointrange(
+      data = r_country,
+      aes(ymin = .lower, ymax = .upper),
+      colour = "grey45",
+      fatten = 1,
+      size = 0.2
+    ) +
+    geom_text_repel(
+      data = r_country,
+      aes(label = country),
+      size = 6/.pt, segment.size = 0.2,
+      colour = "grey45"
+    ) +
+    geom_line(size = 0.5) +
[…]

### 2021-03-02 figures/figure-7.R

@@ -1,0 +1,193 @@
+rm(list = ls())
+
+# Notes -------------------------------------------------------------------
+
+
+# Library -----------------------------------------------------------------
+
+  # Load packages
+  library(tidyverse); library(ggtext); library(patchwork); library(numform)
+
+
+# Prepare -----------------------------------------------------------------
+  
+  # Import results from analyses with alternative predictors
+  results <- bind_rows(
+    read_rds("results/results_analyses_with_negative_contact.rds"),
+    read_rds("results/results_analyses_with_ingroup_contact.rds")
+  )
+
+  # Name predictor and outcome variables
+  results <- results %>% 
+    mutate(
+      x_name = recode_factor(
+        x_var,
+        "pc" = "Positive contact",
+        "nc" = "Negative contact",
+        "og" = "Outgroup contact",
+        "ig" = "Ingroup contact"
+      ),
+      y_name = recode_factor(
+        y_var,
+        "nc" = "Negative contact",
+        "og" = "Outgroup contact",
+        "pi" = "Perceived injustice",
+        "ca" = "Collective action",
+        "ps" = "Policy support",
+      )
+    )
+
+
+# Figure 7a ---------------------------------------------------------------
+
+  # Prepare
+  d_7a <- results %>% 
+    filter(x_var %in% c("pc", "nc"), y_var %in% c("pi", "ca", "ps")) %>% 
+    mutate(
+      text = paste0("*I* = ", I, ", *J* = ", J, ", *N* = ", f_comma(N))
+    )
+  
+  # Visualize
+  f_7a <- ggplot(d_7a, aes(x = r_mean)) +
+    geom_density(
+      aes(fill = x_name),
+      colour = NA,
+      adjust = 2,
+      n = 1e4,
+      alpha = 0.8
+    ) +
+    geom_density(
+      aes(group = x_name),
+      colour = "white",
+      size = 0.2,
+      adjust = 2, 
+      n = 1e4
+    ) +
+    geom_richtext(
+      data = d_7a %>% group_by(y_name) %>% summarise(text = unique(text)),
+      aes(label = text),
+      x = 0.315, y = 27,
+      hjust = 1, vjust = 1,
+      size = 10*0.8/.pt,
+      label.colour = NA
+    ) +
+    geom_vline(xintercept = 0, linetype = "dashed", size = 0.5) +
[…]

### 2021-03-02 figures/figure-meta-biases.R

@@ -1,101 +1,0 @@
-rm(list = ls())
-
-# Notes -------------------------------------------------------------------
-
-
-# Library -----------------------------------------------------------------
-
-  # Load packages
-  library(tidyverse); library(ggtext); library(numform)
-
-
-# Prepare -----------------------------------------------------------------
-
-  # Import results from meta-bias analyses
-  results <- read_rds("results/results_meta_biases.rds")
-  
-
-# Visualize ---------------------------------------------------------------
-
-  # Make figure
-  results %>% 
-    mutate(
-      estimate = if_else(method == "RMA", "unadjusted", "adjusted")
-    ) %>% 
-  ggplot(., aes(x = est, y = fct_rev(method))) +
-    geom_rect(
-      data = results %>% filter(method == "RMA"),
-      aes(xmin = l95, xmax = u95),
-      ymin = -Inf, ymax = Inf,
-      fill = "grey92"
-    ) +
-    geom_hline(
-      aes(yintercept = fct_rev(method)),
-      colour = "grey92"
-    ) +
-    geom_pointrange(
-      aes(xmin = l95, xmax = u95, fill = estimate),
-      shape = "circle filled",
-      fatten = 2,
-      size = 0.5
-    ) +
-    geom_vline(
-      xintercept = 0, 
-      linetype = "dashed",
-      size = 0.5
-    ) +
-    geom_richtext(
-      aes(label = paste0(f_num(est, 2), ", [", f_num(l95, 2), ", ", f_num(u95, 2), "]")),
-      x = 0.215,
-      size = 8/.pt,
-      hjust = 1, vjust = 0,
-      label.padding = unit(c(0, 0, 0, 0), "lines"),
-      label.margin = unit(c(0.2, 0.2, 0.2, 0.2), "lines"),
-      label.r = unit(0, "lines"),
-      label.colour = NA
-    ) +
-    scale_fill_manual(
-      values = c(
-        "adjusted" = "white",
-        "unadjusted" = "black"
-      )
-    ) +
-    coord_cartesian(
-      xlim = c(-0.215, 0.215),
-      ylim = c(0.5, 4.5),
-      expand = FALSE
-    ) +
-    facet_grid(. ~ y_name) +
-    theme_classic(base_size = 10) +
-    theme(
-      legend.position = "none",
-      strip.background = element_blank(),
-      axis.line = element_blank(),
-      axis.text.y = element_markdown(colour = "black"),
[…]

### 2021-03-02 scripts/code_moderators.R

@@ -457,6 +457,7 @@ rm(list = ls())
     mutate(
       publication_status = case_when(
         !is.na(publication_status) ~ publication_status,
+        id == 2396 ~ "published",
         between(id, 2380L, 2999L) ~ "unpublished",
         id >= 4000L ~ "published",
         id == 2257L ~ "published"

### 2021-03-02 scripts/run_analyses_with_ingroup_contact.R

@@ -1,0 +1,407 @@
+rm(list = ls())
+
+# Notes -------------------------------------------------------------------
+
+
+# Library -----------------------------------------------------------------
+  
+  # Load packages
+  library(tidyverse); library(rstan); library(tidybayes)
+  
+  # Stan options
+  n_cores  <- 8
+  n_iter   <- 8000
+  n_warmup <- 1000
+  seeds    <- c(6967674, 5768664, 7517370, 3223639)
+  options(mc.cores = n_cores)
+  rstan_options(auto_write = TRUE)
+  
+  # Functions
+  source("scripts/functions.R")
+  r_to_z <- function(r) 0.5 * log( (1 + r) / (1 - r) )
+  z_to_r <- function(z) ( exp(2 * z) - 1 ) / ( exp(2 * z) + 1 )
+
+
+# Prepare -----------------------------------------------------------------
+
+  # Import data
+  dl <- read_rds("data/dl.rds") %>% filter(!is.na(n), !is.na(r))
+  
+  # Select studies/samples
+  dl <- dl %>% 
+    filter(x == "in") %>% 
+    distinct(id, sample) %>% 
+    semi_join(dl, ., by = c("id", "sample"))
+  
+  # Select outgroup contact variable
+  dl <- dl %>% 
+    mutate(
+      x = case_when(
+        id ==  703L & x == "cf" ~ "og",
+        id ==  733L & x == "ic" ~ "og",
+        id ==  803L & x == "cq" ~ "og",
+        id == 1020L & sample == 1L & x == "ic" ~ "og",
+        id == 1020L & sample == 2L & x == "ic" ~ "og",
+        id == 1042L & sample == 1L & x == "cq" ~ "og",
+        id == 1042L & sample == 2L & x == "cq" ~ "og",
+        id == 1695L & x == "cq" ~ "og",
+        id == 1891L & x == "cf" ~ "og",
+        id == 1914L & x == "in" ~ "og",
+        id == 1993L & x == "cq" ~ "og",
+        id == 2381L & x == "cf" ~ "og",
+        id == 2382L & x == "cf" ~ "og",
+        id == 2383L & x == "cf" ~ "og",
+        id == 2396L & x == "cf" ~ "og",
+        TRUE ~ x
+      ),
[…]

### 2021-03-02 scripts/run_analyses_with_negative_contact.R

@@ -1,0 +1,355 @@
+rm(list = ls())
+
+# Notes -------------------------------------------------------------------
+
+
+# Library -----------------------------------------------------------------
+
+  # Load packages
+  library(tidyverse); library(rstan); library(tidybayes)
+  
+  # Stan options
+  n_cores  <- 8
+  n_iter   <- 8000
+  n_warmup <- 1000
+  seeds    <- c(6967674, 5768664, 7517370, 1585380)
+  options(mc.cores = n_cores)
+  rstan_options(auto_write = TRUE)
+  
+  # Functions
+  source("scripts/functions.R")
+  r_to_z <- function(r) 0.5 * log( (1 + r) / (1 - r) )
+  z_to_r <- function(z) ( exp(2 * z) - 1 ) / ( exp(2 * z) + 1 )
+  
+  
+# Prepare -----------------------------------------------------------------
+  
+  # Import data
+  dl <- read_rds("data/dl.rds") %>% filter(!is.na(n), !is.na(r))
+  
+  # Prepare data
+  es <- left_join(
+    dl %>% 
+      filter(x == "pc", y_var %in% c("pi", "ca", "ps")) %>% 
+      select(id, sample, n, y, y_var, y_name, r_pc = r),
+    dl %>% 
+      filter(x == "nc", y_var %in% c("pi", "ca", "ps")) %>% 
+      select(id, sample, n, y, y_var, y_name, r_nc = r),
+    by = c("id", "sample", "n", "y", "y_var", "y_name")
+  ) %>% 
+    left_join(
+      dl %>% 
+        filter(x == "pc", y == "nc") %>% 
+        mutate(r = if_else(is.na(r_ac), r, r_ac)) %>% 
+        select(id, sample, n, r_pc_nc = r),
+      by = c("id", "sample", "n")
+    ) %>% 
+    filter(!is.na(r_pc), !is.na(r_nc), !is.na(r_pc_nc))
+  
+  # Exclude irrelevant effect sizes
+  es <- dl %>% 
+    left_join(es) %>% 
+    filter(
+      !is.na(r_pc), 
+      !is.na(r_nc), 
+      !is.na(r_pc_nc),
+      x %in% c("pc", "nc"),
+      y_var %in% c("pi", "ca", "ps")
+    ) %>% 
[…]

### 2021-03-02 scripts/run_confirmatory_moderator_analyses.R

@@ -122,11 +122,15 @@ rm(list = ls())
       r_kk = map2(
         fit,
         es,
-        ~spread_draws(.x, r_kk[kk]) %>% 
+        ~spread_draws(.x, r_kk[kk], R2) %>% 
           left_join(
             distinct(.y, kk, category),
             by = "kk"
           )
+      ),
+      R2 = map(
+        fit,
+        ~spread_draws(., R2)
       )
     )
   
@@ -189,6 +193,10 @@ rm(list = ls())
             distinct(.y, kk, category),
             by = "kk"
           )
+      ),
+      R2 = map(
+        fit,
+        ~spread_draws(., R2)
       )
     )
   
@@ -257,6 +265,10 @@ rm(list = ls())
             distinct(.y, kk, category),
             by = "kk"
           )
+      ),
+      R2 = map(
+        fit,
+        ~spread_draws(.x, R2)
       )
     )
   
@@ -338,6 +350,10 @@ rm(list = ls())
             distinct(.y, kk, category),
             by = "kk"
           )
+      ),
+      R2 = map(
+        fit,
+        ~spread_draws(.x, R2)
       )
     )
   
@@ -420,6 +436,10 @@ rm(list = ls())
             distinct(.y, kk, category),
             by = "kk"
           )
+      ),
+      R2 = map(
+        fit,
+        ~spread_draws(., R2)
       )
     )
   
@@ -503,6 +523,10 @@ rm(list = ls())
             distinct(.y, kk, category),
             by = "kk"
           )
+      ),
+      R2 = map(
+        fit,
+        ~spread_draws(., R2)
       )
     )
   
@@ -530,11 +554,17 @@ rm(list = ls())
           dl %>% distinct(id, sample, category = publication_status),
           by = c("id", "sample")
         ) %>% mutate(
+          category = recode(
+            category,
+            "published" = "published",
+            "unpublished dissertation" = "unpublished",
+            "unpublished" = "unpublished"
+          ),
           kk = recode(
             category,
             "published" = 1L,
-            "unpublished dissertation" = 2L,
-            "unpublished" = 3L
+            # "unpublished dissertation" = 2L,
+            "unpublished" = 2L
           )
         )
       ),
@@ -569,7 +599,11 @@ rm(list = ls())
           left_join(
             distinct(.y, kk, category),
             by = "kk"
-          )
+          ),
+        R2 = map(
+          fit,
+          ~spread_draws(., R2)
+        )
[…]

### 2021-03-02 scripts/run_meta_bias_analyses.R

@@ -29,7 +29,7 @@ rm(list = ls())
   
   # Average effect sizes for multiple (equivalent) outcomes
   es <- es %>% 
-    group_by(id, sample, x, y, x_var, y_var, publication_status) %>% 
+    group_by(id, sample, x, y, x_var, y_var, publication_status, study_intention) %>% 
     summarise(
       n = unique(n), 
       r = mean(r, na.rm = TRUE)
@@ -47,6 +47,16 @@ rm(list = ls())
     ) %>% 
     ungroup()
   
+  # Add predictor variable
+  es <- es %>% 
+    mutate(
+      potential_bias = if_else(
+        publication_status == "published" & study_intention == "Yes",
+        1L,
+        0L
+      )
+    )
+  
   # Compile for analyses
   es <- tibble(
       y_var = c("pi", "ca", "ps"),
@@ -57,7 +67,14 @@ rm(list = ls())
       )
     ) %>% 
       mutate(
-      es = map(es, ~transmute(., ii, jj = as.integer(factor(id)), yi, vi))
+      es = map(es, ~transmute(
+        ., 
+        ii, 
+        jj = as.integer(factor(id)), 
+        yi, 
+        vi,
+        potential_bias
+      ))
     )
   
 
@@ -94,6 +111,13 @@ rm(list = ls())
         yi = .$yi,
         vi = .$vi, 
         side = "left"
+      )),
+      mod = map(es, ~rma.mv(
+        yi = yi, 
+        V = vi, 
+        random = list(~ 1 | ii, ~ 1 | jj), 
+        data = .,
+        mods = ~ potential_bias
       ))
     )
   
@@ -121,7 +145,10 @@ rm(list = ls())
       weightr_u95 = map_dbl(weightr, ~.$ci.ub_adj[2,1]),
       punistar_est = map_dbl(punistar, ~.$est),
       punistar_l95 = map_dbl(punistar, ~.$ci.lb),
-      punistar_u95 = map_dbl(punistar, ~.$ci.ub)
+      punistar_u95 = map_dbl(punistar, ~.$ci.ub),
+      mod_est = map_dbl(mod, ~.$b[1,1]),
+      mod_l95 = map_dbl(mod, ~.$ci.lb[1]),
+      mod_u95 = map_dbl(mod, ~.$ci.ub[1])
     ) %>% 
     select(-starts_with("pet_"), -starts_with("peese_"))
   
@@ -143,7 +170,8 @@ rm(list = ls())
         "rma" = "RMA",
[…]

### 2021-03-20 manuscript/manuscript.Rmd
update figures

--- 2020-08-21 manuscript/manuscript.Rmd
@@
 ---
-title: "Meta-analysis of the `ironic' effects of intergroup contact"
-author:
-  - Nils K. Reimer
-  - Nikhil K. Sengupta
+title: "Meta-Analysis of the `Ironic' Effects of Intergroup Contact"
+bibliography: references.bib
+csl: apa.csl
 output:
@@
     latex_engine: pdflatex
-    keep_tex: true
-    # template: custom-template.tex
+    keep_tex: yes
+    template: custom-template.tex
 ---
@@
 
+[@pettigrew_meta-analytic_2006]
+
 # Results
@@
 ## Search results
+
+```{=latex}
+\begin{figure*}[!t]
+\centering
+\caption{Flow diagram illustrating the preregistered search strategy, study selection, and data collection}
+\includegraphics[scale=1]{../figures/figure-1}
+\label{fig:f1}
+\end{figure*}
+```
+
+```{=latex}
+\begin{figure*}
+\centering
+\caption{Overview of the relevant literature}
+\includegraphics[scale=1]{../figures/figure-2}
+\caption*{\textit{Note.} \textbf{A} Map of all countries included in the meta-analysis with combined sample sizes.
+\textbf{B} Proportion of eligible samples in each category as well as the absolute number of samples in each category.}
+\label{fig:f2}
+\end{figure*}
+```
 
@@
 
-```{r, fig_width = "100%", fig.align = "center", fig.cap = "Results of preregistered analyses.
-(\\textbf{A}) Posterior distributions for the estimated mean correlation coefficient, highlighting the proportion of posterior samples for which $r_\\text{mean} < 0$.
-(\\textbf{B}) Posterior predictive distributions  for the estimated study-wise correlation coefficients."}
-knitr::include_graphics("../figures/figure-3.pdf") 
+```{=latex}
+\begin{figure*}
+\centering
+\caption{Posterior distributions from the preregistered random-effect meta-analysis models}
+\includegraphics[scale=1]{../figures/figure-3}
+\caption*{\textit{Note.} \textbf{A} Posterior distributions for the estimated mean correlation coefficients, highlighting the proportion of posterior samples for which $r_\text{mean} < 0$.
+\textbf{B} Posterior predictive distributions for the estimated study-wise correlation coefficients, based on point estimates of the $\mu$ and $\tau_J$ parameters, with point estimates for the estimated correlation coefficients for all studies in the sample.}
+\label{fig:f3}
+\end{figure*}
 ```
@@
 Together, these analyses showed that our findings were robust to choosing different prior distributions and to excluding influential studies.
+
+# References
+
+\begingroup
+
+\noindent
+\setlength{\parindent}{-0.5in}
+\setlength{\leftskip}{0.5in}
+
+<div id="refs"></div>
+
+\endgroup

### 2021-03-20 manuscript/manuscript.tex
update figures

@@
-% Options for packages loaded elsewhere
-\PassOptionsToPackage{unicode}{hyperref}
-\PassOptionsToPackage{hyphens}{url}
-%
-\documentclass[
-]{article}
-\usepackage{lmodern}
-\usepackage{amssymb,amsmath}
-\usepackage{ifxetex,ifluatex}
-\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
-  \usepackage[T1]{fontenc}
+\documentclass[twocolumn, 10pt, letterpaper]{article}
+
+% Font
 \usepackage[utf8]{inputenc}
-  \usepackage{textcomp} % provide euro and other symbols
-\else % if luatex or xetex
-  \usepackage{unicode-math}
-  \defaultfontfeatures{Scale=MatchLowercase}
-  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
-\fi
-% Use upquote if available, for straight quotes in verbatim environments
-\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
-\IfFileExists{microtype.sty}{% use microtype if available
-  \usepackage[]{microtype}
-  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
-}{}
-\makeatletter
-\@ifundefined{KOMAClassName}{% if non-KOMA class
-  \IfFileExists{parskip.sty}{%
-    \usepackage{parskip}
-  }{% else
-    \setlength{\parindent}{0pt}
-    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
-}{% if KOMA class
-  \KOMAoptions{parskip=half}}
-\makeatother
-\usepackage{xcolor}
-\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
-\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
-\hypersetup{
-  pdftitle={Meta-analysis of the `ironic' effects of intergroup contact},
-  pdfauthor={Nils K. Reimer; Nikhil K. Sengupta},
-  hidelinks,
-  pdfcreator={LaTeX via pandoc}}
-\urlstyle{same} % disable monospaced font for URLs
-\usepackage[margin=1in]{geometry}
-\usepackage{graphicx,grffile}
-\makeatletter
-\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
-\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
-\makeatother
-% Scale images if necessary, so that they will not overflow the page
-% margins by default, and it is still possible to overwrite the defaults
-% using explicit options in \includegraphics[width, height, ...]{}
-\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
-% Set default figure placement to htbp
-\makeatletter
-\def\fps@figure{htbp}
-\makeatother
-\setlength{\emergencystretch}{3em} % prevent overfull lines
-\providecommand{\tightlist}{%
-  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
-\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
+\usepackage{MinionPro} 
+\input{glyphtounicode}
+\pdfgentounicode=1 
+\usepackage{microtype}
 
-\title{Meta-analysis of the `ironic' effects of intergroup contact}
-\author{Nils K. Reimer \and Nikhil K. Sengupta}
-\date{}
+% Format
+\usepackage[letterpaper, margin = 1in]{geometry}
+\setcounter{secnumdepth}{0}
+\usepackage{authblk}
+% \renewcommand\Affilfont{\small}
+% \usepackage[hang, flushmargin]{footmisc}
+\setlength{\columnsep}{15pt}
+
+% Links
+\usepackage[colorlinks = true, linkcolor = black, urlcolor = black, citecolor = black]{hyperref}
+
+% Figures
+\usepackage{graphicx}
+\usepackage[labelfont = bf, labelsep = newline, singlelinecheck = false]{caption}
+
+% Tables
+\usepackage{booktabs}
+\usepackage{tabularx}
+\usepackage[table, xcdraw]{xcolor}
 
 \begin{document}
-\maketitle
+
+(Pettigrew \& Tropp, 2006)
 
@@
 \subsection{Search results}\label{search-results}}
+
+\begin{figure*}[!t]
+\centering
+\caption{Flow diagram illustrating the preregistered search strategy, study selection, and data collection}
+\includegraphics[scale=1]{../figures/figure-1}
+\label{fig:f1}
+\end{figure*}
+
+\begin{figure*}
+\centering
+\caption{Overview of the relevant literature}
+\includegraphics[scale=1]{../figures/figure-2}
+\caption*{\textit{Note.} \textbf{A} Map of all countries included in the meta-analysis with combined sample sizes.
+\textbf{B} Proportion of eligible samples in each category as well as the absolute number of samples in each category.}
+\label{fig:f2}
+\end{figure*}
 
@@
 
-\begin{figure}
+\begin{figure*}
+\centering
+\caption{Posterior distributions from the preregistered random-effect meta-analysis models}
+\includegraphics[scale=1]{../figures/figure-3}
+\caption*{\textit{Note.} \textbf{A} Posterior distributions for the estimated mean correlation coefficients, highlighting the proportion of posterior samples for which $r_\text{mean} < 0$.
+\textbf{B} Posterior predictive distributions for the estimated study-wise correlation coefficients, based on point estimates of the $\mu$ and $\tau_J$ parameters, with point estimates for the estimated correlation coefficients for all studies in the sample.}
+\label{fig:f3}
+\end{figure*}
 
-{\centering \includegraphics{../figures/figure-3}
-
-}
-
-\caption{Results of preregistered analyses.
-(\textbf{A}) Posterior distributions for the estimated mean correlation coefficient, highlighting the proportion of posterior samples for which $r_\text{mean} < 0$.
-(\textbf{B}) Posterior predictive distributions for the estimated study-wise correlation coefficients, based on point estimates of the $\mu$ and $\tau_J$ parameters, with point estimates for the estimated correlation coefficients for all studies.}\label{fig:unnamed-chunk-3}
-\end{figure}
-
-\emph{Perceived injustice.} Across 201,411 participants from 122 samples
-in 83 studies, we found strong evidence for a weak association
-(\(r = -.07, [-.11, -.04]\)) between intergroup contact and perceived
+\emph{Perceived injustice.} Across 201,912 participants from 123 samples
+in 84 studies, we found strong evidence for a weak association
+(\(r = -.07, [-.10, -.04]\)) between intergroup contact and perceived
 injustice, with \(>99.9\%\) of posterior samples for the mean
@@
 that 80\% of studies would result in correlation coefficients between
-\(-.25, [-.30, -.21]\) and \(.10, [.06, .15]\) and that researchers
-would need sample sizes of at least 2,295, {[}1,562, 3,293{]}
+\(-.25, [-.30, -.21]\) and \(.11, [.07, .16]\) and that researchers
+would need sample sizes of at least 2,299, {[}1,558, 3,295{]}
 participants to find significant associations (\(\alpha = .05\),
@@
   \(|r| > .041, [.034, .050]\) for perceived injustice,
-  \(|r| > .046, [.033, .067]\) for collective action, and
+  \(|r| > .045, [.032, .065]\) for collective action, and
   \(|r| > .036, [.022, .064]\) for policy support.}
 
-\emph{Collective action.} Across 118,584 participants from 36 samples in
-23 studies, we found some evidence for a weak association
-(\(r = -.06, [-.14, .01]\)) between intergroup contact and collective
-action, with \(95.0\%\) of posterior samples for the mean correlation
+\emph{Collective action.} Across 119,085 participants from 37 samples in
+24 studies, we found some evidence for a weak association
+(\(r = -.06, [-.13, .02]\)) between intergroup contact and collective
+action, with \(93.6\%\) of posterior samples for the mean correlation
 coefficient falling below zero. We found evidence that correlation
-coefficients varied across studies (\(\tau_J = .17, [.12, .24]\)) and
-across samples within studies (\(\tau_I = .09, [.06, .15]\)). Based on
+coefficients varied across studies (\(\tau_J = .16, [.12, .23]\)) and
+across samples within studies (\(\tau_I = .09, [.06, .14]\)). Based on
 these analyses, we predicted that 80\% of studies would result in
-correlation coefficients between \(-.27, [-.38, -.18]\) and
-\(.15, [.06, .27]\) and that researchers would need sample sizes of at
-least 1,801, {[}848, 3,458{]} participants to find significant
+correlation coefficients between \(-.26, [-.37, -.18]\) and
+\(.15, [.07, .27]\) and that researchers would need sample sizes of at
+least 1,925, {[}911, 3,724{]} participants to find significant
 associations (\(\alpha = .05\), two-sided) in 80\% of their studies.
@@
 relationships, we used cross-sectional correlation coefficients as
-effect sizes for longitudinal studies. Across 111,252 participants from
-24 samples in 13 studies, we found evidence for a moderate association
-(\(r = .29, [.21, .37]\)) between perceived injustice and collective
+effect sizes for longitudinal studies. Across 111,753 participants from
+25 samples in 14 studies, we found evidence for a moderate association
+(\(r = .31, [.23, .38]\)) between perceived injustice and collective
 action. Across 6,244 participants from 12 samples in 9 studies, we found
@@
 
+\hypertarget{references}{%
+\section{References}\label{references}}
+
+\begingroup
+
+\noindent \setlength{\parindent}{-0.5in} \setlength{\leftskip}{0.5in}
+
+\hypertarget{refs}{}
+\leavevmode\hypertarget{ref-pettigrew_meta-analytic_2006}{}%
+Pettigrew, T. F., \& Tropp, L. R. (2006). A meta-analytic test of
+intergroup contact theory. \emph{Journal of Personality and Social
+Psychology}, \emph{90}(5), 751--783.
+\url{https://doi.org/10.1037/0022-3514.90.5.751}
+
+\endgroup
+
 \end{document}

### 2021-03-20 figures/figure-1.R

@@ -234,13 +234,13 @@ rm(list = ls())
   # Export figure (as .pdf)
   ggsave(
     "figures/figure-1.pdf",
-    width = 5.6, height = 4.7, units = "in",
+    width = 6.5, height = 4.7, units = "in",
     device = cairo_pdf
   )
   
   # Export figure (as .png)
   ggsave(
     "figures/figure-1.png",
-    width = 5.6, height = 4.7, units = "in",
+    width = 6.5, height = 4.7, units = "in",
     dpi = 600
   )      

### 2021-03-20 figures/figure-2.R

@@ -81,6 +81,7 @@ rm(list = ls())
       panel.grid.major.x = element_line(colour = "grey92")
     ) +
     labs(
+      tag = "B",
       title = "Continent"
     )
 
@@ -263,7 +264,6 @@ rm(list = ls())
     #DE
     "
   ) + plot_annotation(
-    tag_levels = "A",
     theme = theme(plot.tag = element_text(face = "bold"))
   )
 
@@ -272,14 +272,14 @@ rm(list = ls())
   # Export figure (as .pdf)
   ggsave(
     "figures/figure-2.pdf",
-    width = 5.6, height = 5.6/3*4, units = "in",
+    width = 6.5, height = 7.5, units = "in",
     device = cairo_pdf
   )
   
   # Export figure (as .png)
   ggsave(
     "figures/figure-2.png",
-    width = 5.6, height = 5.6/3*4, units = "in",
+    width = 6.5, height = 7.5, units = "in",
     dpi = 600
   )    
     

### 2021-03-20 figures/figure-2a.R

@@ -215,6 +215,9 @@
       legend.justification = c(0, 0),
       panel.background = element_rect(fill = "#56B4E950", color = "white", size = 1),
       panel.grid = element_blank()
+    ) +
+    labs(
+      tag = "A"
     )
 
 

### 2021-03-20 figures/figure-3.R

@@ -6,11 +6,18 @@ rm(list = ls())
 # Library -----------------------------------------------------------------
 
   # Load packages
-  library(tidyverse); library(ggtext); library(patchwork); library(numform)
+  library(tidyverse)
+  library(tidybayes)
+  library(ggtext)
+  library(patchwork)
+  library(numform)
 
   # Link functions
   r_to_z <- function(r) 0.5 * log( (1 + r) / (1 - r) )
   z_to_r <- function(z) ( exp(2 * z) - 1 ) / ( exp(2 * z) + 1 )
+  
+  # Set seed (for posterior predictive simulations)
+  set.seed(9071118)
   
 
 # Prepare -----------------------------------------------------------------
@@ -26,16 +33,16 @@ rm(list = ls())
     mutate(
       x_name = recode_factor(
         x_var,
-        "ic" = "Intergroup contact",
-        "pi" = "Perceived injustice",
-        "ca" = "Collective action",
-        "ps" = "Policy support"
+        "ic" = "Intergroup Contact",
+        "pi" = "Perceived Injustice",
+        "ca" = "Collective Action",
+        "ps" = "Policy Support"
       ),
       y_name = recode_factor(
         y_var,
-        "pi" = "Perceived injustice",
-        "ca" = "Collective action",
-        "ps" = "Policy support"
+        "pi" = "Perceived Injustice",
+        "ca" = "Collective Action",
+        "ps" = "Policy Support"
       )
     )
   
@@ -44,13 +51,13 @@ rm(list = ls())
     mutate(
       x_name = recode_factor(
         x_var,
-        "ic" = "Intergroup contact",
+        "ic" = "Intergroup Contact",
       ),
       y_name = recode_factor(
         y_var,
-        "pi" = "Perceived injustice",
-        "ca" = "Collective action",
-        "ps" = "Policy support"
+        "pi" = "Perceived Injustice",
+        "ca" = "Collective Action",
+        "ps" = "Policy Support"
       )
     )
   
@@ -66,20 +73,16 @@ rm(list = ls())
   
   # Visualize
   f_3a <- ggplot(d_3a, aes(x = r_mean)) +
-    geom_density(
-      aes(fill = y_name),
-      colour = NA,
[…]

### 2021-03-20 figures/figure-4.R

@@ -6,7 +6,8 @@ rm(list = ls())
 # Library -----------------------------------------------------------------
 
   # Load packages
-  library(tidyverse); library(tidybayes); library(ggtext); library(numform)
+  library(tidyverse); library(tidybayes); library(ggtext); 
+  library(patchwork); library(numform)
 
   # Link functions
   r_to_z <- function(r) 0.5 * log( (1 + r) / (1 - r) )
@@ -20,9 +21,22 @@ rm(list = ls())
   
   # Transform to long format
   results <- results %>% 
-    select(y_var, moderator, r_kk) %>% 
-    filter(moderator != "cultural_distance_to_usa") %>% 
-    unnest(r_kk)
+    transmute(
+      y_var, 
+      moderator,
+      draws = map2(
+        r_kk,
+        R2,
+        ~left_join(.x, .y, by = c(".chain", ".iteration", ".draw"))
+      )
+    ) %>% 
+    unnest(draws) %>% 
+    left_join(
+      results %>% 
+        transmute(y_var, moderator, es = map(es, ~count(., kk, name = "I"))) %>% 
+        unnest(es),
+      by = c("y_var", "moderator", "kk")
+    )
   
   # Name moderator and outcome variables
   results <- results %>% 
@@ -35,36 +49,45 @@ rm(list = ls())
       ),
       moderator = recode_factor(
         moderator,
-        "study_setting" = "Study setting",
-        "study_design" = "Study design",
-        "study_sample" = "Study\nsample",
-        "study_intention" = "Study\nintention",
-        "publication_status" = "Publication\nstatus",
-        "ic_direct" = "Intergroup\ncontact",
-        "pi_specific" = "Perceived\ninjustice",
-        "pi_personal" = "Perceived\ninjustice "
+        "study_setting" = "Study Setting",
+        "study_design" = "Study Design",
+        "study_sample" = "Study Sample",
+        "age" = "Age",
+        "study_intention" = "Study Intention",
+        "publication_status" = "Publication Status",
+        "ic_direct" = "Predictor (Direct/Indirect)",
+        "pi_specific" = "Outcome (Specific/General)",
+        "pi_personal" = "Outcome (Personal/Group)"
       ),
-      category = Hmisc::capitalize(category),
       category = recode(
         category,
-        "Quasi-experimental (no random assignment)" = "Quasi-experimental",
[…]

### 2021-03-20 figures/figure-5.R

@@ -23,9 +23,9 @@ rm(list = ls())
     mutate(
       y_name = recode_factor(
         y_var,
-        "pi" = "Perceived injustice",
-        "ca" = "Collective action",
-        "ps" = "Policy support"
+        "pi" = "Perceived Injustice",
+        "ca" = "Collective Action",
+        "ps" = "Policy Support"
       )
     )
   
@@ -76,9 +76,9 @@ rm(list = ls())
     scale_y_continuous(breaks = seq(-1, 1, 0.1)) +
     scale_fill_manual(
       values = c(
-        "Perceived injustice" = "#648FFF", 
-        "Collective action" = "#DC267F", 
-        "Policy support" = "#FFB000"
+        "Perceived Injustice" = "#648FFF", 
+        "Collective Action" = "#DC267F", 
+        "Policy Support" = "#FFB000"
       )
     ) +
     facet_grid(. ~ y_name) +
@@ -104,14 +104,14 @@ rm(list = ls())
   # Export figure (as .pdf)
   ggsave(
     "figures/figure-5.pdf",
-    width = 15.14, height = 15.14/2, units = "cm",
+    width = 6.5, height = 6.5/2, units = "in",
     device = cairo_pdf
   )
   
   # Export figure (as .png)
   ggsave(
     "figures/figure-5.png",
-    width = 15.14, height = 15.14/2, units = "cm",
+    width = 6.5, height = 6.5/2, units = "in",
     dpi = 600
   )  
   

### 2021-03-20 figures/figure-6.R

@@ -6,75 +6,128 @@ rm(list = ls())
 # Library -----------------------------------------------------------------
 
   # Load packages
-  library(tidyverse); library(ggtext); library(numform)
+  library(tidyverse); library(tidybayes); library(patchwork)
+  library(ggtext); library(numform)
 
 
 # Prepare -----------------------------------------------------------------
 
-  # Import results from meta-bias analyses
-  results <- read_rds("results/results_meta_biases.rds")
+  # Import results from meta-regression trees 
+  results <- read_rds("results/results_exploratory_moderator_analyses.rds")
   
+  
+# Figure 6a ---------------------------------------------------------------
 
-# Figure 6 ----------------------------------------------------------------
-
-  # Visualize
-  results %>% 
-    mutate(
-      estimate = if_else(method == "RMA", "unadjusted", "adjusted")
-    ) %>% 
-  ggplot(., aes(x = est)) +
+  # Prepare data for subfigure
+  d_6a <- results %>% distinct(kk, n)
+  
+  # Create boxes
+  boxes <- tibble(
+    xmin = c(0.0, 1.0, 2.0, 3.0, 3.0, 3.0, 3.0),
+    xmax = c(0.8, 1.8, 2.8, 3.8, 3.8, 3.8, 3.8),
+    ymin = c(1.5, 1.0, 0.5, 0.0, 1.0, 2.0, 3.0),
+    ymax = c(2.3, 1.8, 1.3, 0.8, 1.8, 2.8, 3.8)
+  )
+  
+  # Create arrows
+  arrows <- tibble(
+    x    = c(0.8, 0.8, 1.8, 1.8, 2.8, 2.8),
+    xend = c(1.0, 3.0, 2.0, 3.0, 3.0, 3.0),
+    y    = c(1.9, 1.9, 1.4, 1.4, 0.9, 0.9),
+    yend = c(1.4, 3.4, 0.9, 2.4, 1.4, 0.4)
+  )
+  
+  # Create labels
+  labels <- tibble(
+    x = c(0.4, 1.4, 2.4, 3.4, 3.4, 3.4, 3.4),
+    y = c(1.9, 1.4, 0.9, 0.4, 1.4, 2.4, 3.4),
+    text = c(
+      glue("*I* = {sum(d_6a$n)}"),
+      glue("Adults<br>*I* = {d_6a$n[2] + d_6a$n[3] + d_6a$n[4]}"),
[…]

### 2021-03-20 figures/figure-7.R

@@ -6,92 +6,75 @@ rm(list = ls())
 # Library -----------------------------------------------------------------
 
   # Load packages
-  library(tidyverse); library(ggtext); library(patchwork); library(numform)
+  library(tidyverse); library(ggtext); library(numform)
 
 
 # Prepare -----------------------------------------------------------------
-  
-  # Import results from analyses with alternative predictors
-  results <- bind_rows(
-    read_rds("results/results_analyses_with_negative_contact.rds"),
-    read_rds("results/results_analyses_with_ingroup_contact.rds")
-  )
 
-  # Name predictor and outcome variables
-  results <- results %>% 
+  # Import results from meta-bias analyses
+  results <- read_rds("results/results_meta_biases.rds")
+  
+
+# Figure 7 ----------------------------------------------------------------
+
+  # Visualize
+  results %>% 
     mutate(
-      x_name = recode_factor(
-        x_var,
-        "pc" = "Positive contact",
-        "nc" = "Negative contact",
-        "og" = "Outgroup contact",
-        "ig" = "Ingroup contact"
+      estimate = if_else(method == "RMA", "unadjusted", "adjusted")
+    ) %>% 
+  ggplot(., aes(x = est)) +
+    geom_rect(
+      data = results %>% filter(method == "RMA") %>% select(-method),
+      aes(xmin = l95, xmax = u95),
+      ymin = -Inf, ymax = Inf,
+      fill = "grey92"
+    ) +
+    geom_hline(
+      aes(yintercept = fct_rev(method)),
+      colour = "grey92"
+    ) +
+    geom_pointrange(
+      aes(xmin = l95, xmax = u95, y = fct_rev(method), fill = estimate),
+      shape = "circle filled",
+      fatten = 2,
+      size = 0.5
+    ) +
+    geom_vline(
+      xintercept = 0, 
+      linetype = "dashed",
+      size = 0.5
+    ) +
+    geom_richtext(
+      aes(
+        label = paste0(f_num(est, 2), ", [", f_num(l95, 2), ", ", f_num(u95, 2), "]"),
+        y = fct_rev(method)
       ),
-      y_name = recode_factor(
-        y_var,
-        "nc" = "Negative contact",
-        "og" = "Outgroup contact",
-        "pi" = "Perceived injustice",
[…]

### 2021-03-20 figures/figure-8.R

@@ -1,0 +1,215 @@
+rm(list = ls())
+
+# Notes -------------------------------------------------------------------
+
+
+# Library -----------------------------------------------------------------
+
+  # Load packages
+  library(tidyverse)
+  library(tidybayes)
+  library(ggtext)
+  library(patchwork)
+  library(numform)
+
+
+# Prepare -----------------------------------------------------------------
+  
+  # Import results from analyses with alternative predictors
+  results <- bind_rows(
+    read_rds("results/results_analyses_with_negative_contact.rds"),
+    read_rds("results/results_analyses_with_ingroup_contact.rds")
+  )
+
+  # Name predictor and outcome variables
+  results <- results %>% 
+    mutate(
+      x_name = recode_factor(
+        x_var,
+        "pc" = "Positive Contact",
+        "nc" = "Negative Contact",
+        "og" = "Outgroup Contact",
+        "ig" = "Ingroup Contact"
+      ),
+      y_name = recode_factor(
+        y_var,
+        "nc" = "Negative Contact",
+        "og" = "Outgroup Contact",
+        "pi" = "Perceived Injustice",
+        "ca" = "Collective Action",
+        "ps" = "Policy Support",
+      )
+    )
+
+
+# Figure 8a ---------------------------------------------------------------
+
+  # Prepare
+  d_8a <- results %>% 
+    filter(x_var %in% c("pc", "nc"), y_var %in% c("pi", "ca", "ps")) %>% 
+    mutate(
+      text = paste0("*I* = ", I, ", *J* = ", J, ", *N* = ", f_comma(N))
+    )
+  
+  # Visualize
+  f_8a <- ggplot(d_8a, aes(x = r_mean)) +
+    stat_halfeye(
+      aes(fill = x_name),
+      point_interval = NULL,
+      adjust = 2,
+      n = 1e4,
+      alpha = 0.8
+    ) +
+    stat_halfeye(
+      aes(group = x_name),
+      point_interval = NULL,
+      adjust = 2,
+      n = 1e4,
+      slab_colour = "white",
+      slab_fill = NA,
+      slab_size = 0.2
+    ) +
+    geom_vline(xintercept = 0, linetype = "dashed", size = 0.5) +
+    geom_richtext(
+      data = d_8a %>% group_by(y_name) %>% summarise(text = unique(text)),
+      aes(
+        label = text, 
[…]

### 2021-03-20 scripts/run_meta_bias_analyses.R

@@ -175,9 +175,9 @@ rm(list = ls())
       ),
       y_name = recode_factor(
         y_var,
-        "pi" = "Perceived injustice",
-        "ca" = "Collective action",
-        "ps" = "Policy support"
+        "pi" = "Perceived Injustice",
+        "ca" = "Collective Action",
+        "ps" = "Policy Support"
       )
     ) %>% 
     select(y_var, y_name, method, est, l95, u95)

### 2021-03-20 scripts/run_moderator_analyses.R

@@ -96,22 +96,6 @@ rm(list = ls())
     ungroup() %>% 
     select(id, sample, n, r, everything())
   
-  # Create indices
-  es <- es %>% 
-    group_by(y_var) %>% 
-    mutate(
-      ii = 1:n(),
-      jj = as.integer(factor(id))
-    ) %>% 
-    group_by(y_var, jj) %>% 
-    mutate(
-      n_sample = n(),
-      ii = if_else(n_sample == 1L, 0L, ii)
-    ) %>% 
-    ungroup() %>%
-    mutate(ii = as.integer(factor(ii)) - 1) %>% 
-    select(-n_sample)
-  
   # Compile data as lists
   data <- tibble(
       y_var = c("pi", "ca", "ps"),
@@ -122,11 +106,10 @@ rm(list = ls())
       )
     )
 
-
 # Study setting -----------------------------------------------------------
 
   # Load model
-  model <- stan_model("models/2l-meta-analysis-categorical-moderators.stan")
+  model <- stan_model("models/1l-meta-analysis-categorical-moderators.stan")
   
   # Prepare data list
   results <- data %>% 
@@ -141,15 +124,14 @@ rm(list = ls())
         ) %>% filter(
           !str_detect(category, ",")
         ) %>% mutate(
+          ii = row_number(),
           kk = as.integer(factor(category))
         )
       ),
       dlist = map(es, ~with(., list(
         I  = length(ii),
-        J  = max(jj),
         K  = max(kk),
         ii = ii,
-        jj = jj,
         kk = kk,
         r  = r,
         n  = n
@@ -167,20 +149,7 @@ rm(list = ls())
         iter = n_warmup + n_iter/n_cores,
         warmup = n_warmup,
         seed = 4232087
-      )),
-      r_kk = map2(
-        fit,
-        es,
-        ~spread_draws(.x, r_kk[kk], R2) %>% 
-          left_join(
-            distinct(.y, kk, category),
-            by = "kk"
-          )
-      ),
-      R2 = map(
-        fit,
-        ~spread_draws(., R2)
-      )
+      ))
     )
   
   # Compile results
@@ -194,7 +163,7 @@ rm(list = ls())
 # Study design ------------------------------------------------------------
 
   # Load model
-  model <- stan_model("models/2l-meta-analysis-categorical-moderators.stan")
+  model <- stan_model("models/1l-meta-analysis-categorical-moderators.stan")
   
[…]

### 2021-03-22 manuscript/manuscript.Rmd
update posterior predictive simulations

@@
 
-  # Make posterior predictions
+  # Summarize results
   results <- read_rds("../results/results_preregistered_analyses.rds") %>% 
-    mutate(
-      r_pred_l80 = z_to_r(qnorm(0.10, mu, tau_jj)),
-      r_pred_u80 = z_to_r(qnorm(0.90, mu, tau_jj)),
-    )
-
-  # Summarise results
-  results <- results %>% 
     pivot_longer(
-      c(r_mean, tau_ii, tau_jj, r_pred_l80, r_pred_u80),
+      c(r_mean, tau_ii, tau_jj),
       names_to = "parameter",
@@
 
-  # Summarize predictions for statistical power
-  n_req <- read_rds("../results/n_req.rds") %>%
-    group_by(y_var) %>%
+  # Set seed (for posterior predictive simulations)
+  set.seed(9071118)
+
+  # Simulate posterior predictions
+  post_pred <- read_rds("../results/results_preregistered_analyses.rds") %>% 
+    filter(x_var == "ic") %>% 
+    mutate(
+      r_pred = z_to_r(rnorm(n = n(), mean = mu, sd = tau_jj))
+    )
+
+  # Define functions for power calculations
+  p_value <- function(r, n) 2*min(pnorm(0, r_to_z(r), 1/sqrt(n - 3)), 1-pnorm(0, r_to_z(r), 1/sqrt(n - 3)))
+  p_value <- Vectorize(p_value)
+  n_req   <- function(r) uniroot(function(n) ( 0.05 - p_value(r, n) ), c(3, 1e6))$root
+  n_req   <- Vectorize(n_req)
+
+  # Summarize posterior predictions
+  post_pred <- post_pred %>% 
+    group_by(x_var, y_var) %>% 
     summarize(
+      r_pred_l80 = quantile(r_pred, 0.10),
+      r_pred_u80 = quantile(r_pred, 0.90),
+      r_abs = quantile(abs(r_pred), 0.20),
+      n_req = n_req(r_abs)
+    ) %>% 
+    ungroup() %>% 
+    mutate(
       across(
-        c(n, r),
-        list(
-          "med" = ~median(.),
-          "l95" = ~quantile(., 0.025),
-          "u95" = ~quantile(., 0.975)
-        )
-      )
-    ) %>%
-    mutate(
-      across(starts_with("n"), ~f_comma(ceiling(.))),
-      across(starts_with("r"), ~f_num(., digits = 3)),
-      n_text = paste0(n_med, ", [", n_l95, ", ", n_u95, "]"),
-      r_text = paste0("$|r| > ", r_med, ", [", r_l95, ", ", r_u95, "]$")
+        c(r_pred_l80, r_pred_u80),
+        ~f_num(., digits = 2)
+      ),
+      r_abs = paste0("$|r| > ", f_num(r_abs, digits = 3), "$"),
+      n_req = f_comma(ceiling(n_req))
     )
@@
 We found evidence that correlation coefficients varied across studies (`r pi_results$text[pi_results$parameter == "tau_jj"]`) and across samples within studies  (`r pi_results$text[pi_results$parameter == "tau_ii"]`).
-Based on these analyses, we predicted that 80\% of studies would result in correlation coefficients between `r pi_results$text[pi_results$parameter == "r_pred_l80"]` and `r pi_results$text[pi_results$parameter == "r_pred_u80"]` and that researchers would need sample sizes of at least `r n_req$n_text[n_req$y_var == "pi"]` participants to find significant associations ($\alpha = .05$, two-sided) in 80\% of their studies.^[Sample sizes are based on posterior predictions from the three models, which implied that, for 80\% of studies, the absolute correlation coefficient would be `r n_req$r_text[n_req$y_var == "pi"]` for perceived injustice, `r n_req$r_text[n_req$y_var == "ca"]` for collective action, and `r n_req$r_text[n_req$y_var == "ps"]` for policy support.]
+Based on these analyses, we predicted that 80\% of studies would result in correlation coefficients between `r post_pred$r_pred_l80[post_pred$y_var == "pi"]` and `r post_pred$r_pred_u80[post_pred$y_var == "pi"]` and that researchers would need sample sizes of at least `r post_pred$n_req[post_pred$y_var == "pi"]` participants to find significant associations ($\alpha = .05$, two-sided) in 80\% of their studies.^[Sample sizes are based on posterior predictions from the three models, which implied that, for 80\% of studies, the absolute correlation coefficient would be `r post_pred$r_abs[post_pred$y_var == "pi"]` for perceived injustice, `r post_pred$r_abs[post_pred$y_var == "ca"]` for collective action, and `r post_pred$r_abs[post_pred$y_var == "ps"]` for policy support.]
 
@@
 We found evidence that correlation coefficients varied across studies (`r ca_results$text[ca_results$parameter == "tau_jj"]`) and across samples within studies  (`r ca_results$text[ca_results$parameter == "tau_ii"]`).
-Based on these analyses, we predicted that 80\% of studies would result in correlation coefficients between `r ca_results$text[pi_results$parameter == "r_pred_l80"]` and `r ca_results$text[pi_results$parameter == "r_pred_u80"]` and that researchers would need sample sizes of at least `r n_req$n_text[n_req$y_var == "ca"]` participants to find significant associations ($\alpha = .05$, two-sided) in 80\% of their studies.
+Based on these analyses, we predicted that 80\% of studies would result in correlation coefficients between `r post_pred$r_pred_l80[post_pred$y_var == "ca"]` and `r post_pred$r_pred_u80[post_pred$y_var == "ca"]` and that researchers would need sample sizes of at least `r post_pred$n_req[post_pred$y_var == "ca"]` participants to find significant associations ($\alpha = .05$, two-sided) in 80\% of their studies.
 
@@
 We found evidence that correlation coefficients varied across studies (`r ps_results$text[ps_results$parameter == "tau_jj"]`) and, to a lesser extent, across samples within studies  (`r ps_results$text[ps_results$parameter == "tau_ii"]`).
-Based on these analyses, we predicted that 80\% of studies would result in correlation coefficients between `r ps_results$text[pi_results$parameter == "r_pred_l80"]` and `r ps_results$text[pi_results$parameter == "r_pred_u80"]` and that researchers would need sample sizes of at least `r n_req$n_text[n_req$y_var == "ps"]` participants to find significant associations ($\alpha = .05$, two-sided) in 80\% of their studies.
+Based on these analyses, we predicted that 80\% of studies would result in correlation coefficients between `r post_pred$r_pred_l80[post_pred$y_var == "ps"]` and `r post_pred$r_pred_u80[post_pred$y_var == "ps"]` and that researchers would need sample sizes of at least `r post_pred$n_req[post_pred$y_var == "ps1"]` participants to find significant associations ($\alpha = .05$, two-sided) in 80\% of their studies.
 

### 2021-03-22 manuscript/manuscript.tex
update posterior predictive simulations

@@
 that 80\% of studies would result in correlation coefficients between
-\(-.25, [-.30, -.21]\) and \(.11, [.07, .16]\) and that researchers
-would need sample sizes of at least 2,299, {[}1,558, 3,295{]}
-participants to find significant associations (\(\alpha = .05\),
+-.25 and .11 and that researchers would need sample sizes of at least
+2,538 participants to find significant associations (\(\alpha = .05\),
 two-sided) in 80\% of their studies.\footnote{Sample sizes are based on
@@
   80\% of studies, the absolute correlation coefficient would be
-  \(|r| > .041, [.034, .050]\) for perceived injustice,
-  \(|r| > .045, [.032, .065]\) for collective action, and
-  \(|r| > .036, [.022, .064]\) for policy support.}
+  \(|r| > .039\) for perceived injustice, \(|r| > .045\) for collective
+  action, and \(|r| > .035\) for policy support.}
 
@@
 these analyses, we predicted that 80\% of studies would result in
-correlation coefficients between \(-.26, [-.37, -.18]\) and
-\(.15, [.07, .27]\) and that researchers would need sample sizes of at
-least 1,925, {[}911, 3,724{]} participants to find significant
+correlation coefficients between -.27 and .16 and that researchers would
+need sample sizes of at least 1,882 participants to find significant
 associations (\(\alpha = .05\), two-sided) in 80\% of their studies.
@@
 that 80\% of studies would result in correlation coefficients between
-\(-.20, [-.32, -.13]\) and \(.06, [-.02, .18]\) and that researchers
-would need sample sizes of at least 2,992, {[}949, 8,077{]} participants
-to find significant associations (\(\alpha = .05\), two-sided) in 80\%
-of their studies.
+-.21 and .07 and that researchers would need sample sizes of at least
+3,208 participants to find significant associations (\(\alpha = .05\),
+two-sided) in 80\% of their studies.
 

### 2021-03-22 scripts/run_preregistered_analyses.R

@@ -387,29 +387,6 @@ rm(list = ls())
         distinct(id, jj, x_var, y_var),
       by = c("x_var", "y_var", "jj")
     )
-  
-
-# Estimate statistical power ----------------------------------------------
-
-  # Define functions
-  p_value <- function(r, n) 2*min(pnorm(0, r_to_z(r), 1/sqrt(n - 3)), 1-pnorm(0, r_to_z(r), 1/sqrt(n - 3)))
-  p_value <- Vectorize(p_value)
-  n_req   <- function(r) uniroot(function(n) ( 0.05 - p_value(r, n) ), c(3, 1e6))$root
-  n_req   <- Vectorize(n_req)
-  
-  # Estimate required n 
-  n_req <- post %>%
-    filter(x_var == "ic") %>% 
-    select(.chain:.draw, y_var, mu, tau_jj) %>% 
-    mutate(
-      z = map2_dbl(
-        mu,
-        tau_jj,
-        ~uniroot(function(z) 0.20 - diff(pnorm(c(-z, z), .x, .y)), c(-1, 1))$root
-      ),
-      r = z_to_r(z),
-      n = n_req(r)
-    )
 
 
 # Export ------------------------------------------------------------------
@@ -419,6 +396,3 @@ rm(list = ls())
   
   # Export study-wise estimates (as .rds)
   write_rds(pred_jj, "results/r_pred_jj.rds")
-  
-  # Export power predictions (as .rds)
-  write_rds(n_req, "results/n_req.rds")

### 2021-04-13 manuscript/manuscript.Rmd
first complete draft

@@
 ---
-title: "Meta-Analysis of the `Ironic' Effects of Intergroup Contact"
+title: "Meta-Analysis of the 'Ironic' Effects of Intergroup Contact"
 bibliography: references.bib
@@
     keep_tex: yes
-    template: custom-template.tex
+    template: preprint-template.tex
+  word_document:
+    reference_docx: word-template.docx
 ---
@@
 
-[@pettigrew_meta-analytic_2006]
+It is ironic that psychology’s most-researched paradigm for reducing prejudice—intergroup contact—should hinder, rather than help, social change.
+Hundreds of studies have confirmed that intergroup contact is associated with less negative feelings toward outgroup members [for a meta-analysis, see @pettigrew_meta-analytic_2006].
+Most of these studies have focused on advantaged-group members' contact experiences with disadvantaged-group members [@tropp_relationships_2005], guided by the idea that reducing advantaged-group members' prejudice will prevent interpersonal discrimination.
+Reducing prejudice, however, is rarely enough to overcome institutional and structural discrimination.
+Instead, as the 2020 Black Lives Matter protests have shown, social change often requires political mobilization by the disadvantaged.
+Critics have argued that, by fostering harmony and reducing conflict, intergroup contact might distract disadvantaged-group members from the injustice they face and undermine their motivation for social change [@dixon_beyond_2005; @reicher_rethinking_2007; @brown_strategic_2003].
+By stifling disadvantaged-group members' opposition to injustice, intergroup contact might thus have the 'ironic' [@saguy_irony_2009], 'sedative' [@cakal_investigation_2011], or 'paradoxical' [@dixon_paradox_2010] effect of hindering social change.
 
-# Results
+Supporting this argument, initial studies provided evidence that, among disadvantaged-group members, intergroup contact reduces perceptions of injustice [@saguy_irony_2009], discourages collective action [@cakal_investigation_2011], and diminishes support for reparative policies [@dixon_intergroup_2007].
+Others, however, have pointed to conflicting evidence [@poore_contact_2002] and argued that intergroup contact might instead render discrimination more salient and, thereby, increase disadvantaged-group members' support for social change [@pettigrew_recent_2011].
+A decade after the initial studies, many more studies have examined the relationships between intergroup contact and support for social change in disadvantaged groups.
+We present a systematic review and meta-analysis of this growing literature.
+Specifically, we evaluate the evidence for three hypotheses about how intergroup contact might reduce support for social change.
 
-## Search results
+Perceived injustice—that is, perceiving unjust group-based deprivation or discrimination against the disadvantaged ingroup—is a prerequisite to instigating social change [@van_zomeren_toward_2008].
+Researchers have argued that positive contact with advantaged-group members could contradict perceptions of personal discrimination, undermine negative characterizations of the advantaged outgroup, and, thereby, make group discrimination appear less plausible [@dixon_paradox_2010].
+Positive contact could further reduce perceived injustice by emphasizing commonalities over differences [@saguy_irony_2009] and by motivating disadvantaged-group members to adopt system-justifying ideologies [@sengupta_perpetuating_2013].
+To the extent that it reduces perceived injustice, intergroup contact hinders social change.
+
+Collective action—that is, any action directed at improving the conditions of the disadvantaged ingroup [@wright_responding_1990]—is crucial to achieving social change because advantaged-group members rarely surrender their advantages without sustained pressure from disadvantaged-group members [@blumer_race_1958; for a review, see @dixon_beyond_2012].
+Researchers have argued that intergroup contact could discourage disadvantaged-group members from engaging in collective action by diminishing their perceived discrimination [@tropp_crossethnic_2012], by blurring boundaries between the disadvantaged ingroup and the advantaged outgroup [@saguy_irony_2009], by reducing negative attitudes toward the advantaged outgroup [@wright_struggle_2009], and by quelling anger about inequality [@tausch_how_2015] or toward the advantaged outgroup [@hayward_how_2018].
+To the extent that it discourages collective action, intergroup contact hinders social change.
+
+Reparative policies (e.g., affirmative action) can be effective means to reduce social inequality.
+Disadvantaged-group members, who stand to benefit from their implementation, are important advocates for these policies.
+Researchers have argued that intergroup contact could diminish disadvantaged-group members’ support for redistributive policies by creating sympathy for advantaged-group members [@dixon_intergroup_2007], by fostering positive outgroup attitudes and reducing attention to inequality [@saguy_irony_2009], and by increasing their endorsement of system-justifying ideologies [@sengupta_perpetuating_2013].
+To the extent that it diminishes support for redistributive policies, intergroup contact hinders social change.
+
+As a growing number of studies had been examining these relationships, we conducted a preregistered meta-analytic review of the available evidence for the hypothesized negative effects of intergroup contact on perceived injustice, collective action, and policy support in disadvantaged groups.
+
+Our first objective was to systematically review the available evidence and to evaluate its strengths and limitations.
+Our second objective was to synthesize the available evidence to establish the direction and magnitude of the relationships between intergroup contact and the three outcomes.
+Doing so allows us, first, to determine whether the available evidence supports a negative or positive [see @pettigrew_recent_2011] relationship between contact and support for social change and, second, to estimate the strength of this relationship.
+Our third objective was to explore the variability of this relationship across study settings, designs, and other potential moderators.
+For example, we examined whether any effects were confined to Western, Educated, Industrialized, Rich, Democratic (WEIRD) settings, the cultural context of most psychological research [@henrich_weirdest_2010].
+Our fourth objective was to assess how robust the available evidence was to publication bias.
+Together, these objectives provided a comprehensive answer to the question whether intergroup contact diminishes support for social change in disadvantaged groups.
+
+In addition, we explored the evidence for two alternative accounts of this relationship.
+First, we considered studies that measured both ingroup and outgroup contact as predictors of the three outcomes.
+@sengupta_ingroup_2015 argued that contact with other members of the disadvantaged ingroup would increase political mobilization in disadvantaged groups.
+As outgroup contact places limits on how much ingroup contact disadvantaged-group members can have [@pfister_contact_2020], the mobilizing effect of ingroup contact is an alternative explanation for negative associations between outgroup contact and support for social change.
+
+Second, we considered studies that measured both negative and positive (outgroup) contact as predictors of the three outcomes.
+Researchers [@hayward_how_2018; @reimer_intergroup_2017] found negative contact with advantaged-group members to be associated with greater perceived discrimination and stronger collective action intentions.
+@reimer_intergroup_2017 argued that, to the extent disadvantaged-group members who have more positive contact also tend to have less negative contact, the mobilizing effect of negative contact is an alternative explanation for negative associations between outgroup contact and support for social change.
+For both alternative explanations, we collate and synthesize the available evidence for the relative effects of each predictor variable on the three outcomes.
+
+# Method
+
+## Transparency
+
+We prepared a protocol in accordance with the PRISMA-P statement [@moher_preferred_2015] and preregistered it on the Open Science Framework.^[[https://osf.io/ryuev/?view_only=8938ac6178914da98bdda1da4a6e27f0](https://osf.io/ryuev/?view_only=8938ac6178914da98bdda1da4a6e27f0)] Preregistration precludes undisclosed flexibility in study selection, outcome selection, and other decisions that influence effect size estimates—and thus prevents confirmation bias from determining the conclusions of a meta-analysis [@lakens_reproducibility_2016].
+We report all deviations from our protocol in the Supplemental Materials.
+We make all data and analysis scripts available online.^[[https://osf.io/w5tqv/?view_only=5cbf7ad5b2b449a7a0f4ada0337b802a](https://osf.io/w5tqv/?view_only=5cbf7ad5b2b449a7a0f4ada0337b802a)]
+
+## Eligibility Criteria
+
+As preregistered, we considered all quantitative studies that included participants of a relatively disadvantaged group (see *Types of Participants*), that manipulated or measured intergroup contact with a relatively advantaged group (see *Types of Predictor Variables*), and that measured one or more of the following outcomes: perceptions or expectations of injustice, collective action intentions and behaviours, and/or support for policies that benefit or harm the participants’ ingroup (see *Types of Outcome Variables*).
+
+### Types of Participants
+
+We included studies with participants whose ingroup is disadvantaged (in terms of status, power, or resources) relative to the outgroup they have (or report to have) contact with.
+
+### Types of Predictor Variables
+
+We included studies if they measured or manipulated the quantity of, quality of, and opportunity for contact with members of outgroups that are relatively advantaged compared to the participants’ ingroup.
+We considered opportunity for contact, as it is a potential precursor to and proxy for face-to-face contact, but not imagined or indirect contact.
+Similarly, we included studies that measured intergroup contact indirectly by, for example, asking what proportion of someone’s friends were *not* from the participants’ ingroup.
+
+### Types of Outcome Variables
+
+***Perceived Injustice.*** We included studies that measured perceptions that one is discriminated against because of one’s group membership, that one’s group faces discrimination in society, that one’s group is relatively deprived compared to other groups, or that the deprivation and/or discrimination faced by one’s group is unjust and illegitimate.
+We also considered expectations of fair treatment as the reverse of perceived injustice.
+We included studies that measured personal and/or group discrimination or a mixture of both.
+
+***Collective Action.*** We included studies that measured observed, reported, or intended engagement in any action aimed at improving the position of the participants’ ingroup in society.
+This included participating in protests, signing petitions, and any other form of violent or nonviolent collective action.
+
+***Policy Support.*** We included studies that measured support for (or opposition to) policies and initiatives designed to improve the position of the participants’ ingroup in society, for example, affirmative action policies.
+
+## Search Strategy
 
@@
 ```
+
+As preregistered, we searched titles, abstract, and keywords for relevant terms in four electronic databases.
+We searched for relevant articles in the *Scopus* and *PsycINFO* databases.
+We searched for gray literature in the *ProQuest Dissertations and Theses* database.
+We used similar non-exclusive search terms for all databases (see Supplemental Materials).
+We searched databases on April 1, 2019 and again on April 1, 2020.
+We exported records and relevant metadata from each database.
+We removed duplicates using the *revtools* package [@westgate_revtools:_2019].
+
+To find unpublished studies, we sent a call to the mailing lists of several professional organizations (see Supplemental Materials).
+We also advertised on social media and at relevant conferences.
+We directed researchers to an online survey in which they answered questions about the eligibility of their unpublished research and, if the research was eligible, provided data on moderator variables and effect sizes.
+We also contacted experts in the field, asking for unpublished research and other studies we might have missed.
+
+In addition, we used the *Scopus* citation database to find records that cited at least one of the published articles included in the meta-analysis or at least one of three relevant review articles [@dixon_beyond_2012; @reicher_rethinking_2007; @wright_struggle_2009].
+This search resulted in 2,075 records.
+Of these, we focused on 145 records that cited at least three eligible studies or relevant reviews and looked for eligible studies that were not among those from our original search.
+
+## Study Selection
+
+As preregistered, we selected studies in three stages.
+First, we screened records based on their title, abstract, and keywords.
+We refined our coding strategy over three random samples of 100 records until we achieved acceptable inter-rater agreement ($\kappa_1 = .56$, $\kappa_2 = .60$, $\kappa_3 = .79$).
+We then divided the remaining records between the two authors.
+For each record, one of the authors coded whether the record met the eligibility criteria (yes, maybe, no), or whether it was a relevant review article.
+We kept all records coded as “yes” or “maybe”.
+Second, both authors reviewed each of the full-text manuscripts from the previous stage and coded whether any study or sample in the manuscript fulfilled the preregistered eligibility criteria ($\kappa = .75$).
+Third, we resolved any disagreements (by consensus) and excluded ineligible records.
+
+## Data Collection
+
+### Effect Sizes
+
+From all eligible records, we extracted correlation coefficients ($r$) as the relevant measure of effect size and extracted sample sizes ($n$) to calculate standard errors for each sample’s correlation coefficients.
+When provided, we copied correlation coefficients from the text or tables.
+When other effect-size measures were provided, we converted them to correlation coefficients using common conversion formulas [@borenstein_introduction_2009].
+When effect sizes were not provided, we attempted to contact the authors to obtain the relevant effect sizes.
+We did not contact authors for studies that were more than twenty years old as we considered it unlikely that authors still had access to the underlying data.
+When we could not extract or obtain an effect size for a study or sample, we either imputed missing correlation coefficients from standardized beta coefficients [@peterson_use_2005] if reported or excluded the study or sample if not.
+
+### Outcomes Selection
+
+We collected effect sizes for all relationships between eligible predictor and outcome variables.
+When more than one eligible measure was reported, we extracted effect sizes for all of them.
+As preregistered, we also extracted effect sizes for negative contact, ingroup contact, group identification, and outgroup attitudes.
+
+When a study reported effect sizes for more than one measure of intergroup contact, we prioritized the predictor variable in the preregistered analyses that measured the most intense or intimate form of contact.
+As preregistered, we used the following ranking: cross-group friendship > quality of contact/positive contact > quantity of contact > opportunity for contact.
+When it was unclear which of several predictor variables measured the most intense form of contact, we combined and averaged effect sizes.
+
+When a study reported effect sizes for more than one measure of one of the three outcome variables, we selected effect sizes for the preregistered analyses as follows: For perceived injustice, we prioritized the measure closest to perceptions of injustice against the participants’ ingroup (rather than against the participants themselves); when it was ambiguous which measure that was, we combined and averaged effect sizes across outcome measures.
+For collective action, we prioritized the measure that was the primary focus of the reported analyses; otherwise, we combined and averaged effects sizes across outcome measures.
+For policy support, we combined and averaged effect sizes for all policies designed to improve the position of the participants’ ingroup in society.
+
+Some study designs resulted in more than one effect size for the same measure: When a longitudinal study reported results from more than two waves, we prioritized effect sizes spanning the inter-survey interval closest to one year.
+If a longitudinal study reported results from more than two waves and spanned multiple years, we combined and averaged effect sizes from each one-year inter-survey interval.
+In the preregistered analyses, we included the cross-lagged partial correlation between the relevant predictor variable (at time 1) and outcome variable (at time 2) controlling for initial levels of the outcome variable (at time 1).
+When an experimental or quasi-experimental study reported comparisons between more than two conditions, we prioritized the effect size that compared two conditions that most closely resembled generic contact and no-contact conditions.
+
+### Potential Moderators
 
@@
 
-## Preregistered analyses
+In addition to extracting and selecting effect sizes for the preregistered analyses, we collected data on a broad range of potential moderators.
+All moderators that required subjective assessments were coded by both authors.
+We calculated inter-rater agreement (Cohen’s $\kappa$) and resolved all disagreements by consensus.
+
+***Study Setting.*** For each sample, we recorded in what country (or countries) the data was collected ($\kappa = .97$) and what the disadvantaged ingroup and the advantaged outgroup were.
+We categorized each sample’s setting according to whether the source of the groups’ relative inequality was long-term migration (e.g., Asian Americans), short-term  migration (e.g., international students), slavery (e.g., Black Americans), colonization (e.g., Māori, Black South Africans), religion, caste, sexuality, or another distinction ($\kappa = .84$).
+
+***Study Design.*** We categorized each study as either observational and cross-sectional, observational and longitudinal, quasi-experimental, experimental, an intervention, or other ($\kappa = .85$).
+We categorized each sample as either a student convenience sample, a non-student convenience sample, a probability or representative sample, or another kind of sample ($\kappa = .73$).
+We categorized the age group(s) in each sample as children ($\leq 12$ years), adolescents (13–18 years), or adults ($\geq 18$ years; $\kappa = .64$).
+
+***Study Intention.*** We coded whether or not each study was conducted with the intention to examine the effects of intergroup contact on one or more of the three outcome measures ($\kappa = .48$).
+
+***Publication status.*** For each study, we coded whether it was published, unpublished, or an unpublished dissertation based on the information source from which we obtained it.
+
+***Predictor Variables.*** For each measure of intergroup contact, we coded whether it assessed contact with the specific advantaged outgroup of interest directly—or whether it assessed contact indirectly by, for example, asking what proportion of someone’s friends were not from the participants’ ingroup or what proportion of residents in someone’s neighbourhood were from the relevant outgroup ($\kappa = .82$).
+
+***Outcome Variables.*** For each measure of perceived injustice, we coded whether it refered to specific instances of discrimination, to a more general perception of discrimination, or to both ($\kappa = .67$) and whether it assessed personal discrimination, group discrimination, or both ($\kappa = .83$).
+
+***Cultural Distance.*** We also used the measure developed by @muthukrishna_beyond_2020, when available, to quantify each country’s cultural distance from the United States, which represents the cultural context of most psychological research [@henrich_weirdest_2010].
+
+## Analysis Strategy
+
+### Preregistered Analyses
+
+We transformed correlation coefficients to Fisher’s $z$ which is unbounded and has a normal sampling distribution: \begin{align*} 
+z & = \frac{1}{2} \ln\left(\frac{1 + r}{1 - r}\right) \\ \sigma & = \frac{1}{\sqrt{n - 3}} \end{align*} where $r$ is the sample correlation coefficient, $z$ is the transformed effect size, $n$ is the sample size, and $\sigma$ is the standard error of the transformed effect size.
+
+We estimated effect sizes using Bayesian random-effects meta-analysis models in *RStan* [@stan_development_team_rstan:_2020] which modeled the *z*-transformed correlation coefficients with a normal likelihood function: \begin{align*} z_{ij} &\sim \text{Normal}(\theta_{ij}, \sigma_{ij}) \\ \theta_{ij} &= \begin{cases} \mu + \beta_j\tau_J & \text{if } I_j = 1 \\ \mu + \beta_j\tau_J + \beta_i\tau_I & \text{if } I_j > 1 \end{cases} \\ \end{align*} where $z_{ij}$ is the observed effect size in sample $i$ of study $j$, $\sigma_{ij}$ is the sample standard error, and $\theta_{ij}$ is the estimated effect size.
+We estimated $z_{ij}$ as a function of the mean effect size $\mu$ and of two varying (random) intercepts, $\beta_i$ and $\beta_j$, with the corresponding standard deviations, $\tau_I$ and $\tau_J$.
+We used the non-centered parameterization to model the random effects.
+For studies that contained only one sample ($I_j = 1$), we only included $\beta_j\tau_J$, the study-wise deviation from the mean effect size $\mu$.
+For studies that contained more than one sample ($I_j > 1$), we also estimated $\beta_i\tau_I$, the sample-wise deviation from the study-specific effect size.
+
+Models assigned weakly informative prior distributions to all parameters.
+The prior distribution for the mean effect size, $\mu \sim \text{Normal}(0, 0.31605)$, was centered around 0 and concentrated 50% of the most plausible values between $r = -.21$ and $r = .21$.
+We focus on $|r| = .21$ because it corresponds to the mean effect size observed in both Pettigrew and Tropp’s [-@pettigrew_meta-analytic_2006] meta-analysis of the contact literature and Richard et al.’s [-@richard_one_2003] meta-analysis of effect sizes across a century of social-psychological research.
+The prior distribution for the standard deviation of random effects, $\tau \sim \text{Half-Cauchy}(0, 0.3)$, allocated 30% of plausible values below $\tau = 0.15$ and had a wide tail.
+We focus on $\tau = 0.15$ because it corresponds to the standard deviations observed in both Pettigrew and Tropp’s [-@pettigrew_meta-analytic_2006] and Richard et al.’s [-@richard_one_2003] meta-analyses.
+We chose this prior distribution in line with recommendations by Williams et al.
+(2018).
+
+Bayesian inference involves choosing a likelihood function and prior distributions.
+A likelihood function links the observed data to one or more model parameters and states how likely the observed data are given different values of said model parameters.
+Prior distributions state how plausible different values of said model parameters are before considering the observed data.
+Bayesian inference applies Bayes’ theorem to update prior distributions in light of the observed data to produce posterior distributions.
+Other than *p*-values and confidence intervals, the resulting posterior distributions have a straightforward interpretation as stating how plausible different values of the model parameters are given the observed data.
+We report point estimates, based on the median of posterior samples, and uncertainty intervals, based on the quantiles of posterior samples, that enclose the 95% most plausible estimates.
+In addition, we report the posterior probability, based on the proportion of posterior samples below zero, that an estimated mean effect size is negative.
+
+### Other Analyses
+
+We also conducted non-preregistered analyses to estimate to what extent moderator variables explained heterogeneity in the estimated effect sizes, to what extent meta-biases influenced the estimated effect sizes, and to what extent the three outcome variables were associated with two alternative predictor variables, ingroup contact and negative contact.
+
+# Results
+
+## Search Results
+
+Figure 1 shows a flow diagram illustrating our search strategy, study selection, and data collection.
+Our preregistered search strategy returned 2,610 unique records from electronic databases.
+Of these, we excluded 2,379 (91\%) ineligible records after screening titles, abstracts, and keywords.
+Of the remaining 231 records, we excluded 116 (50\%) ineligible records after reviewing full-text manuscripts.
+We supplemented these records with 14 unpublished studies solicited from researchers and 6 records that cited at least three relevant works.
+Of 135 eligible studies, we had to exclude 39 (29\%) studies for which we could not extract or impute any relevant effect size.
+At each stage, we also excluded studies that used the same data as another study.
+Our final sample comprised effect sizes from $J = 96$  studies spanning $N = 211,360$ participants in $I = 137$ samples.
+
+Figure 2 provides a qualitative overview of the literature.
+Even though most participants came from studies conducted in India ($N = 104,639$) and the United States ($N = 61,089$; Figure 2a), most samples were collected in North America ($I = 48$) and Europe ($I = 40$), with few samples from South America and Africa (Figure 2b).
+Most samples focused on relative inequalities that resulted from long-term migration ($I = 54$), slavery ($I = 19$), colonization ($I = 17$), and short-term migration ($I = 14$).
+With few exceptions, studies used observational, cross-sectional survey designs.
+Samples sizes ranged from 64 to 49,764 ($\textit{Mdn} = 282$).
+Unlike most psychological research, 2 in 5 samples used probability or representative sampling.
+Of all samples, 55\% ($I = 75$) were collected with the intention to examine the effects of intergroup contact on the outcomes considered in this meta-analysis.^[Many studies examined acculturation processes (Berry, 1997) and measured both intergroup contact and perceived injustice without the relationship between the two being of interest.] Together, these observations highlight both limitations and strengths of the empirical literature.
+
+## Preregistered Analyses
 
@@
 ```{=latex}
-\begin{figure*}
+\begin{figure*}[!t]
 \centering
@@
 \includegraphics[scale=1]{../figures/figure-3}
-\caption*{\textit{Note.} \textbf{A} Posterior distributions for the estimated mean correlation coefficients, highlighting the proportion of posterior samples for which $r_\text{mean} < 0$.
-\textbf{B} Posterior predictive distributions for the estimated study-wise correlation coefficients, based on point estimates of the $\mu$ and $\tau_J$ parameters, with point estimates for the estimated correlation coefficients for all studies in the sample.}
+\caption*{\textit{Note.} \textbf{A} Posterior distributions for the mean correlation coefficients, highlighting the proportion of posterior samples for which $r_\text{mean} < 0$.
+\textbf{B} Posterior predictive distributions of study-wise correlation coefficients, highlighting the 80\% most common effect sizes, with point estimates for the correlation coefficients for all studies in the sample.}
 \label{fig:f3}
@@
 
-*Perceived injustice.* Across `r unique(pi_results$N)` participants from `r unique(pi_results$I)` samples in `r unique(pi_results$J)` studies, we found strong evidence for a weak association (`r pi_results$text[pi_results$parameter == "r_mean"]`) between intergroup contact and perceived injustice, with `r pi_results$p_below[pi_results$parameter == "r_mean"]` of posterior samples for the mean correlation coefficient falling below zero.
+***Perceived Injustice.*** Across `r unique(pi_results$N)` participants from `r unique(pi_results$I)` samples in `r unique(pi_results$J)` studies, we found strong evidence for a weak association (`r pi_results$text[pi_results$parameter == "r_mean"]`) between intergroup contact and perceived injustice, with `r pi_results$p_below[pi_results$parameter == "r_mean"]` of posterior samples for the mean correlation coefficient falling below zero.
 We found evidence that correlation coefficients varied across studies (`r pi_results$text[pi_results$parameter == "tau_jj"]`) and across samples within studies  (`r pi_results$text[pi_results$parameter == "tau_ii"]`).
@@
 
-*Collective action.* Across `r unique(ca_results$N)` participants from `r unique(ca_results$I)` samples in `r unique(ca_results$J)` studies, we found some evidence for a weak association (`r ca_results$text[ca_results$parameter == "r_mean"]`) between intergroup contact and collective action, with `r ca_results$p_below[ca_results$parameter == "r_mean"]` of posterior samples for the mean correlation coefficient falling below zero.
+***Collective Action.*** Across `r unique(ca_results$N)` participants from `r unique(ca_results$I)` samples in `r unique(ca_results$J)` studies, we found some evidence for a weak association (`r ca_results$text[ca_results$parameter == "r_mean"]`) between intergroup contact and collective action, with `r ca_results$p_below[ca_results$parameter == "r_mean"]` of posterior samples for the mean correlation coefficient falling below zero.
 We found evidence that correlation coefficients varied across studies (`r ca_results$text[ca_results$parameter == "tau_jj"]`) and across samples within studies  (`r ca_results$text[ca_results$parameter == "tau_ii"]`).
@@
 
-*Policy support.* Across `r unique(ps_results$N)` participants from `r unique(ps_results$I)` samples in `r unique(ps_results$J)` studies, we found some evidence for a weak association (`r ps_results$text[ps_results$parameter == "r_mean"]`) between intergroup contact and policy support, with `r ps_results$p_below[ps_results$parameter == "r_mean"]` of posterior samples for the mean correlation coefficient falling below zero.
+***Policy Support.*** Across `r unique(ps_results$N)` participants from `r unique(ps_results$I)` samples in `r unique(ps_results$J)` studies, we found evidence for a weak association (`r ps_results$text[ps_results$parameter == "r_mean"]`) between intergroup contact and policy support, with `r ps_results$p_below[ps_results$parameter == "r_mean"]` of posterior samples for the mean correlation coefficient falling below zero.
 We found evidence that correlation coefficients varied across studies (`r ps_results$text[ps_results$parameter == "tau_jj"]`) and, to a lesser extent, across samples within studies  (`r ps_results$text[ps_results$parameter == "tau_ii"]`).
-Based on these analyses, we predicted that 80\% of studies would result in correlation coefficients between `r post_pred$r_pred_l80[post_pred$y_var == "ps"]` and `r post_pred$r_pred_u80[post_pred$y_var == "ps"]` and that researchers would need sample sizes of at least `r post_pred$n_req[post_pred$y_var == "ps1"]` participants to find significant associations ($\alpha = .05$, two-sided) in 80\% of their studies.
+Based on these analyses, we predicted that 80\% of studies would result in correlation coefficients between `r post_pred$r_pred_l80[post_pred$y_var == "ps"]` and `r post_pred$r_pred_u80[post_pred$y_var == "ps"]` and that researchers would need sample sizes of at least `r post_pred$n_req[post_pred$y_var == "ps"]` participants to find significant associations ($\alpha = .05$, two-sided) in 80\% of their studies.
 
@@
 
-### Robustness checks
+In addition, we ran preregistered robustness checks which showed that our main analyses were robust to choosing different prior distributions and to excluding influential studies (see Supplemental Materials).
+
+## Moderator Analyses
+
+We conducted two kinds of moderator analyses.
+For both analyses, we had an insufficient number of effect sizes to examine moderators for any outcomes except perceived injustice (for details, see Supplemental Materials).
+
+```{=latex}
+\begin{figure*}
+\centering
+\caption{Estimated effect sizes for the association between intergroup contact and perceived injustice as a function of various categorical moderator variables}
+\includegraphics[scale=1]{../figures/figure-4}
+\caption*{\textit{Note.} Intervals enclose the 95\% most plausible estimates of the category-specific effect size.
+Shaded ribbons enclose the 95\% most plausible estimates of the mean effect size from the main analyses.
+Percentages indicate the estimated between-sample variance explained by each moderator variable.}
+\label{fig:f4}
+\end{figure*}
+```
 
@@
 
-  # Summarize prior choice results
-  d_priors <- read_rds("../results/results_robustness_checks_priors.rds") %>% 
-    group_by(y_var, prior) %>% 
-    median_qi(d_r_mean) %>% 
+  # Load results
+  weird_results <- read_rds("../results/results_cultural_distance.rds")
+
+  # Summarize results
+  weird_results <- weird_results %>% 
+    group_by(y_var) %>% 
+    distinct(.chain, .iteration, .draw, b_x) %>% 
+    summarize(
+      median = median(b_x),
+      .lower = quantile(b_x, 0.025),
+      .upper = quantile(b_x, 0.975),
+      p = mean(b_x < 0)
+    ) %>% 
     mutate(
-      across(c(d_r_mean, .lower, .upper), ~f_num(., digits = 2)),
-      text = paste0("$\\Delta r = ", d_r_mean, ", [", .lower, ", ", .upper, "]$")
+      across(
+        c(.lower, .upper), 
+        ~f_pad_zero(f_num(., digits = 2))
+      ),
+      median = str_replace(f_num(median, digits = 2), "-.", "-0."),
+      p_text = case_when(
+        p < .001 ~ "$\\Pr (\\beta < 0) < 0.1\\%$",
+        p > .999 ~ "$\\Pr (\\beta < 0) > 99.9\\%$",
+        TRUE ~ paste0("$\\Pr (\\beta < 0) = ", f_num(p * 100, digits = 1), "\\%$")
+      ),
+      r_text = paste0("$\\beta = ", median, ", [", .lower, ", ", .upper, "]$"),
+      text = paste(r_text, p_text, sep = "; ")
     )
@@
 
+```{=latex}
+\begin{figure*}
+\centering
+\caption{Estimated effect size as a function of cultural distance from the United States, with point estimates and uncertainty intervals for each country}
+\includegraphics[scale=1]{../figures/figure-5}
+\caption*{\textit{Note.} We had data from too few countries to reach firm conclusions about the direction of these associations for perceived injustice (`r with(weird_results, text[y_var == "pi"])`), collective action (`r with(weird_results, text[y_var == "ca"])`), and policy support (`r with(weird_results, text[y_var == "ps"])`).}
+\label{fig:f5}
+\end{figure*}
+
+\begin{figure*}
+\centering
+\caption{Results from the random-effects meta-regression tree analysis}
+\includegraphics[scale=1]{../figures/figure-6}
+\caption*{\textit{Note.} Posterior distributions for the estimated correlation coefficient in each leaf of the meta-regression tree, highlighting the proportion of posterior samples for which $r_\text{mean} < 0$.
+S.-T.
+Migration = Short-Term Migration.}
+\label{fig:f6}
+\end{figure*}
+```
+
+First, we used meta-regression models to examine specific moderator variables which we expected to explain heterogeneity in effect sizes across samples.
+Figure 4 shows results for categorical moderator variables.
+We found that the setting of the study ($R^2 = 20\%$), participants’ age group ($R^2 = 12\%$), and whether intergroup contact was measured directly or indirectly ($R^2 = 10\%$) explained the most variance across effect sizes.
+Figure 5 shows results from country-level analyses examining cultural context as a moderator variable.
+We found that cultural distance from the United States tended to be associated with larger effect sizes—although we had data from too few countries to reach any firm conclusions.
+
+Second, we used meta-regression trees to discover interactions between moderator variables that best explained heterogeneity in effect sizes [@li_multiple_2020].
+Figure 6 shows the resulting meta-regression that explained more variance across samples than any individual moderator ($R^2 = 31\%$).
+We found that intergroup contact was associated with less perceived injustice only in studies that focused on adults and that measured intergroup contact directly.
+Among these studies, this association was stronger in settings in which the groups’ relative inequality stemmed from short-term migration or colonization ($r = -.18, [-.23, -.13]$) than in other settings ($r = -.09, [-.12, -.06]$).
+
+## Meta Bias
+
+```{=latex}
+\begin{figure*}
+\centering
+\caption{Unadjusted ($\bullet$) and adjusted ($\circ$) point estimates with confidence intervals from the random-effects meta-analysis (RMA), the PET-PEESE estimator, the three-parameter selection model (3PSM), the \textit{p}-uniform* estimator, and the subgroup analysis}
+\includegraphics[scale=1]{../figures/figure-7}
+\label{fig:f7}
+\end{figure*}
+```
+
+Developing methods to detect and correct for publication bias and other meta-biases is an active area of research, with no single method outperforming all others [@carter_correcting_2019].
+Following Carter et al.’s recommendations, we compared results of several methods to adjust meta-analytic estimates for publication bias: the PET-PEESE estimator [@stanley_meta-regression_2014]; the three-parameter selection model [3PSM; @vevea_general_1995]; and the *p*-uniform* estimator [@van_aert_correcting_2018].
+As these methods do not use Bayesian statistics, we compared adjusted estimates from these methods to unadjusted estimates from a random-effects meta-analysis estimated with restricted maximum likelihood estimation using the *metafor* package [@viechtbauer_conducting_2010].
+In addition, we ran a meta-regression model that compared studies that were published *and* were conducted with the intention to examine the effects of intergroup contact on any of the outcomes to all other studies.
+We report estimates from the latter subgroup of studies as we can assume that effect sizes in this subgroup were not affected by publication bias.
+
+Figure 7 shows adjusted and unadjusted estimates with confidence intervals for the three outcomes.
+Comparing adjusted and unadjusted estimates shows that the PET-PEESE and 3PSM methods tended to estimate the mean correlation coefficients to be closer to zero than the unadjusted estimate, with all confidence intervals including zero.
+The *p*-uniform* method and the subgroup analysis tended to estimate the mean correlations coefficients to be closer to the unadjusted estimates, with the confidence interval for perceived injustice—but not for the other outcomes—excluding zero.
+All methods, however, resulted in confidence intervals that largely overlapped with, but were wider than, the confidence intervals around the unadjusted estimates.
+This reflects the reduced power of the various methods to correct for meta-biases when sample sizes are small, effect sizes are heterogeneous, or publication bias is strong [@carter_correcting_2019].
+Therefore, there was insufficient evidence to conclude *either* that, after adjusting for publication bias, intergroup contact was not associated with support of social change in disadvantaged groups *or* that publication bias did not affect the relevant literature.
+
+## Alternative Predictors
+
 ```{r, include = FALSE}
 
-  # Calculate Mean Absolute Deviation (MAD)
-  mad_loo <- read_rds("../results/results_robustness_checks_loo.rds") %>% 
-    group_by(.draw, y_var) %>% 
-    summarize(mad_loo = mean(ae_loo)) %>% 
-    group_by(y_var) %>% 
-    median_qi(mad_loo) %>% 
+  # Summarize results
+  alt_results <- bind_rows(
+      read_rds("../results/results_analyses_with_negative_contact.rds"),
+      read_rds("../results/results_analyses_with_ingroup_contact.rds") 
+    ) %>% 
+    group_by(x_var, y_var) %>% 
+    summarize(
+      I = f_comma(unique(I)),
+      J = f_comma(unique(J)),
+      N = f_comma(unique(N)),
+      median = median(r_mean),
+      .lower = quantile(r_mean, 0.025),
+      .upper = quantile(r_mean, 0.975),
+      p_below = mean(r_mean < 0),
+      p_above = mean(r_mean > 0)
+    ) %>% 
+    ungroup() %>% 
     mutate(
-      across(c(mad_loo, .lower, .upper), ~f_num(., digits = 2)),
-      text = paste0("$\\textit{MAD} = ", mad_loo, ", [", .lower, ", ", .upper, "]$")
+      across(
+        c(median, .lower, .upper), 
+        ~f_num(., digits = 2)
+      ),
+      p_below = case_when(
+        p_below < .001 ~ "$\\Pr (r < 0) < 0.1\\%$",
+        p_below > .999 ~ "$\\Pr (r < 0) > 99.9\\%$",
+        TRUE ~ paste0("$\\Pr (r < 0) = ", f_num(p_below * 100, digits = 1), "\\%$")
+      ),
+      p_above = case_when(
+        p_above < .001 ~ "$\\Pr (r > 0) < 0.1\\%$",
+        p_above > .999 ~ "$\\Pr (r > 0) > 99.9\\%$",
+        TRUE ~ paste0("$\\Pr (r > 0) = ", f_num(p_above * 100, digits = 1), "\\%$")
+      ),
+      p_text = case_when(
+        x_var %in% c("nc", "ig") ~ p_above,
+        x_var %in% c("pc", "og") ~ p_below
+      ),
+      r_text = paste0("$r = ", median, ", [", .lower, ", ", .upper, "]$"),
+      text = paste(r_text, p_text, sep = "; ")
+    ) %>% 
+    select(-median, -.lower, -.upper)
+
+```
+
+```{=latex}
+\begin{figure*}
+\centering
+\caption{Posterior distributions from the random-effect meta-analysis models with alternative predictor variables}
+\includegraphics[scale=1]{../figures/figure-8}
+\label{fig:f8}
+\end{figure*}
+```
+
+We ran three random-effects meta-analysis models estimating the partial correlations of positive and negative contact with each outcome, using effect sizes from all studies that measured both predictors (Figure 8a).
+By using partial correlations, we estimated the effect of one form of contact while controlling for the other.
+Across `r alt_results$N[alt_results$x_var == "nc" & alt_results$y_var == "pi"]` participants from `r alt_results$I[alt_results$x_var == "nc" & alt_results$y_var == "pi"]` samples in `r alt_results$J[alt_results$x_var == "nc" & alt_results$y_var == "pi"]` studies, we found stronger evidence for a positive association between negative contact and perceived injustice (`r alt_results$text[alt_results$x_var == "nc" & alt_results$y_var == "pi"]`) than for a negative association between positive contact and perceived injustice (`r alt_results$text[alt_results$x_var == "pc" & alt_results$y_var == "pi"]`).
+Across `r alt_results$N[alt_results$x_var == "nc" & alt_results$y_var == "ca"]` participants from `r alt_results$I[alt_results$x_var == "nc" & alt_results$y_var == "ca"]` samples in `r alt_results$J[alt_results$x_var == "nc" & alt_results$y_var == "ca"]` studies, we again found stronger evidence for a positive association between negative contact and collective action (`r alt_results$text[alt_results$x_var == "nc" & alt_results$y_var == "ca"]`) than for a negative association between positive contact and collective action (`r alt_results$text[alt_results$x_var == "pc" & alt_results$y_var == "ca"]`).
+Across `r alt_results$N[alt_results$x_var == "nc" & alt_results$y_var == "ps"]` participants from `r alt_results$I[alt_results$x_var == "nc" & alt_results$y_var == "ps"]` samples in `r alt_results$J[alt_results$x_var == "nc" & alt_results$y_var == "ps"]` studies, we also found stronger evidence for a positive association between negative contact and policy support (`r alt_results$text[alt_results$x_var == "nc" & alt_results$y_var == "ps"]`) than for a negative association between positive contact and policy support (`r alt_results$text[alt_results$x_var == "pc" & alt_results$y_var == "ps"]`).
+Across `r alt_results$N[alt_results$x_var == "pc" & alt_results$y_var == "nc"]` participants from `r alt_results$I[alt_results$x_var == "pc" & alt_results$y_var == "nc"]` samples in `r alt_results$J[alt_results$x_var == "pc" & alt_results$y_var == "nc"]` studies, we found a negative association between positive and negative contact (`r alt_results$text[alt_results$x_var == "pc" & alt_results$y_var == "nc"]`).
+
+We ran three random-effects meta-analysis models that estimated the partial correlations of ingroup and outgroup contact with each outcomes, using effect sizes from all studies that measured both predictors (Figure 8b).
+Across `r alt_results$N[alt_results$x_var == "ig" & alt_results$y_var == "pi"]` participants from `r alt_results$I[alt_results$x_var == "ig" & alt_results$y_var == "pi"]` samples in `r alt_results$J[alt_results$x_var == "ig" & alt_results$y_var == "pi"]` studies, we found insufficient evidence for associations of ingroup contact (`r alt_results$text[alt_results$x_var == "ig" & alt_results$y_var == "pi"]`) and outgroup contact (`r alt_results$text[alt_results$x_var == "og" & alt_results$y_var == "pi"]`) with perceived injustice.
+Across `r alt_results$N[alt_results$x_var == "ig" & alt_results$y_var == "ca"]` participants from `r alt_results$I[alt_results$x_var == "ig" & alt_results$y_var == "ca"]` samples in `r alt_results$J[alt_results$x_var == "ig" & alt_results$y_var == "ca"]` studies, we found stronger evidence for a positive association between ingroup contact and collective action (`r alt_results$text[alt_results$x_var == "ig" & alt_results$y_var == "ca"]`) than for a negative association between outgroup contact and collective action (`r alt_results$text[alt_results$x_var == "og" & alt_results$y_var == "ca"]`).
+Across `r alt_results$N[alt_results$x_var == "ig" & alt_results$y_var == "ps"]` participants from `r alt_results$I[alt_results$x_var == "ig" & alt_results$y_var == "ps"]` samples in `r alt_results$J[alt_results$x_var == "ig" & alt_results$y_var == "ps"]` study, we found insufficient evidence for associations of ingroup contact (`r alt_results$text[alt_results$x_var == "ig" & alt_results$y_var == "ps"]`) and outgroup contact (`r alt_results$text[alt_results$x_var == "og" & alt_results$y_var == "ps"]`) with policy support.
+Across `r alt_results$N[alt_results$x_var == "ig" & alt_results$y_var == "og"]` participants from `r alt_results$I[alt_results$x_var == "ig" & alt_results$y_var == "og"]` samples in `r alt_results$J[alt_results$x_var == "ig" & alt_results$y_var == "og"]` studies, we found a positive association between ingroup and outgroup contact (`r alt_results$text[alt_results$x_var == "ig" & alt_results$y_var == "og"]`).
+
+# Discussion
+
+```{r, include = FALSE}
+
+  # Set seed (for posterior predictive simulations)
+  set.seed(9071118)
+
+  # Summarize results
+  summary <- read_rds("../results/results_preregistered_analyses.rds") %>% 
+    filter(x_var == "ic", y_var %in% c("pi", "ca", "ps")) %>% 
+    mutate(
+      r_pred = z_to_r(rnorm(n = n(), mean = mu, sd = tau_jj))
+    ) %>% 
+    group_by(x_var, y_var) %>% 
+    summarize(
+      r = median(r_mean),
+      p = mean(r_mean < 0),
+      r_lower = quantile(r_mean, 0.025),
+      r_upper = quantile(r_mean, 0.975),
+      p_pred_positive = mean(r_pred > 0)
+    ) %>% 
+    ungroup() %>% 
+    mutate(
+      r_text = paste0("$r = ", f_num(r, digits = 2), "$"),
+      p_text = case_when(
+        p < .001 ~ "$\\Pr (r < 0) < 0.1\\%$",
+        p > .999 ~ "$\\Pr (r < 0) > 99.9\\%$",
+        TRUE ~ paste0("$\\Pr (r < 0) = ", f_num(p * 100, digits = 1), "\\%$")
       )
-
-  # Leave out most influential studies
-  d_loo <- read_rds("../results/results_robustness_checks_loo.rds") %>% 
-    group_by(y_var, id) %>%
-    median_qi(e_loo) %>% 
-    top_n(n = 1, wt = abs(e_loo)) %>% 
-    mutate(
-      across(c(e_loo, .lower, .upper), ~f_num(., digits = 2)),
-      text = paste0("$\\Delta r = ", e_loo, ", [", .lower, ", ", .upper, "]$")
     )
@@
 
-First, we assessed to what extent our findings were sensitive to choosing narrower, $\mu \sim \text{Normal}(0, 0.1)$, or wider, $\mu \sim \text{Normal}(0, 1)$, prior distributions.
-Choosing narrower or wider prior distribution did not affect mean effect size estimates for perceived injustice (`r d_priors$text[d_priors$y_var == "pi" & d_priors$prior == "N(0, 0.1)"]` and `r d_priors$text[d_priors$y_var == "pi" & d_priors$prior == "N(0, 1.0)"]`), collective action (`r d_priors$text[d_priors$y_var == "ca" & d_priors$prior == "N(0, 0.1)"]` and `r d_priors$text[d_priors$y_var == "ca" & d_priors$prior == "N(0, 1.0)"]`), and policy support (`r d_priors$text[d_priors$y_var == "ps" & d_priors$prior == "N(0, 0.1)"]` and `r d_priors$text[d_priors$y_var == "ps" & d_priors$prior == "N(0, 1.0)"]`).
-Second, we assessed to what extent our findings were sensitive to including or excluding influential studies by repeating the preregistered analyses $J$ times while leaving out one of $J$ studies each time and by calculating the mean absolute difference (*MAD*) for the estimated mean effect size across left-out studies.
-For perceived injustice (`r mad_loo$text[mad_loo$y_var == "pi"]`), collective action (`r mad_loo$text[mad_loo$y_var == "ca"]`), and policy support (`r mad_loo$text[mad_loo$y_var == "ps"]`), the *MAD* was small.
-Leaving out the most influential study, for example, did not change estimates of the mean effect size for the three outcomes (`r d_loo$text[d_loo$y_var == "pi"]`; `r d_loo$text[d_loo$y_var == "ca"]`; `r d_loo$text[d_loo$y_var == "ps"]`).
-Together, these analyses showed that our findings were robust to choosing different prior distributions and to excluding influential studies.
+There is an emerging consensus that intergroup contact has the 'ironic' effect of undermining support for social change in disadvantaged groups.
+We conducted a preregistered meta-analytic test of this effect across 96 studies with 137 samples of 211,360 disadvantaged-group members.
+We found that, based on the available evidence, the associations of intergroup contact with perceived injustice (`r with(summary, p_text[y_var == "pi"])`), collective action (`r with(summary, p_text[y_var == "ca"])`), and support for reparative policies (`r with(summary, p_text[y_var == "ps"])`) were, on average, much more likely to be negative than positive.
+Thus, our meta-analysis seems to support the emerging consensus that intergroup contact diminishes support for social change in disadvantaged groups.
+We use the rest of this section to argue why this conclusion might be premature.
+
+First, the estimated effect sizes for the average associations of intergroup contact with perceived injustice (`r with(summary, r_text[y_var == "pi"])`), collective action (`r with(summary, r_text[y_var == "ca"])`), and policy support (`r with(summary, r_text[y_var == "ps"])`) were small.
+Across the three outcomes, the 95% most plausible estimates included effect sizes between `r paste0("$r = ", f_num(min(summary$r_lower), digits = 2), "$")` and `r paste0("$r = ", f_num(max(summary$r_upper), digits = 2), "$")`.
+Effect sizes were thus much smaller than for the association between contact and prejudice in minority ($r = -.18$) and majority ($r = -.23$) groups [@tropp_relationships_2005].^[Comparing standardized effect sizes assumes that the two outcomes are of equal importance.
+That is not always the case: for example, a drug that reduces mild symptoms by 0.20 standard deviations is not better than a drug that reduces deaths by 0.10 standard deviations.] Small effects can still be important if they accumulate over time or across people.
+For example, even a small change in policy attitudes could, if it affects enough people, sway a tight election.
+Cumulative effects, however, should not be assumed without an empirical or theoretical rationale [@funder_evaluating_2019]—neither of which has been provided in the published literature.
+
+Second, the estimated effect sizes varied across studies.
+For example, we estimated that `r f_prop2percent(with(summary, p_pred_positive[y_var == "pi"]), digits = 0)` of studies find a positive association between intergroup contact and perceived injustice.
+While the between-study heterogeneity is comparable to that in other meta-analyses [e.g., @pettigrew_meta-analytic_2006], it supports Pettigrew et al.'s [-@pettigrew_recent_2011] argument that, at least in some circumstances, intergroup contact renders discrimination *more* salient.
+
+A combination of moderators explained about a third of the between-study variance in the association between intergroup contact and perceived injustice.
+We found that, on average, this association was negative only in studies of adults that measured contact *directly* by asking, for example, about the number of friends from the advantaged outgroup.
+This suggests that, as hypothesized, the 'ironic' effects result from direct contact and not from mere exposure or other contextual factors.
+We also found that, on average, effect sizes were greater for studies in post-colonial settings or on short-term migration than for studies in other contexts.
+Future research should systematically investigate variance in how contact affects support for social change across settings and cultures.
+
+```{=latex}
+\begin{figure}
+\centering
+\caption{Directed acyclic graphs for plausible causal relations between intergroup contact and support for social change}
+\includegraphics[scale=1]{../figures/figure-9}
+\caption*{\textit{Note.} IC = (Positive) Intergroup Contact, SC = Support for Social Change, U = Unobserved Variable(s), NC = Negative (Integroup) Contact, IN = Ingroup Contact}
+\label{fig:f9}
+\end{figure}
+```
+
+Third, the available evidence is almost entirely from cross-sectional, observational studies and thus consistent with alternative explanations for the observed associations (Figure 9).
+Support for social change could reduce intergroup contact (B) rather than the other way around (A).
+For example, disadvantaged-group members involved in collective action might purposefully avoid forming friendships with advantaged-group members.
+Alternatively, the association between intergroup contact and support for social change could be spurious with both being caused by an unobserved confounder (C).
+For example, a disadvantaged-group member's socioeconomic status might both expose them to more advantaged-group members and reduce their perception of injustice.
+Future research should prioritize longitudinal studies to confirm the direction of the observed associations and (field) experiments to rule out confounding and other alternative explanations.^[Published research includes only three longitudinal studies [@koschate_when_2012; @reimer_intergroup_2017; @tropp_crossethnic_2012], all of which conflated within-person change and between-person stability [@hamaker_critique_2015], two experimental studies with a no-contact control condition [@becker_friend_2013; @droogendyk_renewed_2016], and two intervention studies [@reimer_building_2021; @shani_effect_2017].]
+
+Further, the observed association between intergroup contact and support for social change could be confounded by an alternative predictor that *increases* support for social change (D, E).
+Supporting Reimer et al.'s [-@reimer_intergroup_2017] argument, we found that positive intergroup contact was not associated with support for social change after controlling for negative contact which, in turn, was associated with *greater* support for social change.
+We found mixed evidence for ingroup contact as an alternative explanation for the 'ironic' effects of intergroup contact [@sengupta_ingroup_2015] but note that few studies measured both ingroup and outgroup contact.
+Going forward, researchers should clarify which aspects of intergroup contact they hypothesize to affect support for social change—and include measures that allow testing both the hypothesized and competing explanations.
+
+Fourth, we cannot rule out that biases in the literature caused our meta-analysis to overestimate the 'ironic' effects of intergroup contact.
+Publication bias could have prevented studies that found positive or non-significant associations from entering the published literature.
+Even though we used state-of-the-art methods to detect and correct for publication bias, we did not find conclusive evidence for or against publication bias.
+That said, 61% of samples were *either* not collected with the intention to study the effects of intergroup contact on a relevant outcome (45%) *or* from unpublished studies (32%)—and thus unlikely to have been affected by publication bias.
+Another bias that could have affected our findings is that researchers made data-dependent decisions when analyzing data that inflate false-positive findings [@gelman_statistical_2014].
+Future research should use preregistration and other methods to prevent undisclosed flexibility in data collection and analysis.^[To date, one preregistered study has been published [@hassler_large-scale_2020].]
+
+To conclude, our preregistered meta-analysis found some evidence that intergroup contact reduces perceived injustice, discourages collective action, and diminishes support for reparative policies in disadvantaged groups—but also showed that the estimated effect sizes were small, variable, and consistent with alternative explanations.
+Our research was motivated by the broader question whether intergroup contact helps or hinders social change.
+By examining the narrower question whether intergroup contact diminishes support for social change in disadvantaged groups, we tested the most prominent hypothesis explaining how intergroup contact might *hinder* social change.
+We did not consider whether intergroup contact might *help* social change by reducing prejudice [for a critical perspective, see @dixon_beyond_2012] or by motivating advantaged-group members to acknowledge and challenge social inequality [@tropp_making_2018].
+Still, we hope that our meta-analytic review motivates researchers to address the open questions about how intergroup contact relates to support for social change in disadvantaged groups.
 
@@
 \setlength{\leftskip}{0.5in}
+\small
 

### 2021-04-13 manuscript/manuscript.tex
first complete draft

@@
-\documentclass[twocolumn, 10pt, letterpaper]{article}
+\documentclass[twocolumn, 11pt, letterpaper]{article}
 
@@
 \setcounter{secnumdepth}{0}
+\usepackage{sectsty}
+\sectionfont{\centering}
 \usepackage{authblk}
-% \renewcommand\Affilfont{\small}
+\renewcommand\Affilfont{\small}
 % \usepackage[hang, flushmargin]{footmisc}
-\setlength{\columnsep}{15pt}
+\setlength{\columnsep}{18pt}
 
@@
 \usepackage{graphicx}
-\usepackage[labelfont = bf, labelsep = newline, singlelinecheck = false]{caption}
+\usepackage[labelfont = bf, font = small, labelsep = newline, singlelinecheck = false]{caption}
 
@@
 \usepackage{tabularx}
-\usepackage[table, xcdraw]{xcolor}
+
+% Frontmatter
+\title{ Meta-Analysis of the `Ironic' Effects of Intergroup Contact }
+\author{  }
 
@@
 
-(Pettigrew \& Tropp, 2006)
+\maketitle
 
-\hypertarget{results}{%
-\section{Results}\label{results}}
+\noindent It is ironic that psychology's most-researched paradigm for reducing
+prejudice---intergroup contact---should hinder, rather than help, social
+change. Hundreds of studies have confirmed that intergroup contact is
+associated with less negative feelings toward outgroup members (for a
+meta-analysis, see Pettigrew \& Tropp, 2006). Most of these studies have
+focused on advantaged-group members' contact experiences with
+disadvantaged-group members (Tropp \& Pettigrew, 2005), guided by the
+idea that reducing advantaged-group members' prejudice will prevent
+interpersonal discrimination. Reducing prejudice, however, is rarely
+enough to overcome institutional and structural discrimination. Instead,
+as the 2020 Black Lives Matter protests have shown, social change often
+requires political mobilization by the disadvantaged. Critics have
+argued that, by fostering harmony and reducing conflict, intergroup
+contact might distract disadvantaged-group members from the injustice
+they face and undermine their motivation for social change (Dixon et
+al., 2005; Reicher, 2007; Wright, 2003). By stifling disadvantaged-group
+members' opposition to injustice, intergroup contact might thus have the
+`ironic' (Saguy et al., 2009), `sedative' (Çakal et al., 2011), or
+`paradoxical' (Dixon et al., 2010) effect of hindering social change.
 
-\hypertarget{search-results}{%
-\subsection{Search results}\label{search-results}}
+Supporting this argument, initial studies provided evidence that, among
+disadvantaged-group members, intergroup contact reduces perceptions of
+injustice (Saguy et al., 2009), discourages collective action (Çakal et
+al., 2011), and diminishes support for reparative policies (Dixon et
+al., 2007). Others, however, have pointed to conflicting evidence (Poore
+et al., 2002) and argued that intergroup contact might instead render
+discrimination more salient and, thereby, increase disadvantaged-group
+members' support for social change (Pettigrew et al., 2011). A decade
+after the initial studies, many more studies have examined the
+relationships between intergroup contact and support for social change
+in disadvantaged groups. We present a systematic review and
+meta-analysis of this growing literature. Specifically, we evaluate the
+evidence for three hypotheses about how intergroup contact might reduce
+support for social change.
+
+Perceived injustice---that is, perceiving unjust group-based deprivation
+or discrimination against the disadvantaged ingroup---is a prerequisite
+to instigating social change (van Zomeren et al., 2008). Researchers
+have argued that positive contact with advantaged-group members could
+contradict perceptions of personal discrimination, undermine negative
+characterizations of the advantaged outgroup, and, thereby, make group
+discrimination appear less plausible (Dixon et al., 2010). Positive
+contact could further reduce perceived injustice by emphasizing
+commonalities over differences (Saguy et al., 2009) and by motivating
+disadvantaged-group members to adopt system-justifying ideologies
+(Sengupta \& Sibley, 2013). To the extent that it reduces perceived
+injustice, intergroup contact hinders social change.
+
+Collective action---that is, any action directed at improving the
+conditions of the disadvantaged ingroup (Wright et al., 1990)---is
+crucial to achieving social change because advantaged-group members
+rarely surrender their advantages without sustained pressure from
+disadvantaged-group members (Blumer, 1958; for a review, see Dixon et
+al., 2012). Researchers have argued that intergroup contact could
+discourage disadvantaged-group members from engaging in collective
+action by diminishing their perceived discrimination (Tropp et al.,
+2012), by blurring boundaries between the disadvantaged ingroup and the
+advantaged outgroup (Saguy et al., 2009), by reducing negative attitudes
+toward the advantaged outgroup (Wright \& Lubensky, 2009), and by
+quelling anger about inequality (Tausch et al., 2015) or toward the
+advantaged outgroup (Hayward et al., 2018). To the extent that it
+discourages collective action, intergroup contact hinders social change.
+
+Reparative policies (e.g., affirmative action) can be effective means to
+reduce social inequality. Disadvantaged-group members, who stand to
+benefit from their implementation, are important advocates for these
+policies. Researchers have argued that intergroup contact could diminish
+disadvantaged-group members' support for redistributive policies by
+creating sympathy for advantaged-group members (Dixon et al., 2007), by
+fostering positive outgroup attitudes and reducing attention to
+inequality (Saguy et al., 2009), and by increasing their endorsement of
+system-justifying ideologies (Sengupta \& Sibley, 2013). To the extent
+that it diminishes support for redistributive policies, intergroup
+contact hinders social change.
+
+As a growing number of studies had been examining these relationships,
+we conducted a preregistered meta-analytic review of the available
+evidence for the hypothesized negative effects of intergroup contact on
+perceived injustice, collective action, and policy support in
+disadvantaged groups.
+
+Our first objective was to systematically review the available evidence
+and to evaluate its strengths and limitations. Our second objective was
+to synthesize the available evidence to establish the direction and
+magnitude of the relationships between intergroup contact and the three
+outcomes. Doing so allows us, first, to determine whether the available
+evidence supports a negative or positive (see Pettigrew et al., 2011)
+relationship between contact and support for social change and, second,
+to estimate the strength of this relationship. Our third objective was
+to explore the variability of this relationship across study settings,
+designs, and other potential moderators. For example, we examined
+whether any effects were confined to Western, Educated, Industrialized,
+Rich, Democratic (WEIRD) settings, the cultural context of most
+psychological research (Henrich et al., 2010). Our fourth objective was
+to assess how robust the available evidence was to publication bias.
+Together, these objectives provided a comprehensive answer to the
+question whether intergroup contact diminishes support for social change
+in disadvantaged groups.
+
+In addition, we explored the evidence for two alternative accounts of
+this relationship. First, we considered studies that measured both
+ingroup and outgroup contact as predictors of the three outcomes.
+Sengupta et al. (2015) argued that contact with other members of the
+disadvantaged ingroup would increase political mobilization in
+disadvantaged groups. As outgroup contact places limits on how much
+ingroup contact disadvantaged-group members can have (Pfister et al.,
+2020), the mobilizing effect of ingroup contact is an alternative
+explanation for negative associations between outgroup contact and
+support for social change.
+
+Second, we considered studies that measured both negative and positive
+(outgroup) contact as predictors of the three outcomes. Researchers
+(Hayward et al., 2018; Reimer et al., 2017) found negative contact with
+advantaged-group members to be associated with greater perceived
+discrimination and stronger collective action intentions. Reimer et al.
+(2017) argued that, to the extent disadvantaged-group members who have
+more positive contact also tend to have less negative contact, the
+mobilizing effect of negative contact is an alternative explanation for
+negative associations between outgroup contact and support for social
+change. For both alternative explanations, we collate and synthesize the
+available evidence for the relative effects of each predictor variable
+on the three outcomes.
+
+\hypertarget{method}{%
+\section{Method}\label{method}}
+
+\hypertarget{transparency}{%
+\subsection{Transparency}\label{transparency}}
+
+We prepared a protocol in accordance with the PRISMA-P statement (Moher
+et al., 2015) and preregistered it on the Open Science
+Framework.\footnote{\url{https://osf.io/ryuev/?view_only=8938ac6178914da98bdda1da4a6e27f0}}
+Preregistration precludes undisclosed flexibility in study selection,
+outcome selection, and other decisions that influence effect size
+estimates---and thus prevents confirmation bias from determining the
+conclusions of a meta-analysis (Lakens et al., 2016). We report all
+deviations from our protocol in the Supplemental Materials. We make all
+data and analysis scripts available online.\footnote{\url{https://osf.io/w5tqv/?view_only=5cbf7ad5b2b449a7a0f4ada0337b802a}}
+
+\hypertarget{eligibility-criteria}{%
+\subsection{Eligibility Criteria}\label{eligibility-criteria}}
+
+As preregistered, we considered all quantitative studies that included
+participants of a relatively disadvantaged group (see \emph{Types of
+Participants}), that manipulated or measured intergroup contact with a
+relatively advantaged group (see \emph{Types of Predictor Variables}),
+and that measured one or more of the following outcomes: perceptions or
+expectations of injustice, collective action intentions and behaviours,
+and/or support for policies that benefit or harm the participants'
+ingroup (see \emph{Types of Outcome Variables}).
+
+\hypertarget{types-of-participants}{%
+\subsubsection{Types of Participants}\label{types-of-participants}}
+
+We included studies with participants whose ingroup is disadvantaged (in
+terms of status, power, or resources) relative to the outgroup they have
+(or report to have) contact with.
+
+\hypertarget{types-of-predictor-variables}{%
+\subsubsection{Types of Predictor
+Variables}\label{types-of-predictor-variables}}
+
+We included studies if they measured or manipulated the quantity of,
+quality of, and opportunity for contact with members of outgroups that
+are relatively advantaged compared to the participants' ingroup. We
+considered opportunity for contact, as it is a potential precursor to
+and proxy for face-to-face contact, but not imagined or indirect
+contact. Similarly, we included studies that measured intergroup contact
+indirectly by, for example, asking what proportion of someone's friends
+were \emph{not} from the participants' ingroup.
+
+\hypertarget{types-of-outcome-variables}{%
+\subsubsection{Types of Outcome
+Variables}\label{types-of-outcome-variables}}
+
+\textbf{\emph{Perceived Injustice.}} We included studies that measured
+perceptions that one is discriminated against because of one's group
+membership, that one's group faces discrimination in society, that one's
+group is relatively deprived compared to other groups, or that the
+deprivation and/or discrimination faced by one's group is unjust and
+illegitimate. We also considered expectations of fair treatment as the
+reverse of perceived injustice. We included studies that measured
+personal and/or group discrimination or a mixture of both.
+
+\textbf{\emph{Collective Action.}} We included studies that measured
+observed, reported, or intended engagement in any action aimed at
+improving the position of the participants' ingroup in society. This
+included participating in protests, signing petitions, and any other
+form of violent or nonviolent collective action.
+
+\textbf{\emph{Policy Support.}} We included studies that measured
+support for (or opposition to) policies and initiatives designed to
+improve the position of the participants' ingroup in society, for
+example, affirmative action policies.
+
+\hypertarget{search-strategy}{%
+\subsection{Search Strategy}\label{search-strategy}}
 
@@
 \end{figure*}
+
+As preregistered, we searched titles, abstract, and keywords for
+relevant terms in four electronic databases. We searched for relevant
+articles in the \emph{Scopus} and \emph{PsycINFO} databases. We searched
+for gray literature in the \emph{ProQuest Dissertations and Theses}
+database. We used similar non-exclusive search terms for all databases
+(see Supplemental Materials). We searched databases on April 1, 2019 and
+again on April 1, 2020. We exported records and relevant metadata from
+each database. We removed duplicates using the \emph{revtools} package
+(Westgate, 2019).
+
+To find unpublished studies, we sent a call to the mailing lists of
+several professional organizations (see Supplemental Materials). We also
+advertised on social media and at relevant conferences. We directed
+researchers to an online survey in which they answered questions about
+the eligibility of their unpublished research and, if the research was
+eligible, provided data on moderator variables and effect sizes. We also
+contacted experts in the field, asking for unpublished research and
+other studies we might have missed.
+
+In addition, we used the \emph{Scopus} citation database to find records
+that cited at least one of the published articles included in the
+meta-analysis or at least one of three relevant review articles (Dixon
+et al., 2012; Reicher, 2007; Wright \& Lubensky, 2009). This search
+resulted in 2,075 records. Of these, we focused on 145 records that
+cited at least three eligible studies or relevant reviews and looked for
+eligible studies that were not among those from our original search.
+
+\hypertarget{study-selection}{%
+\subsection{Study Selection}\label{study-selection}}
+
+As preregistered, we selected studies in three stages. First, we
+screened records based on their title, abstract, and keywords. We
+refined our coding strategy over three random samples of 100 records
+until we achieved acceptable inter-rater agreement (\(\kappa_1 = .56\),
+\(\kappa_2 = .60\), \(\kappa_3 = .79\)). We then divided the remaining
+records between the two authors. For each record, one of the authors
+coded whether the record met the eligibility criteria (yes, maybe, no),
+or whether it was a relevant review article. We kept all records coded
+as ``yes'' or ``maybe''. Second, both authors reviewed each of the
+full-text manuscripts from the previous stage and coded whether any
+study or sample in the manuscript fulfilled the preregistered
+eligibility criteria (\(\kappa = .75\)). Third, we resolved any
+disagreements (by consensus) and excluded ineligible records.
+
+\hypertarget{data-collection}{%
+\subsection{Data Collection}\label{data-collection}}
+
+\hypertarget{effect-sizes}{%
+\subsubsection{Effect Sizes}\label{effect-sizes}}
+
+From all eligible records, we extracted correlation coefficients (\(r\))
+as the relevant measure of effect size and extracted sample sizes
+(\(n\)) to calculate standard errors for each sample's correlation
+coefficients. When provided, we copied correlation coefficients from the
+text or tables. When other effect-size measures were provided, we
+converted them to correlation coefficients using common conversion
+formulas (Borenstein et al., 2009). When effect sizes were not provided,
+we attempted to contact the authors to obtain the relevant effect sizes.
+We did not contact authors for studies that were more than twenty years
+old as we considered it unlikely that authors still had access to the
+underlying data. When we could not extract or obtain an effect size for
+a study or sample, we either imputed missing correlation coefficients
+from standardized beta coefficients (Peterson \& Brown, 2005) if
+reported or excluded the study or sample if not.
+
+\hypertarget{outcomes-selection}{%
+\subsubsection{Outcomes Selection}\label{outcomes-selection}}
+
+We collected effect sizes for all relationships between eligible
+predictor and outcome variables. When more than one eligible measure was
+reported, we extracted effect sizes for all of them. As preregistered,
+we also extracted effect sizes for negative contact, ingroup contact,
+group identification, and outgroup attitudes.
+
+When a study reported effect sizes for more than one measure of
+intergroup contact, we prioritized the predictor variable in the
+preregistered analyses that measured the most intense or intimate form
+of contact. As preregistered, we used the following ranking: cross-group
+friendship \textgreater{} quality of contact/positive contact
+\textgreater{} quantity of contact \textgreater{} opportunity for
+contact. When it was unclear which of several predictor variables
+measured the most intense form of contact, we combined and averaged
+effect sizes.
+
+When a study reported effect sizes for more than one measure of one of
+the three outcome variables, we selected effect sizes for the
+preregistered analyses as follows: For perceived injustice, we
+prioritized the measure closest to perceptions of injustice against the
+participants' ingroup (rather than against the participants themselves);
+when it was ambiguous which measure that was, we combined and averaged
+effect sizes across outcome measures. For collective action, we
+prioritized the measure that was the primary focus of the reported
+analyses; otherwise, we combined and averaged effects sizes across
+outcome measures. For policy support, we combined and averaged effect
+sizes for all policies designed to improve the position of the
+participants' ingroup in society.
+
+Some study designs resulted in more than one effect size for the same
+measure: When a longitudinal study reported results from more than two
+waves, we prioritized effect sizes spanning the inter-survey interval
+closest to one year. If a longitudinal study reported results from more
+than two waves and spanned multiple years, we combined and averaged
+effect sizes from each one-year inter-survey interval. In the
+preregistered analyses, we included the cross-lagged partial correlation
+between the relevant predictor variable (at time 1) and outcome variable
+(at time 2) controlling for initial levels of the outcome variable (at
+time 1). When an experimental or quasi-experimental study reported
+comparisons between more than two conditions, we prioritized the effect
+size that compared two conditions that most closely resembled generic
+contact and no-contact conditions.
+
+\hypertarget{potential-moderators}{%
+\subsubsection{Potential Moderators}\label{potential-moderators}}
 
@@
 
+In addition to extracting and selecting effect sizes for the
+preregistered analyses, we collected data on a broad range of potential
+moderators. All moderators that required subjective assessments were
+coded by both authors. We calculated inter-rater agreement (Cohen's
+\(\kappa\)) and resolved all disagreements by consensus.
+
+\textbf{\emph{Study Setting.}} For each sample, we recorded in what
+country (or countries) the data was collected (\(\kappa = .97\)) and
+what the disadvantaged ingroup and the advantaged outgroup were. We
+categorized each sample's setting according to whether the source of the
+groups' relative inequality was long-term migration (e.g., Asian
+Americans), short-term migration (e.g., international students), slavery
+(e.g., Black Americans), colonization (e.g., Māori, Black South
+Africans), religion, caste, sexuality, or another distinction
+(\(\kappa = .84\)).
+
+\textbf{\emph{Study Design.}} We categorized each study as either
+observational and cross-sectional, observational and longitudinal,
+quasi-experimental, experimental, an intervention, or other
+(\(\kappa = .85\)). We categorized each sample as either a student
+convenience sample, a non-student convenience sample, a probability or
+representative sample, or another kind of sample (\(\kappa = .73\)). We
+categorized the age group(s) in each sample as children (\(\leq 12\)
+years), adolescents (13--18 years), or adults (\(\geq 18\) years;
+\(\kappa = .64\)).
+
+\textbf{\emph{Study Intention.}} We coded whether or not each study was
+conducted with the intention to examine the effects of intergroup
+contact on one or more of the three outcome measures (\(\kappa = .48\)).
+
+\textbf{\emph{Publication status.}} For each study, we coded whether it
+was published, unpublished, or an unpublished dissertation based on the
+information source from which we obtained it.
+
+\textbf{\emph{Predictor Variables.}} For each measure of intergroup
+contact, we coded whether it assessed contact with the specific
+advantaged outgroup of interest directly---or whether it assessed
+contact indirectly by, for example, asking what proportion of someone's
+friends were not from the participants' ingroup or what proportion of
+residents in someone's neighbourhood were from the relevant outgroup
+(\(\kappa = .82\)).
+
+\textbf{\emph{Outcome Variables.}} For each measure of perceived
+injustice, we coded whether it refered to specific instances of
+discrimination, to a more general perception of discrimination, or to
+both (\(\kappa = .67\)) and whether it assessed personal discrimination,
+group discrimination, or both (\(\kappa = .83\)).
+
+\textbf{\emph{Cultural Distance.}} We also used the measure developed by
+Muthukrishna et al. (2020), when available, to quantify each country's
+cultural distance from the United States, which represents the cultural
+context of most psychological research (Henrich et al., 2010).
+
+\hypertarget{analysis-strategy}{%
+\subsection{Analysis Strategy}\label{analysis-strategy}}
+
 \hypertarget{preregistered-analyses}{%
-\subsection{Preregistered analyses}\label{preregistered-analyses}}
+\subsubsection{Preregistered Analyses}\label{preregistered-analyses}}
+
+We transformed correlation coefficients to Fisher's \(z\) which is
+unbounded and has a normal sampling distribution: \begin{align*} 
+z & = \frac{1}{2} \ln\left(\frac{1 + r}{1 - r}\right) \\ \sigma & = \frac{1}{\sqrt{n - 3}} \end{align*}
+where \(r\) is the sample correlation coefficient, \(z\) is the
+transformed effect size, \(n\) is the sample size, and \(\sigma\) is the
+standard error of the transformed effect size.
+
+We estimated effect sizes using Bayesian random-effects meta-analysis
+models in \emph{RStan} (Stan Development Team, 2020) which modeled the
+\emph{z}-transformed correlation coefficients with a normal likelihood
+function:
+\begin{align*} z_{ij} &\sim \text{Normal}(\theta_{ij}, \sigma_{ij}) \\ \theta_{ij} &= \begin{cases} \mu + \beta_j\tau_J & \text{if } I_j = 1 \\ \mu + \beta_j\tau_J + \beta_i\tau_I & \text{if } I_j > 1 \end{cases} \\ \end{align*}
+where \(z_{ij}\) is the observed effect size in sample \(i\) of study
+\(j\), \(\sigma_{ij}\) is the sample standard error, and \(\theta_{ij}\)
+is the estimated effect size. We estimated \(z_{ij}\) as a function of
+the mean effect size \(\mu\) and of two varying (random) intercepts,
+\(\beta_i\) and \(\beta_j\), with the corresponding standard deviations,
+\(\tau_I\) and \(\tau_J\). We used the non-centered parameterization to
+model the random effects. For studies that contained only one sample
+(\(I_j = 1\)), we only included \(\beta_j\tau_J\), the study-wise
+deviation from the mean effect size \(\mu\). For studies that contained
+more than one sample (\(I_j > 1\)), we also estimated \(\beta_i\tau_I\),
+the sample-wise deviation from the study-specific effect size.
+
+Models assigned weakly informative prior distributions to all
+parameters. The prior distribution for the mean effect size,
+\(\mu \sim \text{Normal}(0, 0.31605)\), was centered around 0 and
+concentrated 50\% of the most plausible values between \(r = -.21\) and
+\(r = .21\). We focus on \(|r| = .21\) because it corresponds to the
+mean effect size observed in both Pettigrew and Tropp's (2006)
+meta-analysis of the contact literature and Richard et al.'s (2003)
+meta-analysis of effect sizes across a century of social-psychological
+research. The prior distribution for the standard deviation of random
+effects, \(\tau \sim \text{Half-Cauchy}(0, 0.3)\), allocated 30\% of
+plausible values below \(\tau = 0.15\) and had a wide tail. We focus on
+\(\tau = 0.15\) because it corresponds to the standard deviations
+observed in both Pettigrew and Tropp's (2006) and Richard et al.'s
+(2003) meta-analyses. We chose this prior distribution in line with
+recommendations by Williams et al.~(2018).
+
+Bayesian inference involves choosing a likelihood function and prior
+distributions. A likelihood function links the observed data to one or
+more model parameters and states how likely the observed data are given
+different values of said model parameters. Prior distributions state how
+plausible different values of said model parameters are before
+considering the observed data. Bayesian inference applies Bayes' theorem
+to update prior distributions in light of the observed data to produce
+posterior distributions. Other than \emph{p}-values and confidence
+intervals, the resulting posterior distributions have a straightforward
+interpretation as stating how plausible different values of the model
+parameters are given the observed data. We report point estimates, based
+on the median of posterior samples, and uncertainty intervals, based on
+the quantiles of posterior samples, that enclose the 95\% most plausible
+estimates. In addition, we report the posterior probability, based on
+the proportion of posterior samples below zero, that an estimated mean
+effect size is negative.
+
+\hypertarget{other-analyses}{%
+\subsubsection{Other Analyses}\label{other-analyses}}
+
+We also conducted non-preregistered analyses to estimate to what extent
+moderator variables explained heterogeneity in the estimated effect
+sizes, to what extent meta-biases influenced the estimated effect sizes,
+and to what extent the three outcome variables were associated with two
+alternative predictor variables, ingroup contact and negative contact.
+
+\hypertarget{results}{%
+\section{Results}\label{results}}
+
+\hypertarget{search-results}{%
+\subsection{Search Results}\label{search-results}}
+
+Figure 1 shows a flow diagram illustrating our search strategy, study
+selection, and data collection. Our preregistered search strategy
+returned 2,610 unique records from electronic databases. Of these, we
+excluded 2,379 (91\%) ineligible records after screening titles,
+abstracts, and keywords. Of the remaining 231 records, we excluded 116
+(50\%) ineligible records after reviewing full-text manuscripts. We
+supplemented these records with 14 unpublished studies solicited from
+researchers and 6 records that cited at least three relevant works. Of
+135 eligible studies, we had to exclude 39 (29\%) studies for which we
+could not extract or impute any relevant effect size. At each stage, we
+also excluded studies that used the same data as another study. Our
+final sample comprised effect sizes from \(J = 96\) studies spanning
+\(N = 211,360\) participants in \(I = 137\) samples.
+
+Figure 2 provides a qualitative overview of the literature. Even though
+most participants came from studies conducted in India (\(N = 104,639\))
+and the United States (\(N = 61,089\); Figure 2a), most samples were
+collected in North America (\(I = 48\)) and Europe (\(I = 40\)), with
+few samples from South America and Africa (Figure 2b). Most samples
+focused on relative inequalities that resulted from long-term migration
+(\(I = 54\)), slavery (\(I = 19\)), colonization (\(I = 17\)), and
+short-term migration (\(I = 14\)). With few exceptions, studies used
+observational, cross-sectional survey designs. Samples sizes ranged from
+64 to 49,764 (\(\textit{Mdn} = 282\)). Unlike most psychological
+research, 2 in 5 samples used probability or representative sampling. Of
+all samples, 55\% (\(I = 75\)) were collected with the intention to
+examine the effects of intergroup contact on the outcomes considered in
+this meta-analysis.\footnote{Many studies examined acculturation
+  processes (Berry, 1997) and measured both intergroup contact and
+  perceived injustice without the relationship between the two being of
+  interest.} Together, these observations highlight both limitations and
+strengths of the empirical literature.
+
+\hypertarget{preregistered-analyses-1}{%
+\subsection{Preregistered Analyses}\label{preregistered-analyses-1}}
 
@@
 
-\begin{figure*}
+\begin{figure*}[!t]
 \centering
@@
 
-\emph{Perceived injustice.} Across 201,912 participants from 123 samples
-in 84 studies, we found strong evidence for a weak association
-(\(r = -.07, [-.10, -.04]\)) between intergroup contact and perceived
-injustice, with \(>99.9\%\) of posterior samples for the mean
+\textbf{\emph{Perceived Injustice.}} Across 201,912 participants from
+123 samples in 84 studies, we found strong evidence for a weak
+association (\(r = -.07, [-.10, -.04]\)) between intergroup contact and
+perceived injustice, with \(>99.9\%\) of posterior samples for the mean
 correlation coefficient falling below zero. We found evidence that
@@
 
-\emph{Collective action.} Across 119,085 participants from 37 samples in
-24 studies, we found some evidence for a weak association
+\textbf{\emph{Collective Action.}} Across 119,085 participants from 37
+samples in 24 studies, we found some evidence for a weak association
 (\(r = -.06, [-.13, .02]\)) between intergroup contact and collective
@@
 
-\emph{Policy support.} Across 13,703 participants from 19 samples in 14
-studies, we found some evidence for a weak association
+\textbf{\emph{Policy Support.}} Across 13,703 participants from 19
+samples in 14 studies, we found evidence for a weak association
 (\(r = -.07, [-.14, -.00]\)) between intergroup contact and policy
@@
 
-\hypertarget{robustness-checks}{%
-\subsubsection{Robustness checks}\label{robustness-checks}}
+In addition, we ran preregistered robustness checks which showed that
+our main analyses were robust to choosing different prior distributions
+and to excluding influential studies (see Supplemental Materials).
 
-First, we assessed to what extent our findings were sensitive to
-choosing narrower, \(\mu \sim \text{Normal}(0, 0.1)\), or wider,
-\(\mu \sim \text{Normal}(0, 1)\), prior distributions. Choosing narrower
-or wider prior distribution did not affect mean effect size estimates
-for perceived injustice (\(\Delta r = -.00, [-.05, .04]\) and
-\(\Delta r = .00, [-.05, .05]\)), collective action
-(\(\Delta r = -.01, [-.11, .09]\) and \(\Delta r = -.00, [-.10, .11]\)),
-and policy support (\(\Delta r = -.01, [-.10, .08]\) and
-\(\Delta r = .00, [-.09, .10]\)). Second, we assessed to what extent our
-findings were sensitive to including or excluding influential studies by
-repeating the preregistered analyses \(J\) times while leaving out one
-of \(J\) studies each time and by calculating the mean absolute
-difference (\emph{MAD}) for the estimated mean effect size across
-left-out studies. For perceived injustice
-(\(\textit{MAD} = .02, [.01, .04]\)), collective action
-(\(\textit{MAD} = .04, [.02, .09]\)), and policy support
-(\(\textit{MAD} = .03, [.02, .08]\)), the \emph{MAD} was small. Leaving
-out the most influential study, for example, did not change estimates of
-the mean effect size for the three outcomes
-(\(\Delta r = .00, [-.04, .05]\); \(\Delta r = .02, [-.09, .12]\);
-\(\Delta r = -.02, [-.11, .07]\)). Together, these analyses showed that
-our findings were robust to choosing different prior distributions and
-to excluding influential studies.
+\hypertarget{moderator-analyses}{%
+\subsection{Moderator Analyses}\label{moderator-analyses}}
+
+We conducted two kinds of moderator analyses. For both analyses, we had
+an insufficient number of effect sizes to examine moderators for any
+outcomes except perceived injustice (for details, see Supplemental
+Materials).
+
+\begin{figure*}
+\centering
+\caption{Estimated effect sizes for the association between intergroup contact and perceived injustice as a function of various categorical moderator variables}
+\includegraphics[scale=1]{../figures/figure-4}
+\caption*{\textit{Note.} Intervals enclose the 95\% most plausible estimates of the category-specific effect size.
+Shaded ribbons enclose the 95\% most plausible estimates of the mean effect size from the main analyses.
+Percentages indicate the estimated between-sample variance explained by each moderator variable.}
+\label{fig:f4}
+\end{figure*}
+
+\begin{figure*}
+\centering
+\caption{Estimated effect size as a function of cultural distance from the United States, with point estimates and uncertainty intervals for each country}
+\includegraphics[scale=1]{../figures/figure-5}
+\caption*{\textit{Note.} We had data from too few countries to reach firm conclusions about the direction of these associations for perceived injustice ($\beta = -0.36, [-1.43, 0.78]$; $\Pr (\beta < 0) = 73.5\%$), collective action ($\beta = -0.09, [-1.60, 1.37]$; $\Pr (\beta < 0) = 55.1\%$), and policy support ($\beta = -0.92, [-2.13, 0.55]$; $\Pr (\beta < 0) = 90.3\%$).}
+\label{fig:f5}
+\end{figure*}
+
+\begin{figure*}
+\centering
+\caption{Results from the random-effects meta-regression tree analysis}
+\includegraphics[scale=1]{../figures/figure-6}
+\caption*{\textit{Note.} Posterior distributions for the estimated correlation coefficient in each leaf of the meta-regression tree, highlighting the proportion of posterior samples for which $r_\text{mean} < 0$.
+S.-T.
+Migration = Short-Term Migration.}
+\label{fig:f6}
+\end{figure*}
+
+First, we used meta-regression models to examine specific moderator
+variables which we expected to explain heterogeneity in effect sizes
+across samples. Figure 4 shows results for categorical moderator
+variables. We found that the setting of the study (\(R^2 = 20\%\)),
+participants' age group (\(R^2 = 12\%\)), and whether intergroup contact
+was measured directly or indirectly (\(R^2 = 10\%\)) explained the most
+variance across effect sizes. Figure 5 shows results from country-level
+analyses examining cultural context as a moderator variable. We found
+that cultural distance from the United States tended to be associated
+with larger effect sizes---although we had data from too few countries
+to reach any firm conclusions.
+
+Second, we used meta-regression trees to discover interactions between
+moderator variables that best explained heterogeneity in effect sizes
+(Li et al., 2020). Figure 6 shows the resulting meta-regression that
+explained more variance across samples than any individual moderator
+(\(R^2 = 31\%\)). We found that intergroup contact was associated with
+less perceived injustice only in studies that focused on adults and that
+measured intergroup contact directly. Among these studies, this
+association was stronger in settings in which the groups' relative
+inequality stemmed from short-term migration or colonization
+(\(r = -.18, [-.23, -.13]\)) than in other settings
+(\(r = -.09, [-.12, -.06]\)).
+
+\hypertarget{meta-bias}{%
+\subsection{Meta Bias}\label{meta-bias}}
+
+\begin{figure*}
+\centering
+\caption{Unadjusted ($\bullet$) and adjusted ($\circ$) point estimates with confidence intervals from the random-effects meta-analysis (RMA), the PET-PEESE estimator, the three-parameter selection model (3PSM), the \textit{p}-uniform* estimator, and the subgroup analysis}
+\includegraphics[scale=1]{../figures/figure-7}
+\label{fig:f7}
+\end{figure*}
+
+Developing methods to detect and correct for publication bias and other
+meta-biases is an active area of research, with no single method
+outperforming all others (Carter et al., 2019). Following Carter et
+al.'s recommendations, we compared results of several methods to adjust
+meta-analytic estimates for publication bias: the PET-PEESE estimator
+(Stanley \& Doucouliagos, 2014); the three-parameter selection model
+(3PSM; Vevea \& Hedges, 1995); and the \emph{p}-uniform* estimator (van
+Aert \& Assen, 2018). As these methods do not use Bayesian statistics,
+we compared adjusted estimates from these methods to unadjusted
+estimates from a random-effects meta-analysis estimated with restricted
+maximum likelihood estimation using the \emph{metafor} package
+(Viechtbauer, 2010). In addition, we ran a meta-regression model that
+compared studies that were published \emph{and} were conducted with the
+intention to examine the effects of intergroup contact on any of the
+outcomes to all other studies. We report estimates from the latter
+subgroup of studies as we can assume that effect sizes in this subgroup
+were not affected by publication bias.
+
+Figure 7 shows adjusted and unadjusted estimates with confidence
+intervals for the three outcomes. Comparing adjusted and unadjusted
+estimates shows that the PET-PEESE and 3PSM methods tended to estimate
+the mean correlation coefficients to be closer to zero than the
+unadjusted estimate, with all confidence intervals including zero. The
+\emph{p}-uniform* method and the subgroup analysis tended to estimate
+the mean correlations coefficients to be closer to the unadjusted
+estimates, with the confidence interval for perceived injustice---but
+not for the other outcomes---excluding zero. All methods, however,
+resulted in confidence intervals that largely overlapped with, but were
+wider than, the confidence intervals around the unadjusted estimates.
+This reflects the reduced power of the various methods to correct for
+meta-biases when sample sizes are small, effect sizes are heterogeneous,
+or publication bias is strong (Carter et al., 2019). Therefore, there
+was insufficient evidence to conclude \emph{either} that, after
+adjusting for publication bias, intergroup contact was not associated
+with support of social change in disadvantaged groups \emph{or} that
+publication bias did not affect the relevant literature.
+
+\hypertarget{alternative-predictors}{%
+\subsection{Alternative Predictors}\label{alternative-predictors}}
+
+\begin{figure*}
+\centering
+\caption{Posterior distributions from the random-effect meta-analysis models with alternative predictor variables}
+\includegraphics[scale=1]{../figures/figure-8}
+\label{fig:f8}
+\end{figure*}
+
+We ran three random-effects meta-analysis models estimating the partial
+correlations of positive and negative contact with each outcome, using
+effect sizes from all studies that measured both predictors (Figure 8a).
+By using partial correlations, we estimated the effect of one form of
+contact while controlling for the other. Across 104,545 participants
+from 26 samples in 15 studies, we found stronger evidence for a positive
+association between negative contact and perceived injustice
+(\(r = .15, [.05, .25]\); \(\Pr (r > 0) = 99.8\%\)) than for a negative
+association between positive contact and perceived injustice
+(\(r = -.05, [-.12, .01]\); \(\Pr (r < 0) = 93.8\%\)). Across 107,451
+participants from 16 samples in 9 studies, we again found stronger
+evidence for a positive association between negative contact and
+collective action (\(r = .11, [.01, .20]\); \(\Pr (r > 0) = 98.4\%\))
+than for a negative association between positive contact and collective
+action (\(r = .00, [-.03, .06]\); \(\Pr (r < 0) = 40.7\%\)). Across
+8,273 participants from 7 samples in 3 studies, we also found stronger
+evidence for a positive association between negative contact and policy
+support (\(r = .04, [.00, .07]\); \(\Pr (r > 0) = 98.3\%\)) than for a
+negative association between positive contact and policy support
+(\(r = .03, [-.03, .10]\); \(\Pr (r < 0) = 12.7\%\)). Across 109,428
+participants from 28 samples in 16 studies, we found a negative
+association between positive and negative contact
+(\(r = -.16, [-.26, -.05]\); \(\Pr (r < 0) = 99.7\%\)).
+
+We ran three random-effects meta-analysis models that estimated the
+partial correlations of ingroup and outgroup contact with each outcomes,
+using effect sizes from all studies that measured both predictors
+(Figure 8b). Across 6,059 participants from 14 samples in 7 studies, we
+found insufficient evidence for associations of ingroup contact
+(\(r = .02, [-.13, .16]\); \(\Pr (r > 0) = 61.9\%\)) and outgroup
+contact (\(r = -.10, [-.29, .10]\); \(\Pr (r < 0) = 85.8\%\)) with
+perceived injustice. Across 3,938 participants from 4 samples in 2
+studies, we found stronger evidence for a positive association between
+ingroup contact and collective action (\(r = .12, [.03, .20]\);
+\(\Pr (r > 0) = 99.1\%\)) than for a negative association between
+outgroup contact and collective action (\(r = -.08, [-.25, .10]\);
+\(\Pr (r < 0) = 85.5\%\)). Across 3,187 participants from 3 samples in 1
+study, we found insufficient evidence for associations of ingroup
+contact (\(r = .09, [-.13, .27]\); \(\Pr (r > 0) = 86.2\%\)) and
+outgroup contact (\(r = -.03, [-.12, .08]\); \(\Pr (r < 0) = 78.5\%\))
+with policy support. Across 6,059 participants from 14 samples in 7
+studies, we found a positive association between ingroup and outgroup
+contact (\(r = .23, [.04, .35]\); \(\Pr (r > 0) = 98.8\%\)).
+
+\hypertarget{discussion}{%
+\section{Discussion}\label{discussion}}
+
+There is an emerging consensus that intergroup contact has the `ironic'
+effect of undermining support for social change in disadvantaged groups.
+We conducted a preregistered meta-analytic test of this effect across 96
+studies with 137 samples of 211,360 disadvantaged-group members. We
+found that, based on the available evidence, the associations of
+intergroup contact with perceived injustice (\(\Pr (r < 0) > 99.9\%\)),
+collective action (\(\Pr (r < 0) = 93.6\%\)), and support for reparative
+policies (\(\Pr (r < 0) = 98.1\%\)) were, on average, much more likely
+to be negative than positive. Thus, our meta-analysis seems to support
+the emerging consensus that intergroup contact diminishes support for
+social change in disadvantaged groups. We use the rest of this section
+to argue why this conclusion might be premature.
+
+First, the estimated effect sizes for the average associations of
+intergroup contact with perceived injustice (\(r = -.07\)), collective
+action (\(r = -.06\)), and policy support (\(r = -.07\)) were small.
+Across the three outcomes, the 95\% most plausible estimates included
+effect sizes between \(r = -.14\) and \(r = .02\). Effect sizes were
+thus much smaller than for the association between contact and prejudice
+in minority (\(r = -.18\)) and majority (\(r = -.23\)) groups (Tropp \&
+Pettigrew, 2005).\footnote{Comparing standardized effect sizes assumes
+  that the two outcomes are of equal importance. That is not always the
+  case: for example, a drug that reduces mild symptoms by 0.20 standard
+  deviations is not better than a drug that reduces deaths by 0.10
+  standard deviations.} Small effects can still be important if they
+accumulate over time or across people. For example, even a small change
+in policy attitudes could, if it affects enough people, sway a tight
+election. Cumulative effects, however, should not be assumed without an
+empirical or theoretical rationale (Funder \& Ozer, 2019)---neither of
+which has been provided in the published literature.
+
+Second, the estimated effect sizes varied across studies. For example,
+we estimated that 31\% of studies find a positive association between
+intergroup contact and perceived injustice. While the between-study
+heterogeneity is comparable to that in other meta-analyses (e.g.,
+Pettigrew \& Tropp, 2006), it supports Pettigrew et al.'s (2011)
+argument that, at least in some circumstances, intergroup contact
+renders discrimination \emph{more} salient.
+
+A combination of moderators explained about a third of the between-study
+variance in the association between intergroup contact and perceived
+injustice. We found that, on average, this association was negative only
+in studies of adults that measured contact \emph{directly} by asking,
+for example, about the number of friends from the advantaged outgroup.
+This suggests that, as hypothesized, the `ironic' effects result from
+direct contact and not from mere exposure or other contextual factors.
+We also found that, on average, effect sizes were greater for studies in
+post-colonial settings or on short-term migration than for studies in
+other contexts. Future research should systematically investigate
+variance in how contact affects support for social change across
+settings and cultures.
+
+\begin{figure}
+\centering
+\caption{Directed acyclic graphs for plausible causal relations between intergroup contact and support for social change}
+\includegraphics[scale=1]{../figures/figure-9}
+\caption*{\textit{Note.} IC = (Positive) Intergroup Contact, SC = Support for Social Change, U = Unobserved Variable(s), NC = Negative (Integroup) Contact, IN = Ingroup Contact}
+\label{fig:f9}
+\end{figure}
+
+Third, the available evidence is almost entirely from cross-sectional,
+observational studies and thus consistent with alternative explanations
+for the observed associations (Figure 9). Support for social change
+could reduce intergroup contact (B) rather than the other way around
+(A). For example, disadvantaged-group members involved in collective
+action might purposefully avoid forming friendships with
+advantaged-group members. Alternatively, the association between
+intergroup contact and support for social change could be spurious with
+both being caused by an unobserved confounder (C). For example, a
+disadvantaged-group member's socioeconomic status might both expose them
+to more advantaged-group members and reduce their perception of
+injustice. Future research should prioritize longitudinal studies to
+confirm the direction of the observed associations and (field)
+experiments to rule out confounding and other alternative
+explanations.\footnote{Published research includes only three
+  longitudinal studies (Koschate et al., 2012; Reimer et al., 2017;
+  Tropp et al., 2012), all of which conflated within-person change and
+  between-person stability (Hamaker et al., 2015), two experimental
+  studies with a no-contact control condition (Becker et al., 2013;
+  Droogendyk et al., 2016), and two intervention studies (Reimer et al.,
+  2021; Shani \& Boehnke, 2017).}
+
+Further, the observed association between intergroup contact and support
+for social change could be confounded by an alternative predictor that
+\emph{increases} support for social change (D, E). Supporting Reimer et
+al.'s (2017) argument, we found that positive intergroup contact was not
+associated with support for social change after controlling for negative
+contact which, in turn, was associated with \emph{greater} support for
+social change. We found mixed evidence for ingroup contact as an
+alternative explanation for the `ironic' effects of intergroup contact
+(Sengupta et al., 2015) but note that few studies measured both ingroup
+and outgroup contact. Going forward, researchers should clarify which
+aspects of intergroup contact they hypothesize to affect support for
+social change---and include measures that allow testing both the
+hypothesized and competing explanations.
+
+Fourth, we cannot rule out that biases in the literature caused our
+meta-analysis to overestimate the `ironic' effects of intergroup
+contact. Publication bias could have prevented studies that found
+positive or non-significant associations from entering the published
+literature. Even though we used state-of-the-art methods to detect and
+correct for publication bias, we did not find conclusive evidence for or
+against publication bias. That said, 61\% of samples were \emph{either}
+not collected with the intention to study the effects of intergroup
+contact on a relevant outcome (45\%) \emph{or} from unpublished studies
+(32\%)---and thus unlikely to have been affected by publication bias.
+Another bias that could have affected our findings is that researchers
+made data-dependent decisions when analyzing data that inflate
+false-positive findings (Gelman \& Loken, 2014). Future research should
+use preregistration and other methods to prevent undisclosed flexibility
+in data collection and analysis.\footnote{To date, one preregistered
+  study has been published (Hässler et al., 2020).}
+
+To conclude, our preregistered meta-analysis found some evidence that
+intergroup contact reduces perceived injustice, discourages collective
+action, and diminishes support for reparative policies in disadvantaged
+groups---but also showed that the estimated effect sizes were small,
+variable, and consistent with alternative explanations. Our research was
+motivated by the broader question whether intergroup contact helps or
+hinders social change. By examining the narrower question whether
+intergroup contact diminishes support for social change in disadvantaged
+groups, we tested the most prominent hypothesis explaining how
+intergroup contact might \emph{hinder} social change. We did not
+consider whether intergroup contact might \emph{help} social change by
+reducing prejudice (for a critical perspective, see Dixon et al., 2012)
+or by motivating advantaged-group members to acknowledge and challenge
+social inequality (Tropp \& Barlow, 2018). Still, we hope that our
+meta-analytic review motivates researchers to address the open questions
+about how intergroup contact relates to support for social change in
+disadvantaged groups.
 
@@
 \noindent \setlength{\parindent}{-0.5in} \setlength{\leftskip}{0.5in}
+\small
 
 \hypertarget{refs}{}
+\leavevmode\hypertarget{ref-becker_friend_2013}{}%
+Becker, J. C., Wright, S. C., Lubensky, M. E., \& Zhou, S. (2013).
+Friend or ally: Whether cross-group contact undermines collective action
+depends on what advantaged group members say (or don't say).
+\emph{Personality and Social Psychology Bulletin}, \emph{39}(4),
+442--455. \url{https://doi.org/10.1177/0146167213477155}
+
+\leavevmode\hypertarget{ref-blumer_race_1958}{}%
+Blumer, H. (1958). Race prejudice as a sense of group position.
+\emph{The Pacific Sociological Review}, \emph{1}(1), 3--7.
+\url{https://doi.org/10.2307/1388607}
+
+\leavevmode\hypertarget{ref-borenstein_introduction_2009}{}%
+Borenstein, M., Hedges, L. V., Higgins, J. P. T., \& Rothstein, H. R.
+(2009). \emph{Introduction to meta-analysis}. Wiley.
+
+\leavevmode\hypertarget{ref-carter_correcting_2019}{}%
+Carter, E. C., Schönbrodt, F. D., Gervais, W. M., \& Hilgard, J. (2019).
+Correcting for bias in psychology: A comparison of meta-analytic
+methods. \emph{Advances in Methods and Practices in Psychological
+Science}, \emph{2}(2), 115--144.
+\url{https://doi.org/10.1177/2515245919847196}
+
+\leavevmode\hypertarget{ref-cakal_investigation_2011}{}%
+Çakal, H., Hewstone, M., Schwär, G., \& Heath, A. (2011). An
+investigation of the social identity model of collective action and the
+``sedative'' effect of intergroup contact among Black and White students
+in South Africa. \emph{British Journal of Social Psychology},
+\emph{50}(4), 606--627.
+\url{https://doi.org/10.1111/j.2044-8309.2011.02075.x}
+
+\leavevmode\hypertarget{ref-dixon_beyond_2005}{}%
+Dixon, J., Durrheim, K., \& Tredoux, C. (2005). Beyond the optimal
+contact strategy: A reality check for the contact hypothesis.
+\emph{American Psychologist}, \emph{60}(7), 697--711.
+\url{https://doi.org/10.1037/0003-066X.60.7.697}
+
+\leavevmode\hypertarget{ref-dixon_intergroup_2007}{}%
+Dixon, J., Durrheim, K., \& Tredoux, C. (2007). Intergroup contact and
+attitudes toward the principle and practice of racial equality.
+\emph{Psychological Science}, \emph{18}(10), 867--872.
+\url{https://doi.org/10.1111/j.1467-9280.2007.01993.x}
+
+\leavevmode\hypertarget{ref-dixon_paradox_2010}{}%
+Dixon, J., Durrheim, K., Tredoux, C., Tropp, L., Clack, B., \& Eaton, L.
+(2010). A paradox of integration? Interracial contact, prejudice
+reduction, and perceptions of racial discrimination: A paradox of
+integration. \emph{Journal of Social Issues}, \emph{66}(2), 401--416.
+\url{https://doi.org/10.1111/j.1540-4560.2010.01652.x}
+
+\leavevmode\hypertarget{ref-dixon_beyond_2012}{}%
+Dixon, J., Levine, M., Reicher, S., \& Durrheim, K. (2012). Beyond
+prejudice: Are negative evaluations the problem and is getting us to
+like one another more the solution? \emph{Behavioral and Brain
+Sciences}, \emph{35}(6), 411--425.
+\url{https://doi.org/10.1017/S0140525X11002214}
+
+\leavevmode\hypertarget{ref-droogendyk_renewed_2016}{}%
+Droogendyk, L., Louis, W. R., \& Wright, S. C. (2016). Renewed promise
+for positive cross-group contact: The role of supportive contact in
+empowering collective action. \emph{Canadian Journal of Behavioural
+Science / Revue Canadienne Des Sciences Du Comportement}, \emph{48}(4),
+317--327. \url{https://doi.org/10.1037/cbs0000058}
+
+\leavevmode\hypertarget{ref-funder_evaluating_2019}{}%
+Funder, D. C., \& Ozer, D. J. (2019). Evaluating effect size in
+psychological research: Sense and nonsense. \emph{Advances in Methods
+and Practices in Psychological Science}, \emph{2}(2), 156--168.
+\url{https://doi.org/10.1177/2515245919847202}
+
+\leavevmode\hypertarget{ref-gelman_statistical_2014}{}%
+Gelman, A., \& Loken, E. (2014). The statistical crisis in science.
+\emph{American Scientist}, \emph{102}(6), 460--465.
+\url{https://doi.org/10.1511/2014.111.460}
+
+\leavevmode\hypertarget{ref-hamaker_critique_2015}{}%
+Hamaker, E. L., Kuiper, R. M., \& Grasman, R. P. P. P. (2015). A
+critique of the cross-lagged panel model. \emph{Psychological Methods},
+\emph{20}(1), 102--116. \url{https://doi.org/10.1037/a0038889}
+
+\leavevmode\hypertarget{ref-hayward_how_2018}{}%
+Hayward, L. E., Tropp, L. R., Hornsey, M. J., \& Barlow, F. K. (2018).
+How negative contact and positive contact with Whites predict collective
+action among racial and ethnic minorities. \emph{British Journal of
+Social Psychology}, \emph{57}(1), 1--20.
+\url{https://doi.org/10.1111/bjso.12220}
+
+\leavevmode\hypertarget{ref-hassler_large-scale_2020}{}%
+Hässler, T., Ullrich, J., Bernardino, M., Shnabel, N., Laar, C. V.,
+Valdenegro, D., Sebben, S., Tropp, L. R., Visintin, E. P., González, R.,
+Ditlmann, R. K., Abrams, D., Selvanathan, H. P., Branković, M., Wright,
+S., Zimmermann, J. von, Pasek, M., Aydin, A. L., Žeželj, I., \ldots{}
+Ugarte, L. M. (2020). A large-scale test of the link between intergroup
+contact and support for social change. \emph{Nature Human Behaviour},
+\emph{4}(4), 380--386. \url{https://doi.org/10.1038/s41562-019-0815-z}
+
+\leavevmode\hypertarget{ref-henrich_weirdest_2010}{}%
+Henrich, J., Heine, S. J., \& Norenzayan, A. (2010). The weirdest people
+in the world? \emph{Behavioral and Brain Sciences}, \emph{33}(2-3),
+61--135. \url{https://doi.org/10.1017/S0140525X10000725}
+
+\leavevmode\hypertarget{ref-koschate_when_2012}{}%
+Koschate, M., Hofmann, W., \& Schmitt, M. (2012). When East meets West:
+A longitudinal examination of the relationship between group relative
+deprivation and intergroup contact in reunified Germany. \emph{British
+Journal of Social Psychology}, \emph{51}(2), 290--311.
+\url{https://doi.org/10.1111/j.2044-8309.2011.02056.x}
+
+\leavevmode\hypertarget{ref-lakens_reproducibility_2016}{}%
+Lakens, D., Hilgard, J., \& Staaks, J. (2016). On the reproducibility of
+meta-analyses: Six practical recommendations. \emph{BMC Psychology},
+\emph{4}(1), 24. \url{https://doi.org/10.1186/s40359-016-0126-3}
+
+\leavevmode\hypertarget{ref-li_multiple_2020}{}%
+Li, X., Dusseldorp, E., Su, X., \& Meulman, J. J. (2020). Multiple
+moderator meta-analysis using the R-package Meta-CART. \emph{Behavior
+Research Methods}, \emph{52}(6), 2657--2673.
+\url{https://doi.org/10.3758/s13428-020-01360-0}
+
+\leavevmode\hypertarget{ref-moher_preferred_2015}{}%
+Moher, D., Shamseer, L., Clarke, M., Ghersi, D., Liberati, A.,
+Petticrew, M., Shekelle, P., \& Stewart, L. A. (2015). Preferred
+reporting items for systematic review and meta-analysis protocols
+(PRISMA-P) 2015 statement. \emph{Systematic Reviews}, \emph{4}(1), 1--9.
+\url{https://doi.org/10.1186/2046-4053-4-1}
+
+\leavevmode\hypertarget{ref-muthukrishna_beyond_2020}{}%
+Muthukrishna, M., Bell, A. V., Henrich, J., Curtin, C. M., Gedranovich,
+A., McInerney, J., \& Thue, B. (2020). Beyond western, educated,
+industrial, rich, and democratic (WEIRD) psychology: Measuring and
+mapping scales of cultural and psychological distance.
+\emph{Psychological Science}, \emph{31}(6), 678--701.
+\url{https://doi.org/10.1177/0956797620916782}
+
+\leavevmode\hypertarget{ref-peterson_use_2005}{}%
+Peterson, R. A., \& Brown, S. P. (2005). On the use of beta coefficients
+in meta-analysis. \emph{Journal of Applied Psychology}, \emph{90}(1),
+175--181. \url{https://doi.org/10.1037/0021-9010.90.1.175}
+
 \leavevmode\hypertarget{ref-pettigrew_meta-analytic_2006}{}%
@@
 
+\leavevmode\hypertarget{ref-pettigrew_recent_2011}{}%
+Pettigrew, T. F., Tropp, L. R., Wagner, U., \& Christ, O. (2011). Recent
+advances in intergroup contact theory. \emph{International Journal of
+Intercultural Relations}, \emph{35}(3), 271--280.
+\url{https://doi.org/10.1016/j.ijintrel.2011.03.001}
+
+\leavevmode\hypertarget{ref-pfister_contact_2020}{}%
+Pfister, M., Wölfer, R., \& Hewstone, M. (2020). Contact capacity and
+its effect on intergroup relations. \emph{Social Psychological and
+Personality Science}, \emph{11}(1), 7--15.
+\url{https://doi.org/10.1177/1948550619837004}
+
+\leavevmode\hypertarget{ref-poore_contact_2002}{}%
+Poore, A. G., Gagne, F., Barlow, K. M., Lydon, J. E., Taylor, D. M., \&
+Wright, S. C. (2002). Contact and the personal/group discrimination
+discrepancy in an Inuit community. \emph{The Journal of Psychology},
+\emph{136}(4), 371--382. \url{https://doi.org/10.1080/00223980209604164}
+
+\leavevmode\hypertarget{ref-reicher_rethinking_2007}{}%
+Reicher, S. (2007). Rethinking the paradigm of prejudice. \emph{South
+African Journal of Psychology}, \emph{37}(4), 820--834.
+\url{https://doi.org/10.1177/008124630703700410}
+
+\leavevmode\hypertarget{ref-reimer_intergroup_2017}{}%
+Reimer, N. K., Becker, J. C., Benz, A., Christ, O., Dhont, K., Klocke,
+U., Neji, S., Rychlowska, M., Schmid, K., \& Hewstone, M. (2017).
+Intergroup contact and social change: Implications of negative and
+positive contact for collective action in advantaged and disadvantaged
+groups. \emph{Personality and Social Psychology Bulletin}, \emph{43}(1),
+121--136. \url{https://doi.org/10.1177/0146167216676478}
+
+\leavevmode\hypertarget{ref-reimer_building_2021}{}%
+Reimer, N. K., Love, A., Wölfer, R., \& Hewstone, M. (2021). Building
+social cohesion through intergroup contact: Evaluation of a large-scale
+intervention to improve intergroup relations among adolescents.
+\emph{Journal of Youth and Adolescence}.
+\url{https://doi.org/10.1007/s10964-021-01400-8}
+
+\leavevmode\hypertarget{ref-richard_one_2003}{}%
+Richard, F. D., Bond, C. F., \& Stokes-Zoota, J. J. (2003). One hundred
+years of social psychology quantitatively described. \emph{Review of
+General Psychology}, \emph{7}(4), 331--363.
+\url{https://doi.org/10.1037/1089-2680.7.4.331}
+
+\leavevmode\hypertarget{ref-saguy_irony_2009}{}%
+Saguy, T., Tausch, N., Dovidio, J. F., \& Pratto, F. (2009). The irony
+of harmony: Intergroup contact can produce false expectations for
+equality. \emph{Psychological Science}, \emph{20}(1), 114--121.
+\url{https://doi.org/10.1111/j.1467-9280.2008.02261.x}
+
+\leavevmode\hypertarget{ref-sengupta_ingroup_2015}{}%
+Sengupta, N. K., Milojev, P., Barlow, F. K., \& Sibley, C. G. (2015).
+Ingroup friendship and political mobilization among the disadvantaged.
+\emph{Cultural Diversity and Ethnic Minority Psychology}, \emph{21}(3),
+358--368. \url{https://doi.org/10.1037/a0038007}
+
+\leavevmode\hypertarget{ref-sengupta_perpetuating_2013}{}%
+Sengupta, N. K., \& Sibley, C. G. (2013). Perpetuating one's own
+disadvantage: Intergroup contact enables the ideological legitimation of
+inequality. \emph{Personality and Social Psychology Bulletin},
+\emph{39}(11), 1391--1403.
+\url{https://doi.org/10.1177/0146167213497593}
+
+\leavevmode\hypertarget{ref-shani_effect_2017}{}%
+Shani, M., \& Boehnke, K. (2017). The effect of Jewish--Palestinian
+mixed-model encounters on readiness for contact and policy support.
+\emph{Peace and Conflict: Journal of Peace Psychology}, \emph{23}(3),
+219--227. \url{https://doi.org/10.1037/pac0000220}
+
+\leavevmode\hypertarget{ref-stan_development_team_rstan:_2020}{}%
+Stan Development Team. (2020). \emph{RStan: The R interface to Stan}.
+\url{http://mc-stan.org/}
+
+\leavevmode\hypertarget{ref-stanley_meta-regression_2014}{}%
+Stanley, T. D., \& Doucouliagos, H. (2014). Meta-regression
+approximations to reduce publication selection bias. \emph{Research
+Synthesis Methods}, \emph{5}(1), 60--78.
+\url{https://doi.org/10.1002/jrsm.1095}
+
+\leavevmode\hypertarget{ref-tausch_how_2015}{}%
+Tausch, N., Saguy, T., \& Bryson, J. (2015). How does intergroup contact
+affect social change? Its impact on collective action and individual
+mobility intentions among members of a disadvantaged group.
+\emph{Journal of Social Issues}, \emph{71}(3), 536--553.
+\url{https://doi.org/10.1111/josi.12127}
+
+\leavevmode\hypertarget{ref-tropp_making_2018}{}%
+Tropp, L. R., \& Barlow, F. K. (2018). Making advantaged racial groups
+care about inequality: Intergroup contact as a route to psychological
+investment. \emph{Current Directions in Psychological Science},
+\emph{27}(3), 194--199. \url{https://doi.org/10.1177/0963721417743282}
+
+\leavevmode\hypertarget{ref-tropp_crossethnic_2012}{}%
+Tropp, L. R., Hawi, D. R., Van Laar, C., \& Levin, S. (2012).
+Cross‐ethnic friendships, perceived discrimination, and their effects on
+ethnic activism over time: A longitudinal investigation of three ethnic
+minority groups. \emph{British Journal of Social Psychology},
+\emph{51}(2), 257--272.
+\url{https://doi.org/10.1111/j.2044-8309.2011.02050.x}
+
+\leavevmode\hypertarget{ref-tropp_relationships_2005}{}%
+Tropp, L. R., \& Pettigrew, T. F. (2005). Relationships between
+intergroup contact and prejudice among minority and majority status
+groups. \emph{Psychological Science}, \emph{16}(12), 951--957.
+\url{https://doi.org/10.1111/j.1467-9280.2005.01643.x}
+
+\leavevmode\hypertarget{ref-van_aert_correcting_2018}{}%
+van Aert, R. C. M., \& Assen, M. A. L. M. van. (2018). \emph{Correcting
+for publication bias in a meta-analysis with the p-uniform* method}.
+MetaArXiv. \url{https://doi.org/10.31222/osf.io/zqjr9}
+
+\leavevmode\hypertarget{ref-van_zomeren_toward_2008}{}%
+van Zomeren, M., Postmes, T., \& Spears, R. (2008). Toward an
+integrative social identity model of collective action: A quantitative
+research synthesis of three socio-psychological perspectives.
+\emph{Psychological Bulletin}, \emph{134}(4), 504--535.
+\url{https://doi.org/10.1037/0033-2909.134.4.504}
+
+\leavevmode\hypertarget{ref-vevea_general_1995}{}%
+Vevea, J. L., \& Hedges, L. V. (1995). A general linear model for
+estimating effect size in the presence of publication bias.
+\emph{Psychometrika}, \emph{60}(3), 419--435.
+\url{https://doi.org/10.1007/BF02294384}
+
+\leavevmode\hypertarget{ref-viechtbauer_conducting_2010}{}%
+Viechtbauer, W. (2010). Conducting meta-analyses in R with the metafor
+package. \emph{Journal of Statistical Software}, \emph{36}(1), 1--48.
+\url{https://doi.org/10.18637/jss.v036.i03}
+
+\leavevmode\hypertarget{ref-westgate_revtools:_2019}{}%
+Westgate, M. J. (2019). Revtools: An R package to support article
+screening for evidence synthesis. \emph{Research Synthesis Methods},
+\emph{10}(4), 606--614. \url{https://doi.org/10.1002/jrsm.1374}
+
+\leavevmode\hypertarget{ref-brown_strategic_2003}{}%
+Wright, S. C. (2003). Strategic collective action: Social psychology and
+social change. In R. Brown \& S. L. Gaertner (Eds.), \emph{Blackwell
+handbook of social psychology: Intergroup processes} (pp. 409--430).
+Blackwell. \url{https://doi.org/10.1002/9780470693421.ch20}
+
+\leavevmode\hypertarget{ref-wright_struggle_2009}{}%
+Wright, S. C., \& Lubensky, M. E. (2009). The struggle for social
+equality: Collective action versus prejudice reduction. In S. Demoulin,
+J.-P. Leyens, \& J. F. Dovidio (Eds.), \emph{Intergroup
+misunderstandings: Impact of divergent social realities} (pp. 291--310).
+Psychology Press.
+
+\leavevmode\hypertarget{ref-wright_responding_1990}{}%
+Wright, S. C., Taylor, D. M., \& Moghaddam, F. M. (1990). Responding to
+membership in a disadvantaged group: From acceptance to collective
+protest. \emph{Journal of Personality and Social Psychology},
+\emph{58}(6), 994--1003.
+\url{https://doi.org/10.1037/0022-3514.58.6.994}
+
 \endgroup

### 2021-04-13 manuscript/supplemental-materials.Rmd
first complete draft

---
title: "Supplemental Materials"
bibliography: references.bib
csl: apa.csl
output:
  pdf_document:
    latex_engine: pdflatex
    keep_tex: yes
    template: custom-template.tex
---

```{r setup, include = FALSE}

  # Load packages
  library(tidyverse); library(tidybayes); library(numform)

  # Functions
  r_to_z <- function(r) 0.5 * log( (1 + r) / (1 - r) )
  z_to_r <- function(z) ( exp(2 * z) - 1 ) / ( exp(2 * z) + 1 )

  # knitr options
  knitr::opts_chunk$set(echo = FALSE)

```

# Robustness Checks

```{r, include = FALSE}

  # Summarize prior choice results
  d_priors <- read_rds("../results/results_robustness_checks_priors.rds") %>% 
    group_by(y_var, prior) %>% 
    median_qi(d_r_mean) %>% 
    mutate(
      across(c(d_r_mean, .lower, .upper), ~f_num(., digits = 2)),
      text = paste0("$\\Delta r = ", d_r_mean, ", [", .lower, ", ", .upper, "]$")
    )

```

```{r, include = FALSE}

  # Calculate Mean Absolute Deviation (MAD)
  mad_loo <- read_rds("../results/results_robustness_checks_loo.rds") %>% 
    group_by(.draw, y_var) %>% 
    summarize(mad_loo = mean(ae_loo)) %>% 
    group_by(y_var) %>% 
    median_qi(mad_loo) %>% 
    mutate(
      across(c(mad_loo, .lower, .upper), ~f_num(., digits = 2)),
      text = paste0("$\\textit{MAD} = ", mad_loo, ", [", .lower, ", ", .upper, "]$")
    )

  # Leave out most influential studies
  d_loo <- read_rds("../results/results_robustness_checks_loo.rds") %>% 
    group_by(y_var, id) %>%
    median_qi(e_loo) %>% 
    top_n(n = 1, wt = abs(e_loo)) %>% 
    mutate(
      across(c(e_loo, .lower, .upper), ~f_num(., digits = 2)),
      text = paste0("$\\Delta r = ", e_loo, ", [", .lower, ", ", .upper, "]$")
    )

```

As preregistered, we conducted two kinds of robustness checks. First, we assessed to what extent our findings were sensitive to choosing narrower, $\mu \sim \text{Normal}(0, 0.1)$, or wider, $\mu \sim \text{Normal}(0, 1)$, prior distributions. Choosing narrower or wider prior distribution did not affect mean effect size estimates for perceived injustice (`r d_priors$text[d_priors$y_var == "pi" & d_priors$prior == "N(0, 0.1)"]` and `r d_priors$text[d_priors$y_var == "pi" & d_priors$prior == "N(0, 1.0)"]`), collective action (`r d_priors$text[d_priors$y_var == "ca" & d_priors$prior == "N(0, 0.1)"]` and `r d_priors$text[d_priors$y_var == "ca" & d_priors$prior == "N(0, 1.0)"]`), and policy support (`r d_priors$text[d_priors$y_var == "ps" & d_priors$prior == "N(0, 0.1)"]` and `r d_priors$text[d_priors$y_var == "ps" & d_priors$prior == "N(0, 1.0)"]`). Second, we assessed to what extent our findings were sensitive to including or excluding influential studies by repeating the preregistered analyses $J$ times while leaving out one of $J$ studies each time and by calculating the mean absolute difference (*MAD*) for the estimated mean effect size across left-out studies. For perceived injustice (`r mad_loo$text[mad_loo$y_var == "pi"]`), collective action (`r mad_loo$text[mad_loo$y_var == "ca"]`), and policy support (`r mad_loo$text[mad_loo$y_var == "ps"]`), the *MAD* was small. Leaving out the most influential study, for example, did not change estimates of the mean effect size for the three outcomes (`r d_loo$text[d_loo$y_var == "pi"]`; `r d_loo$text[d_loo$y_var == "ca"]`; `r d_loo$text[d_loo$y_var == "ps"]`). Together, these analyses showed that our findings were robust to choosing different prior distributions and to excluding influential studies.

# References

\begingroup

\noindent
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id="refs"></div>

\endgroup

### 2021-04-13 figures/figure-1.R

@@ -222,11 +222,7 @@ rm(list = ls())
     minor_breaks = seq(47, 0, -1)
   ) +
   coord_equal(xlim = c(0, 56), ylim = c(0, 47), expand = FALSE) +
-  theme_void(base_size = 10) +
-  theme(
-    # panel.grid.major = element_line(colour = "grey92", size = rel(0.75)),
-    # panel.grid.minor = element_line(colour = "grey92", size = rel(0.50))
-  )
+  theme_void(base_size = 10)
 
 
 # Export ------------------------------------------------------------------

### 2021-04-13 figures/figure-2a.R

@@ -174,7 +174,7 @@
     ) +
     scale_colour_viridis_c(
       option = "B",
-      limits = c(min(world_sf$N, na.rm = TRUE), max(world_sf$N, na.rm = TRUE)),
+      limits = c(10, max(world_sf$N, na.rm = TRUE)),
       direction = -1,
       breaks = c(10, 100, 1000, 10000, 100000),
       labels = f_comma(c(10, 100, 1000, 10000, 100000)),
@@ -184,7 +184,7 @@
     ) +
     scale_fill_viridis_c(
       option = "B",
-      limits = c(min(world_sf$N, na.rm = TRUE), max(world_sf$N, na.rm = TRUE)),
+      limits = c(10, max(world_sf$N, na.rm = TRUE)),
       direction = -1,
       breaks = c(10, 100, 1000, 10000, 100000),
       labels = f_comma(c(10, 100, 1000, 10000, 100000)),

### 2021-04-16 manuscript/manuscript.Rmd
add abstract

@@
 csl: apa.csl
+abstract: 
+  Critics have argued that intergroup contact, psychology’s most-researched paradigm for reducing prejudice, has the ‘ironic’ effect of stifling support for social change in disadvantaged groups.
+We conducted a preregistered meta-analytic test of this effect across `r with(dplyr::distinct(readRDS("../data/dl.rds"), sample, id, n), numform::f_comma(dplyr::n_distinct(id)))` studies with `r with(dplyr::distinct(readRDS("../data/dl.rds"), sample, id, n), numform::f_comma(length(sample)))` samples of `r with(dplyr::distinct(readRDS("../data/dl.rds"), sample, id, n), numform::f_comma(sum(n)))` disadvantaged-group members.
+As predicted, intergroup contact was, on average, associated with less perceived injustice (`r with(readRDS("../results/results_preregistered_analyses.rds"), paste0("$r = ", numform::f_num(median(r_mean[x_var == "ic" & y_var == "pi"]), digits = 2), "$"))`), collective action (`r with(readRDS("../results/results_preregistered_analyses.rds"), paste0("$r = ", numform::f_num(median(r_mean[x_var == "ic" & y_var == "ca"]), digits = 2), "$"))`), and support for reparative policies (`r with(readRDS("../results/results_preregistered_analyses.rds"), paste0("$r = ", numform::f_num(median(r_mean[x_var == "ic" & y_var == "ps"]), digits = 2), "$"))`) in disadvantaged groups.
+However, these associations were small, variable, and consistent with alterative explanations.
+Moderator analyses found that these associations were strongest in studies on short-term migration and post-colonial relations, that measured intergroup contact directly, and that involved adults.
+After controlling for the positive association of negative contact with support for social change, positive contact was not (negatively) associated with any outcome in studies that measured both predictors.
+We close by highlighting open questions about the relation between intergroup contact and social change.
 output:
@@
   # Load packages
-  library(tidyverse); library(tidybayes); library(numform)
+  library(tidyverse); library(tidybayes); library(numform); library(glue)
 
@@
 
-As a growing number of studies had been examining these relationships, we conducted a preregistered meta-analytic review of the available evidence for the hypothesized negative effects of intergroup contact on perceived injustice, collective action, and policy support in disadvantaged groups.
-
+We conducted a preregistered meta-analysis of the evidence for the hypothesized negative effects of intergroup contact on perceived injustice, collective action, and policy support in disadvantaged groups.
 Our first objective was to systematically review the available evidence and to evaluate its strengths and limitations.
 Our second objective was to synthesize the available evidence to establish the direction and magnitude of the relationships between intergroup contact and the three outcomes.
-Doing so allows us, first, to determine whether the available evidence supports a negative or positive [see @pettigrew_recent_2011] relationship between contact and support for social change and, second, to estimate the strength of this relationship.
+Doing so allowed us, first, to determine whether the available evidence supports a negative or positive [see @pettigrew_recent_2011] relationship between contact and support for social change and, second, to estimate the strength of this relationship.
 Our third objective was to explore the variability of this relationship across study settings, designs, and other potential moderators.
@@
 Our fourth objective was to assess how robust the available evidence was to publication bias.
-Together, these objectives provided a comprehensive answer to the question whether intergroup contact diminishes support for social change in disadvantaged groups.
 
-In addition, we explored the evidence for two alternative accounts of this relationship.
+In addition, we collated the evidence for two alternative accounts of this relationship.
 First, we considered studies that measured both ingroup and outgroup contact as predictors of the three outcomes.
@@
 As outgroup contact places limits on how much ingroup contact disadvantaged-group members can have [@pfister_contact_2020], the mobilizing effect of ingroup contact is an alternative explanation for negative associations between outgroup contact and support for social change.
-
 Second, we considered studies that measured both negative and positive (outgroup) contact as predictors of the three outcomes.
@@
 @reimer_intergroup_2017 argued that, to the extent disadvantaged-group members who have more positive contact also tend to have less negative contact, the mobilizing effect of negative contact is an alternative explanation for negative associations between outgroup contact and support for social change.
-For both alternative explanations, we collate and synthesize the available evidence for the relative effects of each predictor variable on the three outcomes.
 
@@
 We prepared a protocol in accordance with the PRISMA-P statement [@moher_preferred_2015] and preregistered it on the Open Science Framework.^[[https://osf.io/ryuev/?view_only=8938ac6178914da98bdda1da4a6e27f0](https://osf.io/ryuev/?view_only=8938ac6178914da98bdda1da4a6e27f0)] Preregistration precludes undisclosed flexibility in study selection, outcome selection, and other decisions that influence effect size estimates—and thus prevents confirmation bias from determining the conclusions of a meta-analysis [@lakens_reproducibility_2016].
-We report all deviations from our protocol in the Supplemental Materials.
-We make all data and analysis scripts available online.^[[https://osf.io/w5tqv/?view_only=5cbf7ad5b2b449a7a0f4ada0337b802a](https://osf.io/w5tqv/?view_only=5cbf7ad5b2b449a7a0f4ada0337b802a)]
+We report deviations from our protocol in the Supplemental Materials.
+We make data and analysis scripts available online.^[[https://osf.io/w5tqv/?view_only=5cbf7ad5b2b449a7a0f4ada0337b802a](https://osf.io/w5tqv/?view_only=5cbf7ad5b2b449a7a0f4ada0337b802a)]
 
@@
 
+```{r, include = FALSE}
+
+  # Import data
+  dl <- read_rds("../data/dl.rds")
+  counts <- read_rds("../figures/figure-1.rds")
+
+```
+
 Figure 1 shows a flow diagram illustrating our search strategy, study selection, and data collection.
-Our preregistered search strategy returned 2,610 unique records from electronic databases.
-Of these, we excluded 2,379 (91\%) ineligible records after screening titles, abstracts, and keywords.
-Of the remaining 231 records, we excluded 116 (50\%) ineligible records after reviewing full-text manuscripts.
-We supplemented these records with 14 unpublished studies solicited from researchers and 6 records that cited at least three relevant works.
-Of 135 eligible studies, we had to exclude 39 (29\%) studies for which we could not extract or impute any relevant effect size.
+Our preregistered search strategy returned `r f_comma(counts$n_included[1])` unique records from electronic databases.
+Of these, we excluded `r f_comma(counts$n_excluded[2])` (`r f_comma(counts$p_excluded[2])`) ineligible records after screening titles, abstracts, and keywords.
+Of the remaining `r f_comma(counts$n_included[2])` records, we excluded `r f_comma(counts$n_excluded[3])` (`r f_comma(counts$p_excluded[3])`) ineligible records after reviewing full-text manuscripts.
+We supplemented these records with `r f_comma(with(read_csv("../records/results/unpublished-studies.csv"), n_distinct(id)))` unpublished studies solicited from researchers and `r f_comma(with(read_csv("../records/results/citing-studies.csv"), n_distinct(id)))` records that cited at least three relevant works.
+Of `r f_comma(with(read_csv("../records/results/unpublished-studies.csv"), n_distinct(id)) + with(read_csv("../records/results/citing-studies.csv"), n_distinct(id)) + counts$n_included[3])` eligible studies, we had to exclude `r f_comma(counts$n_excluded[4])` (`r f_comma(counts$p_excluded[4])`) studies for which we could not extract or impute any relevant effect size.
 At each stage, we also excluded studies that used the same data as another study.
-Our final sample comprised effect sizes from $J = 96$  studies spanning $N = 211,360$ participants in $I = 137$ samples.
+Our final sample comprised effect sizes from `r paste0("$J = ", with(dl, f_comma(n_distinct(id))), "$")` studies spanning `r paste0("$N = ", with(distinct(dl, id, sample, n), f_comma(sum(n))), "$")` participants in `r paste0("$I = ", f_comma(nrow(distinct(dl, id, sample))), "$")` samples.
 
 Figure 2 provides a qualitative overview of the literature.
-Even though most participants came from studies conducted in India ($N = 104,639$) and the United States ($N = 61,089$; Figure 2a), most samples were collected in North America ($I = 48$) and Europe ($I = 40$), with few samples from South America and Africa (Figure 2b).
-Most samples focused on relative inequalities that resulted from long-term migration ($I = 54$), slavery ($I = 19$), colonization ($I = 17$), and short-term migration ($I = 14$).
+Even though most participants came from studies conducted in India (`r glue('$N = {f_comma(with(distinct(dl, id, sample, n, country), sum(n[country == "India"])))}$')`) and the United States (`r glue('$N = {f_comma(with(distinct(dl, id, sample, n, country), sum(n[country == "USA"])))}$')`; Figure 2a), most samples were collected in North America (`r glue('$I = {f_comma(with(distinct(dl, id, sample, n, continent), length(sample[continent == "North America"])))}$')`) and Europe (`r glue('$I = {f_comma(with(distinct(dl, id, sample, n, continent), length(sample[continent == "Europe"])))}$')`), with few samples from South America and Africa (Figure 2b).
+Most samples focused on relative inequalities that resulted from long-term migration (`r glue('$I = {f_comma(with(distinct(dl, id, sample, study_setting), length(sample[study_setting == "Long-term migration"])))}$')`), slavery (`r glue('$I = {f_comma(with(distinct(dl, id, sample, study_setting), length(sample[study_setting == "Slavery"])))}$')`), colonization (`r glue('$I = {f_comma(with(distinct(dl, id, sample, study_setting), length(sample[study_setting == "Colonization"])))}$')`), and short-term migration (`r glue('$I = {f_comma(with(distinct(dl, id, sample, study_setting), length(sample[study_setting == "Short-term migration"])))}$')`).
 With few exceptions, studies used observational, cross-sectional survey designs.
-Samples sizes ranged from 64 to 49,764 ($\textit{Mdn} = 282$).
+Samples sizes ranged from `r with(distinct(dl, id, sample, n), paste0(f_comma(min(n)), " to ", f_comma(max(n)), " ($\\textit{Mdn} = ", f_comma(median(n)), "$)"))`.
 Unlike most psychological research, 2 in 5 samples used probability or representative sampling.
-Of all samples, 55\% ($I = 75$) were collected with the intention to examine the effects of intergroup contact on the outcomes considered in this meta-analysis.^[Many studies examined acculturation processes (Berry, 1997) and measured both intergroup contact and perceived injustice without the relationship between the two being of interest.] Together, these observations highlight both limitations and strengths of the empirical literature.
+Of all samples, `r with(distinct(dl, id, sample, study_intention), f_prop2percent(mean(study_intention == "Yes"), digits = 0))` (`r glue('$I = {f_comma(with(distinct(dl, id, sample, n, study_intention), length(sample[study_intention == "Yes"])))}$')`) were collected with the intention to examine the effects of intergroup contact on the outcomes considered in this meta-analysis.^[Many studies examined acculturation processes [@berry_immigration_1997] and measured both intergroup contact and perceived injustice without the relationship between the two being of interest.] Together, these observations highlight both limitations and strengths of the empirical literature.
 
@@
 This reflects the reduced power of the various methods to correct for meta-biases when sample sizes are small, effect sizes are heterogeneous, or publication bias is strong [@carter_correcting_2019].
-Therefore, there was insufficient evidence to conclude *either* that, after adjusting for publication bias, intergroup contact was not associated with support of social change in disadvantaged groups *or* that publication bias did not affect the relevant literature.
+Therefore, we did not find evidence for publication bias—but also did not find conclusive evidence against it.
 
@@
 We found that, based on the available evidence, the associations of intergroup contact with perceived injustice (`r with(summary, p_text[y_var == "pi"])`), collective action (`r with(summary, p_text[y_var == "ca"])`), and support for reparative policies (`r with(summary, p_text[y_var == "ps"])`) were, on average, much more likely to be negative than positive.
-Thus, our meta-analysis seems to support the emerging consensus that intergroup contact diminishes support for social change in disadvantaged groups.
+Thus, our meta-analysis seems to support the emerging consensus.
 We use the rest of this section to argue why this conclusion might be premature.
@@
 For example, even a small change in policy attitudes could, if it affects enough people, sway a tight election.
-Cumulative effects, however, should not be assumed without an empirical or theoretical rationale [@funder_evaluating_2019]—neither of which has been provided in the published literature.
+Cumulative effects, however, should not be assumed without an empirical or theoretical rationale [@funder_evaluating_2019].
 
@@
 
-```{=latex}
-\begin{figure}
-\centering
-\caption{Directed acyclic graphs for plausible causal relations between intergroup contact and support for social change}
-\includegraphics[scale=1]{../figures/figure-9}
-\caption*{\textit{Note.} IC = (Positive) Intergroup Contact, SC = Support for Social Change, U = Unobserved Variable(s), NC = Negative (Integroup) Contact, IN = Ingroup Contact}
-\label{fig:f9}
-\end{figure}
-```
-
-Third, the available evidence is almost entirely from cross-sectional, observational studies and thus consistent with alternative explanations for the observed associations (Figure 9).
-Support for social change could reduce intergroup contact (B) rather than the other way around (A).
+Third, the available evidence is almost entirely from cross-sectional, observational studies and thus consistent with alternative explanations for the observed associations.
+Support for social change could reduce intergroup contact rather than the other way around.
 For example, disadvantaged-group members involved in collective action might purposefully avoid forming friendships with advantaged-group members.
-Alternatively, the association between intergroup contact and support for social change could be spurious with both being caused by an unobserved confounder (C).
+Alternatively, the association between intergroup contact and support for social change could be spurious with both being caused by an unobserved confounder.
 For example, a disadvantaged-group member's socioeconomic status might both expose them to more advantaged-group members and reduce their perception of injustice.
@@
 
-Further, the observed association between intergroup contact and support for social change could be confounded by an alternative predictor that *increases* support for social change (D, E).
+Further, the observed association between intergroup contact and support for social change could be confounded by an alternative predictor that *increases* support for social change.
 Supporting Reimer et al.'s [-@reimer_intergroup_2017] argument, we found that positive intergroup contact was not associated with support for social change after controlling for negative contact which, in turn, was associated with *greater* support for social change.
 We found mixed evidence for ingroup contact as an alternative explanation for the 'ironic' effects of intergroup contact [@sengupta_ingroup_2015] but note that few studies measured both ingroup and outgroup contact.
-Going forward, researchers should clarify which aspects of intergroup contact they hypothesize to affect support for social change—and include measures that allow testing both the hypothesized and competing explanations.
+Going forward, researchers should clarify which aspects of intergroup contact should theoretically affect support for social change—and include measures that allow testing both the hypothesized and competing explanations.
 
@@
 Publication bias could have prevented studies that found positive or non-significant associations from entering the published literature.
-Even though we used state-of-the-art methods to detect and correct for publication bias, we did not find conclusive evidence for or against publication bias.
-That said, 61% of samples were *either* not collected with the intention to study the effects of intergroup contact on a relevant outcome (45%) *or* from unpublished studies (32%)—and thus unlikely to have been affected by publication bias.
+We used state-of-the-art methods to detect and correct for publication bias, yet did not find conclusive evidence for or against publication bias.
+That said, 61% of samples were either not collected with the intention to study the effects of intergroup contact on a relevant outcome (45%) or from unpublished studies (32%)—and thus unlikely to have been affected by publication bias.
 Another bias that could have affected our findings is that researchers made data-dependent decisions when analyzing data that inflate false-positive findings [@gelman_statistical_2014].

### 2021-04-16 manuscript/manuscript.tex
add abstract

@@
 
+\twocolumn[
+  \begin{@twocolumnfalse}
     \maketitle
+    \begin{abstract}
+    \noindent Critics have argued that intergroup contact, psychology's
+most-researched paradigm for reducing prejudice, has the `ironic' effect
+of stifling support for social change in disadvantaged groups. We
+conducted a preregistered meta-analytic test of this effect across 96
+studies with 137 samples of 211,360 disadvantaged-group members. As
+predicted, intergroup contact was, on average, associated with less
+perceived injustice (\(r = -.07\)), collective action (\(r = -.06\)),
+and support for reparative policies (\(r = -.07\)) in disadvantaged
+groups. However, these associations were small, variable, and consistent
+with alterative explanations. Moderator analyses found that these
+associations were strongest in studies on short-term migration and
+post-colonial relations, that measured intergroup contact directly, and
+that involved adults. After controlling for the positive association of
+negative contact with support for social change, positive contact was
+not (negatively) associated with any outcome in studies that measured
+both predictors. We close by highlighting open questions about the
+relation between intergroup contact and social change.
+    \end{abstract}
+  \end{@twocolumnfalse}
+]
 
@@
 
-As a growing number of studies had been examining these relationships,
-we conducted a preregistered meta-analytic review of the available
-evidence for the hypothesized negative effects of intergroup contact on
-perceived injustice, collective action, and policy support in
-disadvantaged groups.
-
-Our first objective was to systematically review the available evidence
-and to evaluate its strengths and limitations. Our second objective was
-to synthesize the available evidence to establish the direction and
-magnitude of the relationships between intergroup contact and the three
-outcomes. Doing so allows us, first, to determine whether the available
-evidence supports a negative or positive (see Pettigrew et al., 2011)
-relationship between contact and support for social change and, second,
-to estimate the strength of this relationship. Our third objective was
-to explore the variability of this relationship across study settings,
-designs, and other potential moderators. For example, we examined
-whether any effects were confined to Western, Educated, Industrialized,
-Rich, Democratic (WEIRD) settings, the cultural context of most
-psychological research (Henrich et al., 2010). Our fourth objective was
-to assess how robust the available evidence was to publication bias.
-Together, these objectives provided a comprehensive answer to the
-question whether intergroup contact diminishes support for social change
-in disadvantaged groups.
-
-In addition, we explored the evidence for two alternative accounts of
+We conducted a preregistered meta-analysis of the evidence for the
+hypothesized negative effects of intergroup contact on perceived
+injustice, collective action, and policy support in disadvantaged
+groups. Our first objective was to systematically review the available
+evidence and to evaluate its strengths and limitations. Our second
+objective was to synthesize the available evidence to establish the
+direction and magnitude of the relationships between intergroup contact
+and the three outcomes. Doing so allowed us, first, to determine whether
+the available evidence supports a negative or positive (see Pettigrew et
+al., 2011) relationship between contact and support for social change
+and, second, to estimate the strength of this relationship. Our third
+objective was to explore the variability of this relationship across
+study settings, designs, and other potential moderators. For example, we
+examined whether any effects were confined to Western, Educated,
+Industrialized, Rich, Democratic (WEIRD) settings, the cultural context
+of most psychological research (Henrich et al., 2010). Our fourth
+objective was to assess how robust the available evidence was to
+publication bias.
+
+In addition, we collated the evidence for two alternative accounts of
 this relationship. First, we considered studies that measured both
@@
 explanation for negative associations between outgroup contact and
-support for social change.
-
-Second, we considered studies that measured both negative and positive
-(outgroup) contact as predictors of the three outcomes. Researchers
-(Hayward et al., 2018; Reimer et al., 2017) found negative contact with
-advantaged-group members to be associated with greater perceived
-discrimination and stronger collective action intentions. Reimer et al.
-(2017) argued that, to the extent disadvantaged-group members who have
-more positive contact also tend to have less negative contact, the
-mobilizing effect of negative contact is an alternative explanation for
-negative associations between outgroup contact and support for social
-change. For both alternative explanations, we collate and synthesize the
-available evidence for the relative effects of each predictor variable
-on the three outcomes.
+support for social change. Second, we considered studies that measured
+both negative and positive (outgroup) contact as predictors of the three
+outcomes. Researchers (Hayward et al., 2018; Reimer et al., 2017) found
+negative contact with advantaged-group members to be associated with
+greater perceived discrimination and stronger collective action
+intentions. Reimer et al. (2017) argued that, to the extent
+disadvantaged-group members who have more positive contact also tend to
+have less negative contact, the mobilizing effect of negative contact is
+an alternative explanation for negative associations between outgroup
+contact and support for social change.
 
@@
 estimates---and thus prevents confirmation bias from determining the
-conclusions of a meta-analysis (Lakens et al., 2016). We report all
-deviations from our protocol in the Supplemental Materials. We make all
-data and analysis scripts available online.\footnote{\url{https://osf.io/w5tqv/?view_only=5cbf7ad5b2b449a7a0f4ada0337b802a}}
+conclusions of a meta-analysis (Lakens et al., 2016). We report
+deviations from our protocol in the Supplemental Materials. We make data
+and analysis scripts available online.\footnote{\url{https://osf.io/w5tqv/?view_only=5cbf7ad5b2b449a7a0f4ada0337b802a}}
 
@@
 researchers and 6 records that cited at least three relevant works. Of
-135 eligible studies, we had to exclude 39 (29\%) studies for which we
+135 eligible studies, we had to exclude 38 (28\%) studies for which we
 could not extract or impute any relevant effect size. At each stage, we
@@
 most participants came from studies conducted in India (\(N = 104,639\))
-and the United States (\(N = 61,089\); Figure 2a), most samples were
+and the United States (\(N = 60,983\); Figure 2a), most samples were
 collected in North America (\(I = 48\)) and Europe (\(I = 40\)), with
@@
 focused on relative inequalities that resulted from long-term migration
-(\(I = 54\)), slavery (\(I = 19\)), colonization (\(I = 17\)), and
+(\(I = 56\)), slavery (\(I = 19\)), colonization (\(I = 19\)), and
 short-term migration (\(I = 14\)). With few exceptions, studies used
@@
 meta-biases when sample sizes are small, effect sizes are heterogeneous,
-or publication bias is strong (Carter et al., 2019). Therefore, there
-was insufficient evidence to conclude \emph{either} that, after
-adjusting for publication bias, intergroup contact was not associated
-with support of social change in disadvantaged groups \emph{or} that
-publication bias did not affect the relevant literature.
+or publication bias is strong (Carter et al., 2019). Therefore, we did
+not find evidence for publication bias---but also did not find
+conclusive evidence against it.
 
@@
 to be negative than positive. Thus, our meta-analysis seems to support
-the emerging consensus that intergroup contact diminishes support for
-social change in disadvantaged groups. We use the rest of this section
-to argue why this conclusion might be premature.
+the emerging consensus. We use the rest of this section to argue why
+this conclusion might be premature.
 
@@
 election. Cumulative effects, however, should not be assumed without an
-empirical or theoretical rationale (Funder \& Ozer, 2019)---neither of
-which has been provided in the published literature.
+empirical or theoretical rationale (Funder \& Ozer, 2019).
 
@@
 
-\begin{figure}
-\centering
-\caption{Directed acyclic graphs for plausible causal relations between intergroup contact and support for social change}
-\includegraphics[scale=1]{../figures/figure-9}
-\caption*{\textit{Note.} IC = (Positive) Intergroup Contact, SC = Support for Social Change, U = Unobserved Variable(s), NC = Negative (Integroup) Contact, IN = Ingroup Contact}
-\label{fig:f9}
-\end{figure}
-
 Third, the available evidence is almost entirely from cross-sectional,
 observational studies and thus consistent with alternative explanations
-for the observed associations (Figure 9). Support for social change
-could reduce intergroup contact (B) rather than the other way around
-(A). For example, disadvantaged-group members involved in collective
-action might purposefully avoid forming friendships with
-advantaged-group members. Alternatively, the association between
-intergroup contact and support for social change could be spurious with
-both being caused by an unobserved confounder (C). For example, a
-disadvantaged-group member's socioeconomic status might both expose them
-to more advantaged-group members and reduce their perception of
-injustice. Future research should prioritize longitudinal studies to
-confirm the direction of the observed associations and (field)
-experiments to rule out confounding and other alternative
-explanations.\footnote{Published research includes only three
-  longitudinal studies (Koschate et al., 2012; Reimer et al., 2017;
-  Tropp et al., 2012), all of which conflated within-person change and
-  between-person stability (Hamaker et al., 2015), two experimental
+for the observed associations. Support for social change could reduce
+intergroup contact rather than the other way around. For example,
+disadvantaged-group members involved in collective action might
+purposefully avoid forming friendships with advantaged-group members.
+Alternatively, the association between intergroup contact and support
+for social change could be spurious with both being caused by an
+unobserved confounder. For example, a disadvantaged-group member's
+socioeconomic status might both expose them to more advantaged-group
+members and reduce their perception of injustice. Future research should
+prioritize longitudinal studies to confirm the direction of the observed
+associations and (field) experiments to rule out confounding and other
+alternative explanations.\footnote{Published research includes only
+  three longitudinal studies (Koschate et al., 2012; Reimer et al.,
+  2017; Tropp et al., 2012), all of which conflated within-person change
+  and between-person stability (Hamaker et al., 2015), two experimental
   studies with a no-contact control condition (Becker et al., 2013;
@@
 for social change could be confounded by an alternative predictor that
-\emph{increases} support for social change (D, E). Supporting Reimer et
-al.'s (2017) argument, we found that positive intergroup contact was not
+\emph{increases} support for social change. Supporting Reimer et al.'s
+(2017) argument, we found that positive intergroup contact was not
 associated with support for social change after controlling for negative
@@
 and outgroup contact. Going forward, researchers should clarify which
-aspects of intergroup contact they hypothesize to affect support for
+aspects of intergroup contact should theoretically affect support for
 social change---and include measures that allow testing both the
@@
 positive or non-significant associations from entering the published
-literature. Even though we used state-of-the-art methods to detect and
-correct for publication bias, we did not find conclusive evidence for or
-against publication bias. That said, 61\% of samples were \emph{either}
-not collected with the intention to study the effects of intergroup
-contact on a relevant outcome (45\%) \emph{or} from unpublished studies
-(32\%)---and thus unlikely to have been affected by publication bias.
-Another bias that could have affected our findings is that researchers
-made data-dependent decisions when analyzing data that inflate
-false-positive findings (Gelman \& Loken, 2014). Future research should
-use preregistration and other methods to prevent undisclosed flexibility
-in data collection and analysis.\footnote{To date, one preregistered
-  study has been published (Hässler et al., 2020).}
+literature. We used state-of-the-art methods to detect and correct for
+publication bias, yet did not find conclusive evidence for or against
+publication bias. That said, 61\% of samples were either not collected
+with the intention to study the effects of intergroup contact on a
+relevant outcome (45\%) or from unpublished studies (32\%)---and thus
+unlikely to have been affected by publication bias. Another bias that
+could have affected our findings is that researchers made data-dependent
+decisions when analyzing data that inflate false-positive findings
+(Gelman \& Loken, 2014). Future research should use preregistration and
+other methods to prevent undisclosed flexibility in data collection and
+analysis.\footnote{To date, one preregistered study has been published
+  (Hässler et al., 2020).}
 
@@
 
+\leavevmode\hypertarget{ref-berry_immigration_1997}{}%
+Berry, J. W. (1997). Immigration, acculturation, and adaptation.
+\emph{Applied Psychology}, \emph{46}(1), 5--34.
+\url{https://doi.org/10.1111/j.1464-0597.1997.tb01087.x}
+
 \leavevmode\hypertarget{ref-blumer_race_1958}{}%

### 2021-04-16 figures/figure-1.R

@@ -240,3 +240,6 @@ rm(list = ls())
     width = 6.5, height = 4.7, units = "in",
     dpi = 600
   )      
+  
+  # Export data (as .rds)
+  write_rds(counts, "figures/figure-1.rds")

### 2021-04-16 figures/figure-2.R

@@ -66,7 +66,7 @@ rm(list = ls())
       size = 9/.pt
     ) +
     scale_x_continuous(
-      labels = scales::percent,
+      labels = scales::percent_format(accuracy = 10),
       expand = c(0, 0)
     ) +
     scale_colour_identity() + 
@@ -123,7 +123,7 @@ rm(list = ls())
       size = 9/.pt
     ) +
     scale_x_continuous(
-      labels = scales::percent,
+      labels = scales::percent_format(accuracy = 10),
       expand = c(0, 0)
     ) +
     scale_colour_identity() + 
@@ -179,7 +179,7 @@ rm(list = ls())
       size = 9/.pt
     ) +
     scale_x_continuous(
-      labels = scales::percent,
+      labels = scales::percent_format(accuracy = 10),
       expand = c(0, 0)
     ) +
     scale_colour_identity() + 
@@ -234,7 +234,7 @@ rm(list = ls())
       size = 9/.pt
     ) +
     scale_x_continuous(
-      labels = scales::percent,
+      labels = scales::percent_format(accuracy = 10),
       expand = c(0, 0)
     ) +
     scale_colour_identity() + 

### 2021-04-16 scripts/prepare_data_for_analyses.R

@@ -199,6 +199,55 @@ rm(list = ls())
   # Arrange for export
   dl <- dl %>% arrange(id, sample, x, y)
   
+  # Code (missing) moderators (for now)
+  dl <- dl %>% 
+    mutate(
+      study_setting = case_when(
+        !is.na(study_setting) ~ study_setting,
+        id == 2395L & sample == 1L ~ "Colonization",
+        id == 2395L & sample == 2L ~ "Long-term migration",
+        id == 2396L & sample == 1L ~ "Other",
+        id == 2396L & sample == 2L ~ "Sexuality",
+        id == 2396L & sample == 3L ~ "Colonization",
+        id == 2397L & sample == 1L ~ "Long-term migration"
+      ),
+      ic_direct = case_when(
+        !is.na(ic_direct) ~ ic_direct,
+        id == 2395L & sample == 1L ~ "Directly",
+        id == 2395L & sample == 2L ~ "Directly",
+        id == 2396L & sample == 1L ~ "Directly",
+        id == 2396L & sample == 2L ~ "Directly",
+        id == 2396L & sample == 3L ~ "Directly",
+        id == 2397L & sample == 1L ~ "Directly"
+      ),
+      pi_specific = case_when(
+        !is.na(pi_specific) ~ pi_specific,
+        id == 2395L & sample == 1L & y == "gd" ~ "General",
+        id == 2395L & sample == 1L & y == "pd" ~ "General",
+        id == 2395L & sample == 1L & y == "rd" ~ "General",
+        id == 2395L & sample == 2L & y == "gd" ~ "General",
+        id == 2395L & sample == 2L & y == "pd" ~ "General",
+        id == 2395L & sample == 2L & y == "rd" ~ "General",
+        id == 2396L & sample == 1L & y == "pd" ~ "Specific",
+        id == 2396L & sample == 2L & y == "pd" ~ "Specific",
+        id == 2396L & sample == 3L & y == "pd" ~ "Specific",
+        id == 2397L & sample == 1L & y == "rd" ~ "Specific"
+      ),
+      pi_personal = case_when(
+        !is.na(pi_personal) ~ pi_personal,
+        id == 2395L & sample == 1L & y == "gd" ~ "Group",
+        id == 2395L & sample == 1L & y == "pd" ~ "Personal",
+        id == 2395L & sample == 1L & y == "rd" ~ "Group",
[…]

### 2021-04-16 scripts/run_moderator_analyses.R

@@ -29,55 +29,6 @@ rm(list = ls())
   # Import data
   dl <- read_rds("data/dl.rds")
   
-  # Code (missing) moderators (for now)
-  dl <- dl %>% 
-    mutate(
-      study_setting = case_when(
-        !is.na(study_setting) ~ study_setting,
-        id == 2395L & sample == 1L ~ "Colonization",
-        id == 2395L & sample == 2L ~ "Long-term migration",
-        id == 2396L & sample == 1L ~ "Other",
-        id == 2396L & sample == 2L ~ "Sexuality",
-        id == 2396L & sample == 3L ~ "Colonization",
-        id == 2397L & sample == 1L ~ "Long-term migration"
-      ),
-      ic_direct = case_when(
-        !is.na(ic_direct) ~ ic_direct,
-        id == 2395L & sample == 1L ~ "Directly",
-        id == 2395L & sample == 2L ~ "Directly",
-        id == 2396L & sample == 1L ~ "Directly",
-        id == 2396L & sample == 2L ~ "Directly",
-        id == 2396L & sample == 3L ~ "Directly",
-        id == 2397L & sample == 1L ~ "Directly"
-      ),
-      pi_specific = case_when(
-        !is.na(pi_specific) ~ pi_specific,
-        id == 2395L & sample == 1L & y == "gd" ~ "General",
-        id == 2395L & sample == 1L & y == "pd" ~ "General",
-        id == 2395L & sample == 1L & y == "rd" ~ "General",
-        id == 2395L & sample == 2L & y == "gd" ~ "General",
-        id == 2395L & sample == 2L & y == "pd" ~ "General",
-        id == 2395L & sample == 2L & y == "rd" ~ "General",
-        id == 2396L & sample == 1L & y == "pd" ~ "Specific",
-        id == 2396L & sample == 2L & y == "pd" ~ "Specific",
-        id == 2396L & sample == 3L & y == "pd" ~ "Specific",
-        id == 2397L & sample == 1L & y == "rd" ~ "Specific"
-      ),
-      pi_personal = case_when(
-        !is.na(pi_personal) ~ pi_personal,
-        id == 2395L & sample == 1L & y == "gd" ~ "Group",
-        id == 2395L & sample == 1L & y == "pd" ~ "Personal",
-        id == 2395L & sample == 1L & y == "rd" ~ "Group",
[…]

### 2021-04-20 manuscript/manuscript.Rmd
add statement of relevance

@@
 We close by highlighting open questions about the relation between intergroup contact and social change.
+statement: 
+  As societies are becoming more diverse, there are more opportunities for members of different groups to come in contact with each other.
+Psychologists disagree about what this means for overcoming persistent inequality between advantaged and disadvantaged groups.
+Some argue that intergroup contact reduces advantaged-group members' prejudice and, thereby, prevents interpersonal discrimination.
+Reducing prejudice, however, is rarely enough to overcome institutional and structural discrimination.
+Instead, social change often results from disadvantaged-group members mobilizing against social injustice (for example, in the 2020 Black Lives Matter protests).
+Critics argue that positive intergroup contact could create a false sense of equality and, thereby, stifle disadvantaged-group members' opposition to injustice.
+We present the first systematic review and meta-analysis of the growing number of studies examining how intergroup contact relates to support for social change in disadvantaged groups.
+Our findings help us understand whether, when, and how intergroup contact might hinder, rather than help, social change.
 output:
@@
 ```{=latex}
-\begin{figure*}[!t]
+\begin{figure*}[t!]
 \centering
@@
 
-### Potential Moderators
-
 ```{=latex}
@@
 ```
+
+### Potential Moderators
 
@@
 \end{figure*}
-
 \begin{figure*}

### 2021-04-20 manuscript/manuscript.tex
add statement of relevance

@@
 \usepackage[letterpaper, margin = 1in]{geometry}
+\setlength{\columnsep}{18pt}
 \setcounter{secnumdepth}{0}
-\usepackage{sectsty}
-\sectionfont{\centering}
-\usepackage{authblk}
-\renewcommand\Affilfont{\small}
+\usepackage[compact]{titlesec}  
+\titleformat*{\section}{\centering\normalfont\Large\bfseries}
+% \usepackage{authblk}
+% \renewcommand\Affilfont{\small}
 % \usepackage[hang, flushmargin]{footmisc}
-\setlength{\columnsep}{18pt}
+
+% Header
+% \usepackage{fancyhdr}
+% \pagestyle{fancy}
+% \rhead{\thepage}
+% \lhead{Meta-Analysis of the `Ironic' Effects of Intergroup Contact}
+% \cfoot{}
 
@@
   \end{@twocolumnfalse}
+  \renewcommand{\abstractname}{Statement of Relevance}
+  \begin{@twocolumnfalse}
+    \maketitle
+    \begin{abstract}
+    \noindent As societies are becoming more diverse, there are more opportunities for
+members of different groups to come in contact with each other.
+Psychologists disagree about what this means for overcoming persistent
+inequality between advantaged and disadvantaged groups. Some argue that
+intergroup contact reduces advantaged-group members' prejudice and,
+thereby, prevents interpersonal discrimination. Reducing prejudice,
+however, is rarely enough to overcome institutional and structural
+discrimination. Instead, social change often results from
+disadvantaged-group members mobilizing against social injustice (for
+example, in the 2020 Black Lives Matter protests). Critics argue that
+positive intergroup contact could create a false sense of equality and,
+thereby, stifle disadvantaged-group members' opposition to injustice. We
+present the first systematic review and meta-analysis of the growing
+number of studies examining how intergroup contact relates to support
+for social change in disadvantaged groups. Our findings help us
+understand whether, when, and how intergroup contact might hinder,
+rather than help, social change.
+    \end{abstract}
+  \end{@twocolumnfalse}
 ]
@@
 
-\begin{figure*}[!t]
+\begin{figure*}[t!]
 \centering
@@
 
-\hypertarget{potential-moderators}{%
-\subsubsection{Potential Moderators}\label{potential-moderators}}
-
 \begin{figure*}
@@
 \end{figure*}
+
+\hypertarget{potential-moderators}{%
+\subsubsection{Potential Moderators}\label{potential-moderators}}
 

### 2021-04-21 manuscript/manuscript.Rmd
update run_scripts.R

@@
 Psychologists disagree about what this means for overcoming persistent inequality between advantaged and disadvantaged groups.
-Some argue that intergroup contact reduces advantaged-group members' prejudice and, thereby, prevents interpersonal discrimination.
+Many argue that intergroup contact reduces advantaged-group members' prejudice and, thereby, prevents interpersonal discrimination.
 Reducing prejudice, however, is rarely enough to overcome institutional and structural discrimination.
@@
 We report deviations from our protocol in the Supplemental Materials.
-We make data and analysis scripts available online.^[[https://osf.io/w5tqv/?view_only=5cbf7ad5b2b449a7a0f4ada0337b802a](https://osf.io/w5tqv/?view_only=5cbf7ad5b2b449a7a0f4ada0337b802a)]
+We make data, analysis scripts, and the fully reproducible manuscript available online.^[[https://osf.io/w5tqv/?view_only=5cbf7ad5b2b449a7a0f4ada0337b802a](https://osf.io/w5tqv/?view_only=5cbf7ad5b2b449a7a0f4ada0337b802a)]
 

### 2021-04-21 manuscript/manuscript.tex
update run_scripts.R

@@
 Psychologists disagree about what this means for overcoming persistent
-inequality between advantaged and disadvantaged groups. Some argue that
+inequality between advantaged and disadvantaged groups. Many argue that
 intergroup contact reduces advantaged-group members' prejudice and,
@@
 conclusions of a meta-analysis (Lakens et al., 2016). We report
-deviations from our protocol in the Supplemental Materials. We make data
-and analysis scripts available online.\footnote{\url{https://osf.io/w5tqv/?view_only=5cbf7ad5b2b449a7a0f4ada0337b802a}}
+deviations from our protocol in the Supplemental Materials. We make
+data, analysis scripts, and the fully reproducible manuscript available
+online.\footnote{\url{https://osf.io/w5tqv/?view_only=5cbf7ad5b2b449a7a0f4ada0337b802a}}
 

### 2021-04-21 run_scripts.R

@@ -38,3 +38,40 @@ rm(list = ls())
 
   # Run preregistered robustness checks
   source("scripts/run_preregistered_robustness_checks.R")
+
+  # Run meta-regression moderator analyses
+  source("scripts/run_moderator_analyses.R")
+
+  # Run meta-regression tree moderator analyses
+  source("scripts/run_exploratory_moderator_analyses.R")
+  
+  # Run analyses with negative contact
+  source("scripts/run_analyses_with_negative_contact.R")
+
+  # Run analyses with ingroup contact
+  source("scripts/run_analyses_with_ingroup_contact.R")
+
+  # Run analyses to test and correct for publication bias
+  source("scripts/run_meta_bias_ingroup_contact.R")
+  
+
+# Visualize ---------------------------------------------------------------
+  
+  # Make figures
+  source("scripts/figure-1.R")
+  source("scripts/figure-2.R")
+  source("scripts/figure-3.R")
+  source("scripts/figure-4.R")
+  source("scripts/figure-5.R")
+  source("scripts/figure-6.R")
+  source("scripts/figure-7.R")
+  source("scripts/figure-8.R")
+
+
+# Combine -----------------------------------------------------------------
+
+  # Make manuscript
+  source("manuscript.Rmd")
+
+  # Make supplemental materials
+  source("supplemental-materials.Rmd")

### 2021-05-05 manuscript/manuscript.Rmd
add suplemental material

@@
 output:
+  word_document:
+    reference_docx: word-template.docx
   pdf_document:
@@
     template: preprint-template.tex
-  word_document:
-    reference_docx: word-template.docx
 ---
@@
 We prepared a protocol in accordance with the PRISMA-P statement [@moher_preferred_2015] and preregistered it on the Open Science Framework.^[[https://osf.io/ryuev/?view_only=8938ac6178914da98bdda1da4a6e27f0](https://osf.io/ryuev/?view_only=8938ac6178914da98bdda1da4a6e27f0)] Preregistration precludes undisclosed flexibility in study selection, outcome selection, and other decisions that influence effect size estimates—and thus prevents confirmation bias from determining the conclusions of a meta-analysis [@lakens_reproducibility_2016].
-We report deviations from our protocol in the Supplemental Materials.
+We report deviations from our protocol in the Supplemental Online Material (SOM-R).
 We make data, analysis scripts, and the fully reproducible manuscript available online.^[[https://osf.io/w5tqv/?view_only=5cbf7ad5b2b449a7a0f4ada0337b802a](https://osf.io/w5tqv/?view_only=5cbf7ad5b2b449a7a0f4ada0337b802a)]
@@
 We searched for gray literature in the *ProQuest Dissertations and Theses* database.
-We used similar non-exclusive search terms for all databases (see Supplemental Materials).
+We used similar non-exclusive search terms for all databases (see SOM-R).
 We searched databases on April 1, 2019 and again on April 1, 2020.
@@
 
-To find unpublished studies, we sent a call to the mailing lists of several professional organizations (see Supplemental Materials).
+To find unpublished studies, we sent a call to the mailing lists of several professional organizations (see SOM-R).
 We also advertised on social media and at relevant conferences.
@@
 \centering
-\caption{Posterior distributions from the preregistered random-effect meta-analysis models}
+\caption{Posterior distributions from the preregistered random-effects meta-analysis models}
 \includegraphics[scale=1]{../figures/figure-3}
@@
 
-In addition, we ran preregistered robustness checks which showed that our main analyses were robust to choosing different prior distributions and to excluding influential studies (see Supplemental Materials).
+In addition, we ran preregistered robustness checks which showed that our main analyses were robust to choosing different prior distributions and to excluding influential studies (see SOM-R).
 
@@
 We conducted two kinds of moderator analyses.
-For both analyses, we had an insufficient number of effect sizes to examine moderators for any outcomes except perceived injustice (for details, see Supplemental Materials).
+For both analyses, we had an insufficient number of effect sizes to examine moderators for any outcomes except perceived injustice (for details, see SOM-R).
 
@@
 \centering
-\caption{Posterior distributions from the random-effect meta-analysis models with alternative predictor variables}
+\caption{Posterior distributions from the random-effects meta-analysis models with alternative predictor variables}
 \includegraphics[scale=1]{../figures/figure-8}

### 2021-05-05 manuscript/manuscript.tex
add suplemental material

@@
 conclusions of a meta-analysis (Lakens et al., 2016). We report
-deviations from our protocol in the Supplemental Materials. We make
-data, analysis scripts, and the fully reproducible manuscript available
-online.\footnote{\url{https://osf.io/w5tqv/?view_only=5cbf7ad5b2b449a7a0f4ada0337b802a}}
+deviations from our protocol in the Supplemental Online Material
+(SOM-R). We make data, analysis scripts, and the fully reproducible
+manuscript available online.\footnote{\url{https://osf.io/w5tqv/?view_only=5cbf7ad5b2b449a7a0f4ada0337b802a}}
 
@@
 database. We used similar non-exclusive search terms for all databases
-(see Supplemental Materials). We searched databases on April 1, 2019 and
-again on April 1, 2020. We exported records and relevant metadata from
-each database. We removed duplicates using the \emph{revtools} package
-(Westgate, 2019).
+(see SOM-R). We searched databases on April 1, 2019 and again on April
+1, 2020. We exported records and relevant metadata from each database.
+We removed duplicates using the \emph{revtools} package (Westgate,
+2019).
 
 To find unpublished studies, we sent a call to the mailing lists of
-several professional organizations (see Supplemental Materials). We also
-advertised on social media and at relevant conferences. We directed
-researchers to an online survey in which they answered questions about
-the eligibility of their unpublished research and, if the research was
-eligible, provided data on moderator variables and effect sizes. We also
-contacted experts in the field, asking for unpublished research and
-other studies we might have missed.
+several professional organizations (see SOM-R). We also advertised on
+social media and at relevant conferences. We directed researchers to an
+online survey in which they answered questions about the eligibility of
+their unpublished research and, if the research was eligible, provided
+data on moderator variables and effect sizes. We also contacted experts
+in the field, asking for unpublished research and other studies we might
+have missed.
 
@@
 our main analyses were robust to choosing different prior distributions
-and to excluding influential studies (see Supplemental Materials).
+and to excluding influential studies (see SOM-R).
 
@@
 an insufficient number of effect sizes to examine moderators for any
-outcomes except perceived injustice (for details, see Supplemental
-Materials).
+outcomes except perceived injustice (for details, see SOM-R).
 

### 2021-05-05 manuscript/supplemental-materials.Rmd
add suplemental material

@@
 ---
-title: "Supplemental Materials"
+title: "Supplemental Online Materials"
+subtitle: "Meta-Analysis of the 'Ironic' Effects of Intergroup Contact"
 bibliography: references.bib
@@
     keep_tex: yes
-    template: custom-template.tex
+    template: som-template.tex
 ---
@@
 
-# Robustness Checks
+## Deviations
+
+We preregistered the eligibility criteria, search strategy, study selection, data collection, and preregistered analyses.
+Some details of the preregistered protocol proved unrealistic, impractical, or underspecified.
+Therefore, we deviated from the protocol in the following ways:
+
+1.
+We preregistered that we would update our search every four months until we would submit the manuscript.
+This proved unrealistic as the study selection and data collection process for the new studies took almost as long.
+Instead, we concluded our search of electronic databases on April 1, 2020—that is, before we started analyzing and documenting our findings.
+
+2.
+We preregistered that we would randomly select 100 records to be screened by both coders to calculate inter-rater agreement.
+We did not specify, however, what we would do if inter-rater agreement was less than acceptable.
+We decided to refine our coding strategy over three samples of 100 records until we achieved acceptable agreement.
+
+3.
+We preregistered that we would use *Google Scholar* to find records citing eligible studies.
+This proved impractical as *Google Scholar* does not facilitate the electronic export of citing records.
+Instead, we used the *Scopus* citation database.
+
+4.
+We preregistered that we would attempt to contact the authors of all papers with missing effect sizes.
+Instead, we decided to not contact authors for studies published before 2000 as we considered it unlikely that the authors still had access to the data.
+
+5.
+We preregistered that we would use a Bayesian two-level random-effects meta-analysis model, described in the main text, for all preregistered analyses.
+For the association between policy support and collective action, however, we had only few studies and found that the two-level model did not result in a reliable posterior distribution (as indicated by divergent transitions in the estimation algorithm).
+Instead, we used a Bayesian one-level random-effects model to estimate that association.
+
+## Search Strategy
+
+We used similar non-exclusive search terms for all electronic databases:
+
+1.
+(contact OR friendship) AND (“perceived discrimination” OR “perceived \*advantage” OR “relative deprivation” OR “group discrimination” OR “personal discrimination” OR “group deprivation” OR “perception\* of discrimination” OR “perception* of group discrimination” OR “perception* of personal discrimination” OR “rac\* discrimination”)
+
+2. \*group AND (contact OR friendship) AND (“collective action” OR protest OR “collective behavio\*r” OR “political behavio\*r” OR “social change” OR “social justice”)
+
+3.
+\*group AND (contact OR friendship) AND (policy OR policies OR “affirmative action” OR (politi* W/15 attitude\*) OR (politi\* W/15 preferenc\*)) AND (redistribut\* OR reparati\* OR inequalit\* OR equalit\* OR injustice\* OR justice\* OR disadvantage\* OR advantage\* OR minorit\* OR majorit\*)
+
+\noindent We sent a call for unpublished research to the mailing lists of the *European Association of Social Psychology*, the *Society for Personality and Social Psychology*, the *International Society of Political Psychology*, the *Society for the Psychological Study of Social Issues*, and the *Society of Australasian Social Psychologists*.
+
+## Robustness Checks
 
@@
 
+## Moderator Analyses
+
+First, we ran a series of Bayesian random-effects meta-regression models to estimate how much of the between-samples heterogeneity was explained by specific categorical moderator variables (`run_moderator_analyses.R`).
+Figures S1 and S2 show the results for collective action and policy support.
+Comparisons were inconclusive because we had an insufficient number of effect sizes per category.
+Second, we used meta-regression trees to discover interactions between moderator variables that best explained heterogeneity in effect sizes [@li_meta-cart_2017; @li_multiple_2020].
+As recommended, we ran random-effects meta-regression tree analyses using the look-ahead strategy [@li_multiple_2020].
+We set the pruning parameter to $c = 0$ because, for this analysis, we prioritized exploration over error control (`run_exploratory_moderator_analyses.R`).
+For both collective action and policy support, the algorithm found that no moderator or interaction of moderators explained between-samples heterogeneity.
+This results is not, however, surprising as both analyses used fewer than 40 effect sizes, the minimum number required for the algorithm to perform well in detecting even simple interaction effects [@li_meta-cart_2017].
+As both analyses were inconclusive for collective action and policy support, we only report results for perceived injustice in the main text.
+
+```{=latex}
+\begin{figure*}
+\centering
+\caption{Estimated effect sizes for the association between intergroup contact and collective action as a function of various categorical moderator variables}
+\includegraphics[scale=1]{../figures/figure-s1}
+\caption*{\textit{Note.} Intervals enclose the 95\% most plausible estimates of the category-specific effect size.
+Shaded ribbons enclose the 95\% most plausible estimates of the mean effect size from the main analyses.
+Percentages indicate the estimated between-sample variance explained by each moderator variable.}
+\label{fig:s1}
+\end{figure*}
+
+\begin{figure*}
+\centering
+\caption{Estimated effect sizes for the association between intergroup contact and policy support as a function of various categorical moderator variables}
+\includegraphics[scale=1]{../figures/figure-s2}
+\caption*{\textit{Note.} Intervals enclose the 95\% most plausible estimates of the category-specific effect size.
+Shaded ribbons enclose the 95\% most plausible estimates of the mean effect size from the main analyses.
+Percentages indicate the estimated between-sample variance explained by each moderator variable.}
+\label{fig:s2}
+\end{figure*}
+```
+
 # References

### 2021-05-05 manuscript/supplemental-materials.tex
add suplemental material

\documentclass[12pt, letterpaper]{article}

% Font
\usepackage[utf8]{inputenc}
\usepackage{MinionPro} 
\input{glyphtounicode}
\pdfgentounicode=1 
\usepackage{microtype}

% Format
\usepackage[letterpaper, margin = 1in]{geometry}
\setcounter{secnumdepth}{0}
\usepackage{titlesec}  
\titleformat*{\section}{\centering\normalfont\Large\bfseries}

% Links
\usepackage[colorlinks = true, linkcolor = black, urlcolor = black, citecolor = black]{hyperref}

% Figures
\usepackage{graphicx}
\usepackage[labelfont = bf, font = small, labelsep = newline, singlelinecheck = false]{caption}
\renewcommand{\thefigure}{S\arabic{figure}}

% Tables
\usepackage{booktabs}
\usepackage{tabularx}

% Frontmatter
\title{ Supplemental Online Materials:\\\textit{Meta-Analysis of the `Ironic' Effects of Intergroup Contact} }
\author{  }

\begin{document}

\maketitle

\hypertarget{deviations}{%
\subsection{Deviations}\label{deviations}}

We preregistered the eligibility criteria, search strategy, study
selection, data collection, and preregistered analyses. Some details of
the preregistered protocol proved unrealistic, impractical, or
underspecified. Therefore, we deviated from the protocol in the
following ways:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  We preregistered that we would update our search every four months
  until we would submit the manuscript. This proved unrealistic as the
  study selection and data collection process for the new studies took
  almost as long. Instead, we concluded our search of electronic
  databases on April 1, 2020---that is, before we started analyzing and
  documenting our findings.
\item
  We preregistered that we would randomly select 100 records to be
  screened by both coders to calculate inter-rater agreement. We did not
  specify, however, what we would do if inter-rater agreement was less
  than acceptable. We decided to refine our coding strategy over three
  samples of 100 records until we achieved acceptable agreement.
\item
  We preregistered that we would use \emph{Google Scholar} to find
  records citing eligible studies. This proved impractical as
  \emph{Google Scholar} does not facilitate the electronic export of
  citing records. Instead, we used the \emph{Scopus} citation database.
\item
  We preregistered that we would attempt to contact the authors of all
  papers with missing effect sizes. Instead, we decided to not contact
  authors for studies published before 2000 as we considered it unlikely
  that the authors still had access to the data.
\item
  We preregistered that we would use a Bayesian two-level random-effects
  meta-analysis model, described in the main text, for all preregistered
  analyses. For the association between policy support and collective
  action, however, we had only few studies and found that the two-level
  model did not result in a reliable posterior distribution (as
  indicated by divergent transitions in the estimation algorithm).
  Instead, we used a Bayesian one-level random-effects model to estimate
  that association.
\end{enumerate}

\hypertarget{search-strategy}{%
\subsection{Search Strategy}\label{search-strategy}}

We used similar non-exclusive search terms for all electronic databases:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  (contact OR friendship) AND (``perceived discrimination'' OR
  ``perceived *advantage'' OR ``relative deprivation'' OR ``group
  discrimination'' OR ``personal discrimination'' OR ``group
  deprivation'' OR ``perception* of discrimination'' OR ``perception* of
  group discrimination'' OR ``perception* of personal discrimination''
  OR ``rac* discrimination'')
\item
  *group AND (contact OR friendship) AND (``collective action'' OR
  protest OR ``collective behavio*r'' OR ``political behavio*r'' OR
  ``social change'' OR ``social justice'')
\item
  *group AND (contact OR friendship) AND (policy OR policies OR
  ``affirmative action'' OR (politi* W/15 attitude*) OR (politi* W/15
  preferenc*)) AND (redistribut* OR reparati* OR inequalit* OR equalit*
  OR injustice* OR justice* OR disadvantage* OR advantage* OR minorit*
  OR majorit*)
\end{enumerate}

\noindent We sent a call for unpublished research to the mailing lists
of the \emph{European Association of Social Psychology}, the
\emph{Society for Personality and Social Psychology}, the
\emph{International Society of Political Psychology}, the \emph{Society
for the Psychological Study of Social Issues}, and the \emph{Society of
Australasian Social Psychologists}.

\hypertarget{robustness-checks}{%
\subsection{Robustness Checks}\label{robustness-checks}}

As preregistered, we conducted two kinds of robustness checks. First, we
assessed to what extent our findings were sensitive to choosing
narrower, \(\mu \sim \text{Normal}(0, 0.1)\), or wider,
\(\mu \sim \text{Normal}(0, 1)\), prior distributions. Choosing narrower
or wider prior distribution did not affect mean effect size estimates
for perceived injustice (\(\Delta r = -.00, [-.05, .04]\) and
\(\Delta r = .00, [-.05, .05]\)), collective action
(\(\Delta r = -.01, [-.11, .09]\) and \(\Delta r = -.00, [-.10, .11]\)),
and policy support (\(\Delta r = -.01, [-.10, .08]\) and
\(\Delta r = .00, [-.09, .10]\)). Second, we assessed to what extent our
findings were sensitive to including or excluding influential studies by
repeating the preregistered analyses \(J\) times while leaving out one
of \(J\) studies each time and by calculating the mean absolute
difference (\emph{MAD}) for the estimated mean effect size across
left-out studies. For perceived injustice
(\(\textit{MAD} = .02, [.01, .04]\)), collective action
(\(\textit{MAD} = .04, [.02, .09]\)), and policy support
(\(\textit{MAD} = .03, [.02, .08]\)), the \emph{MAD} was small. Leaving
out the most influential study, for example, did not change estimates of
the mean effect size for the three outcomes
(\(\Delta r = .00, [-.04, .05]\); \(\Delta r = .02, [-.09, .12]\);
\(\Delta r = -.02, [-.11, .07]\)). Together, these analyses showed that
our findings were robust to choosing different prior distributions and
to excluding influential studies.

\hypertarget{moderator-analyses}{%
\subsection{Moderator Analyses}\label{moderator-analyses}}

First, we ran a series of Bayesian random-effects meta-regression models
to estimate how much of the between-samples heterogeneity was explained
by specific categorical moderator variables
(\texttt{run\_moderator\_analyses.R}). Figures S1 and S2 show the
results for collective action and policy support. Comparisons were
inconclusive because we had an insufficient number of effect sizes per
category. Second, we used meta-regression trees to discover interactions
between moderator variables that best explained heterogeneity in effect
sizes (Li et al., 2017, 2020). As recommended, we ran random-effects
meta-regression tree analyses using the look-ahead strategy (Li et al.,
2020). We set the pruning parameter to \(c = 0\) because, for this
analysis, we prioritized exploration over error control
(\texttt{run\_exploratory\_moderator\_analyses.R}). For both collective
action and policy support, the algorithm found that no moderator or
interaction of moderators explained between-samples heterogeneity. This
results is not, however, surprising as both analyses used fewer than 40
effect sizes, the minimum number required for the algorithm to perform
well in detecting even simple interaction effects (Li et al., 2017). As
both analyses were inconclusive for collective action and policy
support, we only report results for perceived injustice in the main
text.

\begin{figure*}
\centering
\caption{Estimated effect sizes for the association between intergroup contact and collective action as a function of various categorical moderator variables}
\includegraphics[scale=1]{../figures/figure-s1}
\caption*{\textit{Note.} Intervals enclose the 95\% most plausible estimates of the category-specific effect size. Shaded ribbons enclose the 95\% most plausible estimates of the mean effect size from the main analyses. Percentages indicate the estimated between-sample variance explained by each moderator variable.}
\label{fig:s1}
\end{figure*}

\begin{figure*}
\centering
\caption{Estimated effect sizes for the association between intergroup contact and policy support as a function of various categorical moderator variables}
\includegraphics[scale=1]{../figures/figure-s2}
\caption*{\textit{Note.} Intervals enclose the 95\% most plausible estimates of the category-specific effect size. Shaded ribbons enclose the 95\% most plausible estimates of the mean effect size from the main analyses. Percentages indicate the estimated between-sample variance explained by each moderator variable.}
\label{fig:s2}
\end{figure*}

\hypertarget{references}{%
\section{References}\label{references}}

\begingroup

\noindent \setlength{\parindent}{-0.5in} \setlength{\leftskip}{0.5in}

\hypertarget{refs}{}
\leavevmode\hypertarget{ref-li_meta-cart_2017}{}%
Li, X., Dusseldorp, E., \& Meulman, J. J. (2017). Meta-CART: A tool to
identify interactions between moderators in meta-analysis. \emph{British
Journal of Mathematical and Statistical Psychology}, \emph{70}(1),
118--136. \url{https://doi.org/10.1111/bmsp.12088}

\leavevmode\hypertarget{ref-li_multiple_2020}{}%
Li, X., Dusseldorp, E., Su, X., \& Meulman, J. J. (2020). Multiple
moderator meta-analysis using the R-package Meta-CART. \emph{Behavior
Research Methods}, \emph{52}(6), 2657--2673.
\url{https://doi.org/10.3758/s13428-020-01360-0}

\endgroup

\end{document}

### 2021-05-05 figures/figure-s1.R

@@ -1,0 +1,217 @@
+rm(list = ls())
+
+# Notes -------------------------------------------------------------------
+
+
+# Library -----------------------------------------------------------------
+
+  # Load packages
+  library(tidyverse); library(tidybayes); library(ggtext); 
+  library(patchwork); library(numform)
+
+  # Link functions
+  r_to_z <- function(r) 0.5 * log( (1 + r) / (1 - r) )
+  z_to_r <- function(z) ( exp(2 * z) - 1 ) / ( exp(2 * z) + 1 )
+  
+
+# Prepare -----------------------------------------------------------------
+  
+  # Import results from moderator analyses
+  results <- read_rds("results/results_categorical_moderator_analyses.rds")
+  
+  # Transform to long format
+  results <- results %>% 
+    transmute(
+      y_var, 
+      moderator,
+      draws = map2(
+        r_kk,
+        R2,
+        ~left_join(.x, .y, by = c(".chain", ".iteration", ".draw"))
+      )
+    ) %>% 
+    unnest(draws) %>% 
+    left_join(
+      results %>% 
+        transmute(y_var, moderator, es = map(es, ~count(., kk, name = "I"))) %>% 
+        unnest(es),
+      by = c("y_var", "moderator", "kk")
+    )
+  
+  # Name moderator and outcome variables
+  results <- results %>% 
+    mutate(
+      y_name = recode_factor(
+        y_var,
+        "pi" = "Perceived injustice",
+        "ca" = "Collective action",
+        "ps" = "Policy support"
+      ),
+      moderator = recode_factor(
+        moderator,
+        "study_setting" = "Study Setting",
+        "study_design" = "Study Design",
+        "study_sample" = "Study Sample",
+        "age" = "Age",
+        "study_intention" = "Study Intention",
+        "publication_status" = "Publication Status",
+        "ic_direct" = "Predictor (Direct/Indirect)",
+        "pi_specific" = "Outcome (Specific/General)",
+        "pi_personal" = "Outcome (Personal/Group)"
+      ),
+      category = recode(
+        category,
+        "quasi-experimental (no random assignment)" = "quasi-experimental",
+        "experimental (random assignment)" = "experimental",
+        "convenience sample" = "convenience",
[…]

### 2021-05-05 figures/figure-s2.R

@@ -1,0 +1,217 @@
+rm(list = ls())
+
+# Notes -------------------------------------------------------------------
+
+
+# Library -----------------------------------------------------------------
+
+  # Load packages
+  library(tidyverse); library(tidybayes); library(ggtext); 
+  library(patchwork); library(numform)
+
+  # Link functions
+  r_to_z <- function(r) 0.5 * log( (1 + r) / (1 - r) )
+  z_to_r <- function(z) ( exp(2 * z) - 1 ) / ( exp(2 * z) + 1 )
+  
+
+# Prepare -----------------------------------------------------------------
+  
+  # Import results from moderator analyses
+  results <- read_rds("results/results_categorical_moderator_analyses.rds")
+  
+  # Transform to long format
+  results <- results %>% 
+    transmute(
+      y_var, 
+      moderator,
+      draws = map2(
+        r_kk,
+        R2,
+        ~left_join(.x, .y, by = c(".chain", ".iteration", ".draw"))
+      )
+    ) %>% 
+    unnest(draws) %>% 
+    left_join(
+      results %>% 
+        transmute(y_var, moderator, es = map(es, ~count(., kk, name = "I"))) %>% 
+        unnest(es),
+      by = c("y_var", "moderator", "kk")
+    )
+  
+  # Name moderator and outcome variables
+  results <- results %>% 
+    mutate(
+      y_name = recode_factor(
+        y_var,
+        "pi" = "Perceived injustice",
+        "ca" = "Collective action",
+        "ps" = "Policy support"
+      ),
+      moderator = recode_factor(
+        moderator,
+        "study_setting" = "Study Setting",
+        "study_design" = "Study Design",
+        "study_sample" = "Study Sample",
+        "age" = "Age",
+        "study_intention" = "Study Intention",
+        "publication_status" = "Publication Status",
+        "ic_direct" = "Predictor (Direct/Indirect)",
+        "pi_specific" = "Outcome (Specific/General)",
+        "pi_personal" = "Outcome (Personal/Group)"
+      ),
+      category = recode(
+        category,
+        "quasi-experimental (no random assignment)" = "quasi-experimental",
+        "experimental (random assignment)" = "experimental",
+        "convenience sample" = "convenience",
[…]

### 2021-05-05 scripts/run_exploratory_moderator_analyses.R

@@ -213,6 +213,39 @@ rm(list = ls())
     ) %>% 
     select(.chain:.draw, kk, r = r_kk, n, R2, age:study_setting)
   
+  
+
+# Estimate (collective action) --------------------------------------------
+
+  # Set seed
+  set.seed(3242844)
+  
+  # Run random-effects meta-tree model
+  ca_tree <- REmrt(
+    z ~ ic_direct + study_setting + study_design + study_sample + age + study_intention + publication_status,
+    vi = vi,
+    data = es %>% filter(y_var == "ca"),
+    c = 0.0,
+    xval = nrow(es %>% filter(y_var == "ca")) - 1,
+    lookahead = TRUE
+  )
+  
+
+# Estimate (policy support) -----------------------------------------------
+
+  # Set seed
+  set.seed(1289771)
+  
+  # Run random-effects meta-tree model
+  ps_tree <- REmrt(
+    z ~ ic_direct + study_setting + study_design + study_sample + age + study_intention + publication_status,
+    vi = vi,
+    data = es %>% filter(y_var == "ps"),
+    c = 0.0,
+    xval = nrow(es %>% filter(y_var == "ps")) - 1,
+    lookahead = TRUE
+  )
+
 
 # Export ------------------------------------------------------------------
 

### 2021-05-05 manuscript/manuscript.Rmd
add APA Style template

@@
 title: "Meta-Analysis of the 'Ironic' Effects of Intergroup Contact"
+header: "'IRONIC' EFFECTS META-ANALYSIS"
+keywords: intergroup contact, meta-analysis, perceived discrimination, collective action, policy support, social change, social injustice 
 bibliography: references.bib
@@
 output:
-  word_document:
-    reference_docx: word-template.docx
   pdf_document:
@@
     keep_tex: yes
-    template: preprint-template.tex
+    template: apa-template.tex
+  word_document:
+    reference_docx: word-template.docx
 ---
@@
 
+\newpage
+
 # References

### 2021-05-05 manuscript/manuscript.tex
add APA Style template

@@
-\documentclass[twocolumn, 11pt, letterpaper]{article}
+\documentclass[12pt, letterpaper]{article}
 
@@
 \usepackage[utf8]{inputenc}
-\usepackage{MinionPro} 
-\input{glyphtounicode}
-\pdfgentounicode=1 
+\usepackage{amsmath}
 \usepackage{microtype}
@@
 \usepackage[letterpaper, margin = 1in]{geometry}
-\setlength{\columnsep}{18pt}
 \setcounter{secnumdepth}{0}
+\setlength{\parindent}{0.5in}
 \usepackage[compact]{titlesec}  
-\titleformat*{\section}{\centering\normalfont\Large\bfseries}
-% \usepackage{authblk}
-% \renewcommand\Affilfont{\small}
-% \usepackage[hang, flushmargin]{footmisc}
+\titleformat*{\section}{\centering\normalfont\normalsize\bfseries}
+\titleformat*{\subsection}{\raggedright\normalfont\normalsize\bfseries}
+\titleformat*{\subsubsection}{\raggedright\normalfont\normalsize\bfseries\itshape}
+\usepackage{indentfirst}
+\usepackage[hang,flushmargin]{footmisc}
 
 % Header
-% \usepackage{fancyhdr}
-% \pagestyle{fancy}
-% \rhead{\thepage}
-% \lhead{Meta-Analysis of the `Ironic' Effects of Intergroup Contact}
-% \cfoot{}
+\usepackage{fancyhdr}
+\pagestyle{fancy}
+\fancyhf{}
+\setlength{\headheight}{14.5pt}
+\renewcommand{\headrulewidth}{0pt}
+\fancyhead[L]{`IRONIC' EFFECTS META-ANALYSIS}
+\fancyhead[R]{\thepage}
 
@@
 
-% Frontmatter
-\title{ Meta-Analysis of the `Ironic' Effects of Intergroup Contact }
-\author{  }
+% Line spacing
+\usepackage[doublespacing]{setspace}
 
@@
 
-\twocolumn[
-  \begin{@twocolumnfalse}
-    \maketitle
-    \begin{abstract}
+\section{Abstract}
+
 \noindent Critics have argued that intergroup contact, psychology's
@@
 relation between intergroup contact and social change.
-    \end{abstract}
-  \end{@twocolumnfalse}
-  \renewcommand{\abstractname}{Statement of Relevance}
-  \begin{@twocolumnfalse}
-    \maketitle
-    \begin{abstract}
+
+\textit{Keywords:} intergroup contact, meta-analysis, perceived discrimination, collective
+action, policy support, social change, social injustice
+
+\newpage
+
+\section{Statement of Relevance}
+
 \noindent As societies are becoming more diverse, there are more opportunities for
@@
 rather than help, social change.
-    \end{abstract}
-  \end{@twocolumnfalse}
-]
-
-\noindent It is ironic that psychology's most-researched paradigm for reducing
+
+\newpage
+
+\section{Meta-Analysis of the `Ironic' Effects of Intergroup Contact}
+
+It is ironic that psychology's most-researched paradigm for reducing
 prejudice---intergroup contact---should hinder, rather than help, social
@@
 
+\newpage
+
 \hypertarget{references}{%

### 2021-05-05 manuscript/supplemental-materials.Rmd
add APA Style template

@@
 title: "Supplemental Online Materials"
-subtitle: "Meta-Analysis of the 'Ironic' Effects of Intergroup Contact"
+subtitle: Meta-Analysis of the 'Ironic' Effects of Intergroup Contact
 bibliography: references.bib
-csl: apa.csl
 output:
+  word_document: default
   pdf_document:
@@
     template: som-template.tex
+csl: apa.csl
 ---
@@
 We preregistered the eligibility criteria, search strategy, study selection, data collection, and preregistered analyses.
-Some details of the preregistered protocol proved unrealistic, impractical, or underspecified.
+Some aspects of the preregistered protocol proved unrealistic, impractical, or underspecified.
 Therefore, we deviated from the protocol in the following ways:
@@
 For both collective action and policy support, the algorithm found that no moderator or interaction of moderators explained between-samples heterogeneity.
-This results is not, however, surprising as both analyses used fewer than 40 effect sizes, the minimum number required for the algorithm to perform well in detecting even simple interaction effects [@li_meta-cart_2017].
-As both analyses were inconclusive for collective action and policy support, we only report results for perceived injustice in the main text.
+This result is not surprising, however, as both analyses used fewer than 40 effect sizes, the minimum number required for the algorithm to perform well in detecting even simple interaction effects [@li_meta-cart_2017].
+As both moderator analyses were inconclusive for collective action and policy support, we only report results for perceived injustice in the main text.
 

### 2021-05-05 manuscript/supplemental-materials.tex
add APA Style template

@@
 We preregistered the eligibility criteria, search strategy, study
-selection, data collection, and preregistered analyses. Some details of
+selection, data collection, and preregistered analyses. Some aspects of
 the preregistered protocol proved unrealistic, impractical, or
@@
 interaction of moderators explained between-samples heterogeneity. This
-results is not, however, surprising as both analyses used fewer than 40
+result is not surprising, however, as both analyses used fewer than 40
 effect sizes, the minimum number required for the algorithm to perform
 well in detecting even simple interaction effects (Li et al., 2017). As
-both analyses were inconclusive for collective action and policy
-support, we only report results for perceived injustice in the main
-text.
+both moderator analyses were inconclusive for collective action and
+policy support, we only report results for perceived injustice in the
+main text.
 

### 2021-05-05 scripts/run_exploratory_moderator_analyses.R

@@ -29,55 +29,6 @@ rm(list = ls())
   # Import data
   dl <- read_rds("data/dl.rds")
   
-  # Code (missing) moderators (for now)
-  dl <- dl %>% 
-    mutate(
-      study_setting = case_when(
-        !is.na(study_setting) ~ study_setting,
-        id == 2395L & sample == 1L ~ "Colonization",
-        id == 2395L & sample == 2L ~ "Long-term migration",
-        id == 2396L & sample == 1L ~ "Other",
-        id == 2396L & sample == 2L ~ "Sexuality",
-        id == 2396L & sample == 3L ~ "Colonization",
-        id == 2397L & sample == 1L ~ "Long-term migration"
-      ),
-      ic_direct = case_when(
-        !is.na(ic_direct) ~ ic_direct,
-        id == 2395L & sample == 1L ~ "Directly",
-        id == 2395L & sample == 2L ~ "Directly",
-        id == 2396L & sample == 1L ~ "Directly",
-        id == 2396L & sample == 2L ~ "Directly",
-        id == 2396L & sample == 3L ~ "Directly",
-        id == 2397L & sample == 1L ~ "Directly"
-      ),
-      pi_specific = case_when(
-        !is.na(pi_specific) ~ pi_specific,
-        id == 2395L & sample == 1L & y == "gd" ~ "General",
-        id == 2395L & sample == 1L & y == "pd" ~ "General",
-        id == 2395L & sample == 1L & y == "rd" ~ "General",
-        id == 2395L & sample == 2L & y == "gd" ~ "General",
-        id == 2395L & sample == 2L & y == "pd" ~ "General",
-        id == 2395L & sample == 2L & y == "rd" ~ "General",
-        id == 2396L & sample == 1L & y == "pd" ~ "Specific",
-        id == 2396L & sample == 2L & y == "pd" ~ "Specific",
-        id == 2396L & sample == 3L & y == "pd" ~ "Specific",
-        id == 2397L & sample == 1L & y == "rd" ~ "Specific"
-      ),
-      pi_personal = case_when(
-        !is.na(pi_personal) ~ pi_personal,
-        id == 2395L & sample == 1L & y == "gd" ~ "Group",
-        id == 2395L & sample == 1L & y == "pd" ~ "Personal",
-        id == 2395L & sample == 1L & y == "rd" ~ "Group",
[…]

### 2021-05-06 records/list-of-records.tex
add list of studies

\documentclass[10pt, letterpaper]{article}

% Font
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{MinionPro} 
\input{glyphtounicode}
\pdfgentounicode=1 
\usepackage{microtype}

% Format
\usepackage[letterpaper, margin = 1in]{geometry}
\setcounter{secnumdepth}{0}
\usepackage{sectsty}
\sectionfont{\centering}
\usepackage{lscape}

% Links
\usepackage[colorlinks = true, linkcolor = black, urlcolor = black, citecolor = black]{hyperref}

% Figures
\usepackage{graphicx}
\usepackage[labelfont = bf, labelsep = newline, singlelinecheck = false]{caption}

% Tables
\usepackage{booktabs}
\usepackage{xltabular}

% References
\usepackage[style=apa]{biblatex}
\addbibresource{references.bib}

\begin{document}

\begin{landscape}

\small

\begin{xltabular}{650pt}{Xrrrllrlllll}

	\caption{List of samples/studies for perceived injustice \label{tab:pi}}\\
 \toprule
	Study &  & $N$ & $r$ & Design & Sample & Age & Continent & Country & Setting & Published & Intended \\
 \midrule
 \endfirsthead

 \toprule
	Study &  & $N$ & $r$ & Design & Sample & Age & Continent & Country & Setting & Published & Intended \\
 \midrule
 \endhead

 \bottomrule
 \endfoot

 \bottomrule\addlinespace
 \multicolumn{12}{p{650pt}}{\textit{Note.} Age: > 18 = Sample consisted of adults (> 18 years). > 18 = Sample included adolescents/children (< 18 years). Setting: L.-T. Migration = Long-Term Migration, S.-T. Migration = Short-Term Migration. Published: Has the study been published? Intended: Was the study conducted with the intention to examine the effects of intergroup contact on one or more of the three outcome measures?}
 \endlastfoot

 \cite{2395} & 1 & 132 & -.03 & Cross-Sectional & Convenience & > 18 & Asia & Turkey & Post-Colonial & No & No\\
 & 2 & 188 & -.14 & Cross-Sectional & Probability & > 18 & Europe & UK & L.-T. Migration & No & No\\
\cite{322} & 1 & 151 & -.25 & Cross-Sectional & Students & > 18 & Asia & Turkey & Post-Colonial & Yes & Yes\\
\cite{2257} & 1 & 269 & -.06 & Cross-Sectional & Convenience & > 18 & Asia & Turkey & Other & Yes & No\\
\cite{423} & 1 & 64 & .19 & Cross-Sectional & Convenience & > 18 & Europe & UK & L.-T. Migration & Yes & Yes\\
 & 2 & 67 & -.00 & Cross-Sectional & Convenience & > 18 & Asia & Turkey & Post-Colonial & Yes & Yes\\
 & 3 & 210 & -.08 & Cross-Sectional & Convenience & > 18 & Asia & Turkey & Post-Colonial & Yes & Yes\\
\cite{2396} & 1 & 290 & -.11 & Cross-Sectional & Convenience & > 18 & Asia & Turkey & Other & Yes & No\\
 & 2 & 381 & -.05 & Cross-Sectional & Convenience & > 18 & Asia & Turkey & Sexuality & Yes & No\\
 & 3 & 191 & -.07 & Cross-Sectional & Convenience & > 18 & Asia & Turkey & Post-Colonial & Yes & No\\
\cite{2023} & 1 & 247 & .05 & Cross-Sectional & Students & < 18 & Europe & UK & L.-T. Migration & No & No\\
 & 2 & 118 & -.04 & Cross-Sectional & Students & < 18 & Europe & UK & L.-T. Migration & No & No\\
\cite{1045} & 1 & 252 & .11 & Cross-Sectional & Students & < 18 & N. America & USA & L.-T. Migration & Yes & No\\
\cite{2397} & 1 & 501 & .13 & Cross-Sectional & Probability & > 18 & Europe & UK & L.-T. Migration & No & Yes\\
\cite{284} & 1 & 488 & -.26 & Cross-Sectional & Students & > 18 & Africa & S. Africa & Post-Colonial & Yes & Yes\\
\cite{1248} & 1 & 209 & -.31 & Cross-Sectional & Convenience & > 18 & Asia & Turkey & Post-Colonial & Yes & Yes\\
\cite{1914} & 1 & 216 & -.35 & Cross-Sectional & Students & > 18 & S. America & Argentina & S.-T. Migration & Yes & No\\
\cite{480} & 1 & 407 & -.11 & Cross-Sectional & Students & < 18 & S. America & Costa Rica & Post-Slavery & Yes & No\\
\cite{1614} & 1 & 320 & -.27 & Cross-Sectional & Students & > 18 & Asia & Turkey & Post-Colonial & Yes & Yes\\
\cite{3205} & 1 & 602 & -.11 & Cross-Sectional & Probability & > 18 & Europe & Romania & Other & Yes & Yes\\
\cite{91} & 1 & 284 & .07 & Cross-Sectional & Students & > 18 & N. America & USA & S.-T. Migration & No & Yes\\
\cite{1163} & 1 & 116 & .44 & Cross-Sectional & Students & > 18 & N. America & USA & Post-Slavery & No & Yes\\
\cite{783} & 1 & 869 & .02 & Cross-Sectional & Probability & > 18 & Europe & Netherlands & L.-T. Migration & Yes & No\\
 & 2 & 859 & -.03 & Cross-Sectional & Probability & > 18 & Europe & Netherlands & L.-T. Migration & Yes & No\\
\cite{3196} & 1 & 165 & .23 & Cross-Sectional & Students & < 18 & Europe & Italy & L.-T. Migration & Yes & Yes\\
\cite{1807} & 1 & 2,775 & -.07 & Cross-Sectional & Probability & > 18 & Europe & Netherlands & L.-T. Migration & Yes & Yes\\
\cite{336} & 1 & 596 & -.22 & Cross-Sectional & Probability & > 18 & Africa & S. Africa & Post-Colonial & Yes & Yes\\
\cite{2033} & 1 & 203 & -.01 & Experimental & Students & > 18 & N. America & Canada & L.-T. Migration & Yes & Yes\\
\cite{4001} & 1 & 239 & .07 & Cross-Sectional & Students & > 18 & S. America & Mexico & Other & Yes & No\\
\cite{325} & 1 & 1,100 & -.25 & Cross-Sectional & Probability & > 18 & N. America & USA & Other & Yes & No\\
\cite{1576} & 1 & 1,503 & .22 & Cross-Sectional & Probability & > 18 & N. America & USA & L.-T. Migration & Yes & Yes\\
\cite{1949} & 1 & 94 & -.06 & Cross-Sectional & Convenience & < 18 & Europe & Germany & L.-T. Migration & Yes & No\\
\cite{4003} & 1 & 116 & -.33 & Cross-Sectional & Convenience & > 18 & N. America & USA & Post-Slavery & Yes & Yes\\
\cite{2309} & 1 & 195 & -.04 & Cross-Sectional & Convenience & > 18 & N. America & USA & Post-Slavery & Yes & Yes\\
 & 2 & 170 & -.28 & Cross-Sectional & Convenience & > 18 & N. America & USA & L.-T. Migration & Yes & Yes\\
\cite{1407} & 1 & 2,137 & .10 & Cross-Sectional & Probability & > 18 & N. America & USA & Post-Slavery & No & Yes\\
 & 2 & 695 & .10 & Cross-Sectional & Probability & > 18 & N. America & USA & L.-T. Migration & No & Yes\\
\cite{1494} & 3 & 237 & .02 & Cross-Sectional & Probability & > 18 & N. America & USA & Post-Slavery & No & No\\
 & 4 & 235 & .01 & Cross-Sectional & Probability & > 18 & N. America & USA & L.-T. Migration & No & No\\
\cite{324} & 1 & 353 & .06 & Cross-Sectional & Probability & < 18 & N. America & USA & Post-Slavery & Yes & No\\
 & 2 & 508 & .07 & Cross-Sectional & Probability & < 18 & N. America & USA & L.-T. Migration & Yes & No\\
\cite{609} & 1 & 182 & -.32 & Cross-Sectional & Convenience & > 18 & Asia & Hong Kong & L.-T. Migration & Yes & No\\
\cite{2001} & 1 & 42,445 & .07 & Cross-Sectional & Convenience & > 18 & N. America & USA & Post-Slavery & Yes & Yes\\
\cite{2341} & 1 & 141 & -.41 & Cross-Sectional & Convenience & > 18 & Europe & Finland & L.-T. Migration & Yes & No\\
\cite{19} & 1 & 585 & -.33 & Cross-Sectional & Students & > 18 & Asia & Singapore & S.-T. Migration & Yes & No\\
\cite{303} & 1 & 114 & -.18 & Cross-Sectional & Convenience & > 18 & Multiple & Multiple & Post-Colonial & No & No\\
\cite{856} & 1 & 187 & .19 & Cross-Sectional & Students & < 18 & Europe & Macedonia & Other & Yes & Yes\\
\cite{1411} & 1 & 531 & -.14 & Cross-Sectional & Probability & > 18 & Asia & Indonesia & Religion & Yes & No\\
\cite{4002} & 1 & 1,251 & .05 & Cross-Sectional & Probability & < 18 & Europe & Belgium & L.-T. Migration & Yes & No\\
\cite{1525} & 1 & 169 & -.16 & Cross-Sectional & Probability & < 18 & N. America & USA & L.-T. Migration & Yes & Yes\\
\cite{830} & 1 & 219 & -.03 & Cross-Sectional & Students & < 18 & N. America & USA & L.-T. Migration & No & No\\
 & 2 & 160 & -.08 & Cross-Sectional & Probability & < 18 & N. America & USA & L.-T. Migration & No & No\\
 & 3 & 155 & .09 & Cross-Sectional & Probability & < 18 & N. America & USA & L.-T. Migration & No & No\\
\cite{401} & 1 & 653 & -.00 & Longitudinal & Probability & < 18 & Europe & Germany & Other & Yes & Yes\\
\cite{45} & 1 & 161 & -.16 & Cross-Sectional & Students & > 18 & Europe & Germany & S.-T. Migration & Yes & Yes\\
 & 2 & 139 & -.23 & Cross-Sectional & Students & > 18 & Europe & UK & S.-T. Migration & Yes & Yes\\
 & 3 & 79 & .15 & Cross-Sectional & Convenience & > 18 & Europe & Germany & S.-T. Migration & Yes & Yes\\
\cite{1993} & 1 & 106 & -.16 & Cross-Sectional & Convenience & > 18 & Asia & Singapore & S.-T. Migration & Yes & No\\
\cite{3134} & 1 & 1,172 & -.07 & Cross-Sectional & Probability & < 18 & Europe & Germany & L.-T. Migration & Yes & No\\
 & 2 & 864 & -.06 & Cross-Sectional & Probability & < 18 & Europe & Netherlands & L.-T. Migration & Yes & No\\
 & 3 & 774 & -.05 & Cross-Sectional & Probability & < 18 & Europe & Sweden & L.-T. Migration & Yes & No\\
\cite{1042} & 1 & 165 & .19 & Cross-Sectional & Students & > 18 & N. America & USA & L.-T. Migration & Yes & Yes\\
 & 2 & 92 & -.03 & Cross-Sectional & Students & > 18 & N. America & USA & Post-Slavery & Yes & Yes\\
\cite{4000} & 1 & 121 & -.24 & Cross-Sectional & Convenience & > 18 & Europe & Germany & L.-T. Migration & Yes & Yes\\
\cite{893} & 1 & 410 & .07 & Cross-Sectional & Probability & > 18 & Europe & UK & Religion & Yes & Yes\\
\cite{3005} & 1 & 93 & -.18 & Cross-Sectional & Students & > 18 & Europe & Norway & L.-T. Migration & Yes & No\\
\cite{1850} & 1 & 110 & .04 & Cross-Sectional & Convenience & > 18 & Europe & Russia & L.-T. Migration & No & No\\
\cite{823} & 1 & 612 & -.15 & Cross-Sectional & Students & > 18 & N. America & USA & S.-T. Migration & Yes & No\\
\cite{1762} & 1 & 191 & .14 & Cross-Sectional & Convenience & < 18 & N. America & Canada & Post-Colonial & Yes & Yes\\
\cite{2391} & 1 & 400 & -.03 & Longitudinal & Convenience & > 18 & Europe & Italy & L.-T. Migration & No & Yes\\
\cite{3051} & 1 & 1,211 & -.07 & Cross-Sectional & Probability & > 18 & Europe & Denmark & L.-T. Migration & Yes & No\\
\cite{956} & 1 & 233 & -.24 & Cross-Sectional & Students & > 18 & Europe & UK & Sexuality & Yes & Yes\\
 & 2 & 433 & -.09 & Longitudinal & Students & > 18 & Multiple & Multiple & Sexuality & Yes & Yes\\
\cite{2380} & 1 & 76 & -.13 & Cross-Sectional & Students & > 18 & Asia & India & Caste & No & Yes\\
 & 2 & 127 & -.00 & Cross-Sectional & Students & > 18 & Asia & India & Caste & No & Yes\\
\cite{803} & 1 & 429 & -.12 & Cross-Sectional & Probability & > 18 & N. America & USA & L.-T. Migration & Yes & Yes\\
\cite{703} & 1 & 68 & .04 & Cross-Sectional & Students & < 18 & N. America & USA & Post-Slavery & Yes & Yes\\
\cite{244} & 1 & 129 & .04 & Cross-Sectional & Students & < 18 & N. America & USA & Post-Slavery & Yes & Yes\\
\cite{2333} & 1 & 1,337 & .02 & Cross-Sectional & Students & > 18 & N. America & USA & L.-T. Migration & No & Yes\\
\cite{4005} & 1 & 74 & -.34 & Cross-Sectional & Students & > 18 & Asia & Israel & L.-T. Migration & Yes & Yes\\
\cite{813} & 2 & 175 & -.22 & Cross-Sectional & Students & > 18 & Asia & Israel & Post-Colonial & Yes & Yes\\
\cite{2382} & 1 & 751 & -.02 & Longitudinal & Probability & < 18 & Europe & UK & L.-T. Migration & No & Yes\\
\cite{1695} & 1 & 1,008 & -.02 & Cross-Sectional & Probability & > 18 & Oceania & NZ & Post-Colonial & Yes & Yes\\
\cite{2381} & 1 & 1,977 & -.10 & Longitudinal & Probability & > 18 & Oceania & NZ & Post-Colonial & No & No\\
 & 2 & 526 & -.02 & Longitudinal & Probability & > 18 & Oceania & NZ & L.-T. Migration & No & No\\
 & 3 & 684 & -.03 & Longitudinal & Probability & > 18 & Oceania & NZ & L.-T. Migration & No & No\\
\cite{2385} & 1 & 4,708 & .02 & Cross-Sectional & Probability & > 18 & Asia & India & Religion & No & Yes\\
\cite{2392} & 1 & 13,646 & -.11 & Cross-Sectional & Probability & > 18 & Asia & India & Caste & No & Yes\\
 & 2 & 1,526 & -.21 & Cross-Sectional & Probability & > 18 & Asia & India & Religion & No & Yes\\
 & 2 & 49,764 & -.10 & Cross-Sectional & Probability & > 18 & Asia & India & Caste & No & Yes\\
 & 3 & 935 & -.19 & Cross-Sectional & Probability & > 18 & Asia & India & Religion & No & Yes\\
 & 3 & 33,137 & -.08 & Cross-Sectional & Probability & > 18 & Asia & India & Caste & No & Yes\\
 & 4 & 271 & -.22 & Cross-Sectional & Probability & > 18 & Asia & India & Religion & No & Yes\\
\cite{1891} & 1 & 753 & -.11 & Cross-Sectional & Students & > 18 & N. America & USA & L.-T. Migration & No & No\\
\cite{789} & 1 & 281 & .04 & Quasi-Experimental & Students & < 18 & Asia & Israel & Post-Colonial & Yes & Yes\\
\cite{3060} & 1 & 385 & .00 & Cross-Sectional & Convenience & > 18 & N. America & USA & Post-Slavery & Yes & No\\
\cite{733} & 1 & 249 & -.38 & Cross-Sectional & Students & > 18 & Europe & UK & S.-T. Migration & Yes & No\\
\cite{1020} & 1 & 81 & -.75 & Cross-Sectional & Students & > 18 & Europe & UK & S.-T. Migration & Yes & No\\
 & 2 & 110 & -.03 & Cross-Sectional & Students & > 18 & Europe & UK & S.-T. Migration & Yes & No\\
\cite{2375} & 1 & 112 & -.06 & Cross-Sectional & Students & > 18 & N. America & USA & L.-T. Migration & Yes & Yes\\
\cite{46} & 1 & 1,445 & -.08 & Cross-Sectional & Probability & < 18 & Europe & Belgium & S.-T. Migration & Yes & No\\
\cite{1412} & 1 & 3,958 & -.03 & Cross-Sectional & Probability & > 18 & Europe & Denmark & L.-T. Migration & Yes & No\\
\cite{1966} & 1 & 506 & .00 & Cross-Sectional & Convenience & < 18 & Europe & Germany & L.-T. Migration & Yes & No\\
 & 1 & 506 & -.04 & Cross-Sectional & Convenience & < 18 & Europe & Germany & L.-T. Migration & Yes & No\\
 & 2 & 506 & -.07 & Cross-Sectional & Convenience & < 18 & Asia & Israel & L.-T. Migration & Yes & No\\
 & 2 & 506 & -.12 & Cross-Sectional & Convenience & < 18 & Asia & Israel & L.-T. Migration & Yes & No\\
\cite{1221} & 1 & 313 & -.00 & Cross-Sectional & Probability & < 18 & N. America & USA & L.-T. Migration & No & No\\
 & 2 & 918 & .07 & Cross-Sectional & Probability & < 18 & N. America & USA & Post-Slavery & No & No\\
 & 3 & 118 & .08 & Cross-Sectional & Probability & < 18 & N. America & USA & Post-Colonial & No & No\\
 & 4 & 150 & -.07 & Cross-Sectional & Probability & < 18 & N. America & USA & L.-T. Migration & No & No\\
\cite{1743} & 1 & 72 & -.29 & Longitudinal & Students & > 18 & N. America & USA & Post-Slavery & Yes & Yes\\
 & 2 & 282 & -.11 & Longitudinal & Students & > 18 & N. America & USA & L.-T. Migration & Yes & Yes\\
 & 3 & 417 & .05 & Longitudinal & Students & > 18 & N. America & USA & L.-T. Migration & Yes & Yes\\
\cite{1658} & 1 & 502 & -.25 & Cross-Sectional & Probability & > 18 & N. America & USA & Post-Slavery & Yes & No\\
 & 2 & 500 & -.26 & Cross-Sectional & Probability & > 18 & N. America & USA & L.-T. Migration & Yes & No\\
 & 3 & 501 & -.20 & Cross-Sectional & Probability & > 18 & N. America & USA & L.-T. Migration & Yes & No\\
\cite{933} & 1 & 709 & .06 & Cross-Sectional & Probability & > 18 & N. America & USA & Post-Slavery & Yes & Yes\\
\cite{2394} & 1 & 201 & -.10 & Cross-Sectional & Convenience & > 18 & N. America & USA & L.-T. Migration & No & Yes\\
 & 2 & 209 & .08 & Cross-Sectional & Convenience & > 18 & N. America & USA & Post-Slavery & No & Yes\\
\cite{829} & 1 & 736 & .03 & Cross-Sectional & Students & < 18 & Multiple & Multiple & L.-T. Migration & Yes & No\\
\cite{2383} & 1 & 466 & -.07 & Cross-Sectional & Students & < 18 & Europe & UK & L.-T. Migration & No & No\\
 & 2 & 161 & -.04 & Cross-Sectional & Students & < 18 & Europe & UK & L.-T. Migration & No & No\\
 & 3 & 86 & .06 & Cross-Sectional & Students & < 18 & Europe & UK & Other & No & No\\
\cite{1395} & 1 & 726 & -.09 & Cross-Sectional & Students & > 18 & Asia & Hong Kong & S.-T. Migration & Yes & No\\
\cite{3000} & 1 & 2,201 & -.11 & Cross-Sectional & Students & > 18 & Asia & Hong Kong & S.-T. Migration & Yes & No\\

\end{xltabular}

\newpage

\begin{xltabular}{650pt}{Xrrrllrlllll}

	\caption{List of samples/studies for collective action \label{tab:ca}}\\
 \toprule
	Study &  & $N$ & $r$ & Design & Sample & Age & Continent & Country & Setting & Published & Intended \\
 \midrule
 \endfirsthead

 \toprule
	Study &  & $N$ & $r$ & Design & Sample & Age & Continent & Country & Setting & Published & Intended \\
 \midrule
 \endhead

 \bottomrule
 \endfoot

 \bottomrule\addlinespace
 \multicolumn{12}{p{650pt}}{\textit{Note.} Age: > 18 = Sample consisted of adults (> 18 years). > 18 = Sample included adolescents/children (< 18 years). Setting: L.-T. Migration = Long-Term Migration, S.-T. Migration = Short-Term Migration. Published: Has the study been published? Intended: Was the study conducted with the intention to examine the effects of intergroup contact on one or more of the three outcome measures?}
  \endlastfoot

  \cite{3201} & 1 & 159 & -.19 & Cross-Sectional & Convenience & > 18 & Asia & Palestine & Post-Colonial & Yes & Yes\\
\cite{322} & 1 & 151 & -.10 & Cross-Sectional & Students & > 18 & Asia & Turkey & Post-Colonial & Yes & Yes\\
\cite{414} & 1 & 269 & .31 & Cross-Sectional & Convenience & > 18 & Asia & Turkey & Other & Yes & Yes\\
\cite{2075} & 1 & 81 & -.35 & Experimental & Students & > 18 & N. America & Canada & Other & Yes & Yes\\
\cite{2397} & 1 & 501 & .05 & Cross-Sectional & Probability & > 18 & Europe & UK & L.-T. Migration & No & Yes\\
\cite{284} & 1 & 488 & -.29 & Cross-Sectional & Students & > 18 & Africa & S. Africa & Post-Colonial & Yes & Yes\\
\cite{1248} & 1 & 209 & -.13 & Cross-Sectional & Convenience & > 18 & Asia & Turkey & Post-Colonial & Yes & Yes\\
\cite{3196} & 1 & 165 & .20 & Cross-Sectional & Students & < 18 & Europe & Italy & L.-T. Migration & Yes & Yes\\
\cite{93} & 1 & 449 & .15 & Cross-Sectional & Students & > 18 & Asia & India & Religion & Yes & Yes\\
\cite{2033} & 1 & 203 & .05 & Experimental & Students & > 18 & N. America & Canada & L.-T. Migration & Yes & Yes\\
\cite{3054} & 1 & 1,000 & -.04 & Cross-Sectional & Convenience & > 18 & Multiple & Multiple & Multiple & Yes & Yes\\
 & 11 & 3,883 & -.09 & Cross-Sectional & Convenience & > 18 & Multiple & Multiple & Sexuality & Yes & Yes\\
\cite{2309} & 1 & 195 & .08 & Cross-Sectional & Convenience & > 18 & N. America & USA & Post-Slavery & Yes & Yes\\
 & 2 & 170 & -.03 & Cross-Sectional & Convenience & > 18 & N. America & USA & L.-T. Migration & Yes & Yes\\
\cite{894} & 1 & 176 & -.12 & Cross-Sectional & Students & > 18 & N. America & USA & L.-T. Migration & No & Yes\\
 & 2 & 126 & -.10 & Cross-Sectional & Students & > 18 & N. America & USA & Post-Slavery & No & Yes\\
\cite{1376} & 1 & 85 & -.30 & Cross-Sectional & Students & > 18 & Europe & UK & Religion & Yes & Yes\\
\cite{4004} & 1 & 320 & .16 & Cross-Sectional & Convenience & < 18 & Europe & Bulgaria & Other & Yes & Yes\\
\cite{2391} & 1 & 400 & .04 & Longitudinal & Convenience & > 18 & Europe & Italy & L.-T. Migration & No & Yes\\
\cite{956} & 1 & 233 & -.03 & Cross-Sectional & Students & > 18 & Europe & UK & Sexuality & Yes & Yes\\
 & 2 & 433 & .05 & Longitudinal & Students & > 18 & Multiple & Multiple & Sexuality & Yes & Yes\\
\cite{1114} & 1 & 581 & -.28 & Cross-Sectional & Probability & > 18 & Asia & Lebanon & L.-T. Migration & Yes & Yes\\
\cite{2382} & 1 & 751 & -.22 & Longitudinal & Probability & < 18 & Europe & UK & L.-T. Migration & No & Yes\\
\cite{2381} & 1 & 1,977 & -.06 & Longitudinal & Probability & > 18 & Oceania & NZ & Post-Colonial & No & No\\
 & 2 & 526 & .00 & Longitudinal & Probability & > 18 & Oceania & NZ & L.-T. Migration & No & No\\
 & 3 & 684 & .02 & Longitudinal & Probability & > 18 & Oceania & NZ & L.-T. Migration & No & No\\
\cite{2385} & 1 & 4,708 & .03 & Cross-Sectional & Probability & > 18 & Asia & India & Religion & No & Yes\\
\cite{2392} & 1 & 13,646 & -.03 & Cross-Sectional & Probability & > 18 & Asia & India & Caste & No & Yes\\
 & 2 & 1,526 & -.28 & Cross-Sectional & Probability & > 18 & Asia & India & Religion & No & Yes\\
 & 2 & 49,764 & -.02 & Cross-Sectional & Probability & > 18 & Asia & India & Caste & No & Yes\\
 & 3 & 935 & -.02 & Cross-Sectional & Probability & > 18 & Asia & India & Religion & No & Yes\\
 & 3 & 33,137 & -.03 & Cross-Sectional & Probability & > 18 & Asia & India & Caste & No & Yes\\
 & 4 & 271 & .08 & Cross-Sectional & Probability & > 18 & Asia & India & Religion & No & Yes\\
\cite{2375} & 1 & 112 & -.23 & Cross-Sectional & Students & > 18 & N. America & USA & L.-T. Migration & Yes & Yes\\
\cite{1743} & 1 & 72 & -.12 & Longitudinal & Students & > 18 & N. America & USA & Post-Slavery & Yes & Yes\\
 & 2 & 282 & -.17 & Longitudinal & Students & > 18 & N. America & USA & L.-T. Migration & Yes & Yes\\
 & 3 & 417 & .03 & Longitudinal & Students & > 18 & N. America & USA & L.-T. Migration & Yes & Yes\\

\end{xltabular}

\newpage

\begin{xltabular}{650pt}{Xrrrllrlllll}

	\caption{List of samples/studies for policy support \label{tab:ps}}\\
 \toprule
	Study &  & $N$ & $r$ & Design & Sample & Age & Continent & Country & Setting & Published & Intended \\
 \midrule
 \endfirsthead

 \toprule
	Study &  & $N$ & $r$ & Design & Sample & Age & Continent & Country & Setting & Published & Intended \\
 \midrule
 \endhead

 \bottomrule
 \endfoot

 \bottomrule\addlinespace
 \multicolumn{12}{p{650pt}}{\textit{Note.} Age: > 18 = Sample consisted of adults (> 18 years). > 18 = Sample included adolescents/children (< 18 years). Setting: L.-T. Migration = Long-Term Migration, S.-T. Migration = Short-Term Migration. Published: Has the study been published? Intended: Was the study conducted with the intention to examine the effects of intergroup contact on one or more of the three outcome measures?}
 \endlastfoot

 \cite{284} & 1 & 488 & -.27 & Cross-Sectional & Students & > 18 & Africa & S. Africa & Post-Colonial & Yes & Yes\\
\cite{1614} & 1 & 320 & -.23 & Cross-Sectional & Students & > 18 & Asia & Turkey & Post-Colonial & Yes & Yes\\
\cite{3205} & 1 & 602 & -.09 & Cross-Sectional & Probability & > 18 & Europe & Romania & Other & Yes & Yes\\
\cite{1386} & 1 & 1,556 & -.09 & Cross-Sectional & Probability & > 18 & Africa & S. Africa & Post-Colonial & Yes & Yes\\
\cite{1549} & 1 & 658 & -.09 & Cross-Sectional & Probability & > 18 & N. America & USA & Post-Slavery & No & Yes\\
\cite{3054} & 1 & 1,000 & -.01 & Cross-Sectional & Convenience & > 18 & Multiple & Multiple & Multiple & Yes & Yes\\
 & 11 & 3,883 & -.09 & Cross-Sectional & Convenience & > 18 & Multiple & Multiple & Sexuality & Yes & Yes\\
\cite{856} & 1 & 187 & .06 & Cross-Sectional & Students & < 18 & Europe & Macedonia & Other & Yes & Yes\\
\cite{1042} & 1 & 165 & .17 & Cross-Sectional & Students & > 18 & N. America & USA & L.-T. Migration & Yes & Yes\\
 & 2 & 92 & .10 & Cross-Sectional & Students & > 18 & N. America & USA & Post-Slavery & Yes & Yes\\
\cite{2380} & 1 & 76 & -.10 & Cross-Sectional & Students & > 18 & Asia & India & Caste & No & Yes\\
 & 2 & 127 & -.04 & Cross-Sectional & Students & > 18 & Asia & India & Caste & No & Yes\\
\cite{4005} & 1 & 74 & -.24 & Cross-Sectional & Students & > 18 & Asia & Israel & L.-T. Migration & Yes & Yes\\
\cite{813} & 2 & 175 & .00 & Cross-Sectional & Students & > 18 & Asia & Israel & Post-Colonial & Yes & Yes\\
\cite{1695} & 1 & 1,008 & .03 & Cross-Sectional & Probability & > 18 & Oceania & NZ & Post-Colonial & Yes & Yes\\
\cite{2381} & 1 & 1,977 & -.02 & Longitudinal & Probability & > 18 & Oceania & NZ & Post-Colonial & No & No\\
 & 2 & 526 & -.00 & Longitudinal & Probability & > 18 & Oceania & NZ & L.-T. Migration & No & No\\
 & 3 & 684 & -.00 & Longitudinal & Probability & > 18 & Oceania & NZ & L.-T. Migration & No & No\\
\cite{286} & 1 & 105 & -.14 & Cross-Sectional & Convenience & > 18 & Asia & Turkey & Post-Colonial & Yes & Yes\\

\end{xltabular}

\end{landscape}

\printbibliography

\end{document}

### 2021-05-06 scripts/prepare_data_for_analyses.R

@@ -1,14 +1,7 @@
 rm(list = ls())
 
 # Notes -------------------------------------------------------------------
-  
-  #########################################################################
-  # 414 (1) and 2257 are likely duplicates—but have different measures.   # 
-  #########################################################################
 
-  #########################################################################
-  # Something is wrong with 2381's entry which contains ps double.        #
-  #########################################################################
 
 # Library -----------------------------------------------------------------
 
@@ -199,7 +192,7 @@ rm(list = ls())
   # Arrange for export
   dl <- dl %>% arrange(id, sample, x, y)
   
-  # Code (missing) moderators (for now)
+  # Code missing moderators (for unpublished data)
   dl <- dl %>% 
     mutate(
       study_setting = case_when(

### 2021-05-07 manuscript/manuscript.Rmd
add list of studies
add unpublished study

@@
 
-## Transparency
+## Open Practices Statement
 
@@
 ***Study Setting.*** For each sample, we recorded in what country (or countries) the data was collected ($\kappa = .97$) and what the disadvantaged ingroup and the advantaged outgroup were.
-We categorized each sample’s setting according to whether the source of the groups’ relative inequality was long-term migration (e.g., Asian Americans), short-term  migration (e.g., international students), slavery (e.g., Black Americans), colonization (e.g., Māori, Black South Africans), religion, caste, sexuality, or another distinction ($\kappa = .84$).
+We categorized each sample’s setting according to whether the source of the groups’ relative inequality was long-term migration (e.g., Asian Americans), short-term  migration (e.g., international students), slavery (e.g., Black Americans), colonization (e.g., Māori, Black South Africans), religion, caste, sexuality, or another distinction ($\kappa = .85$).
 
@@
 
-***Outcome Variables.*** For each measure of perceived injustice, we coded whether it refered to specific instances of discrimination, to a more general perception of discrimination, or to both ($\kappa = .67$) and whether it assessed personal discrimination, group discrimination, or both ($\kappa = .83$).
+***Outcome Variables.*** For each measure of perceived injustice, we coded whether it refered to specific instances of discrimination, to a more general perception of discrimination, or to both ($\kappa = .67$) and whether it assessed personal discrimination, group discrimination, or both ($\kappa = .84$).
 
@@
 ```{=latex}
-\begin{figure*}
+\begin{figure*}[t!]
 \centering

### 2021-05-07 records/list-of-records.tex
add unpublished study

@@
 \cite{2397} & 1 & 501 & .13 & Cross-Sectional & Probability & > 18 & Europe & UK & L.-T. Migration & No & Yes\\
+\cite{2398} & 1 & 829 & -.03 & Longitudinal & Students & < 18 & Europe & UK & L.-T. Migration & No & No\\
 \cite{284} & 1 & 488 & -.26 & Cross-Sectional & Students & > 18 & Africa & S. Africa & Post-Colonial & Yes & Yes\\
@@
  & 2 & 695 & .10 & Cross-Sectional & Probability & > 18 & N. America & USA & L.-T. Migration & No & Yes\\
-\cite{1494} & 3 & 237 & .02 & Cross-Sectional & Probability & > 18 & N. America & USA & Post-Slavery & No & No\\
- & 4 & 235 & .01 & Cross-Sectional & Probability & > 18 & N. America & USA & L.-T. Migration & No & No\\
+\cite{1494} & 1 & 237 & .02 & Cross-Sectional & Probability & > 18 & N. America & USA & Post-Slavery & No & No\\
+ & 2 & 235 & .01 & Cross-Sectional & Probability & > 18 & N. America & USA & L.-T. Migration & No & No\\
 \cite{324} & 1 & 353 & .06 & Cross-Sectional & Probability & < 18 & N. America & USA & Post-Slavery & Yes & No\\
@@
 \cite{4005} & 1 & 74 & -.34 & Cross-Sectional & Students & > 18 & Asia & Israel & L.-T. Migration & Yes & Yes\\
-\cite{813} & 2 & 175 & -.22 & Cross-Sectional & Students & > 18 & Asia & Israel & Post-Colonial & Yes & Yes\\
+\cite{813} & 1 & 175 & -.22 & Cross-Sectional & Students & > 18 & Asia & Israel & Post-Colonial & Yes & Yes\\
 \cite{2382} & 1 & 751 & -.02 & Longitudinal & Probability & < 18 & Europe & UK & L.-T. Migration & No & Yes\\
@@
 \cite{2385} & 1 & 4,708 & .02 & Cross-Sectional & Probability & > 18 & Asia & India & Religion & No & Yes\\
+ & 2 & 1,526 & -.21 & Cross-Sectional & Probability & > 18 & Asia & India & Religion & No & Yes\\
+ & 3 & 935 & -.19 & Cross-Sectional & Probability & > 18 & Asia & India & Religion & No & Yes\\
+ & 4 & 271 & -.22 & Cross-Sectional & Probability & > 18 & Asia & India & Religion & No & Yes\\
 \cite{2392} & 1 & 13,646 & -.11 & Cross-Sectional & Probability & > 18 & Asia & India & Caste & No & Yes\\
- & 2 & 1,526 & -.21 & Cross-Sectional & Probability & > 18 & Asia & India & Religion & No & Yes\\
  & 2 & 49,764 & -.10 & Cross-Sectional & Probability & > 18 & Asia & India & Caste & No & Yes\\
- & 3 & 935 & -.19 & Cross-Sectional & Probability & > 18 & Asia & India & Religion & No & Yes\\
  & 3 & 33,137 & -.08 & Cross-Sectional & Probability & > 18 & Asia & India & Caste & No & Yes\\
- & 4 & 271 & -.22 & Cross-Sectional & Probability & > 18 & Asia & India & Religion & No & Yes\\
 \cite{1891} & 1 & 753 & -.11 & Cross-Sectional & Students & > 18 & N. America & USA & L.-T. Migration & No & No\\
@@
 \cite{1412} & 1 & 3,958 & -.03 & Cross-Sectional & Probability & > 18 & Europe & Denmark & L.-T. Migration & Yes & No\\
-\cite{1966} & 1 & 506 & .00 & Cross-Sectional & Convenience & < 18 & Europe & Germany & L.-T. Migration & Yes & No\\
- & 1 & 506 & -.04 & Cross-Sectional & Convenience & < 18 & Europe & Germany & L.-T. Migration & Yes & No\\
- & 2 & 506 & -.07 & Cross-Sectional & Convenience & < 18 & Asia & Israel & L.-T. Migration & Yes & No\\
- & 2 & 506 & -.12 & Cross-Sectional & Convenience & < 18 & Asia & Israel & L.-T. Migration & Yes & No\\
+\cite{1966} & 1 & 506 & -.01 & Cross-Sectional & Convenience & < 18 & Europe & Germany & L.-T. Migration & Yes & No\\
+ & 2 & 506 & -.09 & Cross-Sectional & Convenience & < 18 & Asia & Israel & L.-T. Migration & Yes & No\\
 \cite{1221} & 1 & 313 & -.00 & Cross-Sectional & Probability & < 18 & N. America & USA & L.-T. Migration & No & No\\
@@
 \cite{3000} & 1 & 2,201 & -.11 & Cross-Sectional & Students & > 18 & Asia & Hong Kong & S.-T. Migration & Yes & No\\
-
 \end{xltabular}
@@
 \cite{3054} & 1 & 1,000 & -.04 & Cross-Sectional & Convenience & > 18 & Multiple & Multiple & Multiple & Yes & Yes\\
- & 11 & 3,883 & -.09 & Cross-Sectional & Convenience & > 18 & Multiple & Multiple & Sexuality & Yes & Yes\\
+ & 2 & 3,883 & -.09 & Cross-Sectional & Convenience & > 18 & Multiple & Multiple & Sexuality & Yes & Yes\\
 \cite{2309} & 1 & 195 & .08 & Cross-Sectional & Convenience & > 18 & N. America & USA & Post-Slavery & Yes & Yes\\
@@
 \cite{2385} & 1 & 4,708 & .03 & Cross-Sectional & Probability & > 18 & Asia & India & Religion & No & Yes\\
+ & 2 & 1,526 & -.28 & Cross-Sectional & Probability & > 18 & Asia & India & Religion & No & Yes\\
+ & 3 & 935 & -.02 & Cross-Sectional & Probability & > 18 & Asia & India & Religion & No & Yes\\
+ & 4 & 271 & .08 & Cross-Sectional & Probability & > 18 & Asia & India & Religion & No & Yes\\
 \cite{2392} & 1 & 13,646 & -.03 & Cross-Sectional & Probability & > 18 & Asia & India & Caste & No & Yes\\
- & 2 & 1,526 & -.28 & Cross-Sectional & Probability & > 18 & Asia & India & Religion & No & Yes\\
  & 2 & 49,764 & -.02 & Cross-Sectional & Probability & > 18 & Asia & India & Caste & No & Yes\\
- & 3 & 935 & -.02 & Cross-Sectional & Probability & > 18 & Asia & India & Religion & No & Yes\\
  & 3 & 33,137 & -.03 & Cross-Sectional & Probability & > 18 & Asia & India & Caste & No & Yes\\
- & 4 & 271 & .08 & Cross-Sectional & Probability & > 18 & Asia & India & Religion & No & Yes\\
 \cite{2375} & 1 & 112 & -.23 & Cross-Sectional & Students & > 18 & N. America & USA & L.-T. Migration & Yes & Yes\\
@@
 \cite{3054} & 1 & 1,000 & -.01 & Cross-Sectional & Convenience & > 18 & Multiple & Multiple & Multiple & Yes & Yes\\
- & 11 & 3,883 & -.09 & Cross-Sectional & Convenience & > 18 & Multiple & Multiple & Sexuality & Yes & Yes\\
+ & 2 & 3,883 & -.09 & Cross-Sectional & Convenience & > 18 & Multiple & Multiple & Sexuality & Yes & Yes\\
 \cite{856} & 1 & 187 & .06 & Cross-Sectional & Students & < 18 & Europe & Macedonia & Other & Yes & Yes\\
@@
 \cite{4005} & 1 & 74 & -.24 & Cross-Sectional & Students & > 18 & Asia & Israel & L.-T. Migration & Yes & Yes\\
-\cite{813} & 2 & 175 & .00 & Cross-Sectional & Students & > 18 & Asia & Israel & Post-Colonial & Yes & Yes\\
+\cite{813} & 1 & 175 & .00 & Cross-Sectional & Students & > 18 & Asia & Israel & Post-Colonial & Yes & Yes\\
 \cite{1695} & 1 & 1,008 & .03 & Cross-Sectional & Probability & > 18 & Oceania & NZ & Post-Colonial & Yes & Yes\\

### 2021-05-07 figures/figure-6.R

@@ -26,7 +26,7 @@ rm(list = ls())
     xmin = c(0.0, 1.0, 2.0, 3.0, 3.0, 3.0, 3.0),
     xmax = c(0.8, 1.8, 2.8, 3.8, 3.8, 3.8, 3.8),
     ymin = c(1.5, 1.0, 0.5, 0.0, 1.0, 2.0, 3.0),
-    ymax = c(2.3, 1.8, 1.3, 0.8, 1.8, 2.8, 3.8)
+    ymax = c(2.3, 1.8, 1.3, 0.8, 1.8, 2.8, 3.8) + 0.1
   )
   
   # Create arrows
@@ -40,12 +40,12 @@ rm(list = ls())
   # Create labels
   labels <- tibble(
     x = c(0.4, 1.4, 2.4, 3.4, 3.4, 3.4, 3.4),
-    y = c(1.9, 1.4, 0.9, 0.4, 1.4, 2.4, 3.4),
+    y = c(1.9, 1.4, 0.9, 0.4, 1.4, 2.4, 3.4) + 0.05,
     text = c(
       glue("*I* = {sum(d_6a$n)}"),
       glue("Adults<br>*I* = {d_6a$n[2] + d_6a$n[3] + d_6a$n[4]}"),
       glue("Direct<br>Measurement<br>*I* = {d_6a$n[3] + d_6a$n[4]}"),
-      glue("Post-Colonial/<br>S.-T. Migration<br>*I* = {d_6a$n[4]}"),
+      glue("Post-Colonial/<br>S.-T. Migration/<br>Sexuality<br>*I* = {d_6a$n[4]}"),
       glue("Other Settings<br>*I* = {d_6a$n[3]}"),
       glue("Indirect<br>Measurement<br>*I* = {d_6a$n[2]}"),
       glue("Adolescents/<br>Children<br>*I* = {d_6a$n[1]}")

### 2021-05-07 run_scripts.R

@@ -4,7 +4,8 @@ rm(list = ls())
   
   #########################################################################
   # This script runs all R scripts in the order in which they need to be  #
-  # run to reproduce the analyses reported in the manuscript.             #
+  # run to reproduce the analyses reported in the manuscript. You might   #
+  # need to restart R between scripts.                                    #
   #########################################################################
 
 # Prepare -----------------------------------------------------------------

### 2021-05-07 scripts/code_moderators.R

@@ -246,6 +246,7 @@ rm(list = ls())
       ingroup,
       outgroup,
       age = case_when(
+        age_adolescents == 1L & age_children == 1L ~ "Children\n(≤ 12 years),Adolescents\n(13 - 18 years)",
         age_adolescents == 1L & age_adults == 1L ~ "Adolescents\n(13 - 18 years),Adults\n(≥ 18 years)",
         age_adolescents == 1L ~ "Adolescents\n(13 - 18 years)",
         age_adults == 1L ~ "Adults\n(≥ 18 years)",

### 2021-05-07 scripts/prepare_data_for_analyses.R

@@ -202,42 +202,28 @@ rm(list = ls())
         id == 2396L & sample == 1L ~ "Other",
         id == 2396L & sample == 2L ~ "Sexuality",
         id == 2396L & sample == 3L ~ "Colonization",
-        id == 2397L & sample == 1L ~ "Long-term migration"
+        id == 2397L & sample == 1L ~ "Long-term migration",
+        id == 2398L & sample == 1L ~ "Long-term migration"
       ),
-      ic_direct = case_when(
-        !is.na(ic_direct) ~ ic_direct,
-        id == 2395L & sample == 1L ~ "Directly",
-        id == 2395L & sample == 2L ~ "Directly",
-        id == 2396L & sample == 1L ~ "Directly",
-        id == 2396L & sample == 2L ~ "Directly",
-        id == 2396L & sample == 3L ~ "Directly",
-        id == 2397L & sample == 1L ~ "Directly"
+      ingroup = case_when(
+        !is.na(ingroup) ~ ingroup,
+        id == 2395L & sample == 1L ~ "Kurdish people",
+        id == 2395L & sample == 2L ~ "Black people",
+        id == 2396L & sample == 1L ~ "Disabled people",
+        id == 2396L & sample == 2L ~ "LGBTI people",
+        id == 2396L & sample == 3L ~ "Kurdish people",
+        id == 2397L & sample == 1L ~ "Black people",
+        id == 2398L & sample == 1L ~ "Asian people"
       ),
-      pi_specific = case_when(
-        !is.na(pi_specific) ~ pi_specific,
-        id == 2395L & sample == 1L & y == "gd" ~ "General",
-        id == 2395L & sample == 1L & y == "pd" ~ "General",
-        id == 2395L & sample == 1L & y == "rd" ~ "General",
-        id == 2395L & sample == 2L & y == "gd" ~ "General",
-        id == 2395L & sample == 2L & y == "pd" ~ "General",
-        id == 2395L & sample == 2L & y == "rd" ~ "General",
-        id == 2396L & sample == 1L & y == "pd" ~ "Specific",
-        id == 2396L & sample == 2L & y == "pd" ~ "Specific",
-        id == 2396L & sample == 3L & y == "pd" ~ "Specific",
-        id == 2397L & sample == 1L & y == "rd" ~ "Specific"
-      ),
-      pi_personal = case_when(
-        !is.na(pi_personal) ~ pi_personal,
[…]

### 2021-05-08 manuscript/manuscript.Rmd
check and rerun all scripts

@@
 
+```{r, include = FALSE}
+
+  # Import results from moderator analyses
+  R2 <- read_rds("../results/results_categorical_moderator_analyses.rds") %>% 
+    mutate(
+      R2 = map_dbl(R2, ~median(.$R2)), 
+      R2 = glue("$R^2 = {f_num(R2 * 100, digits = 0)}\\%$")
+    ) %>% 
+    filter(y_var == "pi") %>% 
+    select(moderator, R2)
+
+  # Import results from moderator analyses
+  meta_cart <- read_rds("../results/results_exploratory_moderator_analyses.rds") %>% 
+    group_by(kk, age, ic_direct, study_setting) %>% 
+    summarize(
+      r_kk = glue("$r = {f_num(median(r), digits = 2)}, [{f_num(quantile(r, 0.025), digits = 2)}, {f_num(quantile(r, 0.975), digits = 2)}]$"),
+      R2 = glue("$R^2 = {f_num(median(R2) * 100, digits = 0)}\\%$")
+    ) %>% 
+    ungroup()
+
+```
+
 First, we used meta-regression models to examine specific moderator variables which we expected to explain heterogeneity in effect sizes across samples.
 Figure 4 shows results for categorical moderator variables.
-We found that the setting of the study ($R^2 = 20\%$), participants’ age group ($R^2 = 12\%$), and whether intergroup contact was measured directly or indirectly ($R^2 = 10\%$) explained the most variance across effect sizes.
+We found that the setting of the study (`r with(R2, R2[moderator == "study_setting"])`), participants’ age group (`r with(R2, R2[moderator == "age"])`), and whether intergroup contact was measured directly or indirectly (`r with(R2, R2[moderator == "ic_direct"])`) explained the most variance across effect sizes.
 Figure 5 shows results from country-level analyses examining cultural context as a moderator variable.
@@
 Second, we used meta-regression trees to discover interactions between moderator variables that best explained heterogeneity in effect sizes [@li_multiple_2020].
-Figure 6 shows the resulting meta-regression that explained more variance across samples than any individual moderator ($R^2 = 31\%$).
+Figure 6 shows the resulting meta-regression that explained more variance across samples than any individual moderator (`r with(meta_cart, unique(R2))`).
 We found that intergroup contact was associated with less perceived injustice only in studies that focused on adults and that measured intergroup contact directly.
-Among these studies, this association was stronger in settings in which the groups’ relative inequality stemmed from short-term migration or colonization ($r = -.18, [-.23, -.13]$) than in other settings ($r = -.09, [-.12, -.06]$).
+Among these studies, this association was stronger in settings in which the groups’ relative inequality stemmed from short-term migration or colonization (`r with(meta_cart, r_kk[4])`) than in other settings (`r with(meta_cart, r_kk[3])`).
 

### 2021-05-08 manuscript/manuscript.tex
add list of studies
check and rerun all scripts

@@
 of stifling support for social change in disadvantaged groups. We
-conducted a preregistered meta-analytic test of this effect across 96
-studies with 137 samples of 211,360 disadvantaged-group members. As
+conducted a preregistered meta-analytic test of this effect across 97
+studies with 138 samples of 212,189 disadvantaged-group members. As
 predicted, intergroup contact was, on average, associated with less
@@
 
-\hypertarget{transparency}{%
-\subsection{Transparency}\label{transparency}}
+\hypertarget{open-practices-statement}{%
+\subsection{Open Practices Statement}\label{open-practices-statement}}
 
@@
 Africans), religion, caste, sexuality, or another distinction
-(\(\kappa = .84\)).
+(\(\kappa = .85\)).
 
@@
 both (\(\kappa = .67\)) and whether it assessed personal discrimination,
-group discrimination, or both (\(\kappa = .83\)).
+group discrimination, or both (\(\kappa = .84\)).
 
@@
 (50\%) ineligible records after reviewing full-text manuscripts. We
-supplemented these records with 14 unpublished studies solicited from
+supplemented these records with 15 unpublished studies solicited from
 researchers and 6 records that cited at least three relevant works. Of
-135 eligible studies, we had to exclude 38 (28\%) studies for which we
+136 eligible studies, we had to exclude 38 (28\%) studies for which we
 could not extract or impute any relevant effect size. At each stage, we
 also excluded studies that used the same data as another study. Our
-final sample comprised effect sizes from \(J = 96\) studies spanning
-\(N = 211,360\) participants in \(I = 137\) samples.
+final sample comprised effect sizes from \(J = 97\) studies spanning
+\(N = 212,189\) participants in \(I = 138\) samples.
 
@@
 and the United States (\(N = 60,983\); Figure 2a), most samples were
-collected in North America (\(I = 48\)) and Europe (\(I = 40\)), with
+collected in North America (\(I = 48\)) and Europe (\(I = 41\)), with
 few samples from South America and Africa (Figure 2b). Most samples
 focused on relative inequalities that resulted from long-term migration
-(\(I = 56\)), slavery (\(I = 19\)), colonization (\(I = 19\)), and
+(\(I = 57\)), slavery (\(I = 19\)), colonization (\(I = 19\)), and
 short-term migration (\(I = 14\)). With few exceptions, studies used
 observational, cross-sectional survey designs. Samples sizes ranged from
-64 to 49,764 (\(\textit{Mdn} = 282\)). Unlike most psychological
+64 to 49,764 (\(\textit{Mdn} = 283\)). Unlike most psychological
 research, 2 in 5 samples used probability or representative sampling. Of
-all samples, 55\% (\(I = 75\)) were collected with the intention to
+all samples, 54\% (\(I = 75\)) were collected with the intention to
 examine the effects of intergroup contact on the outcomes considered in
@@
 
-\textbf{\emph{Perceived Injustice.}} Across 201,912 participants from
-123 samples in 84 studies, we found strong evidence for a weak
+\textbf{\emph{Perceived Injustice.}} Across 202,741 participants from
+124 samples in 85 studies, we found strong evidence for a weak
 association (\(r = -.07, [-.10, -.04]\)) between intergroup contact and
@@
 that 80\% of studies would result in correlation coefficients between
--.25 and .11 and that researchers would need sample sizes of at least
-2,538 participants to find significant associations (\(\alpha = .05\),
+-.25 and .10 and that researchers would need sample sizes of at least
+2,549 participants to find significant associations (\(\alpha = .05\),
 two-sided) in 80\% of their studies.\footnote{Sample sizes are based on
@@
 samples in 3 studies, we found evidence for a moderate association
-(\(r = .30, [.13, .42]\)) between collective action and policy support.
+(\(r = .30, [.14, .42]\)) between collective action and policy support.
 
@@
 \includegraphics[scale=1]{../figures/figure-5}
-\caption*{\textit{Note.} We had data from too few countries to reach firm conclusions about the direction of these associations for perceived injustice ($\beta = -0.36, [-1.43, 0.78]$; $\Pr (\beta < 0) = 73.5\%$), collective action ($\beta = -0.09, [-1.60, 1.37]$; $\Pr (\beta < 0) = 55.1\%$), and policy support ($\beta = -0.92, [-2.13, 0.55]$; $\Pr (\beta < 0) = 90.3\%$).}
+\caption*{\textit{Note.} We had data from too few countries to reach firm conclusions about the direction of these associations for perceived injustice ($\beta = -0.34, [-1.41, 0.81]$; $\Pr (\beta < 0) = 73.5\%$), collective action ($\beta = -0.09, [-1.60, 1.37]$; $\Pr (\beta < 0) = 55.1\%$), and policy support ($\beta = -0.92, [-2.13, 0.55]$; $\Pr (\beta < 0) = 90.3\%$).}
 \label{fig:f5}
@@
 variables. We found that the setting of the study (\(R^2 = 20\%\)),
-participants' age group (\(R^2 = 12\%\)), and whether intergroup contact
+participants' age group (\(R^2 = 11\%\)), and whether intergroup contact
 was measured directly or indirectly (\(R^2 = 10\%\)) explained the most
@@
 (\(r = -.18, [-.23, -.13]\)) than in other settings
-(\(r = -.09, [-.12, -.06]\)).
+(\(r = -.09, [-.12, -.05]\)).
 
@@
 
-\begin{figure*}
+\begin{figure*}[t!]
 \centering
@@
 By using partial correlations, we estimated the effect of one form of
-contact while controlling for the other. Across 104,545 participants
-from 26 samples in 15 studies, we found stronger evidence for a positive
+contact while controlling for the other. Across 105,374 participants
+from 27 samples in 16 studies, we found stronger evidence for a positive
 association between negative contact and perceived injustice
-(\(r = .15, [.05, .25]\); \(\Pr (r > 0) = 99.8\%\)) than for a negative
+(\(r = .14, [.05, .23]\); \(\Pr (r > 0) = 99.8\%\)) than for a negative
 association between positive contact and perceived injustice
-(\(r = -.05, [-.12, .01]\); \(\Pr (r < 0) = 93.8\%\)). Across 107,451
+(\(r = -.05, [-.11, .01]\); \(\Pr (r < 0) = 94.8\%\)). Across 107,451
 participants from 16 samples in 9 studies, we again found stronger
@@
 negative association between positive contact and policy support
-(\(r = .03, [-.03, .10]\); \(\Pr (r < 0) = 12.7\%\)). Across 109,428
-participants from 28 samples in 16 studies, we found a negative
+(\(r = .03, [-.03, .10]\); \(\Pr (r < 0) = 12.7\%\)). Across 110,257
+participants from 29 samples in 17 studies, we found a negative
 association between positive and negative contact
-(\(r = -.16, [-.26, -.05]\); \(\Pr (r < 0) = 99.7\%\)).
+(\(r = -.16, [-.25, -.05]\); \(\Pr (r < 0) = 99.8\%\)).
 
@@
 using effect sizes from all studies that measured both predictors
-(Figure 8b). Across 6,059 participants from 14 samples in 7 studies, we
+(Figure 8b). Across 6,888 participants from 15 samples in 8 studies, we
 found insufficient evidence for associations of ingroup contact
-(\(r = .02, [-.13, .16]\); \(\Pr (r > 0) = 61.9\%\)) and outgroup
-contact (\(r = -.10, [-.29, .10]\); \(\Pr (r < 0) = 85.8\%\)) with
+(\(r = .03, [-.10, .15]\); \(\Pr (r > 0) = 69.0\%\)) and outgroup
+contact (\(r = -.10, [-.26, .07]\); \(\Pr (r < 0) = 89.2\%\)) with
 perceived injustice. Across 3,938 participants from 4 samples in 2
@@
 outgroup contact (\(r = -.03, [-.12, .08]\); \(\Pr (r < 0) = 78.5\%\))
-with policy support. Across 6,059 participants from 14 samples in 7
+with policy support. Across 6,888 participants from 15 samples in 8
 studies, we found a positive association between ingroup and outgroup
-contact (\(r = .23, [.04, .35]\); \(\Pr (r > 0) = 98.8\%\)).
+contact (\(r = .25, [.10, .34]\); \(\Pr (r > 0) = 99.7\%\)).
 
@@
 \leavevmode\hypertarget{ref-stan_development_team_rstan:_2020}{}%
-Stan Development Team. (2020). \emph{RStan: The R interface to Stan}.
-\url{http://mc-stan.org/}
+Stan Development Team. (2020). \emph{RStan: The R interface to Stan}
+(Version 2.21.2). \url{http://mc-stan.org/}
 

### 2021-05-08 manuscript/supplemental-materials.Rmd
check and rerun all scripts

@@
 output:
-  word_document: default
   pdf_document:

### 2021-05-08 manuscript/supplemental-materials.tex
check and rerun all scripts

@@
 \(\Delta r = .00, [-.05, .05]\)), collective action
-(\(\Delta r = -.01, [-.11, .09]\) and \(\Delta r = -.00, [-.10, .11]\)),
+(\(\Delta r = -.01, [-.11, .09]\) and \(\Delta r = .00, [-.11, .10]\)),
 and policy support (\(\Delta r = -.01, [-.10, .08]\) and
@@
 the mean effect size for the three outcomes
-(\(\Delta r = .00, [-.04, .05]\); \(\Delta r = .02, [-.09, .12]\);
+(\(\Delta r = .01, [-.04, .05]\); \(\Delta r = .02, [-.08, .12]\);
 \(\Delta r = -.02, [-.11, .07]\)). Together, these analyses showed that

### 2021-05-08 figures/figure-2a.R

@@ -1,230 +1,0 @@
-# Notes -------------------------------------------------------------------
-
-  #########################################################################
-  # Thanks to Claus Wilke for implementing the "Interrupted Goode         #
-  # homolosine" projection in R.                                          #
-  #########################################################################
-
-# Library -----------------------------------------------------------------
-  
-  # Load packages
-  library(tidyverse); library(sf); library(rworldmap); library(numform)
-
-
-# Prepare map -------------------------------------------------------------
-
-  # Load map
-  world_sf <- st_as_sf(getMap(resolution = "low"))
-  
-  # Prepare map projection
-  crs_goode <- "+proj=igh"
-  goode_outline <- list(cbind(
-    longs <- c(
-      rep(180, 181), 
-      rep(c(80.01, 79.99), each = 91), 
-      rep(c(-19.99, -20.01), each = 91), 
-      rep(c(-99.99, -100.01), each = 91),
-      rep(-180, 181), 
-      rep(c(-40.01, -39.99), each = 91),
-      180 
-    ), 
-    lats <- c(
-      90:-90,
-      -90:0, 0:-90, 
-      -90:0, 0:-90, 
-      -90:0, 0:-90, 
-      -90:90, 
-      90:0, 0:90, 
-      90
-    )
-  )) %>%
-    st_polygon() %>%
-    st_sfc(
-      crs = "+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs"
-    )
-  goode_outline <- st_transform(goode_outline, crs = crs_goode)
-  xlim <- st_bbox(goode_outline)[c("xmin", "xmax")]*1.1
-  ylim <- st_bbox(goode_outline)[c("ymin", "ymax")]*1.1
-  goode_encl_rect <- 
-    list(
-      cbind(
-        c(xlim[1], xlim[2], xlim[2], xlim[1], xlim[1]), 
-        c(ylim[1], ylim[1], ylim[2], ylim[2], ylim[1])
-      )
-    ) %>%
-    st_polygon() %>%
-    st_sfc(crs = crs_goode)
-  goode_without <- st_difference(goode_encl_rect, goode_outline)
-  
-  
-# Prepare data ------------------------------------------------------------
-
-  # Import data
-  dl <- read_rds("data/dl.rds")
-  
-  # Select variables
-  dm <- dl %>% distinct(id, sample, n, country)
-  
[…]

### 2021-05-08 scripts/code_measures.R

@@ -95,5 +95,3 @@ rm(list = ls())
   
   # Export as .rds files (data)
   mo_mi %>% write_rds("data/mo_mi.rds")
-    
-  

### 2021-05-08 scripts/prepare_data_for_analyses.R

@@ -170,7 +170,46 @@ rm(list = ls())
         rename(y = variable),
       by = c("id", "sample", "y", "y_var", "y_name", "y_text")
     )
-
+  dl <- dl %>% 
+    filter(y_var == "pi", is.na(pi_specific), is.na(pi_personal), !is.na(r)) %>% 
+    select(-pi_specific, -pi_personal) %>% 
+    left_join(
+      mo_mi %>% 
+        filter(var == "pi") %>% 
+        select(-starts_with("ic_")) %>% 
+        rename_with(~paste0("y_", .), c("var", "name")) %>% 
+        rename(y = variable),
+      by = c("id", "sample", "y", "y_var", "y_name")
+    ) %>% 
+    bind_rows(
+      dl %>% filter(
+        y_var != "pi" | 
+        (y_var == "pi" & !is.na(pi_specific) & !is.na(pi_personal)) | 
+        is.na(r)
+      ),
+      .
+    )
+  dl <- dl %>% 
+    filter(x_var == "ic", is.na(ic_direct), !is.na(r)) %>% 
+    select(-ic_direct) %>% 
+    left_join(
+      mo_mi %>% 
+        filter(var == "ic") %>% 
+        select(-starts_with("pi_")) %>% 
+        rename_with(~paste0("x_", .), c("var")) %>% 
+        rename(x = variable),
+      by = c("id", "sample", "x", "x_var")
+    ) %>% 
+    bind_rows(
+      dl %>% filter(
+        x_var != "ic" | 
+          (x_var == "ic" & !is.na(ic_direct)) | 
+          is.na(r)
+      ),
+      .
+    )
+  
+  
 
 # Export ------------------------------------------------------------------
 
@@ -192,7 +231,7 @@ rm(list = ls())
   # Arrange for export
   dl <- dl %>% arrange(id, sample, x, y)
   
-  # Code missing moderators (for unpublished data)
+  # Add missing study information (for unpublished data)
   dl <- dl %>% 
     mutate(
       study_setting = case_when(

### 2021-05-08 scripts/run_analyses_with_ingroup_contact.R

@@ -52,6 +52,7 @@ rm(list = ls())
         id == 2382L & x == "cf" ~ "og",
         id == 2383L & x == "cf" ~ "og",
         id == 2396L & x == "cf" ~ "og",
+        id == 2398L & x == "pc" ~ "og",
         TRUE ~ x
       ),
       y = case_when(
@@ -70,6 +71,7 @@ rm(list = ls())
         id == 2382L & y == "cf" ~ "og",
         id == 2383L & y == "cf" ~ "og",
         id == 2396L & y == "cf" ~ "og",
+        id == 2398L & y == "pc" ~ "og",
         TRUE ~ y
       )
     ) %>% 

### 2021-05-08 scripts/run_analyses_with_negative_contact.R

@@ -92,6 +92,7 @@ rm(list = ls())
   # Load model
   model <- stan_model("models/2l-meta-analysis-with-negative-contact.stan")
 
+
 # Estimate (perceived injustice) ------------------------------------------
   
   # Prepare data list

### 2021-05-08 scripts/run_exploratory_moderator_analyses.R

@@ -109,7 +109,7 @@ rm(list = ls())
     vi = vi,
     data = es %>% filter(y_var == "pi"),
     c = 0.0,
-    xval = nrow(es %>% filter(y_var == "ca")),
+    xval = nrow(es %>% filter(y_var == "pi")),
     lookahead = TRUE
   )
   
@@ -121,8 +121,8 @@ rm(list = ls())
       kk = case_when(
         age != "Adults" ~ 1L,
         ic_direct != "Directly" ~ 2L,
-        !(study_setting %in% c("Colonization", "Short-term migration", "Sexuality")) ~ 3L,
-        study_setting %in% c("Colonization", "Short-term migration", "Sexuality") ~ 4L
+        !(study_setting %in% c("Colonization", "Short-term migration")) ~ 3L,
+        study_setting %in% c("Colonization", "Short-term migration") ~ 4L
       )
     )
   
@@ -149,7 +149,7 @@ rm(list = ls())
     mutate(
       study_setting = case_when(
         age != "Adults" | ic_direct == "Indirectly" ~ NA_character_, 
-        str_detect(study_setting, "Colonization|Short-term migration|Sexuality") ~ "Colonization/Short-term migration/Sexuality",
+        str_detect(study_setting, "Colonization|Short-term migration") ~ "Colonization/Short-term migration",
         TRUE ~ "Other"
       ),
       ic_direct = case_when(
@@ -176,7 +176,7 @@ rm(list = ls())
     vi = vi,
     data = es %>% filter(y_var == "ca"),
     c = 0.0,
-    xval = 34,
+    xval = nrow(es %>% filter(y_var == "ca")),
     lookahead = TRUE
   )
   
@@ -192,7 +192,7 @@ rm(list = ls())
     vi = vi,
     data = es %>% filter(y_var == "ps"),
     c = 0.0,
-    xval = 17,
+    xval = nrow(es %>% filter(y_var == "ps")),
     lookahead = TRUE
   )
 

### 2021-05-08 scripts/run_preregistered_analyses.R

@@ -313,7 +313,7 @@ rm(list = ls())
     stan(
       "models/1l-meta-analysis.stan",
       data = .,
-      control = list(adapt_delta = 0.95),
+      control = list(adapt_delta = 0.99),
       chains = n_cores,
       iter = n_warmup + n_iter/n_cores,
       warmup = n_warmup,

### 2021-05-08 scripts/run_preregistered_robustness_checks.R

@@ -19,8 +19,7 @@ rm(list = ls())
   seeds    <- c(6967674, 5768664, 7517370)
   options(mc.cores = n_cores)
   rstan_options(auto_write = TRUE)
-  Sys.setenv(LOCAL_CPPFLAGS = '-march=corei7 -mtune=corei7')
-  
+
   # Link functions
   r_to_z <- function(r) 0.5 * log( (1 + r) / (1 - r) )
   z_to_r <- function(z) ( exp(2 * z) - 1 ) / ( exp(2 * z) + 1 )

### 2021-05-14 manuscript/manuscript.Rmd
submit

@@
 abstract: 
-  Critics have argued that intergroup contact, psychology’s most-researched paradigm for reducing prejudice, has the ‘ironic’ effect of stifling support for social change in disadvantaged groups.
-We conducted a preregistered meta-analytic test of this effect across `r with(dplyr::distinct(readRDS("../data/dl.rds"), sample, id, n), numform::f_comma(dplyr::n_distinct(id)))` studies with `r with(dplyr::distinct(readRDS("../data/dl.rds"), sample, id, n), numform::f_comma(length(sample)))` samples of `r with(dplyr::distinct(readRDS("../data/dl.rds"), sample, id, n), numform::f_comma(sum(n)))` disadvantaged-group members.
-As predicted, intergroup contact was, on average, associated with less perceived injustice (`r with(readRDS("../results/results_preregistered_analyses.rds"), paste0("$r = ", numform::f_num(median(r_mean[x_var == "ic" & y_var == "pi"]), digits = 2), "$"))`), collective action (`r with(readRDS("../results/results_preregistered_analyses.rds"), paste0("$r = ", numform::f_num(median(r_mean[x_var == "ic" & y_var == "ca"]), digits = 2), "$"))`), and support for reparative policies (`r with(readRDS("../results/results_preregistered_analyses.rds"), paste0("$r = ", numform::f_num(median(r_mean[x_var == "ic" & y_var == "ps"]), digits = 2), "$"))`) in disadvantaged groups.
-However, these associations were small, variable, and consistent with alterative explanations.
-Moderator analyses found that these associations were strongest in studies on short-term migration and post-colonial relations, that measured intergroup contact directly, and that involved adults.
-After controlling for the positive association of negative contact with support for social change, positive contact was not (negatively) associated with any outcome in studies that measured both predictors.
-We close by highlighting open questions about the relation between intergroup contact and social change.
+  Growing evidence suggests that intergroup contact, psychology’s most-researched paradigm for reducing prejudice, might have the ‘ironic’ effect of reducing support for social change in disadvantaged groups.
+We conducted a preregistered meta-analysis of this effect across `r with(dplyr::distinct(readRDS("../data/dl.rds"), sample, id, n), numform::f_comma(dplyr::n_distinct(id)))` studies with `r with(dplyr::distinct(readRDS("../data/dl.rds"), sample, id, n), numform::f_comma(length(sample)))` samples of `r with(dplyr::distinct(readRDS("../data/dl.rds"), sample, id, n), numform::f_comma(sum(n)))` disadvantaged-group members.
+As predicted, intergroup contact was, on average, associated with less perceived injustice (`r with(readRDS("../results/results_preregistered_analyses.rds"), paste0("$r = ", numform::f_num(median(r_mean[x_var == "ic" & y_var == "pi"]), digits = 2), "$"))`), collective action (`r with(readRDS("../results/results_preregistered_analyses.rds"), paste0("$r = ", numform::f_num(median(r_mean[x_var == "ic" & y_var == "ca"]), digits = 2), "$"))`), and support for reparative policies (`r with(readRDS("../results/results_preregistered_analyses.rds"), paste0("$r = ", numform::f_num(median(r_mean[x_var == "ic" & y_var == "ps"]), digits = 2), "$"))`).
+Moderator analyses found that associations were strongest in studies of adults that measured intergroup contact directly and examined short-term migration or post-colonial intergroup relations.
+After controlling for the positive association of negative contact with support for social change, positive contact was not associated with any outcome in studies that measured both predictors.
+We close by highlighting open questions about the relationship between intergroup contact and social change.
 statement: 
@@
 Hundreds of studies have confirmed that intergroup contact is associated with less negative feelings toward outgroup members [for a meta-analysis, see @pettigrew_meta-analytic_2006].
-Most of these studies have focused on advantaged-group members' contact experiences with disadvantaged-group members [@tropp_relationships_2005], guided by the idea that reducing advantaged-group members' prejudice will prevent interpersonal discrimination.
+Most studies have focused on advantaged-group members' contact experiences with disadvantaged-group members [@tropp_relationships_2005], guided by the idea that reducing advantaged-group members' prejudice will prevent interpersonal discrimination.
 Reducing prejudice, however, is rarely enough to overcome institutional and structural discrimination.
@@
 Critics have argued that, by fostering harmony and reducing conflict, intergroup contact might distract disadvantaged-group members from the injustice they face and undermine their motivation for social change [@dixon_beyond_2005; @reicher_rethinking_2007; @brown_strategic_2003].
-By stifling disadvantaged-group members' opposition to injustice, intergroup contact might thus have the 'ironic' [@saguy_irony_2009], 'sedative' [@cakal_investigation_2011], or 'paradoxical' [@dixon_paradox_2010] effect of hindering social change.
+By reducing disadvantaged-group members' opposition to injustice, intergroup contact might thus have the 'ironic' [@saguy_irony_2009], 'sedative' [@cakal_investigation_2011], or 'paradoxical' [@dixon_paradox_2010] effect of hindering social change.
 
-Supporting this argument, initial studies provided evidence that, among disadvantaged-group members, intergroup contact reduces perceptions of injustice [@saguy_irony_2009], discourages collective action [@cakal_investigation_2011], and diminishes support for reparative policies [@dixon_intergroup_2007].
-Others, however, have pointed to conflicting evidence [@poore_contact_2002] and argued that intergroup contact might instead render discrimination more salient and, thereby, increase disadvantaged-group members' support for social change [@pettigrew_recent_2011].
-A decade after the initial studies, many more studies have examined the relationships between intergroup contact and support for social change in disadvantaged groups.
+Supporting this argument, initial studies provided evidence that contact with advantaged-group members reduces disadvantaged-group members' perceptions of injustice [@saguy_irony_2009], collective action [@cakal_investigation_2011], and support for reparative policies [@dixon_intergroup_2007].
+Others, however, have pointed to conflicting evidence [@poore_contact_2002] and argued that intergroup contact might instead make discrimination more salient and, thereby, increase disadvantaged-group members' support for social change [@pettigrew_recent_2011].
+In the decade since the initial studies, many more studies have examined the relationships between intergroup contact and support for social change in disadvantaged groups.
 We present a systematic review and meta-analysis of this growing literature.
@@
 
-Perceived injustice—that is, perceiving unjust group-based deprivation or discrimination against the disadvantaged ingroup—is a prerequisite to instigating social change [@van_zomeren_toward_2008].
-Researchers have argued that positive contact with advantaged-group members could contradict perceptions of personal discrimination, undermine negative characterizations of the advantaged outgroup, and, thereby, make group discrimination appear less plausible [@dixon_paradox_2010].
+Perceived injustice—that is, perceiving unjust group-based deprivation or discrimination against a disadvantaged ingroup—is a prerequisite to instigating social change [@van_zomeren_toward_2008].
+Researchers have argued that positive contact with advantaged groups could contradict perceptions of personal discrimination and, thereby, make group discrimination appear less plausible [@dixon_paradox_2010].
 Positive contact could further reduce perceived injustice by emphasizing commonalities over differences [@saguy_irony_2009] and by motivating disadvantaged-group members to adopt system-justifying ideologies [@sengupta_perpetuating_2013].
-To the extent that it reduces perceived injustice, intergroup contact hinders social change.
+To the extent that it reduces perceived injustice, intergroup contact reduces support for social change.
 
 Collective action—that is, any action directed at improving the conditions of the disadvantaged ingroup [@wright_responding_1990]—is crucial to achieving social change because advantaged-group members rarely surrender their advantages without sustained pressure from disadvantaged-group members [@blumer_race_1958; for a review, see @dixon_beyond_2012].
-Researchers have argued that intergroup contact could discourage disadvantaged-group members from engaging in collective action by diminishing their perceived discrimination [@tropp_crossethnic_2012], by blurring boundaries between the disadvantaged ingroup and the advantaged outgroup [@saguy_irony_2009], by reducing negative attitudes toward the advantaged outgroup [@wright_struggle_2009], and by quelling anger about inequality [@tausch_how_2015] or toward the advantaged outgroup [@hayward_how_2018].
-To the extent that it discourages collective action, intergroup contact hinders social change.
+Researchers have argued that intergroup contact could discourage disadvantaged-group members from engaging in collective action by diminishing their perceived discrimination [@tropp_crossethnic_2012], by blurring boundaries between the disadvantaged ingroup and the advantaged outgroup [@saguy_irony_2009], by reducing negative attitudes toward the advantaged outgroup [@wright_struggle_2009], and by quelling their anger  [@hayward_how_2018; @tausch_how_2015].
+To the extent that it discourages collective action, intergroup contact reduces support for social change.
 
@@
 Researchers have argued that intergroup contact could diminish disadvantaged-group members’ support for redistributive policies by creating sympathy for advantaged-group members [@dixon_intergroup_2007], by fostering positive outgroup attitudes and reducing attention to inequality [@saguy_irony_2009], and by increasing their endorsement of system-justifying ideologies [@sengupta_perpetuating_2013].
-To the extent that it diminishes support for redistributive policies, intergroup contact hinders social change.
+To the extent that it diminishes support for redistributive policies, intergroup contact reduces support for social change.
 
-We conducted a preregistered meta-analysis of the evidence for the hypothesized negative effects of intergroup contact on perceived injustice, collective action, and policy support in disadvantaged groups.
 Our first objective was to systematically review the available evidence and to evaluate its strengths and limitations.
 Our second objective was to synthesize the available evidence to establish the direction and magnitude of the relationships between intergroup contact and the three outcomes.
-Doing so allowed us, first, to determine whether the available evidence supports a negative or positive [see @pettigrew_recent_2011] relationship between contact and support for social change and, second, to estimate the strength of this relationship.
+Doing so allowed us to determine whether the available evidence supports a negative or positive [see @pettigrew_recent_2011] relationship between contact and support for social change and to estimate the strength of this relationship.
 Our third objective was to explore the variability of this relationship across study settings, designs, and other potential moderators.
-For example, we examined whether any effects were confined to Western, Educated, Industrialized, Rich, Democratic (WEIRD) settings, the cultural context of most psychological research [@henrich_weirdest_2010].
+For example, we examined whether any effects were confined to Western, Educated, Industrialized, Rich, Democratic (WEIRD) countries, the cultural context of most psychological research [@henrich_weirdest_2010].
 Our fourth objective was to assess how robust the available evidence was to publication bias.
 
-In addition, we collated the evidence for two alternative accounts of this relationship.
+In addition, we examined the evidence for two alternative accounts of this relationship.
 First, we considered studies that measured both ingroup and outgroup contact as predictors of the three outcomes.
-@sengupta_ingroup_2015 argued that contact with other members of the disadvantaged ingroup would increase political mobilization in disadvantaged groups.
+@sengupta_ingroup_2015 argued that contact with other members of the disadvantaged ingroup would increase political mobilization.
 As outgroup contact places limits on how much ingroup contact disadvantaged-group members can have [@pfister_contact_2020], the mobilizing effect of ingroup contact is an alternative explanation for negative associations between outgroup contact and support for social change.
+
 Second, we considered studies that measured both negative and positive (outgroup) contact as predictors of the three outcomes.
@@
 We included studies if they measured or manipulated the quantity of, quality of, and opportunity for contact with members of outgroups that are relatively advantaged compared to the participants’ ingroup.
-We considered opportunity for contact, as it is a potential precursor to and proxy for face-to-face contact, but not imagined or indirect contact.
+We considered opportunity for contact, as it is a potential precursor to and proxy for face-to-face contact, but not imagined or extended contact.
 Similarly, we included studies that measured intergroup contact indirectly by, for example, asking what proportion of someone’s friends were *not* from the participants’ ingroup.
@@
 We also considered expectations of fair treatment as the reverse of perceived injustice.
-We included studies that measured personal and/or group discrimination or a mixture of both.
+We included studies that measured personal or group discrimination or a mixture of both.
 
@@
 We report point estimates, based on the median of posterior samples, and uncertainty intervals, based on the quantiles of posterior samples, that enclose the 95% most plausible estimates.
-In addition, we report the posterior probability, based on the proportion of posterior samples below zero, that an estimated mean effect size is negative.
+In addition, we report the posterior probability, based on the proportion of posterior samples below zero, that the mean effect size is negative.
 
@@
 Of the remaining `r f_comma(counts$n_included[2])` records, we excluded `r f_comma(counts$n_excluded[3])` (`r f_comma(counts$p_excluded[3])`) ineligible records after reviewing full-text manuscripts.
-We supplemented these records with `r f_comma(with(read_csv("../records/results/unpublished-studies.csv"), n_distinct(id)))` unpublished studies solicited from researchers and `r f_comma(with(read_csv("../records/results/citing-studies.csv"), n_distinct(id)))` records that cited at least three relevant works.
-Of `r f_comma(with(read_csv("../records/results/unpublished-studies.csv"), n_distinct(id)) + with(read_csv("../records/results/citing-studies.csv"), n_distinct(id)) + counts$n_included[3])` eligible studies, we had to exclude `r f_comma(counts$n_excluded[4])` (`r f_comma(counts$p_excluded[4])`) studies for which we could not extract or impute any relevant effect size.
+We supplemented these records with `r f_comma(counts$unpublished[3])` unpublished studies and `r f_comma(counts$citing[3])` records that cited at least three relevant works.
+Of `r f_comma(with(counts[3,], database + citing + unpublished))` eligible studies, we had to exclude `r f_comma(counts$n_excluded[4])` (`r f_comma(counts$p_excluded[4])`) studies for which we could not extract or impute any relevant effect size.
 At each stage, we also excluded studies that used the same data as another study.
-Our final sample comprised effect sizes from `r paste0("$J = ", with(dl, f_comma(n_distinct(id))), "$")` studies spanning `r paste0("$N = ", with(distinct(dl, id, sample, n), f_comma(sum(n))), "$")` participants in `r paste0("$I = ", f_comma(nrow(distinct(dl, id, sample))), "$")` samples.
+Our final sample comprised effect sizes from `r paste0("$J = ", with(dl, f_comma(n_distinct(id))), "$")` studies spanning `r paste0("$N = ", with(distinct(dl, id, sample, n), f_comma(sum(n))), "$")` participants in `r paste0("$I = ", f_comma(nrow(distinct(dl, id, sample))), "$")` samples (for a complete list of studies, see SOM-U).
 
@@
 Unlike most psychological research, 2 in 5 samples used probability or representative sampling.
-Of all samples, `r with(distinct(dl, id, sample, study_intention), f_prop2percent(mean(study_intention == "Yes"), digits = 0))` (`r glue('$I = {f_comma(with(distinct(dl, id, sample, n, study_intention), length(sample[study_intention == "Yes"])))}$')`) were collected with the intention to examine the effects of intergroup contact on the outcomes considered in this meta-analysis.^[Many studies examined acculturation processes [@berry_immigration_1997] and measured both intergroup contact and perceived injustice without the relationship between the two being of interest.] Together, these observations highlight both limitations and strengths of the empirical literature.
+Of all samples, `r with(distinct(dl, id, sample, study_intention), f_prop2percent(mean(study_intention == "Yes"), digits = 0))` (`r glue('$I = {f_comma(with(distinct(dl, id, sample, n, study_intention), length(sample[study_intention == "Yes"])))}$')`) were collected with the intention to examine the effects of intergroup contact on the outcomes considered in this meta-analysis.
+Many studies instead examined acculturation processes [@berry_immigration_1997] and measured intergroup contact and perceived injustice without hypothesizing that the former would influence the latter.
+Together, these observations highlight both limitations and strengths of the empirical literature.
 
@@
 We found evidence that correlation coefficients varied across studies (`r pi_results$text[pi_results$parameter == "tau_jj"]`) and across samples within studies  (`r pi_results$text[pi_results$parameter == "tau_ii"]`).
-Based on these analyses, we predicted that 80\% of studies would result in correlation coefficients between `r post_pred$r_pred_l80[post_pred$y_var == "pi"]` and `r post_pred$r_pred_u80[post_pred$y_var == "pi"]` and that researchers would need sample sizes of at least `r post_pred$n_req[post_pred$y_var == "pi"]` participants to find significant associations ($\alpha = .05$, two-sided) in 80\% of their studies.^[Sample sizes are based on posterior predictions from the three models, which implied that, for 80\% of studies, the absolute correlation coefficient would be `r post_pred$r_abs[post_pred$y_var == "pi"]` for perceived injustice, `r post_pred$r_abs[post_pred$y_var == "ca"]` for collective action, and `r post_pred$r_abs[post_pred$y_var == "ps"]` for policy support.]
+Based on these analyses, we predicted that 80\% of studies would result in correlation coefficients between `r post_pred$r_pred_l80[post_pred$y_var == "pi"]` and `r post_pred$r_pred_u80[post_pred$y_var == "pi"]` and that researchers would need sample sizes of at least `r post_pred$n_req[post_pred$y_var == "pi"]` participants to find significant associations ($\alpha = .05$, two-sided) in 80\% of their studies.^[Sample sizes are based on posterior predictions which implied that, for 80\% of studies, the absolute correlation coefficient would be `r post_pred$r_abs[post_pred$y_var == "pi"]` for perceived injustice, `r post_pred$r_abs[post_pred$y_var == "ca"]` for collective action, and `r post_pred$r_abs[post_pred$y_var == "ps"]` for policy support.]
 
@@
 We conducted two kinds of moderator analyses.
-For both analyses, we had an insufficient number of effect sizes to examine moderators for any outcomes except perceived injustice (for details, see SOM-R).
+For both analyses, we had an insufficient number of effect sizes to examine moderators for any outcome except perceived injustice (for details, see SOM-R).
 
@@
 Thus, our meta-analysis seems to support the emerging consensus.
-We use the rest of this section to argue why this conclusion might be premature.
+However, our findings qualify this conclusion in several important ways.
 
@@
 A combination of moderators explained about a third of the between-study variance in the association between intergroup contact and perceived injustice.
-We found that, on average, this association was negative only in studies of adults that measured contact *directly* by asking, for example, about the number of friends from the advantaged outgroup.
-This suggests that, as hypothesized, the 'ironic' effects result from direct contact and not from mere exposure or other contextual factors.
+We found that, on average, this association was negative only in studies of adults that measured contact *directly* (e.g., by asking about the number of friends from the advantaged outgroup).
+This suggests that, as hypothesized, the 'ironic' effects result from direct contact and not from other contextual factors.
 We also found that, on average, effect sizes were greater for studies in post-colonial settings or on short-term migration than for studies in other contexts.
@@
 Support for social change could reduce intergroup contact rather than the other way around.
-For example, disadvantaged-group members involved in collective action might purposefully avoid forming friendships with advantaged-group members.
-Alternatively, the association between intergroup contact and support for social change could be spurious with both being caused by an unobserved confounder.
+For example, disadvantaged-group members involved in collective action might avoid forming friendships with advantaged-group members.
+Alternatively, the observed associations could be spurious with both being caused by an unobserved confounder.
 For example, a disadvantaged-group member's socioeconomic status might both expose them to more advantaged-group members and reduce their perception of injustice.
@@
 
-Further, the observed association between intergroup contact and support for social change could be confounded by an alternative predictor that *increases* support for social change.
+Fourth, the observed association between intergroup contact and support for social change could be confounded by an alternative predictor that *increases* support for social change.
 Supporting Reimer et al.'s [-@reimer_intergroup_2017] argument, we found that positive intergroup contact was not associated with support for social change after controlling for negative contact which, in turn, was associated with *greater* support for social change.
@@
 
-Fourth, we cannot rule out that biases in the literature caused our meta-analysis to overestimate the 'ironic' effects of intergroup contact.
+Finally, we cannot rule out that biases in the literature caused our meta-analysis to overestimate the 'ironic' effects of intergroup contact.
 Publication bias could have prevented studies that found positive or non-significant associations from entering the published literature.
-We used state-of-the-art methods to detect and correct for publication bias, yet did not find conclusive evidence for or against publication bias.
+We used various methods to detect and correct for publication bias, yet did not find conclusive evidence for or against publication bias.
 That said, 61% of samples were either not collected with the intention to study the effects of intergroup contact on a relevant outcome (45%) or from unpublished studies (32%)—and thus unlikely to have been affected by publication bias.
 Another bias that could have affected our findings is that researchers made data-dependent decisions when analyzing data that inflate false-positive findings [@gelman_statistical_2014].
-Future research should use preregistration and other methods to prevent undisclosed flexibility in data collection and analysis.^[To date, one preregistered study has been published [@hassler_large-scale_2020].]
+Future research should use preregistration and other methods to prevent undisclosed flexibility in data collection and analysis.^[Only one preregistered study has been published [@hassler_large-scale_2020].]
 

### 2021-05-14 manuscript/manuscript.tex
submit

@@
 
-\noindent Critics have argued that intergroup contact, psychology's
-most-researched paradigm for reducing prejudice, has the `ironic' effect
-of stifling support for social change in disadvantaged groups. We
-conducted a preregistered meta-analytic test of this effect across 97
-studies with 138 samples of 212,189 disadvantaged-group members. As
-predicted, intergroup contact was, on average, associated with less
-perceived injustice (\(r = -.07\)), collective action (\(r = -.06\)),
-and support for reparative policies (\(r = -.07\)) in disadvantaged
-groups. However, these associations were small, variable, and consistent
-with alterative explanations. Moderator analyses found that these
-associations were strongest in studies on short-term migration and
-post-colonial relations, that measured intergroup contact directly, and
-that involved adults. After controlling for the positive association of
-negative contact with support for social change, positive contact was
-not (negatively) associated with any outcome in studies that measured
+\noindent Growing evidence suggests that intergroup contact, psychology's
+most-researched paradigm for reducing prejudice, might have the `ironic'
+effect of reducing support for social change in disadvantaged groups. We
+conducted a preregistered meta-analysis of this effect across 97 studies
+with 138 samples of 212,189 disadvantaged-group members. As predicted,
+intergroup contact was, on average, associated with less perceived
+injustice (\(r = -.07\)), collective action (\(r = -.06\)), and support
+for reparative policies (\(r = -.07\)). Moderator analyses found that
+associations were strongest in studies of adults that measured
+intergroup contact directly and examined short-term migration or
+post-colonial intergroup relations. After controlling for the positive
+association of negative contact with support for social change, positive
+contact was not associated with any outcome in studies that measured
 both predictors. We close by highlighting open questions about the
-relation between intergroup contact and social change.
+relationship between intergroup contact and social change.
 
@@
 associated with less negative feelings toward outgroup members (for a
-meta-analysis, see Pettigrew \& Tropp, 2006). Most of these studies have
-focused on advantaged-group members' contact experiences with
+meta-analysis, see Pettigrew \& Tropp, 2006). Most studies have focused
+on advantaged-group members' contact experiences with
 disadvantaged-group members (Tropp \& Pettigrew, 2005), guided by the
@@
 they face and undermine their motivation for social change (Dixon et
-al., 2005; Reicher, 2007; Wright, 2003). By stifling disadvantaged-group
+al., 2005; Reicher, 2007; Wright, 2003). By reducing disadvantaged-group
 members' opposition to injustice, intergroup contact might thus have the
@@
 
-Supporting this argument, initial studies provided evidence that, among
-disadvantaged-group members, intergroup contact reduces perceptions of
-injustice (Saguy et al., 2009), discourages collective action (Çakal et
-al., 2011), and diminishes support for reparative policies (Dixon et
-al., 2007). Others, however, have pointed to conflicting evidence (Poore
-et al., 2002) and argued that intergroup contact might instead render
+Supporting this argument, initial studies provided evidence that contact
+with advantaged-group members reduces disadvantaged-group members'
+perceptions of injustice (Saguy et al., 2009), collective action (Çakal
+et al., 2011), and support for reparative policies (Dixon et al., 2007).
+Others, however, have pointed to conflicting evidence (Poore et al.,
+2002) and argued that intergroup contact might instead make
 discrimination more salient and, thereby, increase disadvantaged-group
-members' support for social change (Pettigrew et al., 2011). A decade
-after the initial studies, many more studies have examined the
+members' support for social change (Pettigrew et al., 2011). In the
+decade since the initial studies, many more studies have examined the
 relationships between intergroup contact and support for social change
@@
 Perceived injustice---that is, perceiving unjust group-based deprivation
-or discrimination against the disadvantaged ingroup---is a prerequisite
-to instigating social change (van Zomeren et al., 2008). Researchers
-have argued that positive contact with advantaged-group members could
-contradict perceptions of personal discrimination, undermine negative
-characterizations of the advantaged outgroup, and, thereby, make group
+or discrimination against a disadvantaged ingroup---is a prerequisite to
+instigating social change (van Zomeren et al., 2008). Researchers have
+argued that positive contact with advantaged groups could contradict
+perceptions of personal discrimination and, thereby, make group
 discrimination appear less plausible (Dixon et al., 2010). Positive
@@
 (Sengupta \& Sibley, 2013). To the extent that it reduces perceived
-injustice, intergroup contact hinders social change.
+injustice, intergroup contact reduces support for social change.
 
@@
 toward the advantaged outgroup (Wright \& Lubensky, 2009), and by
-quelling anger about inequality (Tausch et al., 2015) or toward the
-advantaged outgroup (Hayward et al., 2018). To the extent that it
-discourages collective action, intergroup contact hinders social change.
+quelling their anger (Hayward et al., 2018; Tausch et al., 2015). To the
+extent that it discourages collective action, intergroup contact reduces
+support for social change.
 
@@
 that it diminishes support for redistributive policies, intergroup
-contact hinders social change.
-
-We conducted a preregistered meta-analysis of the evidence for the
-hypothesized negative effects of intergroup contact on perceived
-injustice, collective action, and policy support in disadvantaged
-groups. Our first objective was to systematically review the available
-evidence and to evaluate its strengths and limitations. Our second
-objective was to synthesize the available evidence to establish the
-direction and magnitude of the relationships between intergroup contact
-and the three outcomes. Doing so allowed us, first, to determine whether
-the available evidence supports a negative or positive (see Pettigrew et
-al., 2011) relationship between contact and support for social change
-and, second, to estimate the strength of this relationship. Our third
-objective was to explore the variability of this relationship across
-study settings, designs, and other potential moderators. For example, we
-examined whether any effects were confined to Western, Educated,
-Industrialized, Rich, Democratic (WEIRD) settings, the cultural context
-of most psychological research (Henrich et al., 2010). Our fourth
-objective was to assess how robust the available evidence was to
-publication bias.
-
-In addition, we collated the evidence for two alternative accounts of
+contact reduces support for social change.
+
+Our first objective was to systematically review the available evidence
+and to evaluate its strengths and limitations. Our second objective was
+to synthesize the available evidence to establish the direction and
+magnitude of the relationships between intergroup contact and the three
+outcomes. Doing so allowed us to determine whether the available
+evidence supports a negative or positive (see Pettigrew et al., 2011)
+relationship between contact and support for social change and to
+estimate the strength of this relationship. Our third objective was to
+explore the variability of this relationship across study settings,
+designs, and other potential moderators. For example, we examined
+whether any effects were confined to Western, Educated, Industrialized,
+Rich, Democratic (WEIRD) countries, the cultural context of most
+psychological research (Henrich et al., 2010). Our fourth objective was
+to assess how robust the available evidence was to publication bias.
+
+In addition, we examined the evidence for two alternative accounts of
 this relationship. First, we considered studies that measured both
@@
 Sengupta et al. (2015) argued that contact with other members of the
-disadvantaged ingroup would increase political mobilization in
-disadvantaged groups. As outgroup contact places limits on how much
-ingroup contact disadvantaged-group members can have (Pfister et al.,
-2020), the mobilizing effect of ingroup contact is an alternative
-explanation for negative associations between outgroup contact and
-support for social change. Second, we considered studies that measured
-both negative and positive (outgroup) contact as predictors of the three
-outcomes. Researchers (Hayward et al., 2018; Reimer et al., 2017) found
-negative contact with advantaged-group members to be associated with
-greater perceived discrimination and stronger collective action
-intentions. Reimer et al. (2017) argued that, to the extent
-disadvantaged-group members who have more positive contact also tend to
-have less negative contact, the mobilizing effect of negative contact is
-an alternative explanation for negative associations between outgroup
-contact and support for social change.
+disadvantaged ingroup would increase political mobilization. As outgroup
+contact places limits on how much ingroup contact disadvantaged-group
+members can have (Pfister et al., 2020), the mobilizing effect of
+ingroup contact is an alternative explanation for negative associations
+between outgroup contact and support for social change.
+
+Second, we considered studies that measured both negative and positive
+(outgroup) contact as predictors of the three outcomes. Researchers
+(Hayward et al., 2018; Reimer et al., 2017) found negative contact with
+advantaged-group members to be associated with greater perceived
+discrimination and stronger collective action intentions. Reimer et al.
+(2017) argued that, to the extent disadvantaged-group members who have
+more positive contact also tend to have less negative contact, the
+mobilizing effect of negative contact is an alternative explanation for
+negative associations between outgroup contact and support for social
+change.
 
@@
 considered opportunity for contact, as it is a potential precursor to
-and proxy for face-to-face contact, but not imagined or indirect
+and proxy for face-to-face contact, but not imagined or extended
 contact. Similarly, we included studies that measured intergroup contact
@@
 reverse of perceived injustice. We included studies that measured
-personal and/or group discrimination or a mixture of both.
+personal or group discrimination or a mixture of both.
 
@@
 estimates. In addition, we report the posterior probability, based on
-the proportion of posterior samples below zero, that an estimated mean
-effect size is negative.
+the proportion of posterior samples below zero, that the mean effect
+size is negative.
 
@@
 (50\%) ineligible records after reviewing full-text manuscripts. We
-supplemented these records with 15 unpublished studies solicited from
-researchers and 6 records that cited at least three relevant works. Of
-136 eligible studies, we had to exclude 38 (28\%) studies for which we
-could not extract or impute any relevant effect size. At each stage, we
-also excluded studies that used the same data as another study. Our
-final sample comprised effect sizes from \(J = 97\) studies spanning
-\(N = 212,189\) participants in \(I = 138\) samples.
+supplemented these records with 14 unpublished studies and 6 records
+that cited at least three relevant works. Of 135 eligible studies, we
+had to exclude 38 (28\%) studies for which we could not extract or
+impute any relevant effect size. At each stage, we also excluded studies
+that used the same data as another study. Our final sample comprised
+effect sizes from \(J = 97\) studies spanning \(N = 212,189\)
+participants in \(I = 138\) samples (for a complete list of studies, see
+SOM-U).
 
@@
 examine the effects of intergroup contact on the outcomes considered in
-this meta-analysis.\footnote{Many studies examined acculturation
-  processes (Berry, 1997) and measured both intergroup contact and
-  perceived injustice without the relationship between the two being of
-  interest.} Together, these observations highlight both limitations and
+this meta-analysis. Many studies instead examined acculturation
+processes (Berry, 1997) and measured intergroup contact and perceived
+injustice without hypothesizing that the former would influence the
+latter. Together, these observations highlight both limitations and
 strengths of the empirical literature.
@@
 two-sided) in 80\% of their studies.\footnote{Sample sizes are based on
-  posterior predictions from the three models, which implied that, for
-  80\% of studies, the absolute correlation coefficient would be
-  \(|r| > .039\) for perceived injustice, \(|r| > .045\) for collective
-  action, and \(|r| > .035\) for policy support.}
+  posterior predictions which implied that, for 80\% of studies, the
+  absolute correlation coefficient would be \(|r| > .039\) for perceived
+  injustice, \(|r| > .045\) for collective action, and \(|r| > .035\)
+  for policy support.}
 
@@
 an insufficient number of effect sizes to examine moderators for any
-outcomes except perceived injustice (for details, see SOM-R).
+outcome except perceived injustice (for details, see SOM-R).
 
@@
 to be negative than positive. Thus, our meta-analysis seems to support
-the emerging consensus. We use the rest of this section to argue why
-this conclusion might be premature.
+the emerging consensus. However, our findings qualify this conclusion in
+several important ways.
 
@@
 injustice. We found that, on average, this association was negative only
-in studies of adults that measured contact \emph{directly} by asking,
-for example, about the number of friends from the advantaged outgroup.
-This suggests that, as hypothesized, the `ironic' effects result from
-direct contact and not from mere exposure or other contextual factors.
-We also found that, on average, effect sizes were greater for studies in
-post-colonial settings or on short-term migration than for studies in
-other contexts. Future research should systematically investigate
-variance in how contact affects support for social change across
-settings and cultures.
+in studies of adults that measured contact \emph{directly} (e.g., by
+asking about the number of friends from the advantaged outgroup). This
+suggests that, as hypothesized, the `ironic' effects result from direct
+contact and not from other contextual factors. We also found that, on
+average, effect sizes were greater for studies in post-colonial settings
+or on short-term migration than for studies in other contexts. Future
+research should systematically investigate variance in how contact
+affects support for social change across settings and cultures.
 
@@
 intergroup contact rather than the other way around. For example,
-disadvantaged-group members involved in collective action might
-purposefully avoid forming friendships with advantaged-group members.
-Alternatively, the association between intergroup contact and support
-for social change could be spurious with both being caused by an
+disadvantaged-group members involved in collective action might avoid
+forming friendships with advantaged-group members. Alternatively, the
+observed associations could be spurious with both being caused by an
 unobserved confounder. For example, a disadvantaged-group member's
@@
 
-Further, the observed association between intergroup contact and support
+Fourth, the observed association between intergroup contact and support
 for social change could be confounded by an alternative predictor that
@@
 
-Fourth, we cannot rule out that biases in the literature caused our
+Finally, we cannot rule out that biases in the literature caused our
 meta-analysis to overestimate the `ironic' effects of intergroup
@@
 positive or non-significant associations from entering the published
-literature. We used state-of-the-art methods to detect and correct for
+literature. We used various methods to detect and correct for
 publication bias, yet did not find conclusive evidence for or against
@@
 other methods to prevent undisclosed flexibility in data collection and
-analysis.\footnote{To date, one preregistered study has been published
+analysis.\footnote{Only one preregistered study has been published
   (Hässler et al., 2020).}

### 2021-05-14 manuscript/supplemental-materials.Rmd
submit

@@
 Comparisons were inconclusive because we had an insufficient number of effect sizes per category.
+We ran another three random-effects meta-regression models with Muthukrishna et al.'s [-@muthukrishna_beyond_2020] measure of cultural distance, where available, as a continuous moderator variable.
+Because cultural distance was a country-level moderator variable, we used two-level random-effects models in which we estimated country-specific deviations from the mean effect size as well as sample-specific deviations from the country-specific effect size.
+Figure 5 (in the main text) show the inconclusive results for all three outcomes.
+
 Second, we used meta-regression trees to discover interactions between moderator variables that best explained heterogeneity in effect sizes [@li_meta-cart_2017; @li_multiple_2020].
@@
 This result is not surprising, however, as both analyses used fewer than 40 effect sizes, the minimum number required for the algorithm to perform well in detecting even simple interaction effects [@li_meta-cart_2017].
-As both moderator analyses were inconclusive for collective action and policy support, we only report results for perceived injustice in the main text.
+As all moderator analyses were inconclusive for collective action and policy support, we only report results for perceived injustice in the main text.
 

### 2021-05-14 manuscript/supplemental-materials.tex
submit

@@
 inconclusive because we had an insufficient number of effect sizes per
-category. Second, we used meta-regression trees to discover interactions
-between moderator variables that best explained heterogeneity in effect
-sizes (Li et al., 2017, 2020). As recommended, we ran random-effects
+category. We ran another three random-effects meta-regression models
+with Muthukrishna et al.'s (2020) measure of cultural distance, where
+available, as a continuous moderator variable. Because cultural distance
+was a country-level moderator variable, we used two-level random-effects
+models in which we estimated country-specific deviations from the mean
+effect size as well as sample-specific deviations from the
+country-specific effect size. Figure 5 (in the main text) show the
+inconclusive results for all three outcomes.
+
+Second, we used meta-regression trees to discover interactions between
+moderator variables that best explained heterogeneity in effect sizes
+(Li et al., 2017, 2020). As recommended, we ran random-effects
 meta-regression tree analyses using the look-ahead strategy (Li et al.,
@@
 well in detecting even simple interaction effects (Li et al., 2017). As
-both moderator analyses were inconclusive for collective action and
+all moderator analyses were inconclusive for collective action and
 policy support, we only report results for perceived injustice in the
@@
 
+\leavevmode\hypertarget{ref-muthukrishna_beyond_2020}{}%
+Muthukrishna, M., Bell, A. V., Henrich, J., Curtin, C. M., Gedranovich,
+A., McInerney, J., \& Thue, B. (2020). Beyond western, educated,
+industrial, rich, and democratic (WEIRD) psychology: Measuring and
+mapping scales of cultural and psychological distance.
+\emph{Psychological Science}, \emph{31}(6), 678--701.
+\url{https://doi.org/10.1177/0956797620916782}
+
 \endgroup

### 2021-05-14 figures/figure-1.R

@@ -242,4 +242,7 @@ rm(list = ls())
   )      
   
   # Export data (as .rds)
-  write_rds(counts, "figures/figure-1.rds")
+  write_rds(
+    left_join(counts, records, by = "stage"), 
+    "figures/figure-1.rds"
+  )

### 2021-06-07 manuscript/manuscript.Rmd
add starred references

@@
 csl: apa.csl
+nocite: | 
+  @19, @45, @46, @91, @93, @244, @284, @286, @303, @322, @324, @325, @336, @401, @414, @423, @480, @609, @703, @733, @783, @789, @803, @813, @823, @829, @830, @856, @893, @894, @933, @956, @1020, @1042, @1045, @1114, @1163, @1221, @1248, @1376, @1386, @1395, @1407, @1411, @1412, @1494, @1525, @1549, @1576, @1614, @1658, @1695, @1743, @1762, @1807, @1850, @1891, @1914, @1949, @1966, @1993, @2001, @2023, @2033, @2075, @2257, @2309, @2333, @2341, @2375, @2380, @2381, @2382, @2383, @2385, @2391, @2392, @2394, @2395, @2396, @2397, @2398, @2399, @3000, @3005, @3051, @3054, @3060, @3134, @3196, @3201, @3205, @4000, @4001, @4002, @4003, @4004, @4005
 abstract: 
-  Growing evidence suggests that intergroup contact, psychology’s most-researched paradigm for reducing prejudice, might have the ‘ironic’ effect of reducing support for social change in disadvantaged groups.
-We conducted a preregistered meta-analysis of this effect across `r with(dplyr::distinct(readRDS("../data/dl.rds"), sample, id, n), numform::f_comma(dplyr::n_distinct(id)))` studies with `r with(dplyr::distinct(readRDS("../data/dl.rds"), sample, id, n), numform::f_comma(length(sample)))` samples of `r with(dplyr::distinct(readRDS("../data/dl.rds"), sample, id, n), numform::f_comma(sum(n)))` disadvantaged-group members.
+  Growing evidence suggests that intergroup contact, psychology’s most-researched paradigm for reducing prejudice, has the ‘ironic’ effect of reducing support for social change in disadvantaged groups.
+We conducted a preregistered meta-analytic test of this effect across `r with(dplyr::distinct(readRDS("../data/dl.rds"), sample, id, n), numform::f_comma(dplyr::n_distinct(id)))` studies with `r with(dplyr::distinct(readRDS("../data/dl.rds"), sample, id, n), numform::f_comma(length(sample)))` samples of `r with(dplyr::distinct(readRDS("../data/dl.rds"), sample, id, n), numform::f_comma(sum(n)))` disadvantaged-group members.
 As predicted, intergroup contact was, on average, associated with less perceived injustice (`r with(readRDS("../results/results_preregistered_analyses.rds"), paste0("$r = ", numform::f_num(median(r_mean[x_var == "ic" & y_var == "pi"]), digits = 2), "$"))`), collective action (`r with(readRDS("../results/results_preregistered_analyses.rds"), paste0("$r = ", numform::f_num(median(r_mean[x_var == "ic" & y_var == "ca"]), digits = 2), "$"))`), and support for reparative policies (`r with(readRDS("../results/results_preregistered_analyses.rds"), paste0("$r = ", numform::f_num(median(r_mean[x_var == "ic" & y_var == "ps"]), digits = 2), "$"))`).
+However, these associations were small, variable, and consistent with alternative explanations.
 Moderator analyses found that associations were strongest in studies of adults that measured intergroup contact directly and examined short-term migration or post-colonial intergroup relations.
@@
 Hundreds of studies have confirmed that intergroup contact is associated with less negative feelings toward outgroup members [for a meta-analysis, see @pettigrew_meta-analytic_2006].
-Most studies have focused on advantaged-group members' contact experiences with disadvantaged-group members [@tropp_relationships_2005], guided by the idea that reducing advantaged-group members' prejudice will prevent interpersonal discrimination.
+Most of these studies have focused on advantaged-group members' contact experiences with disadvantaged-group members [@tropp_relationships_2005], guided by the idea that reducing advantaged-group members' prejudice will prevent interpersonal discrimination.
 Reducing prejudice, however, is rarely enough to overcome institutional and structural discrimination.
 Instead, as the 2020 Black Lives Matter protests have shown, social change often requires political mobilization by the disadvantaged.
-Critics have argued that, by fostering harmony and reducing conflict, intergroup contact might distract disadvantaged-group members from the injustice they face and undermine their motivation for social change [@dixon_beyond_2005; @reicher_rethinking_2007; @brown_strategic_2003].
-By reducing disadvantaged-group members' opposition to injustice, intergroup contact might thus have the 'ironic' [@saguy_irony_2009], 'sedative' [@cakal_investigation_2011], or 'paradoxical' [@dixon_paradox_2010] effect of hindering social change.
+Critics have argued that, by fostering harmony and reducing conflict, intergroup contact might distract disadvantaged-group members from the injustice they face and, thereby, undermine their motivation for social change [@dixon_beyond_2005; @reicher_rethinking_2007; @brown_strategic_2003].
+By reducing disadvantaged-group members' opposition to injustice, intergroup contact might thus have the 'ironic' [@813], 'sedative' [@284], or 'paradoxical' [@336] effect of hindering social change.
 
-Supporting this argument, initial studies provided evidence that contact with advantaged-group members reduces disadvantaged-group members' perceptions of injustice [@saguy_irony_2009], collective action [@cakal_investigation_2011], and support for reparative policies [@dixon_intergroup_2007].
-Others, however, have pointed to conflicting evidence [@poore_contact_2002] and argued that intergroup contact might instead make discrimination more salient and, thereby, increase disadvantaged-group members' support for social change [@pettigrew_recent_2011].
+Supporting this argument, initial studies provided evidence that contact with advantaged-group members reduces disadvantaged-group members' perceptions of injustice [@813], collective action [@284], and support for reparative policies [@1386].
+Others, however, have pointed to conflicting evidence [@1762] and argued that intergroup contact might instead make discrimination more salient and, thereby, increase disadvantaged-group members' support for social change [@pettigrew_recent_2011].
 In the decade since the initial studies, many more studies have examined the relationships between intergroup contact and support for social change in disadvantaged groups.
@@
 Perceived injustice—that is, perceiving unjust group-based deprivation or discrimination against a disadvantaged ingroup—is a prerequisite to instigating social change [@van_zomeren_toward_2008].
-Researchers have argued that positive contact with advantaged groups could contradict perceptions of personal discrimination and, thereby, make group discrimination appear less plausible [@dixon_paradox_2010].
-Positive contact could further reduce perceived injustice by emphasizing commonalities over differences [@saguy_irony_2009] and by motivating disadvantaged-group members to adopt system-justifying ideologies [@sengupta_perpetuating_2013].
+Researchers have argued that positive contact with advantaged groups could contradict perceptions of personal discrimination and, thereby, make group discrimination appear less plausible [@336].
+Positive contact could further reduce perceived injustice by emphasizing commonalities over differences [@813] and by motivating disadvantaged-group members to adopt system-justifying ideologies [@1695].
 To the extent that it reduces perceived injustice, intergroup contact reduces support for social change.
 
-Collective action—that is, any action directed at improving the conditions of the disadvantaged ingroup [@wright_responding_1990]—is crucial to achieving social change because advantaged-group members rarely surrender their advantages without sustained pressure from disadvantaged-group members [@blumer_race_1958; for a review, see @dixon_beyond_2012].
-Researchers have argued that intergroup contact could discourage disadvantaged-group members from engaging in collective action by diminishing their perceived discrimination [@tropp_crossethnic_2012], by blurring boundaries between the disadvantaged ingroup and the advantaged outgroup [@saguy_irony_2009], by reducing negative attitudes toward the advantaged outgroup [@wright_struggle_2009], and by quelling their anger  [@hayward_how_2018; @tausch_how_2015].
+Collective action is any action directed at improving the conditions of the disadvantaged ingroup [@wright_responding_1990].
+Collective action is crucial to achieving social change because advantaged-group members rarely give up their advantages without sustained pressure from disadvantaged-group members [@blumer_race_1958; for a review, see @dixon_beyond_2012].
+Researchers have argued that intergroup contact could discourage disadvantaged-group members from engaging in collective action by diminishing their perceived discrimination [@1743], by blurring boundaries between the disadvantaged ingroup and the advantaged outgroup [@813], by reducing negative attitudes toward the advantaged outgroup [@wright_struggle_2009], and by quelling their anger  [@2309; @2375].
 To the extent that it discourages collective action, intergroup contact reduces support for social change.
@@
 Disadvantaged-group members, who stand to benefit from their implementation, are important advocates for these policies.
-Researchers have argued that intergroup contact could diminish disadvantaged-group members’ support for redistributive policies by creating sympathy for advantaged-group members [@dixon_intergroup_2007], by fostering positive outgroup attitudes and reducing attention to inequality [@saguy_irony_2009], and by increasing their endorsement of system-justifying ideologies [@sengupta_perpetuating_2013].
+Researchers have argued that intergroup contact could diminish disadvantaged-group members’ support for redistributive policies by creating sympathy for advantaged-group members [@1386], by fostering positive outgroup attitudes and reducing attention to inequality [@813], and by increasing their endorsement of system-justifying ideologies [@1695].
 To the extent that it diminishes support for redistributive policies, intergroup contact reduces support for social change.
@@
 Second, we considered studies that measured both negative and positive (outgroup) contact as predictors of the three outcomes.
-Researchers [@hayward_how_2018; @reimer_intergroup_2017] found negative contact with advantaged-group members to be associated with greater perceived discrimination and stronger collective action intentions.
-@reimer_intergroup_2017 argued that, to the extent disadvantaged-group members who have more positive contact also tend to have less negative contact, the mobilizing effect of negative contact is an alternative explanation for negative associations between outgroup contact and support for social change.
+Researchers [@2309; @956] found negative contact with advantaged-group members to be associated with greater perceived discrimination and stronger collective action intentions.
+@956 argued that, to the extent disadvantaged-group members who have more positive contact also tend to have less negative contact, the mobilizing effect of negative contact is an alternative explanation for negative associations between outgroup contact and support for social change.
 
@@
 By using partial correlations, we estimated the effect of one form of contact while controlling for the other.
-Across `r alt_results$N[alt_results$x_var == "nc" & alt_results$y_var == "pi"]` participants from `r alt_results$I[alt_results$x_var == "nc" & alt_results$y_var == "pi"]` samples in `r alt_results$J[alt_results$x_var == "nc" & alt_results$y_var == "pi"]` studies, we found stronger evidence for a positive association between negative contact and perceived injustice (`r alt_results$text[alt_results$x_var == "nc" & alt_results$y_var == "pi"]`) than for a negative association between positive contact and perceived injustice (`r alt_results$text[alt_results$x_var == "pc" & alt_results$y_var == "pi"]`).
+Across `r alt_results$N[alt_results$x_var == "nc" & alt_results$y_var == "pi"]` participants from `r alt_results$I[alt_results$x_var == "nc" & alt_results$y_var == "pi"]` samples in `r alt_results$J[alt_results$x_var == "nc" & alt_results$y_var == "pi"]` studies, we found somewhat stronger evidence for a positive association between negative contact and perceived injustice (`r alt_results$text[alt_results$x_var == "nc" & alt_results$y_var == "pi"]`) than for a negative association between positive contact and perceived injustice (`r alt_results$text[alt_results$x_var == "pc" & alt_results$y_var == "pi"]`).
 Across `r alt_results$N[alt_results$x_var == "nc" & alt_results$y_var == "ca"]` participants from `r alt_results$I[alt_results$x_var == "nc" & alt_results$y_var == "ca"]` samples in `r alt_results$J[alt_results$x_var == "nc" & alt_results$y_var == "ca"]` studies, we again found stronger evidence for a positive association between negative contact and collective action (`r alt_results$text[alt_results$x_var == "nc" & alt_results$y_var == "ca"]`) than for a negative association between positive contact and collective action (`r alt_results$text[alt_results$x_var == "pc" & alt_results$y_var == "ca"]`).
@@
 This suggests that, as hypothesized, the 'ironic' effects result from direct contact and not from other contextual factors.
-We also found that, on average, effect sizes were greater for studies in post-colonial settings or on short-term migration than for studies in other contexts.
+We also found that, on average, effect sizes were greater for studies in (post-)colonial settings or on short-term migration than for studies in other contexts.
 Future research should systematically investigate variance in how contact affects support for social change across settings and cultures.
@@
 For example, a disadvantaged-group member's socioeconomic status might both expose them to more advantaged-group members and reduce their perception of injustice.
-Future research should prioritize longitudinal studies to confirm the direction of the observed associations and (field) experiments to rule out confounding and other alternative explanations.^[Published research includes only three longitudinal studies [@koschate_when_2012; @reimer_intergroup_2017; @tropp_crossethnic_2012], all of which conflated within-person change and between-person stability [@hamaker_critique_2015], two experimental studies with a no-contact control condition [@becker_friend_2013; @droogendyk_renewed_2016], and two intervention studies [@reimer_building_2021; @shani_effect_2017].]
+Future research should prioritize longitudinal studies to confirm the direction of the observed associations and (field) experiments to rule out confounding and other alternative explanations.^[Published research includes only three longitudinal studies [@401; @956; @1743], all of which conflated within-person change and between-person stability [@hamaker_critique_2015], two experimental studies with a no-contact control condition [@2075; @2033], and two intervention studies [@2399; @789].]
 
 Fourth, the observed association between intergroup contact and support for social change could be confounded by an alternative predictor that *increases* support for social change.
-Supporting Reimer et al.'s [-@reimer_intergroup_2017] argument, we found that positive intergroup contact was not associated with support for social change after controlling for negative contact which, in turn, was associated with *greater* support for social change.
+Supporting Reimer et al.'s [-@956] argument, we found that positive intergroup contact was not associated with support for social change after controlling for negative contact which, in turn, was associated with *greater* support for social change.
 We found mixed evidence for ingroup contact as an alternative explanation for the 'ironic' effects of intergroup contact [@sengupta_ingroup_2015] but note that few studies measured both ingroup and outgroup contact.
@@
 Another bias that could have affected our findings is that researchers made data-dependent decisions when analyzing data that inflate false-positive findings [@gelman_statistical_2014].
-Future research should use preregistration and other methods to prevent undisclosed flexibility in data collection and analysis.^[Only one preregistered study has been published [@hassler_large-scale_2020].]
+Future research should use preregistration and other methods to prevent undisclosed flexibility in data collection and analysis.^[Only one preregistered study has been published [@3054].]
 
@@
 
-\newpage
+# References
 
-# References
+\noindent References marked with an asterisk are studies included in the meta-analysis.
 

### 2021-06-07 manuscript/manuscript.tex
add starred references

@@
 \noindent Growing evidence suggests that intergroup contact, psychology's
-most-researched paradigm for reducing prejudice, might have the `ironic'
-effect of reducing support for social change in disadvantaged groups. We
-conducted a preregistered meta-analysis of this effect across 97 studies
-with 138 samples of 212,189 disadvantaged-group members. As predicted,
-intergroup contact was, on average, associated with less perceived
-injustice (\(r = -.07\)), collective action (\(r = -.06\)), and support
-for reparative policies (\(r = -.07\)). Moderator analyses found that
-associations were strongest in studies of adults that measured
-intergroup contact directly and examined short-term migration or
-post-colonial intergroup relations. After controlling for the positive
-association of negative contact with support for social change, positive
-contact was not associated with any outcome in studies that measured
-both predictors. We close by highlighting open questions about the
-relationship between intergroup contact and social change.
+most-researched paradigm for reducing prejudice, has the `ironic' effect
+of reducing support for social change in disadvantaged groups. We
+conducted a preregistered meta-analytic test of this effect across 98
+studies with 140 samples of 213,085 disadvantaged-group members. As
+predicted, intergroup contact was, on average, associated with less
+perceived injustice (\(r = -.07\)), collective action (\(r = -.06\)),
+and support for reparative policies (\(r = -.07\)). However, these
+associations were small, variable, and consistent with alternative
+explanations. Moderator analyses found that associations were strongest
+in studies of adults that measured intergroup contact directly and
+examined short-term migration or post-colonial intergroup relations.
+After controlling for the positive association of negative contact with
+support for social change, positive contact was not associated with any
+outcome in studies that measured both predictors. We close by
+highlighting open questions about the relationship between intergroup
+contact and social change.
 
@@
 associated with less negative feelings toward outgroup members (for a
-meta-analysis, see Pettigrew \& Tropp, 2006). Most studies have focused
-on advantaged-group members' contact experiences with
+meta-analysis, see Pettigrew \& Tropp, 2006). Most of these studies have
+focused on advantaged-group members' contact experiences with
 disadvantaged-group members (Tropp \& Pettigrew, 2005), guided by the
@@
 contact might distract disadvantaged-group members from the injustice
-they face and undermine their motivation for social change (Dixon et
-al., 2005; Reicher, 2007; Wright, 2003). By reducing disadvantaged-group
-members' opposition to injustice, intergroup contact might thus have the
-`ironic' (Saguy et al., 2009), `sedative' (Çakal et al., 2011), or
-`paradoxical' (Dixon et al., 2010) effect of hindering social change.
+they face and, thereby, undermine their motivation for social change
+(Dixon et al., 2005; Reicher, 2007; Wright, 2003). By reducing
+disadvantaged-group members' opposition to injustice, intergroup contact
+might thus have the `ironic' (Saguy et al., 2009), `sedative' (Çakal et
+al., 2011), or `paradoxical' (Dixon et al., 2010) effect of hindering
+social change.
 
@@
 
-Collective action---that is, any action directed at improving the
-conditions of the disadvantaged ingroup (Wright et al., 1990)---is
+Collective action is any action directed at improving the conditions of
+the disadvantaged ingroup (Wright et al., 1990). Collective action is
 crucial to achieving social change because advantaged-group members
-rarely surrender their advantages without sustained pressure from
+rarely give up their advantages without sustained pressure from
 disadvantaged-group members (Blumer, 1958; for a review, see Dixon et
@@
 (50\%) ineligible records after reviewing full-text manuscripts. We
-supplemented these records with 14 unpublished studies and 6 records
-that cited at least three relevant works. Of 135 eligible studies, we
+supplemented these records with 15 unpublished studies and 6 records
+that cited at least three relevant works. Of 136 eligible studies, we
 had to exclude 38 (28\%) studies for which we could not extract or
@@
 that used the same data as another study. Our final sample comprised
-effect sizes from \(J = 97\) studies spanning \(N = 212,189\)
-participants in \(I = 138\) samples (for a complete list of studies, see
+effect sizes from \(J = 98\) studies spanning \(N = 213,085\)
+participants in \(I = 140\) samples (for a complete list of studies, see
 SOM-U).
@@
 and the United States (\(N = 60,983\); Figure 2a), most samples were
-collected in North America (\(I = 48\)) and Europe (\(I = 41\)), with
+collected in North America (\(I = 48\)) and Europe (\(I = 43\)), with
 few samples from South America and Africa (Figure 2b). Most samples
 focused on relative inequalities that resulted from long-term migration
-(\(I = 57\)), slavery (\(I = 19\)), colonization (\(I = 19\)), and
+(\(I = 59\)), slavery (\(I = 19\)), colonization (\(I = 19\)), and
 short-term migration (\(I = 14\)). With few exceptions, studies used
 observational, cross-sectional survey designs. Samples sizes ranged from
-64 to 49,764 (\(\textit{Mdn} = 283\)). Unlike most psychological
+64 to 49,764 (\(\textit{Mdn} = 287\)). Unlike most psychological
 research, 2 in 5 samples used probability or representative sampling. Of
-all samples, 54\% (\(I = 75\)) were collected with the intention to
+all samples, 55\% (\(I = 77\)) were collected with the intention to
 examine the effects of intergroup contact on the outcomes considered in
@@
 
-\textbf{\emph{Perceived Injustice.}} Across 202,741 participants from
-124 samples in 85 studies, we found strong evidence for a weak
+\textbf{\emph{Perceived Injustice.}} Across 203,637 participants from
+126 samples in 86 studies, we found strong evidence for a weak
 association (\(r = -.07, [-.10, -.04]\)) between intergroup contact and
@@
 correlation coefficients varied across studies
-(\(\tau_J = .14, [.12, .17]\)) and across samples within studies
+(\(\tau_J = .14, [.11, .17]\)) and across samples within studies
 (\(\tau_I = .08, [.05, .12]\)). Based on these analyses, we predicted
 that 80\% of studies would result in correlation coefficients between
--.25 and .10 and that researchers would need sample sizes of at least
-2,549 participants to find significant associations (\(\alpha = .05\),
+-.25 and .11 and that researchers would need sample sizes of at least
+2,542 participants to find significant associations (\(\alpha = .05\),
 two-sided) in 80\% of their studies.\footnote{Sample sizes are based on
@@
 \includegraphics[scale=1]{../figures/figure-5}
-\caption*{\textit{Note.} We had data from too few countries to reach firm conclusions about the direction of these associations for perceived injustice ($\beta = -0.34, [-1.41, 0.81]$; $\Pr (\beta < 0) = 73.5\%$), collective action ($\beta = -0.09, [-1.60, 1.37]$; $\Pr (\beta < 0) = 55.1\%$), and policy support ($\beta = -0.92, [-2.13, 0.55]$; $\Pr (\beta < 0) = 90.3\%$).}
+\caption*{\textit{Note.} We had data from too few countries to reach firm conclusions about the direction of these associations for perceived injustice ($\beta = -0.38, [-1.45, 0.72]$; $\Pr (\beta < 0) = 75.7\%$), collective action ($\beta = -0.09, [-1.60, 1.37]$; $\Pr (\beta < 0) = 55.1\%$), and policy support ($\beta = -0.92, [-2.13, 0.55]$; $\Pr (\beta < 0) = 90.3\%$).}
 \label{fig:f5}
@@
 (\(r = -.18, [-.23, -.13]\)) than in other settings
-(\(r = -.09, [-.12, -.05]\)).
+(\(r = -.09, [-.13, -.06]\)).
 
@@
 By using partial correlations, we estimated the effect of one form of
-contact while controlling for the other. Across 105,374 participants
-from 27 samples in 16 studies, we found stronger evidence for a positive
-association between negative contact and perceived injustice
-(\(r = .14, [.05, .23]\); \(\Pr (r > 0) = 99.8\%\)) than for a negative
+contact while controlling for the other. Across 106,270 participants
+from 29 samples in 17 studies, we found somewhat stronger evidence for a
+positive association between negative contact and perceived injustice
+(\(r = .14, [.06, .23]\); \(\Pr (r > 0) = 99.9\%\)) than for a negative
 association between positive contact and perceived injustice
-(\(r = -.05, [-.11, .01]\); \(\Pr (r < 0) = 94.8\%\)). Across 107,451
+(\(r = -.05, [-.10, .01]\); \(\Pr (r < 0) = 95.6\%\)). Across 107,451
 participants from 16 samples in 9 studies, we again found stronger
@@
 negative association between positive contact and policy support
-(\(r = .03, [-.03, .10]\); \(\Pr (r < 0) = 12.7\%\)). Across 110,257
-participants from 29 samples in 17 studies, we found a negative
+(\(r = .03, [-.03, .10]\); \(\Pr (r < 0) = 12.7\%\)). Across 111,153
+participants from 31 samples in 18 studies, we found a negative
 association between positive and negative contact
-(\(r = -.16, [-.25, -.05]\); \(\Pr (r < 0) = 99.8\%\)).
+(\(r = -.16, [-.25, -.07]\); \(\Pr (r < 0) = 99.8\%\)).
 
@@
 contact and not from other contextual factors. We also found that, on
-average, effect sizes were greater for studies in post-colonial settings
-or on short-term migration than for studies in other contexts. Future
-research should systematically investigate variance in how contact
-affects support for social change across settings and cultures.
+average, effect sizes were greater for studies in (post-)colonial
+settings or on short-term migration than for studies in other contexts.
+Future research should systematically investigate variance in how
+contact affects support for social change across settings and cultures.
 
@@
 
-\newpage
-
 \hypertarget{references}{%
@@
 
+\noindent References marked with an asterisk are studies included in the
+meta-analysis.
+
 \begingroup
@@
 \hypertarget{refs}{}
-\leavevmode\hypertarget{ref-becker_friend_2013}{}%
-Becker, J. C., Wright, S. C., Lubensky, M. E., \& Zhou, S. (2013).
+\leavevmode\hypertarget{ref-3201}{}%
+*Albzour, M., Penic, S., Nasser, R., \& Green, E. G. T. (2019). Support
+for ``normalization'' of relations between Palestinians and Israelis,
+and how it relates to contact and resistance in the West Bank.
+\emph{Journal of Social and Political Psychology}, \emph{7}(2),
+978--996. \url{https://doi.org/10.5964/jspp.v7i2.877}
+
+\leavevmode\hypertarget{ref-2023}{}%
+*Bagci, S. C. (2014). \emph{Cross-ethnic friendships in multiethnic
+educational settings: Consequences for psychological, academic and
+motivational outcomes among young adolescents} {[}Doctoral dissertation,
+Goldsmiths, University of London{]}.
+\url{https://doi.org/10.25602/GOLD.00011030}
+
+\leavevmode\hypertarget{ref-2395}{}%
+*Bagci, S. C., \& Stathi, S. (2020). \emph{Secure and insecure ingroup
+identification as mediators between identity threat and psychological
+well-being and intergroup bias} {[}Manuscript in preparation{]}. Faculty
+of Arts and Social Sciences, Sabanci University.
+
+\leavevmode\hypertarget{ref-423}{}%
+*Bagci, S. C., Stathi, S., \& Piyale, Z. E. (2019). Imagined contact
+facilitates acculturation, sometimes: Contradicting evidence from two
+sociocultural contexts. \emph{Cultural Diversity and Ethnic Minority
+Psychology}, \emph{25}(4), 539--552.
+\url{https://doi.org/10.1037/cdp0000256}
+
+\leavevmode\hypertarget{ref-322}{}%
+*Bagci, S. C., \& Turnuklu, A. (2019). Intended, unintended, and unknown
+consequences of contact: The role of positive-negative contact on
+outgroup attitudes, collective action tendencies, and psychological
+well-being. \emph{Social Psychology}, \emph{50}(1), 7--23.
+\url{https://doi.org/10.1027/1864-9335/a000355}
+
+\leavevmode\hypertarget{ref-414}{}%
+*Bagci, S. C., Turnuklu, A., \& Bekmezci, E. (2018a). Cross-group
+friendships and psychological well-being: A dual pathway through social
+integration and empowerment. \emph{British Journal of Social
+Psychology}, \emph{57}(4), 773--792.
+\url{https://doi.org/10.1111/bjso.12267}
+
+\leavevmode\hypertarget{ref-2257}{}%
+*Bagci, S. C., Turnuklu, A., \& Bekmezci, E. (2018b). The buffering role
+of in-group identification and intergroup contact on the association
+between perceived discrimination and mental health. \emph{Journal of
+Community \& Applied Social Psychology}, \emph{28}(5), 293--305.
+\url{https://doi.org/10.1002/casp.2357}
+
+\leavevmode\hypertarget{ref-2396}{}%
+*Bagci, S. C., Verkuyten, M., Koc, Y., Turnuklu, A., Piyale, Z. E., \&
+Bekmezci, E. (2020). Being tolerated and being discriminated against:
+Links to psychological well-being through threatened social identity
+needs. \emph{European Journal of Social Psychology}, \emph{50}(7),
+1463--1477. \url{https://doi.org/10.1002/ejsp.2699}
+
+\leavevmode\hypertarget{ref-2075}{}%
+*Becker, J. C., Wright, S. C., Lubensky, M. E., \& Zhou, S. (2013).
 Friend or ally: Whether cross-group contact undermines collective action
@@
 
+\leavevmode\hypertarget{ref-1045}{}%
+*Benner, A. D., \& Wang, Y. (2017). Racial/ethnic discrimination and
+adolescents' well-being: The role of cross-ethnic friendships and
+friends' experiences of discrimination. \emph{Child Development},
+\emph{88}(2), 493--504. \url{https://doi.org/10.1111/cdev.12606}
+
 \leavevmode\hypertarget{ref-berry_immigration_1997}{}%
@@
 
+\leavevmode\hypertarget{ref-2397}{}%
+*Bond, J., \& Dixon, J. (2020). \emph{White and Black UK residents'
+support for collective action for the removal of public symbols
+associated with historical racism in England} {[}Unpublished dataset{]}.
+The Open University.
+
 \leavevmode\hypertarget{ref-borenstein_introduction_2009}{}%
@@
 (2009). \emph{Introduction to meta-analysis}. Wiley.
+
+\leavevmode\hypertarget{ref-2398}{}%
+*Bracegirdle, C. (2020). \emph{Social network study of two diverse
+schools in Northern England} {[}Unpublished dataset{]}. University of
+Oxford.
 
@@
 
-\leavevmode\hypertarget{ref-cakal_investigation_2011}{}%
-Çakal, H., Hewstone, M., Schwär, G., \& Heath, A. (2011). An
+\leavevmode\hypertarget{ref-480}{}%
+*Castro, V. S. (2005). Discriminación percibida y autoestima en jóvenes
+de grupos minoritarios y mayoritarios en Costa Rica {[}Perceived
+discrimination and self-esteem among ethnic majority and minority youths
+in Costa Rica{]}. \emph{Revista Interamericana de Psicología},
+\emph{39}(1), 93--106.
+
+\leavevmode\hypertarget{ref-1914}{}%
+*Castro Solano, A., \& Lupano Perugini, M. L. (2013). Predictores de la
+adaptación sociocultural de estudiantes universitarios extranjeros en
+Argentina {[}Predictors of socio-cultural adaptation of foreign
+university students in Argentina{]}. \emph{Interdisciplinaria},
+\emph{30}(2), 265--281.
+
+\leavevmode\hypertarget{ref-3205}{}%
+*Cernat, V. (2019). Interminority contact and solidarity under conflict:
+Evidence from the Hungarian and Roma minorities in Romania. \emph{Basic
+and Applied Social Psychology}, \emph{41}(5), 326--339.
+\url{https://doi.org/10.1080/01973533.2019.1652179}
+
+\leavevmode\hypertarget{ref-91}{}%
+*Chang, T. K. (2017). \emph{Psychological distress of Asian
+international students: Applying intergroup contact theory} {[}Doctoral
+dissertation, Indiana University{]}. ProQuest Dissertations and Theses
+Global.
+
+\leavevmode\hypertarget{ref-1163}{}%
+*Cruse, S. L. (2015). \emph{The relationship of ethnic identity,
+perceived discrimination, and outgroup contact to racial attitudes
+toward White people in African American college students} {[}Doctoral
+dissertation, University of Kansas{]}. ProQuest Dissertations and Theses
+Global.
+
+\leavevmode\hypertarget{ref-1248}{}%
+*Çakal, H., Hewstone, M., Güler, M., \& Heath, A. (2016). Predicting
+support for collective action in the conflict between Turks and Kurds:
+Perceived threats as a mediator of intergroup contact and social
+identity. \emph{Group Processes \& Intergroup Relations}, \emph{19}(6),
+732--752. \url{https://doi.org/10.1177/1368430216641303}
+
+\leavevmode\hypertarget{ref-284}{}%
+*Çakal, H., Hewstone, M., Schwär, G., \& Heath, A. (2011). An
 investigation of the social identity model of collective action and the
@@
 
+\leavevmode\hypertarget{ref-1614}{}%
+*Çelebi, E., Verkuyten, M., \& Smyrnioti, N. (2016). Support for Kurdish
+language rights in Turkey: The roles of ethnic group, group
+identifications, contact, and intergroup perceptions. \emph{Ethnic and
+Racial Studies}, \emph{39}(6), 1034--1051.
+\url{https://doi.org/10.1080/01419870.2015.1103881}
+
+\leavevmode\hypertarget{ref-783}{}%
+*de Vroome, T., Verkuyten, M., \& Martinovic, B. (2014). Host national
+identification of immigrants in the Netherlands. \emph{International
+Migration Review}, \emph{48}(1), 1--27.
+\url{https://doi.org/10.1111/imre.12063}
+
+\leavevmode\hypertarget{ref-3196}{}%
+*Di Bernardo, G. A., Vezzali, L., Stathi, S., McKeown Jones, S., Cocco,
+V. M., Saguy, T., \& Dixon, J. (2019). Fostering social change among
+advantaged and disadvantaged group members: Integrating intergroup
+contact and social identity perspectives on collective action.
+\emph{Group Processes \& Intergroup Relations}.
+\url{https://doi.org/10.1177/1368430219889134}
+
+\leavevmode\hypertarget{ref-1807}{}%
+*Di Saint Pierre, F., Martinovic, B., \& de Vroome, T. (2015). Return
+wishes of refugees in the Netherlands: The role of integration, host
+national identification and perceived discrimination. \emph{Journal of
+Ethnic and Migration Studies}, \emph{41}(11), 1836--1857.
+\url{https://doi.org/10.1080/1369183X.2015.1023184}
+
+\leavevmode\hypertarget{ref-93}{}%
+*Dixon, J., Çakal, H., Khan, W., Osmany, M., Majumdar, S., \& Hassan, M.
+(2017). Contact, political solidarity and collective action: An Indian
+case study of relations between historically disadvantaged communities.
+\emph{Journal of Community \& Applied Social Psychology}, \emph{27}(1),
+83--95. \url{https://doi.org/10.1002/casp.2296}
+
 \leavevmode\hypertarget{ref-dixon_beyond_2005}{}%
@@
 
-\leavevmode\hypertarget{ref-dixon_intergroup_2007}{}%
-Dixon, J., Durrheim, K., \& Tredoux, C. (2007). Intergroup contact and
+\leavevmode\hypertarget{ref-1386}{}%
+*Dixon, J., Durrheim, K., \& Tredoux, C. (2007). Intergroup contact and
 attitudes toward the principle and practice of racial equality.
@@
 
-\leavevmode\hypertarget{ref-dixon_paradox_2010}{}%
-Dixon, J., Durrheim, K., Tredoux, C., Tropp, L., Clack, B., \& Eaton, L.
-(2010). A paradox of integration? Interracial contact, prejudice
-reduction, and perceptions of racial discrimination: A paradox of
-integration. \emph{Journal of Social Issues}, \emph{66}(2), 401--416.
+\leavevmode\hypertarget{ref-336}{}%
+*Dixon, J., Durrheim, K., Tredoux, C., Tropp, L. R., Clack, B., \&
+Eaton, L. (2010). A paradox of integration? Interracial contact,
+prejudice reduction, and perceptions of racial discrimination.
+\emph{Journal of Social Issues}, \emph{66}(2), 401--416.
 \url{https://doi.org/10.1111/j.1540-4560.2010.01652.x}
@@
 
-\leavevmode\hypertarget{ref-droogendyk_renewed_2016}{}%
-Droogendyk, L., Louis, W. R., \& Wright, S. C. (2016). Renewed promise
+\leavevmode\hypertarget{ref-2033}{}%
+*Droogendyk, L., Louis, W. R., \& Wright, S. C. (2016). Renewed promise
 for positive cross-group contact: The role of supportive contact in
@@
 317--327. \url{https://doi.org/10.1037/cbs0000058}
+
+\leavevmode\hypertarget{ref-4001}{}%
+*Eller, A., Abrams, D., Wright, S. C., \& Davies, B. (2020). Effects of
+intergroup contact and relative gratification vs deprivation on
+prejudice on both sides of the U.S./Mexico status divide. \emph{Journal
+of Applied Social Psychology}, \emph{50}(7), 406--417.
+\url{https://doi.org/10.1111/jasp.12669}
+
+\leavevmode\hypertarget{ref-1549}{}%
+*Forbes, J. M. (2001). \emph{Affirmative action attitudes in black and
+white} {[}Doctoral dissertation, Wayne State University{]}. ProQuest
+Dissertations and Theses Global.
+
+\leavevmode\hypertarget{ref-325}{}%
+*Franco, M. (2019). Let the racism tell you who your friends are: The
+effects of racism on social connections and life-satisfaction for
+Multiracial people. \emph{International Journal of Intercultural
+Relations}, \emph{69}, 54--65.
+\url{https://doi.org/10.1016/j.ijintrel.2018.12.005}
 
@@
 
+\leavevmode\hypertarget{ref-1576}{}%
+*Goto, S. G., Gee, G. C., \& Takeuchi, D. T. (2002). Strangers still?
+The experience of discrimination among Chinese Americans. \emph{Journal
+of Community Psychology}, \emph{30}(2), 211--224.
+\url{https://doi.org/10.1002/jcop.9998}
+
+\leavevmode\hypertarget{ref-1949}{}%
+*Haase, A., Rohmann, A., \& Hallmann, K. (2019). An ecological approach
+to psychological adjustment: A field survey among refugees in Germany.
+\emph{International Journal of Intercultural Relations}, \emph{68},
+44--54. \url{https://doi.org/10.1016/j.ijintrel.2018.10.003}
+
 \leavevmode\hypertarget{ref-hamaker_critique_2015}{}%
@@
 
-\leavevmode\hypertarget{ref-hayward_how_2018}{}%
-Hayward, L. E., Tropp, L. R., Hornsey, M. J., \& Barlow, F. K. (2018).
+\leavevmode\hypertarget{ref-4003}{}%
+*Hayward, L. E., Hornsey, M. J., Tropp, L. R., \& Barlow, F. K. (2017).
+Positive and negative intergroup contact predict Black and White
+Americans' judgments about police violence against Black Americans.
+\emph{Journal of Applied Social Psychology}, \emph{47}(11), 605--615.
+\url{https://doi.org/10.1111/jasp.12463}
+
+\leavevmode\hypertarget{ref-2309}{}%
+*Hayward, L. E., Tropp, L. R., Hornsey, M. J., \& Barlow, F. K. (2018).
 How negative contact and positive contact with Whites predict collective
@@
 
-\leavevmode\hypertarget{ref-hassler_large-scale_2020}{}%
-Hässler, T., Ullrich, J., Bernardino, M., Shnabel, N., Laar, C. V.,
+\leavevmode\hypertarget{ref-3054}{}%
+*Hässler, T., Ullrich, J., Bernardino, M., Shnabel, N., Laar, C. V.,
 Valdenegro, D., Sebben, S., Tropp, L. R., Visintin, E. P., González, R.,
@@
 
+\leavevmode\hypertarget{ref-1407}{}%
+*Head, R. N. (2013). \emph{Coping with perceived discrimination}
+{[}Doctoral dissertation, North Carolina State University{]}. ProQuest
+Dissertations and Theses Global.
+
 \leavevmode\hypertarget{ref-henrich_weirdest_2010}{}%
@@
 
-\leavevmode\hypertarget{ref-koschate_when_2012}{}%
-Koschate, M., Hofmann, W., \& Schmitt, M. (2012). When East meets West:
+\leavevmode\hypertarget{ref-1494}{}%
+*Herda, D. E. (2013). \emph{Hostile contact: Self-reports of
+interpersonal discrimination among Blacks, Whites and Latinos in
+Chicago} {[}Doctoral dissertation, University of California, Davis{]}.
+ProQuest Dissertations and Theses Global.
+
+\leavevmode\hypertarget{ref-324}{}%
+*Herda, D. E. (2016). The specter of discrimination: Fear of
+interpersonal racial discrimination among adolescents in Chicago.
+\emph{Social Science Research}, \emph{55}, 48--62.
+\url{https://doi.org/10.1016/j.ssresearch.2015.09.010}
+
+\leavevmode\hypertarget{ref-609}{}%
+*Hui, B. P. H., Chen, S. X., Leung, C. M., \& Berry, J. W. (2015).
+Facilitating adaptation and intercultural contact: The role of
+integration and multicultural ideology in dominant and non-dominant
+groups. \emph{International Journal of Intercultural Relations},
+\emph{45}, 70--84. \url{https://doi.org/10.1016/j.ijintrel.2015.01.002}
+
+\leavevmode\hypertarget{ref-2001}{}%
+*Hunt, M. O., Wise, L. A., Jipguep, M.-C., Cozier, Y. C., \& Rosenberg,
+L. (2007). Neighborhood racial composition and perceptions of racial
+discrimination: Evidence from the Black women's health study.
+\emph{Social Psychology Quarterly}, \emph{70}(3), 272--289.
+\url{https://doi.org/10.1177/019027250707000306}
+
+\leavevmode\hypertarget{ref-2341}{}%
+*Jasinskaja-Lahti, I., Mähönen, T. A., \& Liebkind, K. (2012). Identity
+and attitudinal reactions to perceptions of inter-group interactions
+among ethnic migrants: A longitudinal study. \emph{British Journal of
+Social Psychology}, \emph{51}(2), 312--329.
+\url{https://doi.org/10.1111/j.2044-8309.2011.02059.x}
+
+\leavevmode\hypertarget{ref-19}{}%
+*Jiang, Q., Aricat, R. G., Chib, A., Chia, A., Tan, S. M., Tan, L., \&
+Woo, Z. W. (2016). Silent but brewing: Reactive ethnicity and
+interculturality among Chinese students in Singapore. \emph{Journal of
+Intercultural Communication}, \emph{40}.
+\url{http://www.immi.se/intercultural/nr40/aricat.html}
+
+\leavevmode\hypertarget{ref-303}{}%
+*Jones, M. L. (2017). \emph{Attitudes and experiences of close
+interethnic friendships among Native emerging adults: A mixed-methods
+investigation} {[}Doctoral dissertation, Utah State University{]}.
+ProQuest Dissertations and Theses Global.
+
+\leavevmode\hypertarget{ref-856}{}%
+*Kamberi, E., Martinovic, B., \& Verkuyten, M. (2017). Intergroup
+contact and minority group empowerment: The perspective of Roma and
+non-Roma adolescents in Macedonia. \emph{Journal of Community \& Applied
+Social Psychology}, \emph{27}(5), 424--434.
+\url{https://doi.org/10.1002/casp.2320}
+
+\leavevmode\hypertarget{ref-1411}{}%
+*Kanas, A., Scheepers, P., \& Sterkens, C. (2015). Interreligious
+contact, perceived group threat, and perceived discrimination:
+Predicting negative attitudes among religious minorities and majorities
+in Indonesia. \emph{Social Psychology Quarterly}, \emph{78}(2),
+102--126. \url{https://doi.org/10.1177/0190272514564790}
+
+\leavevmode\hypertarget{ref-4002}{}%
+*Kende, J., Baysu, G., Van Laar, C., \& Phalet, K. (2020). Majority
+group belonging without minority group distancing? Minority experiences
+of intergroup contact and inequality. \emph{British Journal of Social
+Psychology}, bjso.12382. \url{https://doi.org/10.1111/bjso.12382}
+
+\leavevmode\hypertarget{ref-1525}{}%
+*Kiang, L., Peterson, J. L., \& Thompson, T. L. (2011). Ethnic peer
+preferences among asian american adolescents in emerging immigrant
+communities. \emph{Journal of Research on Adolescence}, \emph{21}(4),
+754--761. \url{https://doi.org/10.1111/j.1532-7795.2011.00750.x}
+
+\leavevmode\hypertarget{ref-830}{}%
+*Kim, T. Y. (2015). \emph{The influence of perceived racial
+discrimination on depressive symptoms and school outcomes among asian
+american adolescents} {[}Doctoral dissertation, The University of
+Chicago{]}. ProQuest Dissertations and Theses Global.
+
+\leavevmode\hypertarget{ref-401}{}%
+*Koschate, M., Hofmann, W., \& Schmitt, M. (2012). When East meets West:
 A longitudinal examination of the relationship between group relative
@@
 
+\leavevmode\hypertarget{ref-45}{}%
+*Krahé, B., Abraham, C., Felber, J., \& Helbig, M. K. (2005). Perceived
+discrimination of international visitors to universities in Germany and
+the UK. \emph{British Journal of Psychology}, \emph{96}(3), 263--281.
+\url{https://doi.org/10.1348/000712605X48296}
+
 \leavevmode\hypertarget{ref-lakens_reproducibility_2016}{}%
@@
 \emph{4}(1), 24. \url{https://doi.org/10.1186/s40359-016-0126-3}
+
+\leavevmode\hypertarget{ref-1993}{}%
+*Leong, C.-H., \& Ward, C. (2000). Identity conflict in sojourners.
+\emph{International Journal of Intercultural Relations}, \emph{24}(6),
+763--776. \url{https://doi.org/10.1016/S0147-1767(00)00030-4}
+
+\leavevmode\hypertarget{ref-3134}{}%
+*Leszczensky, L., Maxwell, R., \& Bleich, E. (2020). What factors best
+explain national identification among Muslim adolescents? Evidence from
+four European countries. \emph{Journal of Ethnic and Migration Studies},
+\emph{46}(1), 260--276.
+\url{https://doi.org/10.1080/1369183X.2019.1578203}
 
@@
 \url{https://doi.org/10.3758/s13428-020-01360-0}
+
+\leavevmode\hypertarget{ref-1042}{}%
+*Lopez, G. E. (2004). Interethnic contact, curriculum, and attitudes in
+the first year of college. \emph{Journal of Social Issues},
+\emph{60}(1), 75--94.
+\url{https://doi.org/10.1111/j.0022-4537.2004.00100.x}
+
+\leavevmode\hypertarget{ref-894}{}%
+*Lubensky, M. E. (2004). \emph{An unplanned trade-off? The potential
+conflict between reducing prejudice and supporting engagement in
+collective action} {[}Doctoral dissertation, University of California,
+Santa Cruz{]}. ProQuest Dissertations and Theses Global.
+
+\leavevmode\hypertarget{ref-4000}{}%
+*Lutterbach, S., \& Beelmann, A. (2020). Positive and negative
+intergroup contact and shared reality: Contact effects among host
+society and refugees. \emph{European Journal of Social Psychology},
+\emph{50}(1), 143--159. \url{https://doi.org/10.1002/ejsp.2601}
+
+\leavevmode\hypertarget{ref-893}{}%
+*Mallet, J., Lewis, C. A., \& Cairns, E. (2013). Perceived in-group
+density and psychological adjustment in a sample of Northern Irish
+Catholics and Protestants. \emph{Studia Psychologica}, \emph{55}(3),
+229--246. \url{https://doi.org/10.21909/sp.2013.03.639}
+
+\leavevmode\hypertarget{ref-3005}{}%
+*Martiny, S. E., Froehlich, L., Soltanpanah, J., \& Haugen, M. S.
+(2020). Young immigrants in Norway: The role of national and ethnic
+identity in immigrants' integration. \emph{Scandinavian Journal of
+Psychology}, \emph{61}(2), 312--324.
+\url{https://doi.org/10.1111/sjop.12594}
+
+\leavevmode\hypertarget{ref-1850}{}%
+*McGinley, J. E. (2007). \emph{Expatriate adjustment: Resources,
+responses, and outcomes} {[}Doctoral dissertation, Northcentral
+University{]}. ProQuest Dissertations and Theses Global.
+
+\leavevmode\hypertarget{ref-1376}{}%
+*McKeown, S., \& Taylor, L. K. (2017). Beyond the irony of intergroup
+contact: The effects of contact and threat on political participation
+and support for political violence in Northern Ireland. \emph{Group
+Dynamics: Theory, Research, and Practice}, \emph{21}(4), 234--244.
+\url{https://doi.org/10.1037/gdn0000074}
 
@@
 
+\leavevmode\hypertarget{ref-4004}{}%
+*Pereira, A., Green, E. G. T., \& Visintin, E. P. (2017). National
+identification counteracts the sedative effect of positive intergroup
+contact on ethnic activism. \emph{Frontiers in Psychology}, \emph{8}.
+\url{https://doi.org/10.3389/fpsyg.2017.00477}
+
+\leavevmode\hypertarget{ref-823}{}%
+*Perrucci, R., \& Hu, H. (1995). Satisfaction with social and
+educational experiences among international graduate students.
+\emph{Research in Higher Education}, \emph{36}(4), 491--508.
+\url{https://doi.org/10.1007/BF02207908}
+
 \leavevmode\hypertarget{ref-peterson_use_2005}{}%
@@
 
-\leavevmode\hypertarget{ref-poore_contact_2002}{}%
-Poore, A. G., Gagne, F., Barlow, K. M., Lydon, J. E., Taylor, D. M., \&
+\leavevmode\hypertarget{ref-1762}{}%
+*Poore, A. G., Gagne, F., Barlow, K. M., Lydon, J. E., Taylor, D. M., \&
 Wright, S. C. (2002). Contact and the personal/group discrimination
@@
 \emph{136}(4), 371--382. \url{https://doi.org/10.1080/00223980209604164}
+
+\leavevmode\hypertarget{ref-3051}{}%
+*Rafiqi, A., \& Thomsen, J. P. F. (2020). Group discrimination,
+intergroup contact, and ethnic minority members' reactions toward the
+majority. \emph{Ethnicities}, \emph{24}(1), 3--22.
+\url{https://doi.org/10.1177/1468796820909493}
 
@@
 
-\leavevmode\hypertarget{ref-reimer_intergroup_2017}{}%
-Reimer, N. K., Becker, J. C., Benz, A., Christ, O., Dhont, K., Klocke,
+\leavevmode\hypertarget{ref-956}{}%
+*Reimer, N. K., Becker, J. C., Benz, A., Christ, O., Dhont, K., Klocke,
 U., Neji, S., Rychlowska, M., Schmid, K., \& Hewstone, M. (2017).
@@
 
-\leavevmode\hypertarget{ref-reimer_building_2021}{}%
-Reimer, N. K., Love, A., Wölfer, R., \& Hewstone, M. (2021). Building
+\leavevmode\hypertarget{ref-2380}{}%
+*Reimer, N. K., Kamble, S. V., Schmid, K., \& Hewstone, M. (2020).
+Intergroup contact fosters more inclusive social identities. \emph{Group
+Processes \& Intergroup Relations}.
+\url{https://doi.org/10.1177/1368430220960795}
+
+\leavevmode\hypertarget{ref-2399}{}%
+*Reimer, N. K., Love, A., Wölfer, R., \& Hewstone, M. (2021). Building
 social cohesion through intergroup contact: Evaluation of a large-scale
 intervention to improve intergroup relations among adolescents.
-\emph{Journal of Youth and Adolescence}.
+\emph{Journal of Youth and Adolescence}, \emph{50}, 1049--1067.
 \url{https://doi.org/10.1007/s10964-021-01400-8}
@@
 
-\leavevmode\hypertarget{ref-saguy_irony_2009}{}%
-Saguy, T., Tausch, N., Dovidio, J. F., \& Pratto, F. (2009). The irony
+\leavevmode\hypertarget{ref-803}{}%
+*Rodriguez, J., \& Gurin, P. (1990). The relationships of intergroup
+contact to social identity and political consciousness. \emph{Hispanic
+Journal of Behavioral Sciences}, \emph{12}(3), 235--255.
+\url{https://doi.org/10.1177/07399863900123001}
+
+\leavevmode\hypertarget{ref-703}{}%
+*Rowley, S. J., Burchinal, M. R., Roberts, J. E., \& Zeisel, S. A.
+(2008). Racial identity, social context, and race-related social
+cognition in African Americans during middle childhood.
+\emph{Developmental Psychology}, \emph{44}(6), 1537--1546.
+\url{https://doi.org/10.1037/a0013349}
+
+\leavevmode\hypertarget{ref-244}{}%
+*Ruck, M. D., Park, H., Killen, M., \& Crystal, D. S. (2011). Intergroup
+contact and evaluations of race-based exclusion in urban minority
+children and adolescents. \emph{Journal of Youth and Adolescence},
+\emph{40}(6), 633--643. \url{https://doi.org/10.1007/s10964-010-9600-z}
+
+\leavevmode\hypertarget{ref-1114}{}%
+*Saab, R., Harb, C., \& Moughalian, C. (2017). Intergroup contact as a
+predictor of violent and nonviolent collective action: Evidence from
+Syrian refugees and Lebanese nationals. \emph{Peace and Conflict:
+Journal of Peace Psychology}, \emph{23}(3), 297--306.
+\url{https://doi.org/10.1037/pac0000234}
+
+\leavevmode\hypertarget{ref-2333}{}%
+*Saenz, V. B. (2005). \emph{Breaking the cycle of segregation: Examining
+students' pre-college racial environments and their diversity
+experiences in college} {[}Doctoral dissertation, University of
+California, Los Angeles{]}. ProQuest Dissertations and Theses Global.
+
+\leavevmode\hypertarget{ref-4005}{}%
+*Saguy, T., \& Chernyak-Hai, L. (2012). Intergroup contact can undermine
+disadvantaged group members' attributions to discrimination.
+\emph{Journal of Experimental Social Psychology}, \emph{48}(3),
+714--720. \url{https://doi.org/10.1016/j.jesp.2012.01.003}
+
+\leavevmode\hypertarget{ref-813}{}%
+*Saguy, T., Tausch, N., Dovidio, J. F., \& Pratto, F. (2009). The irony
 of harmony: Intergroup contact can produce false expectations for
@@
 \url{https://doi.org/10.1111/j.1467-9280.2008.02261.x}
+
+\leavevmode\hypertarget{ref-2382}{}%
+*Schäfer, S. J., Bracegirdle, C., Christ, O., Hewstone, M., Jaspers, E.,
+Reimer, N. K., \& Wölfer, R. (2018). \emph{Positive-negative asymmetry
+of intergroup contact: A dynamic approach} {[}Unpublished dataset{]}.
+University of Oxford.
+
+\leavevmode\hypertarget{ref-2392}{}%
+*Sengupta, N. K. (2020a). \emph{Inter-caste contact in India}
+{[}Unpublished dataset{]}. University of Kent.
+
+\leavevmode\hypertarget{ref-2385}{}%
+*Sengupta, N. K. (2020b). \emph{Inter-religious contact in India}
+{[}Unpublished dataset{]}. University of Kent.
 
@@
 
-\leavevmode\hypertarget{ref-sengupta_perpetuating_2013}{}%
-Sengupta, N. K., \& Sibley, C. G. (2013). Perpetuating one's own
+\leavevmode\hypertarget{ref-1695}{}%
+*Sengupta, N. K., \& Sibley, C. G. (2013). Perpetuating one's own
 disadvantage: Intergroup contact enables the ideological legitimation of
@@
 
-\leavevmode\hypertarget{ref-shani_effect_2017}{}%
-Shani, M., \& Boehnke, K. (2017). The effect of Jewish--Palestinian
+\leavevmode\hypertarget{ref-2381}{}%
+*Sengupta, N. K., \& Sibley, C. G. (2020). \emph{Intergroup contact and
+political attitudes among ethnic minorities in New Zealand}
+{[}Unpublished dataset{]}. The University of Auckland.
+
+\leavevmode\hypertarget{ref-1891}{}%
+*Shammas, D. (2009). \emph{Expatriate adjustment: Resources, responses,
+and outcomes} {[}Doctoral dissertation, Northcentral University{]}.
+ProQuest Dissertations and Theses Global.
+
+\leavevmode\hypertarget{ref-789}{}%
+*Shani, M., \& Boehnke, K. (2017). The effect of Jewish--Palestinian
 mixed-model encounters on readiness for contact and policy support.
@@
 219--227. \url{https://doi.org/10.1037/pac0000220}
+
+\leavevmode\hypertarget{ref-3060}{}%
+*Simons, R. L., Lei, M.-K., Carter, S., Beach, S. R. H., Gibbons, F. X.,
+Gerrard, M., \& Philibert, R. A. (2019). Inflammation mediates the
+effect of discrimination, religiosity, and friendship network on
+expression of the Tp53 cancer suppressor gene. \emph{SSM - Population
+Health}, \emph{7}, 100389.
+\url{https://doi.org/10.1016/j.ssmph.2019.100389}
 
@@
 
-\leavevmode\hypertarget{ref-tausch_how_2015}{}%
-Tausch, N., Saguy, T., \& Bryson, J. (2015). How does intergroup contact
-affect social change? Its impact on collective action and individual
-mobility intentions among members of a disadvantaged group.
+\leavevmode\hypertarget{ref-1020}{}%
+*Swami, V. (2009). Predictors of sociocultural adjustment among
+sojourning Malaysian students in Britain. \emph{International Journal of
+Psychology}, \emph{44}(4), 266--273.
+\url{https://doi.org/10.1080/00207590801888745}
+
+\leavevmode\hypertarget{ref-733}{}%
+*Swami, V., Arteche, A., Chamorro-Premuzic, T., \& Furnham, A. (2010).
+Sociocultural adjustment among sojourning Malaysian students in Britain:
+A replication and path analytic extension. \emph{Social Psychiatry and
+Psychiatric Epidemiology}, \emph{45}(1), 57--65.
+\url{https://doi.org/10.1007/s00127-009-0042-4}
+
+\leavevmode\hypertarget{ref-2375}{}%
+*Tausch, N., Saguy, T., \& Bryson, J. (2015). How does intergroup
+contact affect social change? Its impact on collective action and
+individual mobility intentions among members of a disadvantaged group.
 \emph{Journal of Social Issues}, \emph{71}(3), 536--553.
 \url{https://doi.org/10.1111/josi.12127}
+
+\leavevmode\hypertarget{ref-46}{}%
+*Teney, C. (2011). Endorsement of assimilationism among ethnic minority
+and majority youth in a multination-multiethnic context: The case of
+Brussels. \emph{European Sociological Review}, \emph{27}(2), 212--229.
+\url{https://doi.org/10.1093/esr/jcq003}
+
+\leavevmode\hypertarget{ref-1412}{}%
+*Thomsen, J. P. F., \& Rafiqi, A. (2016). The contact--prejudice
+relationship among ethnic minorities: Examining personal discrimination
+as a boundary condition. \emph{Ethnic and Racial Studies},
+\emph{39}(10), 1886--1904.
+\url{https://doi.org/10.1080/01419870.2015.1110609}
+
+\leavevmode\hypertarget{ref-1966}{}%
+*Titzmann, P. F., Silbereisen, R. K., \& Schmitt-Rodermund, E. (2007).
+Friendship homophily among diaspora migrant adolescents in Germany and
+Israel. \emph{European Psychologist}, \emph{12}(3), 181--195.
+\url{https://doi.org/10.1027/1016-9040.12.3.181}
+
+\leavevmode\hypertarget{ref-1221}{}%
+*Tostado, P. (2017). \emph{When you aren't who your friends are: The
+moderating influence of racial similarity on the association between
+friendships and mental well-being} {[}Master's thesis, Portland State
+University{]}. ProQuest Dissertations and Theses Global.
+
+\leavevmode\hypertarget{ref-933}{}%
+*Tropp, L. R. (2007). Perceived discrimination and interracial contact:
+Predicting interracial closeness among Black and White Americans.
+\emph{Social Psychology Quarterly}, \emph{70}(1), 70--81.
+\url{https://doi.org/10.1177/019027250707000108}
 
@@
 
-\leavevmode\hypertarget{ref-tropp_crossethnic_2012}{}%
-Tropp, L. R., Hawi, D. R., Van Laar, C., \& Levin, S. (2012).
-Cross‐ethnic friendships, perceived discrimination, and their effects on
+\leavevmode\hypertarget{ref-1743}{}%
+*Tropp, L. R., Hawi, D. R., Van Laar, C., \& Levin, S. (2012).
+Cross-ethnic friendships, perceived discrimination, and their effects on
 ethnic activism over time: A longitudinal investigation of three ethnic
@@
 \url{https://doi.org/10.1111/j.2044-8309.2011.02050.x}
+
+\leavevmode\hypertarget{ref-1658}{}%
+*Tropp, L. R., Okamoto, D. G., Marrow, H. B., \& Jones-Correa, M.
+(2018). How contact experiences shape welcoming: Perspectives from
+U.S.-born and immigrant groups. \emph{Social Psychology Quarterly},
+\emph{81}(1), 23--47. \url{https://doi.org/10.1177/0190272517747265}
 
@@
 \url{https://doi.org/10.1111/j.1467-9280.2005.01643.x}
+
+\leavevmode\hypertarget{ref-2394}{}%
+*Twali, M. S., Tran, J., Stewart, A. L., \& Vollhardt, J. R. (2020).
+\emph{Understanding proactive behaviour in the workplace as a function
+of gender} {[}Manuscript in preparation{]}. University of Kansas.
+
+\leavevmode\hypertarget{ref-286}{}%
+*Uluğ, Ö. M., \& Cohrs, J. C. (2017). "If we become friends, maybe I can
+change my perspective'': Intergroup contact, endorsement of conflict
+narratives, and peace-related attitudes in Turkey. \emph{Peace and
+Conflict: Journal of Peace Psychology}, \emph{23}(3), 278--287.
+\url{https://doi.org/10.1037/pac0000216}
 
@@
 
+\leavevmode\hypertarget{ref-829}{}%
+*Vedder, P., Sam, D. L., \& Liebkind, K. (2007). The acculturation and
+adaptation of Turkish adolescents in North-Western Europe. \emph{Applied
+Developmental Science}, \emph{11}(3), 126--136.
+\url{https://doi.org/10.1080/10888690701454617}
+
 \leavevmode\hypertarget{ref-vevea_general_1995}{}%
@@
 \emph{10}(4), 606--614. \url{https://doi.org/10.1002/jrsm.1374}
+
+\leavevmode\hypertarget{ref-2383}{}%
+*Wölfer, R., \& Hewstone, M. (2019). \emph{Social integration in diverse
+societies: The importance of contact experiences in youth}
+{[}Unpublished dataset{]}. University of Oxford.
 
@@
 
+\leavevmode\hypertarget{ref-1395}{}%
+*Yu, B., Bodycott, P., \& Mak, A. S. (2019). Language and interpersonal
+resource predictors of psychological and sociocultural adaptation:
+International students in Hong Kong. \emph{Journal of Studies in
+International Education}, \emph{23}(5), 572--588.
+\url{https://doi.org/10.1177/1028315318825336}
+
+\leavevmode\hypertarget{ref-3000}{}%
+*Yu, B., Mak, A. S., \& Bodycott, P. (2019). Psychological and academic
+adaptation of mainland Chinese students in Hong Kong universities.
+\emph{Studies in Higher Education}, 1--13.
+\url{https://doi.org/10.1080/03075079.2019.1693991}
+
 \endgroup

### 2021-06-07 manuscript/supplemental-materials.tex
add starred references

@@
 the mean effect size for the three outcomes
-(\(\Delta r = .01, [-.04, .05]\); \(\Delta r = .02, [-.08, .12]\);
+(\(\Delta r = -.00, [-.05, .04]\); \(\Delta r = .02, [-.08, .12]\);
 \(\Delta r = -.02, [-.11, .07]\)). Together, these analyses showed that

### 2021-06-07 figures/figure-2.R

@@ -91,7 +91,7 @@ rm(list = ls())
       study_setting = case_when(
         str_detect(study_setting, ",") ~ "Other",
         study_setting == "Slavery" ~ "Post-Slavery",
-        study_setting == "Colonization" ~ "Post-Colonial",
+        study_setting == "Colonization" ~ "(Post-)Colonial",
         TRUE ~ study_setting
       )
     ) %>% 

### 2021-06-07 figures/figure-2a.R

@@ -1,0 +1,230 @@
+# Notes -------------------------------------------------------------------
+
+  #########################################################################
+  # Thanks to Claus Wilke for implementing the "Interrupted Goode         #
+  # homolosine" projection in R.                                          #
+  #########################################################################
+
+# Library -----------------------------------------------------------------
+  
+  # Load packages
+  library(tidyverse); library(sf); library(rworldmap); library(numform)
+
+
+# Prepare map -------------------------------------------------------------
+
+  # Load map
+  world_sf <- st_as_sf(getMap(resolution = "low"))
+  
+  # Prepare map projection
+  crs_goode <- "+proj=igh"
+  goode_outline <- list(cbind(
+    longs <- c(
+      rep(180, 181), 
+      rep(c(80.01, 79.99), each = 91), 
+      rep(c(-19.99, -20.01), each = 91), 
+      rep(c(-99.99, -100.01), each = 91),
+      rep(-180, 181), 
+      rep(c(-40.01, -39.99), each = 91),
+      180 
+    ), 
+    lats <- c(
+      90:-90,
+      -90:0, 0:-90, 
+      -90:0, 0:-90, 
+      -90:0, 0:-90, 
+      -90:90, 
+      90:0, 0:90, 
+      90
+    )
+  )) %>%
+    st_polygon() %>%
+    st_sfc(
+      crs = "+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs"
+    )
+  goode_outline <- st_transform(goode_outline, crs = crs_goode)
+  xlim <- st_bbox(goode_outline)[c("xmin", "xmax")]*1.1
+  ylim <- st_bbox(goode_outline)[c("ymin", "ymax")]*1.1
+  goode_encl_rect <- 
+    list(
+      cbind(
+        c(xlim[1], xlim[2], xlim[2], xlim[1], xlim[1]), 
+        c(ylim[1], ylim[1], ylim[2], ylim[2], ylim[1])
+      )
+    ) %>%
+    st_polygon() %>%
+    st_sfc(crs = crs_goode)
+  goode_without <- st_difference(goode_encl_rect, goode_outline)
+  
+  
+# Prepare data ------------------------------------------------------------
+
+  # Import data
+  dl <- read_rds("data/dl.rds")
+  
+  # Select variables
+  dm <- dl %>% distinct(id, sample, n, country)
+  
[…]

### 2021-06-07 figures/figure-6.R

@@ -45,7 +45,7 @@ rm(list = ls())
       glue("*I* = {sum(d_6a$n)}"),
       glue("Adults<br>*I* = {d_6a$n[2] + d_6a$n[3] + d_6a$n[4]}"),
       glue("Direct<br>Measurement<br>*I* = {d_6a$n[3] + d_6a$n[4]}"),
-      glue("Post-Colonial/<br>S.-T. Migration<br>*I* = {d_6a$n[4]}"),
+      glue("(Post-)Colonial/<br>S.-T. Migration<br>*I* = {d_6a$n[4]}"),
       glue("Other Settings<br>*I* = {d_6a$n[3]}"),
       glue("Indirect<br>Measurement<br>*I* = {d_6a$n[2]}"),
       glue("Adolescents/<br>Children<br>*I* = {d_6a$n[1]}")

### 2021-06-07 figures/figure-s1.R

@@ -66,7 +66,7 @@ rm(list = ls())
         "convenience sample" = "convenience",
         "probability/representative sample" = "probability/representative",
         "Slavery" = "Post-Slavery",
-        "Colonization" = "Post-Colonial"
+        "Colonization" = "(Post-)Colonial"
       ),
       category = str_replace(category, " ", "\n"),
       category = str_replace(category, "\\/", "/\n"),
@@ -79,7 +79,7 @@ rm(list = ls())
         "Short-term\nmigration",
         "Long-term\nmigration",
         "Post-Slavery",
-        "Post-Colonial",
+        "(Post-)Colonial",
         "Religion",
         "Caste",
         "Sexuality",

### 2021-06-07 run_scripts.R

@@ -53,22 +53,22 @@ rm(list = ls())
   source("scripts/run_analyses_with_ingroup_contact.R")
 
   # Run analyses to test and correct for publication bias
-  source("scripts/run_meta_bias_ingroup_contact.R")
+  source("scripts/run_meta_bias_analyses.R")
   
 
 # Visualize ---------------------------------------------------------------
   
   # Make figures
-  source("scripts/figure-1.R")
-  source("scripts/figure-2.R")
-  source("scripts/figure-3.R")
-  source("scripts/figure-4.R")
-  source("scripts/figure-5.R")
-  source("scripts/figure-6.R")
-  source("scripts/figure-7.R")
-  source("scripts/figure-8.R")
-  source("scripts/figure-s1.R")
-  source("scripts/figure-s2.R")
+  source("figures/figure-1.R")
+  source("figures/figure-2.R")
+  source("figures/figure-3.R")
+  source("figures/figure-4.R")
+  source("figures/figure-5.R")
+  source("figures/figure-6.R")
+  source("figures/figure-7.R")
+  source("figures/figure-8.R")
+  source("figures/figure-s1.R")
+  source("figures/figure-s2.R")
 
 # Combine -----------------------------------------------------------------
 

### 2021-06-07 scripts/prepare_data_for_analyses.R

@@ -242,7 +242,8 @@ rm(list = ls())
         id == 2396L & sample == 2L ~ "Sexuality",
         id == 2396L & sample == 3L ~ "Colonization",
         id == 2397L & sample == 1L ~ "Long-term migration",
-        id == 2398L & sample == 1L ~ "Long-term migration"
+        id == 2398L & sample == 1L ~ "Long-term migration",
+        id == 2399L ~ "Long-term migration"
       ),
       ingroup = case_when(
         !is.na(ingroup) ~ ingroup,
@@ -252,7 +253,9 @@ rm(list = ls())
         id == 2396L & sample == 2L ~ "LGBTI people",
         id == 2396L & sample == 3L ~ "Kurdish people",
         id == 2397L & sample == 1L ~ "Black people",
-        id == 2398L & sample == 1L ~ "Asian people"
+        id == 2398L & sample == 1L ~ "Asian people",
+        id == 2399L & sample == 1L ~ "Asian people",
+        id == 2399L & sample == 2L ~ "Black people"
       ),
       outgroup = case_when(
         !is.na(outgroup) ~ outgroup,
@@ -262,7 +265,8 @@ rm(list = ls())
         id == 2396L & sample == 2L ~ "Heterosexual people",
         id == 2396L & sample == 3L ~ "Turkish people",
         id == 2397L & sample == 1L ~ "White people",
-        id == 2398L & sample == 1L ~ "White people"
+        id == 2398L & sample == 1L ~ "White people",
+        id == 2399L ~ "White people"
       )
     )
   

### 2021-06-11 manuscript/manuscript.Rmd
revise introduction

@@
 header: "'IRONIC' EFFECTS META-ANALYSIS"
-keywords: intergroup contact, meta-analysis, perceived discrimination, collective action, policy support, social change, social injustice 
+keywords: intergroup contact, meta-analysis, perceived discrimination, collective action, policy support
 bibliography: references.bib
@@
 We close by highlighting open questions about the relationship between intergroup contact and social change.
-statement: 
-  As societies are becoming more diverse, there are more opportunities for members of different groups to come in contact with each other.
-Psychologists disagree about what this means for overcoming persistent inequality between advantaged and disadvantaged groups.
-Many argue that intergroup contact reduces advantaged-group members' prejudice and, thereby, prevents interpersonal discrimination.
-Reducing prejudice, however, is rarely enough to overcome institutional and structural discrimination.
-Instead, social change often results from disadvantaged-group members mobilizing against social injustice (for example, in the 2020 Black Lives Matter protests).
-Critics argue that positive intergroup contact could create a false sense of equality and, thereby, stifle disadvantaged-group members' opposition to injustice.
-We present the first systematic review and meta-analysis of the growing number of studies examining how intergroup contact relates to support for social change in disadvantaged groups.
-Our findings help us understand whether, when, and how intergroup contact might hinder, rather than help, social change.
 output:
@@
 Others, however, have pointed to conflicting evidence [@1762] and argued that intergroup contact might instead make discrimination more salient and, thereby, increase disadvantaged-group members' support for social change [@pettigrew_recent_2011].
-In the decade since the initial studies, many more studies have examined the relationships between intergroup contact and support for social change in disadvantaged groups.
-We present a systematic review and meta-analysis of this growing literature.
-Specifically, we evaluate the evidence for three hypotheses about how intergroup contact might reduce support for social change.
+In the decade since the initial studies, many more studies have examined the relationship between intergroup contact and support for social change in disadvantaged groups.
+We present a systematic review and meta-analysis of this growing literature to evaluate the evidence for and against the 'ironic' effects of intergroup contact.
+
+## Why Intergroup Contact Might Reduce Support for Social Change
+
+Researchers have put forward three hypotheses about how intergroup contact might reduce support for social change in disadvantaged groups.
 
@@
 
+To summarize, intergroup contact might hinder social change by reducing disadvantaged-group members' perceived injustice, discouraging them from engaging in collective action, and diminishing their support for reparative policies.
+
+## Why Intergroup Contact Might *not* Reduce Support for Social Change
+
+Researchers have, however, argued that intergroup contact might *not* reduce support for social change and, in some circumstances, might even *increase* support for social change in disadvantaged groups.
+
+Some studies found evidence that intergroup contact is associated with more, not less, support for social change in disadvantaged groups.
+@1762 found that Inuit who had more exposure to non-indigenous Canadians perceived greater discrimination against their group than Inuit who lived in relative isolation.
+Similarly, researchers found that, among members of various disadvantaged groups, intergroup contact was associated with perceiving greater discrimination against the disadvantaged ingroup [@93], perceiving status differences between the advantaged outgroup and disadvantaged ingroup to be less legitimate [@3196], and being more willing to engage in collective action [@93; @3196; @4004].
+These findings align with the argument, based in relative deprivation theory [@smith_relative_2012], that contact with the advantaged provides an opportunity for the disadvantaged to recognize their relative disadvantage and, thereby, can motivate the disadvantaged to support social change [see @pettigrew_recent_2011; @1762].
+
+Other researchers have put forward alternative explanations for the apparent 'ironic' effects of intergroup contact.
+Whereas previous studies had focused on positive contact experiences, recent studies considered both positive and negative contact experiences as predictors of support for social change.
+Researchers [@2309; @956] found negative contact with advantaged-group members to be associated with greater perceived discrimination and stronger collective action intentions, suggesting that negative contact experiences motivate disadvantaged-group members to support social change.
+@956 further found that, first, disadvantaged-group members who have more positive contact also tend to have less negative contact and, second, positive contact is not associated with perceived discrimination or collective action after controlling for negative contact.
+Based on these findings, @956 argued that the mobilizing effect of negative contact could be an alternative explanation for the negative relationship between positive contact and support for social change observed in previous studies.
+
+Another alternative explanation for the apparent 'ironic' effects of intergroup contact centers on intragroup contact.
+Whereas most studies focused on contact with the advantaged outgroup, some studies examined contact with the disadvantaged ingroup as a predictor of support for social change.
+@sengupta_ingroup_2015 found ingroup contact to be associated with decreased endorsement of system-justifying beliefs and increased support for reparative policies benefiting the disadvantaged ingroup, suggesting that contact with other ingroup members can motivate disadvantaged-group members to support social change [see also @1695].
+As outgroup contact places limits on how much ingroup contact one can have [@pfister_contact_2020], disadvantaged-group members who have more outgroup contact can be expected to have less ingroup contact.
+Based on these observations, one might argue that the mobilizing effect of ingroup contact could be an alternative explanation for the negative association between outgroup contact and support for social change observed in previous studies.
+
+To summarize, intergroup contact might increase, not decrease, support for social change in disadvantaged groups and the apparent 'ironic' effects might be based on spurious relationships between (positive) intergroup contact and support for social change.
+
+## Purpose of the Present Study
+
+As societies are becoming more diverse, there are more opportunities for members of different groups to come in contact with each other.
+Psychologists disagree about what this means for disadvantaged-group members' awareness of and opposition to social injustice.
+On the one hand, researchers have argued that intergroup contact might reduce disadvantaged-group members' perceived injustice, discourage them from engaging in collective action, and diminish their support for reparative policies.
+On the other hand, researchers have argued that intergroup contact might not reduce, or even increase, support for social change in disadvantaged groups.
+Settling this debate is important both because intergroup contact is a promising means of reducing prejudice [@pettigrew_meta-analytic_2006] and because political mobilization by the disadvantaged is often crucial for achieving social change [see, e.g., @mazumder_persistent_2018].
+
+While several narrative reviews of the growing literature on this topic have been published [@hassler_intergroup_2021; @macinnis_extending_2019; @mckeown_contact_2017], we present the first systematic review and meta-analysis of the relationship between intergroup contact and support for social change in disadvantaged groups.
+
 Our first objective was to systematically review the available evidence and to evaluate its strengths and limitations.
@@
 Doing so allowed us to determine whether the available evidence supports a negative or positive [see @pettigrew_recent_2011] relationship between contact and support for social change and to estimate the strength of this relationship.
-Our third objective was to explore the variability of this relationship across study settings, designs, and other potential moderators.
+Our third objective was to estimate and explain the variability of this relationship across study settings, designs, and other potential moderators.
 For example, we examined whether any effects were confined to Western, Educated, Industrialized, Rich, Democratic (WEIRD) countries, the cultural context of most psychological research [@henrich_weirdest_2010].
 Our fourth objective was to assess how robust the available evidence was to publication bias.
-
-In addition, we examined the evidence for two alternative accounts of this relationship.
-First, we considered studies that measured both ingroup and outgroup contact as predictors of the three outcomes.
-@sengupta_ingroup_2015 argued that contact with other members of the disadvantaged ingroup would increase political mobilization.
-As outgroup contact places limits on how much ingroup contact disadvantaged-group members can have [@pfister_contact_2020], the mobilizing effect of ingroup contact is an alternative explanation for negative associations between outgroup contact and support for social change.
-
-Second, we considered studies that measured both negative and positive (outgroup) contact as predictors of the three outcomes.
-Researchers [@2309; @956] found negative contact with advantaged-group members to be associated with greater perceived discrimination and stronger collective action intentions.
-@956 argued that, to the extent disadvantaged-group members who have more positive contact also tend to have less negative contact, the mobilizing effect of negative contact is an alternative explanation for negative associations between outgroup contact and support for social change.
+Our final objective was to explore the available evidence for negative contact and ingroup contact as alternative explanations of the apparent 'ironic' effects of intergroup contact.
 
@@
 We prepared a protocol in accordance with the PRISMA-P statement [@moher_preferred_2015] and preregistered it on the Open Science Framework.^[[https://osf.io/ryuev/?view_only=8938ac6178914da98bdda1da4a6e27f0](https://osf.io/ryuev/?view_only=8938ac6178914da98bdda1da4a6e27f0)] Preregistration precludes undisclosed flexibility in study selection, outcome selection, and other decisions that influence effect size estimates—and thus prevents confirmation bias from determining the conclusions of a meta-analysis [@lakens_reproducibility_2016].
-We report deviations from our protocol in the Supplemental Online Material (SOM-R).
+We report deviations from our protocol in the Supplemental Online Material (SOM).
 We make data, analysis scripts, and the fully reproducible manuscript available online.^[[https://osf.io/w5tqv/?view_only=5cbf7ad5b2b449a7a0f4ada0337b802a](https://osf.io/w5tqv/?view_only=5cbf7ad5b2b449a7a0f4ada0337b802a)]
@@
 We also considered expectations of fair treatment as the reverse of perceived injustice.
-We included studies that measured personal or group discrimination or a mixture of both.
+We included studies that measured personal or group discrimination or both.
 
@@
 We searched for gray literature in the *ProQuest Dissertations and Theses* database.
-We used similar non-exclusive search terms for all databases (see SOM-R).
+We used similar non-exclusive search terms for all databases (see SOM).
 We searched databases on April 1, 2019 and again on April 1, 2020.
@@
 
-To find unpublished studies, we sent a call to the mailing lists of several professional organizations (see SOM-R).
+To find unpublished studies, we sent a call to the mailing lists of several professional organizations (see SOM).
 We also advertised on social media and at relevant conferences.
@@
 Bayesian inference applies Bayes’ theorem to update prior distributions in light of the observed data to produce posterior distributions.
-Other than *p*-values and confidence intervals, the resulting posterior distributions have a straightforward interpretation as stating how plausible different values of the model parameters are given the observed data.
+In contrast to *p*-values and confidence intervals, the resulting posterior distributions have a straightforward interpretation as stating how plausible different values of the model parameters are given the observed data.
 We report point estimates, based on the median of posterior samples, and uncertainty intervals, based on the quantiles of posterior samples, that enclose the 95% most plausible estimates.
@@
 At each stage, we also excluded studies that used the same data as another study.
-Our final sample comprised effect sizes from `r paste0("$J = ", with(dl, f_comma(n_distinct(id))), "$")` studies spanning `r paste0("$N = ", with(distinct(dl, id, sample, n), f_comma(sum(n))), "$")` participants in `r paste0("$I = ", f_comma(nrow(distinct(dl, id, sample))), "$")` samples (for a complete list of studies, see SOM-U).
+Our final sample comprised effect sizes from `r paste0("$J = ", with(dl, f_comma(n_distinct(id))), "$")` studies spanning `r paste0("$N = ", with(distinct(dl, id, sample, n), f_comma(sum(n))), "$")` participants in `r paste0("$I = ", f_comma(nrow(distinct(dl, id, sample))), "$")` samples (for a complete list of studies, see SOM).
 
@@
       r_pred_u80 = quantile(r_pred, 0.90),
+      p_pred_positive = mean(r_pred > 0),
       r_abs = quantile(abs(r_pred), 0.20),
@@
 
-***Perceived Injustice.*** Across `r unique(pi_results$N)` participants from `r unique(pi_results$I)` samples in `r unique(pi_results$J)` studies, we found strong evidence for a weak association (`r pi_results$text[pi_results$parameter == "r_mean"]`) between intergroup contact and perceived injustice, with `r pi_results$p_below[pi_results$parameter == "r_mean"]` of posterior samples for the mean correlation coefficient falling below zero.
+***Perceived Injustice.*** Across `r unique(pi_results$N)` participants from `r unique(pi_results$I)` samples in `r unique(pi_results$J)` studies, we found strong evidence for a weak negative association (`r pi_results$text[pi_results$parameter == "r_mean"]`) between intergroup contact and perceived injustice, with `r pi_results$p_below[pi_results$parameter == "r_mean"]` of posterior samples for the mean correlation coefficient falling below zero.
 We found evidence that correlation coefficients varied across studies (`r pi_results$text[pi_results$parameter == "tau_jj"]`) and across samples within studies  (`r pi_results$text[pi_results$parameter == "tau_ii"]`).
-Based on these analyses, we predicted that 80\% of studies would result in correlation coefficients between `r post_pred$r_pred_l80[post_pred$y_var == "pi"]` and `r post_pred$r_pred_u80[post_pred$y_var == "pi"]` and that researchers would need sample sizes of at least `r post_pred$n_req[post_pred$y_var == "pi"]` participants to find significant associations ($\alpha = .05$, two-sided) in 80\% of their studies.^[Sample sizes are based on posterior predictions which implied that, for 80\% of studies, the absolute correlation coefficient would be `r post_pred$r_abs[post_pred$y_var == "pi"]` for perceived injustice, `r post_pred$r_abs[post_pred$y_var == "ca"]` for collective action, and `r post_pred$r_abs[post_pred$y_var == "ps"]` for policy support.]
+Based on these analyses, we predicted that 80\% of studies would result in correlation coefficients between `r post_pred$r_pred_l80[post_pred$y_var == "pi"]` and `r post_pred$r_pred_u80[post_pred$y_var == "pi"]` and that `r f_prop2percent(with(post_pred, p_pred_positive[y_var == "pi"]), digits = 0)` of studies would find a *positive* correlation between intergroup contact and perceived injustice.
+Our analyses suggested that researchers would need sample sizes of at least `r post_pred$n_req[post_pred$y_var == "pi"]` participants to find significant associations ($\alpha = .05$, two-sided) in 80\% of their studies.^[Sample sizes are based on posterior predictions which implied that, for 80\% of studies, the absolute correlation coefficient would be `r post_pred$r_abs[post_pred$y_var == "pi"]` for perceived injustice, `r post_pred$r_abs[post_pred$y_var == "ca"]` for collective action, and `r post_pred$r_abs[post_pred$y_var == "ps"]` for policy support.]
 
@@
 
-***Collective Action.*** Across `r unique(ca_results$N)` participants from `r unique(ca_results$I)` samples in `r unique(ca_results$J)` studies, we found some evidence for a weak association (`r ca_results$text[ca_results$parameter == "r_mean"]`) between intergroup contact and collective action, with `r ca_results$p_below[ca_results$parameter == "r_mean"]` of posterior samples for the mean correlation coefficient falling below zero.
+***Collective Action.*** Across `r unique(ca_results$N)` participants from `r unique(ca_results$I)` samples in `r unique(ca_results$J)` studies, we found some evidence for a weak negative association (`r ca_results$text[ca_results$parameter == "r_mean"]`) between intergroup contact and collective action, with `r ca_results$p_below[ca_results$parameter == "r_mean"]` of posterior samples for the mean correlation coefficient falling below zero.
 We found evidence that correlation coefficients varied across studies (`r ca_results$text[ca_results$parameter == "tau_jj"]`) and across samples within studies  (`r ca_results$text[ca_results$parameter == "tau_ii"]`).
-Based on these analyses, we predicted that 80\% of studies would result in correlation coefficients between `r post_pred$r_pred_l80[post_pred$y_var == "ca"]` and `r post_pred$r_pred_u80[post_pred$y_var == "ca"]` and that researchers would need sample sizes of at least `r post_pred$n_req[post_pred$y_var == "ca"]` participants to find significant associations ($\alpha = .05$, two-sided) in 80\% of their studies.
+Based on these analyses, we predicted that 80\% of studies would result in correlation coefficients between `r post_pred$r_pred_l80[post_pred$y_var == "ca"]` and `r post_pred$r_pred_u80[post_pred$y_var == "ca"]` and that `r f_prop2percent(with(post_pred, p_pred_positive[y_var == "ca"]), digits = 0)` of studies would find a *positive* correlation between intergroup contact and collective action.
+Our analyses suggested that researchers would need sample sizes of at least `r post_pred$n_req[post_pred$y_var == "ca"]` participants to find significant associations ($\alpha = .05$, two-sided) in 80\% of their studies.
 
@@
 
-***Policy Support.*** Across `r unique(ps_results$N)` participants from `r unique(ps_results$I)` samples in `r unique(ps_results$J)` studies, we found evidence for a weak association (`r ps_results$text[ps_results$parameter == "r_mean"]`) between intergroup contact and policy support, with `r ps_results$p_below[ps_results$parameter == "r_mean"]` of posterior samples for the mean correlation coefficient falling below zero.
+***Policy Support.*** Across `r unique(ps_results$N)` participants from `r unique(ps_results$I)` samples in `r unique(ps_results$J)` studies, we found evidence for a weak negative association (`r ps_results$text[ps_results$parameter == "r_mean"]`) between intergroup contact and policy support, with `r ps_results$p_below[ps_results$parameter == "r_mean"]` of posterior samples for the mean correlation coefficient falling below zero.
 We found evidence that correlation coefficients varied across studies (`r ps_results$text[ps_results$parameter == "tau_jj"]`) and, to a lesser extent, across samples within studies  (`r ps_results$text[ps_results$parameter == "tau_ii"]`).
-Based on these analyses, we predicted that 80\% of studies would result in correlation coefficients between `r post_pred$r_pred_l80[post_pred$y_var == "ps"]` and `r post_pred$r_pred_u80[post_pred$y_var == "ps"]` and that researchers would need sample sizes of at least `r post_pred$n_req[post_pred$y_var == "ps"]` participants to find significant associations ($\alpha = .05$, two-sided) in 80\% of their studies.
+Based on these analyses, we predicted that 80\% of studies would result in correlation coefficients between `r post_pred$r_pred_l80[post_pred$y_var == "ps"]` and `r post_pred$r_pred_u80[post_pred$y_var == "ps"]` and that `r f_prop2percent(with(post_pred, p_pred_positive[y_var == "ps"]), digits = 0)` of studies would find a *positive* correlation between intergroup contact and policy support.
+Our analyses suggested that researchers would need sample sizes of at least `r post_pred$n_req[post_pred$y_var == "ps"]` participants to find significant associations ($\alpha = .05$, two-sided) in 80\% of their studies.
 
@@
 
-In addition, we ran preregistered robustness checks which showed that our main analyses were robust to choosing different prior distributions and to excluding influential studies (see SOM-R).
+In addition, we ran preregistered robustness checks which showed that our main analyses were robust to choosing different prior distributions and to excluding influential studies (see SOM).
 
@@
 
-We conducted two kinds of moderator analyses.
-For both analyses, we had an insufficient number of effect sizes to examine moderators for any outcome except perceived injustice (for details, see SOM-R).
+We conducted two kinds of moderator analyses. For both analyses, we had an insufficient number of effect sizes to examine moderators for any outcome except perceived injustice (for details, see SOM).
 
@@
 ```{=latex}
+
 \begin{figure*}
@@
 \end{figure*}
+
 \begin{figure*}
@@
 \end{figure*}
+
 ```
@@
 ```{=latex}
-\begin{figure*}[t!]
+\begin{figure*}
 \centering

### 2021-06-11 manuscript/manuscript.tex
revise introduction

@@
 \textit{Keywords:} intergroup contact, meta-analysis, perceived discrimination, collective
-action, policy support, social change, social injustice
-
-\newpage
-
-\section{Statement of Relevance}
-
-\noindent As societies are becoming more diverse, there are more opportunities for
-members of different groups to come in contact with each other.
-Psychologists disagree about what this means for overcoming persistent
-inequality between advantaged and disadvantaged groups. Many argue that
-intergroup contact reduces advantaged-group members' prejudice and,
-thereby, prevents interpersonal discrimination. Reducing prejudice,
-however, is rarely enough to overcome institutional and structural
-discrimination. Instead, social change often results from
-disadvantaged-group members mobilizing against social injustice (for
-example, in the 2020 Black Lives Matter protests). Critics argue that
-positive intergroup contact could create a false sense of equality and,
-thereby, stifle disadvantaged-group members' opposition to injustice. We
-present the first systematic review and meta-analysis of the growing
-number of studies examining how intergroup contact relates to support
-for social change in disadvantaged groups. Our findings help us
-understand whether, when, and how intergroup contact might hinder,
-rather than help, social change.
+action, policy support
 
@@
 decade since the initial studies, many more studies have examined the
-relationships between intergroup contact and support for social change
-in disadvantaged groups. We present a systematic review and
-meta-analysis of this growing literature. Specifically, we evaluate the
-evidence for three hypotheses about how intergroup contact might reduce
-support for social change.
+relationship between intergroup contact and support for social change in
+disadvantaged groups. We present a systematic review and meta-analysis
+of this growing literature to evaluate the evidence for and against the
+`ironic' effects of intergroup contact.
+
+\hypertarget{why-intergroup-contact-might-reduce-support-for-social-change}{%
+\subsection{Why Intergroup Contact Might Reduce Support for Social
+Change}\label{why-intergroup-contact-might-reduce-support-for-social-change}}
+
+Researchers have put forward three hypotheses about how intergroup
+contact might reduce support for social change in disadvantaged groups.
 
@@
 
+To summarize, intergroup contact might hinder social change by reducing
+disadvantaged-group members' perceived injustice, discouraging them from
+engaging in collective action, and diminishing their support for
+reparative policies.
+
+\hypertarget{why-intergroup-contact-might-not-reduce-support-for-social-change}{%
+\subsection{\texorpdfstring{Why Intergroup Contact Might \emph{not}
+Reduce Support for Social
+Change}{Why Intergroup Contact Might not Reduce Support for Social Change}}\label{why-intergroup-contact-might-not-reduce-support-for-social-change}}
+
+Researchers have, however, argued that intergroup contact might
+\emph{not} reduce support for social change and, in some circumstances,
+might even \emph{increase} support for social change in disadvantaged
+groups.
+
+Some studies found evidence that intergroup contact is associated with
+more, not less, support for social change in disadvantaged groups. Poore
+et al. (2002) found that Inuit who had more exposure to non-indigenous
+Canadians perceived greater discrimination against their group than
+Inuit who lived in relative isolation. Similarly, researchers found
+that, among members of various disadvantaged groups, intergroup contact
+was associated with perceiving greater discrimination against the
+disadvantaged ingroup (Dixon et al., 2017), perceiving status
+differences between the advantaged outgroup and disadvantaged ingroup to
+be less legitimate (Di Bernardo et al., 2019), and being more willing to
+engage in collective action (Di Bernardo et al., 2019; Dixon et al.,
+2017; Pereira et al., 2017). These findings align with the argument,
+based in relative deprivation theory (Smith et al., 2012), that contact
+with the advantaged provides an opportunity for the disadvantaged to
+recognize their relative disadvantage and, thereby, can motivate the
+disadvantaged to support social change (see Pettigrew et al., 2011;
+Poore et al., 2002).
+
+Other researchers have put forward alternative explanations for the
+apparent `ironic' effects of intergroup contact. Whereas previous
+studies had focused on positive contact experiences, recent studies
+considered both positive and negative contact experiences as predictors
+of support for social change. Researchers (Hayward et al., 2018; Reimer
+et al., 2017) found negative contact with advantaged-group members to be
+associated with greater perceived discrimination and stronger collective
+action intentions, suggesting that negative contact experiences motivate
+disadvantaged-group members to support social change. Reimer et al.
+(2017) further found that, first, disadvantaged-group members who have
+more positive contact also tend to have less negative contact and,
+second, positive contact is not associated with perceived discrimination
+or collective action after controlling for negative contact. Based on
+these findings, Reimer et al. (2017) argued that the mobilizing effect
+of negative contact could be an alternative explanation for the negative
+relationship between positive contact and support for social change
+observed in previous studies.
+
+Another alternative explanation for the apparent `ironic' effects of
+intergroup contact centers on intragroup contact. Whereas most studies
+focused on contact with the advantaged outgroup, some studies examined
+contact with the disadvantaged ingroup as a predictor of support for
+social change. Sengupta et al. (2015) found ingroup contact to be
+associated with decreased endorsement of system-justifying beliefs and
+increased support for reparative policies benefiting the disadvantaged
+ingroup, suggesting that contact with other ingroup members can motivate
+disadvantaged-group members to support social change (see also Sengupta
+\& Sibley, 2013). As outgroup contact places limits on how much ingroup
+contact one can have (Pfister et al., 2020), disadvantaged-group members
+who have more outgroup contact can be expected to have less ingroup
+contact. Based on these observations, one might argue that the
+mobilizing effect of ingroup contact could be an alternative explanation
+for the negative association between outgroup contact and support for
+social change observed in previous studies.
+
+To summarize, intergroup contact might increase, not decrease, support
+for social change in disadvantaged groups and the apparent `ironic'
+effects might be based on spurious relationships between (positive)
+intergroup contact and support for social change.
+
+\hypertarget{purpose-of-the-present-study}{%
+\subsection{Purpose of the Present
+Study}\label{purpose-of-the-present-study}}
+
+As societies are becoming more diverse, there are more opportunities for
+members of different groups to come in contact with each other.
+Psychologists disagree about what this means for disadvantaged-group
+members' awareness of and opposition to social injustice. On the one
+hand, researchers have argued that intergroup contact might reduce
+disadvantaged-group members' perceived injustice, discourage them from
+engaging in collective action, and diminish their support for reparative
+policies. On the other hand, researchers have argued that intergroup
+contact might not reduce, or even increase, support for social change in
+disadvantaged groups. Settling this debate is important both because
+intergroup contact is a promising means of reducing prejudice (Pettigrew
+\& Tropp, 2006) and because political mobilization by the disadvantaged
+is often crucial for achieving social change (see, e.g., Mazumder,
+2018).
+
+While several narrative reviews of the growing literature on this topic
+have been published (Hässler et al., 2021; MacInnis \& Hodson, 2019;
+McKeown \& Dixon, 2017), we present the first systematic review and
+meta-analysis of the relationship between intergroup contact and support
+for social change in disadvantaged groups.
+
 Our first objective was to systematically review the available evidence
@@
 estimate the strength of this relationship. Our third objective was to
-explore the variability of this relationship across study settings,
-designs, and other potential moderators. For example, we examined
-whether any effects were confined to Western, Educated, Industrialized,
-Rich, Democratic (WEIRD) countries, the cultural context of most
-psychological research (Henrich et al., 2010). Our fourth objective was
-to assess how robust the available evidence was to publication bias.
-
-In addition, we examined the evidence for two alternative accounts of
-this relationship. First, we considered studies that measured both
-ingroup and outgroup contact as predictors of the three outcomes.
-Sengupta et al. (2015) argued that contact with other members of the
-disadvantaged ingroup would increase political mobilization. As outgroup
-contact places limits on how much ingroup contact disadvantaged-group
-members can have (Pfister et al., 2020), the mobilizing effect of
-ingroup contact is an alternative explanation for negative associations
-between outgroup contact and support for social change.
-
-Second, we considered studies that measured both negative and positive
-(outgroup) contact as predictors of the three outcomes. Researchers
-(Hayward et al., 2018; Reimer et al., 2017) found negative contact with
-advantaged-group members to be associated with greater perceived
-discrimination and stronger collective action intentions. Reimer et al.
-(2017) argued that, to the extent disadvantaged-group members who have
-more positive contact also tend to have less negative contact, the
-mobilizing effect of negative contact is an alternative explanation for
-negative associations between outgroup contact and support for social
-change.
+estimate and explain the variability of this relationship across study
+settings, designs, and other potential moderators. For example, we
+examined whether any effects were confined to Western, Educated,
+Industrialized, Rich, Democratic (WEIRD) countries, the cultural context
+of most psychological research (Henrich et al., 2010). Our fourth
+objective was to assess how robust the available evidence was to
+publication bias. Our final objective was to explore the available
+evidence for negative contact and ingroup contact as alternative
+explanations of the apparent `ironic' effects of intergroup contact.
 
@@
 conclusions of a meta-analysis (Lakens et al., 2016). We report
-deviations from our protocol in the Supplemental Online Material
-(SOM-R). We make data, analysis scripts, and the fully reproducible
-manuscript available online.\footnote{\url{https://osf.io/w5tqv/?view_only=5cbf7ad5b2b449a7a0f4ada0337b802a}}
+deviations from our protocol in the Supplemental Online Material (SOM).
+We make data, analysis scripts, and the fully reproducible manuscript
+available online.\footnote{\url{https://osf.io/w5tqv/?view_only=5cbf7ad5b2b449a7a0f4ada0337b802a}}
 
@@
 reverse of perceived injustice. We included studies that measured
-personal or group discrimination or a mixture of both.
+personal or group discrimination or both.
 
@@
 database. We used similar non-exclusive search terms for all databases
-(see SOM-R). We searched databases on April 1, 2019 and again on April
-1, 2020. We exported records and relevant metadata from each database.
-We removed duplicates using the \emph{revtools} package (Westgate,
-2019).
+(see SOM). We searched databases on April 1, 2019 and again on April 1,
+2020. We exported records and relevant metadata from each database. We
+removed duplicates using the \emph{revtools} package (Westgate, 2019).
 
 To find unpublished studies, we sent a call to the mailing lists of
-several professional organizations (see SOM-R). We also advertised on
+several professional organizations (see SOM). We also advertised on
 social media and at relevant conferences. We directed researchers to an
@@
 to update prior distributions in light of the observed data to produce
-posterior distributions. Other than \emph{p}-values and confidence
+posterior distributions. In contrast to \emph{p}-values and confidence
 intervals, the resulting posterior distributions have a straightforward
@@
 participants in \(I = 140\) samples (for a complete list of studies, see
-SOM-U).
+SOM).
 
@@
 \textbf{\emph{Perceived Injustice.}} Across 203,637 participants from
-126 samples in 86 studies, we found strong evidence for a weak
+126 samples in 86 studies, we found strong evidence for a weak negative
 association (\(r = -.07, [-.10, -.04]\)) between intergroup contact and
@@
 that 80\% of studies would result in correlation coefficients between
--.25 and .11 and that researchers would need sample sizes of at least
+-.25 and .11 and that 31\% of studies would find a \emph{positive}
+correlation between intergroup contact and perceived injustice. Our
+analyses suggested that researchers would need sample sizes of at least
 2,542 participants to find significant associations (\(\alpha = .05\),
@@
 \textbf{\emph{Collective Action.}} Across 119,085 participants from 37
-samples in 24 studies, we found some evidence for a weak association
-(\(r = -.06, [-.13, .02]\)) between intergroup contact and collective
-action, with \(93.6\%\) of posterior samples for the mean correlation
-coefficient falling below zero. We found evidence that correlation
-coefficients varied across studies (\(\tau_J = .16, [.12, .23]\)) and
-across samples within studies (\(\tau_I = .09, [.06, .14]\)). Based on
-these analyses, we predicted that 80\% of studies would result in
-correlation coefficients between -.27 and .16 and that researchers would
-need sample sizes of at least 1,882 participants to find significant
-associations (\(\alpha = .05\), two-sided) in 80\% of their studies.
+samples in 24 studies, we found some evidence for a weak negative
+association (\(r = -.06, [-.13, .02]\)) between intergroup contact and
+collective action, with \(93.6\%\) of posterior samples for the mean
+correlation coefficient falling below zero. We found evidence that
+correlation coefficients varied across studies
+(\(\tau_J = .16, [.12, .23]\)) and across samples within studies
+(\(\tau_I = .09, [.06, .14]\)). Based on these analyses, we predicted
+that 80\% of studies would result in correlation coefficients between
+-.27 and .16 and that 36\% of studies would find a \emph{positive}
+correlation between intergroup contact and collective action. Our
+analyses suggested that researchers would need sample sizes of at least
+1,882 participants to find significant associations (\(\alpha = .05\),
+two-sided) in 80\% of their studies.
 
 \textbf{\emph{Policy Support.}} Across 13,703 participants from 19
-samples in 14 studies, we found evidence for a weak association
+samples in 14 studies, we found evidence for a weak negative association
 (\(r = -.07, [-.14, -.00]\)) between intergroup contact and policy
@@
 that 80\% of studies would result in correlation coefficients between
--.21 and .07 and that researchers would need sample sizes of at least
-3,208 participants to find significant associations (\(\alpha = .05\),
+-.21 and .07 and that 25\% of studies would find a \emph{positive}
+correlation between intergroup contact and policy support. Our analyses
+suggested that researchers would need sample sizes of at least 3,208
+participants to find significant associations (\(\alpha = .05\),
 two-sided) in 80\% of their studies.
@@
 our main analyses were robust to choosing different prior distributions
-and to excluding influential studies (see SOM-R).
+and to excluding influential studies (see SOM).
 
@@
 an insufficient number of effect sizes to examine moderators for any
-outcome except perceived injustice (for details, see SOM-R).
+outcome except perceived injustice (for details, see SOM).
 
@@
 
-\begin{figure*}[t!]
+\begin{figure*}
 \centering
@@
 
+\leavevmode\hypertarget{ref-hassler_intergroup_2021}{}%
+Hässler, T., Uluğ, Ö. M., Kappmeier, M., \& Travaglino, G. A. (2021).
+Intergroup contact and social change: An integrated contact‐collective
+action model. \emph{Journal of Social Issues}, \emph{77}(1), 217--241.
+\url{https://doi.org/10.1111/josi.12412}
+
 \leavevmode\hypertarget{ref-1407}{}%
@@
 
+\leavevmode\hypertarget{ref-macinnis_extending_2019}{}%
+MacInnis, C. C., \& Hodson, G. (2019). Extending the benefits of
+intergroup contact beyond attitudes: When does intergroup contact
+predict greater collective action support? \emph{Journal of Theoretical
+Social Psychology}, \emph{3}(1), 11--22.
+\url{https://doi.org/10.1002/jts5.23}
+
 \leavevmode\hypertarget{ref-893}{}%
@@
 
+\leavevmode\hypertarget{ref-mazumder_persistent_2018}{}%
+Mazumder, S. (2018). The persistent effect of U. S. civil rights
+protests on political attitudes. \emph{American Journal of Political
+Science}, \emph{62}(4), 922--935.
+\url{https://doi.org/10.1111/ajps.12384}
+
 \leavevmode\hypertarget{ref-1850}{}%
@@
 University{]}. ProQuest Dissertations and Theses Global.
+
+\leavevmode\hypertarget{ref-mckeown_contact_2017}{}%
+McKeown, S., \& Dixon, J. (2017). The ``contact hypothesis'': Critical
+reflections and future directions. \emph{Social and Personality
+Psychology Compass}, \emph{11}(1), e12295.
+\url{https://doi.org/10.1111/spc3.12295}
 
@@
 
+\leavevmode\hypertarget{ref-smith_relative_2012}{}%
+Smith, H. J., Pettigrew, T. F., Pippin, G. M., \& Bialosiewicz, S.
+(2012). Relative deprivation: A theoretical and meta-analytic review.
+\emph{Personality and Social Psychology Review}, \emph{16}(3), 203--232.
+\url{https://doi.org/10.1177/1088868311430825}
+
 \leavevmode\hypertarget{ref-stan_development_team_rstan:_2020}{}%

### 2021-06-11 manuscript/manuscript.Rmd
revise method/results

@@
 @956 further found that, first, disadvantaged-group members who have more positive contact also tend to have less negative contact and, second, positive contact is not associated with perceived discrimination or collective action after controlling for negative contact.
-Based on these findings, @956 argued that the mobilizing effect of negative contact could be an alternative explanation for the negative relationship between positive contact and support for social change observed in previous studies.
+Based on these findings, @956 argued that the mobilizing effect of negative contact could be an alternative explanation for the negative relationship between positive contact and support for social change observed in prior studies.
 
@@
 As outgroup contact places limits on how much ingroup contact one can have [@pfister_contact_2020], disadvantaged-group members who have more outgroup contact can be expected to have less ingroup contact.
-Based on these observations, one might argue that the mobilizing effect of ingroup contact could be an alternative explanation for the negative association between outgroup contact and support for social change observed in previous studies.
+Based on these observations, one might argue that the mobilizing effect of ingroup contact could be an alternative explanation for the negative association between outgroup contact and support for social change observed in prior studies.
 
@@
 On the other hand, researchers have argued that intergroup contact might not reduce, or even increase, support for social change in disadvantaged groups.
-Settling this debate is important both because intergroup contact is a promising means of reducing prejudice [@pettigrew_meta-analytic_2006] and because political mobilization by the disadvantaged is often crucial for achieving social change [see, e.g., @mazumder_persistent_2018].
+Settling this debate is important both because intergroup contact is a promising means of reducing prejudice [@pettigrew_meta-analytic_2006] and because political mobilization by the disadvantaged is often crucial for achieving social change [see, for example, @mazumder_persistent_2018].
 
-While several narrative reviews of the growing literature on this topic have been published [@hassler_intergroup_2021; @macinnis_extending_2019; @mckeown_contact_2017], we present the first systematic review and meta-analysis of the relationship between intergroup contact and support for social change in disadvantaged groups.
+While narrative reviews of the growing literature on this topic have been published [@hassler_intergroup_2021; @macinnis_extending_2019; @mckeown_contact_2017], we present the first systematic review and meta-analysis of the relationship between intergroup contact and support for social change in disadvantaged groups.
+To test the hypothesized 'ironic' effects of intergroup contact, we evaluate the evidence that contact with advantaged-group members reduces disadvantaged-group members' perceived injustice, discourages them from engaging in collective action, and diminishes their support for reparative policies.
 
@@
 ***Study Intention.*** We coded whether or not each study was conducted with the intention to examine the effects of intergroup contact on one or more of the three outcome measures ($\kappa = .48$).
+We did not achieve acceptable inter-rater agreement in our initial coding.
+After refining our coding criteria, we re-coded all studies by consensus.
 
@@
 
-***Cultural Distance.*** We also used the measure developed by @muthukrishna_beyond_2020, when available, to quantify each country’s cultural distance from the United States, which represents the cultural context of most psychological research [@henrich_weirdest_2010].
+***Cultural Distance.*** We also used the index developed by @muthukrishna_beyond_2020, where available, to quantify each country’s cultural distance from the United States, which represents the cultural context of most psychological research [@henrich_weirdest_2010].
 
@@
 
-In addition, we ran preregistered robustness checks which showed that our main analyses were robust to choosing different prior distributions and to excluding influential studies (see SOM).
+### Robustness Checks
+
+```{r, include = FALSE}
+
+  # Summarize prior choice results
+  d_priors <- read_rds("../results/results_robustness_checks_priors.rds") %>% 
+    group_by(y_var, prior) %>% 
+    median_qi(d_r_mean) %>% 
+    mutate(
+      across(c(d_r_mean, .lower, .upper), ~f_num(., digits = 2)),
+      text = paste0("$\\Delta r = ", d_r_mean, ", [", .lower, ", ", .upper, "]$")
+    )
+
+```
+
+```{r, include = FALSE}
+
+  # Calculate Mean Absolute Deviation (MAD)
+  mad_loo <- read_rds("../results/results_robustness_checks_loo.rds") %>% 
+    group_by(.draw, y_var) %>% 
+    summarize(mad_loo = mean(ae_loo)) %>% 
+    group_by(y_var) %>% 
+    median_qi(mad_loo) %>% 
+    mutate(
+      across(c(mad_loo, .lower, .upper), ~f_num(., digits = 2)),
+      text = paste0("$\\textit{MAD} = ", mad_loo, ", [", .lower, ", ", .upper, "]$")
+    )
+
+  # Leave out most influential studies
+  d_loo <- read_rds("../results/results_robustness_checks_loo.rds") %>% 
+    group_by(y_var, id) %>%
+    median_qi(e_loo) %>% 
+    top_n(n = 1, wt = abs(e_loo)) %>% 
+    mutate(
+      across(c(e_loo, .lower, .upper), ~f_num(., digits = 2)),
+      text = paste0("$\\Delta r = ", e_loo, ", [", .lower, ", ", .upper, "]$")
+    )
+
+```
+
+As preregistered, we conducted two kinds of robustness checks.
+First, we assessed to what extent our findings were sensitive to choosing narrower, $\mu \sim \text{Normal}(0, 0.1)$, or wider, $\mu \sim \text{Normal}(0, 1)$, prior distributions.
+Choosing narrower or wider prior distribution did not affect mean effect size estimates for perceived injustice (`r d_priors$text[d_priors$y_var == "pi" & d_priors$prior == "N(0, 0.1)"]` and `r d_priors$text[d_priors$y_var == "pi" & d_priors$prior == "N(0, 1.0)"]`), collective action (`r d_priors$text[d_priors$y_var == "ca" & d_priors$prior == "N(0, 0.1)"]` and `r d_priors$text[d_priors$y_var == "ca" & d_priors$prior == "N(0, 1.0)"]`), and policy support (`r d_priors$text[d_priors$y_var == "ps" & d_priors$prior == "N(0, 0.1)"]` and `r d_priors$text[d_priors$y_var == "ps" & d_priors$prior == "N(0, 1.0)"]`).
+Second, we assessed to what extent our findings were sensitive to including or excluding influential studies by repeating the preregistered analyses $J$ times while leaving out one of $J$ studies each time and by calculating the mean absolute difference (*MAD*) for the estimated mean effect size across left-out studies.
+For perceived injustice (`r mad_loo$text[mad_loo$y_var == "pi"]`), collective action (`r mad_loo$text[mad_loo$y_var == "ca"]`), and policy support (`r mad_loo$text[mad_loo$y_var == "ps"]`), the *MAD* was small.
+Leaving out the most influential study, for example, did not change estimates of the mean effect size for the three outcomes (`r d_loo$text[d_loo$y_var == "pi"]`; `r d_loo$text[d_loo$y_var == "ca"]`; `r d_loo$text[d_loo$y_var == "ps"]`).
+These analyses showed that our findings were robust to choosing different prior distributions and to excluding influential studies.
 
@@
 
-We conducted two kinds of moderator analyses. For both analyses, we had an insufficient number of effect sizes to examine moderators for any outcome except perceived injustice (for details, see SOM).
+We conducted three kinds of moderator analyses.
+As we had insufficient numbers of effect sizes to examine moderators for collective action and policy support, we report results for these outcomes in the SOM.
 
@@
 
-First, we used meta-regression models to examine specific moderator variables which we expected to explain heterogeneity in effect sizes across samples.
-Figure 4 shows results for categorical moderator variables.
-We found that the setting of the study (`r with(R2, R2[moderator == "study_setting"])`), participants’ age group (`r with(R2, R2[moderator == "age"])`), and whether intergroup contact was measured directly or indirectly (`r with(R2, R2[moderator == "ic_direct"])`) explained the most variance across effect sizes.
-Figure 5 shows results from country-level analyses examining cultural context as a moderator variable.
-We found that cultural distance from the United States tended to be associated with larger effect sizes—although we had data from too few countries to reach any firm conclusions.
+First, we used meta-regression models to examine categorical moderator variables which we expected to explain heterogeneity in effect sizes across samples.
+As Figure 4 shows, we found that the setting of the study (`r with(R2, R2[moderator == "study_setting"])`), participants’ age group (`r with(R2, R2[moderator == "age"])`), and whether intergroup contact was measured directly or indirectly (`r with(R2, R2[moderator == "ic_direct"])`) explained the most variance across effect sizes.
 
-Second, we used meta-regression trees to discover interactions between moderator variables that best explained heterogeneity in effect sizes [@li_multiple_2020].
-Figure 6 shows the resulting meta-regression that explained more variance across samples than any individual moderator (`r with(meta_cart, unique(R2))`).
+Second, we used meta-regression models to estimate effect sizes as a function of each country's cultural distance from the United States [@muthukrishna_beyond_2020].
+Because cultural distance is a country-level moderator variable, we estimated random intercepts to account for both country-specific deviations from the mean effect size and sample-specific deviations from the country-specific effect size.
+As Figure 5 shows, we found that cultural distance from the United States tended to be associated with larger effect sizes—although we had data from too few countries to reach any firm conclusions.
+
+Third, we used meta-regression trees to discover interactions between moderator variables that best explained heterogeneity in effect sizes [@li_meta-cart_2017; @li_multiple_2020].
+Figure 6 shows the resulting meta-regression model, which explained more variance across samples than any individual moderator (`r with(meta_cart, unique(R2))`).
 We found that intergroup contact was associated with less perceived injustice only in studies that focused on adults and that measured intergroup contact directly.
@@
 Following Carter et al.’s recommendations, we compared results of several methods to adjust meta-analytic estimates for publication bias: the PET-PEESE estimator [@stanley_meta-regression_2014]; the three-parameter selection model [3PSM; @vevea_general_1995]; and the *p*-uniform* estimator [@van_aert_correcting_2018].
-As these methods do not use Bayesian statistics, we compared adjusted estimates from these methods to unadjusted estimates from a random-effects meta-analysis estimated with restricted maximum likelihood estimation using the *metafor* package [@viechtbauer_conducting_2010].
-In addition, we ran a meta-regression model that compared studies that were published *and* were conducted with the intention to examine the effects of intergroup contact on any of the outcomes to all other studies.
-We report estimates from the latter subgroup of studies as we can assume that effect sizes in this subgroup were not affected by publication bias.
+In addition, we ran a subgroup analysis that included only studies that were not published or not conducted with the intention to examine the effects of intergroup contact on any of the outcomes—and that, therefore, can be assumed to have not been affected by publication bias.
+As these methods do not use Bayesian statistics, we compared adjusted estimates to unadjusted estimates from a random-effects meta-analysis estimated with restricted maximum likelihood estimation using the *metafor* package [@viechtbauer_conducting_2010].
 

### 2021-06-11 manuscript/manuscript.tex
revise method/results

@@
 relationship between positive contact and support for social change
-observed in previous studies.
+observed in prior studies.
 
@@
 for the negative association between outgroup contact and support for
-social change observed in previous studies.
+social change observed in prior studies.
 
@@
 \& Tropp, 2006) and because political mobilization by the disadvantaged
-is often crucial for achieving social change (see, e.g., Mazumder,
-2018).
-
-While several narrative reviews of the growing literature on this topic
-have been published (Hässler et al., 2021; MacInnis \& Hodson, 2019;
-McKeown \& Dixon, 2017), we present the first systematic review and
+is often crucial for achieving social change (see, for example,
+Mazumder, 2018).
+
+While narrative reviews of the growing literature on this topic have
+been published (Hässler et al., 2021; MacInnis \& Hodson, 2019; McKeown
+\& Dixon, 2017), we present the first systematic review and
 meta-analysis of the relationship between intergroup contact and support
-for social change in disadvantaged groups.
+for social change in disadvantaged groups. To test the hypothesized
+`ironic' effects of intergroup contact, we evaluate the evidence that
+contact with advantaged-group members reduces disadvantaged-group
+members' perceived injustice, discourages them from engaging in
+collective action, and diminishes their support for reparative policies.
 
@@
 contact on one or more of the three outcome measures (\(\kappa = .48\)).
+We did not achieve acceptable inter-rater agreement in our initial
+coding. After refining our coding criteria, we re-coded all studies by
+consensus.
 
@@
 
-\textbf{\emph{Cultural Distance.}} We also used the measure developed by
-Muthukrishna et al. (2020), when available, to quantify each country's
+\textbf{\emph{Cultural Distance.}} We also used the index developed by
+Muthukrishna et al. (2020), where available, to quantify each country's
 cultural distance from the United States, which represents the cultural
@@
 
-In addition, we ran preregistered robustness checks which showed that
-our main analyses were robust to choosing different prior distributions
-and to excluding influential studies (see SOM).
+\hypertarget{robustness-checks}{%
+\subsubsection{Robustness Checks}\label{robustness-checks}}
+
+As preregistered, we conducted two kinds of robustness checks. First, we
+assessed to what extent our findings were sensitive to choosing
+narrower, \(\mu \sim \text{Normal}(0, 0.1)\), or wider,
+\(\mu \sim \text{Normal}(0, 1)\), prior distributions. Choosing narrower
+or wider prior distribution did not affect mean effect size estimates
+for perceived injustice (\(\Delta r = -.00, [-.05, .04]\) and
+\(\Delta r = .00, [-.05, .05]\)), collective action
+(\(\Delta r = -.01, [-.11, .09]\) and \(\Delta r = .00, [-.11, .10]\)),
+and policy support (\(\Delta r = -.01, [-.10, .08]\) and
+\(\Delta r = .00, [-.09, .10]\)). Second, we assessed to what extent our
+findings were sensitive to including or excluding influential studies by
+repeating the preregistered analyses \(J\) times while leaving out one
+of \(J\) studies each time and by calculating the mean absolute
+difference (\emph{MAD}) for the estimated mean effect size across
+left-out studies. For perceived injustice
+(\(\textit{MAD} = .02, [.01, .04]\)), collective action
+(\(\textit{MAD} = .04, [.02, .09]\)), and policy support
+(\(\textit{MAD} = .03, [.02, .08]\)), the \emph{MAD} was small. Leaving
+out the most influential study, for example, did not change estimates of
+the mean effect size for the three outcomes
+(\(\Delta r = -.00, [-.05, .04]\); \(\Delta r = .02, [-.08, .12]\);
+\(\Delta r = -.02, [-.11, .07]\)). These analyses showed that our
+findings were robust to choosing different prior distributions and to
+excluding influential studies.
 
@@
 
-We conducted two kinds of moderator analyses. For both analyses, we had
-an insufficient number of effect sizes to examine moderators for any
-outcome except perceived injustice (for details, see SOM).
+We conducted three kinds of moderator analyses. As we had insufficient
+numbers of effect sizes to examine moderators for collective action and
+policy support, we report results for these outcomes in the SOM.
 
@@
 
-First, we used meta-regression models to examine specific moderator
+First, we used meta-regression models to examine categorical moderator
 variables which we expected to explain heterogeneity in effect sizes
-across samples. Figure 4 shows results for categorical moderator
-variables. We found that the setting of the study (\(R^2 = 20\%\)),
-participants' age group (\(R^2 = 11\%\)), and whether intergroup contact
-was measured directly or indirectly (\(R^2 = 10\%\)) explained the most
-variance across effect sizes. Figure 5 shows results from country-level
-analyses examining cultural context as a moderator variable. We found
-that cultural distance from the United States tended to be associated
-with larger effect sizes---although we had data from too few countries
-to reach any firm conclusions.
-
-Second, we used meta-regression trees to discover interactions between
+across samples. As Figure 4 shows, we found that the setting of the
+study (\(R^2 = 20\%\)), participants' age group (\(R^2 = 11\%\)), and
+whether intergroup contact was measured directly or indirectly
+(\(R^2 = 10\%\)) explained the most variance across effect sizes.
+
+Second, we used meta-regression models to estimate effect sizes as a
+function of each country's cultural distance from the United States
+(Muthukrishna et al., 2020). Because cultural distance is a
+country-level moderator variable, we estimated random intercepts to
+account for both country-specific deviations from the mean effect size
+and sample-specific deviations from the country-specific effect size. As
+Figure 5 shows, we found that cultural distance from the United States
+tended to be associated with larger effect sizes---although we had data
+from too few countries to reach any firm conclusions.
+
+Third, we used meta-regression trees to discover interactions between
 moderator variables that best explained heterogeneity in effect sizes
-(Li et al., 2020). Figure 6 shows the resulting meta-regression that
-explained more variance across samples than any individual moderator
-(\(R^2 = 31\%\)). We found that intergroup contact was associated with
-less perceived injustice only in studies that focused on adults and that
-measured intergroup contact directly. Among these studies, this
-association was stronger in settings in which the groups' relative
-inequality stemmed from short-term migration or colonization
+(Li et al., 2017, 2020). Figure 6 shows the resulting meta-regression
+model, which explained more variance across samples than any individual
+moderator (\(R^2 = 31\%\)). We found that intergroup contact was
+associated with less perceived injustice only in studies that focused on
+adults and that measured intergroup contact directly. Among these
+studies, this association was stronger in settings in which the groups'
+relative inequality stemmed from short-term migration or colonization
 (\(r = -.18, [-.23, -.13]\)) than in other settings
@@
 (3PSM; Vevea \& Hedges, 1995); and the \emph{p}-uniform* estimator (van
-Aert \& Assen, 2018). As these methods do not use Bayesian statistics,
-we compared adjusted estimates from these methods to unadjusted
-estimates from a random-effects meta-analysis estimated with restricted
-maximum likelihood estimation using the \emph{metafor} package
-(Viechtbauer, 2010). In addition, we ran a meta-regression model that
-compared studies that were published \emph{and} were conducted with the
+Aert \& Assen, 2018). In addition, we ran a subgroup analysis that
+included only studies that were not published or not conducted with the
 intention to examine the effects of intergroup contact on any of the
-outcomes to all other studies. We report estimates from the latter
-subgroup of studies as we can assume that effect sizes in this subgroup
-were not affected by publication bias.
+outcomes---and that, therefore, can be assumed to have not been affected
+by publication bias. As these methods do not use Bayesian statistics, we
+compared adjusted estimates to unadjusted estimates from a
+random-effects meta-analysis estimated with restricted maximum
+likelihood estimation using the \emph{metafor} package (Viechtbauer,
+2010).
 
@@
 
+\leavevmode\hypertarget{ref-li_meta-cart_2017}{}%
+Li, X., Dusseldorp, E., \& Meulman, J. J. (2017). Meta-CART: A tool to
+identify interactions between moderators in meta-analysis. \emph{British
+Journal of Mathematical and Statistical Psychology}, \emph{70}(1),
+118--136. \url{https://doi.org/10.1111/bmsp.12088}
+
 \leavevmode\hypertarget{ref-li_multiple_2020}{}%
@@
 \leavevmode\hypertarget{ref-westgate_revtools:_2019}{}%
-Westgate, M. J. (2019). Revtools: An R package to support article
+Westgate, M. J. (2019). revtools: An R package to support article
 screening for evidence synthesis. \emph{Research Synthesis Methods},

### 2021-06-11 manuscript/supplemental-materials.Rmd
revise method/results

@@
 
-## Robustness Checks
-
-```{r, include = FALSE}
-
-  # Summarize prior choice results
-  d_priors <- read_rds("../results/results_robustness_checks_priors.rds") %>% 
-    group_by(y_var, prior) %>% 
-    median_qi(d_r_mean) %>% 
-    mutate(
-      across(c(d_r_mean, .lower, .upper), ~f_num(., digits = 2)),
-      text = paste0("$\\Delta r = ", d_r_mean, ", [", .lower, ", ", .upper, "]$")
-    )
-
-```
-
-```{r, include = FALSE}
-
-  # Calculate Mean Absolute Deviation (MAD)
-  mad_loo <- read_rds("../results/results_robustness_checks_loo.rds") %>% 
-    group_by(.draw, y_var) %>% 
-    summarize(mad_loo = mean(ae_loo)) %>% 
-    group_by(y_var) %>% 
-    median_qi(mad_loo) %>% 
-    mutate(
-      across(c(mad_loo, .lower, .upper), ~f_num(., digits = 2)),
-      text = paste0("$\\textit{MAD} = ", mad_loo, ", [", .lower, ", ", .upper, "]$")
-    )
-
-  # Leave out most influential studies
-  d_loo <- read_rds("../results/results_robustness_checks_loo.rds") %>% 
-    group_by(y_var, id) %>%
-    median_qi(e_loo) %>% 
-    top_n(n = 1, wt = abs(e_loo)) %>% 
-    mutate(
-      across(c(e_loo, .lower, .upper), ~f_num(., digits = 2)),
-      text = paste0("$\\Delta r = ", e_loo, ", [", .lower, ", ", .upper, "]$")
-    )
-
-```
-
-As preregistered, we conducted two kinds of robustness checks.
-First, we assessed to what extent our findings were sensitive to choosing narrower, $\mu \sim \text{Normal}(0, 0.1)$, or wider, $\mu \sim \text{Normal}(0, 1)$, prior distributions.
-Choosing narrower or wider prior distribution did not affect mean effect size estimates for perceived injustice (`r d_priors$text[d_priors$y_var == "pi" & d_priors$prior == "N(0, 0.1)"]` and `r d_priors$text[d_priors$y_var == "pi" & d_priors$prior == "N(0, 1.0)"]`), collective action (`r d_priors$text[d_priors$y_var == "ca" & d_priors$prior == "N(0, 0.1)"]` and `r d_priors$text[d_priors$y_var == "ca" & d_priors$prior == "N(0, 1.0)"]`), and policy support (`r d_priors$text[d_priors$y_var == "ps" & d_priors$prior == "N(0, 0.1)"]` and `r d_priors$text[d_priors$y_var == "ps" & d_priors$prior == "N(0, 1.0)"]`).
-Second, we assessed to what extent our findings were sensitive to including or excluding influential studies by repeating the preregistered analyses $J$ times while leaving out one of $J$ studies each time and by calculating the mean absolute difference (*MAD*) for the estimated mean effect size across left-out studies.
-For perceived injustice (`r mad_loo$text[mad_loo$y_var == "pi"]`), collective action (`r mad_loo$text[mad_loo$y_var == "ca"]`), and policy support (`r mad_loo$text[mad_loo$y_var == "ps"]`), the *MAD* was small.
-Leaving out the most influential study, for example, did not change estimates of the mean effect size for the three outcomes (`r d_loo$text[d_loo$y_var == "pi"]`; `r d_loo$text[d_loo$y_var == "ca"]`; `r d_loo$text[d_loo$y_var == "ps"]`).
-Together, these analyses showed that our findings were robust to choosing different prior distributions and to excluding influential studies.
-
 ## Moderator Analyses
@@
 Comparisons were inconclusive because we had an insufficient number of effect sizes per category.
-We ran another three random-effects meta-regression models with Muthukrishna et al.'s [-@muthukrishna_beyond_2020] measure of cultural distance, where available, as a continuous moderator variable.
+Second, we ran another three random-effects meta-regression models with Muthukrishna et al.'s [-@muthukrishna_beyond_2020] measure of cultural distance, where available, as a continuous moderator variable.
 Because cultural distance was a country-level moderator variable, we used two-level random-effects models in which we estimated country-specific deviations from the mean effect size as well as sample-specific deviations from the country-specific effect size.
@@
 
-Second, we used meta-regression trees to discover interactions between moderator variables that best explained heterogeneity in effect sizes [@li_meta-cart_2017; @li_multiple_2020].
+Second, we used meta-regression trees to discover interactions between moderator variables that best explained heterogeneity in effect sizes [@li_meta-cart_2017].
 As recommended, we ran random-effects meta-regression tree analyses using the look-ahead strategy [@li_multiple_2020].

### 2021-06-12 manuscript/manuscript.Rmd
revise abstract

@@
 However, these associations were small, variable, and consistent with alternative explanations.
-Moderator analyses found that associations were strongest in studies of adults that measured intergroup contact directly and examined short-term migration or post-colonial intergroup relations.
-After controlling for the positive association of negative contact with support for social change, positive contact was not associated with any outcome in studies that measured both predictors.
-We close by highlighting open questions about the relationship between intergroup contact and social change.
+Across outcomes, `r with(readRDS("../results/results_for_abstract.rds"), paste0(round(min(p_pred)*100), "--", round(max(p_pred)*100), "\\%"))` of studies found *positive* associations with intergroup contact.
+Moderator analyses explained about a third of the between-sample variance, showing that, on average, associations were negative only in studies of adults that measured intergroup contact directly and were strongest in studies that examined short-term migration or (post-)colonial intergroup relations.
+We found evidence for an alternative explanation for the apparent ‘ironic’ effects of intergroup contact as, after controlling for the positive association of negative contact with support for social change, positive contact was not associated with any of the outcomes.
+We close by discussing strengths and limitations of the available evidence and by highlighting open questions about the relationship between intergroup contact and social change in disadvantaged groups.
 output:
@@
 @sengupta_ingroup_2015 found ingroup contact to be associated with decreased endorsement of system-justifying beliefs and increased support for reparative policies benefiting the disadvantaged ingroup, suggesting that contact with other ingroup members can motivate disadvantaged-group members to support social change [see also @1695].
-As outgroup contact places limits on how much ingroup contact one can have [@pfister_contact_2020], disadvantaged-group members who have more outgroup contact can be expected to have less ingroup contact.
+As outgroup contact places limits on how much ingroup contact a person can have [@pfister_contact_2020], disadvantaged-group members who have more outgroup contact can be expected to have less ingroup contact.
 Based on these observations, one might argue that the mobilizing effect of ingroup contact could be an alternative explanation for the negative association between outgroup contact and support for social change observed in prior studies.

### 2021-06-12 manuscript/manuscript.tex
revise abstract

@@
 associations were small, variable, and consistent with alternative
-explanations. Moderator analyses found that associations were strongest
-in studies of adults that measured intergroup contact directly and
-examined short-term migration or post-colonial intergroup relations.
-After controlling for the positive association of negative contact with
-support for social change, positive contact was not associated with any
-outcome in studies that measured both predictors. We close by
+explanations. Across outcomes, 25--36\% of studies found \emph{positive}
+associations with intergroup contact. Moderator analyses explained about
+a third of the between-sample variance, showing that, on average,
+associations were negative only in studies of adults that measured
+intergroup contact directly and were strongest in studies that examined
+short-term migration or (post-)colonial intergroup relations. We found
+evidence for an alternative explanation for the apparent `ironic'
+effects of intergroup contact as, after controlling for the positive
+association of negative contact with support for social change, positive
+contact was not associated with any of the outcomes. We close by
+discussing strengths and limitations of the available evidence and by
 highlighting open questions about the relationship between intergroup
-contact and social change.
+contact and social change in disadvantaged groups.
 
@@
 \& Sibley, 2013). As outgroup contact places limits on how much ingroup
-contact one can have (Pfister et al., 2020), disadvantaged-group members
-who have more outgroup contact can be expected to have less ingroup
-contact. Based on these observations, one might argue that the
+contact a person can have (Pfister et al., 2020), disadvantaged-group
+members who have more outgroup contact can be expected to have less
+ingroup contact. Based on these observations, one might argue that the
 mobilizing effect of ingroup contact could be an alternative explanation

### 2021-06-12 manuscript/supplemental-materials.Rmd
revise abstract

@@
 Comparisons were inconclusive because we had an insufficient number of effect sizes per category.
+
 Second, we ran another three random-effects meta-regression models with Muthukrishna et al.'s [-@muthukrishna_beyond_2020] measure of cultural distance, where available, as a continuous moderator variable.
@@
 
-Second, we used meta-regression trees to discover interactions between moderator variables that best explained heterogeneity in effect sizes [@li_meta-cart_2017].
+Third, we used meta-regression trees to discover interactions between moderator variables that best explained heterogeneity in effect sizes [@li_meta-cart_2017].
 As recommended, we ran random-effects meta-regression tree analyses using the look-ahead strategy [@li_multiple_2020].

### 2021-06-12 manuscript/supplemental-materials.tex
revise abstract

--- 2021-05-14 manuscript/supplemental-materials.tex
@@
 
-\hypertarget{robustness-checks}{%
-\subsection{Robustness Checks}\label{robustness-checks}}
-
-As preregistered, we conducted two kinds of robustness checks. First, we
-assessed to what extent our findings were sensitive to choosing
-narrower, \(\mu \sim \text{Normal}(0, 0.1)\), or wider,
-\(\mu \sim \text{Normal}(0, 1)\), prior distributions. Choosing narrower
-or wider prior distribution did not affect mean effect size estimates
-for perceived injustice (\(\Delta r = -.00, [-.05, .04]\) and
-\(\Delta r = .00, [-.05, .05]\)), collective action
-(\(\Delta r = -.01, [-.11, .09]\) and \(\Delta r = .00, [-.11, .10]\)),
-and policy support (\(\Delta r = -.01, [-.10, .08]\) and
-\(\Delta r = .00, [-.09, .10]\)). Second, we assessed to what extent our
-findings were sensitive to including or excluding influential studies by
-repeating the preregistered analyses \(J\) times while leaving out one
-of \(J\) studies each time and by calculating the mean absolute
-difference (\emph{MAD}) for the estimated mean effect size across
-left-out studies. For perceived injustice
-(\(\textit{MAD} = .02, [.01, .04]\)), collective action
-(\(\textit{MAD} = .04, [.02, .09]\)), and policy support
-(\(\textit{MAD} = .03, [.02, .08]\)), the \emph{MAD} was small. Leaving
-out the most influential study, for example, did not change estimates of
-the mean effect size for the three outcomes
-(\(\Delta r = .01, [-.04, .05]\); \(\Delta r = .02, [-.08, .12]\);
-\(\Delta r = -.02, [-.11, .07]\)). Together, these analyses showed that
-our findings were robust to choosing different prior distributions and
-to excluding influential studies.
-
 \hypertarget{moderator-analyses}{%
@@
 inconclusive because we had an insufficient number of effect sizes per
-category. We ran another three random-effects meta-regression models
-with Muthukrishna et al.'s (2020) measure of cultural distance, where
+category.
+
+Second, we ran another three random-effects meta-regression models with
+Muthukrishna et al.'s (2020) measure of cultural distance, where
 available, as a continuous moderator variable. Because cultural distance
@@
 
-Second, we used meta-regression trees to discover interactions between
+Third, we used meta-regression trees to discover interactions between
 moderator variables that best explained heterogeneity in effect sizes
-(Li et al., 2017, 2020). As recommended, we ran random-effects
-meta-regression tree analyses using the look-ahead strategy (Li et al.,
-2020). We set the pruning parameter to \(c = 0\) because, for this
-analysis, we prioritized exploration over error control
+(Li et al., 2017). As recommended, we ran random-effects meta-regression
+tree analyses using the look-ahead strategy (Li et al., 2020). We set
+the pruning parameter to \(c = 0\) because, for this analysis, we
+prioritized exploration over error control
 (\texttt{run\_exploratory\_moderator\_analyses.R}). For both collective
@@
 \end{figure*}
+
+\newpage
 

### 2021-06-12 scripts/run_preregistered_analyses.R

@@ -387,6 +387,20 @@ rm(list = ls())
         distinct(id, jj, x_var, y_var),
       by = c("x_var", "y_var", "jj")
     )
+  
+  # Extract predicted proportion of studies for which r > 0
+  set.seed(9071118)
+  abstract <- post %>% 
+    filter(x_var == "ic", y_var %in% c("pi", "ca", "ps")) %>% 
+    mutate(
+      r_pred = z_to_r(rnorm(n = n(), mean = mu, sd = tau_jj))
+    ) %>% 
+    group_by(x_var, y_var) %>% 
+    summarize(
+      r_mean = median(r_mean),
+      p_pred = mean(r_pred > 0)
+    ) %>% 
+    ungroup()
 
 
 # Export ------------------------------------------------------------------
@@ -396,3 +410,6 @@ rm(list = ls())
   
   # Export study-wise estimates (as .rds)
   write_rds(pred_jj, "results/r_pred_jj.rds")
+  
+  # Export results for abstract (as .rds)
+  write_rds(abstract, "results/results_for_abstract.rds")

### 2021-06-16 manuscript/manuscript.Rmd
revise discussion

@@
 Moderator analyses explained about a third of the between-sample variance, showing that, on average, associations were negative only in studies of adults that measured intergroup contact directly and were strongest in studies that examined short-term migration or (post-)colonial intergroup relations.
-We found evidence for an alternative explanation for the apparent ‘ironic’ effects of intergroup contact as, after controlling for the positive association of negative contact with support for social change, positive contact was not associated with any of the outcomes.
-We close by discussing strengths and limitations of the available evidence and by highlighting open questions about the relationship between intergroup contact and social change in disadvantaged groups.
+We also found evidence for an alternative explanation for the apparent ‘ironic’ effects of intergroup contact as, after controlling for the positive association of negative contact with support for social change, positive contact was no longer associated with any of the outcomes.
+We close by discussing strengths and limitations of the available evidence and by highlighting open questions about the relationship between intergroup contact and support for social change in disadvantaged groups.
 output:
@@
 While narrative reviews of the growing literature on this topic have been published [@hassler_intergroup_2021; @macinnis_extending_2019; @mckeown_contact_2017], we present the first systematic review and meta-analysis of the relationship between intergroup contact and support for social change in disadvantaged groups.
-To test the hypothesized 'ironic' effects of intergroup contact, we evaluate the evidence that contact with advantaged-group members reduces disadvantaged-group members' perceived injustice, discourages them from engaging in collective action, and diminishes their support for reparative policies.
+To test the hypothesized 'ironic' effects of intergroup contact, we evaluate the evidence that contact with advantaged-group members reduces disadvantaged-group members' perceived injustice, collective action, and support for reparative policies.
 
@@
 Of all samples, `r with(distinct(dl, id, sample, study_intention), f_prop2percent(mean(study_intention == "Yes"), digits = 0))` (`r glue('$I = {f_comma(with(distinct(dl, id, sample, n, study_intention), length(sample[study_intention == "Yes"])))}$')`) were collected with the intention to examine the effects of intergroup contact on the outcomes considered in this meta-analysis.
-Many studies instead examined acculturation processes [@berry_immigration_1997] and measured intergroup contact and perceived injustice without hypothesizing that the former would influence the latter.
+Many studies instead examined acculturation processes [@berry_immigration_1997] and measured intergroup contact and perceived injustice without hypothesizing that the former would affect the latter.
 Together, these observations highlight both limitations and strengths of the empirical literature.
@@
 There is an emerging consensus that intergroup contact has the 'ironic' effect of undermining support for social change in disadvantaged groups.
-We conducted a preregistered meta-analytic test of this effect across 96 studies with 137 samples of 211,360 disadvantaged-group members.
+We conducted a preregistered meta-analytic test of this effect across `r with(dplyr::distinct(readRDS("../data/dl.rds"), sample, id, n), numform::f_comma(dplyr::n_distinct(id)))` studies with `r with(dplyr::distinct(readRDS("../data/dl.rds"), sample, id, n), numform::f_comma(length(sample)))` samples of `r with(dplyr::distinct(readRDS("../data/dl.rds"), sample, id, n), numform::f_comma(sum(n)))` disadvantaged-group members.
 We found that, based on the available evidence, the associations of intergroup contact with perceived injustice (`r with(summary, p_text[y_var == "pi"])`), collective action (`r with(summary, p_text[y_var == "ca"])`), and support for reparative policies (`r with(summary, p_text[y_var == "ps"])`) were, on average, much more likely to be negative than positive.
@@
 That said, 61% of samples were either not collected with the intention to study the effects of intergroup contact on a relevant outcome (45%) or from unpublished studies (32%)—and thus unlikely to have been affected by publication bias.
-Another bias that could have affected our findings is that researchers made data-dependent decisions when analyzing data that inflate false-positive findings [@gelman_statistical_2014].
-Future research should use preregistration and other methods to prevent undisclosed flexibility in data collection and analysis.^[Only one preregistered study has been published [@3054].]
+Another bias that could have affected our findings is that researchers made data-dependent decisions while collecting and analyzing data that are known to inflate false-positive findings [@gelman_statistical_2014; @simmons_false-positive_2011].
+This risk is pertinent to a literature in which most studies are observational, include many measures, and are not preregistered—and, therefore, do not constrain the direction of observed associations or the selection of included variables.^[To date, only one preregistered study has been published [@3054].] Future research should use preregistration and other methods to prevent undisclosed flexibility in data collection and analysis.
+
+Our research was motivated by the broader question whether intergroup contact helps or hinders social change.
+By examining the narrower question whether intergroup contact diminishes support for social change in disadvantaged groups, we tested the most prominent hypotheses explaining how intergroup contact might *hinder* social change.
+We did not consider whether intergroup contact might also *help* social change by reducing prejudice [for critical perspectives, see @dixon_beyond_2012; @jackman_velvet_1994] or by motivating the advantaged to acknowledge and challenge social inequality [@tropp_making_2018].
+Further, we did not consider contact between different disadvantaged groups, which has been found to increase support for social change among the disadvantaged [@dixon_divide_2015; @93].
+Therefore, this meta-analysis could not provide a complete answer to the question whether, on balance, intergroup contact helps or hinders social change.
 
 To conclude, our preregistered meta-analysis found some evidence that intergroup contact reduces perceived injustice, discourages collective action, and diminishes support for reparative policies in disadvantaged groups—but also showed that the estimated effect sizes were small, variable, and consistent with alternative explanations.
-Our research was motivated by the broader question whether intergroup contact helps or hinders social change.
-By examining the narrower question whether intergroup contact diminishes support for social change in disadvantaged groups, we tested the most prominent hypothesis explaining how intergroup contact might *hinder* social change.
-We did not consider whether intergroup contact might *help* social change by reducing prejudice [for a critical perspective, see @dixon_beyond_2012] or by motivating advantaged-group members to acknowledge and challenge social inequality [@tropp_making_2018].
-Still, we hope that our meta-analytic review motivates researchers to address the open questions about how intergroup contact relates to support for social change in disadvantaged groups.
+Future research should (1) compare the direction and magnitude of the associations between intergroup contact and support for social change across cultures, groups, and issues to explain variance in these associations; (2) use longitudinal designs and field experiments to establish the direction of these relationships and to rule out spurious associations; (3) include measures that allow testing alternative explanations for the  apparent 'ironic' effects of intergroup contact; and (4) incorporate practices to prevent undisclosed flexibility in data collection and analysis.
+We hope that our meta-analysis helps researchers to address the open questions about how intergroup contact relates to support for social change in disadvantaged groups.
 
-# References
+\refsection
 

### 2021-06-16 manuscript/manuscript.tex
revise discussion

@@
 \titleformat*{\subsubsection}{\raggedright\normalfont\normalsize\bfseries\itshape}
+\newcommand{\refsection}{\newpage \section{References}}
 \usepackage{indentfirst}
 \usepackage[hang,flushmargin]{footmisc}
+\providecommand{\tightlist}{\setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
 
@@
 
+% Frontmatter
+\title{ Meta-Analysis of the `Ironic' Effects of Intergroup Contact }
+
 \begin{document}
+
+% \maketitle
+% 
+% \newpage
 
@@
 intergroup contact directly and were strongest in studies that examined
-short-term migration or (post-)colonial intergroup relations. We found
-evidence for an alternative explanation for the apparent `ironic'
+short-term migration or (post-)colonial intergroup relations. We also
+found evidence for an alternative explanation for the apparent `ironic'
 effects of intergroup contact as, after controlling for the positive
 association of negative contact with support for social change, positive
-contact was not associated with any of the outcomes. We close by
+contact was no longer associated with any of the outcomes. We close by
 discussing strengths and limitations of the available evidence and by
 highlighting open questions about the relationship between intergroup
-contact and social change in disadvantaged groups.
+contact and support for social change in disadvantaged groups.
 
@@
 contact with advantaged-group members reduces disadvantaged-group
-members' perceived injustice, discourages them from engaging in
-collective action, and diminishes their support for reparative policies.
+members' perceived injustice, collective action, and support for
+reparative policies.
 
@@
 processes (Berry, 1997) and measured intergroup contact and perceived
-injustice without hypothesizing that the former would influence the
-latter. Together, these observations highlight both limitations and
-strengths of the empirical literature.
+injustice without hypothesizing that the former would affect the latter.
+Together, these observations highlight both limitations and strengths of
+the empirical literature.
 
@@
 effect of undermining support for social change in disadvantaged groups.
-We conducted a preregistered meta-analytic test of this effect across 96
-studies with 137 samples of 211,360 disadvantaged-group members. We
+We conducted a preregistered meta-analytic test of this effect across 98
+studies with 140 samples of 213,085 disadvantaged-group members. We
 found that, based on the available evidence, the associations of
@@
 could have affected our findings is that researchers made data-dependent
-decisions when analyzing data that inflate false-positive findings
-(Gelman \& Loken, 2014). Future research should use preregistration and
-other methods to prevent undisclosed flexibility in data collection and
-analysis.\footnote{Only one preregistered study has been published
-  (Hässler et al., 2020).}
+decisions while collecting and analyzing data that are known to inflate
+false-positive findings (Gelman \& Loken, 2014; Simmons et al., 2011).
+This risk is pertinent to a literature in which most studies are
+observational, include many measures, and are not preregistered---and,
+therefore, do not constrain the direction of observed associations or
+the selection of included variables.\footnote{To date, only one
+  preregistered study has been published (Hässler et al., 2020).} Future
+research should use preregistration and other methods to prevent
+undisclosed flexibility in data collection and analysis.
+
+Our research was motivated by the broader question whether intergroup
+contact helps or hinders social change. By examining the narrower
+question whether intergroup contact diminishes support for social change
+in disadvantaged groups, we tested the most prominent hypotheses
+explaining how intergroup contact might \emph{hinder} social change. We
+did not consider whether intergroup contact might also \emph{help}
+social change by reducing prejudice (for critical perspectives, see
+Dixon et al., 2012; Jackman, 1994) or by motivating the advantaged to
+acknowledge and challenge social inequality (Tropp \& Barlow, 2018).
+Further, we did not consider contact between different disadvantaged
+groups, which has been found to increase support for social change among
+the disadvantaged (Dixon et al., 2015, 2017). Therefore, this
+meta-analysis could not provide a complete answer to the question
+whether, on balance, intergroup contact helps or hinders social change.
 
@@
 groups---but also showed that the estimated effect sizes were small,
-variable, and consistent with alternative explanations. Our research was
-motivated by the broader question whether intergroup contact helps or
-hinders social change. By examining the narrower question whether
-intergroup contact diminishes support for social change in disadvantaged
-groups, we tested the most prominent hypothesis explaining how
-intergroup contact might \emph{hinder} social change. We did not
-consider whether intergroup contact might \emph{help} social change by
-reducing prejudice (for a critical perspective, see Dixon et al., 2012)
-or by motivating advantaged-group members to acknowledge and challenge
-social inequality (Tropp \& Barlow, 2018). Still, we hope that our
-meta-analytic review motivates researchers to address the open questions
-about how intergroup contact relates to support for social change in
-disadvantaged groups.
-
-\hypertarget{references}{%
-\section{References}\label{references}}
+variable, and consistent with alternative explanations. Future research
+should (1) compare the direction and magnitude of the associations
+between intergroup contact and support for social change across
+cultures, groups, and issues to explain variance in these associations;
+(2) use longitudinal designs and field experiments to establish the
+direction of these relationships and to rule out spurious associations;
+(3) include measures that allow testing alternative explanations for the
+apparent `ironic' effects of intergroup contact; and (4) incorporate
+practices to prevent undisclosed flexibility in data collection and
+analysis. We hope that our meta-analysis helps researchers to address
+the open questions about how intergroup contact relates to support for
+social change in disadvantaged groups.
+
+\refsection
 
@@
 83--95. \url{https://doi.org/10.1002/casp.2296}
+
+\leavevmode\hypertarget{ref-dixon_divide_2015}{}%
+Dixon, J., Durrheim, K., Thomae, M., Tredoux, C., Kerr, P., \& Quayle,
+M. (2015). Divide and rule, unite and resist: Contact, collective action
+and policy attitudes among historically disadvantaged groups.
+\emph{Journal of Social Issues}, \emph{71}(3), 576--596.
+\url{https://doi.org/10.1111/josi.12129}
 
@@
 
+\leavevmode\hypertarget{ref-jackman_velvet_1994}{}%
+Jackman, M. R. (1994). \emph{The velvet glove: Paternalism and conflict
+in gender, class, and race relations}. University of California Press.
+
 \leavevmode\hypertarget{ref-2341}{}%
@@
 
+\leavevmode\hypertarget{ref-simmons_false-positive_2011}{}%
+Simmons, J. P., Nelson, L. D., \& Simonsohn, U. (2011). False-positive
+psychology: Undisclosed flexibility in data collection and analysis
+allows presenting anything as significant. \emph{Psychological Science},
+\emph{22}(11), 1359--1366.
+\url{https://doi.org/10.1177/0956797611417632}
+
 \leavevmode\hypertarget{ref-3060}{}%

### 2021-06-18 manuscript/manuscript.Rmd
submit

@@
     template: apa-template.tex
-  word_document:
-    reference_docx: word-template.docx
 ---
@@
 
-Researchers have, however, argued that intergroup contact might *not* reduce support for social change and, in some circumstances, might even *increase* support for social change in disadvantaged groups.
+Others have, however, argued that intergroup contact might *not* reduce support for social change and, in some circumstances, might even *increase* support for social change in disadvantaged groups.
 
@@
 Whereas previous studies had focused on positive contact experiences, recent studies considered both positive and negative contact experiences as predictors of support for social change.
-Researchers [@2309; @956] found negative contact with advantaged-group members to be associated with greater perceived discrimination and stronger collective action intentions, suggesting that negative contact experiences motivate disadvantaged-group members to support social change.
+These studies [@2309; @956] found negative contact with advantaged-group members to be associated with greater perceived discrimination and stronger collective action intentions.
+This research suggests that negative contact can motivate disadvantaged-group members to support social change.
 @956 further found that, first, disadvantaged-group members who have more positive contact also tend to have less negative contact and, second, positive contact is not associated with perceived discrimination or collective action after controlling for negative contact.
@@
 Whereas most studies focused on contact with the advantaged outgroup, some studies examined contact with the disadvantaged ingroup as a predictor of support for social change.
-@sengupta_ingroup_2015 found ingroup contact to be associated with decreased endorsement of system-justifying beliefs and increased support for reparative policies benefiting the disadvantaged ingroup, suggesting that contact with other ingroup members can motivate disadvantaged-group members to support social change [see also @1695].
+@levin_ethnic_2006 found that, among minority-group college students, ingroup friendship predicted perceived discrimination 1–2 years later.
+@sengupta_ingroup_2015 found ingroup contact to be associated with decreased endorsement of system-justifying beliefs and increased support for reparative policies benefiting the disadvantaged ingroup [see also @1695].
+These studies suggest that contact with other ingroup members can motivate disadvantaged-group members to support social change.
 As outgroup contact places limits on how much ingroup contact a person can have [@pfister_contact_2020], disadvantaged-group members who have more outgroup contact can be expected to have less ingroup contact.
@@
 
-We ran three random-effects meta-analysis models that estimated the partial correlations of ingroup and outgroup contact with each outcomes, using effect sizes from all studies that measured both predictors (Figure 8b).
+We ran three random-effects meta-analysis models that estimated the partial correlations of ingroup and outgroup contact with each outcome, using effect sizes from all studies that measured both predictors (Figure 8b).
 Across `r alt_results$N[alt_results$x_var == "ig" & alt_results$y_var == "pi"]` participants from `r alt_results$I[alt_results$x_var == "ig" & alt_results$y_var == "pi"]` samples in `r alt_results$J[alt_results$x_var == "ig" & alt_results$y_var == "pi"]` studies, we found insufficient evidence for associations of ingroup contact (`r alt_results$text[alt_results$x_var == "ig" & alt_results$y_var == "pi"]`) and outgroup contact (`r alt_results$text[alt_results$x_var == "og" & alt_results$y_var == "pi"]`) with perceived injustice.
@@
 To conclude, our preregistered meta-analysis found some evidence that intergroup contact reduces perceived injustice, discourages collective action, and diminishes support for reparative policies in disadvantaged groups—but also showed that the estimated effect sizes were small, variable, and consistent with alternative explanations.
-Future research should (1) compare the direction and magnitude of the associations between intergroup contact and support for social change across cultures, groups, and issues to explain variance in these associations; (2) use longitudinal designs and field experiments to establish the direction of these relationships and to rule out spurious associations; (3) include measures that allow testing alternative explanations for the  apparent 'ironic' effects of intergroup contact; and (4) incorporate practices to prevent undisclosed flexibility in data collection and analysis.
+Future research should (1) compare the direction and magnitude of the associations between intergroup contact and support for social change across cultures, groups, and issues; (2) use longitudinal designs and field experiments to establish the direction of these relationships and to rule out spurious associations; (3) include measures that allow testing alternative explanations for the apparent 'ironic' effects of intergroup contact; and (4) incorporate practices to prevent undisclosed flexibility in data collection and analysis.
 We hope that our meta-analysis helps researchers to address the open questions about how intergroup contact relates to support for social change in disadvantaged groups.
@@
 
-\noindent References marked with an asterisk are studies included in the meta-analysis.
+References marked with an asterisk are studies included in the meta-analysis.
 

### 2021-06-18 manuscript/manuscript.tex
submit

@@
 \begin{document}
-
-% \maketitle
-% 
-% \newpage
 
@@
 
-Researchers have, however, argued that intergroup contact might
-\emph{not} reduce support for social change and, in some circumstances,
-might even \emph{increase} support for social change in disadvantaged
-groups.
+Others have, however, argued that intergroup contact might \emph{not}
+reduce support for social change and, in some circumstances, might even
+\emph{increase} support for social change in disadvantaged groups.
 
@@
 considered both positive and negative contact experiences as predictors
-of support for social change. Researchers (Hayward et al., 2018; Reimer
-et al., 2017) found negative contact with advantaged-group members to be
-associated with greater perceived discrimination and stronger collective
-action intentions, suggesting that negative contact experiences motivate
-disadvantaged-group members to support social change. Reimer et al.
-(2017) further found that, first, disadvantaged-group members who have
-more positive contact also tend to have less negative contact and,
-second, positive contact is not associated with perceived discrimination
-or collective action after controlling for negative contact. Based on
-these findings, Reimer et al. (2017) argued that the mobilizing effect
-of negative contact could be an alternative explanation for the negative
-relationship between positive contact and support for social change
-observed in prior studies.
+of support for social change. These studies (Hayward et al., 2018;
+Reimer et al., 2017) found negative contact with advantaged-group
+members to be associated with greater perceived discrimination and
+stronger collective action intentions. This research suggests that
+negative contact can motivate disadvantaged-group members to support
+social change. Reimer et al. (2017) further found that, first,
+disadvantaged-group members who have more positive contact also tend to
+have less negative contact and, second, positive contact is not
+associated with perceived discrimination or collective action after
+controlling for negative contact. Based on these findings, Reimer et al.
+(2017) argued that the mobilizing effect of negative contact could be an
+alternative explanation for the negative relationship between positive
+contact and support for social change observed in prior studies.
 
@@
 contact with the disadvantaged ingroup as a predictor of support for
-social change. Sengupta et al. (2015) found ingroup contact to be
+social change. Levin et al. (2006) found that, among minority-group
+college students, ingroup friendship predicted perceived discrimination
+1--2 years later. Sengupta et al. (2015) found ingroup contact to be
 associated with decreased endorsement of system-justifying beliefs and
 increased support for reparative policies benefiting the disadvantaged
-ingroup, suggesting that contact with other ingroup members can motivate
-disadvantaged-group members to support social change (see also Sengupta
-\& Sibley, 2013). As outgroup contact places limits on how much ingroup
-contact a person can have (Pfister et al., 2020), disadvantaged-group
-members who have more outgroup contact can be expected to have less
-ingroup contact. Based on these observations, one might argue that the
-mobilizing effect of ingroup contact could be an alternative explanation
-for the negative association between outgroup contact and support for
-social change observed in prior studies.
+ingroup (see also Sengupta \& Sibley, 2013). These studies suggest that
+contact with other ingroup members can motivate disadvantaged-group
+members to support social change. As outgroup contact places limits on
+how much ingroup contact a person can have (Pfister et al., 2020),
+disadvantaged-group members who have more outgroup contact can be
+expected to have less ingroup contact. Based on these observations, one
+might argue that the mobilizing effect of ingroup contact could be an
+alternative explanation for the negative association between outgroup
+contact and support for social change observed in prior studies.
 
@@
 We ran three random-effects meta-analysis models that estimated the
-partial correlations of ingroup and outgroup contact with each outcomes,
+partial correlations of ingroup and outgroup contact with each outcome,
 using effect sizes from all studies that measured both predictors
@@
 between intergroup contact and support for social change across
-cultures, groups, and issues to explain variance in these associations;
-(2) use longitudinal designs and field experiments to establish the
-direction of these relationships and to rule out spurious associations;
-(3) include measures that allow testing alternative explanations for the
-apparent `ironic' effects of intergroup contact; and (4) incorporate
-practices to prevent undisclosed flexibility in data collection and
-analysis. We hope that our meta-analysis helps researchers to address
-the open questions about how intergroup contact relates to support for
-social change in disadvantaged groups.
+cultures, groups, and issues; (2) use longitudinal designs and field
+experiments to establish the direction of these relationships and to
+rule out spurious associations; (3) include measures that allow testing
+alternative explanations for the apparent `ironic' effects of intergroup
+contact; and (4) incorporate practices to prevent undisclosed
+flexibility in data collection and analysis. We hope that our
+meta-analysis helps researchers to address the open questions about how
+intergroup contact relates to support for social change in disadvantaged
+groups.
 
@@
 
-\noindent References marked with an asterisk are studies included in the
+References marked with an asterisk are studies included in the
 meta-analysis.
@@
 
+\leavevmode\hypertarget{ref-levin_ethnic_2006}{}%
+Levin, S., Van Laar, C., \& Foote, W. (2006). Ethnic segregation and
+perceived discrimination in college: Mutual influences and effects on
+social and academic life. \emph{Journal of Applied Social Psychology},
+\emph{36}(6), 1471--1501.
+\url{https://doi.org/10.1111/j.0021-9029.2006.00068.x}
+
 \leavevmode\hypertarget{ref-li_meta-cart_2017}{}%

### 2021-12-13 manuscript/manuscript.tex
start revision

@@
-\documentclass[12pt, letterpaper]{article}
+\documentclass[twocolumn, 11pt, letterpaper]{article}
 
@@
 \usepackage[utf8]{inputenc}
-\usepackage{amsmath}
+\usepackage{MinionPro} 
+\input{glyphtounicode}
+\pdfgentounicode=1 
 \usepackage{microtype}
@@
 \usepackage[letterpaper, margin = 1in]{geometry}
+\setlength{\columnsep}{18pt}
 \setcounter{secnumdepth}{0}
-\setlength{\parindent}{0.5in}
 \usepackage[compact]{titlesec}  
-\titleformat*{\section}{\centering\normalfont\normalsize\bfseries}
-\titleformat*{\subsection}{\raggedright\normalfont\normalsize\bfseries}
-\titleformat*{\subsubsection}{\raggedright\normalfont\normalsize\bfseries\itshape}
-\newcommand{\refsection}{\newpage \section{References}}
-\usepackage{indentfirst}
-\usepackage[hang,flushmargin]{footmisc}
+\titleformat*{\section}{\centering\normalfont\Large\bfseries}
+\usepackage{authblk}
+\renewcommand\Affilfont{\small}
+\newcommand{\refsection}{\section{References}}
 \providecommand{\tightlist}{\setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
-
-% Header
-\usepackage{fancyhdr}
-\pagestyle{fancy}
-\fancyhf{}
-\setlength{\headheight}{14.5pt}
-\renewcommand{\headrulewidth}{0pt}
-\fancyhead[L]{`IRONIC' EFFECTS META-ANALYSIS}
-\fancyhead[R]{\thepage}
 
@@
 
-% Line spacing
-\usepackage[doublespacing]{setspace}
+% References
+\newlength{\cslhangindent}
+\setlength{\cslhangindent}{1.5em}
+\newenvironment{CSLReferences}%
+  {}%
+  {\par}
 
 % Frontmatter
-\title{ Meta-Analysis of the `Ironic' Effects of Intergroup Contact }
+\title{ Meta-Analysis of the `Ironic' Effects of Intergroup
+Contact\thanks{} }
+\author[1]{Nils K. Reimer}
+\author[2]{Nikhil K. Sengupta}
+\affil[1]{University of Southern California, Los Angeles, United States}
+\affil[2]{University of Kent, Canterbury, United Kingdom}
+\date{June 15, 2021}
 
@@
 
-\section{Abstract}
-
-\noindent Growing evidence suggests that intergroup contact, psychology's
-most-researched paradigm for reducing prejudice, has the `ironic' effect
-of reducing support for social change in disadvantaged groups. We
-conducted a preregistered meta-analytic test of this effect across 98
-studies with 140 samples of 213,085 disadvantaged-group members. As
-predicted, intergroup contact was, on average, associated with less
-perceived injustice (\(r = -.07\)), collective action (\(r = -.06\)),
-and support for reparative policies (\(r = -.07\)). However, these
-associations were small, variable, and consistent with alternative
-explanations. Across outcomes, 25--36\% of studies found \emph{positive}
-associations with intergroup contact. Moderator analyses explained about
-a third of the between-sample variance, showing that, on average,
-associations were negative only in studies of adults that measured
-intergroup contact directly and were strongest in studies that examined
-short-term migration or (post-)colonial intergroup relations. We also
-found evidence for an alternative explanation for the apparent `ironic'
-effects of intergroup contact as, after controlling for the positive
-association of negative contact with support for social change, positive
-contact was no longer associated with any of the outcomes. We close by
-discussing strengths and limitations of the available evidence and by
-highlighting open questions about the relationship between intergroup
-contact and support for social change in disadvantaged groups.
-
-\textit{Keywords:} intergroup contact, meta-analysis, perceived discrimination, collective
-action, policy support
-
-\newpage
-
-\section{Meta-Analysis of the `Ironic' Effects of Intergroup Contact}
-
-It is ironic that psychology's most-researched paradigm for reducing
-prejudice---intergroup contact---should hinder, rather than help, social
-change. Hundreds of studies have confirmed that intergroup contact is
-associated with less negative feelings toward outgroup members (for a
-meta-analysis, see Pettigrew \& Tropp, 2006). Most of these studies have
-focused on advantaged-group members' contact experiences with
-disadvantaged-group members (Tropp \& Pettigrew, 2005), guided by the
-idea that reducing advantaged-group members' prejudice will prevent
-interpersonal discrimination. Reducing prejudice, however, is rarely
-enough to overcome institutional and structural discrimination. Instead,
-as the 2020 Black Lives Matter protests have shown, social change often
-requires political mobilization by the disadvantaged. Critics have
-argued that, by fostering harmony and reducing conflict, intergroup
-contact might distract disadvantaged-group members from the injustice
-they face and, thereby, undermine their motivation for social change
-(Dixon et al., 2005; Reicher, 2007; Wright, 2003). By reducing
-disadvantaged-group members' opposition to injustice, intergroup contact
-might thus have the `ironic' (Saguy et al., 2009), `sedative' (Çakal et
-al., 2011), or `paradoxical' (Dixon et al., 2010) effect of hindering
-social change.
+\twocolumn[
+  \begin{@twocolumnfalse}
+    \maketitle
+    \begin{abstract}
+      \noindent Growing evidence suggests that intergroup contact,
+psychology's most-researched paradigm for reducing prejudice, has the
+`ironic' effect of reducing support for social change in disadvantaged
+groups. We conducted a preregistered meta-analytic test of this effect
+across 98 studies with 140 samples of 213,085 disadvantaged-group
+members. As predicted, intergroup contact was, on average, associated
+with less perceived injustice (\(r = -.07\)), collective action
+(\(r = -.06\)), and support for reparative policies (\(r = -.07\)).
+However, these associations were small, variable, and consistent with
+alternative explanations. Across outcomes, 25--36\% of studies found
+\emph{positive} associations with intergroup contact. Moderator analyses
+explained about a third of the between-sample variance, showing that, on
+average, associations were negative only in studies of adults that
+measured intergroup contact directly and were strongest in studies that
+examined short-term migration or (post-)colonial intergroup relations.
+We also found evidence for an alternative explanation for the apparent
+`ironic' effects of intergroup contact as, after controlling for the
+positive association of negative contact with support for social change,
+positive contact was no longer associated with any of the outcomes. We
+close by discussing strengths and limitations of the available evidence
+and by highlighting open questions about the relationship between
+intergroup contact and support for social change in disadvantaged
+groups.
+    \end{abstract}
+  \end{@twocolumnfalse}
+  % \renewcommand{\abstractname}{Statement of Relevance}
+  % \begin{@twocolumnfalse}
+  %   \maketitle
+  %   \begin{abstract}
+  %   \noindent 
+  %   \end{abstract}
+  % \end{@twocolumnfalse}
+]
+
+{
+  \renewcommand{\thefootnote}%
+    {\fnsymbol{footnote}}
+  \footnotetext[1]{Manuscript under review.}
+}
+
+\noindent It is ironic that psychology's most-researched paradigm for
+reducing prejudice---intergroup contact---should hinder, rather than
+help, social change. Hundreds of studies have confirmed that intergroup
+contact is associated with less negative feelings toward outgroup
+members (for a meta-analysis, see Pettigrew \& Tropp, 2006). Most of
+these studies have focused on advantaged-group members' contact
+experiences with disadvantaged-group members (L. R. Tropp \& Pettigrew,
+2005), guided by the idea that reducing advantaged-group members'
+prejudice will prevent interpersonal discrimination. Reducing prejudice,
+however, is rarely enough to overcome institutional and structural
+discrimination. Instead, as the 2020 Black Lives Matter protests have
+shown, social change often requires political mobilization by the
+disadvantaged. Critics have argued that, by fostering harmony and
+reducing conflict, intergroup contact might distract disadvantaged-group
+members from the injustice they face and, thereby, undermine their
+motivation for social change (Dixon et al., 2005; Reicher, 2007; Wright,
+2003). By reducing disadvantaged-group members' opposition to injustice,
+intergroup contact might thus have the `ironic' (Saguy et al., 2009),
+`sedative' (Çakal et al., 2011), or `paradoxical' (Dixon et al., 2010)
+effect of hindering social change.
 
@@
 discourage disadvantaged-group members from engaging in collective
-action by diminishing their perceived discrimination (Tropp et al.,
-2012), by blurring boundaries between the disadvantaged ingroup and the
-advantaged outgroup (Saguy et al., 2009), by reducing negative attitudes
-toward the advantaged outgroup (Wright \& Lubensky, 2009), and by
-quelling their anger (Hayward et al., 2018; Tausch et al., 2015). To the
-extent that it discourages collective action, intergroup contact reduces
-support for social change.
+action by diminishing their perceived discrimination (Linda R. Tropp et
+al., 2012), by blurring boundaries between the disadvantaged ingroup and
+the advantaged outgroup (Saguy et al., 2009), by reducing negative
+attitudes toward the advantaged outgroup (Wright \& Lubensky, 2009), and
+by quelling their anger (Hayward et al., 2018; Tausch et al., 2015). To
+the extent that it discourages collective action, intergroup contact
+reduces support for social change.
 
@@
 or whether it was a relevant review article. We kept all records coded
-as ``yes'' or ``maybe''. Second, both authors reviewed each of the
+as ``yes'' or ``maybe.'' Second, both authors reviewed each of the
 full-text manuscripts from the previous stage and coded whether any
@@
 (Stanley \& Doucouliagos, 2014); the three-parameter selection model
-(3PSM; Vevea \& Hedges, 1995); and the \emph{p}-uniform* estimator (van
-Aert \& Assen, 2018). In addition, we ran a subgroup analysis that
+{[}3PSM; Vevea \& Hedges (1995){]}; and the \emph{p}-uniform* estimator
+(van Aert \& Assen, 2018). In addition, we ran a subgroup analysis that
 included only studies that were not published or not conducted with the
@@
 thus much smaller than for the association between contact and prejudice
-in minority (\(r = -.18\)) and majority (\(r = -.23\)) groups (Tropp \&
-Pettigrew, 2005).\footnote{Comparing standardized effect sizes assumes
-  that the two outcomes are of equal importance. That is not always the
-  case: for example, a drug that reduces mild symptoms by 0.20 standard
-  deviations is not better than a drug that reduces deaths by 0.10
-  standard deviations.} Small effects can still be important if they
-accumulate over time or across people. For example, even a small change
-in policy attitudes could, if it affects enough people, sway a tight
-election. Cumulative effects, however, should not be assumed without an
-empirical or theoretical rationale (Funder \& Ozer, 2019).
+in minority (\(r = -.18\)) and majority (\(r = -.23\)) groups (L. R.
+Tropp \& Pettigrew, 2005).\footnote{Comparing standardized effect sizes
+  assumes that the two outcomes are of equal importance. That is not
+  always the case: for example, a drug that reduces mild symptoms by
+  0.20 standard deviations is not better than a drug that reduces deaths
+  by 0.10 standard deviations.} Small effects can still be important if
+they accumulate over time or across people. For example, even a small
+change in policy attitudes could, if it affects enough people, sway a
+tight election. Cumulative effects, however, should not be assumed
+without an empirical or theoretical rationale (Funder \& Ozer, 2019).
 
@@
   three longitudinal studies (Koschate et al., 2012; Reimer et al.,
-  2017; Tropp et al., 2012), all of which conflated within-person change
-  and between-person stability (Hamaker et al., 2015), two experimental
-  studies with a no-contact control condition (Becker et al., 2013;
-  Droogendyk et al., 2016), and two intervention studies (Reimer et al.,
-  2021; Shani \& Boehnke, 2017).}
+  2017; Linda R. Tropp et al., 2012), all of which conflated
+  within-person change and between-person stability (Hamaker et al.,
+  2015), two experimental studies with a no-contact control condition
+  (Becker et al., 2013; Droogendyk et al., 2016), and two intervention
+  studies (Reimer et al., 2021; Shani \& Boehnke, 2017).}
 
@@
 Dixon et al., 2012; Jackman, 1994) or by motivating the advantaged to
-acknowledge and challenge social inequality (Tropp \& Barlow, 2018).
-Further, we did not consider contact between different disadvantaged
-groups, which has been found to increase support for social change among
-the disadvantaged (Dixon et al., 2015, 2017). Therefore, this
-meta-analysis could not provide a complete answer to the question
-whether, on balance, intergroup contact helps or hinders social change.
+acknowledge and challenge social inequality (Linda R. Tropp \& Barlow,
+2018). Further, we did not consider contact between different
+disadvantaged groups, which has been found to increase support for
+social change among the disadvantaged (Dixon et al., 2015, 2017).
+Therefore, this meta-analysis could not provide a complete answer to the
+question whether, on balance, intergroup contact helps or hinders social
+change.
 
@@
 \hypertarget{refs}{}
+\begin{CSLReferences}{1}{0}
 \leavevmode\hypertarget{ref-3201}{}%
 *Albzour, M., Penic, S., Nasser, R., \& Green, E. G. T. (2019). Support
-for ``normalization'' of relations between Palestinians and Israelis,
-and how it relates to contact and resistance in the West Bank.
-\emph{Journal of Social and Political Psychology}, \emph{7}(2),
+for {`normalization'} of relations between {Palestinians} and
+{Israelis}, and how it relates to contact and resistance in the {West}
+{Bank}. \emph{Journal of Social and Political Psychology}, \emph{7}(2),
 978--996. \url{https://doi.org/10.5964/jspp.v7i2.877}
@@
 *Bagci, S. C. (2014). \emph{Cross-ethnic friendships in multiethnic
-educational settings: Consequences for psychological, academic and
+educational settings: {Consequences} for psychological, academic and
 motivational outcomes among young adolescents} {[}Doctoral dissertation,
-Goldsmiths, University of London{]}.
+\{Goldsmiths, University of London\}{]}.
 \url{https://doi.org/10.25602/GOLD.00011030}
@@
 identification as mediators between identity threat and psychological
-well-being and intergroup bias} {[}Manuscript in preparation{]}. Faculty
-of Arts and Social Sciences, Sabanci University.
+well-being and intergroup bias} {[}Manuscript in preparation{]}.
+{Faculty of Arts and Social Sciences, Sabanci University}.
 
@@
 *Bagci, S. C., Stathi, S., \& Piyale, Z. E. (2019). Imagined contact
-facilitates acculturation, sometimes: Contradicting evidence from two
+facilitates acculturation, sometimes: {Contradicting} evidence from two
 sociocultural contexts. \emph{Cultural Diversity and Ethnic Minority
@@
 *Bagci, S. C., \& Turnuklu, A. (2019). Intended, unintended, and unknown
-consequences of contact: The role of positive-negative contact on
+consequences of contact: {The} role of positive-negative contact on
 outgroup attitudes, collective action tendencies, and psychological
@@
 *Bagci, S. C., Turnuklu, A., \& Bekmezci, E. (2018a). Cross-group
-friendships and psychological well-being: A dual pathway through social
-integration and empowerment. \emph{British Journal of Social
+friendships and psychological well-being: {A} dual pathway through
+social integration and empowerment. \emph{British Journal of Social
 Psychology}, \emph{57}(4), 773--792.
@@
 Links to psychological well-being through threatened social identity
-needs. \emph{European Journal of Social Psychology}, \emph{50}(7),
+needs. \emph{European Journal of Social Psychology}, \emph{50},
 1463--1477. \url{https://doi.org/10.1002/ejsp.2699}
@@
 *Becker, J. C., Wright, S. C., Lubensky, M. E., \& Zhou, S. (2013).
-Friend or ally: Whether cross-group contact undermines collective action
-depends on what advantaged group members say (or don't say).
+Friend or ally: {Whether} cross-group contact undermines collective
+action depends on what advantaged group members say (or don't say).
 \emph{Personality and Social Psychology Bulletin}, \emph{39}(4),
@@
 \leavevmode\hypertarget{ref-2397}{}%
-*Bond, J., \& Dixon, J. (2020). \emph{White and Black UK residents'
-support for collective action for the removal of public symbols
-associated with historical racism in England} {[}Unpublished dataset{]}.
-The Open University.
+*Bond, J., \& Dixon, J. (2020). \emph{{White} and {Black} {UK}
+residents' support for collective action for the removal of public
+symbols associated with historical racism in {England}} {[}Unpublished
+dataset{]}. The Open University.
 
@@
 *Bracegirdle, C. (2020). \emph{Social network study of two diverse
-schools in Northern England} {[}Unpublished dataset{]}. University of
+schools in {Northern England}} {[}Unpublished dataset{]}. University of
 Oxford.
@@
 
-\leavevmode\hypertarget{ref-480}{}%
-*Castro, V. S. (2005). Discriminación percibida y autoestima en jóvenes
-de grupos minoritarios y mayoritarios en Costa Rica {[}Perceived
-discrimination and self-esteem among ethnic majority and minority youths
-in Costa Rica{]}. \emph{Revista Interamericana de Psicología},
-\emph{39}(1), 93--106.
-
 \leavevmode\hypertarget{ref-1914}{}%
@@
 adaptación sociocultural de estudiantes universitarios extranjeros en
-Argentina {[}Predictors of socio-cultural adaptation of foreign
-university students in Argentina{]}. \emph{Interdisciplinaria},
+{Argentina} {[}{Predictors} of socio-cultural adaptation of foreign
+university students in {Argentina}{]}. \emph{Interdisciplinaria},
 \emph{30}(2), 265--281.
+
+\leavevmode\hypertarget{ref-480}{}%
+*Castro, V. S. (2005). Discriminación percibida y autoestima en jóvenes
+de grupos minoritarios y mayoritarios en {Costa} {Rica} {[}{Perceived}
+discrimination and self-esteem among ethnic majority and minority youths
+in {Costa} {Rica}{]}. \emph{Revista Interamericana de Psicología},
+\emph{39}(1), 93--106.
 
@@
 *Cernat, V. (2019). Interminority contact and solidarity under conflict:
-Evidence from the Hungarian and Roma minorities in Romania. \emph{Basic
-and Applied Social Psychology}, \emph{41}(5), 326--339.
+{Evidence} from the {Hungarian} and {Roma} minorities in {Romania}.
+\emph{Basic and Applied Social Psychology}, \emph{41}(5), 326--339.
 \url{https://doi.org/10.1080/01973533.2019.1652179}
@@
 \leavevmode\hypertarget{ref-91}{}%
-*Chang, T. K. (2017). \emph{Psychological distress of Asian
+*Chang, T. K. (2017). \emph{Psychological distress of {A}sian
 international students: Applying intergroup contact theory} {[}Doctoral
-dissertation, Indiana University{]}. ProQuest Dissertations and Theses
-Global.
+dissertation, \{Indiana University\}{]}. {ProQuest Dissertations and
+Theses Global}.
 
@@
 perceived discrimination, and outgroup contact to racial attitudes
-toward White people in African American college students} {[}Doctoral
-dissertation, University of Kansas{]}. ProQuest Dissertations and Theses
-Global.
+toward {White} people in {African} {American} college students}
+{[}Doctoral dissertation, \{University of Kansas\}{]}. {ProQuest
+Dissertations and Theses Global}.
 
@@
 *Çakal, H., Hewstone, M., Güler, M., \& Heath, A. (2016). Predicting
-support for collective action in the conflict between Turks and Kurds:
-Perceived threats as a mediator of intergroup contact and social
-identity. \emph{Group Processes \& Intergroup Relations}, \emph{19}(6),
-732--752. \url{https://doi.org/10.1177/1368430216641303}
+support for collective action in the conflict between {Turks} and
+{Kurds}: {Perceived} threats as a mediator of intergroup contact and
+social identity. \emph{Group Processes \& Intergroup Relations},
+\emph{19}(6), 732--752. \url{https://doi.org/10.1177/1368430216641303}
 
@@
 investigation of the social identity model of collective action and the
-``sedative'' effect of intergroup contact among Black and White students
-in South Africa. \emph{British Journal of Social Psychology},
-\emph{50}(4), 606--627.
+{`sedative'} effect of intergroup contact among {Black} and {White}
+students in {South} {Africa}. \emph{British Journal of Social
+Psychology}, \emph{50}(4), 606--627.
 \url{https://doi.org/10.1111/j.2044-8309.2011.02075.x}
@@
 \leavevmode\hypertarget{ref-1614}{}%
-*Çelebi, E., Verkuyten, M., \& Smyrnioti, N. (2016). Support for Kurdish
-language rights in Turkey: The roles of ethnic group, group
+*Çelebi, E., Verkuyten, M., \& Smyrnioti, N. (2016). Support for
+{Kurdish} language rights in {Turkey}: The roles of ethnic group, group
 identifications, contact, and intergroup perceptions. \emph{Ethnic and
@@
 *de Vroome, T., Verkuyten, M., \& Martinovic, B. (2014). Host national
-identification of immigrants in the Netherlands. \emph{International
+identification of immigrants in the {Netherlands}. \emph{International
 Migration Review}, \emph{48}(1), 1--27.
@@
 V. M., Saguy, T., \& Dixon, J. (2019). Fostering social change among
-advantaged and disadvantaged group members: Integrating intergroup
+advantaged and disadvantaged group members: {Integrating} intergroup
 contact and social identity perspectives on collective action.
@@
 *Di Saint Pierre, F., Martinovic, B., \& de Vroome, T. (2015). Return
-wishes of refugees in the Netherlands: The role of integration, host
+wishes of refugees in the {Netherlands}: {The} role of integration, host
 national identification and perceived discrimination. \emph{Journal of
@@
 *Dixon, J., Çakal, H., Khan, W., Osmany, M., Majumdar, S., \& Hassan, M.
-(2017). Contact, political solidarity and collective action: An Indian
-case study of relations between historically disadvantaged communities.
-\emph{Journal of Community \& Applied Social Psychology}, \emph{27}(1),
-83--95. \url{https://doi.org/10.1002/casp.2296}
+(2017). Contact, political solidarity and collective action: {An}
+{Indian} case study of relations between historically disadvantaged
+communities. \emph{Journal of Community \& Applied Social Psychology},
+\emph{27}(1), 83--95. \url{https://doi.org/10.1002/casp.2296}
 
@@
 *Dixon, J., Durrheim, K., Tredoux, C., Tropp, L. R., Clack, B., \&
-Eaton, L. (2010). A paradox of integration? Interracial contact,
+Eaton, L. (2010). A paradox of integration? {Interracial} contact,
 prejudice reduction, and perceptions of racial discrimination.
@@
 Dixon, J., Levine, M., Reicher, S., \& Durrheim, K. (2012). Beyond
-prejudice: Are negative evaluations the problem and is getting us to
+prejudice: {Are} negative evaluations the problem and is getting us to
 like one another more the solution? \emph{Behavioral and Brain
@@
 *Droogendyk, L., Louis, W. R., \& Wright, S. C. (2016). Renewed promise
-for positive cross-group contact: The role of supportive contact in
+for positive cross-group contact: {The} role of supportive contact in
 empowering collective action. \emph{Canadian Journal of Behavioural
@@
 intergroup contact and relative gratification vs deprivation on
-prejudice on both sides of the U.S./Mexico status divide. \emph{Journal
-of Applied Social Psychology}, \emph{50}(7), 406--417.
+prejudice on both sides of the {U}.{S}./{Mexico} status divide.
+\emph{Journal of Applied Social Psychology}, \emph{50}(7), 406--417.
 \url{https://doi.org/10.1111/jasp.12669}
@@
 *Forbes, J. M. (2001). \emph{Affirmative action attitudes in black and
-white} {[}Doctoral dissertation, Wayne State University{]}. ProQuest
-Dissertations and Theses Global.
+white} {[}Doctoral dissertation, \{Wayne State University\}{]}.
+{ProQuest Dissertations and Theses Global}.
 
 \leavevmode\hypertarget{ref-325}{}%
-*Franco, M. (2019). Let the racism tell you who your friends are: The
+*Franco, M. (2019). Let the racism tell you who your friends are: {The}
 effects of racism on social connections and life-satisfaction for
-Multiracial people. \emph{International Journal of Intercultural
+{Multiracial} people. \emph{International Journal of Intercultural
 Relations}, \emph{69}, 54--65.
@@
 *Goto, S. G., Gee, G. C., \& Takeuchi, D. T. (2002). Strangers still?
-The experience of discrimination among Chinese Americans. \emph{Journal
-of Community Psychology}, \emph{30}(2), 211--224.
+{The} experience of discrimination among {Chinese} {Americans}.
+\emph{Journal of Community Psychology}, \emph{30}(2), 211--224.
 \url{https://doi.org/10.1002/jcop.9998}
@@
 *Haase, A., Rohmann, A., \& Hallmann, K. (2019). An ecological approach
-to psychological adjustment: A field survey among refugees in Germany.
-\emph{International Journal of Intercultural Relations}, \emph{68},
-44--54. \url{https://doi.org/10.1016/j.ijintrel.2018.10.003}
+to psychological adjustment: {A} field survey among refugees in
+{Germany}. \emph{International Journal of Intercultural Relations},
+\emph{68}, 44--54. \url{https://doi.org/10.1016/j.ijintrel.2018.10.003}
 
@@
 *Hayward, L. E., Hornsey, M. J., Tropp, L. R., \& Barlow, F. K. (2017).
-Positive and negative intergroup contact predict Black and White
-Americans' judgments about police violence against Black Americans.
-\emph{Journal of Applied Social Psychology}, \emph{47}(11), 605--615.
-\url{https://doi.org/10.1111/jasp.12463}
+Positive and negative intergroup contact predict {Black} and {White}
+{Americans}' judgments about police violence against {Black}
+{Americans}. \emph{Journal of Applied Social Psychology}, \emph{47}(11),
+605--615. \url{https://doi.org/10.1111/jasp.12463}
 
@@
 *Hayward, L. E., Tropp, L. R., Hornsey, M. J., \& Barlow, F. K. (2018).
-How negative contact and positive contact with Whites predict collective
-action among racial and ethnic minorities. \emph{British Journal of
-Social Psychology}, \emph{57}(1), 1--20.
+How negative contact and positive contact with {Whites} predict
+collective action among racial and ethnic minorities. \emph{British
+Journal of Social Psychology}, \emph{57}(1), 1--20.
 \url{https://doi.org/10.1111/bjso.12220}
@@
 *Head, R. N. (2013). \emph{Coping with perceived discrimination}
-{[}Doctoral dissertation, North Carolina State University{]}. ProQuest
-Dissertations and Theses Global.
+{[}Doctoral dissertation, \{North Carolina State University\}{]}.
+{ProQuest Dissertations and Theses Global}.
 
@@
 \leavevmode\hypertarget{ref-1494}{}%
-*Herda, D. E. (2013). \emph{Hostile contact: Self-reports of
-interpersonal discrimination among Blacks, Whites and Latinos in
-Chicago} {[}Doctoral dissertation, University of California, Davis{]}.
-ProQuest Dissertations and Theses Global.
+*Herda, D. E. (2013). \emph{Hostile contact: {Self}-reports of
+interpersonal discrimination among {Blacks}, {Whites} and {Latinos} in
+{Chicago}} {[}Doctoral dissertation, \{University of California,
+Davis\}{]}. {ProQuest Dissertations and Theses Global}.
 
 \leavevmode\hypertarget{ref-324}{}%
-*Herda, D. E. (2016). The specter of discrimination: Fear of
-interpersonal racial discrimination among adolescents in Chicago.
+*Herda, D. E. (2016). The specter of discrimination: {Fear} of
+interpersonal racial discrimination among adolescents in {Chicago}.
 \emph{Social Science Research}, \emph{55}, 48--62.
@@
 *Hui, B. P. H., Chen, S. X., Leung, C. M., \& Berry, J. W. (2015).
-Facilitating adaptation and intercultural contact: The role of
+Facilitating adaptation and intercultural contact: {The} role of
 integration and multicultural ideology in dominant and non-dominant
@@
 L. (2007). Neighborhood racial composition and perceptions of racial
-discrimination: Evidence from the Black women's health study.
+discrimination: Evidence from the {Black} women's health study.
 \emph{Social Psychology Quarterly}, \emph{70}(3), 272--289.
@@
 *Jiang, Q., Aricat, R. G., Chib, A., Chia, A., Tan, S. M., Tan, L., \&
-Woo, Z. W. (2016). Silent but brewing: Reactive ethnicity and
-interculturality among Chinese students in Singapore. \emph{Journal of
-Intercultural Communication}, \emph{40}.
+Woo, Z. W. (2016). Silent but brewing: {Reactive} ethnicity and
+interculturality among {Chinese} students in {Singapore}. \emph{Journal
+of Intercultural Communication}, \emph{40}.
 \url{http://www.immi.se/intercultural/nr40/aricat.html}
@@
 *Jones, M. L. (2017). \emph{Attitudes and experiences of close
-interethnic friendships among Native emerging adults: A mixed-methods
-investigation} {[}Doctoral dissertation, Utah State University{]}.
-ProQuest Dissertations and Theses Global.
+interethnic friendships among {Native} emerging adults: {A}
+mixed-methods investigation} {[}Doctoral dissertation, \{Utah State
+University\}{]}. {ProQuest Dissertations and Theses Global}.
 
@@
 *Kamberi, E., Martinovic, B., \& Verkuyten, M. (2017). Intergroup
-contact and minority group empowerment: The perspective of Roma and
-non-Roma adolescents in Macedonia. \emph{Journal of Community \& Applied
-Social Psychology}, \emph{27}(5), 424--434.
+contact and minority group empowerment: {The} perspective of {Roma} and
+non-{Roma} adolescents in {Macedonia}. \emph{Journal of Community \&
+Applied Social Psychology}, \emph{27}(5), 424--434.
 \url{https://doi.org/10.1002/casp.2320}
@@
 Predicting negative attitudes among religious minorities and majorities
-in Indonesia. \emph{Social Psychology Quarterly}, \emph{78}(2),
+in {Indonesia}. \emph{Social Psychology Quarterly}, \emph{78}(2),
 102--126. \url{https://doi.org/10.1177/0190272514564790}
@@
 *Kende, J., Baysu, G., Van Laar, C., \& Phalet, K. (2020). Majority
-group belonging without minority group distancing? Minority experiences
-of intergroup contact and inequality. \emph{British Journal of Social
-Psychology}, bjso.12382. \url{https://doi.org/10.1111/bjso.12382}
+group belonging without minority group distancing? {Minority}
+experiences of intergroup contact and inequality. \emph{British Journal
+of Social Psychology}, bjso.12382.
+\url{https://doi.org/10.1111/bjso.12382}
 
@@
 discrimination on depressive symptoms and school outcomes among asian
-american adolescents} {[}Doctoral dissertation, The University of
-Chicago{]}. ProQuest Dissertations and Theses Global.
+american adolescents} {[}Doctoral dissertation, \{The University of
+Chicago\}{]}. {ProQuest Dissertations and Theses Global}.
 
 \leavevmode\hypertarget{ref-401}{}%
-*Koschate, M., Hofmann, W., \& Schmitt, M. (2012). When East meets West:
-A longitudinal examination of the relationship between group relative
-deprivation and intergroup contact in reunified Germany. \emph{British
-Journal of Social Psychology}, \emph{51}(2), 290--311.
+*Koschate, M., Hofmann, W., \& Schmitt, M. (2012). When {East} meets
+{West}: {A} longitudinal examination of the relationship between group
+relative deprivation and intergroup contact in reunified {Germany}.
+\emph{British Journal of Social Psychology}, \emph{51}(2), 290--311.
 \url{https://doi.org/10.1111/j.2044-8309.2011.02056.x}
@@
 *Krahé, B., Abraham, C., Felber, J., \& Helbig, M. K. (2005). Perceived
-discrimination of international visitors to universities in Germany and
-the UK. \emph{British Journal of Psychology}, \emph{96}(3), 263--281.
-\url{https://doi.org/10.1348/000712605X48296}
+discrimination of international visitors to universities in {Germany}
+and the {UK}. \emph{British Journal of Psychology}, \emph{96}(3),
+263--281. \url{https://doi.org/10.1348/000712605X48296}
 
@@
 *Leszczensky, L., Maxwell, R., \& Bleich, E. (2020). What factors best
-explain national identification among Muslim adolescents? Evidence from
-four European countries. \emph{Journal of Ethnic and Migration Studies},
-\emph{46}(1), 260--276.
+explain national identification among {Muslim} adolescents? {Evidence}
+from four {European} countries. \emph{Journal of Ethnic and Migration
+Studies}, \emph{46}(1), 260--276.
 \url{https://doi.org/10.1080/1369183X.2019.1578203}
@@
 Levin, S., Van Laar, C., \& Foote, W. (2006). Ethnic segregation and
-perceived discrimination in college: Mutual influences and effects on
+perceived discrimination in college: {Mutual} influences and effects on
 social and academic life. \emph{Journal of Applied Social Psychology},
@@
 \leavevmode\hypertarget{ref-li_meta-cart_2017}{}%
-Li, X., Dusseldorp, E., \& Meulman, J. J. (2017). Meta-CART: A tool to
-identify interactions between moderators in meta-analysis. \emph{British
-Journal of Mathematical and Statistical Psychology}, \emph{70}(1),
-118--136. \url{https://doi.org/10.1111/bmsp.12088}
+Li, X., Dusseldorp, E., \& Meulman, J. J. (2017). Meta-{CART}: {A} tool
+to identify interactions between moderators in meta-analysis.
+\emph{British Journal of Mathematical and Statistical Psychology},
+\emph{70}(1), 118--136. \url{https://doi.org/10.1111/bmsp.12088}
 
@@
 Li, X., Dusseldorp, E., Su, X., \& Meulman, J. J. (2020). Multiple
-moderator meta-analysis using the R-package Meta-CART. \emph{Behavior
-Research Methods}, \emph{52}(6), 2657--2673.
+moderator meta-analysis using the {R}-package {Meta}-{CART}.
+\emph{Behavior Research Methods}, \emph{52}(6), 2657--2673.
 \url{https://doi.org/10.3758/s13428-020-01360-0}
@@
 conflict between reducing prejudice and supporting engagement in
-collective action} {[}Doctoral dissertation, University of California,
-Santa Cruz{]}. ProQuest Dissertations and Theses Global.
+collective action} {[}Doctoral dissertation, \{University of California,
+Santa Cruz\}{]}. {ProQuest Dissertations and Theses Global}.
 
@@
 *Lutterbach, S., \& Beelmann, A. (2020). Positive and negative
-intergroup contact and shared reality: Contact effects among host
+intergroup contact and shared reality: {Contact} effects among host
 society and refugees. \emph{European Journal of Social Psychology},
@@
 MacInnis, C. C., \& Hodson, G. (2019). Extending the benefits of
-intergroup contact beyond attitudes: When does intergroup contact
+intergroup contact beyond attitudes: {When} does intergroup contact
 predict greater collective action support? \emph{Journal of Theoretical
@@
 *Mallet, J., Lewis, C. A., \& Cairns, E. (2013). Perceived in-group
-density and psychological adjustment in a sample of Northern Irish
-Catholics and Protestants. \emph{Studia Psychologica}, \emph{55}(3),
+density and psychological adjustment in a sample of {Northern} {Irish}
+{Catholics} and {Protestants}. \emph{Studia Psychologica}, \emph{55}(3),
 229--246. \url{https://doi.org/10.21909/sp.2013.03.639}
@@
 *Martiny, S. E., Froehlich, L., Soltanpanah, J., \& Haugen, M. S.
-(2020). Young immigrants in Norway: The role of national and ethnic
+(2020). Young immigrants in {Norway}: {The} role of national and ethnic
 identity in immigrants' integration. \emph{Scandinavian Journal of
@@
 \leavevmode\hypertarget{ref-mazumder_persistent_2018}{}%
-Mazumder, S. (2018). The persistent effect of U. S. civil rights
+Mazumder, S. (2018). The persistent effect of {U. S.} Civil rights
 protests on political attitudes. \emph{American Journal of Political
@@
 \leavevmode\hypertarget{ref-1850}{}%
-*McGinley, J. E. (2007). \emph{Expatriate adjustment: Resources,
-responses, and outcomes} {[}Doctoral dissertation, Northcentral
-University{]}. ProQuest Dissertations and Theses Global.
+*McGinley, J. E. (2007). \emph{Expatriate adjustment: {Resources},
+responses, and outcomes} {[}Doctoral dissertation, \{Northcentral
+University\}{]}. {ProQuest Dissertations and Theses Global}.
 
 \leavevmode\hypertarget{ref-mckeown_contact_2017}{}%
-McKeown, S., \& Dixon, J. (2017). The ``contact hypothesis'': Critical
+McKeown, S., \& Dixon, J. (2017). The {``contact hypothesis''}: Critical
 reflections and future directions. \emph{Social and Personality
@@
 *McKeown, S., \& Taylor, L. K. (2017). Beyond the irony of intergroup
-contact: The effects of contact and threat on political participation
-and support for political violence in Northern Ireland. \emph{Group
+contact: {The} effects of contact and threat on political participation
+and support for political violence in {Northern} {Ireland}. \emph{Group
 Dynamics: Theory, Research, and Practice}, \emph{21}(4), 234--244.
@@
 reporting items for systematic review and meta-analysis protocols
-(PRISMA-P) 2015 statement. \emph{Systematic Reviews}, \emph{4}(1), 1--9.
-\url{https://doi.org/10.1186/2046-4053-4-1}
+({PRISMA}-{P}) 2015 statement. \emph{Systematic Reviews}, \emph{4}(1),
+1--9. \url{https://doi.org/10.1186/2046-4053-4-1}
 
@@
 A., McInerney, J., \& Thue, B. (2020). Beyond western, educated,
-industrial, rich, and democratic (WEIRD) psychology: Measuring and
+industrial, rich, and democratic ({WEIRD}) psychology: Measuring and
 mapping scales of cultural and psychological distance.
@@
 Wright, S. C. (2002). Contact and the personal/group discrimination
-discrepancy in an Inuit community. \emph{The Journal of Psychology},
+discrepancy in an {Inuit} community. \emph{The Journal of Psychology},
 \emph{136}(4), 371--382. \url{https://doi.org/10.1080/00223980209604164}
+
+\leavevmode\hypertarget{ref-2391}{}%
+*Prati, F., Kenfack, S. K., Rubini, M., \& Hewstone, M. (2020). {[}Data
+set{]}. University of Oxford.
 
@@
 intergroup contact, and ethnic minority members' reactions toward the
-majority. \emph{Ethnicities}, \emph{24}(1), 3--22.
+majority. \emph{Ethnicities}, \emph{24}, 3--22.
 \url{https://doi.org/10.1177/1468796820909493}
@@
 (2008). Racial identity, social context, and race-related social
-cognition in African Americans during middle childhood.
+cognition in {African} {Americans} during middle childhood.
 \emph{Developmental Psychology}, \emph{44}(6), 1537--1546.
@@
 *Saab, R., Harb, C., \& Moughalian, C. (2017). Intergroup contact as a
-predictor of violent and nonviolent collective action: Evidence from
-Syrian refugees and Lebanese nationals. \emph{Peace and Conflict:
+predictor of violent and nonviolent collective action: {Evidence} from
+{Syrian} refugees and {Lebanese} nationals. \emph{Peace and Conflict:
 Journal of Peace Psychology}, \emph{23}(3), 297--306.
@@
 students' pre-college racial environments and their diversity
-experiences in college} {[}Doctoral dissertation, University of
-California, Los Angeles{]}. ProQuest Dissertations and Theses Global.
+experiences in college} {[}Doctoral dissertation, \{University of
+California, Los Angeles\}{]}. {ProQuest Dissertations and Theses
+Global}.
 
@@
 \leavevmode\hypertarget{ref-2392}{}%
-*Sengupta, N. K. (2020a). \emph{Inter-caste contact in India}
+*Sengupta, N. K. (2020a). \emph{Inter-caste contact in {India}}
 {[}Unpublished dataset{]}. University of Kent.
@@
 \leavevmode\hypertarget{ref-2385}{}%
-*Sengupta, N. K. (2020b). \emph{Inter-religious contact in India}
+*Sengupta, N. K. (2020b). \emph{Inter-religious contact in {India}}
 {[}Unpublished dataset{]}. University of Kent.
@@
 *Sengupta, N. K., \& Sibley, C. G. (2020). \emph{Intergroup contact and
-political attitudes among ethnic minorities in New Zealand}
+political attitudes among ethnic minorities in {New Zealand}}
 {[}Unpublished dataset{]}. The University of Auckland.
@@
 \leavevmode\hypertarget{ref-1891}{}%
-*Shammas, D. (2009). \emph{Expatriate adjustment: Resources, responses,
-and outcomes} {[}Doctoral dissertation, Northcentral University{]}.
-ProQuest Dissertations and Theses Global.
+*Shammas, D. (2009). \emph{Expatriate adjustment: {Resources},
+responses, and outcomes} {[}Doctoral dissertation, \{Northcentral
+University\}{]}. {ProQuest Dissertations and Theses Global}.
 
 \leavevmode\hypertarget{ref-789}{}%
-*Shani, M., \& Boehnke, K. (2017). The effect of Jewish--Palestinian
+*Shani, M., \& Boehnke, K. (2017). The effect of {Jewish}--{Palestinian}
 mixed-model encounters on readiness for contact and policy support.
@@
 effect of discrimination, religiosity, and friendship network on
-expression of the Tp53 cancer suppressor gene. \emph{SSM - Population
+expression of the {Tp53} cancer suppressor gene. \emph{SSM - Population
 Health}, \emph{7}, 100389.
@@
 \leavevmode\hypertarget{ref-stan_development_team_rstan:_2020}{}%
-Stan Development Team. (2020). \emph{RStan: The R interface to Stan}
-(Version 2.21.2). \url{http://mc-stan.org/}
+Stan Development Team. (2020). \emph{{RStan}: {The} {R} interface to
+{Stan}} (Version 2.21.2). \url{http://mc-stan.org/}
 
@@
 *Swami, V. (2009). Predictors of sociocultural adjustment among
-sojourning Malaysian students in Britain. \emph{International Journal of
-Psychology}, \emph{44}(4), 266--273.
+sojourning {Malaysian} students in {Britain}. \emph{International
+Journal of Psychology}, \emph{44}(4), 266--273.
 \url{https://doi.org/10.1080/00207590801888745}
@@
 *Swami, V., Arteche, A., Chamorro-Premuzic, T., \& Furnham, A. (2010).
-Sociocultural adjustment among sojourning Malaysian students in Britain:
-A replication and path analytic extension. \emph{Social Psychiatry and
-Psychiatric Epidemiology}, \emph{45}(1), 57--65.
+Sociocultural adjustment among sojourning {Malaysian} students in
+{Britain}: A replication and path analytic extension. \emph{Social
+Psychiatry and Psychiatric Epidemiology}, \emph{45}(1), 57--65.
 \url{https://doi.org/10.1007/s00127-009-0042-4}
@@
 *Tausch, N., Saguy, T., \& Bryson, J. (2015). How does intergroup
-contact affect social change? Its impact on collective action and
+contact affect social change? {Its} impact on collective action and
 individual mobility intentions among members of a disadvantaged group.
@@
 *Teney, C. (2011). Endorsement of assimilationism among ethnic minority
-and majority youth in a multination-multiethnic context: The case of
-Brussels. \emph{European Sociological Review}, \emph{27}(2), 212--229.
+and majority youth in a multination-multiethnic context: {The} case of
+{Brussels}. \emph{European Sociological Review}, \emph{27}(2), 212--229.
 \url{https://doi.org/10.1093/esr/jcq003}
@@
 *Titzmann, P. F., Silbereisen, R. K., \& Schmitt-Rodermund, E. (2007).
-Friendship homophily among diaspora migrant adolescents in Germany and
-Israel. \emph{European Psychologist}, \emph{12}(3), 181--195.
+Friendship homophily among diaspora migrant adolescents in {Germany} and
+{Israel}. \emph{European Psychologist}, \emph{12}(3), 181--195.
 \url{https://doi.org/10.1027/1016-9040.12.3.181}
@@
 \leavevmode\hypertarget{ref-1221}{}%
-*Tostado, P. (2017). \emph{When you aren't who your friends are: The
+*Tostado, P. (2017). \emph{When you aren't who your friends are: {The}
 moderating influence of racial similarity on the association between
-friendships and mental well-being} {[}Master's thesis, Portland State
-University{]}. ProQuest Dissertations and Theses Global.
+friendships and mental well-being} {[}Master's thesis, \{Portland State
+University\}{]}. {ProQuest Dissertations and Theses Global}.
 
 \leavevmode\hypertarget{ref-933}{}%
-*Tropp, L. R. (2007). Perceived discrimination and interracial contact:
-Predicting interracial closeness among Black and White Americans.
-\emph{Social Psychology Quarterly}, \emph{70}(1), 70--81.
+*Tropp, Linda R. (2007). Perceived discrimination and interracial
+contact: {Predicting} interracial closeness among {Black} and {White}
+{Americans}. \emph{Social Psychology Quarterly}, \emph{70}(1), 70--81.
 \url{https://doi.org/10.1177/019027250707000108}
@@
 \leavevmode\hypertarget{ref-tropp_making_2018}{}%
-Tropp, L. R., \& Barlow, F. K. (2018). Making advantaged racial groups
-care about inequality: Intergroup contact as a route to psychological
-investment. \emph{Current Directions in Psychological Science},
-\emph{27}(3), 194--199. \url{https://doi.org/10.1177/0963721417743282}
+Tropp, Linda R., \& Barlow, F. K. (2018). Making advantaged racial
+groups care about inequality: Intergroup contact as a route to
+psychological investment. \emph{Current Directions in Psychological
+Science}, \emph{27}(3), 194--199.
+\url{https://doi.org/10.1177/0963721417743282}
 
 \leavevmode\hypertarget{ref-1743}{}%
-*Tropp, L. R., Hawi, D. R., Van Laar, C., \& Levin, S. (2012).
+*Tropp, Linda R., Hawi, D. R., Van Laar, C., \& Levin, S. (2012).
 Cross-ethnic friendships, perceived discrimination, and their effects on
-ethnic activism over time: A longitudinal investigation of three ethnic
-minority groups. \emph{British Journal of Social Psychology},
+ethnic activism over time: {A} longitudinal investigation of three
+ethnic minority groups. \emph{British Journal of Social Psychology},
 \emph{51}(2), 257--272.
@@
 \leavevmode\hypertarget{ref-1658}{}%
-*Tropp, L. R., Okamoto, D. G., Marrow, H. B., \& Jones-Correa, M.
+*Tropp, Linda R., Okamoto, D. G., Marrow, H. B., \& Jones-Correa, M.
 (2018). How contact experiences shape welcoming: Perspectives from
-U.S.-born and immigrant groups. \emph{Social Psychology Quarterly},
+{U}.{S}.-born and immigrant groups. \emph{Social Psychology Quarterly},
 \emph{81}(1), 23--47. \url{https://doi.org/10.1177/0190272517747265}
@@
 \leavevmode\hypertarget{ref-286}{}%
-*Uluğ, Ö. M., \& Cohrs, J. C. (2017). "If we become friends, maybe I can
-change my perspective'': Intergroup contact, endorsement of conflict
-narratives, and peace-related attitudes in Turkey. \emph{Peace and
-Conflict: Journal of Peace Psychology}, \emph{23}(3), 278--287.
-\url{https://doi.org/10.1037/pac0000216}
+*Uluğ, Ö. M., \& Cohrs, J. C. (2017). "{If} we become friends, maybe {I}
+can change my perspective'': {Intergroup} contact, endorsement of
+conflict narratives, and peace-related attitudes in {Turkey}.
+\emph{Peace and Conflict: Journal of Peace Psychology}, \emph{23}(3),
+278--287. \url{https://doi.org/10.1037/pac0000216}
 
@@
 van Zomeren, M., Postmes, T., \& Spears, R. (2008). Toward an
-integrative social identity model of collective action: A quantitative
+integrative social identity model of collective action: {A} quantitative
 research synthesis of three socio-psychological perspectives.
@@
 *Vedder, P., Sam, D. L., \& Liebkind, K. (2007). The acculturation and
-adaptation of Turkish adolescents in North-Western Europe. \emph{Applied
-Developmental Science}, \emph{11}(3), 126--136.
+adaptation of {Turkish} adolescents in {North-Western Europe}.
+\emph{Applied Developmental Science}, \emph{11}(3), 126--136.
 \url{https://doi.org/10.1080/10888690701454617}
@@
 \leavevmode\hypertarget{ref-viechtbauer_conducting_2010}{}%
-Viechtbauer, W. (2010). Conducting meta-analyses in R with the metafor
+Viechtbauer, W. (2010). Conducting meta-analyses in {R} with the metafor
 package. \emph{Journal of Statistical Software}, \emph{36}(1), 1--48.
@@
 \leavevmode\hypertarget{ref-westgate_revtools:_2019}{}%
-Westgate, M. J. (2019). revtools: An R package to support article
+Westgate, M. J. (2019). {revtools}: An {R} package to support article
 screening for evidence synthesis. \emph{Research Synthesis Methods},
@@
 social change. In R. Brown \& S. L. Gaertner (Eds.), \emph{Blackwell
-handbook of social psychology: Intergroup processes} (pp. 409--430).
+handbook of social psychology: {Intergroup} processes} (pp. 409--430).
 Blackwell. \url{https://doi.org/10.1002/9780470693421.ch20}
@@
 Wright, S. C., \& Lubensky, M. E. (2009). The struggle for social
-equality: Collective action versus prejudice reduction. In S. Demoulin,
-J.-P. Leyens, \& J. F. Dovidio (Eds.), \emph{Intergroup
-misunderstandings: Impact of divergent social realities} (pp. 291--310).
-Psychology Press.
+equality: {Collective} action versus prejudice reduction. In S.
+Demoulin, J.-P. Leyens, \& J. F. Dovidio (Eds.), \emph{Intergroup
+misunderstandings: {Impact} of divergent social realities} (pp.
+291--310). Psychology Press.
 
@@
 Wright, S. C., Taylor, D. M., \& Moghaddam, F. M. (1990). Responding to
-membership in a disadvantaged group: From acceptance to collective
+membership in a disadvantaged group: {From} acceptance to collective
 protest. \emph{Journal of Personality and Social Psychology},
@@
 resource predictors of psychological and sociocultural adaptation:
-International students in Hong Kong. \emph{Journal of Studies in
+International students in {Hong} {Kong}. \emph{Journal of Studies in
 International Education}, \emph{23}(5), 572--588.
@@
 *Yu, B., Mak, A. S., \& Bodycott, P. (2019). Psychological and academic
-adaptation of mainland Chinese students in Hong Kong universities.
+adaptation of mainland {Chinese} students in {Hong} {Kong} universities.
 \emph{Studies in Higher Education}, 1--13.
@@
 
+\end{CSLReferences}
+
 \endgroup

### 2021-12-13 figures/figure-s3.R

@@ -1,0 +1,287 @@
+rm(list = ls())
+
+# Notes -------------------------------------------------------------------
+
+
+# Library -----------------------------------------------------------------
+
+  # Load packages
+  library(tidyverse)
+  library(tidybayes)
+  library(ggtext)
+  library(patchwork)
+  library(numform)
+
+  # Link functions
+  r_to_z <- function(r) 0.5 * log( (1 + r) / (1 - r) )
+  z_to_r <- function(z) ( exp(2 * z) - 1 ) / ( exp(2 * z) + 1 )
+  
+  # Set seed (for posterior predictive simulations)
+  set.seed(9071118)
+  
+
+# Prepare -----------------------------------------------------------------
+  
+  # Import results from analyses
+  pre_results <- read_rds("results/results_preregistered_analyses.rds")
+  add_results <- read_rds("results/results_additional_analyses.rds")
+  
+  # Import study-wise estimates from analyses
+  pre_r_pred_jj <- read_rds("results/r_pred_jj.rds")
+  add_r_pred_jj <- read_rds("results/r_additional_analyses_pred_jj.rds")
+  
+  # Merge results
+  results <- bind_rows(
+    pre_results %>% mutate(analysis = "Preregistered"),
+    add_results %>% mutate(analysis = "Not Preregistered")
+  )
+  
+  # Merge study-wise estimates
+  r_pred_jj <- bind_rows(
+    pre_r_pred_jj %>% mutate(analysis = "Preregistered"),
+    add_r_pred_jj %>% mutate(analysis = "Not Preregistered")
+  )
+
+  # Name predictor and outcome variables
+  results <- results %>% 
+    mutate(
+      x_name = recode_factor(
+        x_var,
+        "ic" = "Intergroup Contact",
+        "pi" = "Perceived Injustice",
+        "ca" = "Collective Action",
+        "ps" = "Policy Support"
+      ),
+      y_name = recode_factor(
+        y_var,
+        "pi" = "Perceived Injustice",
+        "ca" = "Collective Action",
+        "ps" = "Policy Support"
+      )
+    )
+  
+  # Name predictor and outcome variables
+  r_pred_jj <- r_pred_jj %>% 
+    mutate(
+      x_name = recode_factor(
+        x_var,
+        "ic" = "Intergroup Contact",
+      ),
[…]

### 2021-12-13 scripts/run_additional_analyses.R

@@ -1,0 +1,314 @@
+rm(list = ls())
+
+# Notes -------------------------------------------------------------------
+
+  #########################################################################
+  # Adjust the number of cores to suit your computing environment (e.g.,  #
+  # run parallel::detectCores() to find the number of available cores).   #
+  #########################################################################
+
+  #########################################################################
+  # This is an additional analyses, requested by a reviewer, to test a    #
+  # strong version of the 'ironic' effects hypothesis (qualitatively      #
+  # positive contact between adults).                                     #
+  #########################################################################
+
+# Library -----------------------------------------------------------------
+
+  # Load packages
+  library(tidyverse); library(rstan); library(tidybayes); library(irr)
+
+  # Stan options
+  n_cores  <- 8
+  n_iter   <- 8000
+  n_warmup <- 1000
+  seeds    <- c(6967674, 5768664, 7517370)
+  options(mc.cores = n_cores)
+  rstan_options(auto_write = FALSE)
+  
+  # Link functions
+  r_to_z <- function(r) 0.5 * log( (1 + r) / (1 - r) )
+  z_to_r <- function(z) ( exp(2 * z) - 1 ) / ( exp(2 * z) + 1 )
+
+  
+# Prepare -----------------------------------------------------------------
+  
+  # Load (preregistered) model
+  model <- stan_model("models/2l-meta-analysis.stan")
+  
+  # Import data
+  dl <- read_rds("data/dl.rds")
+  
+  # Import coding results
+  dm <- read_csv(
+    "records/results/coding-for-additional-analyses.csv",
+    col_types = "cicccccc"
+  )
+  
+  # Calculate interrater agreement
+  dm %>% 
+    pivot_wider(names_from = coder, values_from = ic_quality) %>% 
+    with(., kappa2(ratings = cbind(`Coder 1`, `Coder 2`)))
+  
+  # Resolve disagreements
+  dm <- dm %>% 
[…]

### 2021-12-13 scripts/run_exploratory_moderator_analyses.R

@@ -105,7 +105,7 @@ rm(list = ls())
   
   # Run random-effects meta-tree model
   pi_tree <- REmrt(
-    z ~ pi_specific + pi_personal + ic_direct + study_setting + study_design + study_sample + age + study_intention + publication_status,
+    z ~ pi_specific + pi_personal + ic_direct + ic_quality + study_setting + study_design + study_sample + age + study_intention + publication_status,
     vi = vi,
     data = es %>% filter(y_var == "pi"),
     c = 0.0,

### 2022-02-17 manuscript/manuscript.Rmd
start revision
revision

@@
 nocite: | 
-  @19, @45, @46, @91, @93, @244, @284, @286, @303, @322, @324, @325, @336, @401, @414, @423, @480, @609, @703, @733, @783, @789, @803, @813, @823, @829, @830, @856, @893, @894, @933, @956, @1020, @1042, @1045, @1114, @1163, @1221, @1248, @1376, @1386, @1395, @1407, @1411, @1412, @1494, @1525, @1549, @1576, @1614, @1658, @1695, @1743, @1762, @1807, @1850, @1891, @1914, @1949, @1966, @1993, @2001, @2023, @2033, @2075, @2257, @2309, @2333, @2341, @2375, @2380, @2381, @2382, @2383, @2385, @2391, @2392, @2394, @2395, @2396, @2397, @2398, @2399, @3000, @3005, @3051, @3054, @3060, @3134, @3196, @3201, @3205, @4000, @4001, @4002, @4003, @4004, @4005
+  @19, @45, @46, @91, @93, @244, @284, @286, @303, @322, @324, @325, @336, @401, @414, @423, @480, @609, @703, @733, @783, @789, @803, @813, @823, @829, @830, @856, @893, @894, @933, @956, @1020, @1042, @1045, @1114, @1163, @1221, @1248, @1376, @1386, @1395, @1407, @1411, @1412, @1494, @1525, @1549, @1576, @1614, @1658, @1695, @1743, @1762, @1807, @1850, @1891, @1914, @1949, @1966, @1993, @2001, @2023, @2033, @2075, @2257, @2309, @2333, @2341, @2375, @2380, @2381, @2382, @2383, @2385, @2391, @2392, @2394, @2395, @2396, @2397, @2398, @2399, @3000, @3005, @3051, @3054, @3060, @3134, @3196, @3201, @3205, @4000, @4001, @4002, @4003, @4004, @4005, @bracegirdle_disentangling_2022, @sengupta_protect_unpublished
 abstract: 
@@
 Across outcomes, `r with(readRDS("../results/results_for_abstract.rds"), paste0(round(min(p_pred)*100), "--", round(max(p_pred)*100), "\\%"))` of studies found *positive* associations with intergroup contact.
-Moderator analyses explained about a third of the between-sample variance, showing that, on average, associations were negative only in studies of adults that measured intergroup contact directly and were strongest in studies that examined short-term migration or (post-)colonial intergroup relations.
+Moderator analyses explained about a third of the between-sample variance, showing that, at least for perceived injustice, associations with intergroup contact were most consistently negative in studies that measured direct, qualitatively positive contact among adults.
 We also found evidence for an alternative explanation for the apparent ‘ironic’ effects of intergroup contact as, after controlling for the positive association of negative contact with support for social change, positive contact was no longer associated with any of the outcomes.
@@
 Collective action is crucial to achieving social change because advantaged-group members rarely give up their advantages without sustained pressure from disadvantaged-group members [@blumer_race_1958; for a review, see @dixon_beyond_2012].
-Researchers have argued that intergroup contact could discourage disadvantaged-group members from engaging in collective action by diminishing their perceived discrimination [@1743], by blurring boundaries between the disadvantaged ingroup and the advantaged outgroup [@813], by reducing negative attitudes toward the advantaged outgroup [@wright_struggle_2009], and by quelling their anger  [@2309; @2375].
+Researchers have argued that intergroup contact could discourage disadvantaged-group members from engaging in collective action by diminishing their perceived discrimination [@1743], by reducing the perceived threat from the advantaged outgroup [@1248], by blurring boundaries between the disadvantaged ingroup and the advantaged outgroup [@813], by reducing negative attitudes toward the advantaged outgroup [@wright_struggle_2009], and by quelling their anger  [@2309; @2375].
 To the extent that it discourages collective action, intergroup contact reduces support for social change.
@@
 
-While narrative reviews of the growing literature on this topic have been published [@hassler_intergroup_2021; @macinnis_extending_2019; @mckeown_contact_2017], we present the first systematic review and meta-analysis of the relationship between intergroup contact and support for social change in disadvantaged groups.
+As a result of two recent developments, there is now an emerging consensus that, in line with the former argument, intergroup contact has the 'ironic' effect of undermining support for social change in disadvantaged groups.
+First, a large-scale preregistered multi-country study provided the most comprehensive evidence to date that contact with advantaged groups correlates with less support for social change in disadvantaged groups [@3054].
+Second, several narrative reviews of the growing evidence for the 'ironic' effects of intergroup contact have been published [@hassler_intergroup_2021; @macinnis_extending_2019; @mckeown_contact_2017].
+Narrative reviews do not, however, include all relevant studies and do not synthesize the, sometimes conflicting, findings of different studies.
+We present the first systematic review and meta-analysis of the relationship between intergroup contact and support for social change in disadvantaged groups.
 To test the hypothesized 'ironic' effects of intergroup contact, we evaluate the evidence that contact with advantaged-group members reduces disadvantaged-group members' perceived injustice, collective action, and support for reparative policies.
@@
 Our second objective was to synthesize the available evidence to establish the direction and magnitude of the relationships between intergroup contact and the three outcomes.
-Doing so allowed us to determine whether the available evidence supports a negative or positive [see @pettigrew_recent_2011] relationship between contact and support for social change and to estimate the strength of this relationship.
+Doing so allowed us to determine whether the available evidence supports a negative or positive direct relationship between contact and support for social change and to estimate the strength of this relationship.
 Our third objective was to estimate and explain the variability of this relationship across study settings, designs, and other potential moderators.
@@
 
+In pursuing these objectives, we focus on the direct relationships of intergroup contact with perceived injustice, collective action, and support for reparative policies in disadvantaged groups.
+We do not consider indirect and interaction effects or the effects of imagined, extended, or parasocial contact.
+Further, while the argument for the 'ironic' effects of intergroup contact is part of a broader critique of the prejudice reduction model of social change [for a review, see @dixon_beyond_2012], our meta-analysis tests the narrower hypothesis whether intergroup contact reduces support for social change in disadvantaged groups.
+
 # Method
@@
 
-We prepared a protocol in accordance with the PRISMA-P statement [@moher_preferred_2015] and preregistered it on the Open Science Framework.^[[https://osf.io/ryuev/?view_only=8938ac6178914da98bdda1da4a6e27f0](https://osf.io/ryuev/?view_only=8938ac6178914da98bdda1da4a6e27f0)] Preregistration precludes undisclosed flexibility in study selection, outcome selection, and other decisions that influence effect size estimates—and thus prevents confirmation bias from determining the conclusions of a meta-analysis [@lakens_reproducibility_2016].
-We report deviations from our protocol in the Supplemental Online Material (SOM).
-We make data, analysis scripts, and the fully reproducible manuscript available online.^[[https://osf.io/w5tqv/?view_only=5cbf7ad5b2b449a7a0f4ada0337b802a](https://osf.io/w5tqv/?view_only=5cbf7ad5b2b449a7a0f4ada0337b802a)]
+We prepared a protocol in accordance with the PRISMA-P statement [@moher_preferred_2015] and preregistered it on the Open Science Framework.^[[https://osf.io/ryuev](https://osf.io/ryuev)] Preregistration precludes undisclosed flexibility in study selection, outcome selection, and other decisions that influence effect size estimates—and thus prevents confirmation bias from determining the conclusions of a meta-analysis [@lakens_reproducibility_2016].
+We report deviations from our preregistered protocol at the end of the Method section.
+We make data, analysis scripts, and the fully reproducible manuscript available online.^[[https://osf.io/w5tqv](https://osf.io/w5tqv)]
 
@@
 We exported records and relevant metadata from each database.
-We removed duplicates using the *revtools* package [@westgate_revtools:_2019].
+We removed duplicates using the *revtools* R package [@westgate_revtools:_2019].
 
@@
 
-### Outcomes Selection
+### Outcome Selection
 
@@
 ***Study Setting.*** For each sample, we recorded in what country (or countries) the data was collected ($\kappa = .97$) and what the disadvantaged ingroup and the advantaged outgroup were.
-We categorized each sample’s setting according to whether the source of the groups’ relative inequality was long-term migration (e.g., Asian Americans), short-term  migration (e.g., international students), slavery (e.g., Black Americans), colonization (e.g., Māori, Black South Africans), religion, caste, sexuality, or another distinction ($\kappa = .85$).
+We categorized each sample’s setting according to whether the source of the groups’ relative inequality was long-term migration (e.g., Asian Americans), short-term  migration (e.g., international students), slavery (e.g., Black Americans), colonization (e.g., Māori, Black South Africans), religion, caste, sexual/gender identity, or another distinction ($\kappa = .85$; see SOM for details).
 
-***Study Design.*** We categorized each study as either observational and cross-sectional, observational and longitudinal, quasi-experimental, experimental, an intervention, or other ($\kappa = .85$).
-We categorized each sample as either a student convenience sample, a non-student convenience sample, a probability or representative sample, or another kind of sample ($\kappa = .73$).
+***Study Design.*** We categorized each study as either observational and cross-sectional, observational and longitudinal, quasi-experimental, experimental, an intervention, or other ($\kappa = .85$).^[While the term ‘observational study’ is sometimes used to refer to the naturalistic observation of behavior, we use it in its broader sense, that is, to refer to studies that do not involve random assignment into experimental conditions [@cochran_planning_1965; @everitt_observational_2005].] We categorized each sample as either a student convenience sample, a non-student convenience sample, a probability or representative sample, or another kind of sample ($\kappa = .73$).
 We categorized the age group(s) in each sample as children ($\leq 12$ years), adolescents (13–18 years), or adults ($\geq 18$ years; $\kappa = .64$).
@@
 
-***Predictor Variables.*** For each measure of intergroup contact, we coded whether it assessed contact with the specific advantaged outgroup of interest directly—or whether it assessed contact indirectly by, for example, asking what proportion of someone’s friends were not from the participants’ ingroup or what proportion of residents in someone’s neighbourhood were from the relevant outgroup ($\kappa = .82$).
+***Predictor Variables.*** For each measure of intergroup contact, we coded whether it assessed contact with the specific advantaged outgroup of interest directly—or whether it assessed contact indirectly by, for example, asking what proportion of someone’s friends were not from the participants’ ingroup or what proportion of residents in someone’s neighborhood were from the relevant outgroup ($\kappa = .82$).
+In addition, we coded whether each predictor variable assessed direct, qualitatively positive intergroup contact by, for example, measuring contact quality or cross-group friendship with the advantaged outgroup($\kappa = .82$).^[We thank John Dixon for his suggestion to consider the distinction between contact quantity and quality in our analyses.
+As we added this moderator during peer review and as doing so changed the results of our moderator analyses, we report our original findings in the SOM.]
 
@@
 
-We estimated effect sizes using Bayesian random-effects meta-analysis models in *RStan* [@stan_development_team_rstan:_2020] which modeled the *z*-transformed correlation coefficients with a normal likelihood function: \begin{align*} z_{ij} &\sim \text{Normal}(\theta_{ij}, \sigma_{ij}) \\ \theta_{ij} &= \begin{cases} \mu + \beta_j\tau_J & \text{if } I_j = 1 \\ \mu + \beta_j\tau_J + \beta_i\tau_I & \text{if } I_j > 1 \end{cases} \\ \end{align*} where $z_{ij}$ is the observed effect size in sample $i$ of study $j$, $\sigma_{ij}$ is the sample standard error, and $\theta_{ij}$ is the estimated effect size.
+We estimated effect sizes with Bayesian random-effects meta-analysis models, using the *RStan* package [@stan_development_team_rstan:_2020] for the R programming language [@r_version_2021], which modeled the *z*-transformed correlation coefficients with a normal likelihood function: \begin{align*} z_{ij} &\sim \text{Normal}(\theta_{ij}, \sigma_{ij}) \\ \theta_{ij} &= \begin{cases} \mu + \beta_j\tau_J & \text{if } I_j = 1 \\ \mu + \beta_j\tau_J + \beta_i\tau_I & \text{if } I_j > 1 \end{cases} \\ \end{align*} where $z_{ij}$ is the observed effect size in sample $i$ of study $j$, $\sigma_{ij}$ is the sample standard error, and $\theta_{ij}$ is the estimated effect size.
 We estimated $z_{ij}$ as a function of the mean effect size $\mu$ and of two varying (random) intercepts, $\beta_i$ and $\beta_j$, with the corresponding standard deviations, $\tau_I$ and $\tau_J$.
@@
 Bayesian inference applies Bayes’ theorem to update prior distributions in light of the observed data to produce posterior distributions.
-In contrast to *p*-values and confidence intervals, the resulting posterior distributions have a straightforward interpretation as stating how plausible different values of the model parameters are given the observed data.
-We report point estimates, based on the median of posterior samples, and uncertainty intervals, based on the quantiles of posterior samples, that enclose the 95% most plausible estimates.
+In contrast to *p*-values and confidence intervals, the resulting posterior distributions have a straightforward interpretation as stating how plausible different values of the model parameters are given the observed data.^[For an accessible introduction, see @mcelreath_statistical_2020.] We report point estimates, based on the median of posterior samples, and uncertainty intervals, based on the quantiles of posterior samples, that enclose the 95% most plausible estimates.
 In addition, we report the posterior probability, based on the proportion of posterior samples below zero, that the mean effect size is negative.
@@
 We also conducted non-preregistered analyses to estimate to what extent moderator variables explained heterogeneity in the estimated effect sizes, to what extent meta-biases influenced the estimated effect sizes, and to what extent the three outcome variables were associated with two alternative predictor variables, ingroup contact and negative contact.
+
+## Deviations From the Preregistration
+
+Some aspects of the preregistered protocol proved unrealistic, impractical, or underspecified. Therefore, we deviated from the preregistration in the following ways:
+
+1.
+We preregistered that we would update our search every four months until we would submit the manuscript.
+This proved unrealistic as the study selection and data collection process for the new studies took almost as long.
+Instead, we concluded our search of electronic databases on April 1, 2020—that is, before we started analyzing and documenting our findings.
+
+2.
+We preregistered that we would randomly select 100 records to be screened by both coders to calculate inter-rater agreement.
+We did not specify, however, what we would do if inter-rater agreement was less than acceptable.
+We decided to refine our coding strategy over three samples of 100 records until we achieved acceptable agreement.
+
+3.
+We preregistered that we would use *Google Scholar* to find records citing eligible studies.
+This proved impractical as *Google Scholar* does not allow the electronic export of citing records.
+Instead, we used the *Scopus* citation database.
+
+4.
+We preregistered that we would attempt to contact the authors of *all* papers with missing effect sizes.
+Instead, we decided to not contact authors for studies published before 2000 as we considered it unlikely that the authors still had access to the data.
+
+5.
+We preregistered that we would use a Bayesian two-level random-effects meta-analysis model for all preregistered analyses.
+For the association between policy support and collective action, however, we had only few studies and found that the two-level model did not result in a reliable posterior distribution.
+Instead, we used a Bayesian one-level random-effects model to estimate that association.
 
@@
     median_qi(e_loo) %>% 
+    group_by(y_var) %>% 
     top_n(n = 1, wt = abs(e_loo)) %>% 
@@
 For perceived injustice (`r mad_loo$text[mad_loo$y_var == "pi"]`), collective action (`r mad_loo$text[mad_loo$y_var == "ca"]`), and policy support (`r mad_loo$text[mad_loo$y_var == "ps"]`), the *MAD* was small.
-Leaving out the most influential study, for example, did not change estimates of the mean effect size for the three outcomes (`r d_loo$text[d_loo$y_var == "pi"]`; `r d_loo$text[d_loo$y_var == "ca"]`; `r d_loo$text[d_loo$y_var == "ps"]`).
+Leaving out the most influential study, for example, did not change estimates of the mean effect sizes for the three outcomes (`r d_loo$text[d_loo$y_var == "pi"]`; `r d_loo$text[d_loo$y_var == "ca"]`; `r d_loo$text[d_loo$y_var == "ps"]`).
 These analyses showed that our findings were robust to choosing different prior distributions and to excluding influential studies.
@@
   meta_cart <- read_rds("../results/results_exploratory_moderator_analyses.rds") %>% 
-    group_by(kk, age, ic_direct, study_setting) %>% 
+    group_by(kk, ic_quality, age, study_setting) %>% 
     summarize(
       r_kk = glue("$r = {f_num(median(r), digits = 2)}, [{f_num(quantile(r, 0.025), digits = 2)}, {f_num(quantile(r, 0.975), digits = 2)}]$"),
+      p_kk = mean(r < 0),
       R2 = glue("$R^2 = {f_num(median(R2) * 100, digits = 0)}\\%$")
+    ) %>% 
+    mutate(
+      p_kk = case_when(
+        p_kk < .001 ~ "$\\Pr (r < 0) < 0.1\\%$",
+        p_kk > .999 ~ "$\\Pr (r < 0) > 99.9\\%$",
+        TRUE ~ paste0("$\\Pr (r < 0) = ", f_num(p_kk * 100, digits = 1), "\\%$")
+      )
     ) %>% 
@@
 Figure 6 shows the resulting meta-regression model, which explained more variance across samples than any individual moderator (`r with(meta_cart, unique(R2))`).
-We found that intergroup contact was associated with less perceived injustice only in studies that focused on adults and that measured intergroup contact directly.
-Among these studies, this association was stronger in settings in which the groups’ relative inequality stemmed from short-term migration or colonization (`r with(meta_cart, r_kk[4])`) than in other settings (`r with(meta_cart, r_kk[3])`).
+We found that intergroup contact was associated with less perceived injustice only in studies that measured direct, qualitatively positive contact among adults (`r with(meta_cart, r_kk[3])`) or in the few studies that did not measure direct, qualitatively positive contact but in which the groups’ relative inequality stemmed from short-term migration (`r with(meta_cart, r_kk[1])`).
 
@@
 Developing methods to detect and correct for publication bias and other meta-biases is an active area of research, with no single method outperforming all others [@carter_correcting_2019].
-Following Carter et al.’s recommendations, we compared results of several methods to adjust meta-analytic estimates for publication bias: the PET-PEESE estimator [@stanley_meta-regression_2014]; the three-parameter selection model [3PSM; @vevea_general_1995]; and the *p*-uniform* estimator [@van_aert_correcting_2018].
+Following Carter et al.’s recommendations, we compared results of several methods to adjust meta-analytic estimates for publication bias: the PET-PEESE estimator [@stanley_meta-regression_2014] adjusts meta-analytic estimates by correcting for the greater risk of smaller studies to not be published; the *p*-uniform* estimator [@van_aert_correcting_2018] adjusts meta-analytic estimates by correcting for the greater risk of non-significant effects to not be published; and the three-parameter selection model [3PSM, @vevea_general_1995] adjusts meta-analytic estimates for publication bias by estimating both the probability of a non-significant effect being published as well as the true average effect and between-study heterogeneity underlying the observed effect sizes.^[For an accessible introduction to meta bias correction, see @harrer_doing_2021.]
+
 In addition, we ran a subgroup analysis that included only studies that were not published or not conducted with the intention to examine the effects of intergroup contact on any of the outcomes—and that, therefore, can be assumed to have not been affected by publication bias.
-As these methods do not use Bayesian statistics, we compared adjusted estimates to unadjusted estimates from a random-effects meta-analysis estimated with restricted maximum likelihood estimation using the *metafor* package [@viechtbauer_conducting_2010].
+As the methods we used do not use Bayesian statistics, we compared adjusted estimates to unadjusted estimates from a random-effects meta-analysis estimated with restricted maximum likelihood estimation using the *metafor* R package [@viechtbauer_conducting_2010].
 
@@
 
-## Alternative Predictors
+## Additional Analyses
+
+```{=latex}
+\begin{figure*}[t!]
+\centering
+\caption{Posterior distributions for studies that measured direct, qualitatively positive contact among adults}
+\includegraphics[scale=1]{../figures/figure-8}
+\caption*{\textit{Note.} Black outlines show the posterior distributions from the original, preregistered analyses.
+\textbf{A} Posterior distributions for the mean correlation coefficients, highlighting the proportion of posterior samples for which $r_\text{mean} < 0$.
+\textbf{B} Posterior predictive distributions of study-wise correlation coefficients, highlighting the 80\% most common effect sizes, with point estimates for the correlation coefficients for all studies in the sample.}
+\label{fig:f8}
+\end{figure*}
+```
+
+```{r, include = FALSE}
+
+  # Import results from analyses
+  pre_results <- read_rds("../results/results_preregistered_analyses.rds")
+  add_results <- read_rds("../results/results_additional_analyses.rds")
+  add_r_pred_jj <- read_rds("../results/r_additional_analyses_pred_jj.rds")
+
+  # Merge results
+  results <- add_results %>% 
+    select(.chain:.draw, x_var, y_var, I, J, N, r_add = r_mean) %>% 
+    left_join(
+      pre_results %>% 
+        select(.chain:.draw, x_var, y_var, r_pre = r_mean),
+      by = c(".chain", ".iteration", ".draw", "x_var", "y_var")
+    ) %>% 
+    group_by(y_var) %>%
+    summarize(
+      I = f_comma(unique(I)),
+      J = f_comma(unique(J)),
+      N = f_comma(unique(N)),
+      r_median = median(r_add),
+      r_lower = quantile(r_add, 0.025),
+      r_upper = quantile(r_add, 0.975),
+      d_median = median(r_add - r_pre),
+      d_lower = quantile(r_add - r_pre, 0.025),
+      d_upper = quantile(r_add - r_pre, 0.975),
+      p_below = mean(r_add < 0)
+    ) %>% 
+    left_join(
+      add_r_pred_jj %>% 
+        filter(x_var == "ic") %>% 
+        group_by(y_var) %>% 
+        summarize(p_pred = mean(r_pred > 0)),
+      by = "y_var"
+    ) %>% 
+    mutate(
+      across(
+        c(starts_with("r_"), starts_with("d_")), 
+        ~f_num(., digits = 2)
+      ),
+      r_text = paste0("$r = ", r_median, ", [", r_lower, ", ", r_upper, "]$"),
+      d_text = paste0("$\\Delta r = ", d_median, ", [", d_lower, ", ", d_upper, "]$"),
+      p_below = case_when(
+        p_below < .001 ~ "$\\Pr (r < 0) < 0.1\\%$",
+        p_below > .999 ~ "$\\Pr (r < 0) > 99.9\\%$",
+        TRUE ~ paste0("$\\Pr (r < 0) = ", f_num(p_below * 100, digits = 1), "\\%$")
+      ),
+      p_pred = case_when(
+        p_pred < .001 ~ "$< 0.1\\%$",
+        p_pred > .999 ~ "$> 99.9\\%$",
+        TRUE ~ paste0("$", f_num(p_pred * 100, digits = 1), "\\%$")
+      )
+    )
+
+```
+
+Our moderator analyses suggested that, for perceived injustice, the evidence for the 'ironic' effect of intergroup contact was stronger in studies that measured direct, qualitatively positive contact among adults than in most other studies.
+Operationalizing intergroup contact as direct, qualitatively positive contact among adults is closer to the original argument for the 'ironic' effects of intergroup contact and, therefore, tests a stronger case for the hypothesized relationships.
+To test this stronger case, we repeated our original, preregistered analyses for studies that measured direct, qualitatively positive contact among adults.
+
+Figure 8 shows posterior distributions from these analyses.
+Across `r with(results, N[y_var == "pi"])` participants from `r with(results, I[y_var == "pi"])` samples in `r with(results, J[y_var == "pi"])` studies, we found strong evidence for a small to medium negative association between intergroup contact and perceived injustice (`r with(results, r_text[y_var == "pi"])`), an effect size that is larger than estimated in the preregistered analysis (`r with(results, d_text[y_var == "pi"])`).
+Compared to the preregistered analyses, we did not find stronger associations with collective action (`r with(results, r_text[y_var == "ca"])`, `r with(results, d_text[y_var == "ca"])`) or policy support (`r with(results, r_text[y_var == "ps"])`, `r with(results, d_text[y_var == "ps"])`) in studies that measured direct, qualitatively positive contact among adults.
+These findings are not surprising as our preregistered analyses already prioritized predictor variables that measured direct, qualitatively positive contact and as most studies on collective action and policy support included those predictor variables.
+We estimated that `r with(results, p_pred[y_var == "pi"])`, `r with(results, p_pred[y_var == "ca"])`, and `r with(results, p_pred[y_var == "ps"])` of studies that measured direct, qualitatively positive contact among adults would find *positive* associations with perceived injustice, collective action, and policy support---suggesting that, relative to the preregistered analyses, focusing on direct, qualitatively positive contact among adults reduced the variance in effect sizes across studies.
+
+## Alternative Explanations
 
@@
 \caption{Posterior distributions from the random-effects meta-analysis models with alternative predictor variables}
-\includegraphics[scale=1]{../figures/figure-8}
-\label{fig:f8}
+\includegraphics[scale=1]{../figures/figure-9}
+\label{fig:f9}
 \end{figure*}
@@
 
-We ran three random-effects meta-analysis models estimating the partial correlations of positive and negative contact with each outcome, using effect sizes from all studies that measured both predictors (Figure 8a).
+We ran three random-effects meta-analysis models estimating the partial correlations of positive and negative contact with each outcome, using effect sizes from all studies that measured both predictors (Figure 9a).
 By using partial correlations, we estimated the effect of one form of contact while controlling for the other.
@@
 
-We ran three random-effects meta-analysis models that estimated the partial correlations of ingroup and outgroup contact with each outcome, using effect sizes from all studies that measured both predictors (Figure 8b).
+We ran three random-effects meta-analysis models that estimated the partial correlations of ingroup and outgroup contact with each outcome, using effect sizes from all studies that measured both predictors (Figure 9b).
 Across `r alt_results$N[alt_results$x_var == "ig" & alt_results$y_var == "pi"]` participants from `r alt_results$I[alt_results$x_var == "ig" & alt_results$y_var == "pi"]` samples in `r alt_results$J[alt_results$x_var == "ig" & alt_results$y_var == "pi"]` studies, we found insufficient evidence for associations of ingroup contact (`r alt_results$text[alt_results$x_var == "ig" & alt_results$y_var == "pi"]`) and outgroup contact (`r alt_results$text[alt_results$x_var == "og" & alt_results$y_var == "pi"]`) with perceived injustice.
@@
 Effect sizes were thus much smaller than for the association between contact and prejudice in minority ($r = -.18$) and majority ($r = -.23$) groups [@tropp_relationships_2005].^[Comparing standardized effect sizes assumes that the two outcomes are of equal importance.
-That is not always the case: for example, a drug that reduces mild symptoms by 0.20 standard deviations is not better than a drug that reduces deaths by 0.10 standard deviations.] Small effects can still be important if they accumulate over time or across people.
+That is not always the case: for example, a drug that reduces mild symptoms by 0.20 standard deviations is not necessarily better than a drug that reduces deaths by 0.10 standard deviations.] Small effects can still be important if they accumulate over time or across people.
 For example, even a small change in policy attitudes could, if it affects enough people, sway a tight election.
@@
 A combination of moderators explained about a third of the between-study variance in the association between intergroup contact and perceived injustice.
-We found that, on average, this association was negative only in studies of adults that measured contact *directly* (e.g., by asking about the number of friends from the advantaged outgroup).
-This suggests that, as hypothesized, the 'ironic' effects result from direct contact and not from other contextual factors.
-We also found that, on average, effect sizes were greater for studies in (post-)colonial settings or on short-term migration than for studies in other contexts.
-Future research should systematically investigate variance in how contact affects support for social change across settings and cultures.
+We found the most consistent evidence for a negative association in studies that measured direct, qualitatively positive contact among adults (e.g., by asking how much time they spent with friends from the advantaged outgroup).
+This operationalization is closely aligned with, and thus supports, the original argument for the ‘ironic’ effects of intergroup contact.
+More broadly, this finding suggests that the magnitude and direction of the observed effects depends on how intergroup contact is measured.
+Like other measures of social psychological constructs [@flake_construct_2017], few measures of intergroup contact resulted from a systematic process of scale development [for an exception, see @hayward_toward_2017] or underwent a rigorous process of scale validation [for an overview, see @lolliot_measures_2015].
+Although we did not find conclusive evidence for systematic cultural differences in the 'ironic' effects of intergroup contact, we found that, like other areas of psychological research [@henrich_weirdest_2010], this area of research continues to underrepresent large parts of Africa, Asia, and South America.
+Future research should systematically investigate how contact affects support for social change across different measures, settings, and cultures.
 
@@
 
+Considering positive and negative contact helps us understand both the *reality* of contact as experienced in everyday interactions as well as the *ideal* of contact as targeted in planned interventions.
+When considering contact in planned interventions designed to promote positive contact, our findings suggest that contact-based interventions could reduce awareness of, and opposition to, social injustice in disadvantaged groups.
+This finding is consistent with the argument that intergroup contact, as a strategy to reduce prejudice, is in conflict with collective action as a strategy to effect social change [@dixon_beyond_2012; @dixon_models_2012].
+Future research on contact-based interventions should consider strategies to resolve this conflict [e.g., @2075; @2033; @hassler_need_2021; @rodriguez_engaging_2018].
+When considering contact in everyday interactions, our findings suggest that negative experiences, not positive, experiences with the advantaged affect support for social change among the disadvantaged.
+This finding is consistent with the argument that negative contact draws attention to the discrimination disadvantaged-group members faces and strengthens their resolve to challenge social injustice [see @956].
+While theoretical and methodological questions remain in the study of negative contact [@schafer_does_2021], future research should measure both forms of contact to avoid confounding the presence of positive contact with the absence of negative contact.
+
 Finally, we cannot rule out that biases in the literature caused our meta-analysis to overestimate the 'ironic' effects of intergroup contact.
@@
 Another bias that could have affected our findings is that researchers made data-dependent decisions while collecting and analyzing data that are known to inflate false-positive findings [@gelman_statistical_2014; @simmons_false-positive_2011].
-This risk is pertinent to a literature in which most studies are observational, include many measures, and are not preregistered—and, therefore, do not constrain the direction of observed associations or the selection of included variables.^[To date, only one preregistered study has been published [@3054].] Future research should use preregistration and other methods to prevent undisclosed flexibility in data collection and analysis.
+This risk is pertinent to a literature in which most studies are observational, include many measures, and are not preregistered—and, therefore, do not constrain the direction of observed associations or the selection of included variables.
+Future research should use preregistration and other methods to prevent undisclosed flexibility in data collection and analysis.
 
@@
 We did not consider whether intergroup contact might also *help* social change by reducing prejudice [for critical perspectives, see @dixon_beyond_2012; @jackman_velvet_1994] or by motivating the advantaged to acknowledge and challenge social inequality [@tropp_making_2018].
-Further, we did not consider contact between different disadvantaged groups, which has been found to increase support for social change among the disadvantaged [@dixon_divide_2015; @93].
+Likewise, we did not test whether, in certain conditions, positive contact with advantaged-group members might *increase* support for social change in disadvantaged groups.
+For example, studies found positive intergroup contact to increase collective action intentions when advantaged-group members acknowledged intergroup injustice as illegitimate [@2075] or expressed support for social change [@2033].
+More broadly, intergroup contact is associated with more support for social change if it satisfies disadvantaged-group members' need for empowerment, that is, when they felt that the advantaged-group members they had contact with listened to what they had to say and perceived them as competent and intelligent [@hassler_need_2021].^[We did not consider whether, in certain conditions, positive contact might increase support for social change in disadvantaged groups because only few studies measured the relevant moderator variables and because our analyses relied on correlation matrices which are not enough to estimate interaction effects.
+For the latter reason, we also did not consider whether positive and negative contact might interact in their effects on support for social change [see @albzour_talking_inpress].] Further, we did not consider contact between different disadvantaged groups, which has been found to increase support for social change among the disadvantaged [@dixon_divide_2015; @93].
 Therefore, this meta-analysis could not provide a complete answer to the question whether, on balance, intergroup contact helps or hinders social change.
@@
 To conclude, our preregistered meta-analysis found some evidence that intergroup contact reduces perceived injustice, discourages collective action, and diminishes support for reparative policies in disadvantaged groups—but also showed that the estimated effect sizes were small, variable, and consistent with alternative explanations.
-Future research should (1) compare the direction and magnitude of the associations between intergroup contact and support for social change across cultures, groups, and issues; (2) use longitudinal designs and field experiments to establish the direction of these relationships and to rule out spurious associations; (3) include measures that allow testing alternative explanations for the apparent 'ironic' effects of intergroup contact; and (4) incorporate practices to prevent undisclosed flexibility in data collection and analysis.
+Future research should (1) compare the direction and magnitude of the associations between intergroup contact and support for social change across cultures, groups, and issues; (2) use longitudinal designs and field experiments to establish the direction of these relationships and to rule out spurious associations; (3) include validated measures that allow testing alternative explanations for the apparent 'ironic' effects of intergroup contact; and (4) incorporate practices to prevent undisclosed flexibility in data collection and analysis.
 We hope that our meta-analysis helps researchers to address the open questions about how intergroup contact relates to support for social change in disadvantaged groups.

### 2022-02-17 manuscript/manuscript.tex
revision

@@
 \usepackage[letterpaper, margin = 1in]{geometry}
-\setlength{\columnsep}{18pt}
 \setcounter{secnumdepth}{0}
+\setlength{\parindent}{0.5in}
 \usepackage[compact]{titlesec}
-\titleformat*{\section}{\centering\normalfont\Large\bfseries}
-\usepackage{authblk}
-\renewcommand\Affilfont{\small}
-\newcommand{\refsection}{\section{References}}
+\titleformat*{\section}{\centering\normalfont\normalsize\bfseries}
+\titleformat*{\subsection}{\raggedright\normalfont\normalsize\bfseries}
+\titleformat*{\subsubsection}{\raggedright\normalfont\normalsize\bfseries\itshape}
+\newcommand{\refsection}{\newpage \section{References}}
+\usepackage{indentfirst}
+\usepackage[hang,flushmargin]{footmisc}
 \providecommand{\tightlist}{\setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
+
+% Header
+\usepackage{fancyhdr}
+\pagestyle{fancy}
+\fancyhf{}
+\setlength{\headheight}{14.5pt}
+\renewcommand{\headrulewidth}{0pt}
+\fancyhead[L]{`IRONIC' EFFECTS META-ANALYSIS}
+\fancyhead[R]{\thepage}
 
@@
 % References
-\newlength{\cslhangindent}
-\setlength{\cslhangindent}{1.5em}
-\newenvironment{CSLReferences}%
-  {}%
-  {\par}
+\newenvironment{CSLReferences}[2]{}{}
+
+% Line spacing
+\usepackage[doublespacing]{setspace}
 
 % Frontmatter
-\title{ Meta-Analysis of the `Ironic' Effects of Intergroup
-Contact\thanks{} }
-\author[1]{Nils K. Reimer}
-\author[2]{Nikhil K. Sengupta}
-\affil[1]{University of Southern California, Los Angeles, United States}
-\affil[2]{University of Kent, Canterbury, United Kingdom}
-\date{June 15, 2021}
+\title{ Meta-Analysis of the `Ironic' Effects of Intergroup Contact }
 
@@
 
-\twocolumn[
-  \begin{@twocolumnfalse}
-    \maketitle
-    \begin{abstract}
+\section{Abstract}
+
 \noindent Growing evidence suggests that intergroup contact,
@@
 \emph{positive} associations with intergroup contact. Moderator analyses
-explained about a third of the between-sample variance, showing that, on
-average, associations were negative only in studies of adults that
-measured intergroup contact directly and were strongest in studies that
-examined short-term migration or (post-)colonial intergroup relations.
-We also found evidence for an alternative explanation for the apparent
-`ironic' effects of intergroup contact as, after controlling for the
-positive association of negative contact with support for social change,
-positive contact was no longer associated with any of the outcomes. We
-close by discussing strengths and limitations of the available evidence
-and by highlighting open questions about the relationship between
-intergroup contact and support for social change in disadvantaged
-groups.
-    \end{abstract}
-  \end{@twocolumnfalse}
-  % \renewcommand{\abstractname}{Statement of Relevance}
-  % \begin{@twocolumnfalse}
-  %   \maketitle
-  %   \begin{abstract}
-  %   \noindent 
-  %   \end{abstract}
-  % \end{@twocolumnfalse}
-]
-
-{
-  \renewcommand{\thefootnote}%
-    {\fnsymbol{footnote}}
-  \footnotetext[1]{Manuscript under review.}
-}
-
-\noindent It is ironic that psychology's most-researched paradigm for
-reducing prejudice---intergroup contact---should hinder, rather than
-help, social change. Hundreds of studies have confirmed that intergroup
-contact is associated with less negative feelings toward outgroup
-members (for a meta-analysis, see Pettigrew \& Tropp, 2006). Most of
-these studies have focused on advantaged-group members' contact
-experiences with disadvantaged-group members (L. R. Tropp \& Pettigrew,
-2005), guided by the idea that reducing advantaged-group members'
-prejudice will prevent interpersonal discrimination. Reducing prejudice,
-however, is rarely enough to overcome institutional and structural
-discrimination. Instead, as the 2020 Black Lives Matter protests have
-shown, social change often requires political mobilization by the
-disadvantaged. Critics have argued that, by fostering harmony and
-reducing conflict, intergroup contact might distract disadvantaged-group
-members from the injustice they face and, thereby, undermine their
-motivation for social change (Dixon et al., 2005; Reicher, 2007; Wright,
-2003). By reducing disadvantaged-group members' opposition to injustice,
-intergroup contact might thus have the `ironic' (Saguy et al., 2009),
-`sedative' (Çakal et al., 2011), or `paradoxical' (Dixon et al., 2010)
-effect of hindering social change.
+explained about a third of the between-sample variance, showing that, at
+least for perceived injustice, associations with intergroup contact were
+most consistently negative in studies that measured direct,
+qualitatively positive contact among adults. We also found evidence for
+an alternative explanation for the apparent `ironic' effects of
+intergroup contact as, after controlling for the positive association of
+negative contact with support for social change, positive contact was no
+longer associated with any of the outcomes. We close by discussing
+strengths and limitations of the available evidence and by highlighting
+open questions about the relationship between intergroup contact and
+support for social change in disadvantaged groups.
+
+\textit{Keywords:} intergroup contact, meta-analysis, perceived
+discrimination, collective action, policy support
+
+\newpage
+
+\section{Meta-Analysis of the `Ironic' Effects of Intergroup Contact}
+
+It is ironic that psychology's most-researched paradigm for reducing
+prejudice---intergroup contact---should hinder, rather than help, social
+change. Hundreds of studies have confirmed that intergroup contact is
+associated with less negative feelings toward outgroup members (for a
+meta-analysis, see Pettigrew \& Tropp, 2006). Most of these studies have
+focused on advantaged-group members' contact experiences with
+disadvantaged-group members (Tropp \& Pettigrew, 2005), guided by the
+idea that reducing advantaged-group members' prejudice will prevent
+interpersonal discrimination. Reducing prejudice, however, is rarely
+enough to overcome institutional and structural discrimination. Instead,
+as the 2020 Black Lives Matter protests have shown, social change often
+requires political mobilization by the disadvantaged. Critics have
+argued that, by fostering harmony and reducing conflict, intergroup
+contact might distract disadvantaged-group members from the injustice
+they face and, thereby, undermine their motivation for social change
+(Dixon et al., 2005; Reicher, 2007; Wright, 2003). By reducing
+disadvantaged-group members' opposition to injustice, intergroup contact
+might thus have the `ironic' (Saguy et al., 2009), `sedative' (Çakal et
+al., 2011), or `paradoxical' (Dixon et al., 2010) effect of hindering
+social change.
 
@@
 discourage disadvantaged-group members from engaging in collective
-action by diminishing their perceived discrimination (Linda R. Tropp et
-al., 2012), by blurring boundaries between the disadvantaged ingroup and
-the advantaged outgroup (Saguy et al., 2009), by reducing negative
-attitudes toward the advantaged outgroup (Wright \& Lubensky, 2009), and
-by quelling their anger (Hayward et al., 2018; Tausch et al., 2015). To
-the extent that it discourages collective action, intergroup contact
-reduces support for social change.
+action by diminishing their perceived discrimination (Tropp et al.,
+2012), by reducing the perceived threat from the advantaged outgroup
+(Çakal et al., 2016), by blurring boundaries between the disadvantaged
+ingroup and the advantaged outgroup (Saguy et al., 2009), by reducing
+negative attitudes toward the advantaged outgroup (Wright \& Lubensky,
+2009), and by quelling their anger (Hayward et al., 2018; Tausch et al.,
+2015). To the extent that it discourages collective action, intergroup
+contact reduces support for social change.
 
@@
 
-While narrative reviews of the growing literature on this topic have
-been published (Hässler et al., 2021; MacInnis \& Hodson, 2019; McKeown
-\& Dixon, 2017), we present the first systematic review and
-meta-analysis of the relationship between intergroup contact and support
-for social change in disadvantaged groups. To test the hypothesized
-`ironic' effects of intergroup contact, we evaluate the evidence that
-contact with advantaged-group members reduces disadvantaged-group
-members' perceived injustice, collective action, and support for
-reparative policies.
+As a result of two recent developments, there is now an emerging
+consensus that, in line with the former argument, intergroup contact has
+the `ironic' effect of undermining support for social change in
+disadvantaged groups. First, a large-scale preregistered multi-country
+study provided the most comprehensive evidence to date that contact with
+advantaged groups correlates with less support for social change in
+disadvantaged groups (Hässler et al., 2020). Second, several narrative
+reviews of the growing evidence for the `ironic' effects of intergroup
+contact have been published (Hässler, Uluğ, et al., 2021; MacInnis \&
+Hodson, 2019; McKeown \& Dixon, 2017). Narrative reviews do not,
+however, include all relevant studies and do not synthesize the,
+sometimes conflicting, findings of different studies. We present the
+first systematic review and meta-analysis of the relationship between
+intergroup contact and support for social change in disadvantaged
+groups. To test the hypothesized `ironic' effects of intergroup contact,
+we evaluate the evidence that contact with advantaged-group members
+reduces disadvantaged-group members' perceived injustice, collective
+action, and support for reparative policies.
 
@@
 outcomes. Doing so allowed us to determine whether the available
-evidence supports a negative or positive (see Pettigrew et al., 2011)
-relationship between contact and support for social change and to
-estimate the strength of this relationship. Our third objective was to
-estimate and explain the variability of this relationship across study
-settings, designs, and other potential moderators. For example, we
-examined whether any effects were confined to Western, Educated,
-Industrialized, Rich, Democratic (WEIRD) countries, the cultural context
-of most psychological research (Henrich et al., 2010). Our fourth
-objective was to assess how robust the available evidence was to
-publication bias. Our final objective was to explore the available
-evidence for negative contact and ingroup contact as alternative
-explanations of the apparent `ironic' effects of intergroup contact.
+evidence supports a negative or positive direct relationship between
+contact and support for social change and to estimate the strength of
+this relationship. Our third objective was to estimate and explain the
+variability of this relationship across study settings, designs, and
+other potential moderators. For example, we examined whether any effects
+were confined to Western, Educated, Industrialized, Rich, Democratic
+(WEIRD) countries, the cultural context of most psychological research
+(Henrich et al., 2010). Our fourth objective was to assess how robust
+the available evidence was to publication bias. Our final objective was
+to explore the available evidence for negative contact and ingroup
+contact as alternative explanations of the apparent `ironic' effects of
+intergroup contact.
+
+In pursuing these objectives, we focus on the direct relationships of
+intergroup contact with perceived injustice, collective action, and
+support for reparative policies in disadvantaged groups. We do not
+consider indirect and interaction effects or the effects of imagined,
+extended, or parasocial contact. Further, while the argument for the
+`ironic' effects of intergroup contact is part of a broader critique of
+the prejudice reduction model of social change (for a review, see Dixon
+et al., 2012), our meta-analysis tests the narrower hypothesis whether
+intergroup contact reduces support for social change in disadvantaged
+groups.
 
@@
 et al., 2015) and preregistered it on the Open Science
-Framework.\footnote{\url{https://osf.io/ryuev/?view_only=8938ac6178914da98bdda1da4a6e27f0}}
-Preregistration precludes undisclosed flexibility in study selection,
-outcome selection, and other decisions that influence effect size
-estimates---and thus prevents confirmation bias from determining the
-conclusions of a meta-analysis (Lakens et al., 2016). We report
-deviations from our protocol in the Supplemental Online Material (SOM).
-We make data, analysis scripts, and the fully reproducible manuscript
-available online.\footnote{\url{https://osf.io/w5tqv/?view_only=5cbf7ad5b2b449a7a0f4ada0337b802a}}
+Framework.\footnote{\url{https://osf.io/ryuev}} Preregistration
+precludes undisclosed flexibility in study selection, outcome selection,
+and other decisions that influence effect size estimates---and thus
+prevents confirmation bias from determining the conclusions of a
+meta-analysis (Lakens et al., 2016). We report deviations from our
+preregistered protocol at the end of the Method section. We make data,
+analysis scripts, and the fully reproducible manuscript available
+online.\footnote{\url{https://osf.io/w5tqv}}
 
@@
 2020. We exported records and relevant metadata from each database. We
-removed duplicates using the \emph{revtools} package (Westgate, 2019).
+removed duplicates using the \emph{revtools} R package (Westgate, 2019).
 
@@
 
-\hypertarget{outcomes-selection}{%
-\subsubsection{Outcomes Selection}\label{outcomes-selection}}
+\hypertarget{outcome-selection}{%
+\subsubsection{Outcome Selection}\label{outcome-selection}}
 
@@
 (e.g., Black Americans), colonization (e.g., Māori, Black South
-Africans), religion, caste, sexuality, or another distinction
-(\(\kappa = .85\)).
+Africans), religion, caste, sexual/gender identity, or another
+distinction (\(\kappa = .85\); see SOM for details).
 
@@
 quasi-experimental, experimental, an intervention, or other
-(\(\kappa = .85\)). We categorized each sample as either a student
-convenience sample, a non-student convenience sample, a probability or
-representative sample, or another kind of sample (\(\kappa = .73\)). We
-categorized the age group(s) in each sample as children (\(\leq 12\)
-years), adolescents (13--18 years), or adults (\(\geq 18\) years;
-\(\kappa = .64\)).
+(\(\kappa = .85\)).\footnote{While the term `observational study' is
+  sometimes used to refer to the naturalistic observation of behavior,
+  we use it in its broader sense, that is, to refer to studies that do
+  not involve random assignment into experimental conditions (Cochran,
+  1965; Rosenbaum, 2005).} We categorized each sample as either a
+student convenience sample, a non-student convenience sample, a
+probability or representative sample, or another kind of sample
+(\(\kappa = .73\)). We categorized the age group(s) in each sample as
+children (\(\leq 12\) years), adolescents (13--18 years), or adults
+(\(\geq 18\) years; \(\kappa = .64\)).
 
@@
 friends were not from the participants' ingroup or what proportion of
-residents in someone's neighbourhood were from the relevant outgroup
-(\(\kappa = .82\)).
+residents in someone's neighborhood were from the relevant outgroup
+(\(\kappa = .82\)). In addition, we coded whether each predictor
+variable assessed direct, qualitatively positive intergroup contact by,
+for example, measuring contact quality or cross-group friendship with
+the advantaged outgroup(\(\kappa = .82\)).\footnote{We thank John Dixon
+  for his suggestion to consider the distinction between contact
+  quantity and quality in our analyses. As we added this moderator
+  during peer review and as doing so changed the results of our
+  moderator analyses, we report our original findings in the SOM.}
 
@@
 
-We estimated effect sizes using Bayesian random-effects meta-analysis
-models in \emph{RStan} (Stan Development Team, 2020) which modeled the
+We estimated effect sizes with Bayesian random-effects meta-analysis
+models, using the \emph{RStan} package (Stan Development Team, 2021) for
+the R programming language (R Core Team, 2021), which modeled the
 \emph{z}-transformed correlation coefficients with a normal likelihood
@@
 interpretation as stating how plausible different values of the model
-parameters are given the observed data. We report point estimates, based
+parameters are given the observed data.\footnote{For an accessible
+  introduction, see McElreath (2020).} We report point estimates, based
 on the median of posterior samples, and uncertainty intervals, based on
@@
 alternative predictor variables, ingroup contact and negative contact.
+
+\hypertarget{deviations-from-the-preregistration}{%
+\subsection{Deviations From the
+Preregistration}\label{deviations-from-the-preregistration}}
+
+Some aspects of the preregistered protocol proved unrealistic,
+impractical, or underspecified. Therefore, we deviated from the
+preregistration in the following ways:
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
+\item
+  We preregistered that we would update our search every four months
+  until we would submit the manuscript. This proved unrealistic as the
+  study selection and data collection process for the new studies took
+  almost as long. Instead, we concluded our search of electronic
+  databases on April 1, 2020---that is, before we started analyzing and
+  documenting our findings.
+\item
+  We preregistered that we would randomly select 100 records to be
+  screened by both coders to calculate inter-rater agreement. We did not
+  specify, however, what we would do if inter-rater agreement was less
+  than acceptable. We decided to refine our coding strategy over three
+  samples of 100 records until we achieved acceptable agreement.
+\item
+  We preregistered that we would use \emph{Google Scholar} to find
+  records citing eligible studies. This proved impractical as
+  \emph{Google Scholar} does not allow the electronic export of citing
+  records. Instead, we used the \emph{Scopus} citation database.
+\item
+  We preregistered that we would attempt to contact the authors of
+  \emph{all} papers with missing effect sizes. Instead, we decided to
+  not contact authors for studies published before 2000 as we considered
+  it unlikely that the authors still had access to the data.
+\item
+  We preregistered that we would use a Bayesian two-level random-effects
+  meta-analysis model for all preregistered analyses. For the
+  association between policy support and collective action, however, we
+  had only few studies and found that the two-level model did not result
+  in a reliable posterior distribution. Instead, we used a Bayesian
+  one-level random-effects model to estimate that association.
+\end{enumerate}
 
@@
 for perceived injustice (\(\Delta r = -.00, [-.05, .04]\) and
-\(\Delta r = .00, [-.05, .05]\)), collective action
-(\(\Delta r = -.01, [-.11, .09]\) and \(\Delta r = .00, [-.11, .10]\)),
-and policy support (\(\Delta r = -.01, [-.10, .08]\) and
+\(\Delta r = .00, [-.04, .05]\)), collective action
+(\(\Delta r = -.00, [-.10, .10]\) and \(\Delta r = .00, [-.10, .11]\)),
+and policy support (\(\Delta r = -.00, [-.10, .09]\) and
 \(\Delta r = .00, [-.09, .10]\)). Second, we assessed to what extent our
@@
 (\(\textit{MAD} = .04, [.02, .09]\)), and policy support
-(\(\textit{MAD} = .03, [.02, .08]\)), the \emph{MAD} was small. Leaving
+(\(\textit{MAD} = .03, [.02, .09]\)), the \emph{MAD} was small. Leaving
 out the most influential study, for example, did not change estimates of
-the mean effect size for the three outcomes
-(\(\Delta r = -.00, [-.05, .04]\); \(\Delta r = .02, [-.08, .12]\);
-\(\Delta r = -.02, [-.11, .07]\)). These analyses showed that our
+the mean effect sizes for the three outcomes
+(\(\Delta r = .01, [-.04, .05]\); \(\Delta r = .02, [-.09, .11]\);
+\(\Delta r = -.02, [-.10, .08]\)). These analyses showed that our
 findings were robust to choosing different prior distributions and to
@@
 \includegraphics[scale=1]{../figures/figure-5}
-\caption*{\textit{Note.} We had data from too few countries to reach firm conclusions about the direction of these associations for perceived injustice ($\beta = -0.38, [-1.45, 0.72]$; $\Pr (\beta < 0) = 75.7\%$), collective action ($\beta = -0.09, [-1.60, 1.37]$; $\Pr (\beta < 0) = 55.1\%$), and policy support ($\beta = -0.92, [-2.13, 0.55]$; $\Pr (\beta < 0) = 90.3\%$).}
+\caption*{\textit{Note.} We had data from too few countries to reach firm conclusions about the direction of these associations for perceived injustice ($\beta = -0.39, [-1.47, 0.77]$; $\Pr (\beta < 0) = 75.4\%$), collective action ($\beta = -0.08, [-1.53, 1.40]$; $\Pr (\beta < 0) = 54.8\%$), and policy support ($\beta = -0.89, [-2.10, 0.67]$; $\Pr (\beta < 0) = 88.9\%$).}
 \label{fig:f5}
@@
 across samples. As Figure 4 shows, we found that the setting of the
-study (\(R^2 = 20\%\)), participants' age group (\(R^2 = 11\%\)), and
+study (\(R^2 = 21\%\)), participants' age group (\(R^2 = 12\%\)), and
 whether intergroup contact was measured directly or indirectly
@@
 model, which explained more variance across samples than any individual
-moderator (\(R^2 = 31\%\)). We found that intergroup contact was
-associated with less perceived injustice only in studies that focused on
-adults and that measured intergroup contact directly. Among these
-studies, this association was stronger in settings in which the groups'
-relative inequality stemmed from short-term migration or colonization
-(\(r = -.18, [-.23, -.13]\)) than in other settings
-(\(r = -.09, [-.13, -.06]\)).
+moderator (\(R^2 = 37\%\)). We found that intergroup contact was
+associated with less perceived injustice only in studies that measured
+direct, qualitatively positive contact among adults
+(\(r = -.12, [-.16, -.09]\)) or in the few studies that did not measure
+direct, qualitatively positive contact but in which the groups' relative
+inequality stemmed from short-term migration
+(\(r = -.23, [-.31, -.16]\)).
 
@@
 meta-analytic estimates for publication bias: the PET-PEESE estimator
-(Stanley \& Doucouliagos, 2014); the three-parameter selection model
-{[}3PSM; Vevea \& Hedges (1995){]}; and the \emph{p}-uniform* estimator
-(van Aert \& Assen, 2018). In addition, we ran a subgroup analysis that
-included only studies that were not published or not conducted with the
-intention to examine the effects of intergroup contact on any of the
-outcomes---and that, therefore, can be assumed to have not been affected
-by publication bias. As these methods do not use Bayesian statistics, we
-compared adjusted estimates to unadjusted estimates from a
-random-effects meta-analysis estimated with restricted maximum
-likelihood estimation using the \emph{metafor} package (Viechtbauer,
-2010).
+(Stanley \& Doucouliagos, 2014) adjusts meta-analytic estimates by
+correcting for the greater risk of smaller studies to not be published;
+the \emph{p}-uniform* estimator (van Aert \& Assen, 2018) adjusts
+meta-analytic estimates by correcting for the greater risk of
+non-significant effects to not be published; and the three-parameter
+selection model (3PSM, Vevea \& Hedges, 1995) adjusts meta-analytic
+estimates for publication bias by estimating both the probability of a
+non-significant effect being published as well as the true average
+effect and between-study heterogeneity underlying the observed effect
+sizes.\footnote{For an accessible introduction to meta bias correction,
+  see Harrer et al. (2021).}
+
+In addition, we ran a subgroup analysis that included only studies that
+were not published or not conducted with the intention to examine the
+effects of intergroup contact on any of the outcomes---and that,
+therefore, can be assumed to have not been affected by publication bias.
+As the methods we used do not use Bayesian statistics, we compared
+adjusted estimates to unadjusted estimates from a random-effects
+meta-analysis estimated with restricted maximum likelihood estimation
+using the \emph{metafor} R package (Viechtbauer, 2010).
 
@@
 
-\hypertarget{alternative-predictors}{%
-\subsection{Alternative Predictors}\label{alternative-predictors}}
+\hypertarget{additional-analyses}{%
+\subsection{Additional Analyses}\label{additional-analyses}}
+
+\begin{figure*}[t!]
+\centering
+\caption{Posterior distributions for studies that measured direct, qualitatively positive contact among adults}
+\includegraphics[scale=1]{../figures/figure-8}
+\caption*{\textit{Note.} Black outlines show the posterior distributions from the original, preregistered analyses.
+\textbf{A} Posterior distributions for the mean correlation coefficients, highlighting the proportion of posterior samples for which $r_\text{mean} < 0$.
+\textbf{B} Posterior predictive distributions of study-wise correlation coefficients, highlighting the 80\% most common effect sizes, with point estimates for the correlation coefficients for all studies in the sample.}
+\label{fig:f8}
+\end{figure*}
+
+Our moderator analyses suggested that, for perceived injustice, the
+evidence for the `ironic' effect of intergroup contact was stronger in
+studies that measured direct, qualitatively positive contact among
+adults than in most other studies. Operationalizing intergroup contact
+as direct, qualitatively positive contact among adults is closer to the
+original argument for the `ironic' effects of intergroup contact and,
+therefore, tests a stronger case for the hypothesized relationships. To
+test this stronger case, we repeated our original, preregistered
+analyses for studies that measured direct, qualitatively positive
+contact among adults.
+
+Figure 8 shows posterior distributions from these analyses. Across
+122,725 participants from 59 samples in 39 studies, we found strong
+evidence for a small to medium negative association between intergroup
+contact and perceived injustice (\(r = -.13, [-.17, -.09]\)), an effect
+size that is larger than estimated in the preregistered analysis
+(\(\Delta r = -.06, [-.11, -.00]\)). Compared to the preregistered
+analyses, we did not find stronger associations with collective action
+(\(r = -.08, [-.16, .01]\), \(\Delta r = -.02, [-.13, .09]\)) or policy
+support (\(r = -.10, [-.17, -.03]\), \(\Delta r = -.03, [-.12, .07]\))
+in studies that measured direct, qualitatively positive contact among
+adults. These findings are not surprising as our preregistered analyses
+already prioritized predictor variables that measured direct,
+qualitatively positive contact and as most studies on collective action
+and policy support included those predictor variables. We estimated that
+\(13.1\%\), \(29.3\%\), and \(13.2\%\) of studies that measured direct,
+qualitatively positive contact among adults would find \emph{positive}
+associations with perceived injustice, collective action, and policy
+support---suggesting that, relative to the preregistered analyses,
+focusing on direct, qualitatively positive contact among adults reduced
+the variance in effect sizes across studies.
+
+\hypertarget{alternative-explanations}{%
+\subsection{Alternative Explanations}\label{alternative-explanations}}
 
@@
 correlations of positive and negative contact with each outcome, using
-effect sizes from all studies that measured both predictors (Figure 8a).
+effect sizes from all studies that measured both predictors (Figure 9a).
 By using partial correlations, we estimated the effect of one form of
@@
 positive association between negative contact and perceived injustice
-(\(r = .14, [.06, .23]\); \(\Pr (r > 0) = 99.9\%\)) than for a negative
+(\(r = .14, [.06, .23]\); \(\Pr (r > 0) > 99.9\%\)) than for a negative
 association between positive contact and perceived injustice
-(\(r = -.05, [-.10, .01]\); \(\Pr (r < 0) = 95.6\%\)). Across 107,451
+(\(r = -.05, [-.11, .01]\); \(\Pr (r < 0) = 95.4\%\)). Across 107,451
 participants from 16 samples in 9 studies, we again found stronger
@@
 evidence for a positive association between negative contact and policy
-support (\(r = .04, [.00, .07]\); \(\Pr (r > 0) = 98.3\%\)) than for a
+support (\(r = .04, [.01, .07]\); \(\Pr (r > 0) = 98.5\%\)) than for a
 negative association between positive contact and policy support
-(\(r = .03, [-.03, .10]\); \(\Pr (r < 0) = 12.7\%\)). Across 111,153
+(\(r = .03, [-.03, .10]\); \(\Pr (r < 0) = 12.2\%\)). Across 111,153
 participants from 31 samples in 18 studies, we found a negative
 association between positive and negative contact
-(\(r = -.16, [-.25, -.07]\); \(\Pr (r < 0) = 99.8\%\)).
+(\(r = -.16, [-.25, -.07]\); \(\Pr (r < 0) = 99.9\%\)).
 
@@
 using effect sizes from all studies that measured both predictors
-(Figure 8b). Across 6,888 participants from 15 samples in 8 studies, we
+(Figure 9b). Across 6,888 participants from 15 samples in 8 studies, we
 found insufficient evidence for associations of ingroup contact
-(\(r = .03, [-.10, .15]\); \(\Pr (r > 0) = 69.0\%\)) and outgroup
-contact (\(r = -.10, [-.26, .07]\); \(\Pr (r < 0) = 89.2\%\)) with
+(\(r = .03, [-.10, .15]\); \(\Pr (r > 0) = 68.9\%\)) and outgroup
+contact (\(r = -.09, [-.25, .08]\); \(\Pr (r < 0) = 87.9\%\)) with
 perceived injustice. Across 3,938 participants from 4 samples in 2
 studies, we found stronger evidence for a positive association between
-ingroup contact and collective action (\(r = .12, [.03, .20]\);
-\(\Pr (r > 0) = 99.1\%\)) than for a negative association between
+ingroup contact and collective action (\(r = .12, [.04, .19]\);
+\(\Pr (r > 0) = 99.0\%\)) than for a negative association between
 outgroup contact and collective action (\(r = -.08, [-.25, .10]\);
-\(\Pr (r < 0) = 85.5\%\)). Across 3,187 participants from 3 samples in 1
+\(\Pr (r < 0) = 85.2\%\)). Across 3,187 participants from 3 samples in 1
 study, we found insufficient evidence for associations of ingroup
-contact (\(r = .09, [-.13, .27]\); \(\Pr (r > 0) = 86.2\%\)) and
-outgroup contact (\(r = -.03, [-.12, .08]\); \(\Pr (r < 0) = 78.5\%\))
+contact (\(r = .09, [-.14, .27]\); \(\Pr (r > 0) = 85.7\%\)) and
+outgroup contact (\(r = -.02, [-.12, .08]\); \(\Pr (r < 0) = 77.7\%\))
 with policy support. Across 6,888 participants from 15 samples in 8
 studies, we found a positive association between ingroup and outgroup
-contact (\(r = .25, [.10, .34]\); \(\Pr (r > 0) = 99.7\%\)).
+contact (\(r = .25, [.09, .34]\); \(\Pr (r > 0) = 99.7\%\)).
 
@@
 thus much smaller than for the association between contact and prejudice
-in minority (\(r = -.18\)) and majority (\(r = -.23\)) groups (L. R.
-Tropp \& Pettigrew, 2005).\footnote{Comparing standardized effect sizes
-  assumes that the two outcomes are of equal importance. That is not
-  always the case: for example, a drug that reduces mild symptoms by
-  0.20 standard deviations is not better than a drug that reduces deaths
+in minority (\(r = -.18\)) and majority (\(r = -.23\)) groups (Tropp \&
+Pettigrew, 2005).\footnote{Comparing standardized effect sizes assumes
+  that the two outcomes are of equal importance. That is not always the
+  case: for example, a drug that reduces mild symptoms by 0.20 standard
+  deviations is not necessarily better than a drug that reduces deaths
   by 0.10 standard deviations.} Small effects can still be important if
@@
 variance in the association between intergroup contact and perceived
-injustice. We found that, on average, this association was negative only
-in studies of adults that measured contact \emph{directly} (e.g., by
-asking about the number of friends from the advantaged outgroup). This
-suggests that, as hypothesized, the `ironic' effects result from direct
-contact and not from other contextual factors. We also found that, on
-average, effect sizes were greater for studies in (post-)colonial
-settings or on short-term migration than for studies in other contexts.
-Future research should systematically investigate variance in how
-contact affects support for social change across settings and cultures.
+injustice. We found the most consistent evidence for a negative
+association in studies that measured direct, qualitatively positive
+contact among adults (e.g., by asking how much time they spent with
+friends from the advantaged outgroup). This operationalization is
+closely aligned with, and thus supports, the original argument for the
+`ironic' effects of intergroup contact. More broadly, this finding
+suggests that the magnitude and direction of the observed effects
+depends on how intergroup contact is measured. Like other measures of
+social psychological constructs (Flake et al., 2017), few measures of
+intergroup contact resulted from a systematic process of scale
+development (for an exception, see Hayward, Tropp, et al., 2017) or
+underwent a rigorous process of scale validation (for an overview, see
+Lolliot et al., 2015). Although we did not find conclusive evidence for
+systematic cultural differences in the `ironic' effects of intergroup
+contact, we found that, like other areas of psychological research
+(Henrich et al., 2010), this area of research continues to
+underrepresent large parts of Africa, Asia, and South America. Future
+research should systematically investigate how contact affects support
+for social change across different measures, settings, and cultures.
 
@@
   three longitudinal studies (Koschate et al., 2012; Reimer et al.,
-  2017; Linda R. Tropp et al., 2012), all of which conflated
-  within-person change and between-person stability (Hamaker et al.,
-  2015), two experimental studies with a no-contact control condition
-  (Becker et al., 2013; Droogendyk et al., 2016), and two intervention
-  studies (Reimer et al., 2021; Shani \& Boehnke, 2017).}
+  2017; Tropp et al., 2012), all of which conflated within-person change
+  and between-person stability (Hamaker et al., 2015), two experimental
+  studies with a no-contact control condition (Becker et al., 2013;
+  Droogendyk et al., 2016), and two intervention studies (Reimer et al.,
+  2021; Shani \& Boehnke, 2017).}
 
@@
 hypothesized and competing explanations.
+
+Considering positive and negative contact helps us understand both the
+\emph{reality} of contact as experienced in everyday interactions as
+well as the \emph{ideal} of contact as targeted in planned
+interventions. When considering contact in planned interventions
+designed to promote positive contact, our findings suggest that
+contact-based interventions could reduce awareness of, and opposition
+to, social injustice in disadvantaged groups. This finding is consistent
+with the argument that intergroup contact, as a strategy to reduce
+prejudice, is in conflict with collective action as a strategy to effect
+social change (Dixon et al., 2012; Wright \& Baray, 2012). Future
+research on contact-based interventions should consider strategies to
+resolve this conflict (e.g., Becker et al., 2013; Droogendyk et al.,
+2016; Hässler, Ullrich, et al., 2021; Rodríguez et al., 2018). When
+considering contact in everyday interactions, our findings suggest that
+negative experiences, not positive, experiences with the advantaged
+affect support for social change among the disadvantaged. This finding
+is consistent with the argument that negative contact draws attention to
+the discrimination disadvantaged-group members faces and strengthens
+their resolve to challenge social injustice (see Reimer et al., 2017).
+While theoretical and methodological questions remain in the study of
+negative contact (Schäfer et al., 2021), future research should measure
+both forms of contact to avoid confounding the presence of positive
+contact with the absence of negative contact.
 
@@
 therefore, do not constrain the direction of observed associations or
-the selection of included variables.\footnote{To date, only one
-  preregistered study has been published (Hässler et al., 2020).} Future
-research should use preregistration and other methods to prevent
-undisclosed flexibility in data collection and analysis.
+the selection of included variables. Future research should use
+preregistration and other methods to prevent undisclosed flexibility in
+data collection and analysis.
 
@@
 Dixon et al., 2012; Jackman, 1994) or by motivating the advantaged to
-acknowledge and challenge social inequality (Linda R. Tropp \& Barlow,
-2018). Further, we did not consider contact between different
-disadvantaged groups, which has been found to increase support for
-social change among the disadvantaged (Dixon et al., 2015, 2017).
-Therefore, this meta-analysis could not provide a complete answer to the
-question whether, on balance, intergroup contact helps or hinders social
-change.
+acknowledge and challenge social inequality (Tropp \& Barlow, 2018).
+Likewise, we did not test whether, in certain conditions, positive
+contact with advantaged-group members might \emph{increase} support for
+social change in disadvantaged groups. For example, studies found
+positive intergroup contact to increase collective action intentions
+when advantaged-group members acknowledged intergroup injustice as
+illegitimate (Becker et al., 2013) or expressed support for social
+change (Droogendyk et al., 2016). More broadly, intergroup contact is
+associated with more support for social change if it satisfies
+disadvantaged-group members' need for empowerment, that is, when they
+felt that the advantaged-group members they had contact with listened to
+what they had to say and perceived them as competent and intelligent
+(Hässler, Ullrich, et al., 2021).\footnote{We did not consider whether,
+  in certain conditions, positive contact might increase support for
+  social change in disadvantaged groups because only few studies
+  measured the relevant moderator variables and because our analyses
+  relied on correlation matrices which are not enough to estimate
+  interaction effects. For the latter reason, we also did not consider
+  whether positive and negative contact might interact in their effects
+  on support for social change (see Albzour et al., in press).} Further,
+we did not consider contact between different disadvantaged groups,
+which has been found to increase support for social change among the
+disadvantaged (Dixon et al., 2015, 2017). Therefore, this meta-analysis
+could not provide a complete answer to the question whether, on balance,
+intergroup contact helps or hinders social change.
 
@@
 experiments to establish the direction of these relationships and to
-rule out spurious associations; (3) include measures that allow testing
-alternative explanations for the apparent `ironic' effects of intergroup
-contact; and (4) incorporate practices to prevent undisclosed
-flexibility in data collection and analysis. We hope that our
-meta-analysis helps researchers to address the open questions about how
-intergroup contact relates to support for social change in disadvantaged
-groups.
+rule out spurious associations; (3) include validated measures that
+allow testing alternative explanations for the apparent `ironic' effects
+of intergroup contact; and (4) incorporate practices to prevent
+undisclosed flexibility in data collection and analysis. We hope that
+our meta-analysis helps researchers to address the open questions about
+how intergroup contact relates to support for social change in
+disadvantaged groups.
 
@@
 \begin{CSLReferences}{1}{0}
+\leavevmode\hypertarget{ref-albzour_talking_inpress}{}%
+Albzour, M., Bady, Z., Elcheroth, E., Penic, S., Nasser, R., Reimer, N.
+K., \& Green, E. G. T. (in press). Talking to a (segregation) wall:
+Intergroup contact and attitudes toward normalization with {Israelis}
+among {Palestinians} from the occupied territories. \emph{Political
+Psychology}.
+
 \leavevmode\hypertarget{ref-3201}{}%
@@
 motivational outcomes among young adolescents} {[}Doctoral dissertation,
-\{Goldsmiths, University of London\}{]}.
+Goldsmiths, University of London{]}.
 \url{https://doi.org/10.25602/GOLD.00011030}
@@
 
+\leavevmode\hypertarget{ref-bracegirdle_disentangling_2022}{}%
+Bracegirdle, C., Reimer, N. K., Zalk, M. van, Hewstone, M., \& Wölfer,
+R. (2022). Disentangling contact and socialization effects on outgroup
+attitudes in diverse friendship networks. \emph{Journal of Personality
+and Social Psychology}, \emph{122}(1), 1--15.
+\url{https://doi.org/10.1037/pspa0000240}
+
 \leavevmode\hypertarget{ref-carter_correcting_2019}{}%
@@
 international students: Applying intergroup contact theory} {[}Doctoral
-dissertation, \{Indiana University\}{]}. {ProQuest Dissertations and
-Theses Global}.
+dissertation, Indiana University{]}. {ProQuest Dissertations and Theses
+Global}.
+
+\leavevmode\hypertarget{ref-cochran_planning_1965}{}%
+Cochran, W. G. (1965). The planning of observational studies of human
+populations. \emph{Journal of the Royal Statistical Society},
+\emph{128}(2), 234--266. \url{https://doi.org/10.2307/2344179}
 
@@
 toward {White} people in {African} {American} college students}
-{[}Doctoral dissertation, \{University of Kansas\}{]}. {ProQuest
+{[}Doctoral dissertation, University of Kansas{]}. {ProQuest
 Dissertations and Theses Global}.
@@
 
+\leavevmode\hypertarget{ref-flake_construct_2017}{}%
+Flake, J. K., Pek, J., \& Hehman, E. (2017). Construct validation in
+social and personality research: {Current} practice and recommendations.
+\emph{Social Psychological and Personality Science}, \emph{8}(4),
+370--378. \url{https://doi.org/10.1177/1948550617693063}
+
 \leavevmode\hypertarget{ref-1549}{}%
 *Forbes, J. M. (2001). \emph{Affirmative action attitudes in black and
-white} {[}Doctoral dissertation, \{Wayne State University\}{]}.
-{ProQuest Dissertations and Theses Global}.
+white} {[}Doctoral dissertation, Wayne State University{]}. {ProQuest
+Dissertations and Theses Global}.
 
@@
 
+\leavevmode\hypertarget{ref-harrer_doing_2021}{}%
+Harrer, M., Cuijper, P., Furukawa, T. A., \& Ebert, D. D. (2021).
+\emph{Doing meta-analysis with {R}: A hands-on guide}. CRC Press/Taylor
+\& Francis Group.
+\url{https://bookdown.org/MathiasHarrer/Doing_Meta_Analysis_in_R/}
+
 \leavevmode\hypertarget{ref-4003}{}%
@@
 605--615. \url{https://doi.org/10.1111/jasp.12463}
+
+\leavevmode\hypertarget{ref-hayward_toward_2017}{}%
+Hayward, L. E., Tropp, L. R., Hornsey, M. J., \& Barlow, F. K. (2017).
+Toward a comprehensive understanding of intergroup contact: Descriptions
+and mediators of positive and negative contact among majority and
+minority groups. \emph{Personality and Social Psychology Bulletin},
+\emph{43}(3), 347--364. \url{https://doi.org/10.1177/0146167216685291}
 
@@
 
+\leavevmode\hypertarget{ref-hassler_need_2021}{}%
+Hässler, T., Ullrich, J., Sebben, S., Shnabel, N., Bernardino, M.,
+Valdenegro, D., Van Laar, C., González, R., Visintin, E. P., Tropp, L.
+R., Ditlmann, R. K., Abrams, D., Aydin, A. L., Pereira, A., Selvanathan,
+H. P., Zimmermann, J. von, Lantos, N. A., Sainz, M., Glenz, A., \ldots{}
+Pistella, J. (2021). Need satisfaction in intergroup contact: {A}
+multinational study of pathways toward social change. \emph{Journal of
+Personality and Social Psychology}.
+\url{https://doi.org/10.1037/pspi0000365}
+
 \leavevmode\hypertarget{ref-hassler_intergroup_2021}{}%
@@
 *Head, R. N. (2013). \emph{Coping with perceived discrimination}
-{[}Doctoral dissertation, \{North Carolina State University\}{]}.
-{ProQuest Dissertations and Theses Global}.
+{[}Doctoral dissertation, North Carolina State University{]}. {ProQuest
+Dissertations and Theses Global}.
 
@@
 interpersonal discrimination among {Blacks}, {Whites} and {Latinos} in
-{Chicago}} {[}Doctoral dissertation, \{University of California,
-Davis\}{]}. {ProQuest Dissertations and Theses Global}.
+{Chicago}} {[}Doctoral dissertation, University of California, Davis{]}.
+{ProQuest Dissertations and Theses Global}.
 
@@
 interethnic friendships among {Native} emerging adults: {A}
-mixed-methods investigation} {[}Doctoral dissertation, \{Utah State
-University\}{]}. {ProQuest Dissertations and Theses Global}.
+mixed-methods investigation} {[}Doctoral dissertation, Utah State
+University{]}. {ProQuest Dissertations and Theses Global}.
 
@@
 discrimination on depressive symptoms and school outcomes among asian
-american adolescents} {[}Doctoral dissertation, \{The University of
-Chicago\}{]}. {ProQuest Dissertations and Theses Global}.
+american adolescents} {[}Doctoral dissertation, The University of
+Chicago{]}. {ProQuest Dissertations and Theses Global}.
 
@@
 
+\leavevmode\hypertarget{ref-lolliot_measures_2015}{}%
+Lolliot, S., Fell, B., Schmid, K., Wölfer, R., Swart, H., Voci, A.,
+Christ, O., New, R., \& Hewstone, M. (2015). Measures of intergroup
+contact. In G. J. Boyle, D. H. Saklofske, \& G. Matthews (Eds.),
+\emph{Measures of {Personality} and {Social} {Psychological}
+{Constructs}} (pp. 652--683). Elsevier.
+\url{https://doi.org/10.1016/B978-0-12-386915-9.00023-1}
+
 \leavevmode\hypertarget{ref-1042}{}%
@@
 conflict between reducing prejudice and supporting engagement in
-collective action} {[}Doctoral dissertation, \{University of California,
-Santa Cruz\}{]}. {ProQuest Dissertations and Theses Global}.
+collective action} {[}Doctoral dissertation, University of California,
+Santa Cruz{]}. {ProQuest Dissertations and Theses Global}.
 
@@
 
+\leavevmode\hypertarget{ref-mcelreath_statistical_2020}{}%
+McElreath, R. (2020). \emph{Statistical rethinking: A {Bayesian} course
+with examples in {R} and {Stan}} (2nd ed.). CRC Press/Taylor \& Francis
+Group.
+
 \leavevmode\hypertarget{ref-1850}{}%
 *McGinley, J. E. (2007). \emph{Expatriate adjustment: {Resources},
-responses, and outcomes} {[}Doctoral dissertation, \{Northcentral
-University\}{]}. {ProQuest Dissertations and Theses Global}.
+responses, and outcomes} {[}Doctoral dissertation, Northcentral
+University{]}. {ProQuest Dissertations and Theses Global}.
 
@@
 
+\leavevmode\hypertarget{ref-r_version_2021}{}%
+R Core Team. (2021). \emph{R: A language and environment for statistical
+computing} (Version 4.1.1). \url{https://www.R-project.org/}
+
 \leavevmode\hypertarget{ref-3051}{}%
@@
 
+\leavevmode\hypertarget{ref-rodriguez_engaging_2018}{}%
+Rodríguez, J., Nagda, B. R. A., Sorensen, N., \& Gurin, P. (2018).
+Engaging race and racism for socially just intergroup relations: The
+impact of intergroup dialogue on college campuses in the {United
+States}. \emph{Multicultural Education Review}, \emph{10}(3), 224--245.
+\url{https://doi.org/10.1080/2005615X.2018.1497874}
+
+\leavevmode\hypertarget{ref-everitt_observational_2005}{}%
+Rosenbaum, P. R. (2005). Observational study. In B. S. Everitt \& D. C.
+Howell (Eds.), \emph{Encyclopedia of statistics in behavioral science}
+(3rd ed., pp. 1451--1462). John Wiley \& Sons, Ltd.
+\url{https://doi.org/10.1002/0470013192}
+
 \leavevmode\hypertarget{ref-703}{}%
@@
 students' pre-college racial environments and their diversity
-experiences in college} {[}Doctoral dissertation, \{University of
-California, Los Angeles\}{]}. {ProQuest Dissertations and Theses
-Global}.
+experiences in college} {[}Doctoral dissertation, University of
+California, Los Angeles{]}. {ProQuest Dissertations and Theses Global}.
 
@@
 
+\leavevmode\hypertarget{ref-schafer_does_2021}{}%
+Schäfer, S. J., Kauff, M., Prati, F., Kros, M., Lang, T., \& Christ, O.
+(2021). Does negative contact undermine attempts to improve intergroup
+relations? {Deepening} the understanding of negative contact and its
+consequences for intergroup contact research and interventions.
+\emph{Journal of Social Issues}, \emph{77}(1), 197--216.
+\url{https://doi.org/10.1111/josi.12422}
+
 \leavevmode\hypertarget{ref-2392}{}%
@@
 {[}Unpublished dataset{]}. University of Kent.
+
+\leavevmode\hypertarget{ref-sengupta_protect_unpublished}{}%
+Sengupta, N. K. (2021). \emph{{``We protect, you serve''}: Ambivalent
+sexism and violence against women in {India}} {[}Manuscript submitted
+for publication{]}. School of Psychology, University of Kent.
 
@@
 *Shammas, D. (2009). \emph{Expatriate adjustment: {Resources},
-responses, and outcomes} {[}Doctoral dissertation, \{Northcentral
-University\}{]}. {ProQuest Dissertations and Theses Global}.
+responses, and outcomes} {[}Doctoral dissertation, Northcentral
+University{]}. {ProQuest Dissertations and Theses Global}.
 
@@
 \leavevmode\hypertarget{ref-stan_development_team_rstan:_2020}{}%
-Stan Development Team. (2020). \emph{{RStan}: {The} {R} interface to
-{Stan}} (Version 2.21.2). \url{http://mc-stan.org/}
+Stan Development Team. (2021). \emph{{RStan}: {The} {R} interface to
+{Stan}} (Version 2.26.3). \url{http://mc-stan.org/}
 
@@
 \leavevmode\hypertarget{ref-933}{}%
-*Tropp, Linda R. (2007). Perceived discrimination and interracial
-contact: {Predicting} interracial closeness among {Black} and {White}
+*Tropp, L. R. (2007). Perceived discrimination and interracial contact:
+{Predicting} interracial closeness among {Black} and {White}
 {Americans}. \emph{Social Psychology Quarterly}, \emph{70}(1), 70--81.
@@
 \leavevmode\hypertarget{ref-tropp_making_2018}{}%
-Tropp, Linda R., \& Barlow, F. K. (2018). Making advantaged racial
-groups care about inequality: Intergroup contact as a route to
-psychological investment. \emph{Current Directions in Psychological
-Science}, \emph{27}(3), 194--199.
-\url{https://doi.org/10.1177/0963721417743282}
+Tropp, L. R., \& Barlow, F. K. (2018). Making advantaged racial groups
+care about inequality: Intergroup contact as a route to psychological
+investment. \emph{Current Directions in Psychological Science},
+\emph{27}(3), 194--199. \url{https://doi.org/10.1177/0963721417743282}
 
 \leavevmode\hypertarget{ref-1743}{}%
-*Tropp, Linda R., Hawi, D. R., Van Laar, C., \& Levin, S. (2012).
+*Tropp, L. R., Hawi, D. R., Van Laar, C., \& Levin, S. (2012).
 Cross-ethnic friendships, perceived discrimination, and their effects on
@@
 \leavevmode\hypertarget{ref-1658}{}%
-*Tropp, Linda R., Okamoto, D. G., Marrow, H. B., \& Jones-Correa, M.
+*Tropp, L. R., Okamoto, D. G., Marrow, H. B., \& Jones-Correa, M.
 (2018). How contact experiences shape welcoming: Perspectives from
@@
 
+\leavevmode\hypertarget{ref-dixon_models_2012}{}%
+Wright, S. C., \& Baray, G. (2012). Models of social change in social
+psychology: {Collective} action or prejudice reduction? {Conflict} or
+harmony? In J. Dixon \& M. Levine (Eds.), \emph{Beyond prejudice:
+{Extending} the social psychology of conflict, inequality and social
+change} (pp. 225--247). Cambridge University Press.
+\url{https://doi.org/10.1017/CBO9781139022736.014}
+
 \leavevmode\hypertarget{ref-wright_struggle_2009}{}%

### 2022-02-17 manuscript/supplemental-materials.Rmd
revision

@@
 
-## Deviations
-
-We preregistered the eligibility criteria, search strategy, study selection, data collection, and preregistered analyses.
-Some aspects of the preregistered protocol proved unrealistic, impractical, or underspecified.
-Therefore, we deviated from the protocol in the following ways:
-
-1.
-We preregistered that we would update our search every four months until we would submit the manuscript.
-This proved unrealistic as the study selection and data collection process for the new studies took almost as long.
-Instead, we concluded our search of electronic databases on April 1, 2020—that is, before we started analyzing and documenting our findings.
-
-2.
-We preregistered that we would randomly select 100 records to be screened by both coders to calculate inter-rater agreement.
-We did not specify, however, what we would do if inter-rater agreement was less than acceptable.
-We decided to refine our coding strategy over three samples of 100 records until we achieved acceptable agreement.
-
-3.
-We preregistered that we would use *Google Scholar* to find records citing eligible studies.
-This proved impractical as *Google Scholar* does not facilitate the electronic export of citing records.
-Instead, we used the *Scopus* citation database.
-
-4.
-We preregistered that we would attempt to contact the authors of all papers with missing effect sizes.
-Instead, we decided to not contact authors for studies published before 2000 as we considered it unlikely that the authors still had access to the data.
-
-5.
-We preregistered that we would use a Bayesian two-level random-effects meta-analysis model, described in the main text, for all preregistered analyses.
-For the association between policy support and collective action, however, we had only few studies and found that the two-level model did not result in a reliable posterior distribution (as indicated by divergent transitions in the estimation algorithm).
-Instead, we used a Bayesian one-level random-effects model to estimate that association.
-
 ## Search Strategy
@@
 \noindent We sent a call for unpublished research to the mailing lists of the *European Association of Social Psychology*, the *Society for Personality and Social Psychology*, the *International Society of Political Psychology*, the *Society for the Psychological Study of Social Issues*, and the *Society of Australasian Social Psychologists*.
+
+## Coding Criteria (Study Setting)
+
+For each sample, we categorized the study setting according to the source of the ingroup's relative disadvantage.
+This coding scheme is, by necessity, reductive and incomplete.
+We believe, however, that it can offer some insight into relevant differences in study settings.
+
+We coded a study setting as *short-term migration* if the relevant intergroup context resulted from the short-term movement of people for the purposes of temporary employment or education.
+Most studies in this category focus on international students.
+
+We coded a study setting as *long-term migration* if the relevant intergroup context resulted from migration, in either the current or previous generations, and if there is an established intergroup hierarchy that disadvantages the relevant ingroup.
+Examples include Black and Asian people in the United Kingdom and Asian Americans in the United States.
+
+We coded a study setting as *post-slavery* if the ingroup's relative disadvantage resulted from a racial hierarchy rooted in the historical abduction and enslavement of Africans.
+This category includes Black people in the Americas and the Caribbean.
+
+We coded a study setting as *colonization* if the relevant intergroup context resulted from the advantaged group colonizing and subjugating the disadvantaged group in the place that was originally inhabited by the disadvantaged group.
+This category includes contexts in which one nation has occupied the territory of another, resulting in an established intergroup hierarchy that disadvantages the relevant ingroup.
+Examples include Māori in New Zealand and Kurds in Turkey.
+While many of the hierarchies we categorize as resulting from long-term migration or slavery are rooted in a history of colonization, we use colonization in a narrow sense to describe settler colonies and occupied territories.
+
+We coded a study setting as *religion* if the relevant intergroup context was defined in terms of religious group membership (for example, Muslims in India).
+In contexts in which religion is a marker of a disadvantaged immigrant group (e.g., Muslims in the Netherlands), we instead categorized the study setting as long-term migration.
+
+We coded a study setting as *caste* if the ingroup's relative disadvantaged resulted from caste hierarchies in South Asia.
+We coded a study setting as *sexual/gender minorities* if the relevant ingroup was defined in terms of their membership in a discriminated sexual or gender minority (i.e., LGBTQ people).
+We coded a study setting as *other* if the relevant intergroup context did not fit any of the other categories (e.g., disabled people).
 
@@
 
+## Moderator Analyses Without Contact Quality
+
+```{=latex}
+
+\begin{figure*}
+\centering
+\caption{Results from the random-effects meta-regression tree analysis}
+\includegraphics[scale=1]{../figures/figure-s3}
+\caption*{\textit{Note.} Posterior distributions for the estimated correlation coefficient in each leaf of the meta-regression tree, highlighting the proportion of posterior samples for which $r_\text{mean} < 0$.
+In this analysis, we did not consider whether studies measured direct, qualitatively positive contact.
+S.-T.
+Migration = Short-Term Migration.}
+\label{fig:s3}
+\end{figure*}
+
+```
+
+```{r, include = FALSE}
+
+  # Import results from moderator analyses
+  meta_cart <- read_rds("../results/results_old_exploratory_moderator_analyses.rds") %>% 
+    group_by(kk, age, ic_direct, study_setting) %>% 
+    summarize(
+      r_kk = glue("$r = {f_num(median(r), digits = 2)}, [{f_num(quantile(r, 0.025), digits = 2)}, {f_num(quantile(r, 0.975), digits = 2)}]$"),
+      R2 = glue("$R^2 = {f_num(median(R2) * 100, digits = 0)}\\%$")
+    ) %>% 
+    ungroup()
+
+```
+
+In an earlier version of our manuscript, we did not consider the distinction between contact quantity and quality as a moderator.
+As we added this moderator during peer review and as doing so changed the results of some of our moderator analyses, we report our original findings from the moderator analyses below.
+We used meta-regression trees to discover interactions between moderator variables that best explained heterogeneity in effect sizes [@li_meta-cart_2017; @li_multiple_2020].
+Figure S3 shows the resulting meta-regression model, which explained more variance across samples than any individual moderator (`r with(meta_cart, unique(R2))`).
+We found that intergroup contact was associated with less perceived injustice only in studies that focused on adults and that measured intergroup contact directly.
+Among these studies, this association was stronger in settings in which the groups’ relative inequality stemmed from short-term migration or colonization (`r with(meta_cart, r_kk[4])`) than in other settings (`r with(meta_cart, r_kk[3])`).
+
+## Unpublished Studies
+
+Some of the unpublished data included in the meta-analysis were based on studies that involved one of the co-authors of the present research.
+For the sake of transparency, we describe each of these studies and refer to published research based on these studies.
+
+**@2398** is based on data from a longitudinal social network study of two schools in a town in North West England conducted by a graduate students who, at the time, was co-supervised by the first author of the present research.
+The study included measures intended to test a broad range of questions, for example, to disentangle how contact and socialization effects shape outgroup attitudes in diverse friendship networks [@bracegirdle_disentangling_2022].
+@2398 includes data from Asian adolescents who reported their cross-group friendships with White adolescents (*N* = 829).
+
+**@2382** is based on data from a longitudinal survey of Asian British and White British people and included a broad range of measures related to intergroup contact and intergroup relations in England.
+@2382 includes data from Asian British people who reported their contact experiences with White British people, as well as their perceived discrimination and collective action intentions (*N* = 751).
+
+**@2392** and **@2385** is based on data from the Centre for the Monitoring of the Indian Economy’s consumer pyramid sample, a representative national sample of the Indian population.
+In 2017, this sample consisted of 161,183 households (112,657 rural and 48,526 urban households).
+Households were selected by dividing 26 of the 29 States of India into sub-state "Homogenous Regions"—sets of neighboring districts with similar climatic conditions and urbanization levels—and then randomly sampling villages/blocks of towns, and households within each region.
+During August and September, 2017, interviewers attempted to make face-to-face contact with each household.
+One member of the household was asked to volunteer to complete the verbally administered survey.
+In all, 134,531 people were successfully reached by interviewers.
+The survey included measures intended to test a broad range of questions, for example, about the relationship between ambivalent sexism and violence against women [@sengupta_protect_unpublished].
+For the meta-analysis, we calculated correlation coefficients between items measuring positive and negative contact, group identification, perceived discrimination, and collective action intentions.
+Items in the survey were first translated from English into ten Indian languages (Hindi, Urdu, Marathi, Punjabi, Bengali, Tamil, Telugu, Malayalam, Odiya and Gujarati), and then independently back-translated to ensure accuracy.
+Surveys were administered in whichever language the participants were most comfortable with (including English).
+@2392 includes data from participants who belonged to three disadvantaged caste groups and reported their contact experiences with members of upper castes (*N* = 96,547).
+@2385 includes data from participants who belonged to four religious minority groups and reported their contact experiences with Hindus (*N* = 7,440).
+
+**@2381** is based on data from a large-scale national longitudinal study in New Zealand, the New Zealand Attitudes and Values Study (NZAVS; [https://www.psych.auckland.ac.nz/en/about/new-zealand-attitudes-and-values-study.html](https://www.psych.auckland.ac.nz/en/about/new-zealand-attitudes-and-values-study.html)).
+@2381 includes data from Māori, Pacific Islanders, and Asians who reported their contact experiences with European New Zealanders (*N* = 3187).
+
+**@2383** is based on data from a social network study across ten schools in England which was conducted as part of a project for which the first author of the present research worked as a postdoctoral researcher.
+A survey company collected data from the same grade (Year 10, equivalent to 9th grade in the US) at each school.
+Data were collected between January and March 2018.
+Students completed a pen-and-paper survey in a classroom session (40–45 minutes).
+As part of a larger study on intergroup contact among young people, the survey included items measuring cross-group friendship as well as perceptions of discrimination.
+@2383 included data from Black, Asian, and other ethnic minority students who reported their contact experiences with White people (*N* = 713).
+
 \newpage

### 2022-02-17 manuscript/supplemental-materials.tex
revision

@@
 
+% References
+\newenvironment{CSLReferences}[2]{}{}
+
 % Frontmatter
-\title{ Supplemental Online Materials:\\\textit{Meta-Analysis of the `Ironic' Effects of Intergroup Contact} }
+\title{ Supplemental Online Materials:\\\textit{Meta-Analysis of the
+`Ironic' Effects of Intergroup Contact} }
 \author{  }
@@
 \maketitle
-
-\hypertarget{deviations}{%
-\subsection{Deviations}\label{deviations}}
-
-We preregistered the eligibility criteria, search strategy, study
-selection, data collection, and preregistered analyses. Some aspects of
-the preregistered protocol proved unrealistic, impractical, or
-underspecified. Therefore, we deviated from the protocol in the
-following ways:
-
-\begin{enumerate}
-\def\labelenumi{\arabic{enumi}.}
-\item
-  We preregistered that we would update our search every four months
-  until we would submit the manuscript. This proved unrealistic as the
-  study selection and data collection process for the new studies took
-  almost as long. Instead, we concluded our search of electronic
-  databases on April 1, 2020---that is, before we started analyzing and
-  documenting our findings.
-\item
-  We preregistered that we would randomly select 100 records to be
-  screened by both coders to calculate inter-rater agreement. We did not
-  specify, however, what we would do if inter-rater agreement was less
-  than acceptable. We decided to refine our coding strategy over three
-  samples of 100 records until we achieved acceptable agreement.
-\item
-  We preregistered that we would use \emph{Google Scholar} to find
-  records citing eligible studies. This proved impractical as
-  \emph{Google Scholar} does not facilitate the electronic export of
-  citing records. Instead, we used the \emph{Scopus} citation database.
-\item
-  We preregistered that we would attempt to contact the authors of all
-  papers with missing effect sizes. Instead, we decided to not contact
-  authors for studies published before 2000 as we considered it unlikely
-  that the authors still had access to the data.
-\item
-  We preregistered that we would use a Bayesian two-level random-effects
-  meta-analysis model, described in the main text, for all preregistered
-  analyses. For the association between policy support and collective
-  action, however, we had only few studies and found that the two-level
-  model did not result in a reliable posterior distribution (as
-  indicated by divergent transitions in the estimation algorithm).
-  Instead, we used a Bayesian one-level random-effects model to estimate
-  that association.
-\end{enumerate}
 
@@
 Australasian Social Psychologists}.
+
+\hypertarget{coding-criteria-study-setting}{%
+\subsection{Coding Criteria (Study
+Setting)}\label{coding-criteria-study-setting}}
+
+For each sample, we categorized the study setting according to the
+source of the ingroup's relative disadvantage. This coding scheme is, by
+necessity, reductive and incomplete. We believe, however, that it can
+offer some insight into relevant differences in study settings.
+
+We coded a study setting as \emph{short-term migration} if the relevant
+intergroup context resulted from the short-term movement of people for
+the purposes of temporary employment or education. Most studies in this
+category focus on international students.
+
+We coded a study setting as \emph{long-term migration} if the relevant
+intergroup context resulted from migration, in either the current or
+previous generations, and if there is an established intergroup
+hierarchy that disadvantages the relevant ingroup. Examples include
+Black and Asian people in the United Kingdom and Asian Americans in the
+United States.
+
+We coded a study setting as \emph{post-slavery} if the ingroup's
+relative disadvantage resulted from a racial hierarchy rooted in the
+historical abduction and enslavement of Africans. This category includes
+Black people in the Americas and the Caribbean.
+
+We coded a study setting as \emph{colonization} if the relevant
+intergroup context resulted from the advantaged group colonizing and
+subjugating the disadvantaged group in the place that was originally
+inhabited by the disadvantaged group. This category includes contexts in
+which one nation has occupied the territory of another, resulting in an
+established intergroup hierarchy that disadvantages the relevant
+ingroup. Examples include Māori in New Zealand and Kurds in Turkey.
+While many of the hierarchies we categorize as resulting from long-term
+migration or slavery are rooted in a history of colonization, we use
+colonization in a narrow sense to describe settler colonies and occupied
+territories.
+
+We coded a study setting as \emph{religion} if the relevant intergroup
+context was defined in terms of religious group membership (for example,
+Muslims in India). In contexts in which religion is a marker of a
+disadvantaged immigrant group (e.g., Muslims in the Netherlands), we
+instead categorized the study setting as long-term migration.
+
+We coded a study setting as \emph{caste} if the ingroup's relative
+disadvantaged resulted from caste hierarchies in South Asia. We coded a
+study setting as \emph{sexual/gender minorities} if the relevant ingroup
+was defined in terms of their membership in a discriminated sexual or
+gender minority (i.e., LGBTQ people). We coded a study setting as
+\emph{other} if the relevant intergroup context did not fit any of the
+other categories (e.g., disabled people).
 
@@
 
+\hypertarget{moderator-analyses-without-contact-quality}{%
+\subsection{Moderator Analyses Without Contact
+Quality}\label{moderator-analyses-without-contact-quality}}
+
+\begin{figure*}
+\centering
+\caption{Results from the random-effects meta-regression tree analysis}
+\includegraphics[scale=1]{../figures/figure-s3}
+\caption*{\textit{Note.} Posterior distributions for the estimated correlation coefficient in each leaf of the meta-regression tree, highlighting the proportion of posterior samples for which $r_\text{mean} < 0$.
+In this analysis, we did not consider whether studies measured direct, qualitatively positive contact.
+S.-T.
+Migration = Short-Term Migration.}
+\label{fig:s3}
+\end{figure*}
+
+In an earlier version of our manuscript, we did not consider the
+distinction between contact quantity and quality as a moderator. As we
+added this moderator during peer review and as doing so changed the
+results of some of our moderator analyses, we report our original
+findings from the moderator analyses below. We used meta-regression
+trees to discover interactions between moderator variables that best
+explained heterogeneity in effect sizes (Li et al., 2017, 2020). Figure
+S3 shows the resulting meta-regression model, which explained more
+variance across samples than any individual moderator (\(R^2 = 30\%\)).
+We found that intergroup contact was associated with less perceived
+injustice only in studies that focused on adults and that measured
+intergroup contact directly. Among these studies, this association was
+stronger in settings in which the groups' relative inequality stemmed
+from short-term migration or colonization (\(r = -.18, [-.23, -.13]\))
+than in other settings (\(r = -.09, [-.12, -.06]\)).
+
+\hypertarget{unpublished-studies}{%
+\subsection{Unpublished Studies}\label{unpublished-studies}}
+
+Some of the unpublished data included in the meta-analysis were based on
+studies that involved one of the co-authors of the present research. For
+the sake of transparency, we describe each of these studies and refer to
+published research based on these studies.
+
+\textbf{Bracegirdle (2020)} is based on data from a longitudinal social
+network study of two schools in a town in North West England conducted
+by a graduate students who, at the time, was co-supervised by the first
+author of the present research. The study included measures intended to
+test a broad range of questions, for example, to disentangle how contact
+and socialization effects shape outgroup attitudes in diverse friendship
+networks (Bracegirdle et al., 2022). Bracegirdle (2020) includes data
+from Asian adolescents who reported their cross-group friendships with
+White adolescents (\emph{N} = 829).
+
+\textbf{Schäfer et al. (2018)} is based on data from a longitudinal
+survey of Asian British and White British people and included a broad
+range of measures related to intergroup contact and intergroup relations
+in England. Schäfer et al. (2018) includes data from Asian British
+people who reported their contact experiences with White British people,
+as well as their perceived discrimination and collective action
+intentions (\emph{N} = 751).
+
+\textbf{Sengupta (2020a)} and \textbf{Sengupta (2020b)} is based on data
+from the Centre for the Monitoring of the Indian Economy's consumer
+pyramid sample, a representative national sample of the Indian
+population. In 2017, this sample consisted of 161,183 households
+(112,657 rural and 48,526 urban households). Households were selected by
+dividing 26 of the 29 States of India into sub-state ``Homogenous
+Regions''---sets of neighboring districts with similar climatic
+conditions and urbanization levels---and then randomly sampling
+villages/blocks of towns, and households within each region. During
+August and September, 2017, interviewers attempted to make face-to-face
+contact with each household. One member of the household was asked to
+volunteer to complete the verbally administered survey. In all, 134,531
+people were successfully reached by interviewers. The survey included
+measures intended to test a broad range of questions, for example, about
+the relationship between ambivalent sexism and violence against women
+(Sengupta, 2021). For the meta-analysis, we calculated correlation
+coefficients between items measuring positive and negative contact,
+group identification, perceived discrimination, and collective action
+intentions. Items in the survey were first translated from English into
+ten Indian languages (Hindi, Urdu, Marathi, Punjabi, Bengali, Tamil,
+Telugu, Malayalam, Odiya and Gujarati), and then independently
+back-translated to ensure accuracy. Surveys were administered in
+whichever language the participants were most comfortable with
+(including English). Sengupta (2020a) includes data from participants
+who belonged to three disadvantaged caste groups and reported their
+contact experiences with members of upper castes (\emph{N} = 96,547).
+Sengupta (2020b) includes data from participants who belonged to four
+religious minority groups and reported their contact experiences with
+Hindus (\emph{N} = 7,440).
+
+\textbf{Sengupta \& Sibley (2020)} is based on data from a large-scale
+national longitudinal study in New Zealand, the New Zealand Attitudes
+and Values Study (NZAVS;
+\url{https://www.psych.auckland.ac.nz/en/about/new-zealand-attitudes-and-values-study.html}).
+Sengupta \& Sibley (2020) includes data from Māori, Pacific Islanders,
+and Asians who reported their contact experiences with European New
+Zealanders (\emph{N} = 3187).
+
+\textbf{Wölfer \& Hewstone (2019)} is based on data from a social
+network study across ten schools in England which was conducted as part
+of a project for which the first author of the present research worked
+as a postdoctoral researcher. A survey company collected data from the
+same grade (Year 10, equivalent to 9th grade in the US) at each school.
+Data were collected between January and March 2018. Students completed a
+pen-and-paper survey in a classroom session (40--45 minutes). As part of
+a larger study on intergroup contact among young people, the survey
+included items measuring cross-group friendship as well as perceptions
+of discrimination. Wölfer \& Hewstone (2019) included data from Black,
+Asian, and other ethnic minority students who reported their contact
+experiences with White people (\emph{N} = 713).
+
 \newpage
@@
 \hypertarget{refs}{}
+\begin{CSLReferences}{1}{0}
+\leavevmode\hypertarget{ref-2398}{}%
+*Bracegirdle, C. (2020). \emph{Social network study of two diverse
+schools in {Northern England}} {[}Unpublished dataset{]}. University of
+Oxford.
+
+\leavevmode\hypertarget{ref-bracegirdle_disentangling_2022}{}%
+Bracegirdle, C., Reimer, N. K., Zalk, M. van, Hewstone, M., \& Wölfer,
+R. (2022). Disentangling contact and socialization effects on outgroup
+attitudes in diverse friendship networks. \emph{Journal of Personality
+and Social Psychology}, \emph{122}(1), 1--15.
+\url{https://doi.org/10.1037/pspa0000240}
+
 \leavevmode\hypertarget{ref-li_meta-cart_2017}{}%
-Li, X., Dusseldorp, E., \& Meulman, J. J. (2017). Meta-CART: A tool to
-identify interactions between moderators in meta-analysis. \emph{British
-Journal of Mathematical and Statistical Psychology}, \emph{70}(1),
-118--136. \url{https://doi.org/10.1111/bmsp.12088}
+Li, X., Dusseldorp, E., \& Meulman, J. J. (2017). Meta-{CART}: {A} tool
+to identify interactions between moderators in meta-analysis.
+\emph{British Journal of Mathematical and Statistical Psychology},
+\emph{70}(1), 118--136. \url{https://doi.org/10.1111/bmsp.12088}
 
@@
 
+\leavevmode\hypertarget{ref-2382}{}%
+*Schäfer, S. J., Bracegirdle, C., Christ, O., Hewstone, M., Jaspers, E.,
+Reimer, N. K., \& Wölfer, R. (2018). \emph{Positive-negative asymmetry
+of intergroup contact: A dynamic approach} {[}Unpublished dataset{]}.
+University of Oxford.
+
+\leavevmode\hypertarget{ref-2392}{}%
+*Sengupta, N. K. (2020a). \emph{Inter-caste contact in {India}}
+{[}Unpublished dataset{]}. University of Kent.
+
+\leavevmode\hypertarget{ref-2385}{}%
+*Sengupta, N. K. (2020b). \emph{Inter-religious contact in {India}}
+{[}Unpublished dataset{]}. University of Kent.
+
+\leavevmode\hypertarget{ref-sengupta_protect_unpublished}{}%
+Sengupta, N. K. (2021). \emph{{``We protect, you serve''}: Ambivalent
+sexism and violence against women in {India}} {[}Manuscript submitted
+for publication{]}. School of Psychology, University of Kent.
+
+\leavevmode\hypertarget{ref-2381}{}%
+*Sengupta, N. K., \& Sibley, C. G. (2020). \emph{Intergroup contact and
+political attitudes among ethnic minorities in {New Zealand}}
+{[}Unpublished dataset{]}. The University of Auckland.
+
+\leavevmode\hypertarget{ref-2383}{}%
+*Wölfer, R., \& Hewstone, M. (2019). \emph{Social integration in diverse
+societies: The importance of contact experiences in youth}
+{[}Unpublished dataset{]}. University of Oxford.
+
+\end{CSLReferences}
+
 \endgroup

### 2022-02-17 figures/figure-4.R

@@ -56,24 +56,29 @@ rm(list = ls())
         "study_intention" = "Study Intention",
         "publication_status" = "Publication Status",
         "ic_direct" = "Predictor (Direct/Indirect)",
+        "ic_quality" = "Predictor (Contact Quality)",
         "pi_specific" = "Outcome (Specific/General)",
         "pi_personal" = "Outcome (Personal/Group)"
       ),
       category = recode(
         category,
+        "observational, cross-sectional" = "cross-sectional",
+        "observational, longitudinal" = "longitudinal",
         "quasi-experimental (no random assignment)" = "quasi-experimental",
         "experimental (random assignment)" = "experimental",
         "convenience sample" = "convenience",
-        "probability/representative sample" = "probability/representative",
+        "probability/representative sample" = "representative",
         "Slavery" = "Post-Slavery",
-        "Colonization" = "(Post-)Colonial"
+        "Colonization" = "(Post-)Colonial",
+        "Sexuality" = "Sexual/Gender Minorities",
+        "Directly" = "Direct",
+        "Indirectly" = "Indirect"
       ),
       category = str_replace(category, " ", "\n"),
-      category = str_replace(category, "\\/", "/\n"),
       category = Hmisc::capitalize(category),
       category = factor(category, levels = c(
-        "Observational,\ncross-sectional", 
-        "Observational,\nlongitudinal",
+        "Cross-sectional", 
+        "Longitudinal",
         "Quasi-experimental",
         "Experimental",
         "Short-term\nmigration",
@@ -82,23 +87,24 @@ rm(list = ls())
         "(Post-)Colonial",
         "Religion",
         "Caste",
-        "Sexuality",
+        "Sexual/Gender\nMinorities",
         "Other",
         "Convenience",
-        "Probability/\nrepresentative",
+        "Representative",
         "Adults",
-        "Adolescents/\nChildren",
-        "Directly",
-        "Indirectly",
+        "Adolescents",
+        "Children",
+        "Direct",
+        "Indirect",
+        "Yes",
+        "No",
         "Specific",
         "General",
         "Personal",
         "Group",
         "Both",
         "Published",
-        "Unpublished",
-        "Yes",
-        "No"
+        "Unpublished"
       ))
     )
   
@@ -192,11 +198,12 @@ rm(list = ls())
     design = "
     AC
     AD
-    AE
-    BF
-    BG
-    HI
-    HI
+    AB
+    AB
+    EF
+    GH
+    IJ
+    IJ
     ",
     guides = "collect"
   )

### 2022-02-17 figures/figure-6.R

@@ -19,36 +19,36 @@ rm(list = ls())
 # Figure 6a ---------------------------------------------------------------
 
   # Prepare data for subfigure
-  d_6a <- results %>% distinct(kk, n)
+  d_6a <- results %>% distinct(kk, ic_quality, study_setting, age, n)
   
   # Create boxes
   boxes <- tibble(
-    xmin = c(0.0, 1.0, 2.0, 3.0, 3.0, 3.0, 3.0),
-    xmax = c(0.8, 1.8, 2.8, 3.8, 3.8, 3.8, 3.8),
-    ymin = c(1.5, 1.0, 0.5, 0.0, 1.0, 2.0, 3.0),
-    ymax = c(2.3, 1.8, 1.3, 0.8, 1.8, 2.8, 3.8)
+    xmin = c(0.0, 1.0, 1.0, 2.0, 2.0, 2.0, 2.0),
+    xmax = c(0.8, 1.8, 1.8, 2.8, 2.8, 2.8, 2.8),
+    ymin = c(1.5, 0.5, 2.5, 0.0, 1.0, 2.0, 3.0),
+    ymax = c(2.3, 1.3, 3.3, 0.8, 1.8, 2.8, 3.8)
   )
   
   # Create arrows
   arrows <- tibble(
-    x    = c(0.8, 0.8, 1.8, 1.8, 2.8, 2.8),
-    xend = c(1.0, 3.0, 2.0, 3.0, 3.0, 3.0),
-    y    = c(1.9, 1.9, 1.4, 1.4, 0.9, 0.9),
-    yend = c(1.4, 3.4, 0.9, 2.4, 1.4, 0.4)
+    x    = c(0.8, 0.8, 1.8, 1.8, 1.8, 1.8),
+    xend = c(1.0, 1.0, 2.0, 2.0, 2.0, 2.0),
+    y    = c(1.9, 1.9, 0.9, 0.9, 2.9, 2.9),
+    yend = c(0.9, 2.9, 0.4, 1.4, 2.4, 3.4)
   )
   
   # Create labels
   labels <- tibble(
-    x = c(0.4, 1.4, 2.4, 3.4, 3.4, 3.4, 3.4),
-    y = c(1.9, 1.4, 0.9, 0.4, 1.4, 2.4, 3.4),
+    x = c(0.4, 1.4, 1.4, 2.4, 2.4, 2.4, 2.4),
[…]

### 2022-02-17 figures/figure-8.R

@@ -12,13 +12,34 @@ rm(list = ls())
   library(patchwork)
   library(numform)
 
+  # Link functions
+  r_to_z <- function(r) 0.5 * log( (1 + r) / (1 - r) )
+  z_to_r <- function(z) ( exp(2 * z) - 1 ) / ( exp(2 * z) + 1 )
+  
+  # Set seed (for posterior predictive simulations)
+  set.seed(9071118)
+  
 
 # Prepare -----------------------------------------------------------------
   
-  # Import results from analyses with alternative predictors
+  # Import results from analyses
+  pre_results <- read_rds("results/results_preregistered_analyses.rds")
+  add_results <- read_rds("results/results_additional_analyses.rds")
+  
+  # Import study-wise estimates from analyses
+  pre_r_pred_jj <- read_rds("results/r_pred_jj.rds")
+  add_r_pred_jj <- read_rds("results/r_additional_analyses_pred_jj.rds")
+  
+  # Merge results
   results <- bind_rows(
-    read_rds("results/results_analyses_with_negative_contact.rds"),
-    read_rds("results/results_analyses_with_ingroup_contact.rds")
+    pre_results %>% mutate(analysis = "Preregistered"),
+    add_results %>% mutate(analysis = "Not Preregistered")
+  )
+  
+  # Merge study-wise estimates
+  r_pred_jj <- bind_rows(
+    pre_r_pred_jj %>% mutate(analysis = "Preregistered"),
+    add_r_pred_jj %>% mutate(analysis = "Not Preregistered")
   )
 
   # Name predictor and outcome variables
@@ -26,82 +47,107 @@ rm(list = ls())
     mutate(
       x_name = recode_factor(
         x_var,
-        "pc" = "Positive Contact",
-        "nc" = "Negative Contact",
-        "og" = "Outgroup Contact",
-        "ig" = "Ingroup Contact"
+        "ic" = "Intergroup Contact",
+        "pi" = "Perceived Injustice",
+        "ca" = "Collective Action",
+        "ps" = "Policy Support"
       ),
       y_name = recode_factor(
         y_var,
-        "nc" = "Negative Contact",
-        "og" = "Outgroup Contact",
         "pi" = "Perceived Injustice",
         "ca" = "Collective Action",
-        "ps" = "Policy Support",
[…]

### 2022-02-17 figures/figure-9.R

@@ -1,0 +1,215 @@
+rm(list = ls())
+
+# Notes -------------------------------------------------------------------
+
+
+# Library -----------------------------------------------------------------
+
+  # Load packages
+  library(tidyverse)
+  library(tidybayes)
+  library(ggtext)
+  library(patchwork)
+  library(numform)
+
+
+# Prepare -----------------------------------------------------------------
+  
+  # Import results from analyses with alternative predictors
+  results <- bind_rows(
+    read_rds("results/results_analyses_with_negative_contact.rds"),
+    read_rds("results/results_analyses_with_ingroup_contact.rds")
+  )
+
+  # Name predictor and outcome variables
+  results <- results %>% 
+    mutate(
+      x_name = recode_factor(
+        x_var,
+        "pc" = "Positive Contact",
+        "nc" = "Negative Contact",
+        "og" = "Outgroup Contact",
+        "ig" = "Ingroup Contact"
+      ),
+      y_name = recode_factor(
+        y_var,
+        "nc" = "Negative Contact",
+        "og" = "Outgroup Contact",
+        "pi" = "Perceived Injustice",
+        "ca" = "Collective Action",
+        "ps" = "Policy Support",
+      )
+    )
+
+
+# Figure 9a ---------------------------------------------------------------
+
+  # Prepare
+  d_9a <- results %>% 
+    filter(x_var %in% c("pc", "nc"), y_var %in% c("pi", "ca", "ps")) %>% 
+    mutate(
+      text = paste0("*I* = ", I, ", *J* = ", J, ", *N* = ", f_comma(N))
+    )
+  
+  # Visualize
+  f_9a <- ggplot(d_9a, aes(x = r_mean)) +
+    stat_halfeye(
+      aes(fill = x_name),
+      point_interval = NULL,
+      adjust = 2,
+      n = 1e4,
+      alpha = 0.8
+    ) +
+    stat_halfeye(
+      aes(group = x_name),
+      point_interval = NULL,
+      adjust = 2,
+      n = 1e4,
+      slab_colour = "white",
+      slab_fill = NA,
+      slab_size = 0.2
+    ) +
+    geom_vline(xintercept = 0, linetype = "dashed", size = 0.5) +
+    geom_richtext(
+      data = d_9a %>% group_by(y_name) %>% summarise(text = unique(text)),
+      aes(
+        label = text, 
[…]

### 2022-02-17 figures/figure-s1.R

@@ -56,24 +56,29 @@ rm(list = ls())
         "study_intention" = "Study Intention",
         "publication_status" = "Publication Status",
         "ic_direct" = "Predictor (Direct/Indirect)",
+        "ic_quality" = "Predictor (Contact Quality)",
         "pi_specific" = "Outcome (Specific/General)",
         "pi_personal" = "Outcome (Personal/Group)"
       ),
       category = recode(
         category,
+        "observational, cross-sectional" = "cross-sectional",
+        "observational, longitudinal" = "longitudinal",
         "quasi-experimental (no random assignment)" = "quasi-experimental",
         "experimental (random assignment)" = "experimental",
         "convenience sample" = "convenience",
-        "probability/representative sample" = "probability/representative",
+        "probability/representative sample" = "representative",
         "Slavery" = "Post-Slavery",
-        "Colonization" = "(Post-)Colonial"
+        "Colonization" = "(Post-)Colonial",
+        "Sexuality" = "Sexual/Gender Minorities",
+        "Directly" = "Direct",
+        "Indirectly" = "Indirect"
       ),
       category = str_replace(category, " ", "\n"),
-      category = str_replace(category, "\\/", "/\n"),
       category = Hmisc::capitalize(category),
       category = factor(category, levels = c(
-        "Observational,\ncross-sectional", 
-        "Observational,\nlongitudinal",
+        "Cross-sectional", 
+        "Longitudinal",
         "Quasi-experimental",
         "Experimental",
         "Short-term\nmigration",
@@ -82,23 +87,24 @@ rm(list = ls())
         "(Post-)Colonial",
         "Religion",
         "Caste",
-        "Sexuality",
+        "Sexual/Gender\nMinorities",
         "Other",
         "Convenience",
-        "Probability/\nrepresentative",
+        "Representative",
         "Adults",
-        "Adolescents/\nChildren",
-        "Directly",
-        "Indirectly",
+        "Adolescents",
+        "Children",
+        "Direct",
+        "Indirect",
+        "Yes",
+        "No",
         "Specific",
         "General",
         "Personal",
         "Group",
         "Both",
         "Published",
-        "Unpublished",
-        "Yes",
-        "No"
+        "Unpublished"
       ))
     )
   
@@ -191,9 +197,10 @@ rm(list = ls())
     design = "
     AC
     AD
-    AE
-    BF
-    BG
+    AB
+    AB
+    EF
+    GH
     ",
     guides = "collect"
   )

### 2022-02-17 figures/figure-s2.R

@@ -56,24 +56,29 @@ rm(list = ls())
         "study_intention" = "Study Intention",
         "publication_status" = "Publication Status",
         "ic_direct" = "Predictor (Direct/Indirect)",
+        "ic_quality" = "Predictor (Contact Quality)",
         "pi_specific" = "Outcome (Specific/General)",
         "pi_personal" = "Outcome (Personal/Group)"
       ),
       category = recode(
         category,
+        "observational, cross-sectional" = "cross-sectional",
+        "observational, longitudinal" = "longitudinal",
         "quasi-experimental (no random assignment)" = "quasi-experimental",
         "experimental (random assignment)" = "experimental",
         "convenience sample" = "convenience",
-        "probability/representative sample" = "probability/representative",
+        "probability/representative sample" = "representative",
         "Slavery" = "Post-Slavery",
-        "Colonization" = "(Post-)Colonial"
+        "Colonization" = "(Post-)Colonial",
+        "Sexuality" = "Sexual/Gender Minorities",
+        "Directly" = "Direct",
+        "Indirectly" = "Indirect"
       ),
       category = str_replace(category, " ", "\n"),
-      category = str_replace(category, "\\/", "/\n"),
       category = Hmisc::capitalize(category),
       category = factor(category, levels = c(
-        "Observational,\ncross-sectional", 
-        "Observational,\nlongitudinal",
+        "Cross-sectional", 
+        "Longitudinal",
         "Quasi-experimental",
         "Experimental",
         "Short-term\nmigration",
@@ -82,23 +87,24 @@ rm(list = ls())
         "(Post-)Colonial",
         "Religion",
         "Caste",
-        "Sexuality",
+        "Sexual/Gender\nMinorities",
         "Other",
         "Convenience",
-        "Probability/\nrepresentative",
+        "Representative",
         "Adults",
-        "Adolescents/\nChildren",
-        "Directly",
-        "Indirectly",
+        "Adolescents",
+        "Children",
+        "Direct",
+        "Indirect",
+        "Yes",
+        "No",
         "Specific",
         "General",
         "Personal",
         "Group",
         "Both",
         "Published",
-        "Unpublished",
-        "Yes",
-        "No"
+        "Unpublished"
       ))
     )
   
@@ -191,9 +197,9 @@ rm(list = ls())
     design = "
     AC
     AD
-    AE
-    BF
-    BG
+    AB
+    EF
+    GH
     ",
     guides = "collect"
   )

### 2022-02-17 figures/figure-s3.R

@@ -1,287 +1,0 @@
-rm(list = ls())
-
-# Notes -------------------------------------------------------------------
-
-
-# Library -----------------------------------------------------------------
-
-  # Load packages
-  library(tidyverse)
-  library(tidybayes)
-  library(ggtext)
-  library(patchwork)
-  library(numform)
-
-  # Link functions
-  r_to_z <- function(r) 0.5 * log( (1 + r) / (1 - r) )
-  z_to_r <- function(z) ( exp(2 * z) - 1 ) / ( exp(2 * z) + 1 )
-  
-  # Set seed (for posterior predictive simulations)
-  set.seed(9071118)
-  
-
-# Prepare -----------------------------------------------------------------
-  
-  # Import results from analyses
-  pre_results <- read_rds("results/results_preregistered_analyses.rds")
-  add_results <- read_rds("results/results_additional_analyses.rds")
-  
-  # Import study-wise estimates from analyses
-  pre_r_pred_jj <- read_rds("results/r_pred_jj.rds")
-  add_r_pred_jj <- read_rds("results/r_additional_analyses_pred_jj.rds")
-  
-  # Merge results
-  results <- bind_rows(
-    pre_results %>% mutate(analysis = "Preregistered"),
-    add_results %>% mutate(analysis = "Not Preregistered")
-  )
-  
-  # Merge study-wise estimates
-  r_pred_jj <- bind_rows(
-    pre_r_pred_jj %>% mutate(analysis = "Preregistered"),
-    add_r_pred_jj %>% mutate(analysis = "Not Preregistered")
-  )
-
-  # Name predictor and outcome variables
-  results <- results %>% 
-    mutate(
-      x_name = recode_factor(
-        x_var,
-        "ic" = "Intergroup Contact",
-        "pi" = "Perceived Injustice",
-        "ca" = "Collective Action",
-        "ps" = "Policy Support"
-      ),
-      y_name = recode_factor(
-        y_var,
-        "pi" = "Perceived Injustice",
-        "ca" = "Collective Action",
-        "ps" = "Policy Support"
-      )
-    )
-  
-  # Name predictor and outcome variables
-  r_pred_jj <- r_pred_jj %>% 
-    mutate(
-      x_name = recode_factor(
-        x_var,
-        "ic" = "Intergroup Contact",
-      ),
[…]

### 2022-02-17 run_scripts.R

@@ -47,6 +47,9 @@ rm(list = ls())
   source("scripts/run_exploratory_moderator_analyses.R")
   
   # Run analyses with negative contact
+  source("scripts/run_additional_analyses.R")
+  
+  # Run analyses with negative contact
   source("scripts/run_analyses_with_negative_contact.R")
 
   # Run analyses with ingroup contact
@@ -67,6 +70,7 @@ rm(list = ls())
   source("figures/figure-6.R")
   source("figures/figure-7.R")
   source("figures/figure-8.R")
+  source("figures/figure-9.R")
   source("figures/figure-s1.R")
   source("figures/figure-s2.R")
 

### 2022-02-17 scripts/code_measures.R

@@ -16,6 +16,12 @@ rm(list = ls())
     "records/results/coding-measures.csv",
     col_types = "ciiccccccc"
   )
+  
+  # Import results from survey (additional moderator)
+  dr_new <- read_csv(
+    "records/results/coding-for-additional-analyses.csv",
+    col_types = "cicccccc"
+  )
 
   # Import .rds files (data)
   mi <- read_rds("data/mi.rds")
@@ -86,6 +92,40 @@ rm(list = ls())
       values_from = response
     ) %>% 
     arrange(id, sample, var)
+  
+  # Calculate interrater agreement for predictor variable (contact quality)
+  dr_new %>% 
+    pivot_wider(names_from = coder, values_from = ic_quality) %>% 
+    with(., kappa2(ratings = cbind(`Coder 1`, `Coder 2`)))
+  
+  # Resolve disagreements
+  dr_new <- dr_new %>% 
+    mutate(
+      ic_quality = case_when(
+        id == 1045L & var == "cf" ~ "No",
+        id == 1248L & var == "cq" ~ "Yes",
+        id == 1386L & var == "cq" ~ "Yes",
+        id == 1549L & var == "cf" ~ "No",
+        id == 1966L & var == "cf" & name == "Best friend is immigrant (reversed)" ~ "Yes",
+        id == 1966L & var == "cf" & name == "Cross-group friendship" ~ "Yes",
+        id == 1993L & var == "pc" ~ "Yes",
+        id == 1993L & var == "pc" ~ "Yes",
+        id == 2257L & var == "ic" ~ "Yes",
+        id == 2341L & var == "pc" ~ "Yes",
+        id == 284L & var == "cf" ~ "Yes",
+        id == 4002L & var == "pc" ~ "Yes",
+        id == 4005L & var == "cq" ~ "No",
+        id == 4005L & var == "ic" ~ "Yes",
+        id == 4005L & var == "pc" ~ "Yes",
+        TRUE ~ ic_quality
+      )
+    ) %>% 
+    select(id, variable = var, name, ic_quality) %>%
+    distinct()
+  
+  # Add contact quality as additional moderator
+  mo_mi <- left_join(mo_mi, dr_new, by = c("id", "variable", "name")) %>% 
+    select(id:text, ic_direct, ic_quality, pi_personal, pi_specific)
 
   
 # Export ------------------------------------------------------------------

### 2022-02-17 scripts/prepare_data_for_analyses.R

@@ -190,8 +190,8 @@ rm(list = ls())
       .
     )
   dl <- dl %>% 
-    filter(x_var == "ic", is.na(ic_direct), !is.na(r)) %>% 
-    select(-ic_direct) %>% 
+      filter(x_var == "ic", is.na(ic_direct), is.na(ic_quality), !is.na(r)) %>% 
+    select(-ic_direct, -ic_quality) %>% 
     left_join(
       mo_mi %>% 
         filter(var == "ic") %>% 
@@ -209,7 +209,6 @@ rm(list = ls())
       .
     )
   
-  
 
 # Export ------------------------------------------------------------------
 
@@ -221,7 +220,7 @@ rm(list = ls())
       source, note, t1, t2, r_ab, r_bc, r_ac,
       country, region, continent, ingroup, outgroup, study_setting, 
       study_design, study_sample, age, study_intention, publication_status,
-      ic_direct, pi_specific, pi_personal,
+      ic_direct, ic_quality, pi_specific, pi_personal,
       ends_with("to_usa")
     )
   

### 2022-02-17 scripts/run_additional_analyses.R

@@ -39,56 +39,6 @@ rm(list = ls())
   # Import data
   dl <- read_rds("data/dl.rds")
   
-  # Import coding results
-  dm <- read_csv(
-    "records/results/coding-for-additional-analyses.csv",
-    col_types = "cicccccc"
-  )
-  
-  # Calculate interrater agreement
-  dm %>% 
-    pivot_wider(names_from = coder, values_from = ic_quality) %>% 
-    with(., kappa2(ratings = cbind(`Coder 1`, `Coder 2`)))
-  
-  # Resolve disagreements
-  dm <- dm %>% 
-    mutate(
-      ic_quality = case_when(
-        id == 1045L & var == "cf" ~ "No",
-        id == 1248L & var == "cq" ~ "Yes",
-        id == 1386L & var == "cq" ~ "Yes",
-        id == 1549L & var == "cf" ~ "No",
-        id == 1966L & var == "cf" & name == "Best friend is immigrant (reversed)" ~ "Yes",
-        id == 1993L & var == "pc" ~ "Yes",
-        id == 2257L & var == "ic" ~ "Yes",
-        id == 2341L & var == "pc" ~ "Yes",
-        id == 284L & var == "cf" ~ "Yes",
-        id == 4002L & var == "pc" ~ "Yes",
-        id == 4005L & var == "cq" ~ "No",
-        id == 4005L & var == "ic" ~ "Yes",
-        id == 4005L & var == "pc" ~ "Yes",
-        TRUE ~ ic_quality
-      )
-    ) %>% 
-    select(-coder) %>% 
-    distinct()
-  
-  # Add to data
-  dl <- dl %>% 
-    left_join(
-      dm %>% 
-        transmute(
-          id, 
-          x = var, 
-          x_var = "ic", 
-          x_name = name, 
-          x_text = text, 
-          outgroup, 
-          ic_quality
-        ),
-      by = c("id", "x", "x_var", "x_name", "x_text", "outgroup")
-    )
-  
   # Exclude data to test 'strong' version of hypothesis
   dl <- dl %>% 
     filter(

### 2022-02-17 scripts/run_analyses_with_ingroup_contact.R

@@ -14,7 +14,7 @@ rm(list = ls())
   n_warmup <- 1000
   seeds    <- c(6967674, 5768664, 7517370, 3223639)
   options(mc.cores = n_cores)
-  rstan_options(auto_write = TRUE)
+  rstan_options(auto_write = FALSE)
   
   # Functions
   source("scripts/functions.R")

### 2022-02-17 scripts/run_analyses_with_negative_contact.R

@@ -14,7 +14,7 @@ rm(list = ls())
   n_warmup <- 1000
   seeds    <- c(6967674, 5768664, 7517370, 1585380)
   options(mc.cores = n_cores)
-  rstan_options(auto_write = TRUE)
+  rstan_options(auto_write = FALSE)
   
   # Functions
   source("scripts/functions.R")

### 2022-02-17 scripts/run_exploratory_moderator_analyses.R

@@ -17,7 +17,7 @@ rm(list = ls())
   n_iter   <- 8000
   n_warmup <- 1000
   options(mc.cores = n_cores)
-  rstan_options(auto_write = TRUE)
+  rstan_options(auto_write = FALSE)
   
   # Link functions
   r_to_z <- function(r) 0.5 * log( (1 + r) / (1 - r) )
@@ -34,7 +34,8 @@ rm(list = ls())
     mutate(
       age = case_when(
         str_detect(age, "Adults") & !str_detect(age, "Adolescents|Children") ~ "Adults",
-        str_detect(age, "Adolescents|Children") ~ "Adolescents/Children"
+        str_detect(age, "Adolescents") & !str_detect(age, "Children") ~ "Adolescents",
+        str_detect(age, "Children") ~ "Children"
       ),
       publication_status = case_when(
         publication_status == "published" ~ "published",
@@ -61,7 +62,7 @@ rm(list = ls())
   
   # Average effect sizes for multiple (equivalent) outcomes
   es <- es %>% 
-    group_by(id, sample, x, y, x_var, y_var, ic_direct, pi_specific, pi_personal) %>% 
+    group_by(id, sample, x, y, x_var, y_var, ic_direct, ic_quality, pi_specific, pi_personal) %>% 
     summarise(
       n = unique(n), 
       r = mean(r, na.rm = TRUE)
@@ -119,10 +120,10 @@ rm(list = ls())
     mutate(
       ii = row_number(),
       kk = case_when(
-        age != "Adults" ~ 1L,
-        ic_direct != "Directly" ~ 2L,
-        !(study_setting %in% c("Colonization", "Short-term migration")) ~ 3L,
-        study_setting %in% c("Colonization", "Short-term migration") ~ 4L
+        ic_quality == "No" & study_setting == "Short-term migration" ~ 1L,
+        ic_quality == "No" & study_setting != "Short-term migration" ~ 2L,
+        ic_quality == "Yes" & age == "Adults" ~ 3L,
+        ic_quality == "Yes" & age != "Adults" ~ 4L,
       )
     )
   
@@ -148,21 +149,22 @@ rm(list = ls())
   results <- pi_es %>% 
     mutate(
       study_setting = case_when(
-        age != "Adults" | ic_direct == "Indirectly" ~ NA_character_, 
-        str_detect(study_setting, "Colonization|Short-term migration") ~ "Colonization/Short-term migration",
-        TRUE ~ "Other"
[…]

### 2022-02-17 scripts/run_moderator_analyses.R

@@ -17,7 +17,7 @@ rm(list = ls())
   n_iter   <- 8000
   n_warmup <- 1000
   options(mc.cores = n_cores)
-  rstan_options(auto_write = TRUE)
+  rstan_options(auto_write = FALSE)
   
   # Link functions
   r_to_z <- function(r) 0.5 * log( (1 + r) / (1 - r) )
@@ -239,7 +239,8 @@ rm(list = ls())
         ) %>% mutate(
           category = case_when(
             str_detect(category, "Adults") & !str_detect(category, "Adolescents|Children") ~ "Adults",
-            str_detect(category, "Adolescents|Children") ~ "Adolescents/Children"
+            str_detect(category, "Adolescents") & !str_detect(category, "Children") ~ "Adolescents",
+            str_detect(category, "Children") ~ "Children"
           ),
           ii = row_number(),
           kk = as.integer(factor(category))
@@ -277,7 +278,8 @@ rm(list = ls())
   }
 
 
-# Predictor variables -----------------------------------------------------
+
+# Predictor variables (direct/indirect) -----------------------------------
 
   # Load model
   model <- stan_model("models/2l-meta-analysis-categorical-moderators.stan")
@@ -341,6 +343,78 @@ rm(list = ls())
       ))
     )
 
+  # Compile results
+  if (exists("moderators")) {
+    moderators <- bind_rows(moderators, results)
+  } else {
+    moderators <- results
+  }
+
+
+# Predictor variables (quality) -------------------------------------------
+
+  # Load model
+  model <- stan_model("models/2l-meta-analysis-categorical-moderators.stan")
+  
+  # Prepare data list
+  results <- data %>%
+    mutate(
+      moderator = "ic_quality",
+      es = map(
+        y_var,
+        ~filter(dl, x_var == "ic", y_var == .) %>% 
+          group_by(id, sample, ic_direct) %>% 
+          top_n(1, -x_rank) %>% 
+          top_n(1, -y_rank) %>% 
+          group_by(id, sample, x, y, x_var, y_var, category = ic_quality) %>% 
+          summarise(
+            n = unique(n), 
+            r = mean(r, na.rm = TRUE)
+          ) %>% 
+          ungroup() %>% 
+          select(id, sample, n, r, everything()) %>% 
+          mutate(
+            ii = row_number(),
+            jj = as.integer(factor(id)),
+            kk = as.integer(factor(category))
+          ) %>% 
[…]

### 2022-02-17 scripts/run_old_exploratory_moderator_analyses.R

@@ -1,0 +1,204 @@
+rm(list = ls())
+
+# Notes -------------------------------------------------------------------
+
+  #########################################################################
+  # Adjust the number of cores to suit your computing environment (e.g.,  #
+  # run parallel::detectCores() to find the number of available cores).   #
+  #########################################################################
+
+# Library -----------------------------------------------------------------
+
+  # Load packages
+  library(tidyverse); library(rstan); library(tidybayes); library(metacart)
+
+  # Stan options
+  n_cores  <- 8
+  n_iter   <- 8000
+  n_warmup <- 1000
+  options(mc.cores = n_cores)
+  rstan_options(auto_write = TRUE)
+  
+  # Link functions
+  r_to_z <- function(r) 0.5 * log( (1 + r) / (1 - r) )
+  z_to_r <- function(z) ( exp(2 * z) - 1 ) / ( exp(2 * z) + 1 )
+
+  
+# Prepare -----------------------------------------------------------------
+  
+  # Import data
+  dl <- read_rds("data/dl.rds")
+  
+  # Recode variables
+  dl <- dl %>% 
+    mutate(
+      age = case_when(
+        str_detect(age, "Adults") & !str_detect(age, "Adolescents|Children") ~ "Adults",
+        str_detect(age, "Adolescents|Children") ~ "Adolescents/Children"
+      ),
+      publication_status = case_when(
+        publication_status == "published" ~ "published",
+        str_detect(publication_status, "unpublished") ~ "unpublished"
+      ),
+      study_design = ordered(study_design, levels = c(
+        "observational, cross-sectional", "observational, longitudinal", 
+        "quasi-experimental (no random assignment)", "experimental (random assignment)"
+      )),
+      study_sample = ordered(study_sample, levels = c(
+        "convenience sample, students (no random sampling)",
+        "convenience sample, non-students (no random sampling)",
+        "probability or representative sample"
+      ))
+    )
+  
+  # Select outcomes
+  es <- dl %>% 
+    filter(x_var == "ic", y_var %in% c("pi", "ca", "ps")) %>% 
+    group_by(id, sample, y_var) %>% 
+    top_n(1, -x_rank) %>%
[…]

### 2022-02-17 scripts/run_old_moderator_analyses.R

@@ -1,0 +1,705 @@
+rm(list = ls())
+
+# Notes -------------------------------------------------------------------
+
+  #########################################################################
+  # Adjust the number of cores to suit your computing environment (e.g.,  #
+  # run parallel::detectCores() to find the number of available cores).   #
+  #########################################################################
+
+# Library -----------------------------------------------------------------
+
+  # Load packages
+  library(tidyverse); library(rstan); library(tidybayes)
+
+  # Stan options
+  n_cores  <- 8
+  n_iter   <- 8000
+  n_warmup <- 1000
+  options(mc.cores = n_cores)
+  rstan_options(auto_write = TRUE)
+  
+  # Link functions
+  r_to_z <- function(r) 0.5 * log( (1 + r) / (1 - r) )
+  z_to_r <- function(z) ( exp(2 * z) - 1 ) / ( exp(2 * z) + 1 )
+
+  
+# Prepare -----------------------------------------------------------------
+  
+  # Import data
+  dl <- read_rds("data/dl.rds")
+  
+  # Select outcomes
+  es <- dl %>% 
+    filter(x_var == "ic", y_var %in% c("pi", "ca", "ps")) %>% 
+    group_by(id, sample, y_var) %>% 
+    top_n(1, -x_rank) %>%
+    top_n(1, -y_rank) %>% 
+    ungroup()
+  
+  # Average effect sizes for multiple (equivalent) outcomes
+  es <- es %>% 
+    group_by(id, sample, x, y, x_var, y_var) %>% 
+    summarise(
+      n = unique(n), 
+      r = mean(r, na.rm = TRUE)
+    ) %>% 
+    ungroup() %>% 
+    select(id, sample, n, r, everything())
+  
+  # Compile data as lists
+  data <- tibble(
+      y_var = c("pi", "ca", "ps"),
+      es = list(
+        es %>% filter(y_var == "pi"),
+        es %>% filter(y_var == "ca"),
+        es %>% filter(y_var == "ps")
+      )
+    )
+
+# Study setting -----------------------------------------------------------
+
+  # Load model
+  model <- stan_model("models/1l-meta-analysis-categorical-moderators.stan")
+  
+  # Prepare data list
+  results <- data %>% 
+    mutate(
+      moderator = "study_setting",
+      es = map(
+        es,
+        ~left_join(
+          .,
+          dl %>% distinct(id, sample, category = study_setting),
+          by = c("id", "sample")
+        ) %>% filter(
+          !str_detect(category, ",")
[…]

### 2022-02-17 scripts/run_preregistered_analyses.R

@@ -18,7 +18,7 @@ rm(list = ls())
   n_warmup <- 1000
   seeds    <- c(6967674, 5768664, 7517370, 6852246, 9115239, 5279371)
   options(mc.cores = n_cores)
-  rstan_options(auto_write = TRUE)
+  rstan_options(auto_write = FALSE)
   
   # Link functions
   r_to_z <- function(r) 0.5 * log( (1 + r) / (1 - r) )

### 2022-02-17 scripts/run_preregistered_robustness_checks.R

@@ -18,7 +18,7 @@ rm(list = ls())
   n_warmup <- 1000
   seeds    <- c(6967674, 5768664, 7517370)
   options(mc.cores = n_cores)
-  rstan_options(auto_write = TRUE)
+  rstan_options(auto_write = FALSE)
 
   # Link functions
   r_to_z <- function(r) 0.5 * log( (1 + r) / (1 - r) )

### 2022-05-03 manuscript/manuscript.Rmd
revision

@@
 nocite: | 
-  @19, @45, @46, @91, @93, @244, @284, @286, @303, @322, @324, @325, @336, @401, @414, @423, @480, @609, @703, @733, @783, @789, @803, @813, @823, @829, @830, @856, @893, @894, @933, @956, @1020, @1042, @1045, @1114, @1163, @1221, @1248, @1376, @1386, @1395, @1407, @1411, @1412, @1494, @1525, @1549, @1576, @1614, @1658, @1695, @1743, @1762, @1807, @1850, @1891, @1914, @1949, @1966, @1993, @2001, @2023, @2033, @2075, @2257, @2309, @2333, @2341, @2375, @2380, @2381, @2382, @2383, @2385, @2391, @2392, @2394, @2395, @2396, @2397, @2398, @2399, @3000, @3005, @3051, @3054, @3060, @3134, @3196, @3201, @3205, @4000, @4001, @4002, @4003, @4004, @4005, @bracegirdle_disentangling_2022, @sengupta_protect_unpublished
+  @19, @45, @46, @91, @93, @244, @284, @286, @303, @322, @324, @325, @336, @401, @414, @423, @480, @609, @703, @733, @783, @789, @803, @813, @823, @829, @830, @856, @893, @894, @933, @956, @1020, @1042, @1045, @1114, @1163, @1221, @1248, @1376, @1386, @1395, @1407, @1411, @1412, @1494, @1525, @1549, @1576, @1614, @1658, @1695, @1743, @1762, @1807, @1850, @1891, @1914, @1949, @1966, @1993, @2001, @2023, @2033, @2075, @2257, @2309, @2333, @2341, @2375, @2380, @2381, @2382, @2383, @2385, @2391, @2392, @2394, @2395, @2396, @2397, @2398, @2399, @3000, @3005, @3051, @3054, @3060, @3134, @3196, @3201, @3205, @4000, @4001, @4002, @4003, @4004, @4005, @bracegirdle_disentangling_2022, @sengupta_protect_unpublished, @osf_repository
 abstract: 
@@
 
-We prepared a protocol in accordance with the PRISMA-P statement [@moher_preferred_2015] and preregistered it on the Open Science Framework.^[[https://osf.io/ryuev](https://osf.io/ryuev)] Preregistration precludes undisclosed flexibility in study selection, outcome selection, and other decisions that influence effect size estimates—and thus prevents confirmation bias from determining the conclusions of a meta-analysis [@lakens_reproducibility_2016].
+We prepared a protocol in accordance with the PRISMA-P statement [@moher_preferred_2015] and preregistered it on the Open Science Framework.^[[https://osf.io/ryuev/](https://osf.io/ryuev/)] Preregistration precludes undisclosed flexibility in study selection, outcome selection, and other decisions that influence effect size estimates—and thus prevents confirmation bias from determining the conclusions of a meta-analysis [@lakens_reproducibility_2016].
 We report deviations from our preregistered protocol at the end of the Method section.
-We make data, analysis scripts, and the fully reproducible manuscript available online.^[[https://osf.io/w5tqv](https://osf.io/w5tqv)]
+We make data, analysis scripts, and the fully reproducible manuscript available online.^[[https://osf.io/w5tqv/](https://osf.io/w5tqv/)]
 
@@
 
-***Study Design.*** We categorized each study as either observational and cross-sectional, observational and longitudinal, quasi-experimental, experimental, an intervention, or other ($\kappa = .85$).^[While the term ‘observational study’ is sometimes used to refer to the naturalistic observation of behavior, we use it in its broader sense, that is, to refer to studies that do not involve random assignment into experimental conditions [@cochran_planning_1965; @everitt_observational_2005].] We categorized each sample as either a student convenience sample, a non-student convenience sample, a probability or representative sample, or another kind of sample ($\kappa = .73$).
+***Study Design.*** We categorized each study as either correlational and cross-sectional, correlational and longitudinal, quasi-experimental, experimental, an intervention, or other ($\kappa = .85$).
+We categorized each sample as either a student convenience sample, a non-student convenience sample, a probability or representative sample, or another kind of sample ($\kappa = .73$).
 We categorized the age group(s) in each sample as children ($\leq 12$ years), adolescents (13–18 years), or adults ($\geq 18$ years; $\kappa = .64$).
@@
 Most samples focused on relative inequalities that resulted from long-term migration (`r glue('$I = {f_comma(with(distinct(dl, id, sample, study_setting), length(sample[study_setting == "Long-term migration"])))}$')`), slavery (`r glue('$I = {f_comma(with(distinct(dl, id, sample, study_setting), length(sample[study_setting == "Slavery"])))}$')`), colonization (`r glue('$I = {f_comma(with(distinct(dl, id, sample, study_setting), length(sample[study_setting == "Colonization"])))}$')`), and short-term migration (`r glue('$I = {f_comma(with(distinct(dl, id, sample, study_setting), length(sample[study_setting == "Short-term migration"])))}$')`).
-With few exceptions, studies used observational, cross-sectional survey designs.
+With few exceptions, studies used correlational, cross-sectional survey designs.
 Samples sizes ranged from `r with(distinct(dl, id, sample, n), paste0(f_comma(min(n)), " to ", f_comma(max(n)), " ($\\textit{Mdn} = ", f_comma(median(n)), "$)"))`.
@@
 
-Third, the available evidence is almost entirely from cross-sectional, observational studies and thus consistent with alternative explanations for the observed associations.
+Third, the available evidence is almost entirely from cross-sectional, correlational studies and thus consistent with alternative explanations for the observed associations.
 Support for social change could reduce intergroup contact rather than the other way around.
@@
 Another bias that could have affected our findings is that researchers made data-dependent decisions while collecting and analyzing data that are known to inflate false-positive findings [@gelman_statistical_2014; @simmons_false-positive_2011].
-This risk is pertinent to a literature in which most studies are observational, include many measures, and are not preregistered—and, therefore, do not constrain the direction of observed associations or the selection of included variables.
+This risk is pertinent to a literature in which most studies are correlational, include many measures, and are not preregistered—and, therefore, do not constrain the direction of observed associations or the selection of included variables.
 Future research should use preregistration and other methods to prevent undisclosed flexibility in data collection and analysis.

### 2022-05-03 manuscript/manuscript.tex
revision

@@
 et al., 2015) and preregistered it on the Open Science
-Framework.\footnote{\url{https://osf.io/ryuev}} Preregistration
+Framework.\footnote{\url{https://osf.io/ryuev/}} Preregistration
 precludes undisclosed flexibility in study selection, outcome selection,
@@
 analysis scripts, and the fully reproducible manuscript available
-online.\footnote{\url{https://osf.io/w5tqv}}
+online.\footnote{\url{https://osf.io/w5tqv/}}
 
@@
 \textbf{\emph{Study Design.}} We categorized each study as either
-observational and cross-sectional, observational and longitudinal,
+correlational and cross-sectional, correlational and longitudinal,
 quasi-experimental, experimental, an intervention, or other
-(\(\kappa = .85\)).\footnote{While the term `observational study' is
-  sometimes used to refer to the naturalistic observation of behavior,
-  we use it in its broader sense, that is, to refer to studies that do
-  not involve random assignment into experimental conditions (Cochran,
-  1965; Rosenbaum, 2005).} We categorized each sample as either a
-student convenience sample, a non-student convenience sample, a
-probability or representative sample, or another kind of sample
-(\(\kappa = .73\)). We categorized the age group(s) in each sample as
-children (\(\leq 12\) years), adolescents (13--18 years), or adults
-(\(\geq 18\) years; \(\kappa = .64\)).
+(\(\kappa = .85\)). We categorized each sample as either a student
+convenience sample, a non-student convenience sample, a probability or
+representative sample, or another kind of sample (\(\kappa = .73\)). We
+categorized the age group(s) in each sample as children (\(\leq 12\)
+years), adolescents (13--18 years), or adults (\(\geq 18\) years;
+\(\kappa = .64\)).
 
@@
 short-term migration (\(I = 14\)). With few exceptions, studies used
-observational, cross-sectional survey designs. Samples sizes ranged from
+correlational, cross-sectional survey designs. Samples sizes ranged from
 64 to 49,764 (\(\textit{Mdn} = 287\)). Unlike most psychological
@@
 Third, the available evidence is almost entirely from cross-sectional,
-observational studies and thus consistent with alternative explanations
+correlational studies and thus consistent with alternative explanations
 for the observed associations. Support for social change could reduce
@@
 This risk is pertinent to a literature in which most studies are
-observational, include many measures, and are not preregistered---and,
+correlational, include many measures, and are not preregistered---and,
 therefore, do not constrain the direction of observed associations or
@@
 
+\leavevmode\hypertarget{ref-osf_repository}{}%
+Blinded for Review. (2022). \emph{Meta-analysis of the {`ironic'}
+effects of intergroup contact} {[}Dataset{]}.
+\url{https://osf.io/w5tqv/?view_only=5cbf7ad5b2b449a7a0f4ada0337b802a}
+
 \leavevmode\hypertarget{ref-blumer_race_1958}{}%
@@
 Global}.
-
-\leavevmode\hypertarget{ref-cochran_planning_1965}{}%
-Cochran, W. G. (1965). The planning of observational studies of human
-populations. \emph{Journal of the Royal Statistical Society},
-\emph{128}(2), 234--266. \url{https://doi.org/10.2307/2344179}
 
@@
 
-\leavevmode\hypertarget{ref-everitt_observational_2005}{}%
-Rosenbaum, P. R. (2005). Observational study. In B. S. Everitt \& D. C.
-Howell (Eds.), \emph{Encyclopedia of statistics in behavioral science}
-(3rd ed., pp. 1451--1462). John Wiley \& Sons, Ltd.
-\url{https://doi.org/10.1002/0470013192}
-
 \leavevmode\hypertarget{ref-703}{}%

### 2022-05-03 figures/figure-2.R

@@ -148,8 +148,8 @@ rm(list = ls())
         study_design,
         "experimental (random assignment)" = "experimental",
         "quasi-experimental (no random assignment)" = "quasi-experimental",
-        "observational, longitudinal" = "observational,\nlongitudinal",
-        "observational, cross-sectional" = "observational,\ncross-sectional"
+        "observational, longitudinal" = "correlational,\nlongitudinal",
+        "observational, cross-sectional" = "correlational,\ncross-sectional"
       )
     ) %>%
     group_by(study_design) %>% 

### 2022-05-05 manuscript/manuscript.Rmd
update reference

@@
 More broadly, intergroup contact is associated with more support for social change if it satisfies disadvantaged-group members' need for empowerment, that is, when they felt that the advantaged-group members they had contact with listened to what they had to say and perceived them as competent and intelligent [@hassler_need_2021].^[We did not consider whether, in certain conditions, positive contact might increase support for social change in disadvantaged groups because only few studies measured the relevant moderator variables and because our analyses relied on correlation matrices which are not enough to estimate interaction effects.
-For the latter reason, we also did not consider whether positive and negative contact might interact in their effects on support for social change [see @albzour_talking_inpress].] Further, we did not consider contact between different disadvantaged groups, which has been found to increase support for social change among the disadvantaged [@dixon_divide_2015; @93].
+For the latter reason, we also did not consider whether positive and negative contact might interact in their effects on support for social change [see @albzour_talking_2022].] Further, we did not consider contact between different disadvantaged groups, which has been found to increase support for social change among the disadvantaged [@dixon_divide_2015; @93].
 Therefore, this meta-analysis could not provide a complete answer to the question whether, on balance, intergroup contact helps or hinders social change.

### 2022-05-05 manuscript/manuscript.tex
update reference

@@
   whether positive and negative contact might interact in their effects
-  on support for social change (see Albzour et al., in press).} Further,
-we did not consider contact between different disadvantaged groups,
-which has been found to increase support for social change among the
+  on support for social change (see Albzour et al., 2022).} Further, we
+did not consider contact between different disadvantaged groups, which
+has been found to increase support for social change among the
 disadvantaged (Dixon et al., 2015, 2017). Therefore, this meta-analysis
@@
 \begin{CSLReferences}{1}{0}
-\leavevmode\hypertarget{ref-albzour_talking_inpress}{}%
+\leavevmode\hypertarget{ref-albzour_talking_2022}{}%
 Albzour, M., Bady, Z., Elcheroth, E., Penic, S., Nasser, R., Reimer, N.
-K., \& Green, E. G. T. (in press). Talking to a (segregation) wall:
+K., \& Green, E. G. T. (2022). Talking to a (segregation) wall:
 Intergroup contact and attitudes toward normalization with {Israelis}
 among {Palestinians} from the occupied territories. \emph{Political
-Psychology}.
+Psychology}. \url{https://doi.org/10.1111/pops.12816}
 
